### 2017-12-31 YSPH Prospectus/RSV season variability prospectus.tex
YSPH thesis prospectus

\documentclass{article}
\usepackage[backend=bibtex,sorting=none,autocite=superscript,style=numeric]{biblatex}
\renewcommand{\cite}[1]{\autocite{#1}}
\bibliography{../Thesis.bib}

\usepackage{titling}
\setlength{\droptitle}{-.5in}

%\usepackage{draftwatermark}
%\SetWatermarkLightness{.9}
%\SetWatermarkScale{4}

\title{Regional variation in onset and offset of respiratory syncytial virus season in Connecticut}
\author{Author & Ben Artin, YSPH/YSM 2018}
\preauthor{\begin{center}\begin{tabular}{r@{: }l}}
\postauthor{\\ Thesis advisor & Daniel Weinberger, PhD \\ Thesis reader & Virginia Pitzer, ScD \end{tabular}\end{center}}

\begin{document}

\maketitle

\section{Study Aims}

I propose to analyze existing data about respiratory syncytial virus (RSV) infections among infants hospitalized in Connecticut between 1997 and 2013, with the goal of establishing an association between geographic subdivisions (by ZIP code) and RSV season onset and duration. Based on the results of that analysis, I intend to propose a refinement to the guidelines for RSV immunoprophylaxis within Connecticut, aimed at optimizing the use of RSV immunoprophylaxis without adversely affecting RSV infection outcomes.

\section{Hypothesis}

RSV season onset changepoint in ZIP code A $\neq$ RSV season onset changepoint in ZIP code B, for any ZIP codes A and B (A $\neq$ B) in Connecticut; similarly for season offset changepoint.

\section{Background \& Rationale}

RSV causes seasonal respiratory illness of varying severity. RSV infection in infants is often associated with more severe illness (including bronchiolitis and pneumonia), sometimes requiring hospitalization. Several groups of infants are at higher risk of severe illness, hospitalization, and complications; these groups include premature and young infants, infants with lung and heart disease, and immunosuppressed children. \cite{CentersforDiseaseControlandPrevention:368RENtm}

While no targeted treatment exists for RSV infection, preventative monoclonal antibody medication (palivizumab) is available. Due to its high cost (in thousands of USD per patient per year) and its inconvenience (requiring monthly healthcare visits during RSV season), palivizumab immunoprophylaxis is recommended only for high-risk infants, and only during RSV season. \cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj,AmericanAcademyofPediatricsCommitteeonInfectiousDiseasesandCommitteeonFetusandNewborn:2003ug}

With exception of Florida, these guidelines are based on analysis of RSV seasonality on state and national level. \cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseasesandCommitteeonFetusandNewborn:2003ug} However, recent research has revealed regional variation in RSV season patterns within Connecticut. \cite{Noveroske:y4fi3188} This variation is potentially large enough to guide recommendations regarding administration of palivizumab, and therefore lower healthcare burden of RSV immunoprophylaxis.

Since healthcare burden of RSV immunoprophylaxis is primarily tied to the number of doses administered, which is mainly determined by the duration and onset of RSV season, analysis of RSV season duration and onset is needed to optimize use of RSV immunopropylaxis in Connecticut.

Prior analysis of regional variation in RSV seasonality within Connecticut established geographic variability in timing of peak RSV incidence, but did not consider duration or onset of RSV season. \cite{Noveroske:y4fi3188} The analysis I propose is a novel analysis of the existing data.

\section{Methods}

This will be a cross-sectional study of children less than 2 years old infected RSV infection between 1997 and 2013 in Connecticut.

The study population will be sampled using ICD-10 data from hospital admission records of all hospitalizations in Connecticut between 1997 and 2013, as reported to State of Connecticut Office of Health Care Access. The size of this sample is approximately 10000.

Sampled subjects will be aggregated by ZIP code of residence, and for each ZIP code RSV season onset and offset will be estimated using changepoint analysis. Changepoint analysis will be performed in R.

\section{MPH Competencies}

\begin{itemize}
	\item Demonstrate a knowledge base in the disciplines of biostatistics, chronic and infectious disease epidemiology, health systems, public policy, social and behavioral sciences, and environmental health.
	\item Apply basic research skills to specific public health problems in both group and individual settings, including the ability to define problems; construct, articulate and test hypotheses; draw conclusions; and communicate findings to a variety of audiences.
	\item Apply public health concepts, principles, and methodologies obtained through formal course work to actual problems experienced in the community or work environment.
	\item Describe and critically evaluate approaches for the prevention and control of infectious diseases and define the key issues to their effective use.
	\item Apply principles and concepts obtained through coursework to design and implement studies on the etiology, detection, prevention or control of infectious diseases in the laboratory and field.
\end{itemize}

\printbibliography

\end{document}

### 2017-12-31 Analysis/RSV.Rmd
Added RSV analysis code

---
title: "RSV"
output: html_notebook
---

```{r setup, include=FALSE, error=FALSE, warning=FALSE, message=FALSE}
install.packages(c("dplyr", "zipcode", "reshape", "mgcv", "ggplot2", "gridExtra", "devtools"))
library(devtools)
install_github("gavinsimpson/tsgam")
install_github("kassambara/easyGgplot2")
install_github("airbornemint/outbreak-predict")

library(reshape)
library(plyr)
library(dplyr)
library(zipcode)
library(mgcv)
library(tsgam)
library(ggplot2)
library(easyGgplot2)
library(utils)
library(outbreakpredict)
data(zipcode)
set.seed(0)
```

```{r}
rsvWeek = function(weeki) {
  (weeki + 26) %% 52 - 26
}

dataset = read.csv("../ct rsv time series.csv", header=TRUE, colClasses=c("patzip"="character"))
# Add week-of-year, with zero = end of June, drop first 5.5 years because of coding differences
dataset = dataset %>%
  mutate(weekiadj=round(dataset$weeki * 364 / 365.25), weekofyear=rsvWeek(weekiadj), year=1990 + (weekiadj + 26) %/% 52) %>%
  filter(weeki > 5.5*52) %>%
  filter(weeki < 22.5*52)
# Add state based on zipcode and drop everything not in CT
zipState = zipcode %>% select(zip, state)
dataset = dataset %>% 
  left_join(zipcode %>% select(zip, state), by=c("patzip"="zip")) %>% 
  filter(state=="CT")
# Add county based on zipcode
countyByZip = read.csv("../ct counties.csv", header=TRUE, colClasses=c("zip"="character"))
counties = countyByZip %>% select(county) %>% distinct()
dataset = dataset %>% inner_join(countyByZip, by=c("patzip"="zip"))

# Sort counties by total RSV
totalRSVByCounty = dataset %>%
  group_by(county) %>% 
  summarize(total_rsv=sum(rsv)) %>%
  arrange(total_rsv) %>%
  mutate(county=factor(county, county))

rsvCounties = totalRSVByCounty$county
rsvYears = sort(unique(dataset$year))
rsvWeekRange = sort(unique(dataset$weeki))
rsvWeekOfYearRange = sort(unique(dataset$weekofyear))

dataset = dataset %>%
  mutate(county=factor(county, levels=levels(rsvCounties)))

```

```{r}
ggplot(dataset %>% 
         group_by(weeki) %>%
         summarize(rsv=sum(rsv)), 
       aes(x=weeki, y=rsv)) +
  geom_hline(aes(yintercept = 0)) +
  geom_line() +
  labs(y="RSV cases/week", x="Time", title="All counties")

plots = lapply(rsvCounties, function(c) {
  ggplot(dataset %>% 
           filter(county==c) %>%
           group_by(weeki) %>%
           summarize(rsv=sum(rsv)), 
         aes(x=weeki, y=rsv)) +
    geom_hline(aes(yintercept = 0)) +
    geom_line() +
    labs(y="RSV cases/week", x="Time", title=c)
})

ggplot2.multiplot(plotlist=plots, cols=4)

```

```{r include=FALSE}
# Reshape counties into columns and add column for total
rsvByCountyAndWeekOfYear = dataset %>%
  group_by(county, weekofyear) %>%
  summarize(rsv=sum(rsv)) %>%
  group_by(weekofyear) %>%
  do(rbind(., as.data.frame(.) %>%
             summarize(county="total", weekofyear=max(weekofyear), rsv=sum(rsv))
           ))

rsvForAllCountiesByWeekOfYear = rsvByCountyAndWeekOfYear %>%
  melt(id=c("weekofyear", "county"), measured=c("rsv")) %>%
  cast(weekofyear ~ county + variable) %>%
  rename_all(funs(gsub("_rsv", "", .)))

maxRSVByCounty = rsvByCountyAndWeekOfYear %>%
  group_by(county) %>% 
  summarize(max_rsv=max(rsv))

rsvRelForAllCountiesByWeekOfYear = rsvByCountyAndWeekOfYear %>%
  inner_join(maxRSVByCounty, by="county") %>%
  mutate(rsv_rel=rsv/max_rsv) %>%
  select(-max_rsv, -rsv) %>%
  melt(id=c("weekofyear", "county"), measured=c("rsv_rel")) %>%
  cast(weekofyear ~ county + variable)

allCountiesTS = rsvForAllCountiesByWeekOfYear %>%
  arrange(weekofyear) %>%
  select(-weekofyear) %>%
  ts(frequency=1, start=c(-26, 1))

allCountiesRelTS = rsvRelForAllCountiesByWeekOfYear %>%
  arrange(weekofyear) %>%
  select(-weekofyear) %>%
  ts(frequency=1, start=c(-26, 1))

plot.ts(allCountiesTS, nc=1)
plot.ts(allCountiesRelTS, nc=1, plot.type="single", col=rainbow(8), lwd=2)
```

```{r include=FALSE}
# Drop counties in which max # of RSV cases in a week is <100
maxRSVByInterestingCounty = maxRSVByCounty %>% filter(max_rsv > 50)

rsvForInterestingCountiesByWeekOfYear = rsvByCountyAndWeekOfYear %>%
  inner_join(maxRSVByInterestingCounty, by="county") %>%
  select(-max_rsv) %>%
  melt(id=c("weekofyear", "county"), measured=c("rsv", "rsv_rel")) %>%
  cast(weekofyear ~ county + variable)

rsvRelForInterestingCountiesByWeekOfYear = rsvByCountyAndWeekOfYear %>%
  inner_join(maxRSVByInterestingCounty, by="county") %>%
  mutate(rsv_rel=rsv/max_rsv) %>%
  select(-max_rsv, -rsv) %>%
  melt(id=c("weekofyear", "county"), measured=c("rsv_rel")) %>%
  cast(weekofyear ~ county + variable)

interestingCountiesTS = rsvForInterestingCountiesByWeekOfYear %>%
  arrange(weekofyear) %>%
  select(-weekofyear) %>%
  ts(frequency=1, start=c(-26, 1))

interestingCountiesRelTS = rsvRelForInterestingCountiesByWeekOfYear %>%
  arrange(weekofyear) %>%
  select(-weekofyear) %>%
  ts(frequency=1, start=c(-26, 1))

plot.ts(interestingCountiesTS, nc=1)
plot.ts(interestingCountiesRelTS, nc=1, plot.type="single", col=rainbow(5), lwd=2)
```

```{r}
outbreak.calc.unprotected = function(model, params, time, strategies) {
  # Get model predictions for given (randomized) param values
  time = time + 0.5
  predictors = model %>% predict(data.frame(time=time), type="lpmatrix")
  fit = predictors %*% params

  # Map spline fit back to data
  fit = fit %>% model$family$linkinv()

  # Calculate total # of unprotected cases for each strategy
  unprotected = as.data.frame(lapply(strategies, function(strat) {
    sum(fit * (1 - sapply(time, strat)))
  }))

  # Calculate total # of cases 
  total = sum(fit)

  unprotected %>% 
    rename_all(funs(
      sprintf("%s.count", .)
    )) %>%
    cbind(
      (unprotected / total) %>%
        rename_all(funs(
          sprintf("%s.frac", .)
        ))
    ) %>% 
    mutate(total=total)
}
```

```{r}
eps = .05
seasonThreshold = 0.025
rsvTime = dataset$weekofyear
modelTime = data.frame(time=seq(min(rsvTime) - 1 + eps, max(rsvTime), eps))

rsvCountyGroups = data.frame(county=rsvCounties) %>%
  mutate(
    group.all=TRUE,
    group.lowIncidence=county %in% c("Tolland", "Windham", "Middlesex", "Litchfield")
  )

ppxDuration = 24 # weeks

evalStrategy = function(start, end, time) {
  as.numeric((time > rsvWeek(start)) && (time < rsvWeek(end)))
}

evalOnsetStrategy = function(start, time) {
  as.numeric((time > rsvWeek(start)) && (time < rsvWeek(start + ppxDuration)))
}

evalOffsetStrategy = function(end, time) {
  as.numeric((time > rsvWeek(end - ppxDuration)) && (time < rsvWeek(end)))
}

ppxFixedStrategies = function(c=NULL) {
  stateOnset = stateThresholds$onset.median
  stateOffset = stateThresholds$offset.median

  if (!is.null(c)) {
    countyOnset = (thresholdsByCounty %>% filter(county==c))$onset.median
    countyOffset = (thresholdsByCounty %>% filter(county==c))$offset.median
  }

  list(
    # never=function(time) { 0 },
    # always=function(time) { 1 },
    aap=function(time) {
      evalOnsetStrategy(strptime("11-15", format="%m-%d")$yday / 7, time)
    },
    stateOnset=function(time) {
      evalOnsetStrategy(stateOnset, time)
    },
    stateOffset=function(time) {
      evalOffsetStrategy(stateOffset, time)
    },
    countyOnset=function(time) {
      evalOnsetStrategy(countyOnset, time)
    },
    countyOffset=function(time) {
      evalOffsetStrategy(countyOffset, time)
    }
  )
}

ppxSlidingStrategies = function(c=NULL, y=NULL) {
  if (!is.null(y) && !is.null(c)) {
    stateSlidingOnset = (stateThresholdsByWindow %>% filter(year==y))$onset.median
    stateSlidingOffset = (stateThresholdsByWindow %>% filter(year==y))$offset.median
  }

  list(
    stateSlidingOnset=function(time) {
      evalOnsetStrategy(stateSlidingOnset, time)
    },
    stateSlidingOffset=function(time) {
      evalOffsetStrategy(stateSlidingOffset, time)
    }
  )
}

slidingWindowDuration = 3 # Years

```

```{r}
stateObs = dataset %>% 
  rename(time=weekofyear) %>% 
  group_by(time) %>% 
  summarize(rsv=sum(rsv)) %>% 
  mutate(rsv.cum=cumsum(rsv), rsv.cum.frac=rsv.cum / sum(rsv)) %>% 
  as.data.frame()

stateModel = gam(rsv ~ s(time, k=20, bs="cp", m=3), family=poisson, data=stateObs)

statePred = stateModel %>% 
  predict(type="response", newdata=modelTime, se.fit=TRUE)

statePred = modelTime %>% 
  cbind(data.frame(rsv.fit=statePred$fit, rsv.fit.se=statePred$se.fit)) %>%
  cbind(stateModel %>% outbreak.predict.timeseries(modelTime, function(model, params, newdata) { outbreak.calc.cum(model, params, newdata) })) %>%
  rename(rsv.cum.fit.lower=lower, rsv.cum.fit.upper=upper, rsv.cum.fit=median)

stateThresholds = stateModel %>%
  outbreak.predict.scalars(
    modelTime,
    function(model, params, newdata) { 
      outbreak.calc.thresholds(model, params, newdata$time, onset=seasonThreshold, offset=1 - seasonThreshold)
    }
  )

summarizeCountyGroups = function(data) {
  rbind(
      as.data.frame(data) %>%
        select(county, time, rsv), 
      as.data.frame(data) %>%
        filter(group.all==TRUE) %>%
        summarize(county="all", time=max(time), rsv=sum(rsv)),
      as.data.frame(data) %>%
        filter(group.lowIncidence==TRUE) %>%
        summarize(county="lowIncidence", time=max(time), rsv=sum(rsv))
    )  
}
```

```{r}
stateObsByWindow = dataset %>% 
  mutate(time=weeki) %>% 
  group_by(time, year, weekofyear) %>% 
  summarize(rsv=sum(rsv)) %>%
  as.data.frame()

total = data.frame(time=stateObsByWindow$time, rsv=0)

for (idx in seq(1, slidingWindowDuration)) {
  total = total %>%
    inner_join(stateObsByWindow %>%
                 mutate(time=time + 52 * idx) %>%
                 select(time, rsv),
               by="time"
               ) %>%
    mutate(rsv=rsv.x + rsv.y) %>%
    select(time, rsv)
}

stateObsByWindow = stateObsByWindow %>%
  select(-rsv) %>%
  inner_join(total, by="time") %>%
  group_by(year) %>%
  mutate(rsv.cum=cumsum(rsv), rsv.cum.frac=rsv.cum / sum(rsv)) %>% 
  select(-time) %>%
  rename(time=weekofyear) %>%
  filter(year >= min(rsvYears) + slidingWindowDuration) %>%
  as.data.frame()

rsvWindowYears = unique(stateObsByWindow$year)

statePredByWindow = data.frame()
stateThresholdsByWindow = data.frame()

progress = txtProgressBar(max=length(rsvWindowYears), style=3)
idx = 0

for (y in rsvWindowYears) {

  stateYearObs = stateObsByWindow %>% filter(year==y)
  stateYearModel = gam(rsv ~ s(time, k=5, bs="cp", m=3), family=poisson, data=stateYearObs)

  stateYearPred = stateYearModel %>% 
    predict(type="response", newdata=modelTime, se.fit=TRUE)

  stateYearPred = modelTime %>% 
    cbind(data.frame(rsv.fit=stateYearPred$fit, rsv.fit.se=stateYearPred$se.fit)) %>%
    cbind(stateYearModel %>% outbreak.predict.timeseries(modelTime, function(model, params, newdata) { outbreak.calc.cum(model, params, newdata) })) %>%
    rename(rsv.cum.fit.lower=lower, rsv.cum.fit.upper=upper, rsv.cum.fit=median) %>%
    mutate(year=y)

  statePredByWindow = statePredByWindow %>% rbind(stateYearPred)

  stateYearThresholds = stateYearModel %>%
    outbreak.predict.scalars(
      modelTime,
      function(model, params, newdata) { outbreak.calc.thresholds(model, params, newdata$time, onset=seasonThreshold, offset=1 - seasonThreshold) }
    ) %>%
    mutate(year=y)

  stateThresholdsByWindow = stateThresholdsByWindow %>% rbind(stateYearThresholds)

  idx = idx + 1
  setTxtProgressBar(progress, idx)
}
```

```{r}
makeStateWindowPlots = function(c, plotter) {
  lapply(rsvWindowYears, function(y) {
    stateYearObs = stateObsByWindow %>% filter(year==y)
    stateYearPred = statePredByWindow %>% filter(year==y)
    stateYearThresholds = stateThresholdsByWindow %>% filter(year==y)
    plotter(y, stateYearObs, stateYearPred, stateYearThresholds)
  })
}

# Plot RSV cases with model prediction 
ggplot2.multiplot(plotlist=makeStateWindowPlots(rsvWindowYears, function(y, stateYearObs, stateYearPred, stateYearThresholds) {
  ggplot(stateYearObs, aes(x=time)) +
    geom_ribbon(data=stateYearPred, aes(ymin = rsv.fit - rsv.fit.se, ymax = rsv.fit + rsv.fit.se), alpha = 0.2) +
    geom_line(data=stateYearPred, aes(y=rsv.fit)) +
    geom_hline(aes(yintercept = 0)) +
    geom_point(aes(y=rsv), shape=20) +
    annotate("rect",
             xmin=stateYearThresholds$onset.lower,
             xmax=stateYearThresholds$onset.upper,
             ymin=-Inf, ymax=Inf, alpha=.25) +
    annotate("rect",
             xmin=stateYearThresholds$offset.lower,
             xmax=stateYearThresholds$offset.upper,
             ymin=-Inf, ymax=Inf, alpha=.25) +
    labs(y="RSV", x="Time", title=y)
}), cols=4)

# Plot RSV cumulative cases with model prediction 
ggplot2.multiplot(plotlist=makeStateWindowPlots(rsvWindowYears, function(y, stateYearObs, stateYearPred, stateYearThresholds) {
  ggplot(stateYearObs, aes(x=time)) +
    geom_hline(aes(yintercept = 0)) +
    geom_point(shape=20, aes(y=rsv.cum)) +
    annotate("rect", 
             xmin=stateYearThresholds$onset.lower, 
             xmax=stateYearThresholds$onset.upper, 
             ymin=-Inf, ymax=Inf, alpha=.25) +
    annotate("rect", 
             xmin=stateYearThresholds$offset.lower, 
             xmax=stateYearThresholds$offset.upper, 
             ymin=-Inf, ymax=Inf, alpha=.25) +
    labs(y="RSV", x="Time", title=y)
}), cols=4)

# Plot RSV cumulative case % with model prediction 
ggplot2.multiplot(plotlist=makeStateWindowPlots(rsvWindowYears, function(y, stateYearObs, stateYearPred, stateYearThresholds) {
  ggplot(stateYearObs, aes(x=time)) +
    geom_hline(aes(yintercept = 0)) +
    geom_hline(aes(yintercept=seasonThreshold), color=gray(.5)) +
    geom_hline(aes(yintercept=1 - seasonThreshold), color=gray(.5)) +
    geom_ribbon(data=stateYearPred, aes(ymin=rsv.cum.fit.lower, ymax=rsv.cum.fit.upper), alpha=0.2) +
    geom_line(data=stateYearPred, aes(y=rsv.cum.fit)) +
    geom_point(shape=20, aes(y=rsv.cum.frac)) +
    annotate("rect", 
             xmin=stateYearThresholds$onset.lower, 
             xmax=stateYearThresholds$onset.upper, 
             ymin=-Inf, ymax=Inf, alpha=.25) +
    annotate("rect", 
             xmin=stateYearThresholds$offset.lower, 
             xmax=stateYearThresholds$offset.upper, 
             ymin=-Inf, ymax=Inf, alpha=.25) +
    labs(y="RSV", x="Time", title=y)
}), cols=4)

# Zoom in on onsets
ggplot2.multiplot(plotlist=makeStateWindowPlots(rsvWindowYears, function(y, stateYearObs, stateYearPred, stateYearThresholds) {
  ggplot(stateYearObs, aes(x=time)) +
    coord_cartesian(
      xlim=c(min(stateYearThresholds$onset.lower) - 1, max(stateYearThresholds$onset.upper) + 1),
      ylim=c(0, 0.2)
    ) +
    geom_hline(aes(yintercept=0)) +
    geom_hline(aes(yintercept=seasonThreshold), color=gray(.5)) +
    geom_hline(aes(yintercept=1 - seasonThreshold), color=gray(.5)) +
    geom_ribbon(data=stateYearPred, aes(ymin=rsv.cum.fit.lower, ymax=rsv.cum.fit.upper), alpha=0.2) +
    geom_line(data=stateYearPred, aes(y=rsv.cum.fit)) +
    geom_point(shape=20, aes(y=rsv.cum.frac)) +
    annotate("rect", 
             xmin=stateYearThresholds$onset.lower, 
             xmax=stateYearThresholds$onset.upper, 
             ymin=-Inf, ymax=Inf, alpha=.25) +
    annotate("rect", 
             xmin=stateYearThresholds$offset.lower, 
             xmax=stateYearThresholds$offset.upper, 
             ymin=-Inf, ymax=Inf, alpha=.25) +
    labs(y="RSV", x="Time", title=y)
}), cols=4)

# Zoom in on offsets
ggplot2.multiplot(plotlist=makeStateWindowPlots(rsvWindowYears, function(y, stateYearObs, stateYearPred, stateYearThresholds) {
  ggplot(stateYearObs, aes(x=time)) +
    coord_cartesian(
      xlim=c(min(stateYearThresholds$offset.lower) - 1, max(stateYearThresholds$offset.upper) + 1),
      ylim=c(0.8, 1)
    ) +
    geom_hline(aes(yintercept=0)) +
    geom_hline(aes(yintercept=seasonThreshold), color=gray(.5)) +
    geom_hline(aes(yintercept=1 - seasonThreshold), color=gray(.5)) +
    geom_ribbon(data=stateYearPred, aes(ymin=rsv.cum.fit.lower, ymax=rsv.cum.fit.upper), alpha=0.2) +
    geom_line(data=stateYearPred, aes(y=rsv.cum.fit)) +
    geom_point(shape=20, aes(y=rsv.cum.frac)) +
    annotate("rect", 
             xmin=stateYearThresholds$onset.lower, 
             xmax=stateYearThresholds$onset.upper, 
             ymin=-Inf, ymax=Inf, alpha=.25) +
    annotate("rect", 
             xmin=stateYearThresholds$offset.lower, 
             xmax=stateYearThresholds$offset.upper, 
             ymin=-Inf, ymax=Inf, alpha=.25) +
    labs(y="RSV", x="Time", title=y)
}), cols=4)

```

```{r}
onset = ggplot(stateThresholdsByWindow) +
  geom_errorbar(aes(ymin=onset.lower, ymax=onset.upper, x=year), width=.25) + 
  labs(x="RSV Season Onset")
offset = ggplot(stateThresholdsByWindow) +
  geom_errorbar(aes(ymin=offset.lower, ymax=offset.upper, x=year), width=.25) + 
  labs(x="RSV Season Offset")

ggplot2.multiplot(plotlist=list(onset, offset), cols=2)

```

```{r}
obsByCounty = dataset %>% 
  rename(time=weekofyear) %>% 
  group_by(county, time) %>% 
  summarize(rsv=sum(rsv)) %>% 
  left_join(rsvCountyGroups, by="county") %>%
  group_by(time) %>%
  do(summarizeCountyGroups(.)) %>%
  group_by(county) %>% 
  mutate(rsv.cum=cumsum(rsv), rsv.cum.frac=rsv.cum / sum(rsv)) %>% 
  as.data.frame()

predByCounty = data.frame()
thresholdsByCounty = data.frame()
fixedStratUnprotectedByCounty = data.frame()

progress = txtProgressBar(max=length(levels(obsByCounty$county)), style=3)
idx = 0

for (c in levels(obsByCounty$county)) {
  countyObs = obsByCounty %>% filter(county==c)
  countyModel = gam(rsv ~ s(time, k=20, bs="cp", m=3), family=poisson, data=countyObs)

  countyPred = countyModel %>% 
    predict(type="response", newdata=modelTime, se.fit=TRUE)

  countyPred = modelTime %>% 
    cbind(data.frame(rsv.fit=countyPred$fit, rsv.fit.se=countyPred$se.fit)) %>%
    cbind(countyModel %>% outbreak.predict.timeseries(modelTime, function(model, params, newdata) { outbreak.calc.cum(model, params, newdata) })) %>%
    rename(rsv.cum.fit.lower=lower, rsv.cum.fit.upper=upper, rsv.cum.fit=median) %>%
    mutate(county=factor(c, levels=levels(obsByCounty$county)))

  predByCounty = predByCounty %>% rbind(countyPred)

  countyThresholds = countyModel %>%
    outbreak.predict.scalars(
      modelTime,
      function(model, params, newdata) { 
        outbreak.calc.thresholds(model, params, newdata$time, onset=seasonThreshold, offset=1 - seasonThreshold)
      }
    ) %>%
    mutate(county=factor(c, levels=levels(obsByCounty$county)))

  thresholdsByCounty = thresholdsByCounty %>% rbind(countyThresholds)

  countyUnprotected = countyModel %>%
    outbreak.predict.scalars(
      modelTime,
      function(model, params, newdata) { 
        outbreak.calc.unprotected(model, params, newdata$time, ppxFixedStrategies(c))
      }
    ) %>%
    mutate(county=factor(c, levels=levels(obsByCounty$county)))

  fixedStratUnprotectedByCounty = fixedStratUnprotectedByCounty %>% rbind(countyUnprotected)

  idx = idx + 1
  setTxtProgressBar(progress, idx)
}

```

```{r}
makeCountyPlots = function(counties, plotter) {
  lapply(counties, function(c) {
    countyObs = obsByCounty %>% filter(county==c)
    countyPred = predByCounty %>% filter(county==c)
    countyThresholds = thresholdsByCounty %>% filter(county==c)
    plotter(c, countyObs, countyPred, countyThresholds)
  })
}

makeCountyYearPlots = function(c, plotter) {
  lapply(rsvYears, function(y) {
    countyYearObs = obsByCountyYear %>% filter(county==c, year==y)
    countyYearPred = predByCountyYear %>% filter(county==c, year==y)
    countyYearThresholds = thresholdsByCountyYear %>% filter(county==c, year==y)
    plotter(c, y, countyYearObs, countyYearPred, countyYearThresholds)
  })
}

# Plot RSV cases with model prediction 
ggplot_cases = function(obs, pred, thresholds, title) {
  ggplot(obs, aes(x=time)) +
    geom_ribbon(data=pred, aes(ymin = rsv.fit - rsv.fit.se, ymax = rsv.fit + rsv.fit.se), alpha = 0.2) +
    geom_line(data=pred, aes(y=rsv.fit)) +
    geom_hline(aes(yintercept = 0)) +
    geom_point(aes(y=rsv), shape=20) +
    annotate("rect",
             xmin=thresholds$onset.lower,
             xmax=thresholds$onset.upper,
             ymin=-Inf, ymax=Inf, alpha=.25) +
    annotate("rect",
             xmin=thresholds$offset.lower,
             xmax=thresholds$offset.upper,
             ymin=-Inf, ymax=Inf, alpha=.25) +
    labs(y="RSV cases, #", x="Week of year", title=title)
}

# Plot RSV cumulative cases (no model prediction)
ggplot_cum_cases = function(obs, pred, thresholds, title) {
  ggplot(obs, aes(x=time)) +
    geom_hline(aes(yintercept = 0)) +
    geom_point(shape=20, aes(y=rsv.cum)) +
    annotate("rect", 
             xmin=thresholds$onset.lower, 
             xmax=thresholds$onset.upper, 
             ymin=-Inf, ymax=Inf, alpha=.25) +
    annotate("rect", 
             xmin=thresholds$offset.lower, 
             xmax=thresholds$offset.upper, 
             ymin=-Inf, ymax=Inf, alpha=.25) +
    labs(y="RSV cumulative cases, #", x="Week of year", title=title)

}

# Plot RSV cumulative case percentage with model prediction
ggplot_cum_cases_pct = function(obs, pred, thresholds, title) {
  ggplot(obs, aes(x=time)) +
    geom_hline(aes(yintercept = 0)) +
    geom_hline(aes(yintercept=seasonThreshold), color=gray(.5)) +
    geom_hline(aes(yintercept=1 - seasonThreshold), color=gray(.5)) +
    geom_ribbon(data=pred, aes(ymin=rsv.cum.fit.lower, ymax=rsv.cum.fit.upper), alpha=0.2) +
    geom_line(data=pred, aes(y=rsv.cum.fit)) +
    geom_point(shape=20, aes(y=rsv.cum.frac)) +
    annotate("rect", 
             xmin=thresholds$onset.lower, 
             xmax=thresholds$onset.upper, 
             ymin=-Inf, ymax=Inf, alpha=.25) +
    annotate("rect", 
             xmin=thresholds$offset.lower, 
             xmax=thresholds$offset.upper, 
             ymin=-Inf, ymax=Inf, alpha=.25) +
    labs(y="RSV cumulative cases, %", x="Week of year", title=title)
}

# Plot RSV cumulative case % with model prediction, zoomed in on onset
ggplot_cum_cases_pct_zoom = function(obs, pred, thresholds, xmin, xmax, ymin, ymax, title) {
  ggplot(obs, aes(x=time)) +
    coord_cartesian(
      xlim=c(xmin, xmax),
      ylim=c(ymin, ymax)
    ) +
    geom_hline(aes(yintercept = 0)) +
    geom_hline(aes(yintercept=seasonThreshold), color=gray(.5)) +
    geom_hline(aes(yintercept=1 - seasonThreshold), color=gray(.5)) +
    geom_ribbon(data=pred, aes(ymin=rsv.cum.fit.lower, ymax=rsv.cum.fit.upper), alpha=0.2) +
    geom_line(data=pred, aes(y=rsv.cum.fit)) +
    geom_point(shape=20, aes(y=rsv.cum.frac)) +
    annotate("rect", 
             xmin=thresholds$onset.lower, 
             xmax=thresholds$onset.upper, 
             ymin=-Inf, ymax=Inf, alpha=.25) +
    annotate("rect", 
             xmin=thresholds$offset.lower, 
             xmax=thresholds$offset.upper, 
             ymin=-Inf, ymax=Inf, alpha=.25) +
    labs(y="RSV cumulative cases, %", x="Week of year", title=title)
}

ggplot_thresholds_over_time = function(thresholds, title) {
  onset = ggplot(thresholds) +
    geom_errorbar(aes(ymin=onset.lower, ymax=onset.upper, x=year), width=.25) + 
    labs(x="Year", y="RSV season onset week", title=title)
  offset = ggplot(thresholds) +
    geom_errorbar(aes(ymin=offset.lower, ymax=offset.upper, x=year), width=.25) + 
    labs(x="Year", y="RSV season offset week", title=title)

  ggplot2.multiplot(plotlist=list(onset, offset), cols=2)
}

ggplot_prophylaxis_strategy = function(obs, pred, protected, title) {
  ggplot(obs, aes(x=time)) +
    geom_ribbon(data=pred, aes(ymin=rsv.cum.fit.lower, ymax=rsv.cum.fit.upper), alpha=0.2) +
    geom_line(data=pred, aes(y=rsv.cum.fit)) +
    geom_point(shape=20, aes(y=rsv.cum.frac)) +
    annotate("rect", 
             xmin=min(protected, na.rm=TRUE), xmax=max(protected, na.rm=TRUE), 
             ymin=-Inf, ymax=Inf, alpha=.25) +
    geom_hline(aes(yintercept=0)) +
    labs(y="RSV", x="Time", title=title)
}

```

```{r}
ggplot2.multiplot(plotlist=makeCountyPlots(levels(obsByCounty$county), function(c, countyObs, countyPred, countyThresholds) {
  ggplot_cases(countyObs, countyPred, countyThresholds, c)
}), cols=4)

# Plot RSV cumulative cases with model prediction 
ggplot2.multiplot(plotlist=makeCountyPlots(levels(obsByCounty$county), function(c, countyObs, countyPred, countyThresholds) {
  ggplot_cum_cases(countyObs, countyPred, countyThresholds, c)
}), cols=4)

# Plot RSV cumulative case % with model prediction 
ggplot2.multiplot(plotlist=makeCountyPlots(levels(obsByCounty$county), function(c, countyObs, countyPred, countyThresholds) {
  ggplot_cum_cases_pct(countyObs, countyPred, countyThresholds, c)
}), cols=4)

# Zoom in on onsets
ggplot2.multiplot(plotlist=makeCountyPlots(levels(obsByCounty$county), function(c, countyObs, countyPred, countyThresholds) {
  ggplot_cum_cases_pct_zoom(countyObs, countyPred, countyThresholds, xmin=min(countyThresholds$onset.lower) - 1, xmax=max(countyThresholds$onset.upper) + 1, ymin=0, ymax=0.2, c)
}), cols=4)

# Zoom in on offsets
ggplot2.multiplot(plotlist=makeCountyPlots(levels(obsByCounty$county), function(c, countyObs, countyPred, countyThresholds) {
  ggplot_cum_cases_pct_zoom(countyObs, countyPred, countyThresholds, xmin=min(countyThresholds$offset.lower) - 1, xmax=max(countyThresholds$offset.upper) + 1, ymin=0.8, ymax=1, c)
}), cols=4)
```

```{r}
onset = ggplot(thresholdsByCounty) +
  geom_errorbarh(aes(x=onset.median, xmin=onset.lower, xmax=onset.upper, y=county), height=.25) + 
  labs(x="RSV Season Onset")
offset = ggplot(thresholdsByCounty) +
  geom_errorbarh(aes(x=offset.median, xmin=offset.lower, xmax=offset.upper, y=county), height=.25) + 
  labs(x="RSV Season Offset")

ggplot2.multiplot(plotlist=list(onset, offset), cols=2)

```

```{r warning=FALSE}
obsByCountyYear = dataset %>% 
  rename(time=weekofyear) %>% 
  group_by(county, weeki, year, time) %>% 
  summarize(rsv=sum(rsv)) %>% 
  left_join(rsvCountyGroups, by="county") %>%
  group_by(weeki, year, time) %>%
  do(summarizeCountyGroups(.)) %>%
  group_by(county, year) %>%
  mutate(rsv.cum=cumsum(rsv), rsv.cum.frac=rsv.cum / if_else(sum(rsv) > 0, sum(rsv), as.integer(1))) %>% 
  select(-weeki) %>%
  as.data.frame()

predByCountyYear = data.frame()
thresholdsByCountyYear = data.frame()
slidingStratUnprotectedSimByCountyYear = data.frame()

progress = txtProgressBar(max=length(levels(obsByCounty$county)) * length(rsvYears) * 2, style=3)
idx = 0

for (c in levels(obsByCountyYear$county)) {
  for (y in rsvYears) {
    countyYearObs = obsByCountyYear %>% filter(county==c, year==y)
    countyYearModel = gam(rsv ~ s(time, k=5, bs="cp", m=3), family=poisson, data=countyYearObs)

    countyYearPred = countyYearModel %>% 
      predict(type="response", newdata=modelTime, se.fit=TRUE)

    countyYearPred = modelTime %>% 
      cbind(data.frame(rsv.fit=countyYearPred$fit, rsv.fit.se=countyYearPred$se.fit)) %>%
      cbind(countyYearModel %>% outbreak.predict.timeseries(modelTime, function(model, params, newdata) { outbreak.calc.cum(model, params, newdata) })) %>%
      rename(rsv.cum.fit.lower=lower, rsv.cum.fit.upper=upper, rsv.cum.fit=median) %>%
      mutate(county=factor(c, levels=levels(obsByCountyYear$county)), year=y)

    predByCountyYear = predByCountyYear %>% rbind(countyYearPred)

    countyYearThresholds = countyYearModel %>%
      outbreak.predict.scalars(
        modelTime,
        function(model, params, newdata) { outbreak.calc.thresholds(model, params, newdata$time, onset=seasonThreshold, offset=1 - seasonThreshold) }
      ) %>%
      mutate(county=factor(c, levels=levels(obsByCountyYear$county)), year=y)

    thresholdsByCountyYear = thresholdsByCountyYear %>% rbind(countyYearThresholds)

    if (y %in% rsvWindowYears) {
      countyYearUnprotectedSim = countyYearModel %>%
        outbreak.predict.scalars.sim(
          modelTime,
          function(model, params, newdata) { 
            outbreak.calc.unprotected(model, params, newdata$time, ppxSlidingStrategies(c, y))
          }
        ) %>%
        mutate(county=factor(c, levels=levels(obsByCountyYear$county)), year=y)

      slidingStratUnprotectedSimByCountyYear = slidingStratUnprotectedSimByCountyYear %>% rbind(countyYearUnprotectedSim)
    }

    idx = idx + 1
    setTxtProgressBar(progress, idx)
  }
}

# Aggregate sliding strategies over the entire time span

unprotectedByCounty = slidingStratUnprotectedSimByCountyYear %>% 
  group_by(county, outbreak.sim) %>%
  summarize_at(vars(contains("total"), contains("count")), sum) %>%
  group_by(county, outbreak.sim) %>%
  do((function(df) {
    stratNames = names(ppxSlidingStrategies())
    for (stratName in stratNames) {
      countName = sprintf("%s.count", stratName)
      fracName = sprintf("%s.frac", stratName)
      df = df %>% 
        mutate_at(fracName, function(.) { df[[countName]] / df$total })
    }
    df
  }) (.)) %>%
  group_by(county) %>%
  do((function(df) {
    df %>%
      select(-county, -total, -matches(".count")) %>%
      outbreak.predict.scalars.confints () %>%
      mutate(county=unique(df$county))
  })(.)) %>%
  inner_join(fixedStratUnprotectedByCounty, by="county")
```

```{r}
for (c in levels(obsByCountyYear$county)) {
  countyThresholdsByYear = thresholdsByCountyYear %>% filter(county==c)

  ggplot_thresholds_over_time(countyThresholdsByYear, title=c)
}

```

```{r}
# Plot fixed propxylaxis strategies
for (c in levels(obsByCounty$county)) {
  d = "plots/by county"
  if (!dir.exists(d)) {
    dir.create(d, showWarnings=FALSE, recursive=TRUE)
  }

  countyObs = obsByCounty %>% filter(county==c)
  countyPred = predByCounty %>% filter(county==c)

  ggsave(sprintf("%s/%s prophylaxis strategies.pdf", d, c), ggplot2.multiplot(plotlist=lapply(names(ppxFixedStrategies(c)), function(stratName) {
    strat = ppxFixedStrategies(c)[[stratName]]
    protected = modelTime$time %>% sapply(function(t) { if (strat(t) == 0) NA else t })

    ggplot_prophylaxis_strategy(countyObs, countyPred, protected, sprintf("%s w/ %s", c, stratName)) + labs(x=NULL)
  }), cols=1), width=4, height=6, units="in")
}

# Plot sliding propxylaxis strategies
for (c in levels(obsByCounty$county)) {
  for (y in rsvWindowYears) {
    d = sprintf("plots/by county and year/%s", c)
    if (!dir.exists(d)) {
      dir.create(d, showWarnings=FALSE, recursive=TRUE)
    }

    countyYearObs = obsByCountyYear %>% filter(county==c, year==y)
    countyYearPred = predByCountyYear %>% filter(county==c, year==y)

    ggsave(sprintf("%s/%s prophylaxis strategies.pdf", d, y), ggplot2.multiplot(plotlist=lapply(names(ppxSlidingStrategies(c, y)), function(stratName) {
      strat = ppxSlidingStrategies(c, y)[[stratName]]
      protected = modelTime$time %>% sapply(function(t) { if (strat(t) == 0) NA else t })

      ggplot_prophylaxis_strategy(countyYearObs, countyYearPred, protected, sprintf("%s w/ %s", c, stratName)) + labs(x=NULL)
    }), cols=1), width=4, height=6, units="in")
  }
}
```

```{r}
stratNames = c(names(ppxFixedStrategies()), names(ppxSlidingStrategies()))
plot = ggplot(unprotectedByCounty) +
  scale_linetype_manual(breaks=stratNames, values=seq_along(stratNames)) + 
  coord_cartesian(
    xlim=c(0, 0.1)
  ) +
  labs(x="Unprotected cases", y=NULL) +
  theme(aspect.ratio=2, panel.grid.major.y=element_blank())

for (idx in seq_along(stratNames)) {
  stratName = stratNames[idx]
  median = sprintf("%s.frac.median", stratName)
  lower = sprintf("%s.frac.lower", stratName)
  upper = sprintf("%s.frac.upper", stratName)
  linetype = sprintf('"%s"', stratName)

  delta = 0.1
  nudge = (idx - (length(stratNames) + 1) / 2) * -delta

  plot = plot + 
    geom_errorbarh(aes_string(x=median, xmin=lower, xmax=upper, y="county", linetype=linetype), height=0, position=position_nudge(y=nudge)) + 
    geom_point(aes_string(x=lower, y="county"), shape=20, position=position_nudge(y=nudge)) +
    geom_point(aes_string(x=upper, y="county"), shape=20, position=position_nudge(y=nudge))
}

plot
ggsave("plots/prophylaxis strategy comparison.pdf", plot, height=8, width=12, units="in")
```

```{r}
ignore_ = lapply(levels(obsByCountyYear$county), function(c) {
  d = sprintf("plots/by county and year/%s", c)
  if (!dir.exists(d)) {
    dir.create(d, showWarnings=FALSE, recursive=TRUE)
  }

  multiplot = ggplot2.multiplot(plotlist=makeCountyYearPlots(c, function(c, y, countyYearObs, countyYearPred, countyYearThresholds) {
    plot = ggplot_cases(countyYearObs, countyYearPred, countyYearThresholds, NULL)
    ggsave(sprintf("%s/%s cases.pdf", d, y), height=4, width=6, units="in")
    plot
  }), cols=4)

  # Plot RSV cumulative cases with model prediction 
  ggplot2.multiplot(plotlist=makeCountyYearPlots(c, function(c, y, countyYearObs, countyYearPred, countyYearThresholds) {
    plot = ggplot_cum_cases(countyYearObs, countyYearPred, countyYearThresholds, NULL)
    ggsave(sprintf("%s/%s cum cases.pdf", d, y), height=4, width=6, units="in")
    plot
  }), cols=4)

  # Plot RSV cumulative case % with model prediction 
  ggplot2.multiplot(plotlist=makeCountyYearPlots(c, function(c, y, countyYearObs, countyYearPred, countyYearThresholds) {
    plot = ggplot_cum_cases_pct(countyYearObs, countyYearPred, countyYearThresholds, NULL)
    ggsave(sprintf("%s/%s model.pdf", d, y), height=4, width=6, units="in")
    plot
  }), cols=4)

  # Zoom in on onsets
  ggplot2.multiplot(plotlist=makeCountyYearPlots(c, function(c, y, countyYearObs, countyYearPred, countyYearThresholds) {
    plot = ggplot_cum_cases_pct_zoom(countyYearObs, countyYearPred, countyYearThresholds, xmin=min(countyYearThresholds$onset.lower) - 1, xmax=max(countyYearThresholds$onset.upper) + 1, ymin=0, ymax=0.2, NULL)
    ggsave(sprintf("%s/%s onset.pdf", d, y), height=4, width=6, units="in")
    plot
  }), cols=4)

  # Zoom in on offsets
  ggplot2.multiplot(plotlist=makeCountyYearPlots(c, function(c, y, countyYearObs, countyYearPred, countyYearThresholds) {
    plot = ggplot_cum_cases_pct_zoom(countyYearObs, countyYearPred, countyYearThresholds, xmin=min(countyYearThresholds$offset.lower) - 1, xmax=max(countyYearThresholds$offset.upper) + 1, ymin=0.8, ymax=1, c)
    ggsave(sprintf("%s/%s offset.pdf", d, y), height=4, width=6, units="in")
    plot
  }), cols=4)
})
```

### 2017-12-31 Thesis/Thesis.rnw
Initial writings

\documentclass{article}

\usepackage{multicol}

\begin{document}

\begin{abstract}

\end{abstract}

\begin{multicols}{2}

\section{Introduction}

\section{Methods}

\subsection{Case definition}

We identified ? cases of RSV in Connecticut between ? and ?, grouped by week.

The cases were identified from the hospitalization database maintained by the Office of Health Care Access (OHCA) of the Department of Public Health of the state of Connecticut, which records all hospitalizations in non-federal short-stay acute-care general hospitals in Connecticut. Hospitalizations reported to us by the OHCA were grouped by week.

We defined a case of RSV to be a hospital discharge recorded in the OHCA hospitalization database meeting the following criteria:

\begin{itemize}
    \item admission (TODO: or discharge?) date was between ? and ? (inclusive)
    \item postal code of residence listed in patient's medical record was in Connecticut\footnote{According to the R \texttt{zipcode} package version 1.0}
    \item admission was associated with an RSV billing code\footnote{Which codes?}
\end{itemize}

\subsection{Modeling all-years RSV incidence}

Under the assumption that RSV incidence follows an annual cycle, we aggregated RSV incidence by week of year from 19?? to 20?? (inclusive).

Our goal was to generate a model that would allow us to sample from the distribution of (potential) RSV seasons, which in turn would enable us to estimate arbitrary characteristics of RSV seasons.

We accomplished this using a generalized additive model (GAM) with cyclic penalized cubic splines with 20 knots\footnote{Using the R \texttt{mgcv} package version 1.8-22}, via Poisson (log) link function.

This type of model produces normal distribution estimates of all spline parameters. By sampling spline parameters from those normal distributions, we, in effect, sample from the distribution of splines fitting the data.

As a result, we were able to estimate various characteristics of RSV seasons simply by sampling from distribution of splines fitting our data, and then --- with each sample spline corresponding to a putative RSV season --- calculating the desired characteristic of each spline.

For this, we developed a custom R package for estimation of different characteristics of infectious disease outbreaks, which we published at ?.

\subsection{Spatial aggregation of RSV incidence}

All-years RSV incidence was aggregated by county, as well as statewide.

Furthermore, some individual counties, with low incidence of RSV, yielded results with unimpressive statistical power. We aggregated those counties (which ones?) into a single non-contiguous region, and included that region as a separate spatial entity in our analysis.

\subsection{Estimating all-years characteristics of RSV seasons}

Having aggregated RSV incidence by week of year and by region, we estimated two characteristics of all-years RSV incidence in each region: season onset, defined as the time when cumulative incidence rises beyond 5\% of the total cumulative incidence; and season offset, defined as the time when cumulative incidence rises beyond 95\% of the total cumulative incidence.

To arrive at this estimate, we sampled from the RSV season distribution given by the model, and calculated onset and offset for each sampled RSV season.

\subsection{Estimating coverage of prophylaxis following current guidelines}

We then turned our attention to the current guidelines for RSV prophylaxis, published by the American Academy of Pediatricians, most recently revised in ???. These guidelines recommend RSV prophylaxis 6 monthly doses of ?, starting in November, for all infants below 2 (?) years of age who are at high risk of ?.

Given that high-risk infants are a small subgroup of the general population, we assumed that our model for RSV incidence based on hospitalization data is a good approximation of RSV incidence among high-risk infants. We then estimated the fraction of high-risk infants who elude protection from RSV because they are infected before receiving prophylaxis, or after protection from prophylaxis wanes.

To estimate this, we began by sampling from the RSV season distribution given by the model. For each sampled RSV season, we counted every case of RSV prior to November 15th or after May 15th as having eluded protection, and calculated the fraction of those cases among all cases.

\subsection{Devising alternate all-years prophylaxis guidelines}

Following this analysis, we devised four alternative prophylaxis guidelines. In all our alternative guidelines, prophylaxis consists of 6 doses of ?, and protection is assumed to last 6 months from the first dose.

\begin{itemize}
    \item \textbf{Statewide onset}: Under this strategy, prophylaxis administration begins on the date of the median RSV season onset, calculated from statewide all-years data. 
    \item \textbf{Statewide offset}: Under this strategy, prophylaxis administration ends on the date of the median RSV season offset, calculated from statewide all-years data. 
    \item \textbf{Regional onset}: Under this strategy, prophylaxis administration begins on the date of the median RSV season onset, calculated from regional\footnote{county-wide, or --- in the case of low-incidence counties --- low-incidence-region-wide} all-years data. 
    \item \textbf{Regional offset}: Under this strategy, prophylaxis administration ends on the date of the median RSV season offset, calculated from regional all-years data. 
\end{itemize}

\subsection{Evaluating alternate prophylaxis guidelines}

We evaluated each of those guidelines in the same way we evaluated the current AAP guidelines, described above.

For the two statewide alternative strategies, we estimated the number of cases eluding prophylaxis statewide, as well as in each region.

For the two regional alternative strategies, we estimated the number of cases eluding prophylaxis in each region.

(Should we also do a statewide analysis of regional strategies?)

\subsection{Evaluating temporal variation of RSV seasonality}

Our analysis thus far assumed that RSV seasons are similar year-to-year. To evaluate this assumption, we ?

\subsection{Estimating sliding-window characteristics of RSV seasons}

In order to reduce the potential impact of long-term variation in RSV seasons, we repeated our analysis of RSV season characteristics using a three-year sliding window. Instead of aggregating RSV incidence data across all years, we separately analyzed every series of three consecutive years.\footnote{Including overlaps.}

This analysis used the same penalized spline GAM as all-year analysis, and also produced statewide and regional estimates of RSV season 5\% onset and 95\% offset.

\subsection{Devising alternate sliding-window prophylaxis guidelines}

This analysis naturally leads to another approach to prophylaxis guidelines, in which every year prophylaxis recommendation is based on the timing of the RSV season onset and offset from the previous years:

\begin{itemize}
    \item \textbf{Statewide sliding window onset}: Under this strategy, prophylaxis administration in a given year begins on the date of the median RSV season onset calculated from statewide data for the previous three years. 
    \item \textbf{Statewide sliding window offset}: Under this strategy, prophylaxis administration in a given year ends on the date of the median RSV season offset, calculated from statewide data for the previous three years. 
\end{itemize}

As before, both alternate guidelines involve six monthly doses of ?. Although regional sliding-window guidelines would also be a natural extension, this analysis was not performed.

\section{Results}

\subsection{RSV season in Fairfield county is earlier and longer}

In Fairfield county, RSV season begins ? weeks earlier (CI) and ends ? weeks later (CI) than the statewide average; overall, it lasts ? weeks longer (CI) than the statewide average. (Figure)

\subsection{RSV season in low-incidence region is later and shorter}

In the low-incidence region, RSV season begins ? weeks later (CI), but doesn't end later than the statewide average; overall, it lasts ? weeks shorter (CI) than the statewide average. (Figure)

\subsection{AAP guidelines perform best in low-incidence region and worst in Fairfield county}

Statewide, ? cases (CI) elude protection under the AAP guidelines. The AAP guidelines perform better in the low-incidence region, where only ? cases (CI) elude protection, but worse in Fairfield county, where as many as ? cases (CI) elude protection. (Figure)

The cause of this is that the timing of the RSV season in the low-incidence region is better aligned with the AAP guidelines; the RSV season is centered on the prophylaxis time window, which minimizes the number of cases eluding prophylaxis. (Figure)

Meanwhile, Fairfield county --- with its unusually long RSV season --- has a higher fraction of cases outside of the prophylaxis window. (Figure)

\subsection{All-years alternate guidelines are superior to AAP in Hartford county, and non-inferior otherwise}

The four alternate prophylaxis guidelines based on all-years data (in which prophylaxis time window is determined by statewide or regional RSV season onset or offset), when compared to the AAP guidelines, yield non-inferior results in all regions except for Hartford county.  (Figure.)

In Hartford county, they yield superior results; whereas the AAP guidelines have ? cases (CI) eluding prophylaxis, alternate guidelines have fewer. (Table.)

In all cases, the four different alternate guidelines are comparable to each other.

\subsection{Sliding window alternate guidelines are inferior to AAP guidelines in low-incidence region, and non-superior otherwise.}

Contrariwise, the two strategies based on statewide data produced non-superior results in all regions except for the low-incidence region, where they produced inferior results. (Figure.)

Due to the non-superiority of statewide sliding-window strategies, regional sliding-window strategies were not evaluated.

\section{Discussion}

\end{multicols}

\end{document}

### 2018-01-02 Analysis/RSV.Rmd
Refactoring code for paper into separate R file

@@
 
-library(reshape)
-library(plyr)
-library(dplyr)
-library(zipcode)
-library(mgcv)
-library(tsgam)
-library(ggplot2)
-library(easyGgplot2)
-library(utils)
-library(outbreakpredict)
-data(zipcode)
-set.seed(0)
-```
-
-```{r}
-rsvWeek = function(weeki) {
-  (weeki + 26) %% 52 - 26
-}
-
-dataset = read.csv("../ct rsv time series.csv", header=TRUE, colClasses=c("patzip"="character"))
-# Add week-of-year, with zero = end of June, drop first 5.5 years because of coding differences
-dataset = dataset %>%
-  mutate(weekiadj=round(dataset$weeki * 364 / 365.25), weekofyear=rsvWeek(weekiadj), year=1990 + (weekiadj + 26) %/% 52) %>%
-  filter(weeki > 5.5*52) %>%
-  filter(weeki < 22.5*52)
-# Add state based on zipcode and drop everything not in CT
-zipState = zipcode %>% select(zip, state)
-dataset = dataset %>% 
-  left_join(zipcode %>% select(zip, state), by=c("patzip"="zip")) %>% 
-  filter(state=="CT")
-# Add county based on zipcode
-countyByZip = read.csv("../ct counties.csv", header=TRUE, colClasses=c("zip"="character"))
-counties = countyByZip %>% select(county) %>% distinct()
-dataset = dataset %>% inner_join(countyByZip, by=c("patzip"="zip"))
-
-# Sort counties by total RSV
-totalRSVByCounty = dataset %>%
-  group_by(county) %>% 
-  summarize(total_rsv=sum(rsv)) %>%
-  arrange(total_rsv) %>%
-  mutate(county=factor(county, county))
-
-rsvCounties = totalRSVByCounty$county
-rsvYears = sort(unique(dataset$year))
-rsvWeekRange = sort(unique(dataset$weeki))
-rsvWeekOfYearRange = sort(unique(dataset$weekofyear))
-
-dataset = dataset %>%
-  mutate(county=factor(county, levels=levels(rsvCounties)))
-
+source("./RSV.R")
 ```
@@
 
-```{r include=FALSE}
-# Reshape counties into columns and add column for total
-rsvByCountyAndWeekOfYear = dataset %>%
-  group_by(county, weekofyear) %>%
-  summarize(rsv=sum(rsv)) %>%
-  group_by(weekofyear) %>%
-  do(rbind(., as.data.frame(.) %>%
-             summarize(county="total", weekofyear=max(weekofyear), rsv=sum(rsv))
-           ))
-
-rsvForAllCountiesByWeekOfYear = rsvByCountyAndWeekOfYear %>%
-  melt(id=c("weekofyear", "county"), measured=c("rsv")) %>%
-  cast(weekofyear ~ county + variable) %>%
-  rename_all(funs(gsub("_rsv", "", .)))
-
-maxRSVByCounty = rsvByCountyAndWeekOfYear %>%
-  group_by(county) %>% 
-  summarize(max_rsv=max(rsv))
-
-rsvRelForAllCountiesByWeekOfYear = rsvByCountyAndWeekOfYear %>%
-  inner_join(maxRSVByCounty, by="county") %>%
-  mutate(rsv_rel=rsv/max_rsv) %>%
-  select(-max_rsv, -rsv) %>%
-  melt(id=c("weekofyear", "county"), measured=c("rsv_rel")) %>%
-  cast(weekofyear ~ county + variable)
-
-allCountiesTS = rsvForAllCountiesByWeekOfYear %>%
-  arrange(weekofyear) %>%
-  select(-weekofyear) %>%
-  ts(frequency=1, start=c(-26, 1))
-
-allCountiesRelTS = rsvRelForAllCountiesByWeekOfYear %>%
-  arrange(weekofyear) %>%
-  select(-weekofyear) %>%
-  ts(frequency=1, start=c(-26, 1))
-
-plot.ts(allCountiesTS, nc=1)
-plot.ts(allCountiesRelTS, nc=1, plot.type="single", col=rainbow(8), lwd=2)
-```
-
-```{r include=FALSE}
-# Drop counties in which max # of RSV cases in a week is <100
-maxRSVByInterestingCounty = maxRSVByCounty %>% filter(max_rsv > 50)
-
-rsvForInterestingCountiesByWeekOfYear = rsvByCountyAndWeekOfYear %>%
-  inner_join(maxRSVByInterestingCounty, by="county") %>%
-  select(-max_rsv) %>%
-  melt(id=c("weekofyear", "county"), measured=c("rsv", "rsv_rel")) %>%
-  cast(weekofyear ~ county + variable)
-
-rsvRelForInterestingCountiesByWeekOfYear = rsvByCountyAndWeekOfYear %>%
-  inner_join(maxRSVByInterestingCounty, by="county") %>%
-  mutate(rsv_rel=rsv/max_rsv) %>%
-  select(-max_rsv, -rsv) %>%
-  melt(id=c("weekofyear", "county"), measured=c("rsv_rel")) %>%
-  cast(weekofyear ~ county + variable)
-
-interestingCountiesTS = rsvForInterestingCountiesByWeekOfYear %>%
-  arrange(weekofyear) %>%
-  select(-weekofyear) %>%
-  ts(frequency=1, start=c(-26, 1))
-
-interestingCountiesRelTS = rsvRelForInterestingCountiesByWeekOfYear %>%
-  arrange(weekofyear) %>%
-  select(-weekofyear) %>%
-  ts(frequency=1, start=c(-26, 1))
-
-plot.ts(interestingCountiesTS, nc=1)
-plot.ts(interestingCountiesRelTS, nc=1, plot.type="single", col=rainbow(5), lwd=2)
-```
-
 ```{r}
-outbreak.calc.unprotected = function(model, params, time, strategies) {
-  # Get model predictions for given (randomized) param values
-  time = time + 0.5
-  predictors = model %>% predict(data.frame(time=time), type="lpmatrix")
-  fit = predictors %*% params
-
-  # Map spline fit back to data
-  fit = fit %>% model$family$linkinv()
-
-  # Calculate total # of unprotected cases for each strategy
-  unprotected = as.data.frame(lapply(strategies, function(strat) {
-    sum(fit * (1 - sapply(time, strat)))
-  }))
-
-  # Calculate total # of cases 
-  total = sum(fit)
-
-  unprotected %>% 
-    rename_all(funs(
-      sprintf("%s.count", .)
-    )) %>%
-    cbind(
-      (unprotected / total) %>%
-        rename_all(funs(
-          sprintf("%s.frac", .)
-        ))
-    ) %>% 
-    mutate(total=total)
-}
-```
-
-```{r}
-eps = .05
-seasonThreshold = 0.025
-rsvTime = dataset$weekofyear
-modelTime = data.frame(time=seq(min(rsvTime) - 1 + eps, max(rsvTime), eps))
-
-rsvCountyGroups = data.frame(county=rsvCounties) %>%
-  mutate(
-    group.all=TRUE,
-    group.lowIncidence=county %in% c("Tolland", "Windham", "Middlesex", "Litchfield")
-  )
-
-ppxDuration = 24 # weeks
-
-evalStrategy = function(start, end, time) {
-  as.numeric((time > rsvWeek(start)) && (time < rsvWeek(end)))
-}
-
-evalOnsetStrategy = function(start, time) {
-  as.numeric((time > rsvWeek(start)) && (time < rsvWeek(start + ppxDuration)))
-}
-
-evalOffsetStrategy = function(end, time) {
-  as.numeric((time > rsvWeek(end - ppxDuration)) && (time < rsvWeek(end)))
-}
-
-ppxFixedStrategies = function(c=NULL) {
-  stateOnset = stateThresholds$onset.median
-  stateOffset = stateThresholds$offset.median
-
-  if (!is.null(c)) {
-    countyOnset = (thresholdsByCounty %>% filter(county==c))$onset.median
-    countyOffset = (thresholdsByCounty %>% filter(county==c))$offset.median
-  }
-
-  list(
-    # never=function(time) { 0 },
-    # always=function(time) { 1 },
-    aap=function(time) {
-      evalOnsetStrategy(strptime("11-15", format="%m-%d")$yday / 7, time)
-    },
-    stateOnset=function(time) {
-      evalOnsetStrategy(stateOnset, time)
-    },
-    stateOffset=function(time) {
-      evalOffsetStrategy(stateOffset, time)
-    },
-    countyOnset=function(time) {
-      evalOnsetStrategy(countyOnset, time)
-    },
-    countyOffset=function(time) {
-      evalOffsetStrategy(countyOffset, time)
-    }
-  )
-}
-
 ppxSlidingStrategies = function(c=NULL, y=NULL) {
@@
 
-```
-
-```{r}
-stateObs = dataset %>% 
-  rename(time=weekofyear) %>% 
-  group_by(time) %>% 
-  summarize(rsv=sum(rsv)) %>% 
-  mutate(rsv.cum=cumsum(rsv), rsv.cum.frac=rsv.cum / sum(rsv)) %>% 
-  as.data.frame()
-
-stateModel = gam(rsv ~ s(time, k=20, bs="cp", m=3), family=poisson, data=stateObs)
-
-statePred = stateModel %>% 
-  predict(type="response", newdata=modelTime, se.fit=TRUE)
-
-statePred = modelTime %>% 
-  cbind(data.frame(rsv.fit=statePred$fit, rsv.fit.se=statePred$se.fit)) %>%
-  cbind(stateModel %>% outbreak.predict.timeseries(modelTime, function(model, params, newdata) { outbreak.calc.cum(model, params, newdata) })) %>%
-  rename(rsv.cum.fit.lower=lower, rsv.cum.fit.upper=upper, rsv.cum.fit=median)
-
-stateThresholds = stateModel %>%
-  outbreak.predict.scalars(
-    modelTime,
-    function(model, params, newdata) { 
-      outbreak.calc.thresholds(model, params, newdata$time, onset=seasonThreshold, offset=1 - seasonThreshold)
-    }
-  )
-
-summarizeCountyGroups = function(data) {
-  rbind(
-      as.data.frame(data) %>%
-        select(county, time, rsv), 
-      as.data.frame(data) %>%
-        filter(group.all==TRUE) %>%
-        summarize(county="all", time=max(time), rsv=sum(rsv)),
-      as.data.frame(data) %>%
-        filter(group.lowIncidence==TRUE) %>%
-        summarize(county="lowIncidence", time=max(time), rsv=sum(rsv))
-    )  
-}
 ```
@@
 ggplot2.multiplot(plotlist=list(onset, offset), cols=2)
-
-```
-
-```{r}
-obsByCounty = dataset %>% 
-  rename(time=weekofyear) %>% 
-  group_by(county, time) %>% 
-  summarize(rsv=sum(rsv)) %>% 
-  left_join(rsvCountyGroups, by="county") %>%
-  group_by(time) %>%
-  do(summarizeCountyGroups(.)) %>%
-  group_by(county) %>% 
-  mutate(rsv.cum=cumsum(rsv), rsv.cum.frac=rsv.cum / sum(rsv)) %>% 
-  as.data.frame()
-
-predByCounty = data.frame()
-thresholdsByCounty = data.frame()
-fixedStratUnprotectedByCounty = data.frame()
-
-progress = txtProgressBar(max=length(levels(obsByCounty$county)), style=3)
-idx = 0
-
-for (c in levels(obsByCounty$county)) {
-  countyObs = obsByCounty %>% filter(county==c)
-  countyModel = gam(rsv ~ s(time, k=20, bs="cp", m=3), family=poisson, data=countyObs)
-
-  countyPred = countyModel %>% 
-    predict(type="response", newdata=modelTime, se.fit=TRUE)
-
-  countyPred = modelTime %>% 
-    cbind(data.frame(rsv.fit=countyPred$fit, rsv.fit.se=countyPred$se.fit)) %>%
-    cbind(countyModel %>% outbreak.predict.timeseries(modelTime, function(model, params, newdata) { outbreak.calc.cum(model, params, newdata) })) %>%
-    rename(rsv.cum.fit.lower=lower, rsv.cum.fit.upper=upper, rsv.cum.fit=median) %>%
-    mutate(county=factor(c, levels=levels(obsByCounty$county)))
-
-  predByCounty = predByCounty %>% rbind(countyPred)
-
-  countyThresholds = countyModel %>%
-    outbreak.predict.scalars(
-      modelTime,
-      function(model, params, newdata) { 
-        outbreak.calc.thresholds(model, params, newdata$time, onset=seasonThreshold, offset=1 - seasonThreshold)
-      }
-    ) %>%
-    mutate(county=factor(c, levels=levels(obsByCounty$county)))
-
-  thresholdsByCounty = thresholdsByCounty %>% rbind(countyThresholds)
-
-  countyUnprotected = countyModel %>%
-    outbreak.predict.scalars(
-      modelTime,
-      function(model, params, newdata) { 
-        outbreak.calc.unprotected(model, params, newdata$time, ppxFixedStrategies(c))
-      }
-    ) %>%
-    mutate(county=factor(c, levels=levels(obsByCounty$county)))
-
-  fixedStratUnprotectedByCounty = fixedStratUnprotectedByCounty %>% rbind(countyUnprotected)
-
-  idx = idx + 1
-  setTxtProgressBar(progress, idx)
-}
 

### 2018-01-02 Analysis/RSV.R

@@ -1,0 +1,285 @@
+# ---- external ----
+library(reshape)
+library(dplyr)
+library(mgcv)
+library(outbreakpredict)
+library(zipcode)
+library(ggplot2)
+library(easyGgplot2)
+library(data.table)
+
+data(zipcode)
+set.seed(0)
+
+simulations = 20
+
+# RSV week-of-year is -26..25, with week 0 being first week of the year
+rsvWeek = function(weeki) {
+  (weeki + 26) %% 52 - 26
+}
+
+# Augment a (county, time, rsv) data frame with rows for regions consisting of >1 county
+summarizeCountyGroups = function(data) {
+  rbind(
+    as.data.frame(data) %>%
+      select(county, time, rsv),
+    as.data.frame(data) %>%
+      filter(group.all==TRUE) %>%
+      summarize(county="all", time=max(time), rsv=sum(rsv)),
+    as.data.frame(data) %>%
+      filter(group.lowIncidence==TRUE) %>%
+      summarize(county="lowIncidence", time=max(time), rsv=sum(rsv))
+  )
+}
+
+lowIncidenceCounties = c("Tolland", "Windham", "Middlesex", "Litchfield", "New London")
+eps = .05
+level = .95
+seasonThreshold = 0.025
+ppxDuration = 24 # weeks
+
+# Load data
+dataset = fread("../ct rsv time series.csv", sep=",", header=TRUE, colClasses=c("patzip"="character"))
+
+# Add week-of-year, with zero = first week of January, drop first 5.5 years because of coding differences
+dataset = dataset %>%
+  mutate(
+    weekiadj=round(dataset$weeki * 364 / 365.25),
+    weekofyear=rsvWeek(weekiadj),
+    year=1990 + (weekiadj + 26) %/% 52,
+    adate=as.Date(adate, "%d%b%Y")
+  ) %>%
+  filter(weeki > 5.5*52) %>%
+  filter(weeki <= 22.5*52)
+# Add state based on zipcode and drop everything not in CT
+zipState = zipcode %>% select(zip, state)
+dataset = dataset %>%
+  left_join(zipcode %>% select(zip, state), by=c("patzip"="zip")) %>%
+  filter(state=="CT")
+# Add county based on zipcode
+countyByZip = fread("../ct counties.csv", sep=",", header=TRUE, colClasses=c("zip"="character"))
+counties = countyByZip %>% select(county) %>% distinct()
[…]

### 2018-01-02 Analysis/Thesis.tex
Adding charts, rewriting results

\documentclass{article}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}

\usepackage{multicol,float}
\usepackage{hyperref}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

\begin{abstract}

\end{abstract}

\begin{multicols}{2}

\section{Introduction}

\section{Methods}

\subsection{Case definition}

We identified 299676 cases of RSV in Connecticut between June, 30, 1996 and June, 02, 2013.

The cases were identified from the hospitalization database maintained by the Office of Health Care Access (OHCA) of the Department of Public Health of the state of Connecticut, which records all hospitalizations in non-federal short-stay acute-care general hospitals in Connecticut. OHCA provided us with weekly hospitalization statistics.

We defined a case of RSV to be a hospital stay recorded in the OHCA hospitalization database meeting the following criteria:

\begin{itemize}
    \item date of hospital admission was between June, 30, 1996 and June, 02, 2013 (inclusive),
    \item postal code of residence listed in patient's medical record was in Connecticut\footnote{According to the zipcode $\rightarrow$ state mapping in R \texttt{zipcode} package version 1.0}, and
    \item hospital stay was associated with an RSV billing code\footnote{Which codes?}
\end{itemize}

\subsection{Modeling all-years RSV incidence}

Under the assumption that RSV incidence follows an annual cycle peaking during the winter, we aggregated RSV incidence by week of year.

Our goal was to generate a model that would allow us to sample from the distribution of (potential) RSV seasons, which in turn would enable us to estimate arbitrary characteristics of RSV seasons.

We accomplished this using a generalized additive model (GAM) with cyclic penalized cubic splines with 20 knots\footnote{Using the R \texttt{mgcv} package version 1.8-22}, via Poisson (log) link function.

This type of model produces normal distribution estimates of all spline parameters. By sampling spline parameters from those normal distributions, we, in effect, sample from the distribution of splines fitting the data.

As a result, we were able to estimate various characteristics of RSV seasons simply by sampling from distribution of splines fitting our data, and then --- with each sample spline corresponding to a putative RSV season --- calculating the desired characteristic of each spline.

For this, we developed a custom R package for estimation of different characteristics of infectious disease outbreaks, which is available at \href{https://github.com/airbornemint/outbreakpredict}{\nolinkurl{github.com/airbornemint/outbreakpredict}}.

\subsection{Spatial aggregation of RSV incidence}

All-years RSV incidence was aggregated by county, as well as statewide.

Furthermore, some individual counties, with low incidence of RSV, yielded results with unimpressive statistical power. We aggregated those counties --- Tolland, Windham, Middlesex, Litchfield, and New London --- into a single non-contiguous region, and included that region as a separate spatial entity in our analysis.

\subsection{Estimating all-years characteristics of RSV seasons}

Having aggregated RSV incidence by week of year and by region, we estimated two characteristics of all-years RSV incidence in each region: season onset, defined as the time when cumulative incidence rises beyond 2.5\% of the total cumulative incidence; and season offset, defined as the time when cumulative incidence rises beyond 97.5\% of the total cumulative incidence.

To arrive at this estimate, we sampled from the RSV season distribution given by the model, and calculated onset and offset for each sampled RSV season.

\subsection{Estimating coverage of prophylaxis following current guidelines}

We then turned our attention to the current guidelines for RSV prophylaxis, published by the American Academy of Pediatricians, most recently revised in ???. These guidelines recommend RSV prophylaxis with 6 monthly doses of palivizumab, starting in November, for all infants below 2 (?) years of age who are at high risk of ?.

Given that high-risk infants are a small subgroup of the general population (?), we assumed that our model for RSV incidence based on hospitalization data is a good approximation of RSV incidence among high-risk infants. We then estimated the fraction of high-risk infants who elude protection from RSV because they are infected before receiving prophylaxis, or after protection from prophylaxis wanes.

To estimate this, we began by sampling from the RSV season distribution given by the model. For each sampled RSV season, we counted every case of RSV prior to November 15th or after May 15th as having eluded protection, and calculated the fraction of those cases among all cases.

\subsection{Devising alternate all-years prophylaxis guidelines}

Following this analysis, we devised four alternative prophylaxis guidelines. In all our alternative guidelines, prophylaxis consists of six monthly doses of palivizumab, and protection is assumed to last 24 weeks from the first dose.

\begin{itemize}
    \item \textbf{By statewide all-years onset}: prophylaxis administration begins on the date of the statewide all-years median RSV season onset. 
    \item \textbf{By statewide all-years midpoint}: prophylaxis administration begins 12 weeks before the average of the statewide all-years median RSV season onset and offset. 
    \item \textbf{By statewide all-years offset}: prophylaxis administration begins 24 weeks before the statewide all-years median RSV season offset. 
    \item \textbf{By regional all-years onset}: prophylaxis administration begins on the date of the regional\footnote{county-wide, or --- in the case of low-incidence counties --- low-incidence-region-wide} all-years median RSV season onset.
    \item \textbf{By regional all-years midpoint}: prophylaxis administration begins 12 weeks before the average of the regional all-years median RSV season onset and offset. 
    \item \textbf{By regional all-years offset}: prophylaxis administration ends on the date of the regional all-years median RSV season offset. 
\end{itemize}

\subsection{Evaluating alternate prophylaxis guidelines}

We evaluated each of those alternate guidelines in the same way we evaluated the current AAP guidelines, described above.

For the two statewide alternate guidelines, we estimated the number of cases eluding prophylaxis statewide, as well as in each region.

For the two regional alternate guidelines, we estimated the number of cases eluding prophylaxis in each region.

(Should we also do a statewide analysis of regional strategies?)

\subsection{Evaluating temporal variation of RSV seasonality}

Our analysis thus far assumed that RSV seasons are similar year-to-year. To evaluate this assumption, we ?

\subsection{Estimating three-year characteristics of RSV seasons}

In order to reduce the potential impact on our model of long-term variation in RSV season onset and offset, we repeated our analysis of RSV season characteristics using a three-year sliding window. Rather that aggregating RSV incidence data across all years, as before, for sliding-window analysis we separately analyzed every three-year period starting on July 1st.

This analysis used the same penalized spline GAM as all-years analysis, and also produced statewide and regional estimates of RSV season 5\% onset and 95\% offset.

\subsection{Devising alternate recent-years prophylaxis guidelines}

This analysis naturally leads to another approach to prophylaxis guidelines, in which prophylaxis recommendation is adjusted every year based on the timing of the RSV season onset and offset from the recent years. We evaluated two such alternate guidelines:

\begin{itemize}
    \item \textbf{By statewide recent-years onset}: prophylaxis administration in a given year begins on the date of the statewide median RSV season onset over the previous three years. 
    \item \textbf{Statewide sliding window offset}: prophylaxis administration in a given year ends on the date of the statewide median RSV season offset over the previous three years.
\end{itemize}

As before, both alternate guidelines involve six monthly doses of palivizumab.

\section{Results}

\subsection{RSV season in Fairfield county begins early and ends late}

Compared to the statewide median onset of RSV season of 42.38 weeks (95\% CI: 42.15 -- 42.76) and offset of 14.58 weeks (95\% CI: 14.35 -- 14.97), RSV season in Fairfield county has earlier median onset of 41.33 weeks (95\% CI: 40.44 -- 41.91) and later median offset of 15.73 weeks (95\% CI: 15.09 -- 16.27). (Figure \ref{fig:seasonByRegion}.)

\begin{figure*}[t]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/seasonByRegion-1}

\end{knitrout}
\caption{Onset and offset of RSV season in Connecticut by region}
\label{fig:seasonByRegion}
\end{figure*}

\begin{figure*}[t]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: <text>:1:75: unexpected 'in'\\\#\# 1:\ \ \ \  ggplot(unprotectedByCounty \%>\% filter(strat=="{}aap"{}) \%> filter(county \%in\\\#\#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \  \textasciicircum{}}}\end{kframe}
\end{knitrout}
\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis administered according to AAP guidelines, by region.}
\label{fig:coverageByRegionAAP}
\end{figure*}

\begin{figure*}[t]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/coverageByRegionAAPInsight-1}

\end{knitrout}
\caption{RSV relative cumulative incidence by region}
\label{fig:coverageByRegionAAPInsight}
\end{figure*}

\begin{figure*}[t]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/coverageByRegion-1}

\end{knitrout}

\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by region and prophylaxis guidelines.}
\label{fig:coverageByRegion}
\end{figure*}

\subsection{RSV season in low-incidence region begins late}

Meanwhile, in comparison with the statewide RSV season onset and offset, the low-incidence region has RSV season with later onset of 44.95 weeks (95\% CI: 42.15 -- 42.76); however, season offset shows no change from the statewide median. (Figure \ref{fig:seasonByRegion}.)

\subsection{AAP guidelines perform best in low-incidence region and worst in Fairfield county}

Statewide, our model shows that 94.15\% of RSV cases (95\% CI: 93.86 -- 94.40\%) occur during the time when palivizumab is administered according to the AAP guidelines. The AAP guidelines perform better in the low-incidence region, where as many as 96.55\% cases (95\% CI: 96.11 -- 96.98\%) occur during the prophylaxis time window, but worse in Fairfield county, where as few as 91.90\% cases ((95\% CI: 91.12 -- 92.75\%)) occur during this time. (Table \ref{table:coverageByRegionAAP}.)

The cause of this is evident in Figure \ref{fig:coverageByRegionAAPInsight}, which shows temporal misalignment between the time window of the RSV season (delineated by median 2.5\% onset and 97.5\% offset by region), and the time window of AAP prophylaxis guidelines. Fairfield county, owing to its early season onset has disproportionately many cases before prophylaxis administration begins; on the other hand, the low-incidence region, owing to its late season onset, has its RSV seasons almost entirely contained within the prophylaxis window.

\subsection{All-years alternate guidelines are superior to AAP statewide and in Hartford county, and non-inferior otherwise}

The six alternate prophylaxis guidelines based on all-years data (in which prophylaxis time window is determined by statewide or regional all-years RSV season onset or offset), when compared to the AAP guidelines, yield non-inferior results in all regions, and superior results both statewide and in Hartford county. (Figure \ref{fig:coverageByRegion}.)

Statewide, the AAP guidelines produce prophylaxis coverage for 94.15\% cases (95\% CI: 93.86 -- 94.40\%); meanwhile, the guidelines based on all-years onset yield the weakest improvement at 94.76\% coverage (95\% CI: 94.53 -- 95.16\%), and other alternate guidelines yield similar results.

In Hartford county, the improvement is more noteworthy. Here, the AAP guidelines cover 93.56\% of cases (95\% CI: 92.82 -- 93.94\%); the guidelines based on all-years regional offset generate the weakest improvement to 94.99\% coverage (), and other alternate guidelines are comparable.

In all cases, all alternate guidelines based on all-years analysis are non-inferior to AAP guidelines and non-superior to each other.

\subsection{Sliding window alternate guidelines are inferior to AAP guidelines in low-incidence region, and non-superior otherwise.}

Contrariwise, the two strategies based on statewide data produced non-superior results in all regions except for the low-incidence region, where they produced inferior results. (Figure.)

Due to the non-superiority of statewide sliding-window strategies, regional sliding-window strategies were not evaluated.

\section{Discussion}

\end{multicols}

\end{document}

### 2018-01-02 Thesis/Thesis.rnw
Adding charts, rewriting results

@@
+<<options, echo=FALSE>>=
+    opts_chunk$set(echo=FALSE, message=FALSE)
+@
+
 \documentclass{article}
 
-\usepackage{multicol}
+\usepackage{multicol,float}
+\usepackage{hyperref}
+\usepackage{draftwatermark}
+\SetWatermarkText{DRAFT}
+\SetWatermarkScale{4}
 
 \begin{document}
+
+<<load>>=
+read_chunk("../Analysis/RSV.R")
+@
+
+<<external>>=
+@
+
+<<util>>=
+# Formatting utilities
+formatDate = function(date) {
+    format(date, "%B, %d, %Y")
+}
+
+formatThreshold = function(threshold) {
+    sprintf("%.2f", threshold %% 52)
+}
+
+regionOnset = function(c) {
+    formatThreshold((thresholdsByCounty %>% filter(county==c))$onset.median)
+}
+
+regionOffset = function(c) {
+    formatThreshold((thresholdsByCounty %>% filter(county==c))$offset.median)
+}
+
+formatThresholdCI = function(lower, upper, level) {
+    sprintf("%d\\%% CI: %.2f -- %.2f", level * 100, lower %% 52, upper %% 52)
+}
+
+regionOnsetCI = function(c, level) {
+    formatThresholdCI(
+        (thresholdsByCounty %>% filter(county==c))$onset.lower, 
+        (thresholdsByCounty %>% filter(county==c))$onset.upper, 
+        level
+    )
+}
+
+regionOffsetCI = function(c, level) {
+    formatThresholdCI(
+        (thresholdsByCounty %>% filter(county==c))$offset.lower, 
+        (thresholdsByCounty %>% filter(county==c))$offset.upper, 
+        level
+    )
+}
+
+formatPct = function(pct) {
+    sprintf("%.2f\\%%", pct * 100)
+}
+
+formatPctCI = function(lower, upper, level) {
+    sprintf("%d\\%% CI: %.2f -- %.2f\\%%", level * 100, lower * 100, upper * 100)
+}
+
+regionStrategyCoverage = function(c, s) {
+    formatPct((unprotectedByCounty %>% filter(county==c, strat==s))$frac.median)
+}
+
+regionStrategyCoverageCI = function(c, s, level) {
+    formatPctCI(
+        (unprotectedByCounty %>% filter(county==c, strat==s))$frac.upper,
+        (unprotectedByCounty %>% filter(county==c, strat==s))$frac.lower,
+        level
+    )
+}
+
+# Counties which we plot (so, not individual low-incidence counties)
+countiesForPlots = thresholdsByCounty$county[!thresholdsByCounty$county %in% lowIncidenceCounties]
+@
 
@@
 
-We identified ? cases of RSV in Connecticut between ? and ?, grouped by week.
+We identified \Sexpr{nrow(dataset)} cases of RSV in Connecticut between \Sexpr{formatDate(startDate)} and \Sexpr{formatDate(endDate)}.
 
 The cases were identified from the hospitalization database maintained by the Office of Health Care Access (OHCA) of the Department of Public Health of the state of Connecticut, which records all hospitalizations in non-federal short-stay acute-care general hospitals in Connecticut.
-Hospitalizations reported to us by the OHCA were grouped by week.
+OHCA provided us with weekly hospitalization statistics.
 
-We defined a case of RSV to be a hospital discharge recorded in the OHCA hospitalization database meeting the following criteria:
+We defined a case of RSV to be a hospital stay recorded in the OHCA hospitalization database meeting the following criteria:
 
 \begin{itemize}
-    \item admission (TODO: or discharge?) date was between ? and ? (inclusive)
-    \item postal code of residence listed in patient's medical record was in Connecticut\footnote{According to the R \texttt{zipcode} package version 1.0}
-    \item admission was associated with an RSV billing code\footnote{Which codes?}
+    \item date of hospital admission was between \Sexpr{formatDate(startDate)} and \Sexpr{formatDate(endDate)} (inclusive),
+    \item postal code of residence listed in patient's medical record was in Connecticut\footnote{According to the zipcode $\rightarrow$ state mapping in R \texttt{zipcode} package version 1.0}, and
+    \item hospital stay was associated with an RSV billing code\footnote{TODO Which codes?}
 \end{itemize}
@@
 
-Under the assumption that RSV incidence follows an annual cycle, we aggregated RSV incidence by week of year from 19?? to 20?? (inclusive).
+Under the assumption that RSV incidence follows an annual cycle peaking during the winter, we aggregated RSV incidence by week of year.
 
@@
 
-For this, we developed a custom R package for estimation of different characteristics of infectious disease outbreaks, which we published at ?.
+For this, we developed a custom R package for estimation of different characteristics of infectious disease outbreaks, which is available at \href{https://github.com/airbornemint/outbreakpredict}{\nolinkurl{github.com/airbornemint/outbreakpredict}}.
 
@@
 Furthermore, some individual counties, with low incidence of RSV, yielded results with unimpressive statistical power.
-We aggregated those counties (which ones?) into a single non-contiguous region, and included that region as a separate spatial entity in our analysis.
+We aggregated those counties --- \Sexpr{gsub("(.*), (.*)", "\\1, and \\2", paste(lowIncidenceCounties, collapse=", "))} --- into a single non-contiguous region, and included that region as a separate spatial entity in our analysis.
 
@@
 
-Having aggregated RSV incidence by week of year and by region, we estimated two characteristics of all-years RSV incidence in each region: season onset, defined as the time when cumulative incidence rises beyond 5\% of the total cumulative incidence; and season offset, defined as the time when cumulative incidence rises beyond 95\% of the total cumulative incidence.
+Having aggregated RSV incidence by week of year and by region, we estimated two characteristics of all-years RSV incidence in each region: season onset, defined as the time when cumulative incidence rises beyond \Sexpr{seasonThreshold * 100}\% of the total cumulative incidence; and season offset, defined as the time when cumulative incidence rises beyond \Sexpr{(1 - seasonThreshold) * 100}\% of the total cumulative incidence.
 
@@
 We then turned our attention to the current guidelines for RSV prophylaxis, published by the American Academy of Pediatricians, most recently revised in ???.
-These guidelines recommend RSV prophylaxis 6 monthly doses of ?, starting in November, for all infants below 2 (?) years of age who are at high risk of ?.
+These guidelines recommend RSV prophylaxis with 6 monthly doses of palivizumab, starting in November, for all infants below 2 (?) years of age who are at high risk of ?.
 
-Given that high-risk infants are a small subgroup of the general population, we assumed that our model for RSV incidence based on hospitalization data is a good approximation of RSV incidence among high-risk infants.
+Given that high-risk infants are a small subgroup of the general population (?), we assumed that our model for RSV incidence based on hospitalization data is a good approximation of RSV incidence among high-risk infants.
 We then estimated the fraction of high-risk infants who elude protection from RSV because they are infected before receiving prophylaxis, or after protection from prophylaxis wanes.
@@
 To estimate this, we began by sampling from the RSV season distribution given by the model.
-For each sampled RSV season, we counted every case of RSV prior to November 15th or after May 15th as having eluded protection, and calculated the fraction of those cases among all cases.
+For each sampled RSV season, we considereda case of RSV to be covered by prophylaxis if it occurred between zero and 23 weeks (inclusive) after November 15th, and calculated the fraction of those cases among all cases.
 
@@
 
-Following this analysis, we devised four alternative prophylaxis guidelines.
-In all our alternative guidelines, prophylaxis consists of 6 doses of ?, and protection is assumed to last 6 months from the first dose.
+Following this analysis, we devised six alternate prophylaxis guidelines.
+In all our alternative guidelines, prophylaxis consists of six monthly doses of palivizumab, and protection is assumed to last 24 weeks from the first dose.
 
 \begin{itemize}
-    \item \textbf{Statewide onset}: Under this strategy, prophylaxis administration begins on the date of the median RSV season onset, calculated from statewide all-years data. 
-    \item \textbf{Statewide offset}: Under this strategy, prophylaxis administration ends on the date of the median RSV season offset, calculated from statewide all-years data. 
-    \item \textbf{Regional onset}: Under this strategy, prophylaxis administration begins on the date of the median RSV season onset, calculated from regional\footnote{county-wide, or --- in the case of low-incidence counties --- low-incidence-region-wide} all-years data.
-    \item \textbf{Regional offset}: Under this strategy, prophylaxis administration ends on the date of the median RSV season offset, calculated from regional all-years data. 
+    \item \textbf{By statewide all-years onset}: prophylaxis administration begins on the date of the statewide all-years median RSV season onset. 
+    \item \textbf{By statewide all-years midpoint}: prophylaxis administration begins 12 weeks before the average of the statewide all-years median RSV season onset and offset. 
+    \item \textbf{By statewide all-years offset}: prophylaxis administration begins 24 weeks before the statewide all-years median RSV season offset. 
+    \item \textbf{By regional all-years onset}: prophylaxis administration begins on the date of the regional\footnote{county-wide, or --- in the case of low-incidence counties --- low-incidence-region-wide} all-years median RSV season onset.
+    \item \textbf{By regional all-years midpoint}: prophylaxis administration begins 12 weeks before the average of the regional all-years median RSV season onset and offset. 
+    \item \textbf{By regional all-years offset}: prophylaxis administration ends on the date of the regional all-years median RSV season offset. 
 \end{itemize}
@@
 
-We evaluated each of those guidelines in the same way we evaluated the current AAP guidelines, described above.
+We evaluated each of those alternate guidelines in the same way we evaluated the current AAP guidelines, as described above.
 
-For the two statewide alternative strategies, we estimated the number of cases eluding prophylaxis statewide, as well as in each region.
+For the three statewide alternate guidelines, we estimated the number of cases eluding prophylaxis statewide, as well as in each region.
 
-For the two regional alternative strategies, we estimated the number of cases eluding prophylaxis in each region.
+For the three regional alternate guidelines, we estimated the number of cases eluding prophylaxis in each region.
 
-(Should we also do a statewide analysis of regional strategies?)
+(TODO Should we also do a statewide analysis of regional strategies?)
 
@@
 
-Our analysis thus far assumed that RSV seasons are similar year-to-year. To evaluate this assumption, we ?
+Our analysis thus far assumed that RSV seasons are similar year-to-year. To evaluate this assumption, we ? TODO
 
-\subsection{Estimating sliding-window characteristics of RSV seasons}
+\subsection{Estimating three-year characteristics of RSV seasons}
 
-In order to reduce the potential impact of long-term variation in RSV seasons, we repeated our analysis of RSV season characteristics using a three-year sliding window.
-Instead of aggregating RSV incidence data across all years, we separately analyzed every series of three consecutive years.\footnote{Including overlaps.}
+In order to reduce the potential impact on our model of long-term variation in RSV season onset and offset, we repeated our analysis of RSV season characteristics using a three-year sliding window.
+Rather that aggregating RSV incidence data across all years, as before, for sliding-window analysis we separately analyzed every three-year period starting on July 1st.
 
-This analysis used the same penalized spline GAM as all-year analysis, and also produced statewide and regional estimates of RSV season 5\% onset and 95\% offset.
+This analysis used the same penalized spline GAM as all-years analysis, and also produced statewide and regional estimates of RSV season 5\% onset and 95\% offset.
 
-\subsection{Devising alternate sliding-window prophylaxis guidelines}
+\subsection{Devising alternate recent-years prophylaxis guidelines}
 
-This analysis naturally leads to another approach to prophylaxis guidelines, in which every year prophylaxis recommendation is based on the timing of the RSV season onset and offset from the previous years:
+This analysis naturally leads to another approach to prophylaxis guidelines, in which prophylaxis recommendation is adjusted every year based on the timing of the RSV season onset and offset from the recent years.
+We evaluated two such alternate guidelines:
 
 \begin{itemize}
-    \item \textbf{Statewide sliding window onset}: Under this strategy, prophylaxis administration in a given year begins on the date of the median RSV season onset calculated from statewide data for the previous three years.
-    \item \textbf{Statewide sliding window offset}: Under this strategy, prophylaxis administration in a given year ends on the date of the median RSV season offset, calculated from statewide data for the previous three years.
+    \item \textbf{By statewide recent-years onset}: prophylaxis administration in a given year begins on the date of the statewide median RSV season onset over the previous three years. 
+    \item \textbf{Statewide sliding window offset}: prophylaxis administration in a given year ends on the date of the statewide median RSV season offset over the previous three years.
 \end{itemize}
 
-As before, both alternate guidelines involve six monthly doses of ?. Although regional sliding-window guidelines would also be a natural extension, this analysis was not performed.
+As before, both alternate guidelines involve six monthly doses of palivizumab.
 
@@
 
-\subsection{RSV season in Fairfield county is earlier and longer}
+\subsection{RSV season in Fairfield county begins early and ends late}
 
-In Fairfield county, RSV season begins ? weeks earlier (CI) and ends ? weeks later (CI) than the statewide average; overall, it lasts ? weeks longer (CI) than the statewide average. (Figure)
+Compared to the statewide median onset of RSV season at \Sexpr{regionOnset("all")} weeks (\Sexpr{regionOnsetCI("all", level)}) and offset at \Sexpr{regionOffset("all")} weeks (\Sexpr{regionOffsetCI("all", level)}), RSV season in Fairfield county has earlier median onset at \Sexpr{regionOnset("Fairfield")} weeks (\Sexpr{regionOnsetCI("Fairfield", level)}) and later median offset at \Sexpr{regionOffset("Fairfield")} weeks (\Sexpr{regionOffsetCI("Fairfield", level)}).
+(Figure \ref{fig:seasonByRegion}.)
 
-\subsection{RSV season in low-incidence region is later and shorter}
+\begin{figure*}[t]
+<<seasonByRegion>>=
+    onset = ggplot(thresholdsByCounty %>% filter(county %in% countiesForPlots)) +
+        geom_errorbarh(aes(x=onset.median, xmin=onset.lower, xmax=onset.upper, y=county), height=.25) + 
+        labs(x="Season onset") +
+        theme(
+            axis.title.y=element_blank(),
+            axis.ticks.y=element_blank()
+        )
+    offset = ggplot(thresholdsByCounty %>% filter(county %in% countiesForPlots)) +
+        geom_errorbarh(aes(x=offset.median, xmin=offset.lower, xmax=offset.upper, y=county), height=.25) + 
+        labs(x="Season offset", y=NULL) +
+        theme(
+            axis.title.y=element_blank(),
+            axis.text.y=element_blank(),
+            axis.ticks.y=element_blank()
+        )
 
-In the low-incidence region, RSV season begins ? weeks later (CI), but doesn't end later than the statewide average; overall, it lasts ? weeks shorter (CI) than the statewide average. (Figure)
+    ggplot2.multiplot(plotlist=list(onset, offset), cols=2)
+@
+\caption{Onset and offset of RSV season in Connecticut by region}
+\label{fig:seasonByRegion}
+\end{figure*}
 
-\subsection{AAP guidelines perform best in low-incidence region and worst in Fairfield county}
+\begin{figure*}[t]
+<<coverageByRegionAAP>>=
+    ggplot(unprotectedByCounty %>% filter(strat=="aap") %>% filter(county %in% countiesForPlots)) +
+        geom_errorbar(aes(ymax=frac.upper, ymin=frac.lower, x=county), width=.25) + 
+        geom_point(aes(y=frac.median, x=county)) + 
+        scale_y_continuous(labels=scales::percent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
+        labs(y="RSV cases occurring during prophylaxis timeframe, %") +
+        theme(
+            axis.title.x=element_blank(),
+            axis.ticks.x=element_blank()
+        )
+@
+\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis administered according to AAP guidelines, by region.}
+\label{fig:coverageByRegionAAP}
+\end{figure*}
 
-Statewide, ?
-cases (CI) elude protection under the AAP guidelines.
-The AAP guidelines perform better in the low-incidence region, where only ?
-cases (CI) elude protection, but worse in Fairfield county, where as many as ?
-cases (CI) elude protection.
-(Figure)
+\begin{figure*}[t]
+<<coverageByRegionAAPInsight>>=
+    ggplot2.multiplot(plotlist=lapply(countiesForPlots, function(c) {
+        strat = ppxFixedStrategies("all")[["aap"]]
 
-The cause of this is that the timing of the RSV season in the low-incidence region is better aligned with the AAP guidelines; the RSV season is centered on the prophylaxis time window, which minimizes the number of cases eluding prophylaxis.
-(Figure)
+        countyPred = predByCounty %>% filter(county==c) %>% mutate(ppx=strat(time))
+        countyThresholds = thresholdsByCounty %>% filter(county==c)
+        ppxStart = min((countyPred %>% filter(ppx > 0))$time)
+        ppxEnd = max((countyPred %>% filter(ppx > 0))$time)
 
-Meanwhile, Fairfield county --- with its unusually long RSV season --- has a higher fraction of cases outside of the prophylaxis window. (Figure)
+        unprotectedAtStart = (countyPred %>% filter(time==ppxStart))$rsv.cum.fit
+        unprotectedAtEnd = (countyPred %>% filter(time==ppxEnd))$rsv.cum.fit
 
-\subsection{All-years alternate guidelines are superior to AAP in Hartford county, and non-inferior otherwise}
+        ggplot(countyPred) +
+            annotate("rect", xmin=ppxStart, xmax=ppxEnd, ymin=-Inf, ymax=+Inf, fill=hsv(1/3, 1, 1, .25)) + 
+            annotate("rect", xmin=countyThresholds$onset.median, xmax=countyThresholds$offset.median, ymin=-Inf, ymax=+Inf, fill=hsv(0, 1, 1, .25)) + 
+            geom_ribbon(aes(ymin=rsv.cum.fit.lower, ymax=rsv.cum.fit.upper, x=time), fill=grey(.25)) + 
+            annotate("segment", x=ppxStart, y=.45, xend=ppxEnd, yend=.45, color=hsv(1/3, 1, .5)) + 
+            annotate("point", x=(ppxStart + ppxEnd) / 2, y=.45, color=hsv(1/3, 1, .5), shape=3) + 
+            annotate("segment", x=countyThresholds$onset.median, y=.55, xend=countyThresholds$offset.median, yend=.55, color=hsv(0, 1, .5)) + 
+            annotate("point", x=(countyThresholds$onset.median + countyThresholds$offset.median) / 2, y=.55, color=hsv(0, 1, .5), shape=3) + 
+            annotate("point", x=ppxStart, y=unprotectedAtStart) + 
+            annotate("point", x=ppxEnd, y=unprotectedAtEnd) + 
+            scale_y_continuous(labels=scales::percent, breaks=seq(0, 1, by=.2), limits=c(0, 1), expand=c(0.05, 0)) +
+            labs(x=c) +
+            theme(
+                axis.title.y=element_blank(),
+                axis.ticks.x=element_blank()
+            )
+    }), cols=2)
+@
+\caption{RSV relative cumulative incidence by region}
+\label{fig:coverageByRegionAAPInsight}
+\end{figure*}
 
-The four alternate prophylaxis guidelines based on all-years data (in which prophylaxis time window is determined by statewide or regional RSV season onset or offset), when compared to the AAP guidelines, yield non-inferior results in all regions except for Hartford county.
-(Figure.)
+\begin{figure*}[t]
+<<coverageByRegion, warning=FALSE>>=
+    data = unprotectedByCounty %>% 
+        filter(county %in% countiesForPlots)
+    ggplot(data) +
+        scale_y_continuous(labels=scales::percent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
+        scale_linetype_manual(values=c(1, 3, 4, 2, 3, 4, 2)) + 
+        scale_color_manual(values=c(grey(0), rep(hsv(0, 1, 1), 3), rep(hsv(4/6, 1, 1), 3))) + 
+        geom_errorbar(
+            aes(ymin=frac.lower, ymax=frac.upper, x=county, linetype=strat, color=strat, group=strat), 
+            width=0, 
+            position=position_dodge(.5)
+        ) + 
+        geom_point(aes(y=frac.median, x=county, color=strat), position=position_dodge(.5)) +
+        geom_point(aes(y=frac.lower, x=county, color=strat), position=position_dodge(.5), shape=18) +
+        geom_point(aes(y=frac.upper, x=county, color=strat), position=position_dodge(.5), shape=18) +
+        labs(y="RSV cases occurring during prophylaxis timeframe, %") +
+        guides(color=guide_legend(keywidth=3, keyheight=1), linetype=guide_legend(keywidth=3, keyheight=1)) + 
+        theme(
+            axis.title.x=element_blank(),
+            axis.ticks.x=element_blank()
+        )
+@
 
-In Hartford county, they yield superior results; whereas the AAP guidelines have ? cases (CI) eluding prophylaxis, alternate guidelines have fewer. (Table.)
+\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by region and prophylaxis guidelines.}
+\label{fig:coverageByRegion}
+\end{figure*}
 
-In all cases, the four different alternate guidelines are comparable to each other.
+\subsection{RSV season in low-incidence counties begins late}
 
-\subsection{Sliding window alternate guidelines are inferior to AAP guidelines in low-incidence region, and non-superior otherwise.}
+Meanwhile, in comparison with the statewide RSV season onset and offset, the low-incidence region has RSV season with later onset at \Sexpr{regionOnset("lowIncidence")} weeks (\Sexpr{regionOnsetCI("all", level)}); season offset shows no change from the statewide median.
+(Figure \ref{fig:seasonByRegion}.)
 
-Contrariwise, the two strategies based on statewide data produced non-superior results in all regions except for the low-incidence region, where they produced inferior results. (Figure.)
+\subsection{AAP guidelines perform best in low-incidence counties and worst in Fairfield county}
+
+Statewide, our model shows that \Sexpr{regionStrategyCoverage("all", "aap")} of RSV cases (\Sexpr{regionStrategyCoverageCI("all", "aap", level)}) occur during the time when palivizumab is administered according to the AAP guidelines.
+The AAP guidelines perform better in the low-incidence counties, where \Sexpr{regionStrategyCoverage("lowIncidence", "aap")} cases (\Sexpr{regionStrategyCoverageCI("lowIncidence", "aap", level)}) occur during the prophylaxis time window, but worse in Fairfield county, where \Sexpr{regionStrategyCoverage("Fairfield", "aap")} cases ((\Sexpr{regionStrategyCoverageCI("Fairfield", "aap", level)})) occur during this time.
+(Table \ref{table:coverageByRegionAAP}.)
+
+The cause of this is evident in Figure \ref{fig:coverageByRegionAAPInsight}, which shows temporal misalignment between the time window of the RSV season (delineated by median 2.5\% onset and 97.5\% offset in each region), and the time window of AAP prophylaxis guidelines.
+Fairfield county, owing to its early season onset has disproportionately many cases before prophylaxis administration begins; on the other hand, the low-incidence counties, owing to their late season onset, have their RSV seasons almost entirely contained within the prophylaxis window.
+
+\subsection{All-years alternate guidelines are superior to AAP statewide and in Hartford county, and non-inferior otherwise}
+
+The six alternate prophylaxis guidelines based on all-years data (in which prophylaxis time window is determined by statewide or regional all-years RSV season onset or offset), when compared to the AAP guidelines, yield non-inferior results in all regions, and superior results both statewide and in Hartford county.
+(Figure \ref{fig:coverageByRegion}.)
+
+Statewide, the AAP guidelines produce prophylaxis coverage for \Sexpr{regionStrategyCoverage("all", "aap")} cases (\Sexpr{regionStrategyCoverageCI("all", "aap", level)}); meanwhile, the guidelines based on all-years statewide onset yield the weakest improvement at \Sexpr{regionStrategyCoverage("all", "stateOnset")} coverage (\Sexpr{regionStrategyCoverageCI("all", "stateOnset", level)}), and other alternate guidelines yield similar results.
+
+In Hartford county, the improvement is more noteworthy.
+Here, the AAP guidelines cover \Sexpr{regionStrategyCoverage("Hartford", "aap")} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", level)}); the guidelines based on all-years regional offset generate the weakest improvement to \Sexpr{regionStrategyCoverage("Hartford", "countyOffset")} coverage (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", level)}), and other alternate guidelines are comparable.
+
+In every region, all alternate guidelines based on all-years analysis are non-inferior to AAP guidelines and non-superior to each other.
+
+\subsection{Sliding window alternate guidelines are inferior to AAP guidelines in low-incidence counties, and non-superior otherwise.}
+
+Contrariwise, the two strategies based on statewide data produced non-superior results in all regions except for the low-incidence counties, where they produced inferior results. (Figure.)
 

### 2018-01-12 Analysis/RSV.Rmd
Updated to outbreakpredict 0.3

@@
     countyYearPred = countyYearModel %>% 
-      predict(type="response", newdata=modelTime, se.fit=TRUE)
+      predict(type="response", newdata=data.frame(time=modelTime), se.fit=TRUE)
 
-    countyYearPred = modelTime %>% 
+    countyYearPred = data.frame(time=modelTime) %>% 
       cbind(data.frame(rsv.fit=countyYearPred$fit, rsv.fit.se=countyYearPred$se.fit)) %>%
-      cbind(countyYearModel %>% outbreak.predict.timeseries(modelTime, function(model, params, newdata) { outbreak.calc.cum(model, params, newdata) })) %>%
+      cbind(countyYearModel %>% outbreak.predict.timeseries(modelTime, outbreak.calc.cum())) %>%
       rename(rsv.cum.fit.lower=lower, rsv.cum.fit.upper=upper, rsv.cum.fit=median) %>%
@@
         modelTime,
-        function(model, params, newdata) { outbreak.calc.thresholds(model, params, newdata$time, onset=seasonThreshold, offset=1 - seasonThreshold) }
+        outbreak.calc.thresholds(onset=seasonThreshold, offset=1 - seasonThreshold)
       ) %>%
@@
           modelTime,
-          function(model, params, newdata) { 
-            outbreak.calc.unprotected(model, params, newdata$time, ppxSlidingStrategies(c, y))
-          }
+          outbreak.calc.unprotected(ppxSlidingStrategies(c, y))
         ) %>%

### 2018-01-12 Analysis/RSV.R

@@ -13,6 +13,8 @@ set.seed(0)
 
 simulations = 20
 
+# *** Data munging helpers
+
 # RSV week-of-year is -26..25, with week 0 being first week of the year
 rsvWeek = function(weeki) {
   (weeki + 26) %% 52 - 26
@@ -32,11 +34,16 @@ summarizeCountyGroups = function(data) {
   )
 }
 
+# *** Analysis parameters
+
 lowIncidenceCounties = c("Tolland", "Windham", "Middlesex", "Litchfield", "New London")
 eps = .05
 level = .95
 seasonThreshold = 0.025
 ppxDuration = 24 # weeks
+slidingWindowDuration = 3 # Years
+
+# *** Load / munge data
 
 # Load data
 dataset = fread("../ct rsv time series.csv", sep=",", header=TRUE, colClasses=c("patzip"="character"))
@@ -91,7 +98,9 @@ startDate = min(dataset$adate)
 endDate = max(dataset$adate)
 
 rsvTime = dataset$weekofyear
-modelTime = data.frame(time=seq(min(rsvTime) - 1 + eps, max(rsvTime), eps))
+modelTime = seq(min(rsvTime) - 1 + eps, max(rsvTime), eps)
+
+# *** Prophyaxis assessment helpers
 
 evalStrategy = function(start, end, time) {
   as.numeric((time > rsvWeek(start)) & (time < rsvWeek(end)))
@@ -105,6 +114,7 @@ evalOffsetStrategy = function(end, time) {
   as.numeric((time > rsvWeek(end - ppxDuration)) & (time < rsvWeek(end)))
 }
 
+# *** Prophylaxis regimen definitions
 
 # Return a list of prophylaxis strategies for a county. If c is NULL, then it returns a list of prophylaxis strategy names
 ppxFixedStrategies = function(c=NULL) {
@@ -143,36 +153,58 @@ ppxFixedStrategies = function(c=NULL) {
   )
 }
 
-# Estimate % left unprotected by prophylaxis strategy
-outbreak.calc.unprotected = function(model, params, time, strategies) {
-  # Get model predictions for given (randomized) param values
-  time = time + 0.5
-  predictors = model %>% predict(data.frame(time=time), type="lpmatrix")
-  fit = predictors %*% params
+ppxSlidingStrategies = function(c=NULL, y=NULL) {
+  if (!is.null(y) && !is.null(c)) {
+    stateSlidingOnset = (stateThresholdsByWindow %>% filter(year==y))$onset.median
[…]

### 2018-01-12 Analysis/RSV.R
Added sliding-window analysis

@@ -283,3 +283,70 @@ unprotectedByCounty = fixedStratUnprotectedByCounty %>%
     frac.median=1 - frac.median,
     strat = factor(strat, names(ppxFixedStrategies(NULL)))
   )
+
+# *** State-level sliding window analysis
+
+stateObsByWindow = dataset %>%
+  mutate(time=weeki) %>%
+  group_by(time, year, weekofyear) %>%
+  summarize(rsv=sum(rsv)) %>%
+  as.data.frame()
+
+total = data.frame(time=stateObsByWindow$time, rsv=0)
+
+for (idx in seq(1, slidingWindowDuration)) {
+  total = total %>%
+    inner_join(stateObsByWindow %>%
+                 mutate(time=time + 52 * idx) %>%
+                 select(time, rsv),
+               by="time"
+    ) %>%
+    mutate(rsv=rsv.x + rsv.y) %>%
+    select(time, rsv)
+}
+
+stateObsByWindow = stateObsByWindow %>%
+  select(-rsv) %>%
+  inner_join(total, by="time") %>%
+  group_by(year) %>%
+  mutate(rsv.cum=cumsum(rsv), rsv.cum.frac=rsv.cum / sum(rsv)) %>%
+  select(-time) %>%
+  rename(time=weekofyear) %>%
+  filter(year >= min(rsvYears) + slidingWindowDuration) %>%
+  as.data.frame()
+
+rsvWindowYears = unique(stateObsByWindow$year)
+
+statePredByWindow = data.frame()
+stateThresholdsByWindow = data.frame()
+
+for (y in rsvWindowYears) {
+
+  stateYearObs = stateObsByWindow %>% filter(year==y)
+  stateYearModel = gam(rsv ~ s(time, k=5, bs="cp", m=3), family=poisson, data=stateYearObs)
+
+  stateYearPred = stateYearModel %>%
+    predict(type="response", newdata=data.frame(time=modelTime), se.fit=TRUE)
+
+  stateYearPred = modelTime %>%
+    cbind(data.frame(rsv.fit=stateYearPred$fit, rsv.fit.se=stateYearPred$se.fit)) %>%
+    cbind(stateYearModel %>% outbreak.predict.timeseries(modelTime, outbreak.calc.cum())) %>%
+    rename(rsv.cum.fit.lower=lower, rsv.cum.fit.upper=upper, rsv.cum.fit=median) %>%
+    mutate(year=y)
+
[…]

### 2018-01-12 Analysis/RSV.Rmd
Install data.table

@@
 ```{r setup, include=FALSE, error=FALSE, warning=FALSE, message=FALSE}
-install.packages(c("dplyr", "zipcode", "reshape", "mgcv", "ggplot2", "gridExtra", "devtools"))
+install.packages(c("dplyr", "zipcode", "reshape", "mgcv", "ggplot2", "gridExtra", "devtools", "data.table"))
 library(devtools)

### 2018-01-12 Analysis/RSV.Rmd
Moved sliding window analysis to RSV.R

@@
 ggplot2.multiplot(plotlist=plots, cols=4)
-
-```
-
-```{r}
-ppxSlidingStrategies = function(c=NULL, y=NULL) {
-  if (!is.null(y) && !is.null(c)) {
-    stateSlidingOnset = (stateThresholdsByWindow %>% filter(year==y))$onset.median
-    stateSlidingOffset = (stateThresholdsByWindow %>% filter(year==y))$offset.median
-  }
-
-  list(
-    stateSlidingOnset=function(time) {
-      evalOnsetStrategy(stateSlidingOnset, time)
-    },
-    stateSlidingOffset=function(time) {
-      evalOffsetStrategy(stateSlidingOffset, time)
-    }
-  )
-}
-
-slidingWindowDuration = 3 # Years
-
-```
-
-```{r}
-stateObsByWindow = dataset %>% 
-  mutate(time=weeki) %>% 
-  group_by(time, year, weekofyear) %>% 
-  summarize(rsv=sum(rsv)) %>%
-  as.data.frame()
-
-total = data.frame(time=stateObsByWindow$time, rsv=0)
-
-for (idx in seq(1, slidingWindowDuration)) {
-  total = total %>%
-    inner_join(stateObsByWindow %>%
-                 mutate(time=time + 52 * idx) %>%
-                 select(time, rsv),
-               by="time"
-               ) %>%
-    mutate(rsv=rsv.x + rsv.y) %>%
-    select(time, rsv)
-}
-
-stateObsByWindow = stateObsByWindow %>%
-  select(-rsv) %>%
-  inner_join(total, by="time") %>%
-  group_by(year) %>%
-  mutate(rsv.cum=cumsum(rsv), rsv.cum.frac=rsv.cum / sum(rsv)) %>% 
-  select(-time) %>%
-  rename(time=weekofyear) %>%
-  filter(year >= min(rsvYears) + slidingWindowDuration) %>%
-  as.data.frame()
-
-rsvWindowYears = unique(stateObsByWindow$year)
-
-statePredByWindow = data.frame()
-stateThresholdsByWindow = data.frame()
-
-progress = txtProgressBar(max=length(rsvWindowYears), style=3)
-idx = 0
-
-for (y in rsvWindowYears) {
-
-  stateYearObs = stateObsByWindow %>% filter(year==y)
-  stateYearModel = gam(rsv ~ s(time, k=5, bs="cp", m=3), family=poisson, data=stateYearObs)
-
-  stateYearPred = stateYearModel %>% 
-    predict(type="response", newdata=modelTime, se.fit=TRUE)
-
-  stateYearPred = modelTime %>% 
-    cbind(data.frame(rsv.fit=stateYearPred$fit, rsv.fit.se=stateYearPred$se.fit)) %>%
-    cbind(stateYearModel %>% outbreak.predict.timeseries(modelTime, function(model, params, newdata) { outbreak.calc.cum(model, params, newdata) })) %>%
-    rename(rsv.cum.fit.lower=lower, rsv.cum.fit.upper=upper, rsv.cum.fit=median) %>%
-    mutate(year=y)
-
-  statePredByWindow = statePredByWindow %>% rbind(stateYearPred)
-
-  stateYearThresholds = stateYearModel %>%
-    outbreak.predict.scalars(
-      modelTime,
-      function(model, params, newdata) { outbreak.calc.thresholds(model, params, newdata$time, onset=seasonThreshold, offset=1 - seasonThreshold) }
-    ) %>%
-    mutate(year=y)
-
-  stateThresholdsByWindow = stateThresholdsByWindow %>% rbind(stateYearThresholds)
-
-  idx = idx + 1
-  setTxtProgressBar(progress, idx)
-}
 ```
@@
 }), cols=4)
-
-```
-
-```{r}
-onset = ggplot(stateThresholdsByWindow) +
-  geom_errorbar(aes(ymin=onset.lower, ymax=onset.upper, x=year), width=.25) + 
-  labs(x="RSV Season Onset")
-offset = ggplot(stateThresholdsByWindow) +
-  geom_errorbar(aes(ymin=offset.lower, ymax=offset.upper, x=year), width=.25) + 
-  labs(x="RSV Season Offset")
-
-ggplot2.multiplot(plotlist=list(onset, offset), cols=2)
 

### 2018-01-12 Thesis/Thesis.rnw
Rewriting for draft #1

@@
+% Agenda
+%  * Is coverage the right word
+%  * Round time periods pre-coverage analysis in order to make conclusion make sense
+%  * Added guidelines based on season midpoint
+%  * Nothing in linear regression of onset/offset
+%  * What level of feedback am I looking for
+%  * Publication-quality not a goal for Jan 26
+% 
+% Todo
+%  * Change how mod 52-1/7 is done
+
 <<options, echo=FALSE>>=
@@
 @
-
-\documentclass{article}
-
-\usepackage{multicol,float}
-\usepackage{hyperref}
-\usepackage{draftwatermark}
-\SetWatermarkText{DRAFT}
-\SetWatermarkScale{4}
-
-\begin{document}
 
@@
 <<util>>=
+library(grid)
+
 # Formatting utilities
@@
     format(date, "%B, %d, %Y")
+}
+
+formatYear = function(date) {
+    format(date, "%Y")
 }
@@
 
+driftYearToWeek = function(year, negate) {
+    drift = 365 / 7 * year
+    if (negate) {
+        -drift
+    } else {
+        drift
+    }
+}
+
+formatDrift = function(lm, negate=FALSE) {
+    sprintf("%.2f weeks", driftYearToWeek(summary(lm)$coefficients['year', 1], negate))
+}
+
+formatDriftCI = function(lm, level, negate=TRUE) {
+    ci = confint(lm, "year", level=level)
+    sprintf(
+        "%d\\%% CI: %.2f -- %.2f weeks", level * 100, 
+        driftYearToWeek(min(ci), negate), 
+        driftYearToWeek(max(ci), negate)
+    )
+}
+
 # Counties which we plot (so, not individual low-incidence counties)
@@
 
+\documentclass{article}
+
+\usepackage{multicol,float}
+\usepackage{hyperref}
+\usepackage{draftwatermark}
+\SetWatermarkText{DRAFT}
+\SetWatermarkScale{4}
+
+\usepackage{titling}
+\newcommand{\subtitle}[1]{%
+  \posttitle{%
+    \par\end{center}
+    \begin{center}\large#1\end{center}
+    \vskip0.5em}%
+}
+
+\newcommand{\abstractsection}[1]{\section*{#1}}
+
+\title{Assessment and optimization of respiratory syncytial virus immunoprophylaxis regimens using Monte Carlo sampling of a penalized spline generalized additive model of hospital admissions in Connecticut between \Sexpr{formatYear(startDate)} and \Sexpr{formatYear(endDate)}}
+
+\author{Ben Artin, YSPH/YSM 2018, if all goes well}
+\date{Draft \#1, \today}
+
+\begin{document}
+
+\maketitle
+
 \begin{abstract}
+
+\abstractsection{Background}
+
+Respiratory syncytial virus (RSV) causes seasonal respiratory infection with potentially serious complications in young infants.
+Immunoprophylaxis (palivizumab) is available, but costly.
+The American Academy of Pediatrics (AAP) recommends palivizumab only for infants at high risk of complications, and only during the RSV season.
+Although the current AAP guidelines acknowledge the existence of spatial and temporal variation in RSV incidence, they do not recommend spatial or temporal adjustments to immunprophylaxis regimen outside of Florida.
+
+\abstractsection{Methods}
+
+We describe a generalized additive model of RSV incidence using cubic cyclic penalized splines and apply that model to hospital admissions records from Connecticut between \Sexpr{formatDate(startDate)} and \Sexpr{formatDate(endDate)} to estimate coverage (TODO: is coverage the best term?) of RSV immunoprophylaxis administered in Connecticut according to the AAP guidelines.
+We also formulate several alternative immunoprophylaxis regimens with the same net pharmaceutical cost, and compare the coverage and implementation complexity of those alternative regimens to the AAP-recommended regimen.
+
+\abstractsection{Results}
+
+At 95\% confidence level, we found alternative regimens which account for spatial variability of RSV incidence to have superior coverage (to that of the AAP regimen) in some regions of Connecticut, and non-inferior coverage in other regions.
+We also found alternative regimens which account for temporal RSV variability to have non-superior coverage to our spatially-adjusted regimens, while being considerably more complex to implement.
+Finally, we found our best-performing alternative to AAP guidelines to provide a XX\% state-wide increase in RSV prophylaxis coverage over the AAP regimen.
+
+\abstractsection{Conclusion}
+
+We conclude that the increased prophylaxis coverage provided by regimens based on our spatial analysis warrants further analysis to determine whether the potential reduction in hospitalization rate is nullified by the potential increase in implementation cost.
 
@@
 
+\subsection{Respiratory syncytial virus}
+
+Respiratory syncytial virus (RSV) causes upper respiratory infections in humans of all ages. In adults, RSV infection is typically asymptomatic or gives rise to mild respiratory illness.
+
+In children, however, the infection often incites more serious respiratory illness, sometimes leading to hospitalization.
+
+Risk factors for serious illness and hospitalization due to RSV infection in children include prematurity, chronic lung disease of prematurity, congenital heart disease, anatomic pulmonary abnormalities, neuromuscular disorders, trisomy 21, immunocompromised status, and cystic fibrosis.
+
+Hospitalization rate of RSV-infected infants at high risk of complications is approximately 10\% in the populations in which it has been studied.
+
+\subsection{Respiratory syncytial virus seasonality}
+
+TODO
+
+\subsection{RSV immunoprophylaxis}
+
+Immunoprophylaxis with palivizumab, a monoclonal antibody medication, has been approved for prevention of RSV infection since 1998.
+Palivizumab is administered via intramuscular injection, and requires monthly dosing.
+Its price is \$1500-\$3000 per dose.
+
+Palivizumab has been found to be effective in reducing hospitalizations due to RSV; in double-blinded trials in high-risk infants, it reduced hospitalization rate by 45-55\% compared to placebo.
+
+Owing to the high cost, the American Academy of Pediatrics (AAP) recommends palivizumab immunoprophylaxis only for high-risk infants, and only during RSV season.
+These guidelines were most recently revised in ???.
+
+In their guidelines, the AAP acknowledges the potential significance of spatial and temporal variation in RSV incidence, but does not recommend local variance from nation-wide prophylaxis guidelines outside of Florida.
+
+\subsection{Spatio-temporal variability of RSV in Connecticut}
+
+The Department of Public Health of the state of Connecticut, via its Office of Health Care Access (OHCA), maintains a database of all hospitalizations in every non-federal short-stay acute-care general hospital in the state.
+This database has previously been used to show regional variability in time of peak RSV incidence within Connecticut.
+
+No prior research is available regarding year-to-year variation in timing of RSV season in Connecticut.
+
+\subsection{Study aims}
+
+Motivated by AAP's recognition of the impact of spatial variation in RSV incidence on optimizing RSV immunoprophylaxis guidelines, and the known spatial variability of RSV incidence in Connecticut, our study asks these questions:
+
+\begin{itemize}
+	\item To what extent does regional variability of RSV incidence in Connecticut impact the effectiveness of the AAP-recommended prophylaxis regimen?
+	\item Can we use spatial analysis of RSV to propose alternative guidelines, either state-wide or regional, that would improve effectiveness over AAP-recommended prophylaxis, without increasing treatment cost?
+	\item Is there year-to-year variation in timing of RSV season in Connecticut?
+	\item Can we take advantage of any year-to-year variation to improve upon AAP-recommended prophylaxis, without increasing treatment cost?
+\end{itemize}
+
 \section{Methods}
@@
 
-The cases were identified from the hospitalization database maintained by the Office of Health Care Access (OHCA) of the Department of Public Health of the state of Connecticut, which records all hospitalizations in non-federal short-stay acute-care general hospitals in Connecticut.
-OHCA provided us with weekly hospitalization statistics.
+The cases were identified from the hospitalization database maintained by the OHCA, who provided us with weekly hospitalization statistics.
 
@@
 
-\subsection{Modeling all-years RSV incidence}
+\section{Data normalization}
 
-Under the assumption that RSV incidence follows an annual cycle peaking during the winter, we aggregated RSV incidence by week of year.
+TODO: something about mod 52.14 for week-of-year, something about which weeks are attributed to which year/season
 
-Our goal was to generate a model that would allow us to sample from the distribution of (potential) RSV seasons, which in turn would enable us to estimate arbitrary characteristics of RSV seasons.
+\subsection{Choice of model}
 
-We accomplished this using a generalized additive model (GAM) with cyclic penalized cubic splines with 20 knots\footnote{Using the R \texttt{mgcv} package version 1.8-22}, via Poisson (log) link function.
+Our goal was to construct a model of RSV incidence over time that allows us to easily estimate complex characteristics of RSV seasons, such as season onset and offset, or RSV prophylaxis coverage.
 
-This type of model produces normal distribution estimates of all spline parameters.
-By sampling spline parameters from those normal distributions, we, in effect, sample from the distribution of splines fitting the data.
+To that end, we looked for a model that allows easy sampling of estimated model parameters; coupling this with Monte Carlo sampling would --- after transforming model parameters into response variables --- allow us to sample arbitrary response variables.
 
-As a result, we were able to estimate various characteristics of RSV seasons simply by sampling from distribution of splines fitting our data, and then --- with each sample spline corresponding to a putative RSV season --- calculating the desired characteristic of each spline.
+We were willing to assume that RSV incidence can be modeled as a piecewise time series of Poisson variables, and is twice differentiable.
 
-For this, we developed a custom R package for estimation of different characteristics of infectious disease outbreaks, which is available at \href{https://github.com/airbornemint/outbreakpredict}{\nolinkurl{github.com/airbornemint/outbreakpredict}}.
+To meet those criteria and assumptions, we chose generalized additive models (GAM) with penalized cubic B-splines for our analysis. (TODO prior use of pspline GAM in ID epi?)
+
+We developed a custom R package for estimation of arbitrary characteristics of infectious disease outbreaks, as long as the outbreaks are amenable to GAM predictions; this package is available at \href{https://github.com/airbornemint/outbreakpredict}{\nolinkurl{github.com/airbornemint/outbreakpredict}}.
 
@@
 
-All-years RSV incidence was aggregated by county, as well as statewide.
+For our spatial analysis, we aggregated RSV incidence data across all years in our data set. We then spatially aggregated the data to form five regions:
 
-Furthermore, some individual counties, with low incidence of RSV, yielded results with unimpressive statistical power.
-We aggregated those counties --- \Sexpr{gsub("(.*), (.*)", "\\1, and \\2", paste(lowIncidenceCounties, collapse=", "))} --- into a single non-contiguous region, and included that region as a separate spatial entity in our analysis.
+\begin{itemize}
+    \item One region for the entire state
+    \item One region for each of the counties with high incidence of RSV: Hartford County, Fairfield County, and New Haven County.
+    \item One region comprised of all remaining counties in Connecticut: \Sexpr{gsub("(.*), (.*)", "\\1, and \\2", paste(lowIncidenceCounties, collapse=", "))}
+\end{itemize}
+
+We chose county-level aggregation with an eye towards using this data to inform clinical practice guidelines, which are typically based on administrative regions for reasons of administrative and implementation simplicity.
+
+We chose to aggregate low-incidence counties into a single (non-contiguous) region because our analysis in those counties individually would have yielded results with unacceptably low statistical power.
+
+\subsection{Estimating coverage of prophylaxis following current guidelines}
+
+We began by assessing the current AAP RSV prophylaxis guidelines.
+These guidelines recommend RSV prophylaxis with 6 monthly doses of palivizumab, starting in November, for all high-risk infants under 2 (confirm in guidelines) years of age.
+
+For simplicity, we assumed that protection by palivizumab begins on November 15th and lasts 24 weeks.
+
+We defined coverage of a prophylaxis regimen to be the fraction of high-risk infants who would be exposed to RSV while they are protected by palivizumab.
+
+Given that high-risk infants are a small fraction of the general population (citation needed), we assumed that our model for RSV incidence based on hospitalization data of all infants is an unbiased estimate of RSV incidence among unprotected high-risk infants.
 
@@
 
-Having aggregated RSV incidence by week of year and by region, we estimated two characteristics of all-years RSV incidence in each region: season onset, defined as the time when cumulative incidence rises beyond \Sexpr{seasonThreshold * 100}\% of the total cumulative incidence; and season offset, defined as the time when cumulative incidence rises beyond \Sexpr{(1 - seasonThreshold) * 100}\% of the total cumulative incidence.
+We then turned our attention to spatial variation of seasonal RSV patterns across the time period covered by our data.
+In particular, we defined season onset as the time when cumulative incidence rises beyond \Sexpr{seasonThreshold * 100}\% of the total cumulative incidence and season offset as the time when cumulative incidence rises beyond \Sexpr{(1 - seasonThreshold) * 100}\% of the total cumulative incidence.
+We aggregated our data by week of year across all seasons, and estimated RSV season onset for each region.
 
-To arrive at this estimate, we sampled from the RSV season distribution given by the model, and calculated onset and offset for each sampled RSV season.
-
-\subsection{Estimating coverage of prophylaxis following current guidelines}
-
-We then turned our attention to the current guidelines for RSV prophylaxis, published by the American Academy of Pediatricians, most recently revised in ???.
-These guidelines recommend RSV prophylaxis with 6 monthly doses of palivizumab, starting in November, for all infants below 2 (?) years of age who are at high risk of ?.
-
-Given that high-risk infants are a small subgroup of the general population (?), we assumed that our model for RSV incidence based on hospitalization data is a good approximation of RSV incidence among high-risk infants.
-We then estimated the fraction of high-risk infants who elude protection from RSV because they are infected before receiving prophylaxis, or after protection from prophylaxis wanes.
-
-To estimate this, we began by sampling from the RSV season distribution given by the model.
-For each sampled RSV season, we considereda case of RSV to be covered by prophylaxis if it occurred between zero and 23 weeks (inclusive) after November 15th, and calculated the fraction of those cases among all cases.
+The choice of \Sexpr{seasonThreshold * 100}\% and \Sexpr{(1 - seasonThreshold) * 100}\% incidence thresholds was based on our intent to use estimates of RSV season onset and offset to put forth alternate prophylaxis regimens, as described below, while maintaining 6-month dosing schedule (and therefore not increasing medication cost).
+Incidence cutoffs other than \Sexpr{seasonThreshold * 100}\% and \Sexpr{(1 - seasonThreshold) * 100}\% were briefly investigated, but quickly ruled out because they produced suboptimal results.
 
@@
 
-Following this analysis, we devised six alternate prophylaxis guidelines.
-In all our alternative guidelines, prophylaxis consists of six monthly doses of palivizumab, and protection is assumed to last 24 weeks from the first dose.
+Following this analysis, we devised six alternate spatially adjusted prophylaxis regimens.
+In all our alternate regimens, prophylaxis consists of six monthly doses of palivizumab, and protection is assumed to last 24 weeks from the first dose.
 
 \begin{itemize}
-    \item \textbf{By statewide all-years onset}: prophylaxis administration begins on the date of the statewide all-years median RSV season onset. 
-    \item \textbf{By statewide all-years midpoint}: prophylaxis administration begins 12 weeks before the average of the statewide all-years median RSV season onset and offset. 
-    \item \textbf{By statewide all-years offset}: prophylaxis administration begins 24 weeks before the statewide all-years median RSV season offset. 
-    \item \textbf{By regional all-years onset}: prophylaxis administration begins on the date of the regional\footnote{county-wide, or --- in the case of low-incidence counties --- low-incidence-region-wide} all-years median RSV season onset.
-    \item \textbf{By regional all-years midpoint}: prophylaxis administration begins 12 weeks before the average of the regional all-years median RSV season onset and offset. 
-    \item \textbf{By regional all-years offset}: prophylaxis administration ends on the date of the regional all-years median RSV season offset. 
+    \item \textbf{By statewide all-years onset}: prophylaxis administration begins at statewide all-years median RSV season onset. 
+    \item \textbf{By statewide all-years midpoint}: prophylaxis administration begins 12 weeks before the average of the (statewide all-years median) season onset and offset. 
+    \item \textbf{By statewide all-years offset}: prophylaxis administration begins 24 weeks before the (statewide all-years median) RSV season offset. 
+    \item \textbf{By regional all-years onset}: prophylaxis administration begins at regional\footnote{county-wide, or --- in the case of low-incidence counties --- low-incidence-region-wide} all-years median RSV season onset.
+    \item \textbf{By regional all-years midpoint}: prophylaxis administration begins 12 weeks before the average of the (regional all-years median) RSV season onset and offset. 
+    \item \textbf{By regional all-years offset}: prophylaxis administration begins 24 weeks before the (regional all-years median) RSV season offset. 
 \end{itemize}
@@
 
-For the three statewide alternate guidelines, we estimated the number of cases eluding prophylaxis statewide, as well as in each region.
+For the three statewide alternate guidelines, we estimated coverage statewide, as well as in each region.
 
-For the three regional alternate guidelines, we estimated the number of cases eluding prophylaxis in each region.
+For the three regional alternate guidelines, we estimated coverage in each region.
 
-(TODO Should we also do a statewide analysis of regional strategies?)
+(TODO Consider also reporting net statewide coverage of regional regimens?)
+
+\subsection{Temporal aggregation of RSV incidence}
+
+Our analysis thus far assumed that RSV seasons are similar year-to-year.
+To analyze the effects on prophylaxis regimens of year-to-year variation between RSV seasons, we chose to aggregate our data into (overlapping) runs of three consecutive seasons, in order to maintain a higher level of statistical power, as well as to limit impact of short-term variation on our results.
+
+This gave us \Sexpr{year(endDate) - year(startDate) -1} ``superseasons'', the first covering \Sexpr{formatYear(startDate)} through \Sexpr{formatYear(startDate + 2*365)}, and the last covering \Sexpr{formatYear(endDate - 2*365)} through \Sexpr{formatYear(endDate)}.
+
+\subsection{Estimating three-year characteristics of RSV seasons}
+
+We began our temporal analysis by estimating RSV season onset and offset for each three-year superseason, using the same penalized spline GAM as all-years analysis, producing --- as before --- statewide and regional estimates of RSV season \Sexpr{seasonThreshold * 100}\% onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset.
 
@@
 
-Our analysis thus far assumed that RSV seasons are similar year-to-year. To evaluate this assumption, we ? TODO
-
-\subsection{Estimating three-year characteristics of RSV seasons}
-
-In order to reduce the potential impact on our model of long-term variation in RSV season onset and offset, we repeated our analysis of RSV season characteristics using a three-year sliding window.
-Rather that aggregating RSV incidence data across all years, as before, for sliding-window analysis we separately analyzed every three-year period starting on July 1st.
-
-This analysis used the same penalized spline GAM as all-years analysis, and also produced statewide and regional estimates of RSV season 5\% onset and 95\% offset.
+To evaluate year-to-year variation in RSV season onset and offset we modeled median RSV season onset and offset across 3-year superseasons against year using simple linear regression.
 
@@
 
-This analysis naturally leads to another approach to prophylaxis guidelines, in which prophylaxis recommendation is adjusted every year based on the timing of the RSV season onset and offset from the recent years.
-We evaluated two such alternate guidelines:
+Finally, to assess the impact of any long-term trends in timing of RSV season on prophylaxis, we formulated three additional prophylaxis regimens.
+Here, each prophylaxis regimen is adjusted annually based on RSV data from previous three seasons:
 
 \begin{itemize}
-    \item \textbf{By statewide recent-years onset}: prophylaxis administration in a given year begins on the date of the statewide median RSV season onset over the previous three years. 
-    \item \textbf{Statewide sliding window offset}: prophylaxis administration in a given year ends on the date of the statewide median RSV season offset over the previous three years.
+    \item \textbf{By statewide recent-years onset}: prophylaxis administration in a given year begins at statewide median RSV season onset from the previous three years. 
+    \item \textbf{By statewide recent-years midpoint}: prophylaxis administration begins 12 weeks before the average of the (statewide median) RSV RSV season onset and offset from the previous three years.
+    \item \textbf{By statewide recent-years offset}: prophylaxis administration in a given year begins 24 weeks before the (statewide median) RSV season offset over the previous three years.
 \end{itemize}
 
-As before, both alternate guidelines involve six monthly doses of palivizumab.
+We then compared those regimens to the one recommended by AAP and to the alternatives we previously devised based on spatial analysis.
+
+As before, all of these three alternate guidelines involved six monthly doses of palivizumab giving 24 weeks of protection.
 
@@
 
-        ggplot(countyPred) +
-            annotate("rect", xmin=ppxStart, xmax=ppxEnd, ymin=-Inf, ymax=+Inf, fill=hsv(1/3, 1, 1, .25)) + 
-            annotate("rect", xmin=countyThresholds$onset.median, xmax=countyThresholds$offset.median, ymin=-Inf, ymax=+Inf, fill=hsv(0, 1, 1, .25)) + 
-            geom_ribbon(aes(ymin=rsv.cum.fit.lower, ymax=rsv.cum.fit.upper, x=time), fill=grey(.25)) + 
-            annotate("segment", x=ppxStart, y=.45, xend=ppxEnd, yend=.45, color=hsv(1/3, 1, .5)) + 
-            annotate("point", x=(ppxStart + ppxEnd) / 2, y=.45, color=hsv(1/3, 1, .5), shape=3) + 
-            annotate("segment", x=countyThresholds$onset.median, y=.55, xend=countyThresholds$offset.median, yend=.55, color=hsv(0, 1, .5)) + 
-            annotate("point", x=(countyThresholds$onset.median + countyThresholds$offset.median) / 2, y=.55, color=hsv(0, 1, .5), shape=3) + 
-            annotate("point", x=ppxStart, y=unprotectedAtStart) + 
-            annotate("point", x=ppxEnd, y=unprotectedAtEnd) + 
-            scale_y_continuous(labels=scales::percent, breaks=seq(0, 1, by=.2), limits=c(0, 1), expand=c(0.05, 0)) +
+        annotation_timespan = function(plot, xmin, xmax, y, color, label) {
+            ymin = y - .01
+            ymax = y + .01
+            yminlabel = y + .01
+            ymaxlabel = y + .11
+            plot + annotation_custom(linesGrob(gp=gpar(col=color)), xmin=xmin, ymin=y, xmax=xmax, ymax=y) + 
+            annotation_custom(linesGrob(gp=gpar(col=color)), xmin=xmin, ymin=ymin, xmax=xmin, ymax=ymax) + 
+            annotation_custom(linesGrob(gp=gpar(col=color, lty="dotted")), xmin=xmin, ymin=0, xmax=xmin, ymax=1) + 
+            annotation_custom(linesGrob(gp=gpar(col=color)), xmin=xmax, ymin=ymin, xmax=xmax, ymax=ymax) + 
+            annotation_custom(linesGrob(gp=gpar(col=color, lty="dotted")), xmin=xmax, ymin=0, xmax=xmax, ymax=1) + 
+#            annotation_custom(linesGrob(gp=gpar(col=color)), xmin=(xmin + xmax) / 2, ymin=y-0.02, xmax=(xmin + xmax) / 2, ymax=y+0.02) + 
+            annotation_custom(textGrob(label, gp=gpar(col=color)), xmin=xmin, xmax=xmax, ymin=yminlabel, ymax=ymaxlabel)
+        }
+
+        plot = ggplot(countyPred) +
+            geom_ribbon(aes(ymin=rsv.cum.fit.lower, ymax=rsv.cum.fit.upper, x=time), fill=grey(.25))
+        plot = plot %>%
+            annotation_timespan(ppxStart, ppxEnd, 1.05, hsv(1/3, 1, .5), "Prophylaxis") %>%
+            annotation_timespan(countyThresholds$onset.median, countyThresholds$offset.median, -0.05, hsv(0, 1, .5), "RSV Season")
+        plot = plot + 
+            annotate("segment", x=-Inf, y=unprotectedAtStart, xend=ppxStart, yend=unprotectedAtStart, linetype=3) + 
+            annotate("segment", x=-Inf, y=unprotectedAtEnd, xend=ppxEnd, yend=unprotectedAtEnd, linetype=3) + 
+            scale_y_continuous(labels=scales::percent, breaks=seq(0, 1, by=.2), limits=c(0, 1), expand=c(0.2, 0)) +
             labs(x=c) +
@@
             )
+        table = ggplot_gtable(ggplot_build(plot))
+        table$layout$clip[table$layout$name == "panel"] <- "off"
+
+        plot
     }), cols=2)
@@
 
+\begin{figure*}[t]
+<<onsetOffsetByYear, warning=FALSE>>=
+    onset = ggplot(stateThresholdsByWindow) +
+        geom_errorbar(aes(ymin=onset.lower, ymax=onset.upper, x=year), width=.25) + 
+        geom_point(aes(y=onset.median, x=year)) + 
+        labs(x="RSV Season Onset")
+    offset = ggplot(stateThresholdsByWindow) +
+        geom_errorbar(aes(ymin=offset.lower, ymax=offset.upper, x=year), width=.25) + 
+        geom_point(aes(y=offset.median, x=year)) + 
+        labs(x="RSV Season Offset")
+
+    ggplot2.multiplot(plotlist=list(onset, offset), cols=2)
+@
+
+\caption{RSV season onset and offset by three-year superseason.}
+\label{fig:onsetOffsetByYear}
+\end{figure*}
+
 \subsection{RSV season in low-incidence counties begins late}
@@
 
-Statewide, our model shows that \Sexpr{regionStrategyCoverage("all", "aap")} of RSV cases (\Sexpr{regionStrategyCoverageCI("all", "aap", level)}) occur during the time when palivizumab is administered according to the AAP guidelines.
+Statewide, our model shows that \Sexpr{regionStrategyCoverage("all", "aap")} of RSV cases (\Sexpr{regionStrategyCoverageCI("all", "aap", level)}) occur while palivizumab, administered according to AAP guidelines, offers protection.
 The AAP guidelines perform better in the low-incidence counties, where \Sexpr{regionStrategyCoverage("lowIncidence", "aap")} cases (\Sexpr{regionStrategyCoverageCI("lowIncidence", "aap", level)}) occur during the prophylaxis time window, but worse in Fairfield county, where \Sexpr{regionStrategyCoverage("Fairfield", "aap")} cases ((\Sexpr{regionStrategyCoverageCI("Fairfield", "aap", level)})) occur during this time.
@@
 
-The cause of this is evident in Figure \ref{fig:coverageByRegionAAPInsight}, which shows temporal misalignment between the time window of the RSV season (delineated by median 2.5\% onset and 97.5\% offset in each region), and the time window of AAP prophylaxis guidelines.
-Fairfield county, owing to its early season onset has disproportionately many cases before prophylaxis administration begins; on the other hand, the low-incidence counties, owing to their late season onset, have their RSV seasons almost entirely contained within the prophylaxis window.
+The cause of this is evident in Figure \ref{fig:coverageByRegionAAPInsight}, which shows temporal misalignment between the time window of the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each region), and the time window of AAP prophylaxis guidelines.
+Fairfield county, owing to its early season onset, has disproportionately many cases before prophylaxis administration begins; on the other hand, the low-incidence counties, owing to their late season onset, have their RSV seasons almost entirely contained within the prophylaxis window.
 
-\subsection{All-years alternate guidelines are superior to AAP statewide and in Hartford county, and non-inferior otherwise}
+\subsection{All-years prophylaxis regimens are superior to AAP recommendations statewide and in Hartford county}
 
-The six alternate prophylaxis guidelines based on all-years data (in which prophylaxis time window is determined by statewide or regional all-years RSV season onset or offset), when compared to the AAP guidelines, yield non-inferior results in all regions, and superior results both statewide and in Hartford county.
+The six spatially adjusted prophylaxis guidelines based on all-years data, when compared to the AAP guidelines, yield non-inferior results in all regions, and superior results both statewide and in Hartford county.
 (Figure \ref{fig:coverageByRegion}.)
@@
 
-In every region, all alternate guidelines based on all-years analysis are non-inferior to AAP guidelines and non-superior to each other.
+In every region, all alternate regimens based on all-years analysis are non-inferior to the AAP guidelines and non-superior to each other.
 
-\subsection{Sliding window alternate guidelines are inferior to AAP guidelines in low-incidence counties, and non-superior otherwise.}
+\subsection{RSV season onset and offset is unchanged over time}
 
-Contrariwise, the two strategies based on statewide data produced non-superior results in all regions except for the low-incidence counties, where they produced inferior results. (Figure.)
+Our linear regression of median superseason onset and offset against calendar year (Figure \ref{fig:onsetOffsetByYear}) indicates (at 95\% confidence level) that season onset has not been drifting (\Sexpr{formatDriftCI(onsetByYear, level)}), and neither has season offset (\Sexpr{formatDriftCI(offsetByYear, level)}).
 
-Due to the non-superiority of statewide sliding-window strategies, regional sliding-window strategies were not evaluated.
+We did not analyze any long-term patterns, such as cyclicity.
+
+\subsection{Recent-years prophylaxis regimens are non-superior to others.}
+
+The three regimens based on statewide recent-years analysis produced non-superior results in all regions except for the low-incidence counties, where they produced inferior results.
+(TODO: Figure.) TODO: specifics
+
+Due to the non-superiority of regimens based on statewide recent-years data, we did not evaluate regimens based on regional recent-years data.
 
 \section{Discussion}
+
+Our model shows that coverage of RSV immunoprophylaxis in high-risk infants in Connecticut can be improved from that provided by the prophylaxis regimen currently recommended by the AAP.
+
+The simplest such improvement we can propose is to ignore regional variation within Connecticut, and begin prophylaxis throughout Connecticut a month earlier, according to the regimen based on all-years statewide season onset analysis.
+However --- because our analysis suggests that that regimen might be slightly inferior to the AAP-recommended regimen in counties with low incidence of RSV --- this might lead to a bifurcation, in which clinicians in low-incidence counties would continue following the current AAP guidelines, and in others would adopt the new guidelines.
+
+Therefore, since an attempt to transition to new state-wide guidelines might effectively result in a transition to county-level guidelines, it would likely be preferable to use our county-level analysis in the first place.
+With that, our analysis favors the prophylaxis regimen linked to regional RSV season midpoint.
+Under this regimen, TODO which county uses what, and the net benefit would be XX\% increase in prophylaxis coverage.
+
+However, that leaves open the question of whether transitioning to such guidelines would be too costly.
+Although our prophylaxis regimens were specifically chosen to keep fixed the cost of pharmaceuticals, we did not evaluate implementation cost of our proposals; such analysis would be necessary before elevating them from proposals to recommendations.
 

### 2018-01-13 Thesis/Thesis.rnw
Meeting notes
Assorted rewrite and applied nice template

@@
 % Agenda
-%  * Is coverage the right word
 %  * Round time periods pre-coverage analysis in order to make conclusion make sense
-%  * Added guidelines based on season midpoint
-%  * Nothing in linear regression of onset/offset
-%  * What level of feedback am I looking for
-%  * Publication-quality not a goal for Jan 26
 % 
@@
 %  * Change how mod 52-1/7 is done
+%  * "Coverage" -> preventable fraction
+%  * "Statewide"
 
@@
 
-\documentclass{article}
+\documentclass[10pt, a4paper, twocolumn]{article}
+\input{structure.tex}
 
-\usepackage{multicol,float}
+\usepackage{float}
 \usepackage{hyperref}
 \usepackage{draftwatermark}
-\SetWatermarkText{DRAFT}
-\SetWatermarkScale{4}
-
-\usepackage{titling}
-\newcommand{\subtitle}[1]{%
-  \posttitle{%
-    \par\end{center}
-    \begin{center}\large#1\end{center}
-    \vskip0.5em}%
-}
+\SetWatermarkText{DRAFT \#1}
+\SetWatermarkScale{1}
 
@@
 
-\title{Assessment and optimization of respiratory syncytial virus immunoprophylaxis regimens using Monte Carlo sampling of a penalized spline generalized additive model of hospital admissions in Connecticut between \Sexpr{formatYear(startDate)} and \Sexpr{formatYear(endDate)}}
+\title{Optimization of respiratory syncytial virus prophylaxis using a generalized additive model of Connecticut hospitalizations}
 
-\author{Ben Artin, YSPH/YSM 2018, if all goes well}
+\author{
+	\authorstyle{Ben Artin\textsuperscript{1}} % Authors
+	\newline\newline
+	\authorstyle{Daniel Weinberger, PhD\textsuperscript{2}, advisor}\\
+	\authorstyle{Virginia Pitzer, ScD\textsuperscript{2}, advisor}
+	\newline\newline
+	\textsuperscript{1}\institution{Yale University, School of Public Health and School of Medicine}\\
+	\textsuperscript{2}\institution{Yale University, School of Public Health}
+}
+
 \date{Draft \#1, \today}
@@
 \maketitle
+\thispagestyle{firstpage}
+
+\clearpage
 
@@
 
-We describe a generalized additive model of RSV incidence using cubic cyclic penalized splines and apply that model to hospital admissions records from Connecticut between \Sexpr{formatDate(startDate)} and \Sexpr{formatDate(endDate)} to estimate coverage (TODO: is coverage the best term?) of RSV immunoprophylaxis administered in Connecticut according to the AAP guidelines.
-We also formulate several alternative immunoprophylaxis regimens with the same net pharmaceutical cost, and compare the coverage and implementation complexity of those alternative regimens to the AAP-recommended regimen.
+We describe a generalized additive model of RSV incidence using cubic cyclic penalized splines and apply that model to hospital admissions records from Connecticut between \Sexpr{formatDate(startDate)} and \Sexpr{formatDate(endDate)} to estimate fraction of RSV cases in Connecticut preventable by immunoprophylaxis administered according to the AAP guidelines.
+We also formulate several alternate immunoprophylaxis regimens with the same net pharmaceutical cost, estimate the fraction preventable by those alternate regimens.
 
@@
 
-At 95\% confidence level, we found alternative regimens which account for spatial variability of RSV incidence to have superior coverage (to that of the AAP regimen) in some regions of Connecticut, and non-inferior coverage in other regions.
-We also found alternative regimens which account for temporal RSV variability to have non-superior coverage to our spatially-adjusted regimens, while being considerably more complex to implement.
-Finally, we found our best-performing alternative to AAP guidelines to provide a XX\% state-wide increase in RSV prophylaxis coverage over the AAP regimen.
+At 95\% confidence level, we found alternate regimens that account for spatial variability of RSV incidence at the county level to have superior coverage (to that of the AAP-recommended regimen) in some regions of Connecticut, and non-inferior coverage in other regions.
+We also found alternate regimens that account for temporal RSV variability at the annual level to have non-superior coverage to our spatially-adjusted regimens.
+Overall, we found our best-performing spatially-adjusted alternate to AAP guidelines to provide a XX\% state-wide increase in RSV prophylaxis coverage over the AAP regimen.
 
@@
 
-We conclude that the increased prophylaxis coverage provided by regimens based on our spatial analysis warrants further analysis to determine whether the potential reduction in hospitalization rate is nullified by the potential increase in implementation cost.
+We conclude that the increased prophylaxis coverage provided by regimens based on our county-level spatial analysis warrants further analysis to determine whether the potential reduction in hospitalization rate is nullified by the potential increase in implementation cost.
+Our temporal analysis at the annual level showed no additional benefit beyond the spatial analysis, while simultaneously increasing implementation complexity.
+Overall, we recommend county-level spatial analysis of RSV incidence as the starting point for RSV immunoprophylaxis optimization in Connecticut.
 
@@
 
-\begin{multicols}{2}
+\clearpage
+
+%\begin{multicols}{2}
 
@@
 Owing to the high cost, the American Academy of Pediatrics (AAP) recommends palivizumab immunoprophylaxis only for high-risk infants, and only during RSV season.
-These guidelines were most recently revised in ???.
+These guidelines were most recently revised in 2014.
 
@@
 
-Motivated by AAP's recognition of the impact of spatial variation in RSV incidence on optimizing RSV immunoprophylaxis guidelines, and the known spatial variability of RSV incidence in Connecticut, our study asks these questions:
+Motivated by AAP's recognition of the impact of spatial variation in RSV incidence on optimizing RSV immunoprophylaxis regimens, and the known spatial variability of RSV incidence in Connecticut, our study asks these questions:
 
@@
 	\item To what extent does regional variability of RSV incidence in Connecticut impact the effectiveness of the AAP-recommended prophylaxis regimen?
-	\item Can we use spatial analysis of RSV to propose alternative guidelines, either state-wide or regional, that would improve effectiveness over AAP-recommended prophylaxis, without increasing treatment cost?
+	\item Can we use spatial analysis of RSV to propose alternate regimens, either state-wide or regional, that would improve effectiveness over AAP-recommended prophylaxis, without increasing treatment cost?
 	\item Is there year-to-year variation in timing of RSV season in Connecticut?
@@
 
-We defined a case of RSV to be a hospital stay recorded in the OHCA hospitalization database meeting the following criteria:
+We defined a case of RSV to be a hospital stay recorded in the OHCA hospitalization database meeting for which:
 
@@
     \item postal code of residence listed in patient's medical record was in Connecticut\footnote{According to the zipcode $\rightarrow$ state mapping in R \texttt{zipcode} package version 1.0}, and
-    \item hospital stay was associated with an RSV billing code\footnote{TODO Which codes?}
+    \item hospital stay was associated with ICD-9-CM diagnosis code \texttt{079.6} (RSV), \texttt{466.11} (Acute bronchiolitis due to RSV), or \texttt{480.1} (Pneumonia due to RSV).
 \end{itemize}
@@
 
-TODO: something about mod 52.14 for week-of-year, something about which weeks are attributed to which year/season
+Given that RSV seasons peak early in each calendar year, to each surveillance year we assigned 12 months of data starting in July of previous year.
+
+OHCA data was provided grouped by Monday-Sunday calendar week; we assigned the first full calendar week of July to be surveillance week 1.
+
+Due to changes in diagnostic coding, we excluded data prior to July 1996; surveillance year 2014 had incomplete data and was also excluded.
 
@@
 
-Our goal was to construct a model of RSV incidence over time that allows us to easily estimate complex characteristics of RSV seasons, such as season onset and offset, or RSV prophylaxis coverage.
+Our goal was to construct a model of RSV incidence over time that allows us to easily estimate complex characteristics of RSV seasons, such as season onset and offset, or preventable RSV case fraction.
 
@@
 
-We were willing to assume that RSV incidence can be modeled as a piecewise time series of Poisson variables, and is twice differentiable.
+We were willing to assume that RSV incidence can be modeled as a twice-differentiable piecewise Poisson time series.
 
-To meet those criteria and assumptions, we chose generalized additive models (GAM) with penalized cubic B-splines for our analysis. (TODO prior use of pspline GAM in ID epi?)
+To meet those criteria and assumptions, we chose a log-linked generalized additive model (GAM) with penalized cubic B-splines for our analysis.
 
-We developed a custom R package for estimation of arbitrary characteristics of infectious disease outbreaks, as long as the outbreaks are amenable to GAM predictions; this package is available at \href{https://github.com/airbornemint/outbreakpredict}{\nolinkurl{github.com/airbornemint/outbreakpredict}}.
+% Looked for prior art on using GAM/pspline for ID epi, didn't find anything that was relevant. (Not even by Goldstein or Lipsitch.)
+
+We developed a custom R package for estimation of arbitrary characteristics of infectious disease outbreaks (as long as the outbreaks are amenable to GAM); this package is available at \href{https://github.com/airbornemint/outbreakpredict}{\nolinkurl{github.com/airbornemint/outbreakpredict}}.
 
@@
     \item One region for each of the counties with high incidence of RSV: Hartford County, Fairfield County, and New Haven County.
-    \item One region comprised of all remaining counties in Connecticut: \Sexpr{gsub("(.*), (.*)", "\\1, and \\2", paste(lowIncidenceCounties, collapse=", "))}
+    \item One discontiguous region comprised of all remaining counties in Connecticut: \Sexpr{gsub("(.*), (.*)", "\\1, and \\2", paste(lowIncidenceCounties, collapse=", "))}
 \end{itemize}
@@
 
-We chose to aggregate low-incidence counties into a single (non-contiguous) region because our analysis in those counties individually would have yielded results with unacceptably low statistical power.
+We chose to aggregate low-incidence counties into a single region because our analysis in those counties individually would have yielded results with unacceptably low statistical power.
 
-\subsection{Estimating coverage of prophylaxis following current guidelines}
+\subsection{Estimating RSV fraction preventable by AAP-recommended prophylaxis}
 
 We began by assessing the current AAP RSV prophylaxis guidelines.
-These guidelines recommend RSV prophylaxis with 6 monthly doses of palivizumab, starting in November, for all high-risk infants under 2 (confirm in guidelines) years of age.
+These guidelines recommend RSV prophylaxis with 6 monthly doses of palivizumab, starting in November, for all high-risk infants in their first year of life; in the second year of life, only some subgroups are recommended to receive palivizumab.
 
@@
 
-We defined coverage of a prophylaxis regimen to be the fraction of high-risk infants who would be exposed to RSV while they are protected by palivizumab.
+We defined fraction of RSV cases preventable by a prophylaxis regimen (``preventable fraction'') to be the fraction of high-risk infants who would be exposed to RSV while they are protected by palivizumab.
 
@@
 We then turned our attention to spatial variation of seasonal RSV patterns across the time period covered by our data.
-In particular, we defined season onset as the time when cumulative incidence rises beyond \Sexpr{seasonThreshold * 100}\% of the total cumulative incidence and season offset as the time when cumulative incidence rises beyond \Sexpr{(1 - seasonThreshold) * 100}\% of the total cumulative incidence.
-We aggregated our data by week of year across all seasons, and estimated RSV season onset for each region.
+In particular, we defined season onset as the time when cumulative incidence rises beyond \Sexpr{seasonThreshold * 100}\% of the total cumulative incidence, and season offset as the time when cumulative incidence rises beyond \Sexpr{(1 - seasonThreshold) * 100}\% of the total cumulative incidence.
+We aggregated our data by surveillance week across all surveillance years, and estimated RSV season onset and offset for each region.
 
-The choice of \Sexpr{seasonThreshold * 100}\% and \Sexpr{(1 - seasonThreshold) * 100}\% incidence thresholds was based on our intent to use estimates of RSV season onset and offset to put forth alternate prophylaxis regimens, as described below, while maintaining 6-month dosing schedule (and therefore not increasing medication cost).
+The choice of \Sexpr{seasonThreshold * 100}\% and \Sexpr{(1 - seasonThreshold) * 100}\% incidence thresholds was based on our intent to use estimates of RSV season onset and offset to put forth alternate prophylaxis regimens (as described below), while maintaining 6-month dosing schedule (and therefore not increasing medication cost).
 Incidence cutoffs other than \Sexpr{seasonThreshold * 100}\% and \Sexpr{(1 - seasonThreshold) * 100}\% were briefly investigated, but quickly ruled out because they produced suboptimal results.
 
-\subsection{Devising alternate all-years prophylaxis guidelines}
+\subsection{Devising alternate all-years prophylaxis regimens}
 
@@
 
-\subsection{Evaluating alternate prophylaxis guidelines}
+\subsection{Evaluating alternate prophylaxis regimens}
 
-We evaluated each of those alternate guidelines in the same way we evaluated the current AAP guidelines, as described above.
+We evaluated each of those alternate regimens in the same way we evaluated the current AAP guidelines, as described above.
 
-For the three statewide alternate guidelines, we estimated coverage statewide, as well as in each region.
+For the three alternate regimens based on state-wide data, we estimated preventable fraction statewide, as well as in each region.
 
-For the three regional alternate guidelines, we estimated coverage in each region.
+For the three alternate regimens based on regional data, we estimated coverage in the corresponding region.
 
-(TODO Consider also reporting net statewide coverage of regional regimens?)
+% TODO Consider also reporting net statewide coverage of regional regimens
 
@@
 Our analysis thus far assumed that RSV seasons are similar year-to-year.
-To analyze the effects on prophylaxis regimens of year-to-year variation between RSV seasons, we chose to aggregate our data into (overlapping) runs of three consecutive seasons, in order to maintain a higher level of statistical power, as well as to limit impact of short-term variation on our results.
+To analyze the effects on prophylaxis regimens of year-to-year variation between RSV seasons, we chose to aggregate our data into (overlapping) runs of three consecutive seasons --- in order to maintain a higher level of statistical power, as well as to limit impact of short-term variation on our results.
 
-This gave us \Sexpr{year(endDate) - year(startDate) -1} ``superseasons'', the first covering \Sexpr{formatYear(startDate)} through \Sexpr{formatYear(startDate + 2*365)}, and the last covering \Sexpr{formatYear(endDate - 2*365)} through \Sexpr{formatYear(endDate)}.
+This gave us \Sexpr{year(endDate) - year(startDate) -1} ``surseasons'', with the \Sexpr{formatYear(startDate + 2*365)} surseason covering \Sexpr{formatYear(startDate)} through \Sexpr{formatYear(startDate + 2*365)} surveillance year, and the \Sexpr{formatYear(endDate)} surseason covering \Sexpr{formatYear(endDate - 2*365)} through \Sexpr{formatYear(endDate)}.
 
-\subsection{Estimating three-year characteristics of RSV seasons}
+\subsection{Estimating characteristics of RSV surseasons}
 
-We began our temporal analysis by estimating RSV season onset and offset for each three-year superseason, using the same penalized spline GAM as all-years analysis, producing --- as before --- statewide and regional estimates of RSV season \Sexpr{seasonThreshold * 100}\% onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset.
+We began our temporal analysis by estimating onset and offset for each surseason, using the same penalized spline GAM as all-years analysis, producing --- as before --- statewide and regional estimates of \Sexpr{seasonThreshold * 100}\% onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset.
 
@@
 
-To evaluate year-to-year variation in RSV season onset and offset we modeled median RSV season onset and offset across 3-year superseasons against year using simple linear regression.
+To evaluate year-to-year variation in RSV season onset and offset we modeled median RSV surseason onset and offset against surseason year using simple linear regression.
 
-\subsection{Devising alternate recent-years prophylaxis guidelines}
+We did not analyze any other long-term patterns, such as cyclicity.
 
-Finally, to assess the impact of any long-term trends in timing of RSV season on prophylaxis, we formulated three additional prophylaxis regimens.
-Here, each prophylaxis regimen is adjusted annually based on RSV data from previous three seasons:
+\subsection{Devising alternate recent-years prophylaxis regimens}
+
+Finally, to assess the impact of any long-term trends in RSV season timing on prophylaxis, we formulated three additional prophylaxis regimens.
+Here, each prophylaxis regimen is adjusted annually based on RSV data from the preceding surseason:
 
 \begin{itemize}
-    \item \textbf{By statewide recent-years onset}: prophylaxis administration in a given year begins at statewide median RSV season onset from the previous three years. 
-    \item \textbf{By statewide recent-years midpoint}: prophylaxis administration begins 12 weeks before the average of the (statewide median) RSV RSV season onset and offset from the previous three years.
-    \item \textbf{By statewide recent-years offset}: prophylaxis administration in a given year begins 24 weeks before the (statewide median) RSV season offset over the previous three years.
+    \item \textbf{By statewide recent-years onset}: prophylaxis administration in a given year begins at statewide median onset from the preceding three years. 
+    \item \textbf{By statewide recent-years midpoint}: prophylaxis administration begins 12 weeks before the average of the (statewide median) onset and offset from the preceding three years. 
+    \item \textbf{By statewide recent-years offset}: prophylaxis administration in a given year begins 24 weeks before the (statewide median) offset from the preceding three years.
 \end{itemize}
 
-We then compared those regimens to the one recommended by AAP and to the alternatives we previously devised based on spatial analysis.
+We then compared those regimens to the one recommended by AAP and to the alternates we previously devised based on spatial analysis.
 
-As before, all of these three alternate guidelines involved six monthly doses of palivizumab giving 24 weeks of protection.
+As before, these alternate regimens involved six monthly doses of palivizumab giving 24 weeks of protection.
 
@@
 
-\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by region and prophylaxis guidelines.}
+\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by region and prophylaxis regimen.}
 \label{fig:coverageByRegion}
@@
 
-\subsection{All-years prophylaxis regimens are superior to AAP recommendations statewide and in Hartford county}
+\subsection{Spatially-informed regimens are superior to AAP recommendations overall and in Hartford county}
 
-The six spatially adjusted prophylaxis guidelines based on all-years data, when compared to the AAP guidelines, yield non-inferior results in all regions, and superior results both statewide and in Hartford county.
+Based on all-years data, the six spatially adjusted prophylaxis regimens, when compared to the AAP guidelines, yield non-inferior results in all regions, and superior results both statewide and in Hartford county.
 (Figure \ref{fig:coverageByRegion}.)
 
-Statewide, the AAP guidelines produce prophylaxis coverage for \Sexpr{regionStrategyCoverage("all", "aap")} cases (\Sexpr{regionStrategyCoverageCI("all", "aap", level)}); meanwhile, the guidelines based on all-years statewide onset yield the weakest improvement at \Sexpr{regionStrategyCoverage("all", "stateOnset")} coverage (\Sexpr{regionStrategyCoverageCI("all", "stateOnset", level)}), and other alternate guidelines yield similar results.
+Statewide, the AAP guidelines generate protection for \Sexpr{regionStrategyCoverage("all", "aap")} cases (\Sexpr{regionStrategyCoverageCI("all", "aap", level)}); meanwhile, the regimens based on all-years statewide onset produce the weakest improvement at \Sexpr{regionStrategyCoverage("all", "stateOnset")} coverage (\Sexpr{regionStrategyCoverageCI("all", "stateOnset", level)}), and other alternate regimens yield similar results.
 
 In Hartford county, the improvement is more noteworthy.
-Here, the AAP guidelines cover \Sexpr{regionStrategyCoverage("Hartford", "aap")} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", level)}); the guidelines based on all-years regional offset generate the weakest improvement to \Sexpr{regionStrategyCoverage("Hartford", "countyOffset")} coverage (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", level)}), and other alternate guidelines are comparable.
+Here, the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap")} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", level)}); the regimens based on all-years regional offset generate the weakest improvement to \Sexpr{regionStrategyCoverage("Hartford", "countyOffset")} protection (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", level)}), and other alternate regimens are comparable.
 
@@
 
-Our linear regression of median superseason onset and offset against calendar year (Figure \ref{fig:onsetOffsetByYear}) indicates (at 95\% confidence level) that season onset has not been drifting (\Sexpr{formatDriftCI(onsetByYear, level)}), and neither has season offset (\Sexpr{formatDriftCI(offsetByYear, level)}).
-
-We did not analyze any long-term patterns, such as cyclicity.
+Our linear regression of median surseason onset and offset against surseason year (Figure \ref{fig:onsetOffsetByYear}) indicates (at 95\% confidence level) that season onset has not been drifting earlier (\Sexpr{formatDriftCI(onsetByYear, level)}), and neither has season offset (\Sexpr{formatDriftCI(offsetByYear, level)}).
 
@@
 
-The three regimens based on statewide recent-years analysis produced non-superior results in all regions except for the low-incidence counties, where they produced inferior results.
+Compared to our regional analysis, the three regimens based on statewide recent-years analysis produced non-superior results in all regions except for the low-incidence counties, where they produced inferior results.
 (TODO: Figure.) TODO: specifics
 
-Due to the non-superiority of regimens based on statewide recent-years data, we did not evaluate regimens based on regional recent-years data.
+Due to the non-superiority of regimens based on statewide recent-years analysis, we did not evaluate regimens based on regional recent-years data.
 
@@
 
-\end{multicols}
+%\end{multicols}
 

### 2018-01-14 Analysis/RSV.Rmd
Abstract sections; inline figures using TikZ; refactoring

@@
 ```{r setup, include=FALSE, error=FALSE, warning=FALSE, message=FALSE}
-install.packages(c("dplyr", "zipcode", "reshape", "mgcv", "ggplot2", "gridExtra", "devtools", "data.table"))
+install.packages(c("dplyr", "zipcode", "reshape", "mgcv", "ggplot2", "gridExtra", "devtools", "data.table", "tikzDevice", "splitstackshape"))
 library(devtools)

### 2018-01-14 Thesis/Thesis.rnw
Abstract sections; inline figures using TikZ; refactoring

@@
 <<options, echo=FALSE>>=
-    opts_chunk$set(echo=FALSE, message=FALSE)
+    opts_chunk$set(echo=FALSE, message=FALSE, root.dir=".texpadtmp")
 @
@@
 read_chunk("../Analysis/RSV.R")
+read_chunk("../Thesis/Thesis.R")
 @
@@
 <<util>>=
-library(grid)
-
-# Formatting utilities
-formatDate = function(date) {
-    format(date, "%B, %d, %Y")
-}
-
-formatYear = function(date) {
-    format(date, "%Y")
-}
-
-formatThreshold = function(threshold) {
-    sprintf("%.2f", threshold %% 52)
-}
-
-regionOnset = function(c) {
-    formatThreshold((thresholdsByCounty %>% filter(county==c))$onset.median)
-}
-
-regionOffset = function(c) {
-    formatThreshold((thresholdsByCounty %>% filter(county==c))$offset.median)
-}
-
-formatThresholdCI = function(lower, upper, level) {
-    sprintf("%d\\%% CI: %.2f -- %.2f", level * 100, lower %% 52, upper %% 52)
-}
-
-regionOnsetCI = function(c, level) {
-    formatThresholdCI(
-        (thresholdsByCounty %>% filter(county==c))$onset.lower, 
-        (thresholdsByCounty %>% filter(county==c))$onset.upper, 
-        level
-    )
-}
-
-regionOffsetCI = function(c, level) {
-    formatThresholdCI(
-        (thresholdsByCounty %>% filter(county==c))$offset.lower, 
-        (thresholdsByCounty %>% filter(county==c))$offset.upper, 
-        level
-    )
-}
-
-formatPct = function(pct) {
-    sprintf("%.2f\\%%", pct * 100)
-}
-
-formatPctCI = function(lower, upper, level) {
-    sprintf("%d\\%% CI: %.2f -- %.2f\\%%", level * 100, lower * 100, upper * 100)
-}
-
-regionStrategyCoverage = function(c, s) {
-    formatPct((unprotectedByCounty %>% filter(county==c, strat==s))$frac.median)
-}
-
-regionStrategyCoverageCI = function(c, s, level) {
-    formatPctCI(
-        (unprotectedByCounty %>% filter(county==c, strat==s))$frac.upper,
-        (unprotectedByCounty %>% filter(county==c, strat==s))$frac.lower,
-        level
-    )
-}
-
-driftYearToWeek = function(year, negate) {
-    drift = 365 / 7 * year
-    if (negate) {
-        -drift
-    } else {
-        drift
-    }
-}
-
-formatDrift = function(lm, negate=FALSE) {
-    sprintf("%.2f weeks", driftYearToWeek(summary(lm)$coefficients['year', 1], negate))
-}
-
-formatDriftCI = function(lm, level, negate=TRUE) {
-    ci = confint(lm, "year", level=level)
-    sprintf(
-        "%d\\%% CI: %.2f -- %.2f weeks", level * 100, 
-        driftYearToWeek(min(ci), negate), 
-        driftYearToWeek(max(ci), negate)
-    )
-}
-
-# Counties which we plot (so, not individual low-incidence counties)
-countiesForPlots = thresholdsByCounty$county[!thresholdsByCounty$county %in% lowIncidenceCounties]
 @
 
-\documentclass[10pt, a4paper, twocolumn]{article}
+\documentclass[10pt,a4paper,draft]{article}
+
+\usepackage{multicol,float}
+\floatplacement{figure}{H}
+
+\usepackage{printlen}
+\usepackage{textcomp}
+
+\usepackage{hyperref}
+\usepackage[svgnames]{xcolor} % Must go before tikz and before structure.tex
+\usepackage{tikz}
+\usepackage{draftwatermark}
+\SetWatermarkScale{1}
+\SetWatermarkAngle{45}
+\SetWatermarkFontSize{4ex}
+\SetWatermarkHorCenter{12ex}
+\SetWatermarkVerCenter{12ex}
+\SetWatermarkLightness{.5}
+\SetWatermarkText{DRAFT 2}
+
 \input{structure.tex}
 
-\usepackage{float}
-\usepackage{hyperref}
-\usepackage{draftwatermark}
-\SetWatermarkText{DRAFT \#1}
-\SetWatermarkScale{1}
+\usepackage[bf,medium,raggedright,compact]{titlesec}
+\titleformat{\section}{\normalfont\large\bfseries\scshape}{\thesection}{1em}{}
+\titleformat{\subsection}{\normalfont\normalsize\bfseries\scshape}{}{0em}{}
+\titleformat{\paragraph}{\normalfont\normalsize\bfseries}{}{0em}{}
+\titlespacing*{\paragraph}{0pt}{3.25ex plus 1ex minus .2ex}{0em}
 
-\newcommand{\abstractsection}[1]{\section*{#1}}
+\newcommand{\abstractsection}[1]{\makebox[1in][l]{\textbf{#1}}}
 
 \title{Optimization of respiratory syncytial virus prophylaxis using a generalized additive model of Connecticut hospitalizations}
+\def\headertitle{Optimization of RSV prophylaxis using a generalized additive model of Connecticut hospitalizations}
 
 \author{
-	\authorstyle{Ben Artin\textsuperscript{1}} % Authors
+    \authorstyle{Ben Artin\textsuperscript{1}}
     \newline\newline
@@
 
-\date{Draft \#1, \today}
+\date{\today}
 
 \begin{document}
+
+\begingroup
+\setlength\parindent{0em}
 
@@
 \clearpage
+\endgroup
 
@@
 
-\abstractsection{Background}
-
-Respiratory syncytial virus (RSV) causes seasonal respiratory infection with potentially serious complications in young infants.
+\abstractsection{Background} Respiratory syncytial virus (RSV) causes seasonal respiratory infection with potentially serious complications in young infants.
 Immunoprophylaxis (palivizumab) is available, but costly.
@@
 
-\abstractsection{Methods}
-
-We describe a generalized additive model of RSV incidence using cubic cyclic penalized splines and apply that model to hospital admissions records from Connecticut between \Sexpr{formatDate(startDate)} and \Sexpr{formatDate(endDate)} to estimate fraction of RSV cases in Connecticut preventable by immunoprophylaxis administered according to the AAP guidelines.
+\abstractsection{Methods} We describe a generalized additive model of RSV incidence using cubic cyclic penalized splines and apply that model to hospital admissions records from Connecticut between \Sexpr{formatDate(startDate)} and \Sexpr{formatDate(endDate)} to estimate fraction of RSV cases in Connecticut preventable by immunoprophylaxis administered according to the AAP guidelines.
 We also formulate several alternate immunoprophylaxis regimens with the same net pharmaceutical cost, estimate the fraction preventable by those alternate regimens.
 
-\abstractsection{Results}
-
-At 95\% confidence level, we found alternate regimens that account for spatial variability of RSV incidence at the county level to have superior coverage (to that of the AAP-recommended regimen) in some regions of Connecticut, and non-inferior coverage in other regions.
+\abstractsection{Results} At 95\% confidence level, we found alternate regimens that account for spatial variability of RSV incidence at the county level to have superior coverage (to that of the AAP-recommended regimen) in some regions of Connecticut, and non-inferior coverage in other regions.
 We also found alternate regimens that account for temporal RSV variability at the annual level to have non-superior coverage to our spatially-adjusted regimens.
@@
 
-\abstractsection{Conclusion}
-
-We conclude that the increased prophylaxis coverage provided by regimens based on our county-level spatial analysis warrants further analysis to determine whether the potential reduction in hospitalization rate is nullified by the potential increase in implementation cost.
+\abstractsection{Conclusion} We conclude that the increased prophylaxis coverage provided by regimens based on our county-level spatial analysis warrants further analysis to determine whether the potential reduction in hospitalization rate is nullified by the potential increase in implementation cost.
 Our temporal analysis at the annual level showed no additional benefit beyond the spatial analysis, while simultaneously increasing implementation complexity.
@@
 
+\thispagestyle{empty}
 \clearpage
 
-%\begin{multicols}{2}
+\begin{multicols}{2}
 
@@
 
-\section{Data normalization}
+\subsection{Data normalization}
 
@@
 
-\subsection{RSV season in Fairfield county begins early and ends late}
+\paragraph{RSV season in Fairfield county begins early and ends late}
 
@@
 
-\begin{figure*}[t]
-<<seasonByRegion>>=
-    onset = ggplot(thresholdsByCounty %>% filter(county %in% countiesForPlots)) +
-        geom_errorbarh(aes(x=onset.median, xmin=onset.lower, xmax=onset.upper, y=county), height=.25) + 
-        labs(x="Season onset") +
+% \uselengthunit{in}\printlength{\columnwidth}
+% column width = 3.20929 in
+
+\begin{figure}
+<<seasonByRegion, results='hide'>>=
+    data = thresholdsByCounty %>% 
+        filter(county %in% countiesForPlots) %>%
+        melt(id=c("county")) %>%
+        cSplit(c("variable"), c(".")) %>%
+        rename(variable=variable_1, pctile=variable_2) %>%
+        mutate(variable=factor(variable, levels=c("onset", "offset"))) %>%
+        cast(county + variable ~ pctile)
+
+    tikz("figure/seasonByRegion.tex", width=plotWidth, height=plotHeight, pointsize=10)
+    ggplot(data) +
+        theme_light(base_size=10) +
+        geom_errorbar(aes(ymin=lower, ymax=upper, x=county), width=.1) + 
+        geom_point(aes(y=median, x=county)) + 
+        labs(aes(x=variable)) +
+        facet_wrap(~variable, ncol=1, scales="free_y", labeller=onsetOffsetLabeller) +
+        labs(y="Surveillance week") + 
         theme(
-            axis.title.y=element_blank(),
-            axis.ticks.y=element_blank()
+            axis.title.x=element_blank(),
+            axis.ticks.x=element_blank(),
         )
-    offset = ggplot(thresholdsByCounty %>% filter(county %in% countiesForPlots)) +
-        geom_errorbarh(aes(x=offset.median, xmin=offset.lower, xmax=offset.upper, y=county), height=.25) + 
-        labs(x="Season offset", y=NULL) +
-        theme(
-            axis.title.y=element_blank(),
-            axis.text.y=element_blank(),
-            axis.ticks.y=element_blank()
-        )
-
-    ggplot2.multiplot(plotlist=list(onset, offset), cols=2)
+    dev.off()
 @
+\begin{center}
+\input{figure/seasonByRegion.tex}
 \caption{Onset and offset of RSV season in Connecticut by region}
 \label{fig:seasonByRegion}
-\end{figure*}
+\end{center}
+\end{figure}
 
-\begin{figure*}[t]
-<<coverageByRegionAAP>>=
+\paragraph{RSV season in low-incidence counties begins late}
+
+Meanwhile, in comparison with the statewide RSV season onset and offset, the low-incidence region has RSV season with later onset at \Sexpr{regionOnset("lowIncidence")} weeks (\Sexpr{regionOnsetCI("all", level)}); season offset shows no change from the statewide median.
+(Figure \ref{fig:seasonByRegion}.)
+
+\paragraph{AAP guidelines perform best in low-incidence counties and worst in Fairfield county}
+
+Statewide, our model shows that \Sexpr{regionStrategyCoverage("all", "aap")} of RSV cases (\Sexpr{regionStrategyCoverageCI("all", "aap", level)}) occur while palivizumab, administered according to AAP guidelines, offers protection.
+The AAP guidelines perform better in the low-incidence counties, where \Sexpr{regionStrategyCoverage("lowIncidence", "aap")} cases (\Sexpr{regionStrategyCoverageCI("lowIncidence", "aap", level)}) occur during the prophylaxis time window, but worse in Fairfield county, where \Sexpr{regionStrategyCoverage("Fairfield", "aap")} cases ((\Sexpr{regionStrategyCoverageCI("Fairfield", "aap", level)})) occur during this time.
+(Table \ref{table:coverageByRegionAAP}.)
+
+\begin{figure}
+<<coverageByRegionAAP, results='hide'>>=
+    tikz("figure/coverageByRegionAAP.tex", width=plotWidth, height=plotHeight, pointsize=10)
     ggplot(unprotectedByCounty %>% filter(strat=="aap") %>% filter(county %in% countiesForPlots)) +
-        geom_errorbar(aes(ymax=frac.upper, ymin=frac.lower, x=county), width=.25) + 
+        theme_light(base_size=10) +
+        geom_errorbar(aes(ymax=frac.upper, ymin=frac.lower, x=county), width=.1) + 
         geom_point(aes(y=frac.median, x=county)) + 
-        scale_y_continuous(labels=scales::percent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
-        labs(y="RSV cases occurring during prophylaxis timeframe, %") +
+        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
+        labs(y="Preventable fraction") +
         theme(
@@
         )
+    dev.off()
 @
+\input{figure/coverageByRegionAAP.tex}
 \caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis administered according to AAP guidelines, by region.}
 \label{fig:coverageByRegionAAP}
-\end{figure*}
+\end{figure}
 
-\begin{figure*}[t]
-<<coverageByRegionAAPInsight>>=
+The cause of this is evident in Figure \ref{fig:coverageByRegionAAPInsight}; temporal misalignment between the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each region), and the time window of AAP prophylaxis regimen.
+Fairfield county, owing to its early season onset, has disproportionately many cases before prophylaxis administration begins; on the other hand, the low-incidence counties, owing to their late season onset, have their RSV seasons almost entirely contained within the prophylaxis window.
+
+\begin{figure}
+<<coverageByRegionAAPInsight, results='hide'>>=
+    tikz("figure/coverageByRegionAAPInsight.tex", width=plotWidth, height=plotHeight*3/2, pointsize=10)
     ggplot2.multiplot(plotlist=lapply(countiesForPlots, function(c) {
@@
             annotate("segment", x=-Inf, y=unprotectedAtEnd, xend=ppxEnd, yend=unprotectedAtEnd, linetype=3) + 
-            scale_y_continuous(labels=scales::percent, breaks=seq(0, 1, by=.2), limits=c(0, 1), expand=c(0.2, 0)) +
+            scale_y_continuous(labels=latexPercent, breaks=seq(0, 1, by=.2), limits=c(0, 1), expand=c(0.2, 0)) +
             labs(x=c) +
@@
     }), cols=2)
+    dev.off()
 @
+\input{figure/coverageByRegionAAPInsight.tex}
 \caption{RSV relative cumulative incidence by region}
 \label{fig:coverageByRegionAAPInsight}
-\end{figure*}
+\end{figure}
 
-\begin{figure*}[t]
-<<coverageByRegion, warning=FALSE>>=
-    data = unprotectedByCounty %>% 
-        filter(county %in% countiesForPlots)
-    ggplot(data) +
-        scale_y_continuous(labels=scales::percent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
-        scale_linetype_manual(values=c(1, 3, 4, 2, 3, 4, 2)) + 
-        scale_color_manual(values=c(grey(0), rep(hsv(0, 1, 1), 3), rep(hsv(4/6, 1, 1), 3))) + 
-        geom_errorbar(
-            aes(ymin=frac.lower, ymax=frac.upper, x=county, linetype=strat, color=strat, group=strat), 
-            width=0, 
-            position=position_dodge(.5)
-        ) + 
-        geom_point(aes(y=frac.median, x=county, color=strat), position=position_dodge(.5)) +
-        geom_point(aes(y=frac.lower, x=county, color=strat), position=position_dodge(.5), shape=18) +
-        geom_point(aes(y=frac.upper, x=county, color=strat), position=position_dodge(.5), shape=18) +
-        labs(y="RSV cases occurring during prophylaxis timeframe, %") +
-        guides(color=guide_legend(keywidth=3, keyheight=1), linetype=guide_legend(keywidth=3, keyheight=1)) + 
-        theme(
-            axis.title.x=element_blank(),
-            axis.ticks.x=element_blank()
-        )
-@
-
-\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by region and prophylaxis regimen.}
-\label{fig:coverageByRegion}
-\end{figure*}
-
-\begin{figure*}[t]
-<<onsetOffsetByYear, warning=FALSE>>=
-    onset = ggplot(stateThresholdsByWindow) +
-        geom_errorbar(aes(ymin=onset.lower, ymax=onset.upper, x=year), width=.25) + 
-        geom_point(aes(y=onset.median, x=year)) + 
-        labs(x="RSV Season Onset")
-    offset = ggplot(stateThresholdsByWindow) +
-        geom_errorbar(aes(ymin=offset.lower, ymax=offset.upper, x=year), width=.25) + 
-        geom_point(aes(y=offset.median, x=year)) + 
-        labs(x="RSV Season Offset")
-
-    ggplot2.multiplot(plotlist=list(onset, offset), cols=2)
-@
-
-\caption{RSV season onset and offset by three-year superseason.}
-\label{fig:onsetOffsetByYear}
-\end{figure*}
-
-\subsection{RSV season in low-incidence counties begins late}
-
-Meanwhile, in comparison with the statewide RSV season onset and offset, the low-incidence region has RSV season with later onset at \Sexpr{regionOnset("lowIncidence")} weeks (\Sexpr{regionOnsetCI("all", level)}); season offset shows no change from the statewide median.
-(Figure \ref{fig:seasonByRegion}.)
-
-\subsection{AAP guidelines perform best in low-incidence counties and worst in Fairfield county}
-
-Statewide, our model shows that \Sexpr{regionStrategyCoverage("all", "aap")} of RSV cases (\Sexpr{regionStrategyCoverageCI("all", "aap", level)}) occur while palivizumab, administered according to AAP guidelines, offers protection.
-The AAP guidelines perform better in the low-incidence counties, where \Sexpr{regionStrategyCoverage("lowIncidence", "aap")} cases (\Sexpr{regionStrategyCoverageCI("lowIncidence", "aap", level)}) occur during the prophylaxis time window, but worse in Fairfield county, where \Sexpr{regionStrategyCoverage("Fairfield", "aap")} cases ((\Sexpr{regionStrategyCoverageCI("Fairfield", "aap", level)})) occur during this time.
-(Table \ref{table:coverageByRegionAAP}.)
-
-The cause of this is evident in Figure \ref{fig:coverageByRegionAAPInsight}, which shows temporal misalignment between the time window of the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each region), and the time window of AAP prophylaxis guidelines.
-Fairfield county, owing to its early season onset, has disproportionately many cases before prophylaxis administration begins; on the other hand, the low-incidence counties, owing to their late season onset, have their RSV seasons almost entirely contained within the prophylaxis window.
-
-\subsection{Spatially-informed regimens are superior to AAP recommendations overall and in Hartford county}
+\paragraph{Spatially-informed regimens are superior to AAP recommendations overall and in Hartford county}
 
@@
 
-\subsection{RSV season onset and offset is unchanged over time}
+\begin{figure}
+<<coverageByRegion, results='hide', warning=FALSE>>=
+    data = unprotectedByCounty %>% 
+        filter(county %in% countiesForPlots)
+    tikz("figure/coverageByRegionRegimen.tex", width=plotWidth, height=plotHeight, pointsize=10)
+    ggplot(data) +
+        theme_light(base_size=10) +
+        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
+        scale_linetype_manual(values=c(1, 3, 4, 2, 3, 4, 2)) + 
+        scale_color_manual(values=c(grey(0), rep(hsv(0, 1, 1), 3), rep(hsv(4/6, 1, 1), 3))) + 
+        geom_errorbar(
+            aes(ymin=frac.lower, ymax=frac.upper, x=county, linetype=strat, color=strat, group=strat), 
+            width=0, 
+            position=position_dodge(.5)
+        ) + 
+        geom_point(aes(y=frac.median, x=county, color=strat), position=position_dodge(.5)) +
+        geom_point(aes(y=frac.lower, x=county, color=strat), position=position_dodge(.5), shape=18) +
+        geom_point(aes(y=frac.upper, x=county, color=strat), position=position_dodge(.5), shape=18) +
+        labs(y="Preventable fraction") +
+        guides(color=guide_legend(keywidth=3, keyheight=1), linetype=guide_legend(keywidth=3, keyheight=1)) + 
+        theme(
+            axis.title.x=element_blank(),
+            axis.ticks.x=element_blank(),
+            legend.position="bottom"
+        )
+    dev.off()
+@
+\input{figure/coverageByRegionRegimen.tex}
+\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by region and prophylaxis regimen.}
+\label{fig:coverageByRegionRegimen}
+\end{figure}
+
+\paragraph{RSV season onset and offset are unchanged over time}
 
@@
 
-\subsection{Recent-years prophylaxis regimens are non-superior to others.}
+\begin{figure}
+<<onsetOffsetByYear, results='hide', warning=FALSE>>=
+    data = stateThresholdsByWindow %>% 
+        melt(id=c("year")) %>%
+        cSplit(c("variable"), c(".")) %>%
+        rename(variable=variable_1, pctile=variable_2) %>%
+        mutate(variable=factor(variable, levels=c("onset", "offset"))) %>%
+        cast(year + variable ~ pctile)
+
+    tikz("figure/onsetOffsetByYear.tex", width=plotWidth, height=plotHeight, pointsize=10)
+    ggplot(data) +
+        theme_light(base_size=10) +
+        geom_errorbar(aes(ymin=lower, ymax=upper, x=year), width=.1) + 
+        geom_point(aes(y=median, x=year)) +
+        facet_wrap(~variable, ncol=1, scales="free_y", labeller=onsetOffsetLebeller) +
+        scale_x_continuous(breaks=seq(1990, 2020, by=5)) +
+        labs(y="Surveillance week") + 
+        theme(
+            axis.title.x=element_blank()
+        )
+
+    dev.off()
+@
+\input{figure/onsetOffsetByYear.tex}
+\caption{RSV season onset and offset by three-year superseason.}
+\label{fig:onsetOffsetByYear}
+\end{figure}
+
+\paragraph{Recent-years prophylaxis regimens are non-superior to others.}
 
@@
 
-Our model shows that coverage of RSV immunoprophylaxis in high-risk infants in Connecticut can be improved from that provided by the prophylaxis regimen currently recommended by the AAP.
+Our model shows that fraction of RSV preventable by immunoprophylaxis in high-risk infants in Connecticut can be increased from that of the prophylaxis regimen currently recommended by the AAP.
 
@@
 
-%\end{multicols}
+\end{multicols}
 

### 2018-01-14 Analysis/RSV.R

@@ -7,6 +7,7 @@ library(zipcode)
 library(ggplot2)
 library(easyGgplot2)
 library(data.table)
+library(splitstackshape)
 
 data(zipcode)
 set.seed(0)

### 2018-01-14 Thesis/Thesis.R

@@ -1,0 +1,98 @@
+# ---- util ----
+library(grid)
+library(tikzDevice)
+options(tikzDefaultEngine='pdftex')
+
+plotWidth=3.1
+plotHeight=2.5
+
+# Formatting utilities
+formatDate = function(date) {
+  format(date, "%B, %d, %Y")
+}
+
+formatYear = function(date) {
+  format(date, "%Y")
+}
+
+formatThreshold = function(threshold) {
+  sprintf("%.2f", threshold %% 52)
+}
+
+regionOnset = function(c) {
+  formatThreshold((thresholdsByCounty %>% filter(county==c))$onset.median)
+}
+
+regionOffset = function(c) {
+  formatThreshold((thresholdsByCounty %>% filter(county==c))$offset.median)
+}
+
+formatThresholdCI = function(lower, upper, level) {
+  sprintf("%d\\%% CI: %.2f -- %.2f", level * 100, lower %% 52, upper %% 52)
+}
+
+regionOnsetCI = function(c, level) {
+  formatThresholdCI(
+    (thresholdsByCounty %>% filter(county==c))$onset.lower,
+    (thresholdsByCounty %>% filter(county==c))$onset.upper,
+    level
+  )
+}
+
+regionOffsetCI = function(c, level) {
+  formatThresholdCI(
+    (thresholdsByCounty %>% filter(county==c))$offset.lower,
+    (thresholdsByCounty %>% filter(county==c))$offset.upper,
+    level
+  )
+}
+
+formatPct = function(pct) {
+  sprintf("%.2f\\%%", pct * 100)
+}
+
+formatPctCI = function(lower, upper, level) {
+  sprintf("%d\\%% CI: %.2f -- %.2f\\%%", level * 100, lower * 100, upper * 100)
+}
+
+regionStrategyCoverage = function(c, s) {
+  formatPct((unprotectedByCounty %>% filter(county==c, strat==s))$frac.median)
+}
+
+regionStrategyCoverageCI = function(c, s, level) {
+  formatPctCI(
+    (unprotectedByCounty %>% filter(county==c, strat==s))$frac.upper,
+    (unprotectedByCounty %>% filter(county==c, strat==s))$frac.lower,
+    level
+  )
+}
+
+driftYearToWeek = function(year, negate) {
+  drift = 365 / 7 * year
+  if (negate) {
+    -drift
+  } else {
+    drift
+  }
+}
+
[…]

### 2018-01-14 Thesis/structure.tex
Title improvements

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wenneker Article
% Structure Specification File
% Version 1.0 (28/2/17)
%
% This file originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Frits Wenneker
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\usepackage[english]{babel} % English language hyphenation

\usepackage{microtype} % Better typography

\usepackage{amsmath,amsfonts,amsthm} % Math packages for equations

\usepackage[svgnames]{xcolor} % Enabling colors by their 'svgnames'

\usepackage[hang, small, labelfont=bf, up, textfont=it]{caption} % Custom captions under/above tables and figures

\usepackage{booktabs} % Horizontal rules in tables

\usepackage{lastpage} % Used to determine the number of pages in the document (for "Page X of Total")

\usepackage{graphicx} % Required for adding images

\usepackage{enumitem} % Required for customising lists
\setlist{noitemsep} % Remove spacing between bullet/numbered list elements

\usepackage{sectsty} % Enables custom section titles
\allsectionsfont{\usefont{OT1}{phv}{b}{n}} % Change the font of all section commands (Helvetica)

%----------------------------------------------------------------------------------------
%	MARGINS AND SPACING
%----------------------------------------------------------------------------------------

\usepackage{geometry} % Required for adjusting page dimensions

\geometry{
	top=1cm, % Top margin
	bottom=1.5cm, % Bottom margin
	left=2cm, % Left margin
	right=2cm, % Right margin
	includehead, % Include space for a header
	includefoot, % Include space for a footer
	%showframe, % Uncomment to show how the type block is set on the page
}

\setlength{\columnsep}{7mm} % Column separation width

%----------------------------------------------------------------------------------------
%	FONTS
%----------------------------------------------------------------------------------------

\usepackage[T1]{fontenc} % Output font encoding for international characters
\usepackage[utf8]{inputenc} % Required for inputting international characters

\usepackage{XCharter} % Use the XCharter font

%----------------------------------------------------------------------------------------
%	HEADERS AND FOOTERS
%----------------------------------------------------------------------------------------

\usepackage{fancyhdr} % Needed to define custom headers/footers
\pagestyle{fancy} % Enables the custom headers/footers

\renewcommand{\headrulewidth}{0.0pt} % No header rule
\renewcommand{\footrulewidth}{0.4pt} % Thin footer rule

\renewcommand{\sectionmark}[1]{\markboth{#1}{}} % Removes the section number from the header when \leftmark is used

%\nouppercase\leftmark % Add this to one of the lines below if you want a section title in the header/footer

% Headers
\lhead{} % Left header
\chead{\textit{\headertitle}} % Center header - currently printing the article title
\rhead{} % Right header

% Footers
\lfoot{} % Left footer
\cfoot{} % Center footer
\rfoot{\footnotesize Page \thepage\ of \pageref{LastPage}} % Right footer, "Page 1 of 2"

\fancypagestyle{firstpage}{ % Page style for the first page with the title
	\fancyhf{}
	\renewcommand{\footrulewidth}{0pt} % Suppress footer rule
}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\newcommand{\authorstyle}[1]{{\large\usefont{OT1}{phv}{b}{n}\color{DarkRed}#1}} % Authors style (Helvetica)

\newcommand{\institution}[1]{{\footnotesize\usefont{OT1}{phv}{m}{sl}\color{Black}#1}} % Institutions style (Helvetica)

\usepackage{titling} % Allows custom title configuration

\newcommand{\HorRule}{\color{DarkGoldenrod}\rule{\linewidth}{1pt}} % Defines the gold horizontal rule around the title

\pretitle{
	\vspace{-30pt} % Move the entire title section up
	\HorRule\vspace{10pt} % Horizontal rule before the title
	\fontsize{32}{36}\usefont{OT1}{phv}{b}{n}\selectfont % Helvetica
	\color{DarkRed} % Text colour for the title and author(s)
	\raggedright
}

\posttitle{\par\vskip 15pt} % Whitespace under the title

\preauthor{} % Anything that will appear before \author is printed

\postauthor{ % Anything that will appear after \author is printed
	\vspace{10pt} % Space before the rule
	\par\HorRule % Horizontal rule after the title
	\vspace{20pt} % Space after the title section
}

%----------------------------------------------------------------------------------------
%	ABSTRACT
%----------------------------------------------------------------------------------------

\usepackage{lettrine} % Package to accentuate the first letter of the text (lettrine)
\usepackage{fix-cm}	% Fixes the height of the lettrine

\newcommand{\initial}[1]{ % Defines the command and style for the lettrine
	\lettrine[lines=3,findent=4pt,nindent=0pt]{% Lettrine takes up 3 lines, the text to the right of it is indented 4pt and further indenting of lines 2+ is stopped
		\color{DarkGoldenrod}% Lettrine colour
		{#1}% The letter
	}{}%
}

\usepackage{xstring} % Required for string manipulation

\newcommand{\lettrineabstract}[1]{
	\StrLeft{#1}{1}[\firstletter] % Capture the first letter of the abstract for the lettrine
	\initial{\firstletter}\textbf{\StrGobbleLeft{#1}{1}} % Print the abstract with the first letter as a lettrine and the rest in bold
}

%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY
%----------------------------------------------------------------------------------------

\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)

\addbibresource{example.bib} % The filename of the bibliography

\usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography

### 2018-01-14 Analysis/RSV.R
Separate library loading to enable caching

@@ -1,14 +1,4 @@
 # ---- external ----
-library(reshape)
-library(dplyr)
-library(mgcv)
-library(outbreakpredict)
-library(zipcode)
-library(ggplot2)
-library(easyGgplot2)
-library(data.table)
-library(splitstackshape)
-
 data(zipcode)
 set.seed(0)
 

### 2018-01-14 Thesis/Thesis.rnw
More plot refactoring, added bibliography

@@
 <<load>>=
+library(reshape)
+library(dplyr)
+library(mgcv)
+library(outbreakpredict)
+library(zipcode)
+library(ggplot2)
+library(easyGgplot2)
+library(data.table)
+library(splitstackshape)
+
 read_chunk("../Analysis/RSV.R")
@@
 
-<<external>>=
+<<external, cache=TRUE>>=
 @
@@
 
+\tableofcontents
+\clearpage
+
+\listoftables
+\clearpage
+
+\listoffigures
+\clearpage
+
 \begin{multicols}{2}
@@
 
-In children, however, the infection often incites more serious respiratory illness, sometimes leading to hospitalization.
+In children, however, the infection often incites more serious respiratory illness, making RSV a leading cause of hospitalization among infants.\cite{Hall:2009gi,Hall:2013jo,Zhou:2012ho,Boyce:2000gz}
 
@@
 Immunoprophylaxis with palivizumab, a monoclonal antibody medication, has been approved for prevention of RSV infection since 1998.
-Palivizumab is administered via intramuscular injection, and requires monthly dosing.
-Its price is \$1500-\$3000 per dose.
+Palivizumab is administered via intramuscular injection, and requires monthly dosing.\cite{Andabaka:2013dr} Its price is \$1500-\$3000 per dose.\cite{Hampp:2011ju}
 
-Palivizumab has been found to be effective in reducing hospitalizations due to RSV; in double-blinded trials in high-risk infants, it reduced hospitalization rate by 45-55\% compared to placebo.
+Palivizumab has been found to be effective in reducing hospitalizations due to RSV; in double-blinded trials in high-risk infants, it reduced hospitalization rate by 45-55\% compared to placebo.\cite{Group:1998ih,Feltes:2003wm}
 
-Owing to the high cost, the American Academy of Pediatrics (AAP) recommends palivizumab immunoprophylaxis only for high-risk infants, and only during RSV season.
-These guidelines were most recently revised in 2014.
+Owing to the high cost, the American Academy of Pediatrics (AAP) recommends palivizumab immunoprophylaxis only for high-risk infants, and only during RSV season.\cite{Anonymous:1998up,AmericanAcademyofPediatricsCommitteeonInfectiousDiseasesandCommitteeonFetusandNewborn:2003ug,AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj} These guidelines were most recently revised in 2014.
 
-In their guidelines, the AAP acknowledges the potential significance of spatial and temporal variation in RSV incidence, but does not recommend local variance from nation-wide prophylaxis guidelines outside of Florida.
+In their guidelines, the AAP acknowledges the potential significance of spatial and temporal variation in RSV incidence, but does not recommend local variance from nation-wide prophylaxis guidelines outside of Florida.\cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
 
@@
 The Department of Public Health of the state of Connecticut, via its Office of Health Care Access (OHCA), maintains a database of all hospitalizations in every non-federal short-stay acute-care general hospital in the state.
-This database has previously been used to show regional variability in time of peak RSV incidence within Connecticut.
+Previous analysis of this database has shown regional variability in time of peak RSV incidence within Connecticut.\cite{Noveroske:y4fi3188}
 
@@
     ggplot(data) +
-        theme_light(base_size=10) +
+        theme_light(base_size=plotTextBaseSize) +
         geom_errorbar(aes(ymin=lower, ymax=upper, x=county), width=.1) + 
@@
     ggplot(unprotectedByCounty %>% filter(strat=="aap") %>% filter(county %in% countiesForPlots)) +
-        theme_light(base_size=10) +
+        theme_light(base_size=plotTextBaseSize) +
         geom_errorbar(aes(ymax=frac.upper, ymin=frac.lower, x=county), width=.1) + 
@@
     ggplot(data) +
-        theme_light(base_size=10) +
+        theme_light(base_size=plotTextBaseSize) +
         scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
@@
     ggplot(data) +
-        theme_light(base_size=10) +
+        theme_light(base_size=plotTextBaseSize) +
         geom_errorbar(aes(ymin=lower, ymax=upper, x=year), width=.1) + 
         geom_point(aes(y=median, x=year)) +
-        facet_wrap(~variable, ncol=1, scales="free_y", labeller=onsetOffsetLebeller) +
+        facet_wrap(~variable, ncol=1, scales="free_y", labeller=onsetOffsetLabeller) +
         scale_x_continuous(breaks=seq(1990, 2020, by=5)) +
@@
 \input{figure/onsetOffsetByYear.tex}
-\caption{RSV season onset and offset by three-year superseason.}
+\caption{RSV season onset and offset by three-year surseason.}
 \label{fig:onsetOffsetByYear}
@@
 
+\printbibliography[title={Bibliography}] % Print the bibliography, section title in curly brackets
+
 \end{document}

### 2018-01-14 Thesis/structure.tex
More plot refactoring, added bibliography

@@
 
-\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
+\usepackage[backend=bibtex,style=numeric,sorting=none,autocite=superscript]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
+%\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
 
-\addbibresource{example.bib} % The filename of the bibliography
+\addbibresource{Thesis.bib} % The filename of the bibliography
+\renewcommand{\cite}[1]{\autocite{#1}}
 

### 2018-01-14 Thesis/Thesis.R

@@ -5,6 +5,7 @@ options(tikzDefaultEngine='pdftex')
 
 plotWidth=3.1
 plotHeight=2.5
+plotTextBaseSize=8
 
 # Formatting utilities
 formatDate = function(date) {
@@ -92,6 +93,10 @@ formatDriftCI = function(lm, level, negate=TRUE) {
 latexPercent = function(f) {
   sprintf("%.0f\\%%", f * 100)
 }
+
+onsetOffsetLabeller = labeller(
+  variable=c(`onset` = "RSV season onset", `offset` = "RSV season offset")
+)
 
 # Counties which we plot (so, not individual low-incidence counties)
 countiesForPlots = thresholdsByCounty$county[!thresholdsByCounty$county %in% lowIncidenceCounties]

### 2018-01-15 Analysis/RSV.Rmd
Changed calendar to use epi year; added sliding window analysis

--- 2018-01-12 Analysis/RSV.Rmd
@@
 install_github("airbornemint/outbreak-predict")
-
+```
+```{r}
 source("./RSV.R")
@@
 
-```{r warning=FALSE}
-obsByCountyYear = dataset %>% 
-  rename(time=weekofyear) %>% 
-  group_by(county, weeki, year, time) %>% 
-  summarize(rsv=sum(rsv)) %>% 
-  left_join(rsvCountyGroups, by="county") %>%
-  group_by(weeki, year, time) %>%
-  do(summarizeCountyGroups(.)) %>%
-  group_by(county, year) %>%
-  mutate(rsv.cum=cumsum(rsv), rsv.cum.frac=rsv.cum / if_else(sum(rsv) > 0, sum(rsv), as.integer(1))) %>% 
-  select(-weeki) %>%
-  as.data.frame()
-
-predByCountyYear = data.frame()
-thresholdsByCountyYear = data.frame()
-slidingStratUnprotectedSimByCountyYear = data.frame()
-
-progress = txtProgressBar(max=length(levels(obsByCounty$county)) * length(rsvYears) * 2, style=3)
-idx = 0
-
-for (c in levels(obsByCountyYear$county)) {
-  for (y in rsvYears) {
-    countyYearObs = obsByCountyYear %>% filter(county==c, year==y)
-    countyYearModel = gam(rsv ~ s(time, k=5, bs="cp", m=3), family=poisson, data=countyYearObs)
-
-    countyYearPred = countyYearModel %>% 
-      predict(type="response", newdata=data.frame(time=modelTime), se.fit=TRUE)
-
-    countyYearPred = data.frame(time=modelTime) %>% 
-      cbind(data.frame(rsv.fit=countyYearPred$fit, rsv.fit.se=countyYearPred$se.fit)) %>%
-      cbind(countyYearModel %>% outbreak.predict.timeseries(modelTime, outbreak.calc.cum())) %>%
-      rename(rsv.cum.fit.lower=lower, rsv.cum.fit.upper=upper, rsv.cum.fit=median) %>%
-      mutate(county=factor(c, levels=levels(obsByCountyYear$county)), year=y)
-
-    predByCountyYear = predByCountyYear %>% rbind(countyYearPred)
-
-    countyYearThresholds = countyYearModel %>%
-      outbreak.predict.scalars(
-        modelTime,
-        outbreak.calc.thresholds(onset=seasonThreshold, offset=1 - seasonThreshold)
-      ) %>%
-      mutate(county=factor(c, levels=levels(obsByCountyYear$county)), year=y)
-
-    thresholdsByCountyYear = thresholdsByCountyYear %>% rbind(countyYearThresholds)
-
-    if (y %in% rsvWindowYears) {
-      countyYearUnprotectedSim = countyYearModel %>%
-        outbreak.predict.scalars.sim(
-          modelTime,
-          outbreak.calc.unprotected(ppxSlidingStrategies(c, y))
-        ) %>%
-        mutate(county=factor(c, levels=levels(obsByCountyYear$county)), year=y)
-
-      slidingStratUnprotectedSimByCountyYear = slidingStratUnprotectedSimByCountyYear %>% rbind(countyYearUnprotectedSim)
-    }
-
-    idx = idx + 1
-    setTxtProgressBar(progress, idx)
-  }
-}
-
-# Aggregate sliding strategies over the entire time span
-
-unprotectedByCounty = slidingStratUnprotectedSimByCountyYear %>% 
-  group_by(county, outbreak.sim) %>%
-  summarize_at(vars(contains("total"), contains("count")), sum) %>%
-  group_by(county, outbreak.sim) %>%
-  do((function(df) {
-    stratNames = names(ppxSlidingStrategies())
-    for (stratName in stratNames) {
-      countName = sprintf("%s.count", stratName)
-      fracName = sprintf("%s.frac", stratName)
-      df = df %>% 
-        mutate_at(fracName, function(.) { df[[countName]] / df$total })
-    }
-    df
-  }) (.)) %>%
-  group_by(county) %>%
-  do((function(df) {
-    df %>%
-      select(-county, -total, -matches(".count")) %>%
-      outbreak.predict.scalars.confints () %>%
-      mutate(county=unique(df$county))
-  })(.)) %>%
-  inner_join(fixedStratUnprotectedByCounty, by="county")
-```
-
 ```{r}
@@
 ```
+
+```
+
+```

### 2018-01-15 Analysis/RSV.R

@@ -1,3 +1,14 @@
+# ---- libraries ----
+library(reshape)
+library(dplyr)
+library(mgcv)
+library(outbreakpredict)
+library(zipcode)
+library(ggplot2)
+library(easyGgplot2)
+library(data.table)
+library(splitstackshape)
+
 # ---- external ----
 data(zipcode)
 set.seed(0)
@@ -5,11 +16,6 @@ set.seed(0)
 simulations = 20
 
 # *** Data munging helpers
-
-# RSV week-of-year is -26..25, with week 0 being first week of the year
-rsvWeek = function(weeki) {
-  (weeki + 26) %% 52 - 26
-}
 
 # Augment a (county, time, rsv) data frame with rows for regions consisting of >1 county
 summarizeCountyGroups = function(data) {
@@ -33,22 +39,35 @@ level = .95
 seasonThreshold = 0.025
 ppxDuration = 24 # weeks
 slidingWindowDuration = 3 # Years
+ppxRounding = c(0, 1, 2, 4)
 
 # *** Load / munge data
 
 # Load data
-dataset = fread("../ct rsv time series.csv", sep=",", header=TRUE, colClasses=c("patzip"="character"))
+admissions = fread("../ct rsv time series.csv", sep=",", header=TRUE, colClasses=c("patzip"="character"))
+
+epiyear = function(date) {
+  ifelse(month(date) > 6, year(date) + 1, year(date))
+}
+
+epiyday = function(date) {
+  as.numeric(date - as.Date(ISOdate(epiyear(date) - 1, 6, 30)))
+}
+
+epiweek = function(date) {
+  floor((epiyday(date) - 1) / 7) + 1
+}
 
 # Add week-of-year, with zero = first week of January, drop first 5.5 years because of coding differences
-dataset = dataset %>%
+dataset = admissions %>%
   mutate(
-    weekiadj=round(dataset$weeki * 364 / 365.25),
-    weekofyear=rsvWeek(weekiadj),
-    year=1990 + (weekiadj + 26) %/% 52,
-    adate=as.Date(adate, "%d%b%Y")
+    adate=as.Date(adate, "%d%b%Y"),
+    epiyear=epiyear(adate),
+    epiyday=epiyday(adate),
+    epiweek=epiweek(adate)
   ) %>%
-  filter(weeki > 5.5*52) %>%
-  filter(weeki <= 22.5*52)
+  filter(epiyear >= 1996, epiyear <= 2013) %>%
[…]

### 2018-01-15 Thesis/structure.tex
Use NEJM reference style

@@
 
-\usepackage[backend=bibtex,style=numeric,sorting=none,autocite=superscript]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
+\usepackage[backend=bibtex,style=nejm,sorting=none,autocite=superscript,articledoi=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
 %\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
+\usepackage[nottoc]{tocbibind}
 
-\addbibresource{Thesis.bib} % The filename of the bibliography
+\addbibresource{../Thesis.bib} % The filename of the bibliography
 \renewcommand{\cite}[1]{\autocite{#1}}

### 2018-01-15 Thesis/Thesis.rnw
Added calendrical rounding analysis and rewrote conclusions

@@
-% Agenda
-%  * Round time periods pre-coverage analysis in order to make conclusion make sense
-% 
-% Todo
-%  * Change how mod 52-1/7 is done
-%  * "Coverage" -> preventable fraction
-%  * "Statewide"
+% TODO: DOI in bib?
+% TODO: Prettier abstract sectioning
+% TODO: Better calendrical cues in plots
 
 <<options, echo=FALSE>>=
-    opts_chunk$set(echo=FALSE, message=FALSE, root.dir=".texpadtmp")
+    opts_chunk$set(echo=FALSE, message=FALSE)
 @
@@
 <<load>>=
-library(reshape)
-library(dplyr)
-library(mgcv)
-library(outbreakpredict)
-library(zipcode)
-library(ggplot2)
-library(easyGgplot2)
-library(data.table)
-library(splitstackshape)
-
 read_chunk("../Analysis/RSV.R")
 read_chunk("../Thesis/Thesis.R")
+@
+
+<<libraries, cache=FALSE>>=
 @
@@
 \input{structure.tex}
+\edef\figuresDir{\Sexpr{figuresDir}}
 
@@
 \newcommand{\abstractsection}[1]{\makebox[1in][l]{\textbf{#1}}}
+
+\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
 
@@
 We also found alternate regimens that account for temporal RSV variability at the annual level to have non-superior coverage to our spatially-adjusted regimens.
-Overall, we found our best-performing spatially-adjusted alternate to AAP guidelines to provide a XX\% state-wide increase in RSV prophylaxis coverage over the AAP regimen.
+Overall, we found our best-performing spatially-adjusted alternate to AAP guidelines to provide a XX\% statewide increase in RSV prophylaxis coverage over the AAP regimen.
 
@@
 
-\listoftables
-\clearpage
+%\listoftables
+%\clearpage
 
@@
 
-TODO
+RSV seasonality has been established throughout the United States, with a stable onset between mid-November and early January and a stable offset between mid-March and late April in all states except for Florida, based on National Respiratory and Enteric Virus Surveillance System data.\cite{CentersforDiseaseControlandPreventionCDC:2011wt,CentersforDiseaseControlandPreventionCDC:2013wv}
 
@@
 	\item To what extent does regional variability of RSV incidence in Connecticut impact the effectiveness of the AAP-recommended prophylaxis regimen?
-	\item Can we use spatial analysis of RSV to propose alternate regimens, either state-wide or regional, that would improve effectiveness over AAP-recommended prophylaxis, without increasing treatment cost?
+	\item Can we use spatial analysis of RSV to propose alternate regimens, either statewide or regional, that would improve effectiveness over AAP-recommended prophylaxis, without increasing treatment cost?
 	\item Is there year-to-year variation in timing of RSV season in Connecticut?
@@
 
-Due to changes in diagnostic coding, we excluded data prior to July 1996; surveillance year 2014 had incomplete data and was also excluded.
+Due to changes in diagnostic coding, we excluded data prior to July 1996; we similarly excluded data starting after June 2013, due to incompleteness.
 
@@
 For our spatial analysis, we aggregated RSV incidence data across all years in our data set. We then spatially aggregated the data to form five regions:
+
+% TODO: map
 
@@
 
-For the three alternate regimens based on state-wide data, we estimated preventable fraction statewide, as well as in each region.
+For the three alternate regimens based on statewide data, we estimated preventable fraction statewide, as well as in each region.
 
-For the three alternate regimens based on regional data, we estimated coverage in the corresponding region.
+For the three alternate regimens based on regional data, we estimated preventable fraction in the corresponding region.
 
-% TODO Consider also reporting net statewide coverage of regional regimens
+\subsection{Accommodating implementation complexity}
+
+Keeping in mind implementation constraints of clinical practice guidelines, we performed three additional variants of our spatial analysis:
+
+\begin{itemize}
+    \item \textbf{Weekly rounding}: prophylaxis start and end date rounded to the nearest calendar week,
+    \item \textbf{Biweekly rounding}: prophylaxis start and end date rounded to the nearest two-week calendar period, with two-week period boundary chosen , and % TODO: specifics
+    \item \textbf{Monthly rounding}: prophylaxis start and end date rounded to the nearest four-week calendar period.  % TODO: specifics and also not actually in code now
+\end{itemize}
+
+In each variant, we again estimated the preventable fraction of all six spatially-adjusted regimens.
 
@@
 
+\setcounter{figure}{1}
+\begin{figure*}
+<<coverageByRegionAAPInsight, results='hide'>>=
+    tikz(sprintf("%s/coverageByRegionAAPInsight.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight, pointsize=10)
+
+    strat = ppxFixedStrategies("all")[["aap"]]
+
+    data = predByCounty %>%
+	    filter(county %in% countiesForPlots)
+
+    thresholds = data %>%
+    	mutate(ppx=strat(time)) %>%
+    	filter(ppx > 0) %>%
+    	group_by(county) %>%
+    	do(
+    		data.frame(
+    			ppx.start=min(.$time),
+    			ppx.end=max(.$time),
+    			unprotected.start=min(.$rsv.cum.fit),
+    			unprotected.end=max(.$rsv.cum.fit)
+    		)
+    	) %>%
+    	ungroup() %>%
+    	as.data.frame() %>%
+    	inner_join(thresholdsByCounty, by="county")
+
+    barYmin = 0.025
+    barYmax = 0.075
+
+    spanExtents = data.frame(
+        variable=c("ppx", "season"), 
+        barYmin=c(1 + barYmin, -barYmax), 
+        barYmax=c(1 + barYmax, -barYmin), 
+        lineYmin=c(0, -barYmin), 
+        lineYmax=c(1 + barYmin, 1)
+    )
+
+    spans = thresholds %>%
+        select(county, matches("ppx."), matches(".median")) %>%
+        rename(season.start=onset.median, season.end=offset.median) %>%
+        melt(id.vars="county") %>%
+        cSplit("variable", ".") %>%
+        rename(variable=variable_1, part=variable_2) %>%
+        cast(county + variable ~ part) %>%
+        right_join(spanExtents, by="variable")
+
+    spanLabels = legendLabels(c("AAP-recommended prophylaxis", "RSV season"))
+
+    ggplot(data) +
+        theme_light(base_size=plotTextBaseSize) +
+        geom_ribbon(aes(ymin=rsv.cum.fit.lower, ymax=rsv.cum.fit.upper, x=time), fill=grey(.25)) +
+    	geom_segment(aes(x=start, y=lineYmin, xend=start, yend=lineYmax, color=variable), linetype="11", data=spans) + 
+    	geom_segment(aes(x=end, y=lineYmin, xend=end, yend=lineYmax, color=variable), linetype="11", data=spans) + 
+    	geom_rect(aes(xmin=start, ymin=barYmin, xmax=end, ymax=barYmax, fill=variable, color=variable), data=spans) + 
+    	geom_segment(aes(x=-Inf, y=unprotected.start, xend=ppx.start, yend=unprotected.start), linetype=3, data=thresholds) + 
+        geom_segment(aes(x=-Inf, y=unprotected.end, xend=ppx.end, yend=unprotected.end), linetype=3, data=thresholds) + 
+        scale_y_continuous(labels=latexPercent, breaks=seq(0, 1, by=.2), limits=c(-0.1, 1.1), expand=c(0, 0)) +
+        scale_color_manual(labels=spanLabels, values=twoTone) +
+        scale_fill_manual(labels=spanLabels, values=twoTone) +
+        guides(color=guide_legend(keywidth=3, keyheight=.4)) + 
+        facet_wrap(~county, ncol=5) +
+        labs(x="Surveillance week") + 
+        theme(
+            legend.title=element_blank(),
+            axis.title.y=element_blank(),
+            axis.ticks.x=element_blank(),
+            legend.position="bottom"
+        )
+
+    dev.off()
+@
+\input{\figuresDir/coverageByRegionAAPInsight.tex}
+\caption{Weekly RSV relative cumulative incidence in Connecticut, by region}
+\label{fig:coverageByRegionAAPInsight}
+\end{figure*}
+\setcounter{figure}{0}
+
 \paragraph{RSV season in Fairfield county begins early and ends late}
 
-Compared to the statewide median onset of RSV season at \Sexpr{regionOnset("all")} weeks (\Sexpr{regionOnsetCI("all", level)}) and offset at \Sexpr{regionOffset("all")} weeks (\Sexpr{regionOffsetCI("all", level)}), RSV season in Fairfield county has earlier median onset at \Sexpr{regionOnset("Fairfield")} weeks (\Sexpr{regionOnsetCI("Fairfield", level)}) and later median offset at \Sexpr{regionOffset("Fairfield")} weeks (\Sexpr{regionOffsetCI("Fairfield", level)}).
+Compared to the statewide median onset of RSV season at \Sexpr{regionOnset("all")} weeks (\Sexpr{regionOnsetCI("all", level)} weeks) and offset at \Sexpr{regionOffset("all")} weeks (\Sexpr{regionOffsetCI("all", level)} weeks), RSV season in Fairfield county has earlier median onset at \Sexpr{regionOnset("Fairfield")} weeks (\Sexpr{regionOnsetCI("Fairfield", level)} weeks) and later median offset at \Sexpr{regionOffset("Fairfield")} weeks (\Sexpr{regionOffsetCI("Fairfield", level)} weeks).
 (Figure \ref{fig:seasonByRegion}.)
@@
 
+\paragraph{RSV season in low-incidence counties begins late}
+
+Meanwhile, in comparison with the statewide RSV season onset and offset, the low-incidence region has RSV season with later onset at \Sexpr{regionOnset("lowIncidence")} weeks (\Sexpr{regionOnsetCI("all", level)} weeks); season offset shows no change from the statewide median.
+(Figure \ref{fig:seasonByRegion}.)
+
 \begin{figure}
 <<seasonByRegion, results='hide'>>=
+    tikz(sprintf("%s/seasonByRegion.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
     data = thresholdsByCounty %>% 
@@
         rename(variable=variable_1, pctile=variable_2) %>%
-        mutate(variable=factor(variable, levels=c("onset", "offset"))) %>%
+        mutate(variable=factor(variable, levels=c("offset", "onset"))) %>%
         cast(county + variable ~ pctile)
 
-    tikz("figure/seasonByRegion.tex", width=plotWidth, height=plotHeight, pointsize=10)
     ggplot(data) +
@@
 \begin{center}
-\input{figure/seasonByRegion.tex}
-\caption{Onset and offset of RSV season in Connecticut by region}
+\input{\figuresDir/seasonByRegion.tex}
+\caption{RSV season onset and offset in Connecticut, by region}
 \label{fig:seasonByRegion}
@@
 \end{figure}
-
-\paragraph{RSV season in low-incidence counties begins late}
-
-Meanwhile, in comparison with the statewide RSV season onset and offset, the low-incidence region has RSV season with later onset at \Sexpr{regionOnset("lowIncidence")} weeks (\Sexpr{regionOnsetCI("all", level)}); season offset shows no change from the statewide median.
-(Figure \ref{fig:seasonByRegion}.)
+\setcounter{figure}{2}
 
@@
 
-Statewide, our model shows that \Sexpr{regionStrategyCoverage("all", "aap")} of RSV cases (\Sexpr{regionStrategyCoverageCI("all", "aap", level)}) occur while palivizumab, administered according to AAP guidelines, offers protection.
-The AAP guidelines perform better in the low-incidence counties, where \Sexpr{regionStrategyCoverage("lowIncidence", "aap")} cases (\Sexpr{regionStrategyCoverageCI("lowIncidence", "aap", level)}) occur during the prophylaxis time window, but worse in Fairfield county, where \Sexpr{regionStrategyCoverage("Fairfield", "aap")} cases ((\Sexpr{regionStrategyCoverageCI("Fairfield", "aap", level)})) occur during this time.
-(Table \ref{table:coverageByRegionAAP}.)
+Statewide, our model shows that \Sexpr{regionStrategyCoverage("all", "aap", 0)} of RSV cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) occur while palivizumab, administered according to AAP guidelines, offers protection.
+
+The AAP guidelines perform better in the low-incidence counties, where \Sexpr{regionStrategyCoverage("lowIncidence", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("lowIncidence", "aap", 0, level)}) occur during the prophylaxis time window, but worse in Fairfield county, where \Sexpr{regionStrategyCoverage("Fairfield", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("Fairfield", "aap", 0, level)}) occur during this time.
+(Figure \ref{fig:coverageByRegionAAP}.)
 
@@
 <<coverageByRegionAAP, results='hide'>>=
-    tikz("figure/coverageByRegionAAP.tex", width=plotWidth, height=plotHeight, pointsize=10)
-    ggplot(unprotectedByCounty %>% filter(strat=="aap") %>% filter(county %in% countiesForPlots)) +
+    tikz(sprintf("%s/coverageByRegionAAP.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
+
+    data = unprotectedByCounty %>% 
+        filter(strat=="aap", rounding==0) %>% 
+        filter(county %in% countiesForPlots)
+
+    ggplot(data) +
         theme_light(base_size=plotTextBaseSize) +
@@
 @
-\input{figure/coverageByRegionAAP.tex}
-\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis administered according to AAP guidelines, by region.}
+\input{\figuresDir/coverageByRegionAAP.tex}
+\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis administered according to AAP guidelines, by region}
 \label{fig:coverageByRegionAAP}
@@
 
-The cause of this is evident in Figure \ref{fig:coverageByRegionAAPInsight}; temporal misalignment between the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each region), and the time window of AAP prophylaxis regimen.
-Fairfield county, owing to its early season onset, has disproportionately many cases before prophylaxis administration begins; on the other hand, the low-incidence counties, owing to their late season onset, have their RSV seasons almost entirely contained within the prophylaxis window.
-
-\begin{figure}
-<<coverageByRegionAAPInsight, results='hide'>>=
-    tikz("figure/coverageByRegionAAPInsight.tex", width=plotWidth, height=plotHeight*3/2, pointsize=10)
-    ggplot2.multiplot(plotlist=lapply(countiesForPlots, function(c) {
-        strat = ppxFixedStrategies("all")[["aap"]]
-
-        countyPred = predByCounty %>% filter(county==c) %>% mutate(ppx=strat(time))
-        countyThresholds = thresholdsByCounty %>% filter(county==c)
-        ppxStart = min((countyPred %>% filter(ppx > 0))$time)
-        ppxEnd = max((countyPred %>% filter(ppx > 0))$time)
-
-        unprotectedAtStart = (countyPred %>% filter(time==ppxStart))$rsv.cum.fit
-        unprotectedAtEnd = (countyPred %>% filter(time==ppxEnd))$rsv.cum.fit
-
-        annotation_timespan = function(plot, xmin, xmax, y, color, label) {
-            ymin = y - .01
-            ymax = y + .01
-            yminlabel = y + .01
-            ymaxlabel = y + .11
-            plot + annotation_custom(linesGrob(gp=gpar(col=color)), xmin=xmin, ymin=y, xmax=xmax, ymax=y) + 
-            annotation_custom(linesGrob(gp=gpar(col=color)), xmin=xmin, ymin=ymin, xmax=xmin, ymax=ymax) + 
-            annotation_custom(linesGrob(gp=gpar(col=color, lty="dotted")), xmin=xmin, ymin=0, xmax=xmin, ymax=1) + 
-            annotation_custom(linesGrob(gp=gpar(col=color)), xmin=xmax, ymin=ymin, xmax=xmax, ymax=ymax) + 
-            annotation_custom(linesGrob(gp=gpar(col=color, lty="dotted")), xmin=xmax, ymin=0, xmax=xmax, ymax=1) + 
-#            annotation_custom(linesGrob(gp=gpar(col=color)), xmin=(xmin + xmax) / 2, ymin=y-0.02, xmax=(xmin + xmax) / 2, ymax=y+0.02) + 
-            annotation_custom(textGrob(label, gp=gpar(col=color)), xmin=xmin, xmax=xmax, ymin=yminlabel, ymax=ymaxlabel)
-        }
-
-        plot = ggplot(countyPred) +
-            geom_ribbon(aes(ymin=rsv.cum.fit.lower, ymax=rsv.cum.fit.upper, x=time), fill=grey(.25))
-        plot = plot %>%
-            annotation_timespan(ppxStart, ppxEnd, 1.05, hsv(1/3, 1, .5), "Prophylaxis") %>%
-            annotation_timespan(countyThresholds$onset.median, countyThresholds$offset.median, -0.05, hsv(0, 1, .5), "RSV Season")
-        plot = plot + 
-            annotate("segment", x=-Inf, y=unprotectedAtStart, xend=ppxStart, yend=unprotectedAtStart, linetype=3) + 
-            annotate("segment", x=-Inf, y=unprotectedAtEnd, xend=ppxEnd, yend=unprotectedAtEnd, linetype=3) + 
-            scale_y_continuous(labels=latexPercent, breaks=seq(0, 1, by=.2), limits=c(0, 1), expand=c(0.2, 0)) +
-            labs(x=c) +
-            theme(
-                axis.title.y=element_blank(),
-                axis.ticks.x=element_blank()
-            )
-        table = ggplot_gtable(ggplot_build(plot))
-        table$layout$clip[table$layout$name == "panel"] <- "off"
-
-        plot
-    }), cols=2)
-    dev.off()
-@
-\input{figure/coverageByRegionAAPInsight.tex}
-\caption{RSV relative cumulative incidence by region}
-\label{fig:coverageByRegionAAPInsight}
-\end{figure}
+The cause of this is evident in figure \ref{fig:coverageByRegionAAPInsight}, showing temporal misalignment between the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each region), and the time window of the AAP-recommended prophylaxis regimen.
+Fairfield county, owing to its early season onset, sees disproportionately many cases before prophylaxis administration begins; on the other hand, the low-incidence counties, owing to their late season onset and relatively shorter RSV seasons, see almost all of their RSV cases within the prophylaxis window.
 
@@
 
-Based on all-years data, the six spatially adjusted prophylaxis regimens, when compared to the AAP guidelines, yield non-inferior results in all regions, and superior results both statewide and in Hartford county.
-(Figure \ref{fig:coverageByRegion}.)
+Based on all-years data, the six spatially adjusted prophylaxis regimens (with no rounding of prophylaxis dates), when compared to the AAP guidelines, yield non-inferior results in all regions, and superior results both statewide and in Hartford county.
+(Figure \ref{fig:coverageByRegionRegimen}.)
 
-Statewide, the AAP guidelines generate protection for \Sexpr{regionStrategyCoverage("all", "aap")} cases (\Sexpr{regionStrategyCoverageCI("all", "aap", level)}); meanwhile, the regimens based on all-years statewide onset produce the weakest improvement at \Sexpr{regionStrategyCoverage("all", "stateOnset")} coverage (\Sexpr{regionStrategyCoverageCI("all", "stateOnset", level)}), and other alternate regimens yield similar results.
+Statewide, the AAP guidelines offer protection for \Sexpr{regionStrategyCoverage("all", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}); meanwhile, the regimens based on all-years statewide onset produce the weakest improvement at \Sexpr{regionStrategyCoverage("all", "stateOnset", 0)} coverage (\Sexpr{regionStrategyCoverageCI("all", "stateOnset", 0, level)}), and other alternate regimens yield similar results.
 
-In Hartford county, the improvement is more noteworthy.
-Here, the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap")} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", level)}); the regimens based on all-years regional offset generate the weakest improvement to \Sexpr{regionStrategyCoverage("Hartford", "countyOffset")} protection (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", level)}), and other alternate regimens are comparable.
+In Hartford county, the improvement is similar.
+Here, the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", 0, level)}); the regimens based on all-years regional offset generate the weakest improvement to \Sexpr{regionStrategyCoverage("Hartford", "countyOffset", 0)} protection (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", 0, level)}), and other alternate regimens are comparable.
 
@@
 
-\begin{figure}
+\begin{figure*}
 <<coverageByRegion, results='hide', warning=FALSE>>=
+    tikz(sprintf("%s/coverageByRegionRegimen.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10)
     data = unprotectedByCounty %>% 
-        filter(county %in% countiesForPlots)
-    tikz("figure/coverageByRegionRegimen.tex", width=plotWidth, height=plotHeight, pointsize=10)
+        filter(county %in% countiesForPlots, rounding==0, sliding==FALSE)
+
+    stratLabels = legendLabels(c(
+        "Statewide onset", "Statewide midseason", "Statewide offset", 
+        "Regional onset", "Regional midseason", "Regional offset", 
+        "Statewide recent-years onset", "Statewide recent-years midseason", "Statewide recent-years offset", 
+        "AAP guidelines"
+    ))
+
     ggplot(data) +
@@
         scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
-        scale_linetype_manual(values=c(1, 3, 4, 2, 3, 4, 2)) + 
-        scale_color_manual(values=c(grey(0), rep(hsv(0, 1, 1), 3), rep(hsv(4/6, 1, 1), 3))) + 
+        scale_color_manual(labels=stratLabels[c(seq(1, 6), 10)], values=c(rep(twoTone, each=3), grey(0))) + 
         geom_errorbar(
-            aes(ymin=frac.lower, ymax=frac.upper, x=county, linetype=strat, color=strat, group=strat), 
-            width=0, 
+            aes(ymin=frac.lower, ymax=frac.upper, x=county, color=strat, group=strat), 
+            width=.3, 
             position=position_dodge(.5)
         ) + 
-        geom_point(aes(y=frac.median, x=county, color=strat), position=position_dodge(.5)) +
-        geom_point(aes(y=frac.lower, x=county, color=strat), position=position_dodge(.5), shape=18) +
-        geom_point(aes(y=frac.upper, x=county, color=strat), position=position_dodge(.5), shape=18) +
-        labs(y="Preventable fraction") +
-        guides(color=guide_legend(keywidth=3, keyheight=1), linetype=guide_legend(keywidth=3, keyheight=1)) + 
+        geom_point(aes(y=frac.median, x=county, color=strat), position=position_dodge(.5), size=.75) +
+        labs(y="Preventable fraction", color="Prophylaxis regimen") +
+        guides(color=guide_legend(keywidth=3, keyheight=1, ncol=3)) + 
         theme(
@@
 @
-\input{figure/coverageByRegionRegimen.tex}
-\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by region and prophylaxis regimen.}
+\input{\figuresDir/coverageByRegionRegimen.tex}
+\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by region and prophylaxis regimen}
 \label{fig:coverageByRegionRegimen}
-\end{figure}
+\end{figure*}
 
-\paragraph{RSV season onset and offset are unchanged over time}
+\paragraph{Calendrical rounding rapidly erases gains over the AAP-recommended regimen}
 
-Our linear regression of median surseason onset and offset against surseason year (Figure \ref{fig:onsetOffsetByYear}) indicates (at 95\% confidence level) that season onset has not been drifting earlier (\Sexpr{formatDriftCI(onsetByYear, level)}), and neither has season offset (\Sexpr{formatDriftCI(offsetByYear, level)}).
+\begin{figure*}
+<<coverageByRounding, results='hide', warning=FALSE>>=
+    tikz(sprintf("%s/coverageByRoundingRegimen.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10)
+
+    data = unprotectedByCounty %>% 
+        filter(county == "all", sliding==FALSE)
+
+    ggplot(data) +
+        theme_light(base_size=plotTextBaseSize) +
+        scale_y_continuous(labels=latexPercent, limits=c(0.935, 0.965), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
+        scale_color_manual(labels=stratLabels[c(seq(1, 6), 10)], values=c(rep(twoTone, each=3), grey(0))) + 
+        scale_x_discrete(labels=roundingLabels) + 
+        geom_errorbar(
+            aes(ymin=frac.lower, ymax=frac.upper, x=rounding, color=strat, group=strat), 
+            width=.3, 
+            position=position_dodge(.5)
+        ) + 
+        geom_point(aes(y=frac.median, x=rounding, color=strat), position=position_dodge(.5), size=.75) +
+        labs(x="Calendrical rounding", y="Preventable fraction", color="Prophylaxis regimen") +
+        guides(color=guide_legend(keywidth=3, keyheight=1, ncol=3)) + 
+        theme(
+            legend.position="bottom"
+        )
+    dev.off()
+@
+\input{\figuresDir/coverageByRoundingRegimen.tex}
+\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by calendrical rounding of prophylaxis regimen}
+\label{fig:coverageByRoundingRegimen}
+\end{figure*}
+
+\begin{figure*}
+<<coverageByRegionWithSliding, results='hide', warning=FALSE>>=
+    tikz(sprintf("%s/coverageByRegionRegimenWithSliding.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10)
+    data = unprotectedByCounty %>% 
+        filter(county %in% countiesForPlots, rounding==0, !grepl("county", strat))
+
+    stratLabels = legendLabels(c(
+        "Statewide all-years onset", "Statewide all-years midseason", "Statewide all-years offset", 
+        "Regional onset", "Regional midseason", "Regional offset", 
+        "Statewide recent-years onset", "Statewide recent-years midseason", "Statewide recent-years offset", 
+        "AAP guidelines"
+    ))
+
+    ggplot(data) +
+        theme_light(base_size=plotTextBaseSize) +
+        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
+        scale_color_manual(labels=stratLabels[c(seq(1, 3), seq(7, 10))], values=c(rep(twoTone, each=3), grey(0))) + 
+        geom_errorbar(
+            aes(ymin=frac.lower, ymax=frac.upper, x=county, color=strat, group=strat), 
+            width=.3, 
+            position=position_dodge(.5)
+        ) + 
+        geom_point(aes(y=frac.median, x=county, color=strat), position=position_dodge(.5), size=.75) +
+        labs(y="Preventable fraction", color="Prophylaxis regimen") +
+        guides(color=guide_legend(keywidth=3, keyheight=1, ncol=3)) + 
+        theme(
+            axis.title.x=element_blank(),
+            axis.ticks.x=element_blank(),
+            legend.position="bottom"
+        )
+    dev.off()
+@
+\input{\figuresDir/coverageByRegionRegimenWithSliding.tex}
+\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by region and prophylaxis regimen}
+\label{fig:coverageByRegionRegimenWithSliding}
+\end{figure*}
+
+After we applied weekly, biweekly, and monthly rounding to start and end dates of our six alternate immunoprophylaxis regimens, overall we found that longer rounding intervals diminished the net benefit of spatial analysis.
+
+With weekly rounding, our regimens were non-inferior to the AAP recommendation, and produced an increase in preventable fraction from AAP's \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) to \Sexpr{bestCaseCoverage(1)} (\Sexpr{bestCaseCoverageCI(1, level)}) statewide.
+The increase was most notable in Fairfield and Hartford counties.
+% TODO Details?
+
+Biweekly rounding yielded regimens similarly non-inferior to the AAP recommendation, with an increase in preventable fraction to \Sexpr{bestCaseCoverage(2)} (\Sexpr{bestCaseCoverageCI(2, level)}) statewide.
+The increase was most notable in Fairfield and New Haven counties.
+% TODO Details?
+
+However, with monthly rounding, the gains almost completely vanished, with preventable fraction not exceeding \Sexpr{bestCaseCoverage(4)} (\Sexpr{bestCaseCoverageCI(4, level)}).
+With this rounding, all our regimens were non-superior to the AAP-recommended regimen in all regions.
+
+\paragraph{RSV season onset is slowly moving earlier}
+
+Our linear regression of median surseason onset and offset against surseason year (Figure \ref{fig:onsetOffsetByYear}) indicates that season onset has slowly been drifting earlier, at a rate of \Sexpr{formatDrift(onsetByYear)} (\Sexpr{formatDriftCI(onsetByYear, level)}).
+It is unclear whether this is a part of a larger pattern, such as a cycle spanning decades.
+
+Season offset, on the other hand, has not been drifting earlier or later (\Sexpr{formatDriftCI(offsetByYear, level)}).
 
@@
     data = stateThresholdsByWindow %>% 
-        melt(id=c("year")) %>%
+        melt(id=c("epiyear")) %>%
         cSplit(c("variable"), c(".")) %>%
         rename(variable=variable_1, pctile=variable_2) %>%
-        mutate(variable=factor(variable, levels=c("onset", "offset"))) %>%
-        cast(year + variable ~ pctile)
+        mutate(variable=factor(variable, levels=c("offset", "onset"))) %>%
+        cast(epiyear + variable ~ pctile)
 
-    tikz("figure/onsetOffsetByYear.tex", width=plotWidth, height=plotHeight, pointsize=10)
+    tikz(sprintf("%s/onsetOffsetByYear.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
     ggplot(data) +
         theme_light(base_size=plotTextBaseSize) +
-        geom_errorbar(aes(ymin=lower, ymax=upper, x=year), width=.1) + 
-        geom_point(aes(y=median, x=year)) +
+        geom_errorbar(aes(ymin=lower, ymax=upper, x=epiyear), width=.1) + 
+        geom_point(aes(y=median, x=epiyear)) +
         facet_wrap(~variable, ncol=1, scales="free_y", labeller=onsetOffsetLabeller) +
@@
 @
-\input{figure/onsetOffsetByYear.tex}
-\caption{RSV season onset and offset by three-year surseason.}
+\input{\figuresDir/onsetOffsetByYear.tex}
+\caption{RSV season onset and offset in Connecticut, by three-year surseason}
 \label{fig:onsetOffsetByYear}
@@
 Compared to our regional analysis, the three regimens based on statewide recent-years analysis produced non-superior results in all regions except for the low-incidence counties, where they produced inferior results.
-(TODO: Figure.) TODO: specifics
+(Figure \ref{fig:coverageByRegionRegimenWithSliding}.)
 
@@
 
-Our model shows that fraction of RSV preventable by immunoprophylaxis in high-risk infants in Connecticut can be increased from that of the prophylaxis regimen currently recommended by the AAP.
+\subsection{Limitations}
 
-The simplest such improvement we can propose is to ignore regional variation within Connecticut, and begin prophylaxis throughout Connecticut a month earlier, according to the regimen based on all-years statewide season onset analysis.
-However --- because our analysis suggests that that regimen might be slightly inferior to the AAP-recommended regimen in counties with low incidence of RSV --- this might lead to a bifurcation, in which clinicians in low-incidence counties would continue following the current AAP guidelines, and in others would adopt the new guidelines.
+Although we were able to reach some conclusions about the impact of calendrical rounding on spatially-adjusted prophylaxis regimens, ultimately our analysis is hamstrung by weekly aggregation of hospital admission data in our initial data.
+To properly propose and evaluate any fine-tuning to RSV prophylaxis guidelines, we recommend use of daily data.
 
-Therefore, since an attempt to transition to new state-wide guidelines might effectively result in a transition to county-level guidelines, it would likely be preferable to use our county-level analysis in the first place.
-With that, our analysis favors the prophylaxis regimen linked to regional RSV season midpoint.
-Under this regimen, TODO which county uses what, and the net benefit would be XX\% increase in prophylaxis coverage.
+Throughout, we assume that RSV-associated hospitalizations are an unbiased estimate of RSV incidence in the general population; in doing so, we implicitly assumed that infectiousness and virulence of RSV are constant over time, for which we have no verification.
 
-However, that leaves open the question of whether transitioning to such guidelines would be too costly.
-Although our prophylaxis regimens were specifically chosen to keep fixed the cost of pharmaceuticals, we did not evaluate implementation cost of our proposals; such analysis would be necessary before elevating them from proposals to recommendations.
+Our model of palivizumab immunoprophylaxis assumes a protection period with a hard start at administration and a hard stop at 24 weeks post-administration; the physiologic response to monoclonal antibody immunoprophylaxis is actually tapered on both ends.
+
+Similarly, we assumed the protection by palivizumab is constant at 100\% throughout the protection period; however, not only is breakthrough RSV illness known to occur in patients on palivizumab, but it is an indication for discontinuing the remained of the prophylaxis regimen.
+
+In areas of Connecticut associated with relatively high amount of interstate travel (such as urban centers near the state lines), our analysis --- by only considering residents of Connecticut --- likely underestimates RSV burden.
+
+Similarly, towns that see substantial intercounty travel (for example, employment hubs near county lines) likely bias our estimates towards higher counts in high-population counties.
+
+\subsection{Conclusions}
+
+Our analysis confirms regional variation of RSV season timing in Connecticut, defined by RSV season onset and offset, and observable at the county level.
+We have also shown a misalignment between the prophylaxis regimen recommended by the AAP and the timing of the RSV season in Fairfield County, resulting in the start of the RSV season occurring outside of the prophylaxis window.
+
+Our attempt to optimize timing of the prophylaxis regimen (without changing it duration and therefore its cost) shows a theoretical possibility of a 1-2\% increase in preventable RSV cases each year, occurring primarily in counties with a higher RSV burden (Fairfield, Hartford, and New Haven counties).
+
+However, that theoretical improvement rapidly wanes when faced with practicalities of clinical practice guideline implementation; in order to derive real-world benefit from our analysis, clinical practice guidelines would need to be localized at the county level, and the timing of prophylaxis adjusted by less than a whole month in each region.
+
+As a result, we conclude that the case for regional adjustment to RSV immunoprophylaxis guidelines is weak.
+
+Although we found a weak statewide trend in RSV season onset becoming earlier over time, further analysis did not yield any improvements to prophylaxis based on that trend; the results of our temporal analysis were no stronger than the results of our spatial analysis.
+Since temporal variation in clinical guidelines would lead to a higher burden of implementation than spatial variation, we see no reason to base RSV immunoprophylaxis clinical practice guidelines on temporal variation in RSV reason timing.
+
+% TODO proofread references
+
+\phantomsection
+\addcontentsline{toc}{section}{Bibliography}
+\printbibliography[title={Bibliography}] % Print the bibliography, section title in curly brackets
 
@@
 
-\printbibliography[title={Bibliography}] % Print the bibliography, section title in curly brackets
-
 \end{document}

### 2018-01-15 Thesis/Thesis.R

@@ -3,9 +3,17 @@ library(grid)
 library(tikzDevice)
 options(tikzDefaultEngine='pdftex')
 
-plotWidth=3.1
-plotHeight=2.5
-plotTextBaseSize=8
+figuresDir = ".texpadtmp/figures"
+if (!dir.exists(figuresDir)) {
+  dir.create(figuresDir, recursive=TRUE)
+}
+options(tikzMetricsDictionary='.texpadtmp/tikzDictionary.dat')
+
+inlinePlotWidth = 3.1
+inlinePlotHeight = 2.5
+pagePlotWidth = inlinePlotWidth * 2.1
+pagePlotHeight = inlinePlotHeight * 2.1 * 2 / 5
+plotTextBaseSize = 8
 
 # Formatting utilities
 formatDate = function(date) {
@@ -56,37 +64,40 @@ formatPctCI = function(lower, upper, level) {
   sprintf("%d\\%% CI: %.2f -- %.2f\\%%", level * 100, lower * 100, upper * 100)
 }
 
-regionStrategyCoverage = function(c, s) {
-  formatPct((unprotectedByCounty %>% filter(county==c, strat==s))$frac.median)
+regionStrategyCoverage = function(c, s, r) {
+  formatPct((unprotectedByCounty %>% filter(county==c, strat==s, rounding==r))$frac.median)
 }
 
-regionStrategyCoverageCI = function(c, s, level) {
+regionStrategyCoverageCI = function(c, s, r, level) {
   formatPctCI(
-    (unprotectedByCounty %>% filter(county==c, strat==s))$frac.upper,
-    (unprotectedByCounty %>% filter(county==c, strat==s))$frac.lower,
+    (unprotectedByCounty %>% filter(county==c, strat==s, rounding==r))$frac.upper,
+    (unprotectedByCounty %>% filter(county==c, strat==s, rounding==r))$frac.lower,
     level
   )
 }
 
-driftYearToWeek = function(year, negate) {
-  drift = 365 / 7 * year
-  if (negate) {
-    -drift
-  } else {
-    drift
-  }
+bestCaseCoverage = function(r) {
+  formatPct((bestCaseCoverageByRounding %>% filter(rounding==r))$frac.median)
 }
 
-formatDrift = function(lm, negate=FALSE) {
-  sprintf("%.2f weeks", driftYearToWeek(summary(lm)$coefficients['year', 1], negate))
+bestCaseCoverageCI = function(r, level) {
[…]

### 2018-01-15 Thesis/Thesis.rnw
County labels

@@
         facet_wrap(~variable, ncol=1, scales="free_y", labeller=onsetOffsetLabeller) +
+        scale_x_discrete(labels=countyLabels) + 
         labs(y="Surveillance week") + 
@@
             axis.ticks.x=element_blank(),
+            axis.text.x=element_text(angle=30, hjust=1)
         )
@@
         scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
+        scale_x_discrete(labels=countyLabels) + 
         labs(y="Preventable fraction") +
@@
             axis.title.x=element_blank(),
-            axis.ticks.x=element_blank()
+            axis.ticks.x=element_blank(),
+            axis.text.x=element_text(angle=30, hjust=1)
         )
@@
         guides(color=guide_legend(keywidth=3, keyheight=1, ncol=3)) + 
+        scale_x_discrete(labels=countyLabels) + 
         theme(

### 2018-01-15 Thesis/Thesis.R

@@ -111,6 +111,14 @@ onsetOffsetLabeller = labeller(
 
 roundingLabels = c(`0` = "No rounding", `1` = "Weekly", `2` = "Biweekly", `4` = "Monthly")
 
+countyLabels = c(
+  `all` = "Statewide",
+  `New Haven` = "New Haven county",
+  `Fairfield` = "Fairfield county",
+  `Hartford` = "Hartford county",
+  `lowIncidence` = "Low-incidence counties"
+)
+
 legendLabels = function(labels) {
   as.vector(sapply(labels, function(label) {
     sprintf("%s\\qquad\\qquad", label)

### 2018-01-15 Thesis/Thesis.rnw
Abstract rewrite / relayout

@@
 
-\newcommand{\abstractsection}[1]{\makebox[1in][l]{\textbf{#1}}}
+\usepackage{hanging}
+
+\newlength\abstractindent
+\setlength\abstractindent{1in}
+\newcommand{\abstractsection}[1]{\hangpara{\abstractindent}{1}\makebox[1in][l]{\textbf{\textsc{#1}}}}
+\newcommand{\abstractpara}{\hskip\abstractindent\hskip\baseparindent}
 
@@
 
+\newlength\baseparindent
+\setlength\baseparindent{\parindent}
 \begingroup
@@
 
-\begin{abstract}
+\section*{\centerline{Abstract}}
+\begin{hangparas}{\abstractindent}{1}
 
-\abstractsection{Background} Respiratory syncytial virus (RSV) causes seasonal respiratory infection with potentially serious complications in young infants.
+\abstractsection{Background}Respiratory syncytial virus (RSV) causes seasonal respiratory infection with potentially serious complications in young infants.
 Immunoprophylaxis (palivizumab) is available, but costly.
@@
 
-\abstractsection{Methods} We describe a generalized additive model of RSV incidence using cubic cyclic penalized splines and apply that model to hospital admissions records from Connecticut between \Sexpr{formatDate(startDate)} and \Sexpr{formatDate(endDate)} to estimate fraction of RSV cases in Connecticut preventable by immunoprophylaxis administered according to the AAP guidelines.
-We also formulate several alternate immunoprophylaxis regimens with the same net pharmaceutical cost, estimate the fraction preventable by those alternate regimens.
+\abstractsection{Methods}We describe a generalized additive model of RSV incidence using cubic cyclic penalized splines and apply that model to hospital admissions records from Connecticut between \Sexpr{formatDate(startDate)} and \Sexpr{formatDate(endDate)} to estimate the fraction of RSV cases in Connecticut preventable by immunoprophylaxis administered according to the AAP guidelines.
+We also formulate several alternate immunoprophylaxis regimens with the same net pharmaceutical cost, and estimate the fraction preventable by those alternate regimens.
 
-\abstractsection{Results} At 95\% confidence level, we found alternate regimens that account for spatial variability of RSV incidence at the county level to have superior coverage (to that of the AAP-recommended regimen) in some regions of Connecticut, and non-inferior coverage in other regions.
-We also found alternate regimens that account for temporal RSV variability at the annual level to have non-superior coverage to our spatially-adjusted regimens.
-Overall, we found our best-performing spatially-adjusted alternate to AAP guidelines to provide a XX\% statewide increase in RSV prophylaxis coverage over the AAP regimen.
+\abstractsection{Results}At \Sexpr{level * 100}\% confidence level, we found that, when it comes to the fraction of RSV cases preventable by an immunoprophylaxis regimen, regimens adjusted for spatial variation in incidence at the county level have superior preventable fraction (than the AAP-recommended regimen) in some regions of Connecticut, and non-inferior preventable fraction in other regions.
+However, when those regimens were modified to accommodate practicable calendrical boundaries (weekly, biweekly, and monthly), their gains rapidly diminished.
 
-\abstractsection{Conclusion} We conclude that the increased prophylaxis coverage provided by regimens based on our county-level spatial analysis warrants further analysis to determine whether the potential reduction in hospitalization rate is nullified by the potential increase in implementation cost.
+\abstractpara{}We also found that alternate regimens adjusted for temporal variation in incidence at the annual level to have non-superior preventable fraction to our spatially-adjusted regimens.
+
+\abstractpara{}Overall, we found our best-performing spatially-adjusted practicable alternate to the AAP guidelines to be based on regional RSV season midpoint with biweekly rounding, and to provide a statewide increase in preventable fraction from \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) to \Sexpr{regionStrategyCoverage("all", "countyMiddle", 2)} (\Sexpr{regionStrategyCoverageCI("all", "countyMiddle", 2, level)}).
+
+\abstractsection{Conclusion}We conclude that the increased preventable fraction provided by prophylaxis regimens based on our county-level spatial analysis warrants further analysis to determine whether the potential reduction in hospitalization rate is nullified by the potential increase in implementation cost.
 Our temporal analysis at the annual level showed no additional benefit beyond the spatial analysis, while simultaneously increasing implementation complexity.
-Overall, we recommend county-level spatial analysis of RSV incidence as the starting point for RSV immunoprophylaxis optimization in Connecticut.
 
-\end{abstract}
+\abstractpara{}Overall, we recommend county-level spatial analysis of RSV incidence as the starting point for RSV immunoprophylaxis optimization in Connecticut.
+
+\end{hangparas}
 

### 2018-01-16 Thesis/structure.tex
Exclude URLs from bibliography

@@
 
-\usepackage[backend=bibtex,style=nejm,sorting=none,autocite=superscript,articledoi=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
+\usepackage[backend=bibtex,style=nejm,sorting=none,autocite=superscript,articledoi=true,url=false]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
 %\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)

### 2018-01-16 Thesis/Thesis.R
Better labels for epi week axis

@@ -1,6 +1,7 @@
 # ---- util ----
 library(grid)
 library(tikzDevice)
+library(rgdal)
 options(tikzDefaultEngine='pdftex')
 
 figuresDir = ".texpadtmp/figures"
@@ -116,12 +117,16 @@ countyLabels = c(
   `New Haven` = "New Haven county",
   `Fairfield` = "Fairfield county",
   `Hartford` = "Hartford county",
-  `lowIncidence` = "Low-incidence counties"
+  `lowIncidence` = "Low-RSV counties"
 )
 
-legendLabels = function(labels) {
+# .01 to let minor gridlines show through
+epiWeekBreaks = c(3.01, 7.25, 11.75, 16.01, 20.25, 24.75, 29.01, 33.01, 37.5, 42.01, 46.25, 50.75)
+epiWeekLabels = c("Jul", "Aug", "Sep", "Oct", "Nov", "Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun")
+
+legendLabels = function(labels, size="") {
   as.vector(sapply(labels, function(label) {
-    sprintf("%s\\qquad\\qquad", label)
+    sprintf("%s%s%s\\qquad\\qquad", size, ifelse(nchar(size) > 0, " ", ""), label)
   }))
 }
 

### 2018-01-16 Analysis/RSV.R
Ensure calendar rounding aligns with Nov 15

@@ -8,6 +8,7 @@ library(ggplot2)
 library(easyGgplot2)
 library(data.table)
 library(splitstackshape)
+library(maps)
 
 # ---- external ----
 data(zipcode)
@@ -113,12 +114,19 @@ modelTime = seq(min(rsvTime) - 1 + eps, max(rsvTime), eps)
 
 # *** Prophyaxis assessment helpers
 
-evalStrategy = function(start, end, time, rounding) {
-  if (rounding > 0) {
-    start = rounding * round(start / rounding)
-    end = rounding * round(end / rounding)
+epochRound = function(time, epoch) {
+  if (epoch > 0) {
+    # Rounding for prophylaxis strategies has phase as follows
+    # For rounding=1, .5 .. 1.5 round to 1
+    # For rounding=2, 1 .. 3 round to 2
+    # For rounding=4, 2 .. 6 round to 4
+    time = epoch * round(time / epoch)
   }
-  as.numeric((time >= start) & (time < end))
+  time
+}
+
+evalStrategy = function(start, end, time, rounding) {
+  as.numeric((time >= epochRound(start, rounding)) & (time < epochRound(end, rounding)))
 }
 
 evalOnsetStrategy = function(start, time, rounding=0) {

### 2018-01-16 Analysis/RSV.Rmd
Added maps packages

@@
 ```{r setup, include=FALSE, error=FALSE, warning=FALSE, message=FALSE}
-install.packages(c("dplyr", "zipcode", "reshape", "mgcv", "ggplot2", "gridExtra", "devtools", "data.table", "tikzDevice", "splitstackshape"))
+install.packages(c("dplyr", "zipcode", "reshape", "mgcv", "ggplot2", "gridExtra", "devtools", "data.table", "tikzDevice", "splitstackshape", "maps", "mapproj"))
 library(devtools)

### 2018-01-16 Thesis/Thesis.rnw
Assorted edits and figure rearrangements

@@
-% TODO: DOI in bib?
-% TODO: Prettier abstract sectioning
-% TODO: Better calendrical cues in plots
+% TODO: Better calendrical cues in plots, maybe also with bars?
+% TODO: establish need in intro
+% TODO: adverse effects of immunoprophylaxis
 
@@
 
-<<util>>=
+<<util, warning=FALSE>>=
 @
 
-\documentclass[10pt,a4paper,draft]{article}
+\documentclass[10pt,a4paper]{article}
 
@@
 \SetWatermarkLightness{.5}
-\SetWatermarkText{DRAFT 2}
+\SetWatermarkText{DRAFT 3}
 
@@
 \usepackage{hanging}
+\usepackage{graphicx}
 
@@
 
-\title{Optimization of respiratory syncytial virus prophylaxis using a generalized additive model of Connecticut hospitalizations}
-\def\headertitle{Optimization of RSV prophylaxis using a generalized additive model of Connecticut hospitalizations}
+\title{Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}}
+\def\headertitle{Assessment and optimization of RSV prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}}
 
@@
 \maketitle
+
+\begin{center}
+
+\vspace{20pt}
+\large Submitted to the School of Public Health and the School of Medicine, in partial fulfillment of the requirements for the degrees of Master of Public Health and Master of Medical Sciences
+
+\vspace{40pt}
+
+\includegraphics[height=2.5in]{EPH}
+\hspace{40pt}
+\includegraphics[height=2.5in]{Medicine}
+
+\end{center}
+
 \thispagestyle{firstpage}
@@
 
-\subsection{Spatio-temporal variability of RSV in Connecticut}
+\subsection{Spatio-temporal variability of RSV}
 
-The Department of Public Health of the state of Connecticut, via its Office of Health Care Access (OHCA), maintains a database of all hospitalizations in every non-federal short-stay acute-care general hospital in the state.
-Previous analysis of this database has shown regional variability in time of peak RSV incidence within Connecticut.\cite{Noveroske:y4fi3188}
+Nationwide spatial variability of RSV season has been established by the Centers for Disease Control and Prevention (CDC).\cite{CentersforDiseaseControlandPreventionCDC:2011wt,CentersforDiseaseControlandPreventionCDC:2013wv}
+
+The Department of Public Health of the state of Connecticut (CT DPH), via its Office of Health Care Access (OHCA), maintains a database of all hospitalizations in every non-federal short-stay acute-care general hospital in the state.
+Previous analysis of this database at the Yale University School of Public Health has shown regional variability in time of peak RSV incidence within Connecticut.\cite{Noveroske:y4fi3188}
 
@@
 	\item To what extent does regional variability of RSV incidence in Connecticut impact the effectiveness of the AAP-recommended prophylaxis regimen?
-	\item Can we use spatial analysis of RSV to propose alternate regimens, either statewide or regional, that would improve effectiveness over AAP-recommended prophylaxis, without increasing treatment cost?
+	\item Can we use spatial analysis of RSV to propose alternate regimens, either statewide or regional, that would regionally improve effectiveness over AAP-recommended prophylaxis, without increasing the total cost of the prophylactics the regimen?
 	\item Is there year-to-year variation in timing of RSV season in Connecticut?
@@
 
-We identified \Sexpr{nrow(dataset)} cases of RSV in Connecticut between \Sexpr{formatDate(startDate)} and \Sexpr{formatDate(endDate)}.
+We identified \Sexpr{nrow(dataset)} hospitalization coded as RSV in Connecticut between \Sexpr{formatDate(startDate)} and \Sexpr{formatDate(endDate)}.
 
 The cases were identified from the hospitalization database maintained by the OHCA, who provided us with weekly hospitalization statistics.
+
+The study was approved by the Human Investigation Committees at Yale University and the CT DPH. The authors assume full responsibility for analyses and interpretation of the data obtained from CT DPH.
 
@@
 
-Our goal was to construct a model of RSV incidence over time that allows us to easily estimate complex characteristics of RSV seasons, such as season onset and offset, or preventable RSV case fraction.
+Our goal was to construct a model of annual RSV incidence that allows us to easily estimate complex characteristics of RSV seasons, such as season onset and offset, or preventable RSV case fraction.
 
@@
 
-We were willing to assume that RSV incidence can be modeled as a twice-differentiable piecewise Poisson time series.
+We were willing to assume that RSV incidence is the result of a Poisson process whose log can be modeled as a piecewise twice-differentiable function of time.
 
@@
 
-We developed a custom R package for estimation of arbitrary characteristics of infectious disease outbreaks (as long as the outbreaks are amenable to GAM); this package is available at \href{https://github.com/airbornemint/outbreakpredict}{\nolinkurl{github.com/airbornemint/outbreakpredict}}.
+We developed a custom R package for estimation of arbitrary characteristics of infectious disease outbreaks (as long as the outbreaks are amenable to GAM); this package is available at \href{https://github.com/airbornemint/outbreak-predict}{\nolinkurl{github.com/airbornemint/outbreak-predict}}.
+
+\begin{figure}
+\begin{center}
+\input{\figuresDir/map.tex}
+\caption{RSV case burden in Connecticut counties}
+\label{fig:map}
+\end{center}
+\end{figure}
 
@@
 
-For our spatial analysis, we aggregated RSV incidence data across all years in our data set. We then spatially aggregated the data to form five regions:
+<<map, results='hide'>>=
+    tikz(sprintf("%s/map.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
+    US.counties = readOGR(dsn="../Maps/cb_2016_us_county_5m",layer="cb_2016_us_county_5m")
+    US.counties = US.counties[US.counties$STATEFP == "09",]
+    county.data = US.counties@data %>%
+        mutate(id=rownames(.)) %>%
+        data.table() %>%
+        mutate(highRSV=ifelse(NAME %in% lowIncidenceCounties, FALSE, TRUE))
 
-% TODO: map
+    map.df = US.counties %>% 
+        fortify() %>% 
+        data.table() %>%
+        inner_join(county.data %>% select(highRSV, id), by="id")
+
+    county.data = map.df %>%
+        group_by(id) %>%
+        summarize(lat=mean(range(lat)), long=mean(range(long))) %>%
+        ungroup() %>%
+        inner_join(county.data, by="id") %>%
+        rename(name=NAME)
+
+    ggplot(map.df, aes(x=long, y=lat)) +
+        theme_light(base_size=plotTextBaseSize) +
+        scale_fill_manual(labels=legendLabels(c("$<$50", "$>$100")), values=twoTone) +
+        geom_polygon(aes(fill=highRSV, group=group), color="white", size=.5) +
+        geom_text(data=county.data, aes(label=name), size=2.2) +
+        coord_map() + 
+        labs(fill="Average RSV cases per year") +
+        theme(
+            rect=element_blank(),
+            line=element_blank(),
+            axis.text=element_blank(),
+            axis.title=element_blank(),
+            legend.position="bottom"
+        )
+    dev.off()
+@
+
+For our spatial analysis, we aggregated RSV incidence data across all years in our data set. We then spatially aggregated the data to form five regions (Figure \ref{fig:map}):
 
@@
     \item One region for the entire state
-    \item One region for each of the counties with high incidence of RSV: Hartford County, Fairfield County, and New Haven County.
-    \item One discontiguous region comprised of all remaining counties in Connecticut: \Sexpr{gsub("(.*), (.*)", "\\1, and \\2", paste(lowIncidenceCounties, collapse=", "))}
+    \item One region for each of the counties with high case counts of RSV: Hartford County, Fairfield County, and New Haven County.
+    \item One discontiguous region comprised of all remaining counties in Connecticut: \Sexpr{gsub("(.*), (.*)", "\\1, and \\2", paste(lowIncidenceCounties, collapse=", "))} (``low-RSV counties'')
 \end{itemize}
@@
 
-We chose to aggregate low-incidence counties into a single region because our analysis in those counties individually would have yielded results with unacceptably low statistical power.
+We chose to aggregate low-RSV counties into a single region because our analysis in those counties individually would have yielded results with unacceptably low statistical power.
 
@@
 The choice of \Sexpr{seasonThreshold * 100}\% and \Sexpr{(1 - seasonThreshold) * 100}\% incidence thresholds was based on our intent to use estimates of RSV season onset and offset to put forth alternate prophylaxis regimens (as described below), while maintaining 6-month dosing schedule (and therefore not increasing medication cost).
-Incidence cutoffs other than \Sexpr{seasonThreshold * 100}\% and \Sexpr{(1 - seasonThreshold) * 100}\% were briefly investigated, but quickly ruled out because they produced suboptimal results.
+Incidence cutoffs other than \Sexpr{seasonThreshold * 100}\% and \Sexpr{(1 - seasonThreshold) * 100}\% were briefly investigated, but quickly ruled out because they produced prophylaxis regimens starting weeks prior to RSV season onset or ending weeks after RSV season offset.
 
-\subsection{Devising alternate all-years prophylaxis regimens}
+\subsection{Evaluating alternate all-years prophylaxis regimens}
 
-Following this analysis, we devised six alternate spatially adjusted prophylaxis regimens.
-In all our alternate regimens, prophylaxis consists of six monthly doses of palivizumab, and protection is assumed to last 24 weeks from the first dose.
+Following this analysis, we estimated the regional and statewide preventable fraction for six alternate spatially adjusted prophylaxis regimens:
 
@@
     \item \textbf{By statewide all-years offset}: prophylaxis administration begins 24 weeks before the (statewide all-years median) RSV season offset. 
-    \item \textbf{By regional all-years onset}: prophylaxis administration begins at regional\footnote{county-wide, or --- in the case of low-incidence counties --- low-incidence-region-wide} all-years median RSV season onset.
+    \item \textbf{By regional all-years onset}: prophylaxis administration begins at regional\footnote{county-wide, or --- in the case of low-RSV counties --- low-RSV-region-wide} all-years median RSV season onset.
     \item \textbf{By regional all-years midpoint}: prophylaxis administration begins 12 weeks before the average of the (regional all-years median) RSV season onset and offset. 
@@
 
-\subsection{Evaluating alternate prophylaxis regimens}
-
-We evaluated each of those alternate regimens in the same way we evaluated the current AAP guidelines, as described above.
-
-For the three alternate regimens based on statewide data, we estimated preventable fraction statewide, as well as in each region.
-
-For the three alternate regimens based on regional data, we estimated preventable fraction in the corresponding region.
+In all our alternate regimens, prophylaxis consists of five monthly doses of palivizumab, and protection is assumed to last 24 weeks from the first dose.
 
@@
     \item \textbf{Weekly rounding}: prophylaxis start and end date rounded to the nearest calendar week,
-    \item \textbf{Biweekly rounding}: prophylaxis start and end date rounded to the nearest two-week calendar period, with two-week period boundary chosen , and % TODO: specifics
-    \item \textbf{Monthly rounding}: prophylaxis start and end date rounded to the nearest four-week calendar period.  % TODO: specifics and also not actually in code now
+    \item \textbf{Biweekly rounding}: prophylaxis start and end date rounded to the nearest two-week calendar period, with periods chosen to approximately align with November 15th, and
+    \item \textbf{Monthly rounding}: prophylaxis start and end date rounded to the nearest four-week calendar periods, with periods chosen to approximately align with November 15th.
 \end{itemize}
@@
 
-\subsection{Estimating characteristics of RSV surseasons}
-
 We began our temporal analysis by estimating onset and offset for each surseason, using the same penalized spline GAM as all-years analysis, producing --- as before --- statewide and regional estimates of \Sexpr{seasonThreshold * 100}\% onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset.
-
-\subsection{Evaluating temporal variation of RSV seasonality}
 
@@
 
-\subsection{Devising alternate recent-years prophylaxis regimens}
+\subsection{Evaluating alternate recent-years prophylaxis regimens}
 
-Finally, to assess the impact of any long-term trends in RSV season timing on prophylaxis, we formulated three additional prophylaxis regimens.
+Finally, to assess the impact of any long-term trends in RSV season timing on prophylaxis, we evaluated three additional prophylaxis regimens.
 Here, each prophylaxis regimen is adjusted annually based on RSV data from the preceding surseason:
@@
 
-As before, these alternate regimens involved six monthly doses of palivizumab giving 24 weeks of protection.
+As before, these alternate regimens involved five monthly doses of palivizumab giving 24 weeks of protection.
+
+% \uselengthunit{in}\printlength{\columnwidth}
+% column width = 3.20929 in
+
+\begin{figure*}[b]
+\begin{center}
+\input{\figuresDir/coverageByRegionAAPInsight.tex}
+\caption{RSV relative cumulative incidence in Connecticut, by region}
+\label{fig:coverageByRegionAAPInsight}
+\end{center}
+\end{figure*}
 
@@
 
-\setcounter{figure}{1}
-\begin{figure*}
+\paragraph{RSV season timing varies regionally}
+
+<<seasonByRegion, results='hide'>>=
+    tikz(sprintf("%s/seasonByRegion.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
+    data = thresholdsByCounty %>% 
+        filter(county %in% countiesForPlots) %>%
+        melt(id=c("county")) %>%
+        cSplit(c("variable"), c(".")) %>%
+        rename(variable=variable_1, pctile=variable_2) %>%
+        mutate(variable=factor(variable, levels=c("offset", "onset"))) %>%
+        cast(county + variable ~ pctile)
+
+    onsetOffsetRange = 6 # weeks
+    onsetOffsetAdjust = data.frame(variable=c("onset", "offset"), nudge=c(-1, -2))
+
+    limits = data %>% 
+        select(variable, median) %>%
+        group_by(variable) %>%
+        summarize(mid=round(mean(range(median)))) %>%
+        inner_join(onsetOffsetAdjust, by="variable") %>%
+        mutate(mid=mid + nudge, min=mid - onsetOffsetRange / 2, max=mid + onsetOffsetRange / 2)
+
+    ggplot(data) +
+        theme_light(base_size=plotTextBaseSize) +
+        geom_errorbar(aes(ymin=lower, ymax=upper, x=county), width=.1) + 
+        geom_point(aes(y=median, x=county)) + 
+        geom_blank(data=limits, aes(y=min)) + 
+        geom_blank(data=limits, aes(y=max)) + 
+        labs(aes(x=variable)) +
+        facet_wrap(~variable, ncol=1, scales="free_y", labeller=onsetOffsetLabeller) +
+        scale_x_discrete(labels=countyLabels) + 
+        scale_y_continuous(minor_breaks=seq(1, 52), breaks=epiWeekBreaks, labels=epiWeekLabels) + 
+        labs(y=NULL) + 
+        theme(
+            panel.grid.major.y=element_blank(),
+            panel.grid.minor.y=element_line(size=rel(2)),
+            axis.title.x=element_blank(),
+            axis.ticks.x=element_blank(),
+            axis.ticks.y=element_blank(),
+            axis.text.x=element_text(angle=30, hjust=1)
+        )
+    dev.off()
+@
+
+Compared to the statewide median onset of RSV season at \Sexpr{regionOnset("all")} weeks (\Sexpr{regionOnsetCI("all", level)} weeks) and offset at \Sexpr{regionOffset("all")} weeks (\Sexpr{regionOffsetCI("all", level)} weeks), RSV season in Fairfield county has earlier median onset at \Sexpr{regionOnset("Fairfield")} weeks (\Sexpr{regionOnsetCI("Fairfield", level)} weeks) and later median offset at \Sexpr{regionOffset("Fairfield")} weeks (\Sexpr{regionOffsetCI("Fairfield", level)} weeks).
+(Figure \ref{fig:seasonByRegion}.)
+
+Meanwhile, in comparison with the statewide RSV season onset and offset, the low-RSV region has RSV season with later onset at \Sexpr{regionOnset("lowIncidence")} weeks (\Sexpr{regionOnsetCI("all", level)} weeks); season offset shows no change from the statewide median.
+(Figure \ref{fig:seasonByRegion}.)
+
+\begin{figure}
+\begin{center}
+\input{\figuresDir/seasonByRegion.tex}
+\caption{RSV season onset and offset in Connecticut, by region}
+\label{fig:seasonByRegion}
+\end{center}
+\end{figure}
+
+\paragraph{The AAP guidelines perform best in low-RSV counties and worst in Fairfield county}
+
+<<coverageByRegionAAP, results='hide'>>=
+    tikz(sprintf("%s/coverageByRegionAAP.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
+
+    data = unprotectedByCounty %>% 
+        filter(strat=="aap", rounding==0) %>% 
+        filter(county %in% countiesForPlots)
+
+    ggplot(data) +
+        theme_light(base_size=plotTextBaseSize) +
+        geom_errorbar(aes(ymax=frac.upper, ymin=frac.lower, x=county), width=.1) + 
+        geom_point(aes(y=frac.median, x=county)) + 
+        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
+        scale_x_discrete(labels=countyLabels) + 
+        labs(y="Preventable fraction") +
+        theme(
+            axis.title.x=element_blank(),
+            axis.ticks.x=element_blank(),
+            axis.text.x=element_text(angle=30, hjust=1)
+        )
+    dev.off()
+@
+
 <<coverageByRegionAAPInsight, results='hide'>>=
@@
         scale_y_continuous(labels=latexPercent, breaks=seq(0, 1, by=.2), limits=c(-0.1, 1.1), expand=c(0, 0)) +
+        scale_x_continuous(breaks=epiWeekBreaks, labels=epiWeekLabels, limits=c(1, 52)) + 
         scale_color_manual(labels=spanLabels, values=twoTone) +
@@
         guides(color=guide_legend(keywidth=3, keyheight=.4)) + 
-        facet_wrap(~county, ncol=5) +
-        labs(x="Surveillance week") + 
+        facet_wrap(~county, ncol=5, labeller=labeller(county=countyLabels)) +
+        labs(x=NULL) + 
         theme(
+            panel.grid.major.x=element_blank(),
+            panel.grid.minor.x=element_blank(),
             legend.title=element_blank(),
@@
             axis.ticks.x=element_blank(),
+            axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
             legend.position="bottom"
@@
 @
-\input{\figuresDir/coverageByRegionAAPInsight.tex}
-\caption{Weekly RSV relative cumulative incidence in Connecticut, by region}
-\label{fig:coverageByRegionAAPInsight}
-\end{figure*}
-\setcounter{figure}{0}
 
-\paragraph{RSV season in Fairfield county begins early and ends late}
+Statewide, our model shows that \Sexpr{regionStrategyCoverage("all", "aap", 0)} of RSV cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) occur while palivizumab, administered according to the AAP guidelines, offers protection.
 
-Compared to the statewide median onset of RSV season at \Sexpr{regionOnset("all")} weeks (\Sexpr{regionOnsetCI("all", level)} weeks) and offset at \Sexpr{regionOffset("all")} weeks (\Sexpr{regionOffsetCI("all", level)} weeks), RSV season in Fairfield county has earlier median onset at \Sexpr{regionOnset("Fairfield")} weeks (\Sexpr{regionOnsetCI("Fairfield", level)} weeks) and later median offset at \Sexpr{regionOffset("Fairfield")} weeks (\Sexpr{regionOffsetCI("Fairfield", level)} weeks).
-(Figure \ref{fig:seasonByRegion}.)
+The AAP guidelines perform better in the low-RSV counties, where \Sexpr{regionStrategyCoverage("lowIncidence", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("lowIncidence", "aap", 0, level)}) occur during the prophylaxis time window, but worse in Fairfield county, where \Sexpr{regionStrategyCoverage("Fairfield", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("Fairfield", "aap", 0, level)}) occur during this time.
+(Figure \ref{fig:coverageByRegionAAP}.)
 
-% \uselengthunit{in}\printlength{\columnwidth}
-% column width = 3.20929 in
-
-\paragraph{RSV season in low-incidence counties begins late}
-
-Meanwhile, in comparison with the statewide RSV season onset and offset, the low-incidence region has RSV season with later onset at \Sexpr{regionOnset("lowIncidence")} weeks (\Sexpr{regionOnsetCI("all", level)} weeks); season offset shows no change from the statewide median.
-(Figure \ref{fig:seasonByRegion}.)
+The cause of this is evident in Figure \ref{fig:coverageByRegionAAPInsight}, showing temporal misalignment between the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each region), and the time window of the AAP-recommended prophylaxis regimen.
+Fairfield county, owing to its early season onset, sees disproportionately many cases before prophylaxis administration begins; on the other hand, the low-RSV counties, owing to their late season onset and relatively shorter RSV seasons, see almost all of their RSV cases within the prophylaxis window.
 
 \begin{figure}
-<<seasonByRegion, results='hide'>>=
-    tikz(sprintf("%s/seasonByRegion.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
-    data = thresholdsByCounty %>% 
-        filter(county %in% countiesForPlots) %>%
-        melt(id=c("county")) %>%
-        cSplit(c("variable"), c(".")) %>%
-        rename(variable=variable_1, pctile=variable_2) %>%
-        mutate(variable=factor(variable, levels=c("offset", "onset"))) %>%
-        cast(county + variable ~ pctile)
-
-    ggplot(data) +
-        theme_light(base_size=plotTextBaseSize) +
-        geom_errorbar(aes(ymin=lower, ymax=upper, x=county), width=.1) + 
-        geom_point(aes(y=median, x=county)) + 
-        labs(aes(x=variable)) +
-        facet_wrap(~variable, ncol=1, scales="free_y", labeller=onsetOffsetLabeller) +
-        scale_x_discrete(labels=countyLabels) + 
-        labs(y="Surveillance week") + 
-        theme(
-            axis.title.x=element_blank(),
-            axis.ticks.x=element_blank(),
-            axis.text.x=element_text(angle=30, hjust=1)
-        )
-    dev.off()
-@
 \begin{center}
-\input{\figuresDir/seasonByRegion.tex}
-\caption{RSV season onset and offset in Connecticut, by region}
-\label{fig:seasonByRegion}
+\input{\figuresDir/coverageByRegionAAP.tex}
+\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis administered according to the AAP guidelines, by region}
+\label{fig:coverageByRegionAAP}
 \end{center}
 \end{figure}
-\setcounter{figure}{2}
 
-\paragraph{AAP guidelines perform best in low-incidence counties and worst in Fairfield county}
+\paragraph{Spatially-adjusted regimens are superior to the AAP recommendations}
 
-Statewide, our model shows that \Sexpr{regionStrategyCoverage("all", "aap", 0)} of RSV cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) occur while palivizumab, administered according to AAP guidelines, offers protection.
-
-The AAP guidelines perform better in the low-incidence counties, where \Sexpr{regionStrategyCoverage("lowIncidence", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("lowIncidence", "aap", 0, level)}) occur during the prophylaxis time window, but worse in Fairfield county, where \Sexpr{regionStrategyCoverage("Fairfield", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("Fairfield", "aap", 0, level)}) occur during this time.
-(Figure \ref{fig:coverageByRegionAAP}.)
-
-\begin{figure}
-<<coverageByRegionAAP, results='hide'>>=
-    tikz(sprintf("%s/coverageByRegionAAP.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
-
-    data = unprotectedByCounty %>% 
-        filter(strat=="aap", rounding==0) %>% 
-        filter(county %in% countiesForPlots)
-
-    ggplot(data) +
-        theme_light(base_size=plotTextBaseSize) +
-        geom_errorbar(aes(ymax=frac.upper, ymin=frac.lower, x=county), width=.1) + 
-        geom_point(aes(y=frac.median, x=county)) + 
-        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
-        scale_x_discrete(labels=countyLabels) + 
-        labs(y="Preventable fraction") +
-        theme(
-            axis.title.x=element_blank(),
-            axis.ticks.x=element_blank(),
-            axis.text.x=element_text(angle=30, hjust=1)
-        )
-    dev.off()
-@
-\input{\figuresDir/coverageByRegionAAP.tex}
-\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis administered according to AAP guidelines, by region}
-\label{fig:coverageByRegionAAP}
-\end{figure}
-
-The cause of this is evident in figure \ref{fig:coverageByRegionAAPInsight}, showing temporal misalignment between the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each region), and the time window of the AAP-recommended prophylaxis regimen.
-Fairfield county, owing to its early season onset, sees disproportionately many cases before prophylaxis administration begins; on the other hand, the low-incidence counties, owing to their late season onset and relatively shorter RSV seasons, see almost all of their RSV cases within the prophylaxis window.
-
-\paragraph{Spatially-informed regimens are superior to AAP recommendations overall and in Hartford county}
-
-Based on all-years data, the six spatially adjusted prophylaxis regimens (with no rounding of prophylaxis dates), when compared to the AAP guidelines, yield non-inferior results in all regions, and superior results both statewide and in Hartford county.
-(Figure \ref{fig:coverageByRegionRegimen}.)
-
-Statewide, the AAP guidelines offer protection for \Sexpr{regionStrategyCoverage("all", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}); meanwhile, the regimens based on all-years statewide onset produce the weakest improvement at \Sexpr{regionStrategyCoverage("all", "stateOnset", 0)} coverage (\Sexpr{regionStrategyCoverageCI("all", "stateOnset", 0, level)}), and other alternate regimens yield similar results.
-
-In Hartford county, the improvement is similar.
-Here, the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", 0, level)}); the regimens based on all-years regional offset generate the weakest improvement to \Sexpr{regionStrategyCoverage("Hartford", "countyOffset", 0)} protection (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", 0, level)}), and other alternate regimens are comparable.
-
-In every region, all alternate regimens based on all-years analysis are non-inferior to the AAP guidelines and non-superior to each other.
-
-\begin{figure*}
 <<coverageByRegion, results='hide', warning=FALSE>>=
@@
 @
+
+% TODO: Dan says state next paragraph more clearly, it's important
+
+\begin{figure*}
 \input{\figuresDir/coverageByRegionRegimen.tex}
@@
 
+Based on all-years data, the six spatially adjusted prophylaxis regimens (with no rounding of prophylaxis dates), when compared to the AAP guidelines, yield non-inferior results in all regions, and superior results both statewide and in Hartford county.
+(Figure \ref{fig:coverageByRegionRegimen}.)
+
+Statewide, the AAP guidelines offer protection for \Sexpr{regionStrategyCoverage("all", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}).
+The regimen based on all-years statewide onset yields the smallest increase, to \Sexpr{regionStrategyCoverage("all", "stateOnset", 0)} (\Sexpr{regionStrategyCoverageCI("all", "stateOnset", 0, level)}); other alternate regimens yield similar results.
+
+Most of the increase comes from Hartford county, where the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", 0, level)}).
+The regimen based on all-years regional offset generates the smallest increase, to \Sexpr{regionStrategyCoverage("Hartford", "countyOffset", 0)} (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", 0, level)}); other alternate regimens are comparable.
+
+\begin{figure*}
+\begin{center}
+\input{\figuresDir/coverageByRoundingRegimen.tex}
+\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by calendrical rounding of prophylaxis regimen}
+\label{fig:coverageByRoundingRegimen}
+\end{center}
+\end{figure*}
+
+\begin{figure*}[!b]
+\begin{center}
+\input{\figuresDir/coverageByRegionRegimenWithSliding.tex}
+\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by region and prophylaxis regimen}
+\label{fig:coverageByRegionRegimenWithSliding}
+\end{center}
+\end{figure*}
+
+In every region, all alternate regimens based on all-years analysis are non-inferior to the AAP guidelines and non-superior to each other.
+
 \paragraph{Calendrical rounding rapidly erases gains over the AAP-recommended regimen}
 
-\begin{figure*}
 <<coverageByRounding, results='hide', warning=FALSE>>=
@@
         theme_light(base_size=plotTextBaseSize) +
-        scale_y_continuous(labels=latexPercent, limits=c(0.935, 0.965), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
+        scale_y_continuous(labels=latexPercent, limits=c(0.90, 1.00), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
         scale_color_manual(labels=stratLabels[c(seq(1, 6), 10)], values=c(rep(twoTone, each=3), grey(0))) + 
@@
 @
-\input{\figuresDir/coverageByRoundingRegimen.tex}
-\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by calendrical rounding of prophylaxis regimen}
-\label{fig:coverageByRoundingRegimen}
-\end{figure*}
 
-\begin{figure*}
+After we applied weekly, biweekly, and monthly rounding to start and end dates of our six alternate immunoprophylaxis regimens, overall we found that longer rounding intervals diminished the net benefit of spatial analysis.
+
+With weekly rounding, our regimens were non-inferior to the AAP recommendation, and produced an increase in preventable fraction from AAP's \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) to \Sexpr{bestCaseCoverage(1)} (\Sexpr{bestCaseCoverageCI(1, level)}) statewide.
+The increase was most notable in Fairfield and Hartford counties.
+
+Biweekly rounding yielded regimens similarly non-inferior to the AAP recommendation, with an increase in preventable fraction to \Sexpr{bestCaseCoverage(2)} (\Sexpr{bestCaseCoverageCI(2, level)}) statewide.
+The increase was most notable in Fairfield and New Haven counties.
+
+However, with monthly rounding, the gains almost completely vanished, with preventable fraction not exceeding \Sexpr{bestCaseCoverage(4)} (\Sexpr{bestCaseCoverageCI(4, level)}).
+With this rounding, all our regimens were non-superior to the AAP-recommended regimen in all regions.
+
+\paragraph{RSV season onset is slowly moving earlier}
+
+<<onsetOffsetByYear, results='hide', warning=FALSE>>=
+    tikz(sprintf("%s/onsetOffsetByYear.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
+    data = stateThresholdsByWindow %>% 
+        melt(id=c("epiyear")) %>%
+        cSplit(c("variable"), c(".")) %>%
+        rename(variable=variable_1, pctile=variable_2) %>%
+        mutate(variable=factor(variable, levels=c("offset", "onset"))) %>%
+        cast(epiyear + variable ~ pctile)
+
+    onsetOffsetAdjust = data.frame(variable=c("onset", "offset"), nudge=c(0, -1))
+
+    limits = data %>% 
+        select(variable, median) %>%
+        group_by(variable) %>%
+        summarize(mid=round(mean(range(median)))) %>%
+        inner_join(onsetOffsetAdjust, by="variable") %>%
+        mutate(mid=mid + nudge) %>%
+        mutate(min=mid - onsetOffsetRange / 2, max=mid + onsetOffsetRange / 2)
+
+    ggplot(data) +
+        theme_light(base_size=plotTextBaseSize) +
+        geom_errorbar(aes(ymin=lower, ymax=upper, x=epiyear), width=.1) + 
+        geom_point(aes(y=median, x=epiyear)) +
+        geom_blank(data=limits, aes(y=min)) + 
+        geom_blank(data=limits, aes(y=max)) + 
+        facet_wrap(~variable, ncol=1, scales="free_y", labeller=onsetOffsetLabeller) +
+        scale_x_continuous(breaks=seq(1990, 2020, by=5)) +
+        scale_y_continuous(minor_breaks=seq(1, 52), breaks=epiWeekBreaks, labels=epiWeekLabels) + 
+        labs(y=NULL) + 
+        theme(
+            panel.grid.major.y=element_blank(),
+            panel.grid.minor.y=element_line(size=rel(2)),
+            axis.ticks.y=element_blank(),
+            axis.title.x=element_blank()
+        )
+    dev.off()
+@
+
+Our linear regression of median surseason onset and offset against surseason year (Figure \ref{fig:onsetOffsetByYear}) indicates that season onset has slowly been drifting earlier, at a rate of \Sexpr{formatDrift(onsetByYear)} (\Sexpr{formatDriftCI(onsetByYear, level)}).
+It is unclear whether this is a part of a larger pattern, such as a cycle spanning decades.
+
+Season offset, on the other hand, has not been drifting earlier or later (\Sexpr{formatDriftCI(offsetByYear, level)}).
+
+\paragraph{Temporally-adjusted prophylaxis regimens are non-superior to others}
+
 <<coverageByRegionWithSliding, results='hide', warning=FALSE>>=
@@
 @
-\input{\figuresDir/coverageByRegionRegimenWithSliding.tex}
-\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by region and prophylaxis regimen}
-\label{fig:coverageByRegionRegimenWithSliding}
-\end{figure*}
 
-After we applied weekly, biweekly, and monthly rounding to start and end dates of our six alternate immunoprophylaxis regimens, overall we found that longer rounding intervals diminished the net benefit of spatial analysis.
+Compared to our regional analysis, the three regimens based on statewide recent-years analysis produced non-superior results in all regions except for the low-RSV counties, where they produced inferior results.
+(Figure \ref{fig:coverageByRegionRegimenWithSliding}.)
 
-With weekly rounding, our regimens were non-inferior to the AAP recommendation, and produced an increase in preventable fraction from AAP's \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) to \Sexpr{bestCaseCoverage(1)} (\Sexpr{bestCaseCoverageCI(1, level)}) statewide.
-The increase was most notable in Fairfield and Hartford counties.
-% TODO Details?
-
-Biweekly rounding yielded regimens similarly non-inferior to the AAP recommendation, with an increase in preventable fraction to \Sexpr{bestCaseCoverage(2)} (\Sexpr{bestCaseCoverageCI(2, level)}) statewide.
-The increase was most notable in Fairfield and New Haven counties.
-% TODO Details?
-
-However, with monthly rounding, the gains almost completely vanished, with preventable fraction not exceeding \Sexpr{bestCaseCoverage(4)} (\Sexpr{bestCaseCoverageCI(4, level)}).
-With this rounding, all our regimens were non-superior to the AAP-recommended regimen in all regions.
-
-\paragraph{RSV season onset is slowly moving earlier}
-
-Our linear regression of median surseason onset and offset against surseason year (Figure \ref{fig:onsetOffsetByYear}) indicates that season onset has slowly been drifting earlier, at a rate of \Sexpr{formatDrift(onsetByYear)} (\Sexpr{formatDriftCI(onsetByYear, level)}).
-It is unclear whether this is a part of a larger pattern, such as a cycle spanning decades.
-
-Season offset, on the other hand, has not been drifting earlier or later (\Sexpr{formatDriftCI(offsetByYear, level)}).
+Due to the non-superiority of regimens based on statewide recent-years analysis, we did not evaluate regimens based on regional recent-years data.
 
 \begin{figure}
-<<onsetOffsetByYear, results='hide', warning=FALSE>>=
-    data = stateThresholdsByWindow %>% 
-        melt(id=c("epiyear")) %>%
-        cSplit(c("variable"), c(".")) %>%
-        rename(variable=variable_1, pctile=variable_2) %>%
-        mutate(variable=factor(variable, levels=c("offset", "onset"))) %>%
-        cast(epiyear + variable ~ pctile)
-
-    tikz(sprintf("%s/onsetOffsetByYear.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
-    ggplot(data) +
-        theme_light(base_size=plotTextBaseSize) +
-        geom_errorbar(aes(ymin=lower, ymax=upper, x=epiyear), width=.1) + 
-        geom_point(aes(y=median, x=epiyear)) +
-        facet_wrap(~variable, ncol=1, scales="free_y", labeller=onsetOffsetLabeller) +
-        scale_x_continuous(breaks=seq(1990, 2020, by=5)) +
-        labs(y="Surveillance week") + 
-        theme(
-            axis.title.x=element_blank()
-        )
-
-    dev.off()
-@
+\begin{center}
 \input{\figuresDir/onsetOffsetByYear.tex}
@@
 \label{fig:onsetOffsetByYear}
+\end{center}
 \end{figure}
-
-\paragraph{Recent-years prophylaxis regimens are non-superior to others.}
-
-Compared to our regional analysis, the three regimens based on statewide recent-years analysis produced non-superior results in all regions except for the low-incidence counties, where they produced inferior results.
-(Figure \ref{fig:coverageByRegionRegimenWithSliding}.)
-
-Due to the non-superiority of regimens based on statewide recent-years analysis, we did not evaluate regimens based on regional recent-years data.
 
@@
 
+% TODO bring back discussion of cost from draft 1?
+
 % TODO proofread references
+
+\end{multicols}
 
@@
 
-\end{multicols}
-
 \end{document}

### 2018-01-16 Thesis/Thesis.rnw
Intro / conclusion edits

@@
 % TODO: Better calendrical cues in plots, maybe also with bars?
-% TODO: establish need in intro
-% TODO: adverse effects of immunoprophylaxis
 
@@
 
-\abstractsection{Background}Respiratory syncytial virus (RSV) causes seasonal respiratory infection with potentially serious complications in young infants.
-Immunoprophylaxis (palivizumab) is available, but costly.
+\abstractsection{Background}Respiratory syncytial virus (RSV) causes seasonal respiratory infection with potentially serious complications in children, leading to hospitalization rates as high as 50\% in high-risk infants.
+Safe and effective immunoprophylaxis (palivizumab) is available, but costly.
 The American Academy of Pediatrics (AAP) recommends palivizumab only for infants at high risk of complications, and only during the RSV season.
-Although the current AAP guidelines acknowledge the existence of spatial and temporal variation in RSV incidence, they do not recommend spatial or temporal adjustments to immunprophylaxis regimen outside of Florida.
+Although the current AAP guidelines acknowledge the existence of spatial and temporal variation in RSV incidence, they do not recommend spatial or temporal adjustments to immunoprophylaxis regimen outside of Florida.
 
@@
 
-In children, however, the infection often incites more serious respiratory illness, making RSV a leading cause of hospitalization among infants.\cite{Hall:2009gi,Hall:2013jo,Zhou:2012ho,Boyce:2000gz}
+In children, however, the infection often incites more serious respiratory illness --- with hospitalization rates as high as 4.4\% in infants with no comorbidities --- making RSV a leading cause of hospitalization among infants.\cite{Hall:2009gi,Hall:2013jo,Zhou:2012ho,Boyce:2000gz}
 
-Risk factors for serious illness and hospitalization due to RSV infection in children include prematurity, chronic lung disease of prematurity, congenital heart disease, anatomic pulmonary abnormalities, neuromuscular disorders, trisomy 21, immunocompromised status, and cystic fibrosis.
+Risk factors for serious illness and hospitalization due to RSV infection in children include prematurity, chronic lung disease of prematurity, congenital heart disease, anatomic pulmonary abnormalities, neuromuscular disorders, trisomy 21, and immunocompromised status.\cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
 
-Hospitalization rate of RSV-infected infants at high risk of complications is approximately 10\% in the populations in which it has been studied.
+Hospitalization rate of high-risk infants is anywhere from $2\times$ to $10\times$ higher than in infants with no comorbidities.\cite{Boyce:2000gz}
 
@@
 
-Palivizumab has been found to be effective in reducing hospitalizations due to RSV; in double-blinded trials in high-risk infants, it reduced hospitalization rate by 45-55\% compared to placebo.\cite{Group:1998ih,Feltes:2003wm}
+Palivizumab has been found to be effective in reducing hospitalizations due to RSV; in double-blinded trials in high-risk infants, it reduced hospitalization rate by 45-55\% compared to placebo.\cite{Group:1998ih,Feltes:2003wm} Its has also been found in clinical trials to be safe and well-tolerated.\cite{Group:1998ih}
 
@@
 
+\setcounter{figure}{3}
 \begin{figure*}[b]
@@
 \end{figure*}
+\setcounter{figure}{1}
 
@@
 
-Statewide, our model shows that \Sexpr{regionStrategyCoverage("all", "aap", 0)} of RSV cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) occur while palivizumab, administered according to the AAP guidelines, offers protection.
+Statewide, our model shows that \Sexpr{regionStrategyCoverage("all", "aap", 0)} of RSV cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) occur while palivizumab, administered per the AAP guidelines, offers protection.
 
-The AAP guidelines perform better in the low-RSV counties, where \Sexpr{regionStrategyCoverage("lowIncidence", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("lowIncidence", "aap", 0, level)}) occur during the prophylaxis time window, but worse in Fairfield county, where \Sexpr{regionStrategyCoverage("Fairfield", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("Fairfield", "aap", 0, level)}) occur during this time.
+The AAP guidelines perform better in the low-RSV counties, where \Sexpr{regionStrategyCoverage("lowIncidence", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("lowIncidence", "aap", 0, level)}) occur during the prophylaxis interval, but worse in Fairfield county, where \Sexpr{regionStrategyCoverage("Fairfield", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("Fairfield", "aap", 0, level)}) occur during this time.
 (Figure \ref{fig:coverageByRegionAAP}.)
 
-The cause of this is evident in Figure \ref{fig:coverageByRegionAAPInsight}, showing temporal misalignment between the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each region), and the time window of the AAP-recommended prophylaxis regimen.
+The cause of this is evident in Figure \ref{fig:coverageByRegionAAPInsight}, showing temporal misalignment between the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each region), and the timing of the AAP-recommended prophylaxis regimen.
 Fairfield county, owing to its early season onset, sees disproportionately many cases before prophylaxis administration begins; on the other hand, the low-RSV counties, owing to their late season onset and relatively shorter RSV seasons, see almost all of their RSV cases within the prophylaxis window.
@@
 \input{\figuresDir/coverageByRegionAAP.tex}
-\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis administered according to the AAP guidelines, by region}
+\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis administered per the AAP guidelines, by region}
 \label{fig:coverageByRegionAAP}
@@
 
-% TODO: Dan says state next paragraph more clearly, it's important
-
+\setcounter{figure}{4}
 \begin{figure*}
@@
 
+% TODO: Dan says state next paragraph more clearly, it's important
+
 Based on all-years data, the six spatially adjusted prophylaxis regimens (with no rounding of prophylaxis dates), when compared to the AAP guidelines, yield non-inferior results in all regions, and superior results both statewide and in Hartford county.
@@
 
-Statewide, the AAP guidelines offer protection for \Sexpr{regionStrategyCoverage("all", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}).
+Statewide, the AAP guidelines offer protection to \Sexpr{regionStrategyCoverage("all", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}).
 The regimen based on all-years statewide onset yields the smallest increase, to \Sexpr{regionStrategyCoverage("all", "stateOnset", 0)} (\Sexpr{regionStrategyCoverageCI("all", "stateOnset", 0, level)}); other alternate regimens yield similar results.
@@
 
+\setcounter{figure}{7}
 \begin{figure*}[!b]
@@
 
+\setcounter{figure}{6}
 \begin{figure}
@@
 
-Our analysis confirms regional variation of RSV season timing in Connecticut, defined by RSV season onset and offset, and observable at the county level.
-We have also shown a misalignment between the prophylaxis regimen recommended by the AAP and the timing of the RSV season in Fairfield County, resulting in the start of the RSV season occurring outside of the prophylaxis window.
+Our analysis confirms the existence of regional variation of RSV season timing in Connecticut (defined by RSV season onset and offset) observable at the county level.
 
-Our attempt to optimize timing of the prophylaxis regimen (without changing it duration and therefore its cost) shows a theoretical possibility of a 1-2\% increase in preventable RSV cases each year, occurring primarily in counties with a higher RSV burden (Fairfield, Hartford, and New Haven counties).
+We have also shown a misalignment between the prophylaxis regimen recommended by the AAP and the timing of the RSV season throughout Connecticut, with most counties RSV season starting before protection from the first dose of prophylaxis takes hold, and ending before protection from the last does wanes.
+This misalignment is particularly notable in Fairfield County, due to its notably early season onset.
 
-However, that theoretical improvement rapidly wanes when faced with practicalities of clinical practice guideline implementation; in order to derive real-world benefit from our analysis, clinical practice guidelines would need to be localized at the county level, and the timing of prophylaxis adjusted by less than a whole month in each region.
+Our attempt to optimize timing of the prophylaxis regimen (without changing its duration and therefore its cost) shows the possibility of a theoretical 1-2\% statewide decrease in RSV-associated hospitalizations among high-risk infants each year, occurring primarily in counties with higher RSV burden (Fairfield, Hartford, and New Haven counties).
 
-As a result, we conclude that the case for regional adjustment to RSV immunoprophylaxis guidelines is weak.
+However, the magnitude of that improvement wanes upon encountering practicalities of clinical practice guideline implementation.
+However, with clinical practice guidelines localized at the county level, and the timing of prophylaxis adjusted in each county by less than a whole month from the current AAP guidelines, we still found the potential for $\sim$1\% statewide decrease in RSV-associated hospitalizations among high risk infants.
 
-Although we found a weak statewide trend in RSV season onset becoming earlier over time, further analysis did not yield any improvements to prophylaxis based on that trend; the results of our temporal analysis were no stronger than the results of our spatial analysis.
-Since temporal variation in clinical guidelines would lead to a higher burden of implementation than spatial variation, we see no reason to base RSV immunoprophylaxis clinical practice guidelines on temporal variation in RSV reason timing.
+The prophylaxis regimen with which we were able to attain this improvement is the one in which prophylaxis in each county is timed to the midpoint of the RSV season (rounded to two weeks) in that county, which simultaneously reduces unprotected cases early in the season and ineffective prophylaxis late in the season.
 
-% TODO bring back discussion of cost from draft 1?
+However, increasing complexity of practice guidelines carries with it increased cost of implementation, such as training of clinicians and other healthcare workers.
+It is therefore not apparent from our research alone that the potential benefits would outweigh the costs.
 
-% TODO proofread references
+Finally, although we found a weak statewide trend in RSV season onset becoming earlier over time, further analysis did not yield any improvements to prophylaxis based on that trend.
+Since temporal variation in clinical guidelines would lead to a higher implementation burden than spatial variation, we see no reason to base RSV immunoprophylaxis clinical practice guidelines on temporal variation in RSV reason timing.
 

### 2018-01-16 Thesis/Thesis.rnw
Hyde hyperref links
Plot tweaks

@@
 % TODO: Better calendrical cues in plots, maybe also with bars?
+% TODO: Plot regression line in onset/offset analysis
 
@@
 
-\usepackage{hyperref}
+\usepackage[hidelinks]{hyperref}
 \usepackage[svgnames]{xcolor} % Must go before tikz and before structure.tex
@@
         geom_errorbar(aes(ymin=lower, ymax=upper, x=county), width=.1) + 
-        geom_point(aes(y=median, x=county)) + 
+        geom_point(aes(y=median, x=county), size=.75) + 
         geom_blank(data=limits, aes(y=min)) + 
@@
         geom_errorbar(aes(ymax=frac.upper, ymin=frac.lower, x=county), width=.1) + 
-        geom_point(aes(y=frac.median, x=county)) + 
+        geom_point(aes(y=frac.median, x=county), size=.75) + 
         scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
@@
             aes(ymin=frac.lower, ymax=frac.upper, x=rounding, color=strat, group=strat), 
-            width=.3, 
+            width=.25, 
             position=position_dodge(.5)
@@
         theme_light(base_size=plotTextBaseSize) +
-        geom_errorbar(aes(ymin=lower, ymax=upper, x=epiyear), width=.1) + 
-        geom_point(aes(y=median, x=epiyear)) +
+        geom_errorbar(aes(ymin=lower, ymax=upper, x=epiyear), width=.3) + 
+        geom_point(aes(y=median, x=epiyear), size=.75) +
         geom_blank(data=limits, aes(y=min)) + 

### 2018-01-16 Thesis/Thesis.rnw
A4 🤦‍♂️

@@
 
-\documentclass[10pt,a4paper]{article}
+\documentclass[10pt,letter]{article}
 
@@
 \floatplacement{figure}{H}
+\raggedcolumns
 
@@
 
-\includegraphics[height=2.5in]{EPH}
+\includegraphics[height=160pt]{EPH}
 \hspace{40pt}
-\includegraphics[height=2.5in]{Medicine}
+\includegraphics[height=160pt]{Medicine}
 
@@
 
-\begin{figure}
-\begin{center}
-\input{\figuresDir/map.tex}
-\caption{RSV case burden in Connecticut counties}
-\label{fig:map}
-\end{center}
-\end{figure}
-
 \subsection{Spatial aggregation of RSV incidence}
@@
 We chose to aggregate low-RSV counties into a single region because our analysis in those counties individually would have yielded results with unacceptably low statistical power.
+
+\begin{figure}
+\begin{center}
+\input{\figuresDir/map.tex}
+\caption{RSV case burden in Connecticut counties}
+\label{fig:map}
+\end{center}
+\end{figure}
 
@@
 
+\begin{figure}
+\begin{center}
+\input{\figuresDir/seasonByRegion.tex}
+\caption{RSV season onset and offset in Connecticut, by region}
+\label{fig:seasonByRegion}
+\end{center}
+\end{figure}
+
 \section{Results}
@@
 \begin{center}
-\input{\figuresDir/seasonByRegion.tex}
-\caption{RSV season onset and offset in Connecticut, by region}
-\label{fig:seasonByRegion}
+\input{\figuresDir/coverageByRegionAAP.tex}
+\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis administered per the AAP guidelines, by region}
+\label{fig:coverageByRegionAAP}
 \end{center}
@@
 
-The cause of this is evident in Figure \ref{fig:coverageByRegionAAPInsight}, showing temporal misalignment between the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each region), and the timing of the AAP-recommended prophylaxis regimen.
-Fairfield county, owing to its early season onset, sees disproportionately many cases before prophylaxis administration begins; on the other hand, the low-RSV counties, owing to their late season onset and relatively shorter RSV seasons, see almost all of their RSV cases within the prophylaxis window.
-
-\begin{figure}
-\begin{center}
-\input{\figuresDir/coverageByRegionAAP.tex}
-\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis administered per the AAP guidelines, by region}
-\label{fig:coverageByRegionAAP}
-\end{center}
-\end{figure}
+The cause of this is in temporal misalignment between the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each region), and the timing of the AAP-recommended prophylaxis regimen.
+(Figure \ref{fig:coverageByRegionAAPInsight}.) Fairfield county, owing to its early season onset, sees disproportionately many cases before prophylaxis administration begins; on the other hand, the low-RSV counties, owing to their late season onset and relatively shorter RSV seasons, see almost all of their RSV cases within the prophylaxis window.
 
@@
 \begin{figure*}
+\begin{center}
 \input{\figuresDir/coverageByRegionRegimen.tex}
@@
 \label{fig:coverageByRegionRegimen}
+\end{center}
 \end{figure*}
@@
 
-\begin{figure*}
-\begin{center}
-\input{\figuresDir/coverageByRoundingRegimen.tex}
-\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by calendrical rounding of prophylaxis regimen}
-\label{fig:coverageByRoundingRegimen}
-\end{center}
-\end{figure*}
-
-\setcounter{figure}{7}
-\begin{figure*}[!b]
-\begin{center}
-\input{\figuresDir/coverageByRegionRegimenWithSliding.tex}
-\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by region and prophylaxis regimen}
-\label{fig:coverageByRegionRegimenWithSliding}
-\end{center}
-\end{figure*}
+\columnbreak
 
@@
 
-After we applied weekly, biweekly, and monthly rounding to start and end dates of our six alternate immunoprophylaxis regimens, overall we found that longer rounding intervals diminished the net benefit of spatial analysis.
+After we applied weekly, biweekly, and monthly rounding to start and end dates of our six alternate immunoprophylaxis regimens, we found that longer rounding intervals diminished the benefit of spatial analysis.
+(Figure \ref{fig:coverageByRoundingRegimen}.)
 
@@
 With this rounding, all our regimens were non-superior to the AAP-recommended regimen in all regions.
+
+\begin{figure*}
+\begin{center}
+\input{\figuresDir/coverageByRoundingRegimen.tex}
+\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by calendrical rounding of prophylaxis regimen}
+\label{fig:coverageByRoundingRegimen}
+\end{center}
+\end{figure*}
+
+\columnbreak
 
@@
 
+\setcounter{figure}{6}
+\begin{figure}
+\begin{center}
+\input{\figuresDir/onsetOffsetByYear.tex}
+\caption{RSV season onset and offset in Connecticut, by three-year surseason}
+\label{fig:onsetOffsetByYear}
+\end{center}
+\end{figure}
+
 \paragraph{Temporally-adjusted prophylaxis regimens are non-superior to others}
@@
 
-Compared to our regional analysis, the three regimens based on statewide recent-years analysis produced non-superior results in all regions except for the low-RSV counties, where they produced inferior results.
+Compared to our regional analysis, the three regimens based on statewide recent-years analysis produced non-superior results everywhere, and inferior results in the low-RSV counties.
 (Figure \ref{fig:coverageByRegionRegimenWithSliding}.)
@@
 
-\setcounter{figure}{6}
-\begin{figure}
+\section{Discussion}
+
+\setcounter{figure}{7}
+\begin{figure*}
 \begin{center}
-\input{\figuresDir/onsetOffsetByYear.tex}
-\caption{RSV season onset and offset in Connecticut, by three-year surseason}
-\label{fig:onsetOffsetByYear}
+\input{\figuresDir/coverageByRegionRegimenWithSliding.tex}
+\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by region and prophylaxis regimen}
+\label{fig:coverageByRegionRegimenWithSliding}
 \end{center}
-\end{figure}
-
-\section{Discussion}
+\end{figure*}
 

### 2018-01-17 Analysis/RSV.Rmd
Install rgdal for maps

--- 2018-01-15 Analysis/RSV.Rmd
@@
 ```{r setup, include=FALSE, error=FALSE, warning=FALSE, message=FALSE}
-install.packages(c("dplyr", "zipcode", "reshape", "mgcv", "ggplot2", "gridExtra", "devtools", "data.table", "tikzDevice", "splitstackshape"))
+install.packages(c("dplyr", "zipcode", "reshape", "mgcv", "ggplot2", "gridExtra", "devtools", "data.table", "tikzDevice", "splitstackshape", "maps", "mapproj", "rgdal"))
 library(devtools)

### 2018-01-17 Thesis/Thesis.rnw
Plot month cues, abstract 1.5-spacing

@@
-% TODO: Better calendrical cues in plots, maybe also with bars?
 % TODO: Plot regression line in onset/offset analysis
@@
 \usepackage{textcomp}
+\usepackage{setspace}
 
@@
 \SetWatermarkLightness{.5}
-\SetWatermarkText{DRAFT 3}
+\SetWatermarkText{DRAFT 4}
 
@@
 \begin{hangparas}{\abstractindent}{1}
+\begin{onehalfspacing}
 
@@
 
+\end{onehalfspacing}
 \end{hangparas}
@@
 
-    ggplot(data) +
+    monthBarX = 0.5 + (0.5 - 5.5) * 0.04
+    monthGrob = function(month) {
+        textGrob(epiWeekLabels[month], just="right", gp=gpar(fontsize="6.4", col="grey30"))
+    }
+
+    plot = ggplot(data) +
         theme_light(base_size=plotTextBaseSize) +
@@
         scale_x_discrete(labels=countyLabels) + 
-        scale_y_continuous(minor_breaks=seq(1, 52), breaks=epiWeekBreaks, labels=epiWeekLabels) + 
+        scale_y_continuous(minor_breaks=seq(1, 52), breaks=epiWeekBreaks, labels=rep("\\qquad\\qquad", length(epiWeekBreaks))) + 
         labs(y=NULL) + 
+        annotation_custom(monthGrob(4), xmin=monthBarX, xmax=monthBarX, ymin=monthBoundaries$mid[4], ymax=monthBoundaries$mid[4]) + 
+        annotation_custom(monthGrob(5), xmin=monthBarX, xmax=monthBarX, ymin=monthBoundaries$mid[5], ymax=monthBoundaries$mid[5]) + 
+        annotation_custom(monthGrob(9), xmin=monthBarX, xmax=monthBarX, ymin=monthBoundaries$mid[9], ymax=monthBoundaries$mid[9]) + 
+        annotation_custom(monthGrob(10), xmin=monthBarX, xmax=monthBarX, ymin=monthBoundaries$mid[10], ymax=monthBoundaries$mid[10]) + 
         theme(
@@
             axis.ticks.x=element_blank(),
-            axis.ticks.y=element_blank(),
             axis.text.x=element_text(angle=30, hjust=1)
         )
+
+	plotGrob = ggplotGrob(plot)
+	plotGrob$layout$clip[grepl("panel", plotGrob$layout$name)] <- "off"
+	grid.draw(plotGrob)
+
     dev.off()
@@
 
-    ggplot(data) +
+    monthBarX = 1998.5 + (1998.5 - 2013.5) * 0.04
+
+    plot = ggplot(data) +
         theme_light(base_size=plotTextBaseSize) +
@@
         scale_x_continuous(breaks=seq(1990, 2020, by=5)) +
-        scale_y_continuous(minor_breaks=seq(1, 52), breaks=epiWeekBreaks, labels=epiWeekLabels) + 
+        scale_y_continuous(minor_breaks=seq(1, 52), breaks=epiWeekBreaks, labels=rep("\\qquad\\qquad", length(epiWeekBreaks))) + 
+        annotation_custom(monthGrob(4), xmin=monthBarX, xmax=monthBarX, ymin=monthBoundaries$mid[4], ymax=monthBoundaries$mid[4]) + 
+        annotation_custom(monthGrob(5), xmin=monthBarX, xmax=monthBarX, ymin=monthBoundaries$mid[5], ymax=monthBoundaries$mid[5]) + 
+        annotation_custom(monthGrob(9), xmin=monthBarX, xmax=monthBarX, ymin=monthBoundaries$mid[9], ymax=monthBoundaries$mid[9]) + 
+        annotation_custom(monthGrob(10), xmin=monthBarX, xmax=monthBarX, ymin=monthBoundaries$mid[10], ymax=monthBoundaries$mid[10]) + 
         labs(y=NULL) + 
@@
             panel.grid.minor.y=element_line(size=rel(2)),
-            axis.ticks.y=element_blank(),
             axis.title.x=element_blank()
         )
+
+	plotGrob = ggplotGrob(plot)
+	plotGrob$layout$clip[grepl("panel", plotGrob$layout$name)] <- "off"
+	grid.draw(plotGrob)
+
     dev.off()

### 2018-01-17 Thesis/Thesis.R

@@ -124,6 +124,24 @@ countyLabels = c(
 epiWeekBreaks = c(3.01, 7.25, 11.75, 16.01, 20.25, 24.75, 29.01, 33.01, 37.5, 42.01, 46.25, 50.75)
 epiWeekLabels = c("Jul", "Aug", "Sep", "Oct", "Nov", "Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun")
 
+breaks.df = data.frame(i=seq(1, 12), mid=epiWeekBreaks)
+monthBoundaries = breaks.df %>%
+  inner_join(
+    breaks.df %>% mutate(i=i %% 12 + 1) %>% rename(prevMid=mid),
+    by="i"
+  ) %>%
+  inner_join(
+    breaks.df %>% mutate(i=(i - 2) %% 12 + 1) %>% rename(nextMid=mid),
+    by="i"
+  ) %>%
+  mutate(
+    min=prevMid + (mid - prevMid) %% 52 / 2,
+    max=mid + (nextMid - mid) %% 52 / 2
+  ) %>%
+  select(i, min, mid, max)
+
+epiWeekBreaks = sort(unique(c(monthBoundaries$min, monthBoundaries$max)))
+
 legendLabels = function(labels, size="") {
   as.vector(sapply(labels, function(label) {
     sprintf("%s%s%s\\qquad\\qquad", size, ifelse(nchar(size) > 0, " ", ""), label)

### 2018-01-18 Thesis/Thesis.rnw
Minor cleanup

@@
 % TODO: Plot regression line in onset/offset analysis
+% TODO Erin: CL vs CI in abstract?
+% TODO clarify all years analysis in figure captions
+% TODO generally make figures stand more on their own
+% TODO Put 1-2% punchline in the abstract, maybe
+% TODO mention misalignment in results
 
@@
 
+% TODO reword next paragraph
+
 \abstractsection{Results}At \Sexpr{level * 100}\% confidence level, we found that, when it comes to the fraction of RSV cases preventable by an immunoprophylaxis regimen, regimens adjusted for spatial variation in incidence at the county level have superior preventable fraction (than the AAP-recommended regimen) in some regions of Connecticut, and non-inferior preventable fraction in other regions.
@@
 
-Our goal was to construct a model of annual RSV incidence that allows us to easily estimate complex characteristics of RSV seasons, such as season onset and offset, or preventable RSV case fraction.
+Our goal was to construct a model of annual RSV incidence that allows us to easily estimate complex characteristics of RSV seasons, such as season onset and offset.
 
@@
 % TODO: Dan says state next paragraph more clearly, it's important
+% TODO: Hartford county is a lie
 
@@
 The increase was most notable in Fairfield and Hartford counties.
+
+% TODO data not shown
 
@@
 
-Similarly, we assumed the protection by palivizumab is constant at 100\% throughout the protection period; however, not only is breakthrough RSV illness known to occur in patients on palivizumab, but it is an indication for discontinuing the remained of the prophylaxis regimen.
+Similarly, we assumed the protection by palivizumab is constant at 100\% throughout the protection period; however, not only is breakthrough RSV illness known to occur in patients on palivizumab, but it is an indication for discontinuing the remainder of the prophylaxis regimen.
 

### 2018-01-18 Thesis/Thesis.rnw
Assorted improvements to figures for clarity; various minor text edits

@@
 \SetWatermarkLightness{.5}
-\SetWatermarkText{DRAFT 4}
+\SetWatermarkText{DRAFT 5}
 
@@
 
-\abstractsection{Methods}We describe a generalized additive model of RSV incidence using cubic cyclic penalized splines and apply that model to hospital admissions records from Connecticut between \Sexpr{formatDate(startDate)} and \Sexpr{formatDate(endDate)} to estimate the fraction of RSV cases in Connecticut preventable by immunoprophylaxis administered according to the AAP guidelines.
-We also formulate several alternate immunoprophylaxis regimens with the same net pharmaceutical cost, and estimate the fraction preventable by those alternate regimens.
+\abstractsection{Methods}We describe a generalized additive model of RSV incidence using cubic cyclic penalized splines and apply that model to hospital admissions in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)}.
+We use the model to estimate the fraction of all RSV cases in Connecticut that occurs while immunoprophylaxis, administered according to the AAP guidelines, offers protection from RSV infection (``preventable fraction'').
+We also formulate several alternate immunoprophylaxis regimens, with the same net pharmaceutical cost as the AAP-recommended regimen, and similarly estimate their preventable fraction.
 
@@
 
-\abstractsection{Results}At \Sexpr{level * 100}\% confidence level, we found that, when it comes to the fraction of RSV cases preventable by an immunoprophylaxis regimen, regimens adjusted for spatial variation in incidence at the county level have superior preventable fraction (than the AAP-recommended regimen) in some regions of Connecticut, and non-inferior preventable fraction in other regions.
-However, when those regimens were modified to accommodate practicable calendrical boundaries (weekly, biweekly, and monthly), their gains rapidly diminished.
+\abstractsection{Results}Using preventable fraction to assess different immunoprophylaxis regimens, we found that (at \Sexpr{level * 100}\% confidence level), regimens adjusted for county-level variation in RSV incidence are superior to the AAP-recommended regimen.
+When we rounded the timing of those regimens to pragmatic calendrical boundaries (weekly, biweekly, and monthly), their gains over the AAP regimen diminished to.
 
-\abstractpara{}We also found that alternate regimens adjusted for temporal variation in incidence at the annual level to have non-superior preventable fraction to our spatially-adjusted regimens.
+\abstractpara{}Our best-performing spatially-adjusted pragmatic alternate to the AAP guidelines was the one based on regional RSV season midpoint with biweekly rounding.
+In comparison to the AAP recommendation, whose preventable fraction is \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}), our best alternate yields improvement to \Sexpr{regionStrategyCoverage("all", "countyMiddle", 2)} (\Sexpr{regionStrategyCoverageCI("all", "countyMiddle", 2, level)}) preventable fraction.
 
-\abstractpara{}Overall, we found our best-performing spatially-adjusted practicable alternate to the AAP guidelines to be based on regional RSV season midpoint with biweekly rounding, and to provide a statewide increase in preventable fraction from \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) to \Sexpr{regionStrategyCoverage("all", "countyMiddle", 2)} (\Sexpr{regionStrategyCoverageCI("all", "countyMiddle", 2, level)}).
+\abstractpara{}We also found that alternate regimens adjusted for temporal variation in incidence at the annual level have non-superior preventable fraction to our spatially-adjusted regimens.
 
-\abstractsection{Conclusion}We conclude that the increased preventable fraction provided by prophylaxis regimens based on our county-level spatial analysis warrants further analysis to determine whether the potential reduction in hospitalization rate is nullified by the potential increase in implementation cost.
+\abstractsection{Conclusion}We conclude that the increased preventable fraction provided by prophylaxis regimens based on our county-level spatial analysis warrants further analysis to determine whether the potential reduction in hospitalizations is nullified by the potential increase in implementation cost.
 Our temporal analysis at the annual level showed no additional benefit beyond the spatial analysis, while simultaneously increasing implementation complexity.
@@
 
-In children, however, the infection often incites more serious respiratory illness --- with hospitalization rates as high as 4.4\% in infants with no comorbidities --- making RSV a leading cause of hospitalization among infants.\cite{Hall:2009gi,Hall:2013jo,Zhou:2012ho,Boyce:2000gz}
+However, RSV infection often incites more serious respiratory illness in children, with hospitalization rates as high as 4.4\% in infants with no comorbidities, making RSV a leading cause of hospitalization among infants.\cite{Hall:2009gi,Hall:2013jo,Zhou:2012ho,Boyce:2000gz}
 
-Risk factors for serious illness and hospitalization due to RSV infection in children include prematurity, chronic lung disease of prematurity, congenital heart disease, anatomic pulmonary abnormalities, neuromuscular disorders, trisomy 21, and immunocompromised status.\cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
+For infants, risk factors of serious illness and hospitalization due to RSV infection include prematurity, chronic lung disease of prematurity, congenital heart disease, anatomic pulmonary abnormalities, neuromuscular disorders, trisomy 21, and immunocompromised status.\cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
 
-Hospitalization rate of high-risk infants is anywhere from $2\times$ to $10\times$ higher than in infants with no comorbidities.\cite{Boyce:2000gz}
+Hospitalization rate due to RSV among high-risk infants is anywhere from $2\times$ to $10\times$ higher than among infants with no comorbidities.\cite{Boyce:2000gz}
 
-\subsection{Respiratory syncytial virus seasonality}
+\subsection{RSV seasonality}
 
-RSV seasonality has been established throughout the United States, with a stable onset between mid-November and early January and a stable offset between mid-March and late April in all states except for Florida, based on National Respiratory and Enteric Virus Surveillance System data.\cite{CentersforDiseaseControlandPreventionCDC:2011wt,CentersforDiseaseControlandPreventionCDC:2013wv}
+RSV seasonality has been established throughout the United States, based on National Respiratory and Enteric Virus Surveillance System data.
+In all states except for Florida, it shows a stable season onset between mid-November and early January and a stable season offset between mid-March and late April in all states except for Florida.\cite{CentersforDiseaseControlandPreventionCDC:2011wt,CentersforDiseaseControlandPreventionCDC:2013wv}
 
@@
 
-Immunoprophylaxis with palivizumab, a monoclonal antibody medication, has been approved for prevention of RSV infection since 1998.
-Palivizumab is administered via intramuscular injection, and requires monthly dosing.\cite{Andabaka:2013dr} Its price is \$1500-\$3000 per dose.\cite{Hampp:2011ju}
+Immunoprophylaxis with palivizumab, a monoclonal antibody medication, has been approved in the US for prevention of RSV infection since 1998.
+Palivizumab is administered via intramuscular injection and requires five monthly doses, priced at \$1500-\$3000 per dose.\cite{Hampp:2011ju,Andabaka:2013dr}
 
-Palivizumab has been found to be effective in reducing hospitalizations due to RSV; in double-blinded trials in high-risk infants, it reduced hospitalization rate by 45-55\% compared to placebo.\cite{Group:1998ih,Feltes:2003wm} Its has also been found in clinical trials to be safe and well-tolerated.\cite{Group:1998ih}
+Palivizumab has been found to be effective in reducing hospitalizations due to RSV; in double-blinded trials in high-risk infants, it reduced hospitalization rate by 45-55\% compared to placebo.\cite{Group:1998ih,Feltes:2003wm} Its has also been found to be safe and well-tolerated in clinical trials.\cite{Group:1998ih}
 
@@
 
-In their guidelines, the AAP acknowledges the potential significance of spatial and temporal variation in RSV incidence, but does not recommend local variance from nation-wide prophylaxis guidelines outside of Florida.\cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
+In their guidelines, the AAP acknowledges the potential significance of spatial and temporal variation in RSV incidence, but --- outside of Florida --- does not recommend local variance from nation-wide prophylaxis guidelines.\cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
 
@@
 
-Motivated by AAP's recognition of the impact of spatial variation in RSV incidence on optimizing RSV immunoprophylaxis regimens, and the known spatial variability of RSV incidence in Connecticut, our study asks these questions:
+Motivated by the AAP's recognition of the impact of spatial variation in RSV incidence on optimizing RSV immunoprophylaxis regimens, and the known spatial variability of RSV incidence in Connecticut, our study asks these questions:
 
@@
 	\item To what extent does regional variability of RSV incidence in Connecticut impact the effectiveness of the AAP-recommended prophylaxis regimen?
-	\item Can we use spatial analysis of RSV to propose alternate regimens, either statewide or regional, that would regionally improve effectiveness over AAP-recommended prophylaxis, without increasing the total cost of the prophylactics the regimen?
+	\item Can we use spatial analysis of RSV to propose alternate regimens that would increase the benefits of prophylaxis in comparison to the AAP-recommended regimen, without increasing the total cost of the prophylactics the regimen?
 	\item Is there year-to-year variation in timing of RSV season in Connecticut?
@@
 \end{itemize}
+
+The study was approved by the Human Investigation Committees at Yale University and the CT DPH. The authors assume full responsibility for analyses and interpretation of the data obtained from CT DPH.
 
@@
 
-We identified \Sexpr{nrow(dataset)} hospitalization coded as RSV in Connecticut between \Sexpr{formatDate(startDate)} and \Sexpr{formatDate(endDate)}.
-
-The cases were identified from the hospitalization database maintained by the OHCA, who provided us with weekly hospitalization statistics.
-
-The study was approved by the Human Investigation Committees at Yale University and the CT DPH. The authors assume full responsibility for analyses and interpretation of the data obtained from CT DPH.
-
-We defined a case of RSV to be a hospital stay recorded in the OHCA hospitalization database meeting for which:
+We defined an RSV-associated hospitalization in Connecticut to be a hospital stay for which:
 
 \begin{itemize}
-    \item date of hospital admission was between \Sexpr{formatDate(startDate)} and \Sexpr{formatDate(endDate)} (inclusive),
-    \item postal code of residence listed in patient's medical record was in Connecticut\footnote{According to the zipcode $\rightarrow$ state mapping in R \texttt{zipcode} package version 1.0}, and
-    \item hospital stay was associated with ICD-9-CM diagnosis code \texttt{079.6} (RSV), \texttt{466.11} (Acute bronchiolitis due to RSV), or \texttt{480.1} (Pneumonia due to RSV).
+    \item the postal code of residence listed in patient's medical record was in Connecticut\footnote{According to the zipcode $\rightarrow$ state mapping in R \texttt{zipcode} package version 1.0}, and
+    \item the hospital stay was associated with ICD-9-CM diagnosis code \texttt{079.6} (RSV), \texttt{466.11} (Acute bronchiolitis due to RSV), or \texttt{480.1} (Pneumonia due to RSV).
 \end{itemize}
+
+Using the OHCA weekly hospitalization statistics, we identified \Sexpr{nrow(dataset)} RSV-associated hospitalizations in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)} (inclusive).
+
+% TODO patient age
 
@@
 
-Given that RSV seasons peak early in each calendar year, to each surveillance year we assigned 12 months of data starting in July of previous year.
+Given that RSV seasons peak early in each calendar year, we assigned to each surveillance year 12 months of data starting in July of previous year.
 
-OHCA data was provided grouped by Monday-Sunday calendar week; we assigned the first full calendar week of July to be surveillance week 1.
+OHCA provided us with hospitalization records aggregated into Monday-Sunday calendar weeks; we assigned the first full calendar week of July to be surveillance week 1 in each surveillance year.
 
@@
 
-We were willing to assume that RSV incidence is the result of a Poisson process whose log can be modeled as a piecewise twice-differentiable function of time.
+We were willing to assume that RSV incidence is the result of a Poisson process whose $\log$ can be modeled as a piecewise twice-differentiable function of time.
 
@@
         theme_light(base_size=plotTextBaseSize) +
-        scale_fill_manual(labels=legendLabels(c("$<$50", "$>$100")), values=twoTone) +
+        scale_fill_manual(labels=legendLabels(c("$<$50", "$>$100")), values=twoToneAlt) +
         geom_polygon(aes(fill=highRSV, group=group), color="white", size=.5) +
@@
 
-For our spatial analysis, we aggregated RSV incidence data across all years in our data set. We then spatially aggregated the data to form five regions (Figure \ref{fig:map}):
+For our spatial analysis, we aggregated RSV incidence data between \Sexpr{formatYear(startDate)} and \Sexpr{formatYear(endDate)} into five regions:
 
@@
     \item One region for the entire state
-    \item One region for each of the counties with high case counts of RSV: Hartford County, Fairfield County, and New Haven County.
-    \item One discontiguous region comprised of all remaining counties in Connecticut: \Sexpr{gsub("(.*), (.*)", "\\1, and \\2", paste(lowIncidenceCounties, collapse=", "))} (``low-RSV counties'')
+    \item One region for each of the counties with high RSV case counts: Hartford County, Fairfield County, and New Haven County. (Figure \ref{fig:map})
+    \item One discontiguous region comprised of all remaining counties in Connecticut: \Sexpr{gsub("(.*), (.*)", "\\1, and \\2", paste(lowIncidenceCounties, collapse=", "))} (``low-RSV counties'').
 \end{itemize}
@@
 \input{\figuresDir/map.tex}
-\caption{RSV case burden in Connecticut counties}
+\caption{Subdivision of Connecticut into high-RSV and low-RSV counties}
 \label{fig:map}
@@
 
-\subsection{Estimating RSV fraction preventable by AAP-recommended prophylaxis}
+\subsection{Evaluating the AAP prophylaxis recommendation}
 
 We began by assessing the current AAP RSV prophylaxis guidelines.
-These guidelines recommend RSV prophylaxis with 6 monthly doses of palivizumab, starting in November, for all high-risk infants in their first year of life; in the second year of life, only some subgroups are recommended to receive palivizumab.
+These guidelines recommend RSV prophylaxis with 5 monthly doses of palivizumab, starting in November, for all high-risk infants in their first year of life; in the second year of life, only some subgroups are recommended to receive palivizumab.
 
@@
 
-We defined fraction of RSV cases preventable by a prophylaxis regimen (``preventable fraction'') to be the fraction of high-risk infants who would be exposed to RSV while they are protected by palivizumab.
+We defined the fraction of all RSV cases that is preventable by a prophylaxis regimen (``preventable fraction'') to be the ratio of
 
-Given that high-risk infants are a small fraction of the general population (citation needed), we assumed that our model for RSV incidence based on hospitalization data of all infants is an unbiased estimate of RSV incidence among unprotected high-risk infants.
+\begin{itemize}
+\item the number of RSV-associated hospitalizations that occur while the prophylaxis regimen offers protection to those who receive prophylaxis as scheduled, and
+\item the total number of RSV-associated hospitalizations.
+\end{itemize}
+
+Given that high-risk infants are a small subgroup of the general population (citation needed), we assumed that our model of RSV hospitalizations among all infants is an unbiased approximation of RSV hospitalizations among high-risk infants, and that, therefore, the preventable fraction of a prophylactic regimen is an unbiased estimate of the fraction of high-risk infants who benefit from prophylaxis.
 
@@
 
-We then turned our attention to spatial variation of seasonal RSV patterns across the time period covered by our data.
+We then turned our attention to spatial variation of seasonal RSV patterns between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)}.
 In particular, we defined season onset as the time when cumulative incidence rises beyond \Sexpr{seasonThreshold * 100}\% of the total cumulative incidence, and season offset as the time when cumulative incidence rises beyond \Sexpr{(1 - seasonThreshold) * 100}\% of the total cumulative incidence.
@@
 
-The choice of \Sexpr{seasonThreshold * 100}\% and \Sexpr{(1 - seasonThreshold) * 100}\% incidence thresholds was based on our intent to use estimates of RSV season onset and offset to put forth alternate prophylaxis regimens (as described below), while maintaining 6-month dosing schedule (and therefore not increasing medication cost).
-Incidence cutoffs other than \Sexpr{seasonThreshold * 100}\% and \Sexpr{(1 - seasonThreshold) * 100}\% were briefly investigated, but quickly ruled out because they produced prophylaxis regimens starting weeks prior to RSV season onset or ending weeks after RSV season offset.
+The choice of \Sexpr{seasonThreshold * 100}\% and \Sexpr{(1 - seasonThreshold) * 100}\% incidence thresholds was based on our intent to use estimates of RSV season onset and offset to put forth alternate prophylaxis regimens (as described below), while maintaining 5-month dosing schedule (and therefore not increasing medication cost).
+Incidence cutoffs other than \Sexpr{seasonThreshold * 100}\% and \Sexpr{(1 - seasonThreshold) * 100}\% were briefly investigated, but quickly ruled out because they produced prophylaxis regimens starting long prior to RSV season onset or ending long after RSV season offset, and therefore had very low preventable fractions.
 
-\subsection{Evaluating alternate all-years prophylaxis regimens}
+\subsection{Evaluating spatially-adjusted prophylaxis regimens}
 
-Following this analysis, we estimated the regional and statewide preventable fraction for six alternate spatially adjusted prophylaxis regimens:
+Following this analysis, we estimated the regional and statewide preventable fraction for six spatially adjusted prophylaxis regimens:
 
@@
 Our analysis thus far assumed that RSV seasons are similar year-to-year.
-To analyze the effects on prophylaxis regimens of year-to-year variation between RSV seasons, we chose to aggregate our data into (overlapping) runs of three consecutive seasons --- in order to maintain a higher level of statistical power, as well as to limit impact of short-term variation on our results.
+To analyze the effects on prophylaxis regimens of year-to-year variation between RSV seasons, we chose to aggregate our data into (overlapping) periods of three consecutive years --- in order to maintain a higher level of statistical power, as well as to limit impact of short-term variation on our results.
 
-This gave us \Sexpr{year(endDate) - year(startDate) -1} ``surseasons'', with the \Sexpr{formatYear(startDate + 2*365)} surseason covering \Sexpr{formatYear(startDate)} through \Sexpr{formatYear(startDate + 2*365)} surveillance year, and the \Sexpr{formatYear(endDate)} surseason covering \Sexpr{formatYear(endDate - 2*365)} through \Sexpr{formatYear(endDate)}.
+This gave us \Sexpr{year(endDate) - year(startDate) -1} three-year periods, with the \Sexpr{formatYear(startDate + 2*365)} period covering surveillance years \Sexpr{formatYear(startDate)} through \Sexpr{formatYear(startDate + 2*365)}, and the \Sexpr{formatYear(endDate)} period covering \Sexpr{formatYear(endDate - 2*365)} through \Sexpr{formatYear(endDate)}.
 
-We began our temporal analysis by estimating onset and offset for each surseason, using the same penalized spline GAM as all-years analysis, producing --- as before --- statewide and regional estimates of \Sexpr{seasonThreshold * 100}\% onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset.
+We began our temporal analysis by estimating onset and offset for each three-year period, using the same penalized spline GAM as all-years analysis, producing --- as before --- statewide and regional estimates of \Sexpr{seasonThreshold * 100}\% onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset.
 
-To evaluate year-to-year variation in RSV season onset and offset we modeled median RSV surseason onset and offset against surseason year using simple linear regression.
+To evaluate year-to-year variation in RSV season onset and offset we modeled median RSV three-year onset and offset against time using simple linear regression.
 
@@
 Finally, to assess the impact of any long-term trends in RSV season timing on prophylaxis, we evaluated three additional prophylaxis regimens.
-Here, each prophylaxis regimen is adjusted annually based on RSV data from the preceding surseason:
+Here, each prophylaxis regimen is adjusted annually based on RSV data from the preceding three-year period:
 
@@
 
-We then compared those regimens to the one recommended by AAP and to the alternates we previously devised based on spatial analysis.
-
-As before, these alternate regimens involved five monthly doses of palivizumab giving 24 weeks of protection.
-
-% \uselengthunit{in}\printlength{\columnwidth}
-% column width = 3.20929 in
-
 \setcounter{figure}{3}
@@
 \input{\figuresDir/coverageByRegionAAPInsight.tex}
-\caption{RSV relative cumulative incidence in Connecticut, by region}
+\caption[Regional variation in the relative timing of the RSV season in Connecticut and the AAP-recommended prophylaxis regimen]{Regional variation in the relative timing of the RSV season in Connecticut and the AAP-recommended prophylaxis regimen, showing the gap between season onset and prophylaxis start date, notable particularly in Fairfield county}
 \label{fig:coverageByRegionAAPInsight}
@@
 \input{\figuresDir/seasonByRegion.tex}
-\caption{RSV season onset and offset in Connecticut, by region}
+\caption{Regional variation in RSV season onset and offset in Connecticut}
 \label{fig:seasonByRegion}
@@
 \end{figure}
+
+We then compared those regimens to the one recommended by AAP and to the six spatially-adjusted alternates (with no calendrical rounding) discussed above.
+
+As before, these alternate regimens involved five monthly doses of palivizumab giving 24 weeks of protection.
+
+% \uselengthunit{in}\printlength{\columnwidth}
+% column width = 3.20929 in
 
@@
 
-Meanwhile, in comparison with the statewide RSV season onset and offset, the low-RSV region has RSV season with later onset at \Sexpr{regionOnset("lowIncidence")} weeks (\Sexpr{regionOnsetCI("all", level)} weeks); season offset shows no change from the statewide median.
-(Figure \ref{fig:seasonByRegion}.)
-
 \begin{figure}
@@
 \input{\figuresDir/coverageByRegionAAP.tex}
-\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis administered per the AAP guidelines, by region}
+\caption[Regional variation in the fraction of RSV hospitalizations occurring while the AAP-recommended RSV prophylaxis is active]{Regional variation in the fraction of RSV hospitalizations occurring while when protection by palivizumab --- when administered per the AAP guidelines ---  is active}
 \label{fig:coverageByRegionAAP}
@@
 \end{figure}
+
+Meanwhile, in comparison with the statewide RSV season onset and offset, the low-RSV region has RSV season with later onset at \Sexpr{regionOnset("lowIncidence")} weeks (\Sexpr{regionOnsetCI("all", level)} weeks); season offset shows no change from the statewide median.
+(Figure \ref{fig:seasonByRegion}.)
 
@@
         scale_x_continuous(breaks=epiWeekBreaks, labels=epiWeekLabels, limits=c(1, 52)) + 
-        scale_color_manual(labels=spanLabels, values=twoTone) +
-        scale_fill_manual(labels=spanLabels, values=twoTone) +
+        scale_color_manual(labels=spanLabels, values=twoToneAlt) +
+        scale_fill_manual(labels=spanLabels, values=twoToneAlt) +
         guides(color=guide_legend(keywidth=3, keyheight=.4)) + 
         facet_wrap(~county, ncol=5, labeller=labeller(county=countyLabels)) +
-        labs(x=NULL) + 
+        labs(x=NULL, y="Cumulative indicence fraction") + 
         theme(
@@
 Statewide, our model shows that \Sexpr{regionStrategyCoverage("all", "aap", 0)} of RSV cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) occur while palivizumab, administered per the AAP guidelines, offers protection.
+
+\setcounter{figure}{4}
+\begin{figure*}
+\begin{center}
+\input{\figuresDir/coverageByRegionRegimen.tex}
+\caption[Comparison of six spatially-adjusted RSV prophylaxis regimens to the AAP-recommended regimen]{Comparison of six spatially-adjusted RSV prophylaxis regimens to the AAP-recommended regimen, showing statewide superiority and regional non-inferiority of spatially-adjusted regimens.
+Preventable fraction: the fraction of all RSV-associated hospitalizations occurring while the prophylaxis regimen provides protection against RSV}
+\label{fig:coverageByRegionRegimen}
+\end{center}
+\end{figure*}
 
@@
 
-\setcounter{figure}{4}
-\begin{figure*}
-\begin{center}
-\input{\figuresDir/coverageByRegionRegimen.tex}
-\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by region and prophylaxis regimen}
-\label{fig:coverageByRegionRegimen}
-\end{center}
-\end{figure*}
+% TODO: Dan says state next paragraph more clearly, it's important
 
-% TODO: Dan says state next paragraph more clearly, it's important
-% TODO: Hartford county is a lie
-
-Based on all-years data, the six spatially adjusted prophylaxis regimens (with no rounding of prophylaxis dates), when compared to the AAP guidelines, yield non-inferior results in all regions, and superior results both statewide and in Hartford county.
+Based on all-years data, the six spatially adjusted prophylaxis regimens (with no rounding of prophylaxis dates), when compared to the AAP guidelines, yield non-inferior results in all regions, and superior results statewide.
 (Figure \ref{fig:coverageByRegionRegimen}.)
@@
 Statewide, the AAP guidelines offer protection to \Sexpr{regionStrategyCoverage("all", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}).
-The regimen based on all-years statewide onset yields the smallest increase, to \Sexpr{regionStrategyCoverage("all", "stateOnset", 0)} (\Sexpr{regionStrategyCoverageCI("all", "stateOnset", 0, level)}); other alternate regimens yield similar results.
+The alternate regimen based on all-years statewide onset yields the smallest increase, to \Sexpr{regionStrategyCoverage("all", "stateOnset", 0)} (\Sexpr{regionStrategyCoverageCI("all", "stateOnset", 0, level)}); other alternate regimens yield similar results.
 
-Most of the increase comes from Hartford county, where the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", 0, level)}).
-The regimen based on all-years regional offset generates the smallest increase, to \Sexpr{regionStrategyCoverage("Hartford", "countyOffset", 0)} (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", 0, level)}); other alternate regimens are comparable.
-
-\columnbreak
+Most of the increase comes from Hartford county, where the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", 0, level)}), whereas the alternate regimen based on all-years regional offset generates the smallest increase, to \Sexpr{regionStrategyCoverage("Hartford", "countyOffset", 0)} (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", 0, level)}); other alternate regimens are comparable.
 
@@
 With weekly rounding, our regimens were non-inferior to the AAP recommendation, and produced an increase in preventable fraction from AAP's \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) to \Sexpr{bestCaseCoverage(1)} (\Sexpr{bestCaseCoverageCI(1, level)}) statewide.
-The increase was most notable in Fairfield and Hartford counties.
-
-% TODO data not shown
 
 Biweekly rounding yielded regimens similarly non-inferior to the AAP recommendation, with an increase in preventable fraction to \Sexpr{bestCaseCoverage(2)} (\Sexpr{bestCaseCoverageCI(2, level)}) statewide.
-The increase was most notable in Fairfield and New Haven counties.
 
 However, with monthly rounding, the gains almost completely vanished, with preventable fraction not exceeding \Sexpr{bestCaseCoverage(4)} (\Sexpr{bestCaseCoverageCI(4, level)}).
-With this rounding, all our regimens were non-superior to the AAP-recommended regimen in all regions.
+Furthermore, all our regimens with monthly rounding were non-superior to the AAP-recommended regimen in all regions.
 
@@
 \input{\figuresDir/coverageByRoundingRegimen.tex}
-\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by calendrical rounding of prophylaxis regimen}
+\caption[The effect of calendrical rounding of start and end of RSV prophylaxis regimens on their performance]{The effect of calendrical rounding of start and end of RSV prophylaxis regimens on their performance, showing that longer rounding intervals diminish the benefits of using an alternate regimen over the existing AAP-recommended regimen.
+Preventable fraction: the fraction of all RSV hospitalizations occurring while the prophylaxis regimen offers protection}
 \label{fig:coverageByRoundingRegimen}
@@
 
-Our linear regression of median surseason onset and offset against surseason year (Figure \ref{fig:onsetOffsetByYear}) indicates that season onset has slowly been drifting earlier, at a rate of \Sexpr{formatDrift(onsetByYear)} (\Sexpr{formatDriftCI(onsetByYear, level)}).
-It is unclear whether this is a part of a larger pattern, such as a cycle spanning decades.
+Our linear regression of median RSV season onset and offset over three-year periods indicates that season onset has slowly been drifting earlier, at a rate of \Sexpr{formatDrift(onsetByYear)} (\Sexpr{formatDriftCI(onsetByYear, level)}).
+(Figure \ref{fig:onsetOffsetByYear}) It is unclear whether this is a part of a larger pattern, such as a cycle spanning decades.
 
@@
 \input{\figuresDir/onsetOffsetByYear.tex}
-\caption{RSV season onset and offset in Connecticut, by three-year surseason}
+\caption{Annual variability in RSV season onset and offset in Connecticut}
 \label{fig:onsetOffsetByYear}
@@
 \paragraph{Temporally-adjusted prophylaxis regimens are non-superior to others}
+
+% TODO third color
 
@@
         scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
-        scale_color_manual(labels=stratLabels[c(seq(1, 3), seq(7, 10))], values=c(rep(twoTone, each=3), grey(0))) + 
+        scale_color_manual(labels=stratLabels[c(seq(1, 3), seq(7, 10))], values=c(rep(twoToneAlt, each=3), grey(0))) + 
         geom_errorbar(
@@
 
-Compared to our regional analysis, the three regimens based on statewide recent-years analysis produced non-superior results everywhere, and inferior results in the low-RSV counties.
+Compared to our regional all-years analysis, the three regimens based on statewide recent-years analysis produced non-superior results everywhere, and inferior results in the low-RSV counties.
 (Figure \ref{fig:coverageByRegionRegimenWithSliding}.)
@@
 \input{\figuresDir/coverageByRegionRegimenWithSliding.tex}
-\caption{Fraction of RSV cases occurring in Connecticut during the protection window of palivizumab prophylaxis, by region and prophylaxis regimen}
+\caption[Comparison of prophylaxis regimens based on all-years data to those based on recent-years data]{Comparison of prophylaxis regimens based on all-years data to those based on recent-years data, showing temporal analysis adds no benefit over spatial analysis alone.
+Preventable fraction: fraction of RSV hospitalizations occurring while while the prophylaxis regimen offers protection}
 \label{fig:coverageByRegionRegimenWithSliding}
@@
 
-In areas of Connecticut associated with relatively high amount of interstate travel (such as urban centers near the state lines), our analysis --- by only considering residents of Connecticut --- likely underestimates RSV burden.
+In areas of Connecticut associated with a relatively high amount of interstate travel (such as urban centers near the state lines), our analysis --- by only considering residents of Connecticut --- likely underestimates RSV burden.
 
-Similarly, towns that see substantial intercounty travel (for example, employment hubs near county lines) likely bias our estimates towards higher counts in high-population counties.
+Similarly, towns that see substantial inter-county travel (for example, employment hubs near county lines) likely bias our regional analysis.
 
@@
 
-We have also shown a misalignment between the prophylaxis regimen recommended by the AAP and the timing of the RSV season throughout Connecticut, with most counties RSV season starting before protection from the first dose of prophylaxis takes hold, and ending before protection from the last does wanes.
+We have also shown a misalignment between the prophylaxis regimen recommended by the AAP and the timing of the RSV season throughout Connecticut, with most counties' RSV season starting before protection from the first dose of prophylaxis takes hold, and ending before protection from the last dose wanes.
 This misalignment is particularly notable in Fairfield County, due to its notably early season onset.
@@
 However, the magnitude of that improvement wanes upon encountering practicalities of clinical practice guideline implementation.
-However, with clinical practice guidelines localized at the county level, and the timing of prophylaxis adjusted in each county by less than a whole month from the current AAP guidelines, we still found the potential for $\sim$1\% statewide decrease in RSV-associated hospitalizations among high risk infants.
+Nonetheless, with clinical practice guidelines localized at the county level, and the timing of prophylaxis adjusted in each county by less than a whole month from the current AAP guidelines, we still found the potential for $\sim$1\% statewide decrease in RSV-associated hospitalizations among high risk infants.
 
-The prophylaxis regimen with which we were able to attain this improvement is the one in which prophylaxis in each county is timed to the midpoint of the RSV season (rounded to two weeks) in that county, which simultaneously reduces unprotected cases early in the season and ineffective prophylaxis late in the season.
+The prophylaxis regimen with which we were able to attain this improvement is the one in which prophylaxis in each county is timed relative to the midpoint of the RSV season (rounded to two weeks) in that county, which simultaneously reduces unprotected cases early in the season and ineffective prophylaxis late in the season.
 

### 2018-01-18 Thesis/Thesis.R

@@ -18,11 +18,15 @@ plotTextBaseSize = 8
 
 # Formatting utilities
 formatDate = function(date) {
-  format(date, "%B, %d, %Y")
+  format(date, "%B, %e, %Y")
 }
 
 formatYear = function(date) {
   format(date, "%Y")
+}
+
+formatMonth = function(date) {
+  format(date, "%B %Y")
 }
 
 formatThreshold = function(threshold) {
@@ -148,7 +152,8 @@ legendLabels = function(labels, size="") {
   }))
 }
 
-twoTone = c("#f1a340", "#998ec3")
+twoTone = c("#018571", "#80cdc1")
+twoToneAlt = c("#018571", "#a6611a")
 
 # Counties which we plot (so, not individual low-incidence counties)
 countiesForPlots = thresholdsByCounty$county[!thresholdsByCounty$county %in% lowIncidenceCounties]

### 2018-01-20 Thesis/Thesis.R
Better rounding labels

@@ -114,7 +114,7 @@ onsetOffsetLabeller = labeller(
   variable=c(`onset` = "RSV season onset", `offset` = "RSV season offset")
 )
 
-roundingLabels = c(`0` = "No rounding", `1` = "Weekly", `2` = "Biweekly", `4` = "Monthly")
+roundingLabels = c(`0` = "No rounding", `1` = "Weekly rounding", `2` = "Biweekly rounding", `4` = "Monthly rounding")
 
 countyLabels = c(
   `all` = "Statewide",

### 2018-01-20 Thesis/Thesis.R
Fixed month min/max calculation

@@ -1,4 +1,6 @@
 # ---- util ----
+library(magrittr)
+library(rgeos)
 library(grid)
 library(tikzDevice)
 library(rgdal)
@@ -139,7 +141,7 @@ monthBoundaries = breaks.df %>%
     by="i"
   ) %>%
   mutate(
-    min=prevMid + (mid - prevMid) %% 52 / 2,
+    min=(prevMid + (mid - prevMid) %% 52 / 2) %% 52,
     max=mid + (nextMid - mid) %% 52 / 2
   ) %>%
   select(i, min, mid, max)

### 2018-01-20 Analysis/RSV.Rmd
Install rgeos

--- 2018-01-15 Analysis/RSV.Rmd
@@
 ```{r setup, include=FALSE, error=FALSE, warning=FALSE, message=FALSE}
-install.packages(c("dplyr", "zipcode", "reshape", "mgcv", "ggplot2", "gridExtra", "devtools", "data.table", "tikzDevice", "splitstackshape"))
+install.packages(c("dplyr", "zipcode", "reshape", "mgcv", "ggplot2", "gridExtra", "devtools", "data.table", "tikzDevice", "splitstackshape", "maps", "mapproj", "rgdal", "rgeos"))
 library(devtools)

### 2018-01-20 Thesis/Thesis.rnw
Improved figures, wording tweaks

@@
 
-In their guidelines, the AAP acknowledges the potential significance of spatial and temporal variation in RSV incidence, but --- outside of Florida --- does not recommend local variance from nation-wide prophylaxis guidelines.\cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
+The AAP acknowledges the potential significance of spatial and temporal variation in RSV incidence, but --- outside of Florida --- does not recommend local variance from nation-wide prophylaxis guidelines.\cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
 
@@
 \input{\figuresDir/coverageByRegionAAP.tex}
-\caption[Regional variation in the fraction of RSV hospitalizations occurring while the AAP-recommended RSV prophylaxis is active]{Regional variation in the fraction of RSV hospitalizations occurring while when protection by palivizumab --- when administered per the AAP guidelines ---  is active}
+\caption[Regional variation in the fraction of RSV hospitalizations occurring while the AAP-recommended RSV prophylaxis is active]{Regional variation in the fraction of RSV hospitalizations occurring while protection by palivizumab --- administered per the AAP guidelines ---  is active}
 \label{fig:coverageByRegionAAP}
@@
         geom_ribbon(aes(ymin=rsv.cum.fit.lower, ymax=rsv.cum.fit.upper, x=time), fill=grey(.25)) +
-    	geom_segment(aes(x=start, y=lineYmin, xend=start, yend=lineYmax, color=variable), linetype="11", data=spans) + 
-    	geom_segment(aes(x=end, y=lineYmin, xend=end, yend=lineYmax, color=variable), linetype="11", data=spans) + 
-    	geom_rect(aes(xmin=start, ymin=barYmin, xmax=end, ymax=barYmax, fill=variable, color=variable), data=spans) + 
-    	geom_segment(aes(x=-Inf, y=unprotected.start, xend=ppx.start, yend=unprotected.start), linetype=3, data=thresholds) + 
-        geom_segment(aes(x=-Inf, y=unprotected.end, xend=ppx.end, yend=unprotected.end), linetype=3, data=thresholds) + 
-        scale_y_continuous(labels=latexPercent, breaks=seq(0, 1, by=.2), limits=c(-0.1, 1.1), expand=c(0, 0)) +
-        scale_x_continuous(breaks=epiWeekBreaks, labels=epiWeekLabels, limits=c(1, 52)) + 
+    	geom_segment(aes(x=start, y=lineYmin, xend=start, yend=lineYmax, color=variable), data=spans, size=.375) + 
+    	geom_segment(aes(x=end, y=lineYmin, xend=end, yend=lineYmax, color=variable), data=spans, size=.375) + 
+    	geom_rect(aes(xmin=start, ymin=barYmin, xmax=end, ymax=barYmax, fill=variable, color=variable), data=spans, size=.375) + 
+    	geom_segment(aes(x=-Inf, y=unprotected.start, xend=ppx.start, yend=unprotected.start), linetype="11", data=thresholds, size=.375) + 
+        geom_segment(aes(x=-Inf, y=unprotected.end, xend=ppx.end, yend=unprotected.end), linetype="11", data=thresholds, size=.375) + 
+        geom_point(aes(x=min(monthBoundaries$min), y=unprotected.end), data=thresholds, shape=18) + 
+        geom_point(aes(x=min(monthBoundaries$min), y=unprotected.start), data=thresholds, shape=18) + 
+        scale_y_continuous(labels=latexPercent, breaks=seq(0, 1, by=.2), limits=c(-0.1, 1.1), expand=c(0, 0), minor_breaks=epiWeekBreaks) +
+        scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, limits=range(c(monthBoundaries$min, monthBoundaries$max)), expand=c(0, 0)) + 
         scale_color_manual(labels=spanLabels, values=twoToneAlt) +
@@
             panel.grid.major.x=element_blank(),
-            panel.grid.minor.x=element_blank(),
             legend.title=element_blank(),
@@
         scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
-        scale_color_manual(labels=stratLabels[c(seq(1, 6), 10)], values=c(rep(twoTone, each=3), grey(0))) + 
+        scale_color_manual(name="Prophylaxis regimen", labels=stratLabels[c(seq(1, 6), 10)], values=c(rep(twoTone, each=3), grey(0))) + 
+        scale_shape_manual(name="Prophylaxis regimen", labels=stratLabels[c(seq(1, 6), 10)], values=c(15, 16, 17, 15, 16, 17, 15)) + 
         geom_errorbar(
@@
         ) + 
-        geom_point(aes(y=frac.median, x=county, color=strat), position=position_dodge(.5), size=.75) +
+        geom_point(aes(y=frac.median, x=county, color=strat, shape=strat), position=position_dodge(.5), size=.75) +
         labs(y="Preventable fraction", color="Prophylaxis regimen") +
@@
         scale_y_continuous(labels=latexPercent, limits=c(0.90, 1.00), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
-        scale_color_manual(labels=stratLabels[c(seq(1, 6), 10)], values=c(rep(twoTone, each=3), grey(0))) + 
+        scale_color_manual(name="Prophylaxis regimen", labels=stratLabels[c(seq(1, 6), 10)], values=c(rep(twoTone, each=3), grey(0))) + 
+        scale_shape_manual(name="Prophylaxis regimen", labels=stratLabels[c(seq(1, 6), 10)], values=c(15, 16, 17, 15, 16, 17, 15)) + 
         scale_x_discrete(labels=roundingLabels) + 
@@
         ) + 
-        geom_point(aes(y=frac.median, x=rounding, color=strat), position=position_dodge(.5), size=.75) +
-        labs(x="Calendrical rounding", y="Preventable fraction", color="Prophylaxis regimen") +
+        geom_point(aes(y=frac.median, x=rounding, color=strat, shape=strat), position=position_dodge(.5), size=.75) +
+        labs(x="Calendrical rounding", y="Preventable fraction") +
         guides(color=guide_legend(keywidth=3, keyheight=1, ncol=3)) + 
@@
 \input{\figuresDir/coverageByRoundingRegimen.tex}
-\caption[The effect of calendrical rounding of start and end of RSV prophylaxis regimens on their performance]{The effect of calendrical rounding of start and end of RSV prophylaxis regimens on their performance, showing that longer rounding intervals diminish the benefits of using an alternate regimen over the existing AAP-recommended regimen.
+\caption[The effect of calendrical rounding of start and end of spatially adjusted RSV prophylaxis regimens on their performance]{The effect of calendrical rounding of start and end of spatially adjusted RSV prophylaxis regimens on their performance, showing that longer rounding intervals diminish the benefits of alternate regimens over the AAP-recommended regimen.
 Preventable fraction: the fraction of all RSV hospitalizations occurring while the prophylaxis regimen offers protection}
@@
         scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
-        scale_color_manual(labels=stratLabels[c(seq(1, 3), seq(7, 10))], values=c(rep(twoToneAlt, each=3), grey(0))) + 
+        scale_color_manual(name="Prophylaxis regimen", labels=stratLabels[c(seq(1, 3), seq(7, 10))], values=c(rep(twoToneAlt, each=3), grey(0))) + 
+        scale_shape_manual(name="Prophylaxis regimen", labels=stratLabels[c(seq(1, 3), seq(7, 10))], values=c(15, 16, 17, 15, 16, 17, 15)) + 
         geom_errorbar(
@@
         ) + 
-        geom_point(aes(y=frac.median, x=county, color=strat), position=position_dodge(.5), size=.75) +
-        labs(y="Preventable fraction", color="Prophylaxis regimen") +
+        geom_point(aes(y=frac.median, x=county, color=strat, shape=strat), position=position_dodge(.5), size=.75) +
+        labs(y="Preventable fraction") +
         guides(color=guide_legend(keywidth=3, keyheight=1, ncol=3)) + 
@@
 \caption[Comparison of prophylaxis regimens based on all-years data to those based on recent-years data]{Comparison of prophylaxis regimens based on all-years data to those based on recent-years data, showing temporal analysis adds no benefit over spatial analysis alone.
-Preventable fraction: fraction of RSV hospitalizations occurring while while the prophylaxis regimen offers protection}
+Preventable fraction: fraction of RSV hospitalizations occurring while the prophylaxis regimen offers protection}
 \label{fig:coverageByRegionRegimenWithSliding}
@@
 
-Similarly, we assumed the protection by palivizumab is constant at 100\% throughout the protection period; however, not only is breakthrough RSV illness known to occur in patients on palivizumab, but it is an indication for discontinuing the remainder of the prophylaxis regimen.
+Similarly, we assumed the protection by palivizumab is constant at 100\% throughout the protection period; however, not only is breakthrough RSV illness known to occur in patients on palivizumab, but it is an indication for discontinuing the prophylaxis regimen.
 
@@
 
-Our attempt to optimize timing of the prophylaxis regimen (without changing its duration and therefore its cost) shows the possibility of a theoretical 1-2\% statewide decrease in RSV-associated hospitalizations among high-risk infants each year, occurring primarily in counties with higher RSV burden (Fairfield, Hartford, and New Haven counties).
+Our attempt to optimize timing of the prophylaxis regimen (without changing its duration and therefore its cost) shows the possibility of a theoretical 1-2\% statewide decrease in RSV-associated hospitalizations among high-risk infants each year, primarily in counties with higher RSV burden (Fairfield, Hartford, and New Haven counties).
 

### 2018-01-21 Thesis/Thesis.rnw
Secondary axis for epi weeks; text tweaks

@@
 % TODO: Plot regression line in onset/offset analysis
-% TODO Erin: CL vs CI in abstract?
 % TODO clarify all years analysis in figure captions
-% TODO generally make figures stand more on their own
 % TODO Put 1-2% punchline in the abstract, maybe
-% TODO mention misalignment in results
 
@@
 
-\abstractsection{Background}Respiratory syncytial virus (RSV) causes seasonal respiratory infection with potentially serious complications in children, leading to hospitalization rates as high as 50\% in high-risk infants.
+\abstractsection{Background}Respiratory syncytial virus (RSV) causes seasonal respiratory infection with potentially serious complications in children, and leads to hospitalization rates as high as 50\% in high-risk infants.
 Safe and effective immunoprophylaxis (palivizumab) is available, but costly.
@@
 Although the current AAP guidelines acknowledge the existence of spatial and temporal variation in RSV incidence, they do not recommend spatial or temporal adjustments to immunoprophylaxis regimen outside of Florida.
+
+% TODO: connect better to next paragraph (In order to determine if CT is also variable)
 
@@
 \abstractsection{Results}Using preventable fraction to assess different immunoprophylaxis regimens, we found that (at \Sexpr{level * 100}\% confidence level), regimens adjusted for county-level variation in RSV incidence are superior to the AAP-recommended regimen.
-When we rounded the timing of those regimens to pragmatic calendrical boundaries (weekly, biweekly, and monthly), their gains over the AAP regimen diminished to.
+When we rounded the timing of those regimens to pragmatic calendrical boundaries (weekly, biweekly, and monthly), their gains over the AAP regimen diminished.
 
-\abstractpara{}Our best-performing spatially-adjusted pragmatic alternate to the AAP guidelines was the one based on regional RSV season midpoint with biweekly rounding.
+\abstractpara{}Our best-performing spatially adjusted pragmatic alternate to the AAP guidelines was the one based on regional RSV season midpoint with biweekly rounding.
 In comparison to the AAP recommendation, whose preventable fraction is \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}), our best alternate yields improvement to \Sexpr{regionStrategyCoverage("all", "countyMiddle", 2)} (\Sexpr{regionStrategyCoverageCI("all", "countyMiddle", 2, level)}) preventable fraction.
 
-\abstractpara{}We also found that alternate regimens adjusted for temporal variation in incidence at the annual level have non-superior preventable fraction to our spatially-adjusted regimens.
+\abstractpara{}We also found that alternate regimens adjusted for temporal variation in incidence at the annual level have non-superior preventable fraction to our spatially adjusted regimens.
 
@@
 RSV seasonality has been established throughout the United States, based on National Respiratory and Enteric Virus Surveillance System data.
-In all states except for Florida, it shows a stable season onset between mid-November and early January and a stable season offset between mid-March and late April in all states except for Florida.\cite{CentersforDiseaseControlandPreventionCDC:2011wt,CentersforDiseaseControlandPreventionCDC:2013wv}
+In all states except for Florida, it shows a stable season onset between mid-November and early January and a stable season offset between mid-March and late April.\cite{CentersforDiseaseControlandPreventionCDC:2011wt,CentersforDiseaseControlandPreventionCDC:2013wv}
 
@@
 
-Motivated by the AAP's recognition of the impact of spatial variation in RSV incidence on optimizing RSV immunoprophylaxis regimens, and the known spatial variability of RSV incidence in Connecticut, our study asks these questions:
+Motivated by the AAP's recognition of the significance of spatial variation in formulating prophylaxis guidelines, and the known spatial variability of RSV incidence in Connecticut, we aim to determine whether spatial and temporal variability can be used to optimize RSV prophylaxis in Connecticut by asking these questions:
 
@@
     \item One region for the entire state
-    \item One region for each of the counties with high RSV case counts: Hartford County, Fairfield County, and New Haven County. (Figure \ref{fig:map})
+    \item One region for each of the counties with high RSV case counts: Hartford County, Fairfield County, and New Haven County. (Figure \ref{fig:map}.)
     \item One discontiguous region comprised of all remaining counties in Connecticut: \Sexpr{gsub("(.*), (.*)", "\\1, and \\2", paste(lowIncidenceCounties, collapse=", "))} (``low-RSV counties'').
@@
 
+%TODO citation needed
+
 Given that high-risk infants are a small subgroup of the general population (citation needed), we assumed that our model of RSV hospitalizations among all infants is an unbiased approximation of RSV hospitalizations among high-risk infants, and that, therefore, the preventable fraction of a prophylactic regimen is an unbiased estimate of the fraction of high-risk infants who benefit from prophylaxis.
@@
 
-\subsection{Evaluating spatially-adjusted prophylaxis regimens}
+\subsection{Evaluating spatially adjusted prophylaxis regimens}
 
@@
 
-In each variant, we again estimated the preventable fraction of all six spatially-adjusted regimens.
+In each variant, we again estimated the preventable fraction of all six spatially adjusted regimens.
 
@@
 
-We then compared those regimens to the one recommended by AAP and to the six spatially-adjusted alternates (with no calendrical rounding) discussed above.
+We then compared those regimens to the one recommended by AAP and to the six spatially adjusted alternates (with no calendrical rounding) discussed above.
 
@@
         scale_x_discrete(labels=countyLabels) + 
-        scale_y_continuous(minor_breaks=seq(1, 52), breaks=epiWeekBreaks, labels=rep("\\qquad\\qquad", length(epiWeekBreaks))) + 
+        scale_y_continuous(minor_breaks=seq(1, 52), breaks=epiWeekBreaks, labels=rep("\\qquad\\qquad", length(epiWeekBreaks)), sec.axis=sec_axis(trans=~., breaks=seq(1, 52))) + 
         labs(y=NULL) + 
@@
         geom_point(aes(x=min(monthBoundaries$min), y=unprotected.start), data=thresholds, shape=18) + 
-        scale_y_continuous(labels=latexPercent, breaks=seq(0, 1, by=.2), limits=c(-0.1, 1.1), expand=c(0, 0), minor_breaks=epiWeekBreaks) +
+        scale_y_continuous(labels=latexPercent, breaks=seq(0, 1, by=.2), limits=c(-0.1, 1.1), expand=c(0, 0)) +
         scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, limits=range(c(monthBoundaries$min, monthBoundaries$max)), expand=c(0, 0)) + 
@@
 \input{\figuresDir/coverageByRegionRegimen.tex}
-\caption[Comparison of six spatially-adjusted RSV prophylaxis regimens to the AAP-recommended regimen]{Comparison of six spatially-adjusted RSV prophylaxis regimens to the AAP-recommended regimen, showing statewide superiority and regional non-inferiority of spatially-adjusted regimens.
-Preventable fraction: the fraction of all RSV-associated hospitalizations occurring while the prophylaxis regimen provides protection against RSV}
+\caption[Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen]{Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen, showing statewide superiority and regional non-inferiority of spatially adjusted regimens.
+Preventable fraction: the fraction of all RSV-associated hospitalizations occurring while the prophylaxis regimen provides protection}
 \label{fig:coverageByRegionRegimen}
@@
 
-The cause of this is in temporal misalignment between the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each region), and the timing of the AAP-recommended prophylaxis regimen.
+This is caused by temporal misalignment between the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each region), and the timing of the AAP-recommended prophylaxis regimen.
 (Figure \ref{fig:coverageByRegionAAPInsight}.) Fairfield county, owing to its early season onset, sees disproportionately many cases before prophylaxis administration begins; on the other hand, the low-RSV counties, owing to their late season onset and relatively shorter RSV seasons, see almost all of their RSV cases within the prophylaxis window.
 
-\paragraph{Spatially-adjusted regimens are superior to the AAP recommendations}
+\paragraph{Spatially adjusted regimens are superior to the AAP recommendations}
 
@@
         scale_x_continuous(breaks=seq(1990, 2020, by=5)) +
-        scale_y_continuous(minor_breaks=seq(1, 52), breaks=epiWeekBreaks, labels=rep("\\qquad\\qquad", length(epiWeekBreaks))) + 
+        scale_y_continuous(minor_breaks=seq(1, 52), breaks=epiWeekBreaks, labels=rep("\\qquad\\qquad", length(epiWeekBreaks)), sec.axis=sec_axis(trans=~., breaks=seq(1, 52))) + 
         annotation_custom(monthGrob(4), xmin=monthBarX, xmax=monthBarX, ymin=monthBoundaries$mid[4], ymax=monthBoundaries$mid[4]) + 
@@
 Our linear regression of median RSV season onset and offset over three-year periods indicates that season onset has slowly been drifting earlier, at a rate of \Sexpr{formatDrift(onsetByYear)} (\Sexpr{formatDriftCI(onsetByYear, level)}).
-(Figure \ref{fig:onsetOffsetByYear}) It is unclear whether this is a part of a larger pattern, such as a cycle spanning decades.
+(Figure \ref{fig:onsetOffsetByYear}.) It is unclear whether this is a part of a larger pattern, such as a cycle spanning decades.
 
@@
 
-Although we were able to reach some conclusions about the impact of calendrical rounding on spatially-adjusted prophylaxis regimens, ultimately our analysis is hamstrung by weekly aggregation of hospital admission data in our initial data.
+Although we were able to reach some conclusions about the impact of calendrical rounding on spatially adjusted prophylaxis regimens, ultimately our analysis is hamstrung by weekly aggregation of hospital admission data in our initial data.
 To properly propose and evaluate any fine-tuning to RSV prophylaxis guidelines, we recommend use of daily data.
@@
 
+% TODO Revisit
+
 Our analysis confirms the existence of regional variation of RSV season timing in Connecticut (defined by RSV season onset and offset) observable at the county level.
 
-We have also shown a misalignment between the prophylaxis regimen recommended by the AAP and the timing of the RSV season throughout Connecticut, with most counties' RSV season starting before protection from the first dose of prophylaxis takes hold, and ending before protection from the last dose wanes.
-This misalignment is particularly notable in Fairfield County, due to its notably early season onset.
+Furthermore, we have shown a misalignment between the prophylaxis schedule recommended by the AAP and the timing of the RSV season throughout Connecticut, with most counties' RSV season starting before protection from the first dose of prophylaxis takes hold, and ending before protection from the last dose wanes.
+This misalignment is particularly notable in Fairfield County, due to its early season onset.
 
@@
 
-However, increasing complexity of practice guidelines carries with it increased cost of implementation, such as training of clinicians and other healthcare workers.
+Increasing complexity of practice guidelines carries with it increased cost of implementation, such as training of clinicians and other healthcare workers.
 It is therefore not apparent from our research alone that the potential benefits would outweigh the costs.
@@
 Finally, although we found a weak statewide trend in RSV season onset becoming earlier over time, further analysis did not yield any improvements to prophylaxis based on that trend.
-Since temporal variation in clinical guidelines would lead to a higher implementation burden than spatial variation, we see no reason to base RSV immunoprophylaxis clinical practice guidelines on temporal variation in RSV reason timing.
+Since temporal variation in clinical guidelines would lead to a higher implementation burden than spatial variation, we see no reason to base RSV immunoprophylaxis clinical practice guidelines on temporal variation in RSV season timing.
 

### 2018-01-24 Thesis/Thesis.rnw
Final tweaks, removed draft watermark

@@
 % TODO Put 1-2% punchline in the abstract, maybe
+% TODO So it turns out that several regimens are actually the same, and that the best regional regimen @ 2w rounding is actually the same as the best statewide regimen @ 2w rounding.
+As a result, the conclusion could be simplified to statewide 2w rounding.
+% TODO paragraphs
 
@@
 \usepackage{tikz}
-\usepackage{draftwatermark}
-\SetWatermarkScale{1}
-\SetWatermarkAngle{45}
-\SetWatermarkFontSize{4ex}
-\SetWatermarkHorCenter{12ex}
-\SetWatermarkVerCenter{12ex}
-\SetWatermarkLightness{.5}
-\SetWatermarkText{DRAFT 5}
+%\usepackage{draftwatermark}
+%\SetWatermarkScale{1}
+%\SetWatermarkAngle{45}
+%\SetWatermarkFontSize{4ex}
+%\SetWatermarkHorCenter{12ex}
+%\SetWatermarkVerCenter{12ex}
+%\SetWatermarkLightness{.5}
+%\SetWatermarkText{DRAFT 5}
 
@@
 Although the current AAP guidelines acknowledge the existence of spatial and temporal variation in RSV incidence, they do not recommend spatial or temporal adjustments to immunoprophylaxis regimen outside of Florida.
-
-% TODO: connect better to next paragraph (In order to determine if CT is also variable)
+In this study, we investigate the value of using spatial and temporal variation in RSV incidence to adjust the RSV prophylaxis regimen in Connecticut.
 
 \abstractsection{Methods}We describe a generalized additive model of RSV incidence using cubic cyclic penalized splines and apply that model to hospital admissions in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)}.
-We use the model to estimate the fraction of all RSV cases in Connecticut that occurs while immunoprophylaxis, administered according to the AAP guidelines, offers protection from RSV infection (``preventable fraction'').
-We also formulate several alternate immunoprophylaxis regimens, with the same net pharmaceutical cost as the AAP-recommended regimen, and similarly estimate their preventable fraction.
+We use the model to estimate the fraction of all RSV cases in Connecticut occurring while immunoprophylaxis (administered according to the AAP guidelines) offers protection from RSV infection (``preventable fraction'').
+We also formulate several alternative immunoprophylaxis regimens, with the same net pharmaceutical cost as the AAP-recommended regimen, and similarly estimate their preventable fraction.
 
-% TODO reword next paragraph
+\abstractsection{Results}Using preventable fraction to assess different immunoprophylaxis regimens, we found that regimens adjusted for county-level variation in timing of RSV seasons are superior to the current AAP-recommended regimen.
+We also considered the effect of rounding the timing of the first dose of prophylaxis to pragmatic calendrical boundaries (weekly, biweekly, and monthly), and found that benefits of alternative regimens over the AAP-recommended regimen persisted with biweekly rounding, but not with monthly rounding.
+Our best-performing pragmatic alternative to the AAP guidelines was based on the regional RSV season midpoint with biweekly rounding.
+In comparison to the AAP recommendation, whose preventable fraction is \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}), that alternative yielded improvement to preventable fraction of \Sexpr{regionStrategyCoverage("all", "countyMiddle", 2)} (\Sexpr{regionStrategyCoverageCI("all", "countyMiddle", 2, level)}).
+We also found that alternative regimens adjusted for annual variation in RSV season are non-superior to spatially adjusted regimens.
 
-\abstractsection{Results}Using preventable fraction to assess different immunoprophylaxis regimens, we found that (at \Sexpr{level * 100}\% confidence level), regimens adjusted for county-level variation in RSV incidence are superior to the AAP-recommended regimen.
-When we rounded the timing of those regimens to pragmatic calendrical boundaries (weekly, biweekly, and monthly), their gains over the AAP regimen diminished.
+\abstractsection{Conclusion}Overall, we recommend county-level spatial analysis of RSV incidence as the starting point for RSV immunoprophylaxis optimization in Connecticut.
+However, the potential reduction in RSV hospitalizations should be weighed against the potential increase in implementation cost.
 
-\abstractpara{}Our best-performing spatially adjusted pragmatic alternate to the AAP guidelines was the one based on regional RSV season midpoint with biweekly rounding.
-In comparison to the AAP recommendation, whose preventable fraction is \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}), our best alternate yields improvement to \Sexpr{regionStrategyCoverage("all", "countyMiddle", 2)} (\Sexpr{regionStrategyCoverageCI("all", "countyMiddle", 2, level)}) preventable fraction.
-
-\abstractpara{}We also found that alternate regimens adjusted for temporal variation in incidence at the annual level have non-superior preventable fraction to our spatially adjusted regimens.
-
-\abstractsection{Conclusion}We conclude that the increased preventable fraction provided by prophylaxis regimens based on our county-level spatial analysis warrants further analysis to determine whether the potential reduction in hospitalizations is nullified by the potential increase in implementation cost.
-Our temporal analysis at the annual level showed no additional benefit beyond the spatial analysis, while simultaneously increasing implementation complexity.
-
-\abstractpara{}Overall, we recommend county-level spatial analysis of RSV incidence as the starting point for RSV immunoprophylaxis optimization in Connecticut.
+\abstractpara{}
 
@@
 
-Respiratory syncytial virus (RSV) causes upper respiratory infections in humans of all ages. In adults, RSV infection is typically asymptomatic or gives rise to mild respiratory illness.
-
+Respiratory syncytial virus (RSV) causes upper respiratory infections in humans of all ages.
+In adults, RSV infection is typically asymptomatic or gives rise to mild respiratory illness.
 However, RSV infection often incites more serious respiratory illness in children, with hospitalization rates as high as 4.4\% in infants with no comorbidities, making RSV a leading cause of hospitalization among infants.\cite{Hall:2009gi,Hall:2013jo,Zhou:2012ho,Boyce:2000gz}
 
-For infants, risk factors of serious illness and hospitalization due to RSV infection include prematurity, chronic lung disease of prematurity, congenital heart disease, anatomic pulmonary abnormalities, neuromuscular disorders, trisomy 21, and immunocompromised status.\cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
-
-Hospitalization rate due to RSV among high-risk infants is anywhere from $2\times$ to $10\times$ higher than among infants with no comorbidities.\cite{Boyce:2000gz}
-
-\subsection{RSV seasonality}
-
-RSV seasonality has been established throughout the United States, based on National Respiratory and Enteric Virus Surveillance System data.
-In all states except for Florida, it shows a stable season onset between mid-November and early January and a stable season offset between mid-March and late April.\cite{CentersforDiseaseControlandPreventionCDC:2011wt,CentersforDiseaseControlandPreventionCDC:2013wv}
+For infants, risk factors of serious illness and hospitalization due to RSV infection include prematurity, chronic lung disease of prematurity, congenital heart disease, anatomic pulmonary abnormalities, neuromuscular disorders, trisomy 21, and immunocompromised status.\cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj} Hospitalization rate due to RSV among high-risk infants is anywhere from two to ten times higher than among infants with no comorbidities.\cite{Boyce:2000gz}
 
@@
 
-Owing to the high cost, the American Academy of Pediatrics (AAP) recommends palivizumab immunoprophylaxis only for high-risk infants, and only during RSV season.\cite{Anonymous:1998up,AmericanAcademyofPediatricsCommitteeonInfectiousDiseasesandCommitteeonFetusandNewborn:2003ug,AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj} These guidelines were most recently revised in 2014.
+Owing to the high cost, the American Academy of Pediatrics (AAP) guidelines, revised in 2014, recommend palivizumab immunoprophylaxis only for high-risk infants, and only during RSV season.\cite{Anonymous:1998up,AmericanAcademyofPediatricsCommitteeonInfectiousDiseasesandCommitteeonFetusandNewborn:2003ug,AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
+
+\subsection{RSV seasonality}
+
+RSV seasonality has been established throughout the United States, based on National Respiratory and Enteric Virus Surveillance System data.
+In all states except for Florida, it shows a stable season onset between mid-November and early January and a stable season offset between mid-March and late April.\cite{CentersforDiseaseControlandPreventionCDC:2011wt,CentersforDiseaseControlandPreventionCDC:2013wv} RSV season in Florida begins approximately two months earlier than in other states.
+\cite{CentersforDiseaseControlandPreventionCDC:2013wv}
 
@@
 
-The Department of Public Health of the state of Connecticut (CT DPH), via its Office of Health Care Access (OHCA), maintains a database of all hospitalizations in every non-federal short-stay acute-care general hospital in the state.
-Previous analysis of this database at the Yale University School of Public Health has shown regional variability in time of peak RSV incidence within Connecticut.\cite{Noveroske:y4fi3188}
-
-No prior research is available regarding year-to-year variation in timing of RSV season in Connecticut.
+In Connecticut, the Department of Public Health (CT DPH), via its Office of Health Care Access (OHCA), maintains a database of all hospitalizations in every non-federal short-stay acute-care general hospital in the state.
+Previous analysis of this database at the Yale University School of Public Health has shown regional variability in time of peak RSV incidence within Connecticut.\cite{Noveroske:y4fi3188} No prior research is available regarding year-to-year variation in timing of RSV season in Connecticut.
 
@@
 	\item To what extent does regional variability of RSV incidence in Connecticut impact the effectiveness of the AAP-recommended prophylaxis regimen?
-	\item Can we use spatial analysis of RSV to propose alternate regimens that would increase the benefits of prophylaxis in comparison to the AAP-recommended regimen, without increasing the total cost of the prophylactics the regimen?
+	\item Can we use spatial analysis of RSV to propose alternative regimens that would increase the benefits of prophylaxis in comparison to the AAP-recommended regimen, without increasing the total cost of the prophylactics the regimen?
 	\item Is there year-to-year variation in timing of RSV season in Connecticut?
@@
 Given that RSV seasons peak early in each calendar year, we assigned to each surveillance year 12 months of data starting in July of previous year.
-
 OHCA provided us with hospitalization records aggregated into Monday-Sunday calendar weeks; we assigned the first full calendar week of July to be surveillance week 1 in each surveillance year.
@@
 
-Our goal was to construct a model of annual RSV incidence that allows us to easily estimate complex characteristics of RSV seasons, such as season onset and offset.
-
-To that end, we looked for a model that allows easy sampling of estimated model parameters; coupling this with Monte Carlo sampling would --- after transforming model parameters into response variables --- allow us to sample arbitrary response variables.
+Our goal was to construct a model of annual RSV incidence that allowed us to easily estimate complex characteristics of RSV seasons, such as season onset and offset.
+To that end, we looked for a model that allowed easy sampling of estimated model parameters; coupling this with Monte Carlo sampling --- after transforming model parameters into response variables --- allowed us to sample arbitrary response variables.
 
 We were willing to assume that RSV incidence is the result of a Poisson process whose $\log$ can be modeled as a piecewise twice-differentiable function of time.
-
 To meet those criteria and assumptions, we chose a log-linked generalized additive model (GAM) with penalized cubic B-splines for our analysis.
@@
 
-We developed a custom R package for estimation of arbitrary characteristics of infectious disease outbreaks (as long as the outbreaks are amenable to GAM); this package is available at \href{https://github.com/airbornemint/outbreak-predict}{\nolinkurl{github.com/airbornemint/outbreak-predict}}.
+We developed a custom R package for estimation of arbitrary characteristics of infectious disease outbreaks (as long as the outbreaks are amenable to GAM); this package is available at \href{https://github.com/airbornemint/outbreak-inference}{\nolinkurl{github.com/airbornemint/outbreak-inference}}.
 
@@
         theme_light(base_size=plotTextBaseSize) +
-        scale_fill_manual(labels=legendLabels(c("$<$50", "$>$100")), values=twoToneAlt) +
+        scale_fill_manual(labels=legendLabels(c("$<$50", "$>$100")), values=c(lightBlue, darkBlue)) +
         geom_polygon(aes(fill=highRSV, group=group), color="white", size=.5) +
@@
     \item One region for the entire state
-    \item One region for each of the counties with high RSV case counts: Hartford County, Fairfield County, and New Haven County. (Figure \ref{fig:map}.)
+    \item One region for each of the counties with high RSV case counts: Hartford County, Fairfield County, and New Haven County (Figure \ref{fig:map}).
     \item One discontiguous region comprised of all remaining counties in Connecticut: \Sexpr{gsub("(.*), (.*)", "\\1, and \\2", paste(lowIncidenceCounties, collapse=", "))} (``low-RSV counties'').
@@
 
-Given that high-risk infants are a small subgroup of the general population (citation needed), we assumed that our model of RSV hospitalizations among all infants is an unbiased approximation of RSV hospitalizations among high-risk infants, and that, therefore, the preventable fraction of a prophylactic regimen is an unbiased estimate of the fraction of high-risk infants who benefit from prophylaxis.
+Given that high-risk infants are a small subgroup of the general population, we assumed that our model of RSV hospitalizations among all infants is an unbiased approximation of RSV hospitalizations among high-risk infants, and that, therefore, the preventable fraction of a prophylactic regimen is an unbiased estimate of the fraction of high-risk infants who benefit from prophylaxis.
 
@@
 
-The choice of \Sexpr{seasonThreshold * 100}\% and \Sexpr{(1 - seasonThreshold) * 100}\% incidence thresholds was based on our intent to use estimates of RSV season onset and offset to put forth alternate prophylaxis regimens (as described below), while maintaining 5-month dosing schedule (and therefore not increasing medication cost).
+The choice of \Sexpr{seasonThreshold * 100}\% and \Sexpr{(1 - seasonThreshold) * 100}\% incidence thresholds was based on our intent to use estimates of RSV season onset and offset to put forth alternative prophylaxis regimens (as described below), while maintaining 5-month dosing schedule (and therefore not increasing medication cost).
 Incidence cutoffs other than \Sexpr{seasonThreshold * 100}\% and \Sexpr{(1 - seasonThreshold) * 100}\% were briefly investigated, but quickly ruled out because they produced prophylaxis regimens starting long prior to RSV season onset or ending long after RSV season offset, and therefore had very low preventable fractions.
@@
 
-In all our alternate regimens, prophylaxis consists of five monthly doses of palivizumab, and protection is assumed to last 24 weeks from the first dose.
+In all our alternative regimens, prophylaxis consists of five monthly doses of palivizumab, and protection is assumed to last 24 weeks from the first dose.
 
@@
 Our analysis thus far assumed that RSV seasons are similar year-to-year.
-To analyze the effects on prophylaxis regimens of year-to-year variation between RSV seasons, we chose to aggregate our data into (overlapping) periods of three consecutive years --- in order to maintain a higher level of statistical power, as well as to limit impact of short-term variation on our results.
+To analyze the effects of year-to-year variation between RSV seasons on prophylaxis regimens, we chose to aggregate our data into (overlapping) periods of three consecutive years --- in order to maintain a higher level of statistical power, as well as to limit impact of short-term variation on our results.
 
@@
 
-\subsection{Evaluating alternate recent-years prophylaxis regimens}
+\subsection{Evaluating alternative recent-years prophylaxis regimens}
 
@@
 
-We then compared those regimens to the one recommended by AAP and to the six spatially adjusted alternates (with no calendrical rounding) discussed above.
+We then compared those regimens to the one recommended by AAP and to the six spatially adjusted alternatives (with no calendrical rounding) discussed above.
 
-As before, these alternate regimens involved five monthly doses of palivizumab giving 24 weeks of protection.
+As before, these alternative regimens involved five monthly doses of palivizumab giving 24 weeks of protection.
 
@@
 
-Compared to the statewide median onset of RSV season at \Sexpr{regionOnset("all")} weeks (\Sexpr{regionOnsetCI("all", level)} weeks) and offset at \Sexpr{regionOffset("all")} weeks (\Sexpr{regionOffsetCI("all", level)} weeks), RSV season in Fairfield county has earlier median onset at \Sexpr{regionOnset("Fairfield")} weeks (\Sexpr{regionOnsetCI("Fairfield", level)} weeks) and later median offset at \Sexpr{regionOffset("Fairfield")} weeks (\Sexpr{regionOffsetCI("Fairfield", level)} weeks).
-(Figure \ref{fig:seasonByRegion}.)
+Compared to the statewide median onset of RSV season at \Sexpr{regionOnset("all")} weeks (\Sexpr{regionOnsetCI("all", level)} weeks) and offset at \Sexpr{regionOffset("all")} weeks (\Sexpr{regionOffsetCI("all", level)} weeks), RSV season in Fairfield county has earlier median onset at \Sexpr{regionOnset("Fairfield")} weeks (\Sexpr{regionOnsetCI("Fairfield", level)} weeks) and later median offset at \Sexpr{regionOffset("Fairfield")} weeks (\Sexpr{regionOffsetCI("Fairfield", level)} weeks) (Figure \ref{fig:seasonByRegion}).
 
@@
 
-Meanwhile, in comparison with the statewide RSV season onset and offset, the low-RSV region has RSV season with later onset at \Sexpr{regionOnset("lowIncidence")} weeks (\Sexpr{regionOnsetCI("all", level)} weeks); season offset shows no change from the statewide median.
-(Figure \ref{fig:seasonByRegion}.)
+Meanwhile, in comparison with the statewide RSV season onset and offset, the low-RSV region has RSV season with later onset at \Sexpr{regionOnset("lowIncidence")} weeks (\Sexpr{regionOnsetCI("all", level)} weeks); season offset shows no change from the statewide median (Figure \ref{fig:seasonByRegion}).
 
@@
         scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, limits=range(c(monthBoundaries$min, monthBoundaries$max)), expand=c(0, 0)) + 
-        scale_color_manual(labels=spanLabels, values=twoToneAlt) +
-        scale_fill_manual(labels=spanLabels, values=twoToneAlt) +
+        scale_color_manual(labels=spanLabels, values=c(darkPurple, darkRed)) +
+        scale_fill_manual(labels=spanLabels, values=c(darkPurple, darkRed)) +
         guides(color=guide_legend(keywidth=3, keyheight=.4)) + 
@@
 
-The AAP guidelines perform better in the low-RSV counties, where \Sexpr{regionStrategyCoverage("lowIncidence", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("lowIncidence", "aap", 0, level)}) occur during the prophylaxis interval, but worse in Fairfield county, where \Sexpr{regionStrategyCoverage("Fairfield", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("Fairfield", "aap", 0, level)}) occur during this time.
-(Figure \ref{fig:coverageByRegionAAP}.)
+The AAP guidelines perform better in the low-RSV counties, where \Sexpr{regionStrategyCoverage("lowIncidence", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("lowIncidence", "aap", 0, level)}) occur during the prophylaxis interval, but worse in Fairfield county, where \Sexpr{regionStrategyCoverage("Fairfield", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("Fairfield", "aap", 0, level)}) occur during this time (Figure \ref{fig:coverageByRegionAAP}).
 
-This is caused by temporal misalignment between the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each region), and the timing of the AAP-recommended prophylaxis regimen.
-(Figure \ref{fig:coverageByRegionAAPInsight}.) Fairfield county, owing to its early season onset, sees disproportionately many cases before prophylaxis administration begins; on the other hand, the low-RSV counties, owing to their late season onset and relatively shorter RSV seasons, see almost all of their RSV cases within the prophylaxis window.
+This is caused by temporal misalignment between the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each region), and the timing of the AAP-recommended prophylaxis regimen (Figure \ref{fig:coverageByRegionAAPInsight}).
+Fairfield county, owing to its early season onset, sees disproportionately many cases before prophylaxis administration begins; on the other hand, the low-RSV counties, owing to their late season onset and relatively shorter RSV seasons, see almost all of their RSV cases within the prophylaxis window.
 
@@
 
-    stratLabels = legendLabels(c(
-        "Statewide onset", "Statewide midseason", "Statewide offset", 
-        "Regional onset", "Regional midseason", "Regional offset", 
-        "Statewide recent-years onset", "Statewide recent-years midseason", "Statewide recent-years offset", 
-        "AAP guidelines"
-    ))
-
     ggplot(data) +
@@
         scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
-        scale_color_manual(name="Prophylaxis regimen", labels=stratLabels[c(seq(1, 6), 10)], values=c(rep(twoTone, each=3), grey(0))) + 
-        scale_shape_manual(name="Prophylaxis regimen", labels=stratLabels[c(seq(1, 6), 10)], values=c(15, 16, 17, 15, 16, 17, 15)) + 
+        scale_color_manual(name="Prophylaxis regimen", labels=legendLabels(stratLabels[c(seq(1, 6), 10)]), values=c(rep(c(darkBrown, darkOrange), each=3), darkPurple)) + 
+        scale_shape_manual(name="Prophylaxis regimen", labels=legendLabels(stratLabels[c(seq(1, 6), 10)]), values=c(16, 15, 17, 16, 15, 17, 16)) + 
         geom_errorbar(
@@
 
-% TODO: Dan says state next paragraph more clearly, it's important
-
-Based on all-years data, the six spatially adjusted prophylaxis regimens (with no rounding of prophylaxis dates), when compared to the AAP guidelines, yield non-inferior results in all regions, and superior results statewide.
-(Figure \ref{fig:coverageByRegionRegimen}.)
+Based on all-years data, the six spatially adjusted prophylaxis regimens (with no rounding of prophylaxis dates), when compared to the AAP guidelines, yield non-inferior results in all regions, and superior results statewide (Figure \ref{fig:coverageByRegionRegimen}).
 
 Statewide, the AAP guidelines offer protection to \Sexpr{regionStrategyCoverage("all", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}).
-The alternate regimen based on all-years statewide onset yields the smallest increase, to \Sexpr{regionStrategyCoverage("all", "stateOnset", 0)} (\Sexpr{regionStrategyCoverageCI("all", "stateOnset", 0, level)}); other alternate regimens yield similar results.
+The alternative regimen based on all-years statewide onset yields the smallest increase, to \Sexpr{regionStrategyCoverage("all", "stateOnset", 0)} (\Sexpr{regionStrategyCoverageCI("all", "stateOnset", 0, level)}); other alternative regimens yield similar results.
 
-Most of the increase comes from Hartford county, where the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", 0, level)}), whereas the alternate regimen based on all-years regional offset generates the smallest increase, to \Sexpr{regionStrategyCoverage("Hartford", "countyOffset", 0)} (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", 0, level)}); other alternate regimens are comparable.
+Most of the increase comes from Hartford county, where the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", 0, level)}), whereas the alternative regimen based on all-years regional offset generates the smallest increase, to \Sexpr{regionStrategyCoverage("Hartford", "countyOffset", 0)} (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", 0, level)}); other alternative regimens are comparable.
 
-In every region, all alternate regimens based on all-years analysis are non-inferior to the AAP guidelines and non-superior to each other.
+In every region, all alternative regimens based on all-years analysis are non-inferior to the AAP guidelines and non-superior to each other.
 
 \paragraph{Calendrical rounding rapidly erases gains over the AAP-recommended regimen}
+
+<<calendarForRounding, results='hide', warning=FALSE>>=
+    tikz(sprintf("%s/calendarForRoundingRegimen.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10)
+
+    roundingStrat = unprotectedByCounty %>% 
+        filter(county %in% countiesForPlots, sliding==FALSE) %>%
+        select(strat, rounding) %>%
+        unique()
+
+    dataAll = predByCounty %>%
+        filter(county %in% countiesForPlots) %>%
+        group_by(county, time) %>%
+        do(
+            roundingStrat
+        ) %>%
+        ungroup() %>%
+        group_by(county, strat, rounding) %>%
+        do(
+            (function(df) {
+                county = unique(df$county)
+                rounding = as.numeric(unique(df$rounding))
+                strat = as.character(unique(df$strat))
+                strat = ppxFixedStrategies(county, rounding)[[strat]]
+                stratActive = strat(df$time)
+                df %>%
+                    mutate(stratActive=stratActive)
+            })(.)
+        ) %>%
+        ungroup() %>%
+        filter(stratActive > 0) %>%
+        group_by(county, strat, rounding) %>%
+        summarize(start=min(time), end=max(time)) %>%
+        ungroup()
+
+    aapStartEnd = dataAll %>%
+        filter(strat == "aap") %>%
+        select(start, end) %>%
+        unique()
+
+    aap = dataAll %>%
+        filter(strat != "aap") %>%
+        group_by(strat, rounding) %>%
+        do(
+            aapStartEnd
+        ) %>%
+        ungroup() %>%
+        mutate(y=ifelse(grepl("state", strat), "all", "lowIncidence")) %>%
+        mutate(y=factor(y, levels(dataAll$county)))
+
+    data = dataAll %>% 
+        filter(strat != "aap") %>%
+        filter(xor(grepl("county", strat), county == "all"))
+
+    ggplot(data) +
+        theme_light(base_size=plotTextBaseSize) +
+    	geom_rect(aes(xmin=start, xmax=end, ymin=as.numeric(county)-0.25, ymax=as.numeric(county)+0.25), size=.375) + 
+    	geom_rect(data=aap, aes(xmin=start, xmax=end, ymin=as.numeric(y)+0.75, ymax=as.numeric(y)+1.25), size=.375) + 
+        scale_y_continuous(breaks=as.numeric(countiesForPlots), labels=countyLabels[as.character(countiesForPlots)]) + 
+        scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, limits=range(c(monthBoundaries$min, monthBoundaries$max)), expand=c(0, 0)) + 
+#        scale_color_manual(labels=spanLabels, values=twoToneAlt) +
+#        scale_fill_manual(labels=spanLabels, values=twoToneAlt)# +
+#        guides(color=guide_legend(keywidth=3, keyheight=.4)) + 
+        facet_wrap(~ rounding + strat, nrow=8, labeller=labeller(rounding=roundingLabels, strat=stratLabels), scales="free_y") #+
+#        labs(x=NULL, y="Cumulative indicence fraction") + 
+#        theme(
+#            panel.grid.major.x=element_blank(),
+#            legend.title=element_blank(),
+#            axis.title.y=element_blank(),
+#            axis.ticks.x=element_blank(),
+#            axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
+#            legend.position="bottom"
+#        )
+    dev.off()
+@
 
@@
         scale_y_continuous(labels=latexPercent, limits=c(0.90, 1.00), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
-        scale_color_manual(name="Prophylaxis regimen", labels=stratLabels[c(seq(1, 6), 10)], values=c(rep(twoTone, each=3), grey(0))) + 
-        scale_shape_manual(name="Prophylaxis regimen", labels=stratLabels[c(seq(1, 6), 10)], values=c(15, 16, 17, 15, 16, 17, 15)) + 
+        scale_color_manual(name="Prophylaxis regimen", labels=legendLabels(stratLabels[c(seq(1, 6), 10)]), values=c(rep(c(darkBrown, darkOrange), each=3), darkPurple)) + 
+        scale_shape_manual(name="Prophylaxis regimen", labels=legendLabels(stratLabels[c(seq(1, 6), 10)]), values=c(16, 15, 17, 16, 15, 17, 16)) + 
         scale_x_discrete(labels=roundingLabels) + 
@@
 
-After we applied weekly, biweekly, and monthly rounding to start and end dates of our six alternate immunoprophylaxis regimens, we found that longer rounding intervals diminished the benefit of spatial analysis.
-(Figure \ref{fig:coverageByRoundingRegimen}.)
+After we applied weekly, biweekly, and monthly rounding to start and end dates of our six alternative immunoprophylaxis regimens, we found that longer rounding intervals diminished the benefit of spatial analysis (Figure \ref{fig:coverageByRoundingRegimen}).
 
@@
 \input{\figuresDir/coverageByRoundingRegimen.tex}
-\caption[The effect of calendrical rounding of start and end of spatially adjusted RSV prophylaxis regimens on their performance]{The effect of calendrical rounding of start and end of spatially adjusted RSV prophylaxis regimens on their performance, showing that longer rounding intervals diminish the benefits of alternate regimens over the AAP-recommended regimen.
+\caption[The effect of calendrical rounding of start and end of spatially adjusted RSV prophylaxis regimens on their performance]{The effect of calendrical rounding of start and end of spatially adjusted RSV prophylaxis regimens on their performance, showing that longer rounding intervals diminish the benefits of alternative regimens over the AAP-recommended regimen.
 Preventable fraction: the fraction of all RSV hospitalizations occurring while the prophylaxis regimen offers protection}
@@
 
-Our linear regression of median RSV season onset and offset over three-year periods indicates that season onset has slowly been drifting earlier, at a rate of \Sexpr{formatDrift(onsetByYear)} (\Sexpr{formatDriftCI(onsetByYear, level)}).
-(Figure \ref{fig:onsetOffsetByYear}.) It is unclear whether this is a part of a larger pattern, such as a cycle spanning decades.
+Our linear regression of median RSV season onset and offset over three-year periods indicates that season onset has slowly been drifting earlier (Figure \ref{fig:onsetOffsetByYear}), at a rate of \Sexpr{formatDrift(onsetByYear)} (\Sexpr{formatDriftCI(onsetByYear, level)}).
+It is unclear whether this is a part of a larger pattern, such as a cycle spanning decades.
 
@@
 
-% TODO third color
-
 <<coverageByRegionWithSliding, results='hide', warning=FALSE>>=
@@
 
-    stratLabels = legendLabels(c(
-        "Statewide all-years onset", "Statewide all-years midseason", "Statewide all-years offset", 
-        "Regional onset", "Regional midseason", "Regional offset", 
-        "Statewide recent-years onset", "Statewide recent-years midseason", "Statewide recent-years offset", 
-        "AAP guidelines"
-    ))
-
     ggplot(data) +
@@
         scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
-        scale_color_manual(name="Prophylaxis regimen", labels=stratLabels[c(seq(1, 3), seq(7, 10))], values=c(rep(twoToneAlt, each=3), grey(0))) + 
-        scale_shape_manual(name="Prophylaxis regimen", labels=stratLabels[c(seq(1, 3), seq(7, 10))], values=c(15, 16, 17, 15, 16, 17, 15)) + 
+        scale_color_manual(name="Prophylaxis regimen", labels=legendLabels(stratLabels[c(seq(1, 3), seq(7, 10))]), values=c(rep(c(darkBrown, darkGreen), each=3), darkPurple)) + 
+        scale_shape_manual(name="Prophylaxis regimen", labels=legendLabels(stratLabels[c(seq(1, 3), seq(7, 10))]), values=c(16, 15, 17, 16, 15, 17, 16)) + 
         geom_errorbar(
@@
 
-Compared to our regional all-years analysis, the three regimens based on statewide recent-years analysis produced non-superior results everywhere, and inferior results in the low-RSV counties.
-(Figure \ref{fig:coverageByRegionRegimenWithSliding}.)
+Compared to our regional all-years analysis, the three regimens based on statewide recent-years analysis produced non-superior results everywhere, and inferior results in the low-RSV counties (Figure \ref{fig:coverageByRegionRegimenWithSliding}).
 
@@
 
+\subsection{Conclusions}
+
+% TODO figure showing prophylaxis regimens on a calendar?
+
+Our analysis confirms the existence of regional variation of RSV season timing in Connecticut (defined by RSV season onset and offset) observable at the county level.
+
+We have also shown a misalignment between the prophylaxis schedule recommended by the AAP and the timing of the RSV season throughout Connecticut, with most counties' RSV season starting before protection from the first dose of prophylaxis takes hold, and ending before protection from the last dose wanes.
+This misalignment is particularly notable in Fairfield County, due to its early season onset.
+
+Our effort to optimize timing of the prophylaxis regimen (without changing its duration, and therefore its pharmaceutical cost) shows the possibility of a theoretical 1-2\% statewide decrease in RSV-associated hospitalizations among high-risk infants each year, primarily in counties with higher RSV burden (Fairfield, Hartford, and New Haven counties).
+
+The magnitude of that improvement wanes upon encountering practicalities of clinical practice guideline implementation.
+Nonetheless, with clinical practice guidelines localized at the county level, and the timing of prophylaxis adjusted in each county by less than a whole month from the current AAP guidelines, we still found the potential for $\sim$1\% statewide decrease in RSV-associated hospitalizations among high risk infants.
+
+The prophylaxis regimen with which we were able to attain this improvement is the one in which prophylaxis in each county is timed relative to the midpoint of the RSV season (rounded to two weeks) in that county, which simultaneously reduces unprotected cases early in the season and ineffective prophylaxis late in the season.
+
+Increasing complexity of practice guidelines carries with it increased cost of implementation, such as training of clinicians and other healthcare workers.
+It is therefore not apparent from our research alone that the potential benefits would outweigh the costs.
+
+Although we found a weak statewide trend in RSV season onset becoming earlier over time, further analysis did not yield any improvements to prophylaxis based on that trend.
+Since temporal variation in clinical guidelines would lead to a higher implementation burden than spatial variation, we see no reason to base RSV immunoprophylaxis clinical practice guidelines on temporal variation in RSV season timing.
+
 \subsection{Limitations}
 
-Although we were able to reach some conclusions about the impact of calendrical rounding on spatially adjusted prophylaxis regimens, ultimately our analysis is hamstrung by weekly aggregation of hospital admission data in our initial data.
+Although we were able to reach some conclusions about the impact of calendrical rounding on spatially adjusted prophylaxis regimens, ultimately our analysis is hamstrung by weekly aggregation of hospital admission data.
 To properly propose and evaluate any fine-tuning to RSV prophylaxis guidelines, we recommend use of daily data.
 
-Throughout, we assume that RSV-associated hospitalizations are an unbiased estimate of RSV incidence in the general population; in doing so, we implicitly assumed that infectiousness and virulence of RSV are constant over time, for which we have no verification.
+Throughout, we assumed that RSV-associated hospitalizations are an unbiased estimate of RSV incidence in the general population; in doing so, we implicitly assumed that infectiousness and virulence of RSV are constant over time, for which we have no verification.
 
@@
 
-Similarly, towns that see substantial inter-county travel (for example, employment hubs near county lines) likely bias our regional analysis.
-
-\subsection{Conclusions}
-
-% TODO Revisit
-
-Our analysis confirms the existence of regional variation of RSV season timing in Connecticut (defined by RSV season onset and offset) observable at the county level.
-
-Furthermore, we have shown a misalignment between the prophylaxis schedule recommended by the AAP and the timing of the RSV season throughout Connecticut, with most counties' RSV season starting before protection from the first dose of prophylaxis takes hold, and ending before protection from the last dose wanes.
-This misalignment is particularly notable in Fairfield County, due to its early season onset.
-
-Our attempt to optimize timing of the prophylaxis regimen (without changing its duration and therefore its cost) shows the possibility of a theoretical 1-2\% statewide decrease in RSV-associated hospitalizations among high-risk infants each year, primarily in counties with higher RSV burden (Fairfield, Hartford, and New Haven counties).
-
-However, the magnitude of that improvement wanes upon encountering practicalities of clinical practice guideline implementation.
-Nonetheless, with clinical practice guidelines localized at the county level, and the timing of prophylaxis adjusted in each county by less than a whole month from the current AAP guidelines, we still found the potential for $\sim$1\% statewide decrease in RSV-associated hospitalizations among high risk infants.
-
-The prophylaxis regimen with which we were able to attain this improvement is the one in which prophylaxis in each county is timed relative to the midpoint of the RSV season (rounded to two weeks) in that county, which simultaneously reduces unprotected cases early in the season and ineffective prophylaxis late in the season.
-
-Increasing complexity of practice guidelines carries with it increased cost of implementation, such as training of clinicians and other healthcare workers.
-It is therefore not apparent from our research alone that the potential benefits would outweigh the costs.
-
-Finally, although we found a weak statewide trend in RSV season onset becoming earlier over time, further analysis did not yield any improvements to prophylaxis based on that trend.
-Since temporal variation in clinical guidelines would lead to a higher implementation burden than spatial variation, we see no reason to base RSV immunoprophylaxis clinical practice guidelines on temporal variation in RSV season timing.
+Finally, towns that see substantial inter-county travel (for example, employment hubs near county lines) likely bias our regional analysis.
 

### 2018-01-24 Thesis/Thesis.R

@@ -1,9 +1,9 @@
 # ---- util ----
 library(magrittr)
-library(rgeos)
 library(grid)
 library(tikzDevice)
 library(rgdal)
+library(ggplot2)
 options(tikzDefaultEngine='pdftex')
 
 figuresDir = ".texpadtmp/figures"
@@ -118,6 +118,19 @@ onsetOffsetLabeller = labeller(
 
 roundingLabels = c(`0` = "No rounding", `1` = "Weekly rounding", `2` = "Biweekly rounding", `4` = "Monthly rounding")
 
+stratLabels = c(
+  `stateOnset` = "Statewide all-years onset",
+  `stateMiddle` = "Statewide all-years midseason", 
+  `stateOffset` = "Statewide all-years offset", 
+  `countyOnset` = "Regional all-years onset",
+  `countyMiddle` = "Regional all-years midseason",
+  `countyOffset` = "Regional all-years offset", 
+  `stateSlidingOnset` = "Statewide recent-years onset",
+  `stateSlidingMiddle` = "Statewide recent-years midseason",
+  `stateSlidingOffset` = "Statewide recent-years offset", 
+  `aap` = "AAP guidelines"
+)
+
 countyLabels = c(
   `all` = "Statewide",
   `New Haven` = "New Haven county",
@@ -155,7 +168,19 @@ legendLabels = function(labels, size="") {
 }
 
 twoTone = c("#018571", "#80cdc1")
-twoToneAlt = c("#018571", "#a6611a")
+
+lightBlue = "#a6cee3"
+darkBlue = "#1f78b4"
+lightGreen = "#b2df8a"
+darkGreen = "#33a02c"
+lightRed = "#fb9a99"
+darkRed = "#e31a1c"
+lightOrange = "#fdbf6f"
+darkOrange = "#ff7f00"
+lightPurple = "#cab2d6"
+darkPurple = "#6a3d9a"
+lightBrown = "#ffff99"
+darkBrown = "#b15928"
 
 # Counties which we plot (so, not individual low-incidence counties)
 countiesForPlots = thresholdsByCounty$county[!thresholdsByCounty$county %in% lowIncidenceCounties]

### 2018-01-24 Analysis/RSV.R
Increase the number of simulations for final version

@@ -14,7 +14,7 @@ library(maps)
 data(zipcode)
 set.seed(0)
 
-simulations = 20
+simulations = 2000
 
 # *** Data munging helpers
 

### 2018-01-24 Thesis/structure.tex
Double-side and no headers before TOC

@@
 	bottom=1.5cm, % Bottom margin
-	left=2cm, % Left margin
-	right=2cm, % Right margin
+	left=2.5cm, % Left margin
+	right=1.5cm, % Right margin
 	includehead, % Include space for a header
@@
 \cfoot{} % Center footer
-\rfoot{\footnotesize Page \thepage\ of \pageref{LastPage}} % Right footer, "Page 1 of 2"
+\fancyfoot[RO,LE]{\footnotesize Page \thepage\ of \pageref{LastPage}} % Right footer, "Page 1 of 2"
 

### 2018-04-30 Thesis/Poster.rnw
Added YSPH research day poster

<<options, echo=FALSE>>=
    opts_chunk$set(echo=FALSE, message=FALSE)
@

<<load>>=
read_chunk("../Analysis/RSV.R")
read_chunk("../Thesis/Thesis.R")
@

<<libraries, cache=FALSE>>=
@

<<external, cache=TRUE>>=
@

<<util, warning=FALSE>>=
@

<<posterUtil, cache=TRUE>>=
posterPlotWidth = 19
posterPlotHeight = posterPlotWidth * 3 / 10
plotTextBaseSize = 24
@

<<coverageByRegionAAPInsightPoster, results='hide'>>=
    tikz(sprintf("%s/coverageByRegionAAPInsightPoster.tex", figuresDir), width=posterPlotWidth, height=posterPlotHeight, pointsize=37)

    strat = ppxFixedStrategies("all")[["aap"]]

    data = predByCounty %>%
	    filter(county %in% countiesForPlots)

    thresholds = data %>%
    	mutate(ppx=strat(time)) %>%
    	filter(ppx > 0) %>%
    	group_by(county) %>%
    	do(
    		data.frame(
    			ppx.start=min(.$time),
    			ppx.end=max(.$time),
    			unprotected.start=min(.$rsv.cum.fit),
    			unprotected.end=max(.$rsv.cum.fit)
    		)
    	) %>%
    	ungroup() %>%
    	as.data.frame() %>%
    	inner_join(thresholdsByCounty, by="county")

    barYmin = 0.025
    barYmax = 0.075

    spanExtents = data.frame(
        variable=c("ppx", "season"), 
        barYmin=c(1 + barYmin, -barYmax), 
        barYmax=c(1 + barYmax, -barYmin), 
        lineYmin=c(0, -barYmin), 
        lineYmax=c(1 + barYmin, 1)
    )

    spans = thresholds %>%
        select(county, matches("ppx."), matches(".median")) %>%
        rename(season.start=onset.median, season.end=offset.median) %>%
        melt(id.vars="county") %>%
        cSplit("variable", ".") %>%
        rename(variable=variable_1, part=variable_2) %>%
        cast(county + variable ~ part) %>%
        right_join(spanExtents, by="variable")

    spanLabels = legendLabels(c("AAP-recommended prophylaxis", "RSV season"), 20)

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        geom_ribbon(aes(ymin=rsv.cum.fit.lower, ymax=rsv.cum.fit.upper, x=time), fill=grey(.25)) +
    	geom_segment(aes(x=start, y=lineYmin, xend=start, yend=lineYmax, color=variable), data=spans, size=2) + 
    	geom_segment(aes(x=end, y=lineYmin, xend=end, yend=lineYmax, color=variable), data=spans, size=2) + 
    	geom_rect(aes(xmin=start, ymin=barYmin, xmax=end, ymax=barYmax, fill=variable, color=variable), data=spans, size=2) + 
    	geom_segment(aes(x=-Inf, y=unprotected.start, xend=ppx.start, yend=unprotected.start), linetype="55", data=thresholds, size=2) + 
        geom_segment(aes(x=-Inf, y=unprotected.end, xend=ppx.end, yend=unprotected.end), linetype="55", data=thresholds, size=2) + 
        geom_point(aes(x=min(monthBoundaries$min), y=unprotected.end), data=thresholds, shape=18) + 
        geom_point(aes(x=min(monthBoundaries$min), y=unprotected.start), data=thresholds, shape=18) + 
        scale_y_continuous(labels=latexPercent, breaks=seq(0, 1, by=.2), limits=c(-0.1, 1.1), expand=c(0, 0)) +
        scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, limits=range(c(monthBoundaries$min, monthBoundaries$max)), expand=c(0, 0)) + 
        scale_color_manual(labels=spanLabels, values=c(darkPurple, darkRed)) +
        scale_fill_manual(labels=spanLabels, values=c(darkPurple, darkRed)) +
        guides(color=guide_legend(keywidth=3, keyheight=.4, label.vjust=0.2)) + 
        facet_wrap(~county, ncol=5, labeller=labeller(county=countyLabels)) +
        labs(x=NULL, y="Cumulative indicence") + 
        theme(
            panel.grid.major.x=element_blank(),
            legend.title=element_blank(),
            axis.title.y=element_text(vjust=1, margin=margin(0, .5, 0, 0, "in")),
            axis.ticks.x=element_blank(),
            axis.text.x=element_text(angle=90, hjust=1, vjust=1),
            axis.text.y=element_text(vjust=1),
            legend.position="top",
            strip.text.x=element_text(margin=margin(.2, 0, .1, 0, "in")),
            plot.margin=unit(c(0,1.5,.375,1.875),"in"),
            panel.border=element_rect(fill=NA, colour="grey70", size=rel(5)),
            panel.grid.major=element_line(size=rel(2.5)),
            panel.grid.minor=element_line(size=rel(1.25)),
            axis.ticks=element_line(colour="grey70", size=rel(2.5)),
        )

    dev.off()
@

<<coverageByRegionPoster, results='hide', warning=FALSE>>=
    tikz(sprintf("%s/coverageByRegionRegimenPoster.tex", figuresDir), width=posterPlotWidth, height=posterPlotHeight * 1.25, pointsize=37)
    data = unprotectedByCounty %>% 
        filter(county %in% countiesForPlots, rounding==0, sliding==FALSE)

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
        scale_color_manual(name="Prophylaxis regimen", labels=legendLabels(stratLabels[c(seq(1, 6), 10)], 15), values=c(rep(c(darkBrown, darkOrange), each=3), darkPurple)) + 
        scale_shape_manual(name="Prophylaxis regimen", labels=legendLabels(stratLabels[c(seq(1, 6), 10)], 15), values=c(16, 15, 17, 16, 15, 17, 16)) + 
        geom_errorbar(
            aes(ymin=frac.lower, ymax=frac.upper, x=county, color=strat, group=strat), 
            width=.3, 
            lwd=2,
            position=position_dodge(.5)
        ) + 
        geom_point(aes(y=frac.median, x=county, color=strat, shape=strat), position=position_dodge(.5), size=.75*5) +
        labs(y="Preventable fraction", color="Prophylaxis regimen") +
        guides(color=guide_legend(keywidth=3, keyheight=.5, ncol=3, title.hjust=1)) + 
        scale_x_discrete(labels=countyLabels) + 
        theme(
            axis.title.x=element_blank(),
            axis.ticks.x=element_blank(),
            axis.title.y=element_text(vjust=1, margin=margin(0, .5, 0, 0, "in")),
            legend.position="top",
            axis.text.x=element_text(vjust=1, margin=margin(.125, 0, 0, 0, "in")),
#            strip.text.x=element_text(margin=margin(.2, 0, .1, 0, "in")),
            plot.margin=unit(c(0,1.5,.375,1.875),"in"),
            panel.border=element_rect(fill=NA, colour="grey70", size=rel(5)),
            panel.grid.major=element_line(size=rel(2.5)),
            panel.grid.minor=element_line(size=rel(1.25)),
            axis.ticks=element_line(colour="grey70", size=rel(2.5)),
        )
    dev.off()
@

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[final]{beamer}

\edef\figuresDir{.texpadtmp/figures}

\usepackage[scale=1.24]{beamerposter} % Use the beamerposter package for laying out the poster

\usetheme{confposter} % Use the confposter theme supplied with this template

\setbeamertemplate{headline}{
 \leavevmode
  \begin{columns}
   \begin{column}{\linewidth}
    \centering
    \usebeamercolor{title in headline}{\color{jblue}\Huge{\textbf{\inserttitle}}\\[0.5ex]}
    \usebeamercolor{author in headline}{\color{fg}\Large{\insertauthor}\\[.5ex]}
%    \usebeamercolor{institute in headline}{\color{fg}\large{\insertinstitute}\\[.5ex]}
    \vskip1cm
   \end{column}
   \vspace{1cm}
  \end{columns}
 \vspace{0.5in}
 \hspace{0.5in}\begin{beamercolorbox}[wd=46in,colsep=0.15cm]{cboxb}\end{beamercolorbox}
 \vspace{0.1in}
}

\setbeamercolor{block title}{fg=ngreen,bg=white} % Colors of the block titles
\setbeamercolor{block body}{fg=black,bg=white} % Colors of the body of blocks
\setbeamercolor{block alerted title}{fg=white,bg=dblue!70} % Colors of the highlighted block titles
\setbeamercolor{block alerted body}{fg=black,bg=white} % Colors of the body of highlighted blocks
% Many more colors are available for use in beamerthemeconfposter.sty

%-----------------------------------------------------------
% Define the column widths and overall poster size
% To set effective sepwid, onecolwid and twocolwid values, first choose how many columns you want and how much separation you want between columns
% In this template, the separation width chosen is 0.024 of the paper width and a 4-column layout
% onecolwid should therefore be (1-(# of columns+1)*sepwid)/# of columns e.g. (1-(4+1)*0.024)/4 = 0.22
% Set twocolwid to be (2*onecolwid)+sepwid = 0.464
% Set threecolwid to be (3*onecolwid)+2*sepwid = 0.708

\newlength{\sepwid}
\newlength{\onecolwid}
\newlength{\twocolwid}
\newlength{\threecolwid}
\setlength{\paperwidth}{47in} % A0 width: 46.8in
\setlength{\paperheight}{35in} % A0 height: 33.1in
\setlength{\sepwid}{0pt} % Separation width (white space) between columns
\setlength{\onecolwid}{0.22\paperwidth} % Width of one column
\setlength{\twocolwid}{0.44\paperwidth} % Width of two columns
\setlength{\threecolwid}{0.708\paperwidth} % Width of three columns
\setlength{\topmargin}{-0.5in} % Reduce the top margin size
%-----------------------------------------------------------

\usepackage{graphicx}  % Required for including images

\usepackage{booktabs} % Top and bottom rules for tables

%----------------------------------------------------------------------------------------
%	TITLE SECTION 
%----------------------------------------------------------------------------------------

\title{Assessment and optimization of RSV prophylaxis in Connecticut} % Poster title

\author{Ben Artin, YSPH/YSM 2018} % Author(s)

\institute{Advisors: Daniel Weinberger, PhD; Virginia Pitzer, ScD} % Institution(s)

%----------------------------------------------------------------------------------------

\usepackage[backend=bibtex,style=nejm,sorting=none,autocite=superscript,articledoi=true,url=false]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)

\addbibresource{../Thesis.bib} % The filename of the bibliography
%\renewcommand{\cite}[1]{\autocite{#1}}
\renewcommand{\cite}[1]{}

\usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography

\begin{document}

\addtobeamertemplate{block end}{}{\vspace*{2ex}} % White space under blocks
\addtobeamertemplate{block alerted end}{}{\vspace*{2ex}} % White space under highlighted (alert) blocks

\setlength{\belowcaptionskip}{2ex} % White space under figures
\setlength\belowdisplayshortskip{2ex} % White space under equations

\begin{frame}[t] % The whole poster is enclosed in one beamer frame

\begin{columns}[t] % The whole poster consists of three major columns, the second of which is split into two columns twice - the [t] option aligns each column's content to the top

\begin{column}{\onecolwid} % The first column

%----------------------------------------------------------------------------------------
%	OBJECTIVES
%----------------------------------------------------------------------------------------

\begin{alertblock}{Objectives}

\begin{itemize}
\item Estimate variation in timing of respiratory syncytial virus (RSV) season in Connecticut by county and by year
\item Evaluate effectiveness of the RSV immunoprophylaxis regimen recommended by the American Academy of Pediatrics (AAP)
\item Formulate alternative prophylaxis regimens to account for regional and annual variation in timing of RSV season in Connecticut
\item Compare effectiveness of alternative regimens against the AAP recommendation
\end{itemize}

\end{alertblock}

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

\begin{block}{Background}

Respiratory syncytial virus (RSV) causes seasonal respiratory infection with potentially serious complications in children,\cite{Hall:2009gi,Hall:2013jo,Zhou:2012ho,Boyce:2000gz} and leads to hospitalization rates as high as 50\% in high-risk infants.\cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj,Boyce:2000gz} Safe and effective immunoprophylaxis (palivizumab) is available, but costly.\cite{Hampp:2011ju,Andabaka:2013dr,Group:1998ih,Feltes:2003wm}

The American Academy of Pediatrics (AAP) recommends palivizumab only for infants at high risk of complications, and only during the RSV season.\cite{Anonymous:1998up,AmericanAcademyofPediatricsCommitteeonInfectiousDiseasesandCommitteeonFetusandNewborn:2003ug,AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj} Although the current AAP guidelines acknowledge the existence of spatial and temporal variation in RSV incidence, they do not recommend spatial or temporal adjustments to immunoprophylaxis regimen outside of Florida.\cite{CentersforDiseaseControlandPreventionCDC:2011wt,CentersforDiseaseControlandPreventionCDC:2013wv,AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}

In this study, we investigated the value of using spatial and temporal variation in RSV incidence to adjust the RSV prophylaxis regimen in Connecticut.

\begin{center}
\vspace{2.35in}
\includegraphics[height=320pt]{EPH}
\hspace{40pt}
\includegraphics[height=320pt]{Medicine}
\end{center}

\end{block}

%------------------------------------------------

%\begin{figure}
%\includegraphics[width=0.8\linewidth]{placeholder.jpg}
%\caption{Figure caption}
%\end{figure}

%----------------------------------------------------------------------------------------

\end{column} % End of the first column

\begin{column}{\twocolwid} % Begin a column which is two columns wide (column 2)

%\begin{columns}[t,totalwidth=\twocolwid] % Split up the two columns wide column
%
%\begin{column}{\onecolwid}\vspace{-.6in} % The first column within column 2 (column 2.1)
%
%\end{column} % End of column 2.1
%
%\begin{column}{\onecolwid}\vspace{-.6in} % The second column within column 2 (column 2.2)
%
%\begin{block}{Methods}
%
%\end{block}
%
%%----------------------------------------------------------------------------------------
%
%\end{column} % End of column 2.2
%
%\end{columns} % End of the split of column 2 - any content after this will now take up 2 columns width

\begin{block}{Methods}

\begin{enumerate}
\item Identified \Sexpr{nrow(dataset)} RSV-associated hospitalizations in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)}. 
\item Modeled RSV seasons using Monte Carlo sampling of log-linked generalized additive model with penalized cubic B-splines.
%\item We developed and published a custom R package, \texttt{outbreak-inference}, for estimation of outbreak characteristics.
\item Estimated the fraction of all RSV-associated hospitalizations that occur during the interval when RSV prophylaxis is recommended (``preventable fraction'') under the AAP guidelines.
\item Estimated RSV season onset and offset in each region across all years.
\item Constructed alternative prophylaxis regimens based on regional variation in RSV season timing.
\item Estimated preventable fraction of the regionally adjusted alternative regimens.
\end{enumerate}

\end{block}

\begin{block}{Results}

\begin{alertblock}{AAP-recommended prophylaxis lags behind RSV season}

\begin{figure}
\begin{center}
\input{\figuresDir/coverageByRegionAAPInsightPoster.tex}
\label{fig:coverageByRegionAAPInsight}
\caption{Regional variation in the lag between RSV seasons and the AAP-recommended prophylaxis regimen}
\end{center}
\end{figure}

\end{alertblock}

\begin{alertblock}{Spatial adjustments yield up to 1\% improvement}

\begin{figure}
\begin{center}
\input{\figuresDir/coverageByRegionRegimenPoster.tex}
\label{fig:coverageByRegionRegimen}
\caption{Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen}
\end{center}
\end{figure}

\end{alertblock}
\end{block}

%----------------------------------------------------------------------------------------
%	RESULTS
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------

\end{column} % End of the second column

\begin{column}{\onecolwid} % The third column

%----------------------------------------------------------------------------------------
%	CONCLUSION
%----------------------------------------------------------------------------------------

\begin{block}{Conclusion}

Timing of RSV season in Connecticut varies by several weeks in different parts of the state. The AAP-recommended
prophylaxis regimen is misaligned with the RSV season in the counties with highest RSV incidence.

Timing of RSV immunoprophylaxis could be adjusted to achieve approximately a 1\% increase in RSV prevention statewide.

This gain requires using immunoprophylaxis schedule based on 1-week or 2-week intervals, rather 
than the month-based schedule currently used in AAP recommendations.

Year-to-year variability of RSV season timing in Connecticut is less significant than regional differences within the state.
Accounting for year-to-year variability in our model did not produce any additional improvements beyond the 1\% gained from accounting 
for regional variability.

\end{block}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{block}{Limitations}

Our model of AAP prophylaxis regimen assumes protection begins on November 15th, whereas prophylaxis start dates
are actually spread out throughout November.

We assumed that RSV illness after receiving prophylaxis (breakthrough illness) is negligible.

We do not have data for RSV infections among travelers from other states, and therefore our analysis underestimates RSV
incidence in regions with high levels of interstate travel, such as urban centers near state lines.

Our regional analysis does not account for inter-county travel, such as in employment hubs near county lines.

\end{block}

%----------------------------------------------------------------------------------------
%	REFERENCES
%----------------------------------------------------------------------------------------

%\begin{block}{References}
%
%\small{\printbibliography}
%
%\end{block}

%----------------------------------------------------------------------------------------
%	CONTACT INFORMATION
%----------------------------------------------------------------------------------------

%\begin{center}
%\begin{tabular}{ccc}
%\includegraphics[width=0.4\linewidth]{logo.png} & \hfill & \includegraphics[width=0.4\linewidth]{logo.png}
%\end{tabular}
%\end{center}

\setbeamercolor{block alerted title}{fg=black,bg=black!10} % Change the alert block title colors
\setbeamercolor{block alerted body}{fg=black,bg=white} % Change the alert block body colors

\vspace{2.1in}

\begin{alertblock}{Thesis advisors}

\begin{itemize}
\item Daniel Weinberger, PhD, YSPH
\item Virginia Pitzer, ScD, YSPH
\end{itemize}

\end{alertblock}

%----------------------------------------------------------------------------------------

\end{column} % End of the third column

\end{columns} % End of all the columns in the poster

\end{frame} % End of the enclosing frame

\end{document}

### 2018-04-30 Thesis/Thesis.R

@@ -161,9 +161,9 @@ monthBoundaries = breaks.df %>%
 
 epiWeekBreaks = sort(unique(c(monthBoundaries$min, monthBoundaries$max)))
 
-legendLabels = function(labels, size="") {
+legendLabels = function(labels, rep=2) {
   as.vector(sapply(labels, function(label) {
-    sprintf("%s%s%s\\qquad\\qquad", size, ifelse(nchar(size) > 0, " ", ""), label)
+    sprintf("%s%s", label, strrep("\\qquad", rep))
   }))
 }
 

### 2019-02-15 Analysis/RSV.R
Package renamed

@@ -2,7 +2,7 @@
 library(reshape)
 library(dplyr)
 library(mgcv)
-library(outbreakpredict)
+library(outbreakinference)
 library(zipcode)
 library(ggplot2)
 library(easyGgplot2)

### 2019-02-15 Paper/RSVOptimization.rnw
Single-column

--- 2018-01-24 Thesis/Thesis.rnw
@@
-% TODO: Plot regression line in onset/offset analysis
-% TODO clarify all years analysis in figure captions
-% TODO Put 1-2% punchline in the abstract, maybe
-% TODO So it turns out that several regimens are actually the same, and that the best regional regimen @ 2w rounding is actually the same as the best statewide regimen @ 2w rounding.
-As a result, the conclusion could be simplified to statewide 2w rounding.
-% TODO paragraphs
-
 <<options, echo=FALSE>>=
@@
 read_chunk("../Analysis/RSV.R")
-read_chunk("../Thesis/Thesis.R")
+read_chunk("../Paper/RSVOptimization.R")
 @
@@
 
-\documentclass[10pt,letter]{article}
+\documentclass[10pt,letter,twoside]{article}
 
@@
 \author{
-    \authorstyle{Ben Artin\textsuperscript{1}}
+    \authorstyle{Ben Artin, MEng, MPH, MMSc\textsuperscript{1}}
     \newline\newline
-    \authorstyle{Daniel Weinberger, PhD\textsuperscript{2}, advisor}\\
-    \authorstyle{Virginia Pitzer, ScD\textsuperscript{2}, advisor}
+    \authorstyle{Daniel Weinberger, PhD\textsuperscript{1}}\\
+    \authorstyle{Virginia Pitzer, ScD\textsuperscript{1}}
     \newline\newline
-    \textsuperscript{1}\institution{Yale University, School of Public Health and School of Medicine}\\
-    \textsuperscript{2}\institution{Yale University, School of Public Health}
+    \textsuperscript{1}\institution{Yale University, School of Public Health}
 }
@@
 
+\pagestyle{empty}
 \begin{document}
@@
 \maketitle
-
-\begin{center}
-
-\vspace{20pt}
-\large Submitted to the School of Public Health and the School of Medicine, in partial fulfillment of the requirements for the degrees of Master of Public Health and Master of Medical Sciences
-
-\vspace{40pt}
-
-\includegraphics[height=160pt]{EPH}
-\hspace{40pt}
-\includegraphics[height=160pt]{Medicine}
-
-\end{center}
 
@@
 
-\abstractsection{Background}Respiratory syncytial virus (RSV) causes seasonal respiratory infection with potentially serious complications in children, and leads to hospitalization rates as high as 50\% in high-risk infants.
+\abstractsection{Background}Respiratory syncytial virus (RSV) causes seasonal respiratory infection with potentially serious complications in children, and leads to hospitalization rates of up to 50\% in high-risk infants.
 Safe and effective immunoprophylaxis (palivizumab) is available, but costly.
 The American Academy of Pediatrics (AAP) recommends palivizumab only for infants at high risk of complications, and only during the RSV season.
-Although the current AAP guidelines acknowledge the existence of spatial and temporal variation in RSV incidence, they do not recommend spatial or temporal adjustments to immunoprophylaxis regimen outside of Florida.
+Although the current AAP guidelines acknowledge the existence of spatial and temporal variation in RSV incidence, they do not recommend spatial or temporal adjustments to the immunoprophylaxis regimen outside of Florida.
 In this study, we investigate the value of using spatial and temporal variation in RSV incidence to adjust the RSV prophylaxis regimen in Connecticut.
@@
 Our best-performing pragmatic alternative to the AAP guidelines was based on the regional RSV season midpoint with biweekly rounding.
-In comparison to the AAP recommendation, whose preventable fraction is \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}), that alternative yielded improvement to preventable fraction of \Sexpr{regionStrategyCoverage("all", "countyMiddle", 2)} (\Sexpr{regionStrategyCoverageCI("all", "countyMiddle", 2, level)}).
-We also found that alternative regimens adjusted for annual variation in RSV season are non-superior to spatially adjusted regimens.
+In comparison to the AAP recommendation, whose preventable fraction is \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}), that alternative yielded improvement to \Sexpr{regionStrategyCoverage("all", "countyMiddle", 2)} (\Sexpr{regionStrategyCoverageCI("all", "countyMiddle", 2, level)}).
+We also found that alternative regimens adjusted for annual variation in the RSV season are non-superior to spatially adjusted regimens.
 
@@
 
-\thispagestyle{empty}
 \clearpage
 
-\tableofcontents
-\clearpage
+\pagestyle{fancy}
 
@@
 
-\begin{multicols}{2}
+%\begin{multicols}{1}
 
@@
 
-For infants, risk factors of serious illness and hospitalization due to RSV infection include prematurity, chronic lung disease of prematurity, congenital heart disease, anatomic pulmonary abnormalities, neuromuscular disorders, trisomy 21, and immunocompromised status.\cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj} Hospitalization rate due to RSV among high-risk infants is anywhere from two to ten times higher than among infants with no comorbidities.\cite{Boyce:2000gz}
+For infants, risk factors of serious illness and hospitalization due to RSV infection include prematurity, chronic lung disease of prematurity, congenital heart disease, anatomic pulmonary abnormalities, neuromuscular disorders, trisomy 21, and immunocompromised status.\cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj} The hospitalization rate due to RSV among high-risk infants is anywhere from two to ten times higher than among infants with no comorbidities.\cite{Boyce:2000gz}
 
@@
 
-Palivizumab has been found to be effective in reducing hospitalizations due to RSV; in double-blinded trials in high-risk infants, it reduced hospitalization rate by 45-55\% compared to placebo.\cite{Group:1998ih,Feltes:2003wm} Its has also been found to be safe and well-tolerated in clinical trials.\cite{Group:1998ih}
+Palivizumab has been found to be effective in reducing hospitalizations due to RSV; in double-blinded trials in high-risk infants, it reduced the hospitalization rate by 45-55\% compared to placebo.\cite{Group:1998ih,Feltes:2003wm} Its has also been found to be safe and well-tolerated in clinical trials.\cite{Group:1998ih}
 
-Owing to the high cost, the American Academy of Pediatrics (AAP) guidelines, revised in 2014, recommend palivizumab immunoprophylaxis only for high-risk infants, and only during RSV season.\cite{Anonymous:1998up,AmericanAcademyofPediatricsCommitteeonInfectiousDiseasesandCommitteeonFetusandNewborn:2003ug,AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
+Owing to the high cost, the American Academy of Pediatrics (AAP) guidelines, revised in 2014, recommend palivizumab immunoprophylaxis only for high-risk infants, and only during the RSV season.\cite{Anonymous:1998up,AmericanAcademyofPediatricsCommitteeonInfectiousDiseasesandCommitteeonFetusandNewborn:2003ug,AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
 
@@
 RSV seasonality has been established throughout the United States, based on National Respiratory and Enteric Virus Surveillance System data.
-In all states except for Florida, it shows a stable season onset between mid-November and early January and a stable season offset between mid-March and late April.\cite{CentersforDiseaseControlandPreventionCDC:2011wt,CentersforDiseaseControlandPreventionCDC:2013wv} RSV season in Florida begins approximately two months earlier than in other states.
+In all states except for Florida, it shows an annual or biennial cycle with a stable seasonal onset between mid-November and early January and a stable seasonal offset between mid-March and late April.\cite{CentersforDiseaseControlandPreventionCDC:2011wt,CentersforDiseaseControlandPreventionCDC:2013wv} RSV season in Florida begins approximately two months earlier than in other states.
 \cite{CentersforDiseaseControlandPreventionCDC:2013wv}
 
-The AAP acknowledges the potential significance of spatial and temporal variation in RSV incidence, but --- outside of Florida --- does not recommend local variance from nation-wide prophylaxis guidelines.\cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
+The AAP acknowledges the potential significance of spatial and temporal variation in RSV incidence, but --- outside of Florida --- does not recommend local variance from nationwide prophylaxis guidelines.\cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
 
@@
 
-Nationwide spatial variability of RSV season has been established by the Centers for Disease Control and Prevention (CDC).\cite{CentersforDiseaseControlandPreventionCDC:2011wt,CentersforDiseaseControlandPreventionCDC:2013wv}
+TODO Nationwide spatial variability of RSV season has been established by the Centers for Disease Control and Prevention (CDC).\cite{CentersforDiseaseControlandPreventionCDC:2011wt,CentersforDiseaseControlandPreventionCDC:2013wv}
 
 In Connecticut, the Department of Public Health (CT DPH), via its Office of Health Care Access (OHCA), maintains a database of all hospitalizations in every non-federal short-stay acute-care general hospital in the state.
-Previous analysis of this database at the Yale University School of Public Health has shown regional variability in time of peak RSV incidence within Connecticut.\cite{Noveroske:y4fi3188} No prior research is available regarding year-to-year variation in timing of RSV season in Connecticut.
+Previous analysis of this database has shown regional variability in time of peak RSV incidence within Connecticut.\cite{Noveroske:y4fi3188} No prior research is available regarding year-to-year variation in timing of RSV season in Connecticut.
 
@@
 	\item To what extent does regional variability of RSV incidence in Connecticut impact the effectiveness of the AAP-recommended prophylaxis regimen?
-	\item Can we use spatial analysis of RSV to propose alternative regimens that would increase the benefits of prophylaxis in comparison to the AAP-recommended regimen, without increasing the total cost of the prophylactics the regimen?
+	\item Can we use spatial analysis of RSV to propose alternative regimens that would increase the benefits of prophylaxis in comparison to the AAP-recommended regimen, without increasing the total cost of the regimen?
 	\item Is there year-to-year variation in timing of RSV season in Connecticut?
@@
 \end{itemize}
-
-The study was approved by the Human Investigation Committees at Yale University and the CT DPH. The authors assume full responsibility for analyses and interpretation of the data obtained from CT DPH.
 
@@
 \begin{itemize}
-    \item the postal code of residence listed in patient's medical record was in Connecticut\footnote{According to the zipcode $\rightarrow$ state mapping in R \texttt{zipcode} package version 1.0}, and
+    \item the postal code of residence listed the in patient's medical record was in Connecticut, and
     \item the hospital stay was associated with ICD-9-CM diagnosis code \texttt{079.6} (RSV), \texttt{466.11} (Acute bronchiolitis due to RSV), or \texttt{480.1} (Pneumonia due to RSV).
@@
 
-Using the OHCA weekly hospitalization statistics, we identified \Sexpr{nrow(dataset)} RSV-associated hospitalizations in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)} (inclusive).
+Using the OHCA weekly hospitalization statistics, we identified \Sexpr{prettyNum(nrow(dataset), big.mark=",")} RSV-associated hospitalizations in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)} (inclusive).
 
@@
 
-Given that RSV seasons peak early in each calendar year, we assigned to each surveillance year 12 months of data starting in July of previous year.
+Given that RSV seasons peak early in each calendar year, we designated the surveillance year as the 12-month period beginning  in July.
 OHCA provided us with hospitalization records aggregated into Monday-Sunday calendar weeks; we assigned the first full calendar week of July to be surveillance week 1 in each surveillance year.
 
-Due to changes in diagnostic coding, we excluded data prior to July 1996; we similarly excluded data starting after June 2013, due to incompleteness.
+Due to changes in diagnostic coding, we excluded data prior to July 1996; we similarly excluded data starting after June 2013 due to incompleteness.
 
@@
 
-We were willing to assume that RSV incidence is the result of a Poisson process whose $\log$ can be modeled as a piecewise twice-differentiable function of time.
+We assumed that RSV incidence is the result of a Poisson process whose $\log$ can be modeled as a piecewise twice-differentiable function of time.
 To meet those criteria and assumptions, we chose a log-linked generalized additive model (GAM) with penalized cubic B-splines for our analysis.
@@
 
-We chose to aggregate low-RSV counties into a single region because our analysis in those counties individually would have yielded results with unacceptably low statistical power.
+We chose to aggregate low-RSV counties into a single region because our analysis in those counties individually would have yielded results with low statistical power.
 
@@
 We began by assessing the current AAP RSV prophylaxis guidelines.
-These guidelines recommend RSV prophylaxis with 5 monthly doses of palivizumab, starting in November, for all high-risk infants in their first year of life; in the second year of life, only some subgroups are recommended to receive palivizumab.
-
+These guidelines recommend RSV prophylaxis with 5 monthly doses of palivizumab, starting in November, for all high-risk infants in their first year of life; in the second year of life, palivizumab is only recommended for some subgroups.
 For simplicity, we assumed that protection by palivizumab begins on November 15th and lasts 24 weeks.
@@
 
-The choice of \Sexpr{seasonThreshold * 100}\% and \Sexpr{(1 - seasonThreshold) * 100}\% incidence thresholds was based on our intent to use estimates of RSV season onset and offset to put forth alternative prophylaxis regimens (as described below), while maintaining 5-month dosing schedule (and therefore not increasing medication cost).
+The choice of \Sexpr{seasonThreshold * 100}\% and \Sexpr{(1 - seasonThreshold) * 100}\% incidence thresholds was based on our intent to use estimates of RSV season onset and offset to put forth alternative prophylaxis regimens (as described below), while maintaining the 5-month dosing schedule (and therefore not increasing medication cost).
 Incidence cutoffs other than \Sexpr{seasonThreshold * 100}\% and \Sexpr{(1 - seasonThreshold) * 100}\% were briefly investigated, but quickly ruled out because they produced prophylaxis regimens starting long prior to RSV season onset or ending long after RSV season offset, and therefore had very low preventable fractions.
@@
 Our analysis thus far assumed that RSV seasons are similar year-to-year.
-To analyze the effects of year-to-year variation between RSV seasons on prophylaxis regimens, we chose to aggregate our data into (overlapping) periods of three consecutive years --- in order to maintain a higher level of statistical power, as well as to limit impact of short-term variation on our results.
+To analyze the effects on prophylaxis regimens of year-to-year variation between RSV seasons, we chose to aggregate our data into (overlapping) periods of three consecutive years --- in order to maintain a higher level of statistical power, as well as to limit the impact of short-term variation on our results.
 
-This gave us \Sexpr{year(endDate) - year(startDate) -1} three-year periods, with the \Sexpr{formatYear(startDate + 2*365)} period covering surveillance years \Sexpr{formatYear(startDate)} through \Sexpr{formatYear(startDate + 2*365)}, and the \Sexpr{formatYear(endDate)} period covering \Sexpr{formatYear(endDate - 2*365)} through \Sexpr{formatYear(endDate)}.
+TODO This gave us \Sexpr{year(endDate) - year(startDate) -1} three-year periods, with the \Sexpr{formatYear(startDate + 2*365)} period covering surveillance years \Sexpr{formatYear(startDate)} through \Sexpr{formatYear(startDate + 2*365)}, and the \Sexpr{formatYear(endDate)} period covering \Sexpr{formatYear(endDate - 2*365)} through \Sexpr{formatYear(endDate)}.
 
-We began our temporal analysis by estimating onset and offset for each three-year period, using the same penalized spline GAM as all-years analysis, producing --- as before --- statewide and regional estimates of \Sexpr{seasonThreshold * 100}\% onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset.
+We began our temporal analysis by estimating onset and offset for each three-year period, using the same penalized spline GAM as for the all-years analysis, producing --- as before --- statewide and regional estimates of \Sexpr{seasonThreshold * 100}\% onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset.
 
@@
 % column width = 3.20929 in
+
+The study was approved by the Human Investigation Committees at Yale University and the CT DPH. The authors assume full responsibility for analyses and interpretation of the data obtained from CT DPH.
 
@@
 
-Meanwhile, in comparison with the statewide RSV season onset and offset, the low-RSV region has RSV season with later onset at \Sexpr{regionOnset("lowIncidence")} weeks (\Sexpr{regionOnsetCI("all", level)} weeks); season offset shows no change from the statewide median (Figure \ref{fig:seasonByRegion}).
+TODO Meanwhile, in comparison with the statewide RSV season onset and offset, the low-RSV region has RSV season with later onset at \Sexpr{regionOnset("lowIncidence")} weeks (\Sexpr{regionOnsetCI("all", level)} weeks); season offset shows no change from the statewide median (Figure \ref{fig:seasonByRegion}).
 
@@
 
-This is caused by temporal misalignment between the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each region), and the timing of the AAP-recommended prophylaxis regimen (Figure \ref{fig:coverageByRegionAAPInsight}).
-Fairfield county, owing to its early season onset, sees disproportionately many cases before prophylaxis administration begins; on the other hand, the low-RSV counties, owing to their late season onset and relatively shorter RSV seasons, see almost all of their RSV cases within the prophylaxis window.
+This is caused by temporal misalignment between the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each region) and the timing of the AAP-recommended prophylaxis regimen (Figure \ref{fig:coverageByRegionAAPInsight}).
+Fairfield county, owing to its early season onset, sees disproportionately more cases before prophylaxis administration begins; on the other hand, the low-RSV counties, owing to their late season onset and relatively shorter RSV seasons, see almost all of their RSV cases within the prophylaxis window.
 
@@
 
-\columnbreak
+%\columnbreak
 

### 2019-02-15 Paper/RSVOptimization.rnw
Draft watermark
Delete thesis-related files that I don’t need for the paper

--- 2018-01-24 Thesis/Thesis.rnw
@@
 
-\begin{center}
-
-\vspace{20pt}
-\large Submitted to the School of Public Health and the School of Medicine, in partial fulfillment of the requirements for the degrees of Master of Public Health and Master of Medical Sciences
-
-\vspace{40pt}
-
-\includegraphics[height=160pt]{EPH}
-\hspace{40pt}
-\includegraphics[height=160pt]{Medicine}
-
-\end{center}
-
 \thispagestyle{firstpage}
 
-\clearpage
+\cleardoublepage
 \endgroup
@@
 
-\thispagestyle{empty}
-\clearpage
+\cleardoublepage
 
+\pagestyle{fancy}
 \tableofcontents

### 2019-02-16 Analysis/RSV.R
Fixed error where “count” was matching “county”

@@ -486,7 +486,7 @@ for (c in levels(obsByCountyYear$county)) {
 
 slidingStratUnprotectedByCounty = slidingStratUnprotectedSimByCountyYear %>%
   group_by(county, outbreak.sim) %>%
-  summarize_at(vars(contains("total"), contains("count")), sum) %>%
+  summarize_at(vars(contains("total"), contains(".count")), sum) %>%
   group_by(county, outbreak.sim) %>%
   do((function(df) {
     stratNames = names(ppxSlidingStrategies())

### 2019-02-17 Paper/RSVOptimization.rnw
Moved todos
Ginny’s non-structural feedback
Qualify calls to knitr

--- 2019-02-15 Paper/RSVOptimization.rnw
@@
 <<options, echo=FALSE>>=
-    opts_chunk$set(echo=FALSE, message=FALSE)
+    knitr::opts_chunk$set(echo=FALSE, message=FALSE)
 @
@@
 <<load>>=
-read_chunk("../Analysis/RSV.R")
-read_chunk("../Paper/RSVOptimization.R")
+knitr::read_chunk("../Analysis/RSV.R")
+knitr::read_chunk("../Paper/RSVOptimization.R")
 @
@@
 \usepackage{tikz}
-%\usepackage{draftwatermark}
-%\SetWatermarkScale{1}
-%\SetWatermarkAngle{45}
-%\SetWatermarkFontSize{4ex}
-%\SetWatermarkHorCenter{12ex}
-%\SetWatermarkVerCenter{12ex}
-%\SetWatermarkLightness{.5}
-%\SetWatermarkText{DRAFT 5}
+\usepackage{draftwatermark}
+\SetWatermarkScale{1}
+\SetWatermarkAngle{45}
+\SetWatermarkFontSize{4ex}
+\SetWatermarkHorCenter{12ex}
+\SetWatermarkVerCenter{12ex}
+\SetWatermarkLightness{.5}
+\SetWatermarkText{DRAFT 1}
 

### 2019-02-17 bootstrap.py
GitLab CI

@@ -1,0 +1,24 @@
+import digitalocean
+import sys
+from os import environ
+from argparse import ArgumentParser
+
+parser = ArgumentParser()
+parser.add_argument("action")
+
+args = parser.parse_args()
+
+token = environ['DO_API_TOKEN']
+prefix = environ['DO_DROPLET_PREFIX']
+
+manager = digitalocean.Manager(token=token)
+droplets = [droplet for droplet in manager.get_all_droplets() if droplet.name.startswith(prefix)]
+if args.action == "on" and not droplets:
+    print(f"No droplets matching {prefix} found", file=sys.stderr)
+    sys.exit(1)
+    
+for droplet in droplets:
+    if args.action == "on":
+        droplet.power_on()
+    else:
+        droplet.shutdown()

### 2019-02-18 bootstrap.py
Migrating digital ocean into separate YAML

@@ -1,24 +1,0 @@
-import digitalocean
-import sys
-from os import environ
-from argparse import ArgumentParser
-
-parser = ArgumentParser()
-parser.add_argument("action")
-
-args = parser.parse_args()
-
-token = environ['DO_API_TOKEN']
-prefix = environ['DO_DROPLET_PREFIX']
-
-manager = digitalocean.Manager(token=token)
-droplets = [droplet for droplet in manager.get_all_droplets() if droplet.name.startswith(prefix)]
-if args.action == "on" and not droplets:
-    print(f"No droplets matching {prefix} found", file=sys.stderr)
-    sys.exit(1)
-    
-for droplet in droplets:
-    if args.action == "on":
-        droplet.power_on()
-    else:
-        droplet.shutdown()

### 2019-02-19 Analysis/RSV.R
Fixing dplyr warning

@@ -216,12 +216,12 @@ outbreak.calc.unprotected = function(strategies) {
     total = sum(fit)
 
     unprotected %>%
-      rename_all(funs(
+      rename_all(list(
         sprintf("%s.count", .)
       )) %>%
       cbind(
         (unprotected / total) %>%
-          rename_all(funs(
+          rename_all(list(
             sprintf("%s.frac", .)
           ))
       ) %>%

### 2019-02-19 Analysis/RSV.R
Revert "Fixing dplyr warning"
This reverts commit de6339481c6621377e5688defdfba6637ec38736.

@@ -216,12 +216,12 @@ outbreak.calc.unprotected = function(strategies) {
     total = sum(fit)
 
     unprotected %>%
-      rename_all(list(
+      rename_all(funs(
         sprintf("%s.count", .)
       )) %>%
       cbind(
         (unprotected / total) %>%
-          rename_all(list(
+          rename_all(funs(
             sprintf("%s.frac", .)
           ))
       ) %>%

### 2019-02-19 build/docker/bootstrap/bootstrap.py
Dispatch bootstrap

@@ -1,0 +1,52 @@
+#!/usr/bin/env python
+
+from argparse import ArgumentParser
+from subprocess import check_call
+from tempfile import mkdtemp
+from shutil import rmtree
+import io
+from os import path
+
+parser = ArgumentParser()
+parser.add_argument(dest="dotoken", help="Digital Ocean API token")
+parser.add_argument(dest="gltoken", help="GitLab CI runner registration token")
+
+args = parser.parse_args()
+
+tempdir = mkdtemp()
+try:
+    userdata = path.join(tempdir, "bootstrap-cloud-config.yml")
+    with io.open(userdata, "w") as tempfile:
+        tempfile.write(io.open(path.join(path.realpath(path.dirname(__file__)), "bootstrap-cloud-config.yml"), encoding="utf-8").read() % dict(
+            DIGITALOCEAN_API_TOKEN=args.dotoken,
+            GITLAB_CI_REGISTRATION_TOKEN=args.gltoken,
+        ))
+
+    name = "gitlab-ci-dispatch"
+    try:
+        check_call([
+            "docker-machine", "rm", 
+            "--force", 
+            name
+        ])
+    except:
+        pass
+
+    io.open("/tmp/foo", "w").write(io.open(userdata).read())
+    check_call([
+        "docker-machine", "create", 
+        "--driver=digitalocean", 
+        "--digitalocean-access-token=%s" % args.dotoken,
+        "--digitalocean-image=ubuntu-16-04-x64",
+        "--digitalocean-monitoring",
+        "--digitalocean-region=sfo2",
+        "--digitalocean-size=s-1vcpu-2gb",
+        "--digitalocean-tags=gitlab-ci",
+        "--digitalocean-userdata=%s" % userdata,
+        name
+    ])
+finally:
+    try:
+        rmtree(tempdir)
+    except:
+        pass

### 2019-02-20 build/docker/bootstrap/bootstrap.py
Scripts for provisioning CI dispatcher

@@ -9,6 +9,8 @@ from os import path
 
 parser = ArgumentParser()
 parser.add_argument(dest="dotoken", help="Digital Ocean API token")
+parser.add_argument(dest="s3token", help="Digital Ocan Spaces access token")
+parser.add_argument(dest="s3secret", help="Digital Ocan Spaces secret key")
 parser.add_argument(dest="gltoken", help="GitLab CI runner registration token")
 
 args = parser.parse_args()
@@ -20,9 +22,26 @@ try:
         tempfile.write(io.open(path.join(path.realpath(path.dirname(__file__)), "bootstrap-cloud-config.yml"), encoding="utf-8").read() % dict(
             DIGITALOCEAN_API_TOKEN=args.dotoken,
             GITLAB_CI_REGISTRATION_TOKEN=args.gltoken,
+            S3_ACCESS_KEY=args.s3token,
+            S3_SECRET_KEY=args.s3secret,
         ))
 
     name = "gitlab-ci-dispatch"
+    try:
+        check_call([
+            "docker-machine", "ssh", name,
+            "gitlab-runner", "unregister", "--all-runners"
+        ])
+    except:
+        pass
+    try:
+        check_call([
+            "docker-machine", "ssh", name,
+            "docker-machine", "ls", "--quiet", "--format", ".", "|", 
+            "xargs", "docker-machine", "rm", "--force"
+        ])
+    except:
+        pass
     try:
         check_call([
             "docker-machine", "rm", 
@@ -40,7 +59,7 @@ try:
         "--digitalocean-image=ubuntu-16-04-x64",
         "--digitalocean-monitoring",
         "--digitalocean-region=sfo2",
-        "--digitalocean-size=s-1vcpu-2gb",
+        "--digitalocean-size=s-1vcpu-1gb",
         "--digitalocean-tags=gitlab-ci",
         "--digitalocean-userdata=%s" % userdata,
         name

### 2019-02-20 Paper/RSVOptimization.R
Fixing problems with figure output location

@@ -6,11 +6,15 @@ library(rgdal)
 library(ggplot2)
 options(tikzDefaultEngine='pdftex')
 
-figuresDir = ".texpadtmp/figures"
+texOutputDir = Sys.getenv("TEX_OUTPUT_DIR")
+if (texOutputDir == "") {
+  texOutputDir = ".texpadtmp"
+}
+figuresDir = paste0(texOutputDir, "/figures")
 if (!dir.exists(figuresDir)) {
   dir.create(figuresDir, recursive=TRUE)
 }
-options(tikzMetricsDictionary='.texpadtmp/tikzDictionary.dat')
+options(tikzMetricsDictionary=paste0(texOutputDir, '/tikzDictionary.dat'))
 
 inlinePlotWidth = 3.1
 inlinePlotHeight = 2.5

### 2019-02-20 build/docker/bootstrap/bootstrap.py
Moving to a separate repo

@@ -1,71 +1,0 @@
-#!/usr/bin/env python
-
-from argparse import ArgumentParser
-from subprocess import check_call
-from tempfile import mkdtemp
-from shutil import rmtree
-import io
-from os import path
-
-parser = ArgumentParser()
-parser.add_argument(dest="dotoken", help="Digital Ocean API token")
-parser.add_argument(dest="s3token", help="Digital Ocan Spaces access token")
-parser.add_argument(dest="s3secret", help="Digital Ocan Spaces secret key")
-parser.add_argument(dest="gltoken", help="GitLab CI runner registration token")
-
-args = parser.parse_args()
-
-tempdir = mkdtemp()
-try:
-    userdata = path.join(tempdir, "bootstrap-cloud-config.yml")
-    with io.open(userdata, "w") as tempfile:
-        tempfile.write(io.open(path.join(path.realpath(path.dirname(__file__)), "bootstrap-cloud-config.yml"), encoding="utf-8").read() % dict(
-            DIGITALOCEAN_API_TOKEN=args.dotoken,
-            GITLAB_CI_REGISTRATION_TOKEN=args.gltoken,
-            S3_ACCESS_KEY=args.s3token,
-            S3_SECRET_KEY=args.s3secret,
-        ))
-
-    name = "gitlab-ci-dispatch"
-    try:
-        check_call([
-            "docker-machine", "ssh", name,
-            "gitlab-runner", "unregister", "--all-runners"
-        ])
-    except:
-        pass
-    try:
-        check_call([
-            "docker-machine", "ssh", name,
-            "docker-machine", "ls", "--quiet", "--format", ".", "|", 
-            "xargs", "docker-machine", "rm", "--force"
-        ])
-    except:
-        pass
-    try:
-        check_call([
-            "docker-machine", "rm", 
-            "--force", 
-            name
-        ])
-    except:
-        pass
-
-    io.open("/tmp/foo", "w").write(io.open(userdata).read())
-    check_call([
-        "docker-machine", "create", 
-        "--driver=digitalocean", 
-        "--digitalocean-access-token=%s" % args.dotoken,
-        "--digitalocean-image=ubuntu-16-04-x64",
-        "--digitalocean-monitoring",
-        "--digitalocean-region=sfo2",
-        "--digitalocean-size=s-1vcpu-1gb",
-        "--digitalocean-tags=gitlab-ci",
-        "--digitalocean-userdata=%s" % userdata,
[…]

### 2019-02-25 Analysis/RSV.R
Draft # of simulations

@@ -14,7 +14,7 @@ library(maps)
 data(zipcode)
 set.seed(0)
 
-simulations = 2000
+simulations = 20
 
 # *** Data munging helpers
 

### 2019-02-25 Paper/RSVOptimization.rnw
Reordering to give knitr a chance to define knitrout
Now building with GitLab CI
Assorted feedback from Dan

@@
+\documentclass[10pt,letter,twoside]{article}
+
 <<options, echo=FALSE>>=
-    knitr::opts_chunk$set(echo=FALSE, message=FALSE)
+    knitr::opts_chunk$set(echo=FALSE, message=FALSE, error=FALSE)
 @
@@
 @
-
-\documentclass[10pt,letter,twoside]{article}
 
@@
 
-\abstractsection{Methods}We describe a generalized additive model of RSV incidence using cubic cyclic penalized splines and apply that model to hospital admissions in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)}.
-We use the model to estimate the fraction of all RSV cases in Connecticut occurring while immunoprophylaxis (administered according to the AAP guidelines) offers protection from RSV infection (``preventable fraction'').
-We also formulate several alternative immunoprophylaxis regimens, with the same net pharmaceutical cost as the AAP-recommended regimen, and similarly estimate their preventable fraction.
+\abstractsection{Methods}We obtained weekly ZIP-code-level counts of RSV-associated hospital admission in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)}.
+We fit smoothed curves to these admission counts using a generalized additive model with cubic cyclic penalized splines, and used these curves to estimate the fraction of all RSV cases in Connecticut occurring during the period of protection offered by RSV immunoprophylaxis (``preventable fraction'') under the AAP guidelines.
+We then used the same model to estimate protection conferred by immunoprophylaxis regimens with alternate start dates (but unchanged duration and net pharmaceutical cost).
 
@@
 
-\subsection{RSV immunoprophylaxis}
+Since 1998, a monoclonal antibody (palivizumab), has been approved in the US for prevention of RSV infection in high-risk infants less than 2 years old.
+Palivizumab is administered via intramuscular injection and requires five monthly doses, priced at \$1500-\$3000 per dose.\cite{Hampp:2011ju,Andabaka:2013dr} Palivizumab has been found to be effective in reducing hospitalizations due to RSV; in double-blinded trials in high-risk infants, it reduced the hospitalization rate by 45-55\% compared to placebo.\cite{Group:1998ih,Feltes:2003wm} It has also been found to be safe and well-tolerated in clinical trials.\cite{Group:1998ih} Owing to the high cost, the 2014 revision of the American Academy of Pediatrics (AAP) RSV prophylaxis guidelines, recommends palivizumab only for high-risk infants, and only during the RSV season.\cite{Anonymous:1998up,AmericanAcademyofPediatricsCommitteeonInfectiousDiseasesandCommitteeonFetusandNewborn:2003ug,AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
 
-Immunoprophylaxis with palivizumab, a monoclonal antibody medication, has been approved in the US for prevention of RSV infection since 1998.
-Palivizumab is administered via intramuscular injection and requires five monthly doses, priced at \$1500-\$3000 per dose.\cite{Hampp:2011ju,Andabaka:2013dr}
-
-Palivizumab has been found to be effective in reducing hospitalizations due to RSV; in double-blinded trials in high-risk infants, it reduced the hospitalization rate by 45-55\% compared to placebo.\cite{Group:1998ih,Feltes:2003wm} Its has also been found to be safe and well-tolerated in clinical trials.\cite{Group:1998ih}
-
-Owing to the high cost, the American Academy of Pediatrics (AAP) guidelines, revised in 2014, recommend palivizumab immunoprophylaxis only for high-risk infants, and only during the RSV season.\cite{Anonymous:1998up,AmericanAcademyofPediatricsCommitteeonInfectiousDiseasesandCommitteeonFetusandNewborn:2003ug,AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
-
-\subsection{RSV seasonality}
-
-RSV seasonality has been established throughout the United States, based on National Respiratory and Enteric Virus Surveillance System data.
-In all states except for Florida, it shows an annual or biennial cycle with a stable seasonal onset between mid-November and early January and a stable seasonal offset between mid-March and late April.\cite{CentersforDiseaseControlandPreventionCDC:2011wt,CentersforDiseaseControlandPreventionCDC:2013wv} RSV season in Florida begins approximately two months earlier than in other states.
+RSV seasonality and spatial variability have been established throughout the United States, based on National Respiratory and Enteric Virus Surveillance System data.
+In all states except for Florida, RSV shows an annual or biennial cycle with a stable seasonal onset between mid-November and early January and a stable seasonal offset between mid-March and late April.\cite{CentersforDiseaseControlandPreventionCDC:2011wt,CentersforDiseaseControlandPreventionCDC:2013wv} RSV season in Florida begins approximately two months earlier than in other states.
 \cite{CentersforDiseaseControlandPreventionCDC:2013wv}
@@
 
-\subsection{Spatio-temporal variability of RSV}
-
-TODO Nationwide spatial variability of RSV season has been established by the Centers for Disease Control and Prevention (CDC).\cite{CentersforDiseaseControlandPreventionCDC:2011wt,CentersforDiseaseControlandPreventionCDC:2013wv}
-
-In Connecticut, the Department of Public Health (CT DPH), via its Office of Health Care Access (OHCA), maintains a database of all hospitalizations in every non-federal short-stay acute-care general hospital in the state.
-Previous analysis of this database has shown regional variability in time of peak RSV incidence within Connecticut.\cite{Noveroske:y4fi3188} No prior research is available regarding year-to-year variation in timing of RSV season in Connecticut.
+Previous analysis of RSV-associated hospital admissions in Connecticu has shown regional variability in time of peak RSV incidence within Connecticut.\cite{Noveroske:y4fi3188} No prior research is available regarding year-to-year variation in timing of RSV season in Connecticut.
 
@@
 
-Motivated by the AAP's recognition of the significance of spatial variation in formulating prophylaxis guidelines, and the known spatial variability of RSV incidence in Connecticut, we aim to determine whether spatial and temporal variability can be used to optimize RSV prophylaxis in Connecticut by asking these questions:
+Motivated by the AAP's recognition of the significance of spatial variation in formulating prophylaxis guidelines, and the known spatial variability of RSV incidence in Connecticut, we aim to determine whether spatial and temporal variability can be used to optimize RSV prophylaxis in Connecticut by
 
@@
 
+In Connecticut, the Department of Public Health (CT DPH), via its Office of Health Care Access (OHCA), maintains a database of all hospitalizations in every non-federal short-stay acute-care general hospital in the state.
 We defined an RSV-associated hospitalization in Connecticut to be a hospital stay for which:
@@
 
+The study was approved by the Human Investigation Committees at Yale University and the CT DPH. The authors assume full responsibility for analyses and interpretation of the data obtained from CT DPH.
+
 % TODO patient age
@@
 
-Given that RSV seasons peak early in each calendar year, we designated the surveillance year as the 12-month period beginning  in July.
-OHCA provided us with hospitalization records aggregated into Monday-Sunday calendar weeks; we assigned the first full calendar week of July to be surveillance week 1 in each surveillance year.
-
-Due to changes in diagnostic coding, we excluded data prior to July 1996; we similarly excluded data starting after June 2013 due to incompleteness.
+We designated epidemiological years as beginning in the first full week of July, in order to accommodate the timing of RSV peaks (which span two calendar years) and the limitations of hospitalization records (which OHCA aggregated into Monday-Sunday calendar weeks).
+Due to changes in diagnostic coding, we excluded data prior to July 1996; we similarly excluded data after June 2013 due to incompleteness.
 
@@
 
-Our goal was to construct a model of annual RSV incidence that allowed us to easily estimate complex characteristics of RSV seasons, such as season onset and offset.
-To that end, we looked for a model that allowed easy sampling of estimated model parameters; coupling this with Monte Carlo sampling --- after transforming model parameters into response variables --- allowed us to sample arbitrary response variables.
+Our goal was to construct a model of annual RSV incidence that allowed us to obtain interval estimates of complex characteristics of RSV seasons, such as season onset, season offset, and preventable fraction of a prophylaxis regimen.
+To that end, we fit smooth curves through annual RSV hospitalization data, and used resampling to obtain interval estimates.
+(TODO See supplement.)
 
-We assumed that RSV incidence is the result of a Poisson process whose $\log$ can be modeled as a piecewise twice-differentiable function of time.
+%To that end, we looked for a model that allowed easy sampling of estimated model parameters; coupling this with Monte Carlo sampling --- after transforming model parameters into response variables --- allowed us to sample arbitrary response variables.
+%
+%We assumed that RSV incidence is the result of a Poisson process whose $\log$ can be modeled as a piecewise twice-differentiable function of time.
 To meet those criteria and assumptions, we chose a log-linked generalized additive model (GAM) with penalized cubic B-splines for our analysis.
-
-% Looked for prior art on using GAM/pspline for ID epi, didn't find anything that was relevant. (Not even by Goldstein or Lipsitch.)
-
-We developed a custom R package for estimation of arbitrary characteristics of infectious disease outbreaks (as long as the outbreaks are amenable to GAM); this package is available at \href{https://github.com/airbornemint/outbreak-inference}{\nolinkurl{github.com/airbornemint/outbreak-inference}}.
+%
+%% Looked for prior work using GAM/pspline for ID epi, didn't find anything that was relevant. (Not even by Goldstein or Lipsitch.)
+%
+%We developed a custom R package for estimation of arbitrary characteristics of infectious disease outbreaks (as long as the outbreaks are amenable to GAM); this package is available at \href{https://github.com/airbornemint/outbreak-inference}{\nolinkurl{github.com/airbornemint/outbreak-inference}}.
 
@@
 % column width = 3.20929 in
-
-The study was approved by the Human Investigation Committees at Yale University and the CT DPH. The authors assume full responsibility for analyses and interpretation of the data obtained from CT DPH.
 

### 2019-02-25 Analysis/RSV.Rmd
More useful overview plot

--- 2018-01-16 Analysis/RSV.Rmd
@@
 ```{r setup, include=FALSE, error=FALSE, warning=FALSE, message=FALSE}
-install.packages(c("dplyr", "zipcode", "reshape", "mgcv", "ggplot2", "gridExtra", "devtools", "data.table", "tikzDevice", "splitstackshape", "maps", "mapproj"))
+install.packages(c("dplyr", "zipcode", "reshape", "mgcv", "ggplot2", "gridExtra", "devtools", "data.table", "tikzDevice", "splitstackshape", "maps", "mapproj", "rgdal", "rgeos", "scales"))
 library(devtools)
@@
 install_github("airbornemint/outbreak-predict")
+library(scales)
 ```
@@
 ```{r}
-ggplot(dataset %>% 
-         group_by(weeki) %>%
+ggplot(datasetAll %>% 
+         group_by(weeki, adate) %>%
          summarize(rsv=sum(rsv)), 
-       aes(x=weeki, y=rsv)) +
+       aes(x=adate, y=rsv)) +
   geom_hline(aes(yintercept = 0)) +
   geom_line() +
-  labs(y="RSV cases/week", x="Time", title="All counties")
+  labs(y="RSV cases/week", x="Time", title="All counties") +
+  scale_x_date(labels=date_format("%Y"), date_breaks="1 year")
 

### 2019-02-25 Analysis/RSV.R

@@ -60,15 +60,18 @@ epiweek = function(date) {
 }
 
 # Add week-of-year, with zero = first week of January, drop first 5.5 years because of coding differences
-dataset = admissions %>%
+datasetAll = admissions %>%
   mutate(
     adate=as.Date(adate, "%d%b%Y"),
     epiyear=epiyear(adate),
     epiyday=epiyday(adate),
     epiweek=epiweek(adate)
   ) %>%
-  filter(epiyear >= 1996, epiyear <= 2013) %>%
   select(patzip, adate, weeki, rsv, epiyear, epiyday, epiweek)
+
+dataset = datasetAll %>%
+  filter(epiyear >= 1996, epiyear <= 2013)
+  
 # Add state based on zipcode and drop everything not in CT
 zipState = zipcode %>% select(zip, state)
 dataset = dataset %>%

### 2019-02-25 Analysis/RSV.R
Fixing disagreement about when an epi year starts

@@ -48,11 +48,11 @@ ppxRounding = c(0, 1, 2, 4)
 admissions = fread("../ct rsv time series.csv", sep=",", header=TRUE, colClasses=c("patzip"="character"))
 
 epiyear = function(date) {
-  ifelse(month(date) > 6, year(date) + 1, year(date))
+  ifelse(month(date) > 6, year(date), year(date) - 1)
 }
 
 epiyday = function(date) {
-  as.numeric(date - as.Date(ISOdate(epiyear(date) - 1, 6, 30)))
+  as.numeric(date - as.Date(ISOdate(epiyear(date), 6, 30)))
 }
 
 epiweek = function(date) {
@@ -70,7 +70,7 @@ datasetAll = admissions %>%
   select(patzip, adate, weeki, rsv, epiyear, epiyday, epiweek)
 
 dataset = datasetAll %>%
-  filter(epiyear >= 1996, epiyear <= 2013)
+  filter(epiyear >= 1996, epiyear <= 2012)
   
 # Add state based on zipcode and drop everything not in CT
 zipState = zipcode %>% select(zip, state)

### 2019-02-25 Analysis/RSV.R
Fixing dplyr deprecation

@@ -219,13 +219,13 @@ outbreak.calc.unprotected = function(strategies) {
     total = sum(fit)
 
     unprotected %>%
-      rename_all(funs(
-        sprintf("%s.count", .)
+      rename_all(list(
+        sprintf=~sprintf("%s.count", .)
       )) %>%
       cbind(
         (unprotected / total) %>%
-          rename_all(funs(
-            sprintf("%s.frac", .)
+          rename_all(list(
+            sprintf=~sprintf("%s.frac", .)
           ))
       ) %>%
       mutate(total=total)

### 2019-02-26 Paper/RSVOptimization.rnw
Mucking around with knitr integration
Typo

@@
-\documentclass[10pt,letter,twoside]{article}
-
-<<options, echo=FALSE>>=
-    knitr::opts_chunk$set(echo=FALSE, message=FALSE, error=FALSE)
-@
-
-<<load>>=
-knitr::read_chunk("../Analysis/RSV.R")
-knitr::read_chunk("../Paper/RSVOptimization.R")
-@
-
-<<libraries, cache=FALSE>>=
-@
-
-<<external, cache=TRUE>>=
-@
-
-<<util, warning=FALSE>>=
-@
-
+\documentclass[10pt,letter]{article}
 \usepackage{multicol,float}
@@
 \input{structure.tex}
-\edef\figuresDir{\Sexpr{figuresDir}}
 
@@
 
+<<options, echo=FALSE>>=
+    knitr::opts_chunk$set(echo=FALSE, message=FALSE, error=FALSE)
+@
+
+<<load>>=
+knitr::read_chunk("../Analysis/RSV.R")
+knitr::read_chunk("../Paper/RSVOptimization.R")
+@
+
+<<libraries, cache=FALSE>>=
+@
+
+<<external, cache=TRUE>>=
+@
+
+<<util, warning=FALSE>>=
+@
+
+\edef\figuresDir{\Sexpr{figuresDir}}
 \title{Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}}
@@
 \begin{document}
+% \SweaveOpts{concordance=TRUE}
 
@@
 
-We then compared those regimens to the one recommended by AAP and to the six spatially adjusted alternatives (with no calendrical rounding) discussed above.
+We then compared those regimens to the one recommended by the AAP and to the six spatially adjusted alternatives (with no calendrical rounding) discussed above.
 

### 2019-02-27 Paper/RSVOptimization.rnw
Don’t use float* outside of multicols
Offloading model details to supplement

@@
 \documentclass[10pt,letter]{article}
-\usepackage{multicol,float}
+\usepackage{float}
 \floatplacement{figure}{H}
-\raggedcolumns
+
+\usepackage[toc,page]{appendix}
+\renewcommand{\appendixpagename}{Supplements}
+\renewcommand{\appendixname}{Supplement}
 
@@
 \abstractsection{Methods}We obtained weekly ZIP-code-level counts of RSV-associated hospital admission in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)}.
-We fit smoothed curves to these admission counts using a generalized additive model with cubic cyclic penalized splines, and used these curves to estimate the fraction of all RSV cases in Connecticut occurring during the period of protection offered by RSV immunoprophylaxis (``preventable fraction'') under the AAP guidelines.
+We fit smoothed curves to these admission counts and used these curves to estimate the fraction of all RSV cases in Connecticut occurring during the period of protection offered by RSV immunoprophylaxis (``preventable fraction'') under the AAP guidelines.
 We then used the same model to estimate protection conferred by immunoprophylaxis regimens with alternate start dates (but unchanged duration and net pharmaceutical cost).
@@
 \clearpage
-
-%\begin{multicols}{1}
 
@@
 To that end, we fit smooth curves through annual RSV hospitalization data, and used resampling to obtain interval estimates.
-(TODO See supplement.)
-
-%To that end, we looked for a model that allowed easy sampling of estimated model parameters; coupling this with Monte Carlo sampling --- after transforming model parameters into response variables --- allowed us to sample arbitrary response variables.
-%
-%We assumed that RSV incidence is the result of a Poisson process whose $\log$ can be modeled as a piecewise twice-differentiable function of time.
-To meet those criteria and assumptions, we chose a log-linked generalized additive model (GAM) with penalized cubic B-splines for our analysis.
-%
-%% Looked for prior work using GAM/pspline for ID epi, didn't find anything that was relevant. (Not even by Goldstein or Lipsitch.)
-%
-%We developed a custom R package for estimation of arbitrary characteristics of infectious disease outbreaks (as long as the outbreaks are amenable to GAM); this package is available at \href{https://github.com/airbornemint/outbreak-inference}{\nolinkurl{github.com/airbornemint/outbreak-inference}}.
+(See Supplement \ref{supplement:splines}.)
 
@@
 \setcounter{figure}{3}
-\begin{figure*}[b]
+\begin{figure}[b]
 \begin{center}
@@
 \end{center}
-\end{figure*}
+\end{figure}
 \setcounter{figure}{1}
@@
 \setcounter{figure}{4}
-\begin{figure*}
+\begin{figure}
 \begin{center}
@@
 \end{center}
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{figure*}
+\begin{figure}
 \begin{center}
@@
 \setcounter{figure}{7}
-\begin{figure*}
+\begin{figure}
 \begin{center}
@@
 
-%\end{multicols}
-
 \phantomsection
 \addcontentsline{toc}{section}{Bibliography}
-\printbibliography[title={Bibliography}] % Print the bibliography, section title in curly brackets
+\printbibliography[title={Bibliography}]
+
+\cleardoublepage
+\begin{appendices}
+
+\section{Interval estimation of complex outcomes using penalized basis splines}
+\begin{refsection}
+
+\label{supplement:splines}
+
+Penalized basis splines (``P-splines'') provide a smoothing mechanism with several qualities desirable in analysis of experimental data, including computational compactness and efficiency, and well-understood statistical behavior.
+Most importantly for our RSV analysis, the parameters of a P-spline approximation have known statistical distributions, which allows interval estimation of arbitrary outcome measures.\cite{Eilers:1996kz}
+
+A simple example of this is our estimation of RSV season onset.
+We begin the process by defining season onset to occur when cumulative incidence rises above \Sexpr{seasonThreshold * 100}\% of total cases, and obtaining a P-spline approximation to our data (using the \texttt{mgcv} R package).
+This approximation is characterized by a matrix of coefficients, each of which is normally distributed with a known mean and variance.
+
+We randomly sample each coefficient from its distribution, thereby obtaining a specific spline that smoothly approximates our data.
+We calculate RSV season onset for this specific spline, and then repeat the coefficient sampling process, thereby iteratively sampling RSV season onset from its (unknown) distribution.
+
+We use the same process to estimate RSV season offset; the process can be generalized to any scalar outcome measure of an infectious disease outbreak or season.
+
+More interestingly, the same approach can be used to estimate time-series outcomes.
+We use this in our computation of preventable cases of RSV.
+We begin by defining a preventable case of RSV to be a case of RSV that occurs while prophylaxis (under a specific set of prophylaxis guidelines) offers protection; that is, a case that would have been prevented by administration of prophylaxis under those guidelines, if the prophylaxis were 100\% effective.
+As before, we obtain a P-spline approximation to our data.
+
+We then sample P-spline coefficients from their distributions to obtain a specific approximation to our data, and compute the corresponding time series of preventable RSV cases.
+Repeating the coefficient-sampling process yields time series of preventable RSV cases sampled from their (again unknown) distribution.
+
+This process can also be generalized to any time-series outcome of an infectious disease outbreak or season.
+
+Furthermore, the two approaches can be combined to calculate complex non-linear outcomes.
+We use this to estimate the fraction of preventable RSV cases in an RSV season, defined as the number of preventable cases divided by the total number of cases.
+The preventable fraction is a non-linear function of the RSV time series; as a result, interval estimation of the preventable fraction cannot be obtained by point-wise estimation of the RSV time, followed by applying a function to point-wise estimates.
+Instead, estimates of the entire time series must be sampled, and the preventable fraction then calculated for each sampled time series.
+
+Here we follow a similar process, wherein we sample coefficients from their distributions, use the resultant P-spline to calculate the all-case time series as well as the preventable-case time series, from which we then calculate the preventable fraction; the end result is that we sample the preventable fraction from its (unknown) distribution.
+
+We developed a custom R package for estimation of arbitrary characteristics of infectious disease outbreaks or seasons (as long as they are amenable to generalized additive modeling); the package is available at \href{https://github.com/airbornemint/outbreak-inference}{\nolinkurl{github.com/airbornemint/outbreak-inference}}.
+
+\printbibliography[heading=subbibliography]
+\end{refsection}
+
+\end{appendices}
 

### 2019-02-28 Paper/RSVOptimization.rnw
Dim strats that (after rounding) contribute nothing to the analysis

@@
 
+    # We are going to dim some data points, because sometimes different strategies under different rounding end up producing the same prophylaxis schedule, and there is no point in showing all of them equally on the plot.
+To do this, we consider the left-to-right order in which strategies will appear in the plot, and dim any strategy whose schedule is the same as some strategy that appears on its left
     data = unprotectedByCounty %>% 
-        filter(county == "all", sliding==FALSE)
+        filter(county == "all", sliding==FALSE) %>%
+        arrange(rounding, strat)
+
+    data$startIdx = match(data$stratStart, data$stratStart)
+    data$isRepeat = data$startIdx != seq(1, length(data$startIdx))
 
@@
         scale_y_continuous(labels=latexPercent, limits=c(0.90, 1.00), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
+        scale_alpha_manual(guide=FALSE, breaks=c(FALSE, TRUE), values=c(1, 0.5)) + 
         scale_color_manual(name="Prophylaxis regimen", labels=legendLabels(stratLabels[c(seq(1, 6), 10)]), values=c(rep(c(darkBrown, darkOrange), each=3), darkPurple)) + 
@@
         geom_errorbar(
-            aes(ymin=frac.lower, ymax=frac.upper, x=rounding, color=strat, group=strat), 
+            aes(ymin=frac.lower, ymax=frac.upper, x=rounding, color=strat, group=strat, alpha=isRepeat), 
             width=.25, 
@@
         ) + 
-        geom_point(aes(y=frac.median, x=rounding, color=strat, shape=strat), position=position_dodge(.5), size=.75) +
+        geom_point(aes(y=frac.median, x=rounding, color=strat, shape=strat, alpha=isRepeat), position=position_dodge(.5), size=.75) +
         labs(x="Calendrical rounding", y="Preventable fraction") +

### 2019-02-28 Analysis/RSV.R

@@ -117,7 +117,7 @@ modelTime = seq(min(rsvTime) - 1 + eps, max(rsvTime), eps)
 
 # *** Prophyaxis assessment helpers
 
-epochRound = function(time, epoch) {
+epochRound = Vectorize(function(time, epoch) {
   if (epoch > 0) {
     # Rounding for prophylaxis strategies has phase as follows
     # For rounding=1, .5 .. 1.5 round to 1
@@ -126,56 +126,44 @@ epochRound = function(time, epoch) {
     time = epoch * round(time / epoch)
   }
   time
-}
+})
 
-evalStrategy = function(start, end, time, rounding) {
-  as.numeric((time >= epochRound(start, rounding)) & (time < epochRound(end, rounding)))
-}
-
-evalOnsetStrategy = function(start, time, rounding=0) {
-  evalStrategy(start, start + ppxDuration, time, rounding)
-}
-
-evalOffsetStrategy = function(end, time, rounding=0) {
-  evalStrategy(end - ppxDuration, end, time, rounding)
+evalStrategy = function(start, end, time) {
+  as.numeric((time >= start) & (time < end))
 }
 
 # *** Prophylaxis regimen definitions
 
-# Return a list of prophylaxis strategies for a county. If c is NULL, then it returns a list of prophylaxis strategy names
-ppxFixedStrategies = function(c=NULL, rounding=0) {
+ppxFixedStrategyStart = function(c, rounding) {
   stateOnset = stateThresholds$onset.median
   stateOffset = stateThresholds$offset.median
-
+  
   if (!is.null(c)) {
     countyOnset = (thresholdsByCounty %>% filter(county==c))$onset.median
     countyOffset = (thresholdsByCounty %>% filter(county==c))$offset.median
+  } else {
+    countyOnset = countyOffset = NA
   }
-
+  
   list(
-    stateOnset=function(time) {
-      evalOnsetStrategy(stateOnset, time, rounding)
-    },
-    stateMiddle=function(time) {
-      evalOnsetStrategy((stateOnset + stateOffset - ppxDuration) / 2, time, rounding)
-    },
-    stateOffset=function(time) {
-      evalOffsetStrategy(stateOffset, time, rounding)
-    },
-    countyOnset=function(time) {
-      evalOnsetStrategy(countyOnset, time, rounding)
-    },
-    countyMiddle=function(time) {
[…]

### 2019-02-28 Paper/RSVOptimization.rnw
Typography

@@
 
-Penalized basis splines (``P-splines'') provide a smoothing mechanism with several qualities desirable in analysis of experimental data, including computational compactness and efficiency, and well-understood statistical behavior.
-Most importantly for our RSV analysis, the parameters of a P-spline approximation have known statistical distributions, which allows interval estimation of arbitrary outcome measures.\cite{Eilers:1996kz}
+Penalized basis splines (``$P$-splines'') provide a smoothing mechanism with several qualities desirable in analysis of experimental data, including computational compactness and efficiency, and well-understood statistical behavior.
+Most importantly for our RSV analysis, the parameters of a $P$-spline approximation have known statistical distributions, which allows interval estimation of arbitrary outcome measures.\cite{Eilers:1996kz}
 
 A simple example of this is our estimation of RSV season onset.
-We begin the process by defining season onset to occur when cumulative incidence rises above \Sexpr{seasonThreshold * 100}\% of total cases, and obtaining a P-spline approximation to our data (using the \texttt{mgcv} R package).
+We begin the process by defining season onset to occur when cumulative incidence rises above \Sexpr{seasonThreshold * 100}\% of total cases, and obtaining a $P$-spline approximation to our data (using the \texttt{mgcv} R package).
 This approximation is characterized by a matrix of coefficients, each of which is normally distributed with a known mean and variance.
@@
 We begin by defining a preventable case of RSV to be a case of RSV that occurs while prophylaxis (under a specific set of prophylaxis guidelines) offers protection; that is, a case that would have been prevented by administration of prophylaxis under those guidelines, if the prophylaxis were 100\% effective.
-As before, we obtain a P-spline approximation to our data.
+As before, we obtain a $P$-spline approximation to our data.
 
-We then sample P-spline coefficients from their distributions to obtain a specific approximation to our data, and compute the corresponding time series of preventable RSV cases.
+We then sample $P$-spline coefficients from their distributions to obtain a specific approximation to our data, and compute the corresponding time series of preventable RSV cases.
 Repeating the coefficient-sampling process yields time series of preventable RSV cases sampled from their (again unknown) distribution.
@@
 
-Here we follow a similar process, wherein we sample coefficients from their distributions, use the resultant P-spline to calculate the all-case time series as well as the preventable-case time series, from which we then calculate the preventable fraction; the end result is that we sample the preventable fraction from its (unknown) distribution.
+Here we follow a similar process, wherein we sample coefficients from their distributions, use the resultant $P$-spline to calculate the all-case time series as well as the preventable-case time series, from which we then calculate the preventable fraction; the end result is that we sample the preventable fraction from its (unknown) distribution.
 

### 2019-02-28 Analysis/RSV.R
Ongoing work on dimming non-illuminating strategy/rounding combos

@@ -14,7 +14,7 @@ library(maps)
 data(zipcode)
 set.seed(0)
 
-simulations = 20
+simulations = 2000
 
 # *** Data munging helpers
 
@@ -268,6 +268,7 @@ obsByCounty = dataset %>%
 predByCounty = data.frame()
 thresholdsByCounty = data.frame()
 fixedStratUnprotectedSimByCountyRounding = data.frame()
+fixedStratDescByCountyRounding = data.frame()
 fixedStratUnprotectedByCounty = data.frame()
 
 for (c in levels(obsByCounty$county)) {
@@ -322,8 +323,37 @@ for (c in levels(obsByCounty$county)) {
         countyUnprotectedSim %>%
         mutate(county=factor(c, levels=levels(obsByCounty$county)), rounding=rounding)
       )
+    
+    fixedStratDescByCountyRounding = fixedStratDescByCountyRounding %>%
+      rbind(
+        data.frame(ppxFixedStrategyStart(c, rounding)) %>%
+        mutate(county=factor(c, levels=levels(obsByCounty$county)), rounding=rounding)
+      )
   }
 }
+
+fixedStratDescStatewide = fixedStratDescByCountyRounding %>%
+  filter(county %in% highIncidenceCounties | county == "lowIncidence") %>%
+  melt(c("county", "rounding")) %>%
+  rename(strat=variable, startWeek=value) %>%
+  group_by(rounding, strat) %>%
+  do((function(df) {
+    df = df %>% arrange(county)
+    name = paste0(sprintf("%s=%s", df$county, df$startWeek), collapse=";")
+    df = df %>% select(-county, -startWeek)
+    df = df[1,]
+    df$variable = "desc"
+    df$value = name
+    df
+  })(.)) %>%
+  ungroup() %>%
+  cast(rounding + strat ~ variable) %>%
+  mutate(
+    sliding=FALSE, 
+    county="all",
+    desc=as.character(desc),
+    county=factor(county)
+  )
 
 fixedStratUnprotectedStatewide = fixedStratUnprotectedSimByCountyRounding %>%
   filter(county %in% highIncidenceCounties | county == "lowIncidence") %>%
@@ -504,10 +534,6 @@ slidingStratUnprotectedByCounty = slidingStratUnprotectedSimByCountyYear %>%
 
 # Merge sliding and fixed strategies into one data frame
 
[…]

### 2019-02-28 Paper/RSVOptimization.rnw
Ongoing work on dimming non-illuminating strategy/rounding combos
Continued work on deemphasizing some strategies in plots

@@
 \documentclass[10pt,letter]{article}
+\usepackage{amssymb}
+\usepackage{wasysym}
+
 \usepackage{float}
@@
 
-    # We are going to dim some data points, because sometimes different strategies under different rounding end up producing the same prophylaxis schedule, and there is no point in showing all of them equally on the plot.
-To do this, we consider the left-to-right order in which strategies will appear in the plot, and dim any strategy whose schedule is the same as some strategy that appears on its left
+    # We are going to de-emphasize some data points, because sometimes different strategies under different rounding end up producing the same prophylaxis schedule, and there is no point in showing all of them equally on the plot.
+To do this, we consider the left-to-right order in which strategies will appear in the plot, and then de-emphasize any strategy whose schedule is the same as some strategy that appears on its left
     data = unprotectedByCounty %>% 
         filter(county == "all", sliding==FALSE) %>%
-        arrange(rounding, strat)
+        arrange(rounding, strat) %>%
+        mutate(strat=factor(strat, levels=c(levels(strat)[1], "_1", "_2", levels(strat)[2:7])))
 
-    data$startIdx = match(data$stratStart, data$stratStart)
+    data$startIdx = match(data$desc, data$desc)
     data$isRepeat = data$startIdx != seq(1, length(data$startIdx))
+    data$isRepeat = data$isRepeat & !data$strat == "aap" 
+    data$strat.isRepeat = sprintf("%s.%s", data$strat, data$isRepeat)
+    idx = order(rep(seq(1, length(levels(data$strat))), 2))
+    strat.isRepeat.levels = (c(
+      sprintf("%s.%s", levels(data$strat), FALSE), 
+      sprintf("%s.%s", levels(data$strat), TRUE)
+    ))[idx]
+    data$strat.isRepeat = factor(data$strat.isRepeat, strat.isRepeat.levels)
 
@@
         scale_alpha_manual(guide=FALSE, breaks=c(FALSE, TRUE), values=c(1, 0.5)) + 
-        scale_color_manual(name="Prophylaxis regimen", labels=legendLabels(stratLabels[c(seq(1, 6), 10)]), values=c(rep(c(darkBrown, darkOrange), each=3), darkPurple)) + 
-        scale_shape_manual(name="Prophylaxis regimen", labels=legendLabels(stratLabels[c(seq(1, 6), 10)]), values=c(16, 15, 17, 16, 15, 17, 16)) + 
+        scale_color_manual(
+          name="Prophylaxis regimen", 
+          breaks=factor(sprintf("%s.%s", levels(data$strat), FALSE), levels=strat.isRepeat.levels),
+          labels=legendLabels(c(as.vector(stratLabels[10]), "_", "__", as.vector(stratLabels[1:6]))),
+          values=c(
+            darkPurple, darkPurple, 
+            NA, NA, NA, NA, 
+            rep(c(darkBrown, darkOrange), each=6)
+          ), 
+          drop=FALSE
+        ) + 
+        scale_shape_manual(
+          name="Prophylaxis regimen", 
+          breaks=factor(sprintf("%s.%s", levels(data$strat), FALSE), levels=strat.isRepeat.levels),
+          labels=legendLabels(c(as.vector(stratLabels[10]), "_", "__", as.vector(stratLabels[1:6]))),
+          values=c(
+            16, 16, 
+            16, 16, 16, 16, 
+            16, 21, 15, 22, 17, 24, 
+            16, 21, 15, 22, 17, 24
+          ), 
+          drop=FALSE
+        ) + 
         scale_x_discrete(labels=roundingLabels) + 
         geom_errorbar(
-            aes(ymin=frac.lower, ymax=frac.upper, x=rounding, color=strat, group=strat, alpha=isRepeat), 
+            aes(ymin=frac.lower, ymax=frac.upper, x=rounding, color=strat.isRepeat, group=strat.isRepeat), 
             width=.25, 
@@
         ) + 
-        geom_point(aes(y=frac.median, x=rounding, color=strat, shape=strat, alpha=isRepeat), position=position_dodge(.5), size=.75) +
+        geom_point(aes(y=frac.median, x=rounding, color=strat.isRepeat, shape=strat.isRepeat), position=position_dodge(.5), size=0.75, fill="white") +
         labs(x="Calendrical rounding", y="Preventable fraction") +
@@
 \caption[The effect of calendrical rounding of start and end of spatially adjusted RSV prophylaxis regimens on their performance]{The effect of calendrical rounding of start and end of spatially adjusted RSV prophylaxis regimens on their performance, showing that longer rounding intervals diminish the benefits of alternative regimens over the AAP-recommended regimen.
-Preventable fraction: the fraction of all RSV hospitalizations occurring while the prophylaxis regimen offers protection}
+Preventable fraction: the fraction of all RSV hospitalizations occurring while the prophylaxis regimen offers protection.
+Hollow plot markers ($\Circle$, $\square$, and $\triangle$) denote a prophylaxis strategy which, as a result of rounding, is identical to another.}
 \label{fig:coverageByRoundingRegimen}

### 2019-02-28 Analysis/RSV.R

@@ -560,7 +560,7 @@ unprotectedByCounty = fixedStratUnprotectedByCounty %>%
     strat = factor(strat, c(
       names(ppxSlidingStrategies(NULL, NULL)),
       names(ppxFixedStrategies(NULL))
-    )[c(4, 5, 6, 7, 8, 9, 1, 2, 3, 10)]),
+    )[c(10, 4, 5, 6, 7, 8, 9, 1, 2, 3)]),
     rounding = factor(rounding),
     county = factor(county)
   ) %>%

### 2019-02-28 Paper/RSVOptimization.R

@@ -167,7 +167,7 @@ epiWeekBreaks = sort(unique(c(monthBoundaries$min, monthBoundaries$max)))
 
 legendLabels = function(labels, rep=2) {
   as.vector(sapply(labels, function(label) {
-    sprintf("%s%s", label, strrep("\\qquad", rep))
+    ifelse(substr(label, 1, 1) == "_", paste0(rep(" ", nchar(label)), collapse=""), sprintf("%s%s", label, strrep("\\qquad", rep)))
   }))
 }
 
@@ -179,11 +179,11 @@ lightGreen = "#b2df8a"
 darkGreen = "#33a02c"
 lightRed = "#fb9a99"
 darkRed = "#e31a1c"
-lightOrange = "#fdbf6f"
+lightOrange = "#FFBF80"
 darkOrange = "#ff7f00"
 lightPurple = "#cab2d6"
 darkPurple = "#6a3d9a"
-lightBrown = "#ffff99"
+lightBrown = "#D19D82"
 darkBrown = "#b15928"
 
 # Counties which we plot (so, not individual low-incidence counties)

### 2019-02-28 Paper/RSVOptimization.R
Better light brown

@@ -183,7 +183,7 @@ lightOrange = "#FFBF80"
 darkOrange = "#ff7f00"
 lightPurple = "#cab2d6"
 darkPurple = "#6a3d9a"
-lightBrown = "#D19D82"
+lightBrown = "#E3C0AC"
 darkBrown = "#b15928"
 
 # Counties which we plot (so, not individual low-incidence counties)

### 2019-02-28 Paper/RSVOptimization.R
Better label spacing

@@ -165,9 +165,19 @@ monthBoundaries = breaks.df %>%
 
 epiWeekBreaks = sort(unique(c(monthBoundaries$min, monthBoundaries$max)))
 
-legendLabels = function(labels, rep=2) {
+legendLabels = function(labels, rep=2, leading=FALSE, trailing=TRUE) {
   as.vector(sapply(labels, function(label) {
-    ifelse(substr(label, 1, 1) == "_", paste0(rep(" ", nchar(label)), collapse=""), sprintf("%s%s", label, strrep("\\qquad", rep)))
+    if(substr(label, 1, 1) == "_") {
+      paste0(rep(" ", nchar(label)), collapse="")
+    } else {
+      if (leading) {
+        label = sprintf("%s%s", strrep("\\qquad", rep), label)
+      }
+      if (trailing) {
+        label = sprintf("%s%s", label, strrep("\\qquad", rep))
+      }
+      label
+    }
   }))
 }
 

### 2019-02-28 Paper/RSVOptimization.rnw
Fixing package order conflict
Better label spacing
Clarify

@@
 \documentclass[10pt,letter]{article}
-\usepackage{amssymb}
-\usepackage{wasysym}
-
 \usepackage{float}
@@
 \input{structure.tex}
+\usepackage{amssymb}
+\usepackage{wasysym}
 
@@
 
-    spanLabels = legendLabels(c("AAP-recommended prophylaxis", "RSV season"))
+    spanLabels = legendLabels(c("AAP-recommended prophylaxis", "RSV season"), leading=TRUE)
 
@@
 Preventable fraction: the fraction of all RSV hospitalizations occurring while the prophylaxis regimen offers protection.
-Hollow plot markers ($\Circle$, $\square$, and $\triangle$) denote a prophylaxis strategy which, as a result of rounding, is identical to another.}
+Hollow plot markers ($\Circle$, $\square$, and $\triangle$) denote a prophylaxis strategy which, as a result of rounding, is identical to another, and therefore does not provide additional insights.}
 \label{fig:coverageByRoundingRegimen}

### 2019-02-28 Analysis/RSV.R
Don’t lose county-level analysis results

@@ -551,7 +551,7 @@ unprotectedByCounty = fixedStratUnprotectedByCounty %>%
   select(-variable_1, -variable_2, -variable_3) %>%
   mutate(strat=as.factor(strat)) %>%
   cast(county + strat + rounding + sliding ~ variable) %>%
-  inner_join(fixedStratDescStatewide) %>%
+  left_join(fixedStratDescStatewide) %>%
   mutate(
     frac.temp = frac.lower,
     frac.lower = 1 - frac.upper,

### 2019-02-28 Paper/RSVOptimization.R
Avoid LaTeX syntax problems with bare \qquad

@@ -171,10 +171,10 @@ legendLabels = function(labels, rep=2, leading=FALSE, trailing=TRUE) {
       paste0(rep(" ", nchar(label)), collapse="")
     } else {
       if (leading) {
-        label = sprintf("%s%s", strrep("\\qquad", rep), label)
+        label = sprintf("%s%s", strrep("\\qquad{}", rep), label)
       }
       if (trailing) {
-        label = sprintf("%s%s", label, strrep("\\qquad", rep))
+        label = sprintf("%s%s", label, strrep("\\qquad{}", rep))
       }
       label
     }

### 2019-02-28 Paper/RSVOptimization.rnw
No need to force figure numbering in one-column
Renamed for clarity
Clarifications

@@
 knitr::read_chunk("../Analysis/RSV.R")
-knitr::read_chunk("../Paper/RSVOptimization.R")
+knitr::read_chunk("../Paper/Paper.R")
 @
@@
         coord_map() + 
-        labs(fill="Average RSV cases per year") +
+        labs(fill="Average RSV-associated hospitalizations per year") +
         theme(
@@
 
-We chose to aggregate low-RSV counties into a single region because our analysis in those counties individually would have yielded results with low statistical power.
+We chose to aggregate low-RSV counties into a single region because our analysis in those counties individually yielded results with low statistical power.
 
@@
 
-\setcounter{figure}{3}
 \begin{figure}[b]
@@
 \end{figure}
-\setcounter{figure}{1}
 
@@
 
-\setcounter{figure}{4}
 \begin{figure}
@@
 
-\setcounter{figure}{6}
 \begin{figure}
@@
 
-\setcounter{figure}{7}
 \begin{figure}

### 2019-03-01 Analysis/RSV.R
Demo of onset estimation with Tolland for supplement

@@ -5,6 +5,7 @@ library(mgcv)
 library(outbreakinference)
 library(zipcode)
 library(ggplot2)
+library(ggstance)
 library(easyGgplot2)
 library(data.table)
 library(splitstackshape)

### 2019-03-01 Paper/Supplement.R

@@ -1,0 +1,119 @@
+tollandObs = obsByCounty %>% filter(county=="Tolland")
+tollandModel = gam(rsv ~ s(time, k=20, bs="cp", m=3), family=poisson, data=tollandObs)
+
+ggplot(tollandObs) +
+    theme_light(base_size=plotTextBaseSize) +
+    geom_point(aes(x=time, y=rsv.cum)) +
+    scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, limits=range(c(monthBoundaries$min, monthBoundaries$max)), expand=c(0, 0)) + 
+    theme(
+        panel.grid.major.x=element_blank(),
+        legend.title=element_blank(),
+        axis.title.y=element_blank(),
+        axis.ticks.x=element_blank(),
+        axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
+        legend.position="bottom"
+    )
+
+tollandNsim = 5
+
+randomMVN = function(mu, sig, nsim) {
+  L = mroot(sig)
+  m = ncol(L)
+  t(mu + L %*% matrix(rnorm(m * nsim), m, nsim))
+}
+
+tollandParams = randomMVN(coef(tollandModel), tollandModel$Vp, tollandNsim)
+
+tollandPred = tollandParams %>%
+  apply(1, function(params) { outbreak.calc.cum(1)(tollandModel, params, modelTime) } ) %>%
+  data.frame() %>%
+  cbind(time=modelTime) %>%
+  melt(c("time")) %>%
+  mutate(variable=as.numeric(substr(variable, 2, 2))) %>%
+  rename(sim=variable, rsv.cum.frac=value)
+
+ggplot(tollandPred) +
+  theme_light(base_size=plotTextBaseSize) +
+  geom_point(data=tollandObs, aes(x=time, y=rsv.cum.frac)) +
+  geom_line(aes(x=time, y=rsv.cum.frac, group=sim)) +
+  geom_segment(aes(x=-Inf, y=seasonThreshold, xend=+Inf, yend=seasonThreshold), linetype="11", data=data.frame(), size=.375) + 
+  scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, limits=range(c(monthBoundaries$min, monthBoundaries$max)), expand=c(0, 0)) + 
+  theme(
+    panel.grid.major.x=element_blank(),
+    legend.title=element_blank(),
[…]

### 2019-03-01 Paper/RSVOptimization.rnw
Migrating supplement plots into paper text

@@
 knitr::read_chunk("../Paper/Paper.R")
+knitr::read_chunk("../Paper/Supplement.R")
 @
@@
 
+<<supplement, warning=FALSE>>=
+@
+
 Penalized basis splines (``$P$-splines'') provide a smoothing mechanism with several qualities desirable in analysis of experimental data, including computational compactness and efficiency, and well-understood statistical behavior.
@@
 
-A simple example of this is our estimation of RSV season onset.
+A simple application of this is our estimation of RSV season onset.
+Consider, for example, RSV-associated hospitalizations in Tolland County, Connecticut in Figure \ref{fig:tollandCases}.
+(This is a low-incidence county, which makes it a poor candidate for our main analysis, but its large confidence intervals make it easier to visualize our methods.)
+
+<<tollandCases, results='hide', warning=FALSE>>=
+    tikz(sprintf("%s/tollandCases.tex", figuresDir), width=pagePlotWidth * 0.4, height=pagePlotHeight, pointsize=10)
+
+    ggplot(tollandObs) +
+        theme_light(base_size=plotTextBaseSize) +
+        geom_point(aes(x=time, y=rsv.cum.frac)) +
+        scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, limits=range(c(monthBoundaries$min, monthBoundaries$max)), expand=c(0, 0)) + 
+        theme(
+            panel.grid.major.x=element_blank(),
+            legend.title=element_blank(),
+            axis.title.y=element_blank(),
+            axis.ticks.x=element_blank(),
+            axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
+            legend.position="bottom"
+        )
+
+    dev.off()
+@
+
+\begin{figure}
+\begin{center}
+\input{\figuresDir/tollandCases.tex}
+\caption{Cumulative relative incidence of RSV-associated hospitalizations in Tolland county, Connecticut, aggregated across years \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}
+\label{fig:tollandCases}
+\end{center}
+\end{figure}
+
+<<tollandPredMini, results='hide', warning=FALSE>>=
+    tikz(sprintf("%s/tollandPredMini.tex", figuresDir), width=pagePlotWidth * 0.4, height=pagePlotHeight, pointsize=10)
+
+    ggplot(tollandPredMini) +
+      theme_light(base_size=plotTextBaseSize) +
+      geom_point(data=tollandObs, aes(x=time, y=rsv.cum.frac)) +
+      geom_line(aes(x=time, y=rsv.cum.frac, group=sim)) +
+      geom_segment(aes(x=-Inf, y=seasonThreshold, xend=+Inf, yend=seasonThreshold), linetype="11", data=data.frame(), size=.375) + 
+      scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, limits=range(c(monthBoundaries$min, monthBoundaries$max)), expand=c(0, 0)) + 
+      theme(
+        panel.grid.major.x=element_blank(),
+        legend.title=element_blank(),
+        axis.title.y=element_blank(),
+        axis.ticks.x=element_blank(),
+        axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
+        legend.position="bottom"
+      )
+
+    dev.off()
+@
+
+\begin{figure}
+\begin{center}
+\input{\figuresDir/tollandPredMini}
+\caption{Cumulative relative incidence of RSV-associated hospitalizations in Tolland county, Connecticut, with five randomly sampled approximating $P$-splines.}
+\label{fig:tollandPredMini}
+\end{center}
+\end{figure}
+
+<<tollandOnsetMini, results='hide', warning=FALSE>>=
+    tikz(sprintf("%s/tollandOnsetMini.tex", figuresDir), width=pagePlotWidth * 0.4, height=pagePlotHeight, pointsize=10)
+
+    ggplot(tollandPredMini) +
+      theme_light(base_size=plotTextBaseSize) +
+      geom_line(aes(x=time, y=rsv.cum.frac, group=sim), color="gray") +
+      geom_segment(aes(x=-Inf, y=seasonThreshold, xend=+Inf, yend=seasonThreshold), linetype="11", data=data.frame(), size=.375) + 
+      scale_y_continuous(limits=c(0, 2*seasonThreshold)) + 
+      scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, limits=c(zoomedStartWeek, zoomedEndWeek), expand=c(0, 0)) + 
+      geom_point(data=tollandOnsetMini, aes(x=onset, y=seasonThreshold)) + 
+      geom_segment(data=tollandOnsetMini, aes(x=onset, xend=onset, y=seasonThreshold, yend=0), linetype="11") + 
+      theme(
+        panel.grid.major.x=element_blank(),
+        legend.title=element_blank(),
+        axis.title.y=element_blank(),
+        axis.ticks.x=element_blank(),
+        axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
+        legend.position="bottom"
+      )
+
+    dev.off()
+@
+
+\begin{figure}
+\begin{center}
+\input{\figuresDir/tollandOnsetMini}
+\caption{Five randomly sampled approximations of cumulative relative incidence of RSV-associated hospitalizations in Tolland county, Connecticut, with their corresponding season onsets.}
+\label{fig:tollandOnsetMini}
+\end{center}
+\end{figure}
+
 We begin the process by defining season onset to occur when cumulative incidence rises above \Sexpr{seasonThreshold * 100}\% of total cases, and obtaining a $P$-spline approximation to our data (using the \texttt{mgcv} R package).
@@
 We randomly sample each coefficient from its distribution, thereby obtaining a specific spline that smoothly approximates our data.
-We calculate RSV season onset for this specific spline, and then repeat the coefficient sampling process, thereby iteratively sampling RSV season onset from its (unknown) distribution.
+Five such randomly sampled splines are shown in Figure \ref{fig:tollandPredMini}.
+We then calculate RSV season onset for each sampled spline (Figure \ref{fig:tollandOnsetMini}).
+
+Repeating this process many times (\Sexpr{simulations}, in our main analysis) then allows us to estimate the distribution of RSV season onset and therefore make interval estimates.
+In the case of Tolland county, the result of similar season onset sampling is shown in Figure \ref{fig:tollandPredFull}.
+
+<<tollandOnsetFull, results='hide', warning=FALSE>>=
+    tikz(sprintf("%s/tollandOnsetFull", figuresDir), width=pagePlotWidth * 0.4, height=pagePlotHeight, pointsize=10)
+
+    ggplot(tollandPredFull) +
+      theme_light(base_size=plotTextBaseSize) +
+      geom_ribbon(aes(x=time, ymin=min, ymax=max), fill="gray", na.rm=FALSE) +
+      geom_segment(aes(x=-Inf, y=seasonThreshold, xend=+Inf, yend=seasonThreshold), linetype="11", data=data.frame(), size=.375) + 
+      geom_violinh(
+        data=tollandOnsetFull,
+        aes(x=onset, y=seasonThreshold),
+        width=.01,
+        fill="gray", color="black",
+        trim=FALSE, draw_quantiles=c(0.025, 0.5, 0.975)
+      ) +
+      scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, expand=c(0, 0)) +
+      scale_y_continuous() +
+      coord_cartesian(xlim=c(zoomedStartWeekFull, zoomedEndWeekFull), ylim=c(0, 4*seasonThreshold)) +
+      theme(
+        panel.grid.major.x=element_blank(),
+        legend.title=element_blank(),
+        axis.title.y=element_blank(),
+        axis.ticks.x=element_blank(),
+        axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
+        legend.position="bottom"
+      )
+    dev.off()
+@
+
+\begin{figure}
+\begin{center}
+\input{\figuresDir/tollandPredFull}
+\caption{Distribution of approximating $P$-splines and the calculated season onset with $N=\Sexpr{simulations}$ samples, for cumulative relative incidence of RSV-associated hospitalizations in Tolland county, Connecticut.}
+\label{fig:tollandPredFull}
+\end{center}
+\end{figure}
 

### 2019-03-01 Analysis/RSV.R

@@ -5,7 +5,6 @@ library(mgcv)
 library(outbreakinference)
 library(zipcode)
 library(ggplot2)
-library(ggstance)
 library(easyGgplot2)
 library(data.table)
 library(splitstackshape)

### 2019-03-01 Paper/Supplement.R

@@ -1,20 +1,10 @@
+# ---- supplement ----
+library(ggstance)
+
 tollandObs = obsByCounty %>% filter(county=="Tolland")
 tollandModel = gam(rsv ~ s(time, k=20, bs="cp", m=3), family=poisson, data=tollandObs)
 
-ggplot(tollandObs) +
-    theme_light(base_size=plotTextBaseSize) +
-    geom_point(aes(x=time, y=rsv.cum)) +
-    scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, limits=range(c(monthBoundaries$min, monthBoundaries$max)), expand=c(0, 0)) + 
-    theme(
-        panel.grid.major.x=element_blank(),
-        legend.title=element_blank(),
-        axis.title.y=element_blank(),
-        axis.ticks.x=element_blank(),
-        axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
-        legend.position="bottom"
-    )
-
-tollandNsim = 5
+tollandNsimMini = 5
 
 randomMVN = function(mu, sig, nsim) {
   L = mroot(sig)
@@ -22,9 +12,9 @@ randomMVN = function(mu, sig, nsim) {
   t(mu + L %*% matrix(rnorm(m * nsim), m, nsim))
 }
 
-tollandParams = randomMVN(coef(tollandModel), tollandModel$Vp, tollandNsim)
+tollandParamsMini = randomMVN(coef(tollandModel), tollandModel$Vp, tollandNsimMini)
 
-tollandPred = tollandParams %>%
+tollandPredMini = tollandParamsMini %>%
   apply(1, function(params) { outbreak.calc.cum(1)(tollandModel, params, modelTime) } ) %>%
   data.frame() %>%
   cbind(time=modelTime) %>%
@@ -32,50 +22,18 @@ tollandPred = tollandParams %>%
   mutate(variable=as.numeric(substr(variable, 2, 2))) %>%
   rename(sim=variable, rsv.cum.frac=value)
 
-ggplot(tollandPred) +
-  theme_light(base_size=plotTextBaseSize) +
-  geom_point(data=tollandObs, aes(x=time, y=rsv.cum.frac)) +
-  geom_line(aes(x=time, y=rsv.cum.frac, group=sim)) +
[…]

### 2019-03-01 Paper/RSVOptimization.rnw
Supplement improvements

--- 2019-02-28 Paper/RSVOptimization.rnw
@@
 
-<<util, warning=FALSE>>=
+<<paper, warning=FALSE>>=
 @
@@
 
-% TODO figure showing prophylaxis regimens on a calendar?
-
 Our analysis confirms the existence of regional variation of RSV season timing in Connecticut (defined by RSV season onset and offset) observable at the county level.
@@
 
+<<supplement_libraries, cache=FALSE>>=
+@
+
+<<supplement, cache=TRUE>>=
+@
+
 Penalized basis splines (``$P$-splines'') provide a smoothing mechanism with several qualities desirable in analysis of experimental data, including computational compactness and efficiency, and well-understood statistical behavior.
@@
 
-A simple example of this is our estimation of RSV season onset.
+A simple application of this is our estimation of RSV season onset.
+Consider, for example, RSV-associated hospitalizations in Tolland County, Connecticut in Figure \ref{fig:tollandCases}.
+(This is a low-incidence county, which makes it a poor candidate for our main analysis, but its large confidence intervals make it easier to visualize our methods.)
+
+<<tollandCases, results='hide', warning=FALSE>>=
+    tikz(sprintf("%s/tollandCases.tex", figuresDir), width=pagePlotWidth * 0.4, height=pagePlotHeight, pointsize=10)
+
+    ggplot(tollandObs) +
+        theme_light(base_size=plotTextBaseSize) +
+        geom_point(aes(x=time, y=rsv.cum.frac), size=.5) +
+        scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, limits=range(c(monthBoundaries$min, monthBoundaries$max)), expand=c(0, 0)) + 
+        theme(
+            panel.grid.major.x=element_blank(),
+            legend.title=element_blank(),
+            axis.title.y=element_blank(),
+            axis.ticks.x=element_blank(),
+            axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
+            legend.position="bottom"
+        )
+
+    dev.off()
+@
+
+\begin{figure}
+\begin{center}
+\input{\figuresDir/tollandCases.tex}
+\caption{Cumulative relative incidence of RSV-associated hospitalizations in Tolland county, Connecticut, aggregated across years \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}}
+\label{fig:tollandCases}
+\end{center}
+\end{figure}
+
+<<tollandPredMini, results='hide', warning=FALSE>>=
+    tikz(sprintf("%s/tollandPredMini.tex", figuresDir), width=pagePlotWidth * 0.4, height=pagePlotHeight, pointsize=10)
+
+    ggplot(tollandPredMini) +
+      theme_light(base_size=plotTextBaseSize) +
+      geom_line(aes(x=time, y=rsv.cum.frac, group=sim), color="grey") +
+      geom_segment(aes(x=-Inf, y=seasonThreshold, xend=+Inf, yend=seasonThreshold), linetype="11", data=data.frame(), size=.375) + 
+      geom_point(data=tollandObs, aes(x=time, y=rsv.cum.frac), size=0.5) +
+      scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, limits=range(c(monthBoundaries$min, monthBoundaries$max)), expand=c(0, 0)) + 
+      theme(
+        panel.grid.major.x=element_blank(),
+        legend.title=element_blank(),
+        axis.title.y=element_blank(),
+        axis.ticks.x=element_blank(),
+        axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
+        legend.position="bottom"
+      )
+
+    dev.off()
+@
+
+<<tollandOnsetMini, results='hide', warning=FALSE>>=
+    tikz(sprintf("%s/tollandOnsetMini.tex", figuresDir), width=pagePlotWidth * 0.4, height=pagePlotHeight, pointsize=10)
+
+    ggplot(tollandPredMini) +
+      theme_light(base_size=plotTextBaseSize) +
+      geom_line(aes(x=time, y=rsv.cum.frac, group=sim), color="grey") +
+      geom_segment(aes(x=-Inf, y=seasonThreshold, xend=+Inf, yend=seasonThreshold), linetype="11", data=data.frame(), size=.375) + 
+      geom_point(data=tollandObs, aes(x=time, y=rsv.cum.frac), size=0.5) +
+      geom_point(data=tollandOnsetMini, aes(x=onset, y=seasonThreshold), size=0.75, shape=17) + 
+      geom_segment(data=tollandOnsetMini, aes(x=onset, xend=onset, y=seasonThreshold, yend=0), linetype="11") + 
+      scale_y_continuous(limits=c(0, 2*seasonThreshold)) + 
+      scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, limits=c(zoomedStartWeek, zoomedEndWeek), expand=c(0, 0)) + 
+      theme(
+        panel.grid.major.x=element_blank(),
+        legend.title=element_blank(),
+        axis.title.y=element_blank(),
+        axis.ticks.x=element_blank(),
+        axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
+        legend.position="bottom"
+      )
+
+    dev.off()
+@
+
+\begin{figure}
+\begin{center}
+\begin{subfigure}{.4\textwidth}
+    \begin{center}
+    \input{\figuresDir/tollandPredMini}
+    \caption{Five randomly sampled $P$-splines approximating the RSV time series.}
+    \label{fig:tollandPredMini}
+    \end{center}
+\end{subfigure}
+\begin{subfigure}{.4\textwidth}
+    \begin{center}
+    \input{\figuresDir/tollandOnsetMini}
+    \caption{Season onsets derived from five randomly sampled approximating splines.}
+    \label{fig:tollandOnsetMini}
+    \end{center}
+\end{subfigure}
+\end{center}
+\caption{Cumulative relative incidence of RSV-associated hospitalizations in Tolland county, Connecticut, with five randomly sampled approximating $P$-splines.}
+\end{figure}
+
 We begin the process by defining season onset to occur when cumulative incidence rises above \Sexpr{seasonThreshold * 100}\% of total cases, and obtaining a $P$-spline approximation to our data (using the \texttt{mgcv} R package).
@@
 We randomly sample each coefficient from its distribution, thereby obtaining a specific spline that smoothly approximates our data.
-We calculate RSV season onset for this specific spline, and then repeat the coefficient sampling process, thereby iteratively sampling RSV season onset from its (unknown) distribution.
+Five such randomly sampled splines are shown in Figure \ref{fig:tollandPredMini}.
+We then calculate RSV season onset for each sampled spline (Figure \ref{fig:tollandOnsetMini}).
+
+Repeating this process many times (\Sexpr{simulations}, in our main analysis) then allows us to estimate the distribution of RSV season onset and therefore make interval estimates.
+In the case of Tolland county, the result of such season onset sampling is shown in Figure \ref{fig:tollandOnsetFull}.
+
+<<tollandOnsetFull, results='hide', warning=FALSE>>=
+    tikz(sprintf("%s/tollandOnsetFull", figuresDir), width=pagePlotWidth * 0.4, height=pagePlotHeight, pointsize=10)
+
+    ggplot(tollandPredFull) +
+      theme_light(base_size=plotTextBaseSize) +
+      geom_ribbon(aes(x=time, ymin=min, ymax=max), fill="gray", na.rm=FALSE) +
+      geom_segment(aes(x=-Inf, y=seasonThreshold, xend=+Inf, yend=seasonThreshold), linetype="11", data=data.frame(), size=.375) + 
+      geom_point(data=tollandObs, aes(x=time, y=rsv.cum.frac), size=0.5) +
+      geom_violinh(
+        data=tollandOnsetFull,
+        aes(x=onset, y=seasonThreshold),
+        width=.01,
+        fill="gray50", color="black",
+        trim=FALSE, draw_quantiles=c(0.025, 0.5, 0.975)
+      ) +
+      scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, expand=c(0, 0)) +
+      scale_y_continuous() +
+      coord_cartesian(xlim=c(zoomedStartWeekFull, zoomedEndWeekFull), ylim=c(0, 4*seasonThreshold)) +
+      theme(
+        panel.grid.major.x=element_blank(),
+        legend.title=element_blank(),
+        axis.title.y=element_blank(),
+        axis.ticks.x=element_blank(),
+        axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
+        legend.position="bottom"
+      )
+    dev.off()
+@
+
+\begin{figure}
+\begin{center}
+\input{\figuresDir/tollandOnsetFull}
+\caption{Distribution of approximating $P$-splines and the calculated season onset with $N=\Sexpr{simulations}$ samples, for cumulative relative incidence of RSV-associated hospitalizations in Tolland county, Connecticut.}
+\label{fig:tollandOnsetFull}
+\end{center}
+\end{figure}
 
@@
 
-More interestingly, the same approach can be used to estimate time-series outcomes.
-We use this in our computation of preventable cases of RSV.
-We begin by defining a preventable case of RSV to be a case of RSV that occurs while prophylaxis (under a specific set of prophylaxis guidelines) offers protection; that is, a case that would have been prevented by administration of prophylaxis under those guidelines, if the prophylaxis were 100\% effective.
-As before, we obtain a $P$-spline approximation to our data.
+Furthermore, because our approach involves sampling approximations to the observed time series as a whole, rather than estimating the time series at isolated points in time, we are able to produce interval estimates of arbitrarily complex outcome measures.
 
-We then sample $P$-spline coefficients from their distributions to obtain a specific approximation to our data, and compute the corresponding time series of preventable RSV cases.
-Repeating the coefficient-sampling process yields time series of preventable RSV cases sampled from their (again unknown) distribution.
+We take advantage of this in our estimation of the preventable fraction of RSV cases.
+Here we begin by defining a preventable case of RSV to be a case of RSV that occurs while prophylaxis offers protection, and we define the preventable fraction of a prophylaxis administration strategy to be the ratio of preventable cases under that prophylaxis strategy to the total cases of RSV.
 
-This process can also be generalized to any time-series outcome of an infectious disease outbreak or season.
-
-Furthermore, the two approaches can be combined to calculate complex non-linear outcomes.
-We use this to estimate the fraction of preventable RSV cases in an RSV season, defined as the number of preventable cases divided by the total number of cases.
-The preventable fraction is a non-linear function of the RSV time series; as a result, interval estimation of the preventable fraction cannot be obtained by point-wise estimation of the RSV time, followed by applying a function to point-wise estimates.
-Instead, estimates of the entire time series must be sampled, and the preventable fraction then calculated for each sampled time series.
-
-Here we follow a similar process, wherein we sample coefficients from their distributions, use the resultant $P$-spline to calculate the all-case time series as well as the preventable-case time series, from which we then calculate the preventable fraction; the end result is that we sample the preventable fraction from its (unknown) distribution.
+As before, we then sample $P$-spline coefficients to obtain a specific $P$-spline approximation, and compute preventable fraction for each sampled $P$-spline in order to obtain the distribution of preventable fractions.
 

### 2019-03-01 Paper/Paper.R

@@ -1,4 +1,4 @@
-# ---- util ----
+# ---- paper ----
 library(magrittr)
 library(grid)
 library(tikzDevice)

### 2019-03-01 Paper/Supplement.R

@@ -1,6 +1,7 @@
-# ---- supplement ----
+# ---- supplement_libraries ----
 library(ggstance)
 
+# ---- supplement ----
 tollandObs = obsByCounty %>% filter(county=="Tolland")
 tollandModel = gam(rsv ~ s(time, k=20, bs="cp", m=3), family=poisson, data=tollandObs)
 
@@ -30,7 +31,7 @@ tollandOnsetMini = tollandParamsMini %>%
 zoomedStartWeek = min(monthBoundaries$min) + 5
 zoomedEndWeek = zoomedStartWeek + 21
 
-tollandNsim = simulations
+tollandNsimFull = simulations
 tollandParamsFull = randomMVN(coef(tollandModel), tollandModel$Vp, tollandNsimFull)
 
 tollandPredFull = tollandParamsFull %>%

### 2019-03-01 Paper/Paper.R
Label improvements

@@ -165,16 +165,16 @@ monthBoundaries = breaks.df %>%
 
 epiWeekBreaks = sort(unique(c(monthBoundaries$min, monthBoundaries$max)))
 
-legendLabels = function(labels, rep=2, leading=FALSE, trailing=TRUE) {
+legendLabels = function(labels, leading=0, trailing=2) {
   as.vector(sapply(labels, function(label) {
     if(substr(label, 1, 1) == "_") {
       paste0(rep(" ", nchar(label)), collapse="")
     } else {
-      if (leading) {
-        label = sprintf("%s%s", strrep("\\qquad{}", rep), label)
+      if (leading > 0) {
+        label = sprintf("%s%s", strrep("\\qquad{}", leading), label)
       }
-      if (trailing) {
-        label = sprintf("%s%s", label, strrep("\\qquad{}", rep))
+      if (trailing > 0) {
+        label = sprintf("%s%s", label, strrep("\\qquad{}", trailing))
       }
       label
     }

### 2019-03-01 Paper/RSVOptimization.rnw
Label improvements
Playing with supplement plots

@@
 
-    spanLabels = legendLabels(c("AAP-recommended prophylaxis", "RSV season"), leading=TRUE)
+    spanLabels = legendLabels(c("AAP-recommended prophylaxis", "RSV season"), leading=1)
 
@@
 A simple application of this is our estimation of RSV season onset.
-Consider, for example, RSV-associated hospitalizations in Tolland County, Connecticut in Figure \ref{fig:tollandCases}.
+Consider, for example, RSV-associated hospitalizations in Tolland county, Connecticut in Figure \ref{fig:tollandCases}.
 (This is a low-incidence county, which makes it a poor candidate for our main analysis, but its large confidence intervals make it easier to visualize our methods.)
@@
 
-    ggplot(tollandPredFull) +
-      theme_light(base_size=plotTextBaseSize) +
-      geom_ribbon(aes(x=time, ymin=min, ymax=max), fill="gray", na.rm=FALSE) +
+    data = tollandPredFull
+
+    ggplot(data) +
+      theme_light(base_size=plotTextBaseSize) +
+      geom_line(aes(x=time, y=rsv.cum.frac, group=sim), color="gray") +
       geom_segment(aes(x=-Inf, y=seasonThreshold, xend=+Inf, yend=seasonThreshold), linetype="11", data=data.frame(), size=.375) + 
@@
       scale_y_continuous() +
-      coord_cartesian(xlim=c(zoomedStartWeekFull, zoomedEndWeekFull), ylim=c(0, 4*seasonThreshold)) +
+      coord_cartesian(xlim=c(zoomedStartWeek, zoomedEndWeek), ylim=c(0, 4*seasonThreshold)) +
       theme(

### 2019-03-01 Paper/Supplement.R

@@ -18,10 +18,11 @@ tollandParamsMini = randomMVN(coef(tollandModel), tollandModel$Vp, tollandNsimMi
 tollandPredMini = tollandParamsMini %>%
   apply(1, function(params) { outbreak.calc.cum(1)(tollandModel, params, modelTime) } ) %>%
   data.frame() %>%
+  setnames(as.character(seq(1:tollandNsimMini))) %>%
   cbind(time=modelTime) %>%
   melt(c("time")) %>%
-  mutate(variable=as.numeric(substr(variable, 2, 2))) %>%
-  rename(sim=variable, rsv.cum.frac=value)
+  rename(sim=variable, rsv.cum.frac=value) %>%
+  mutate(sim=as.numeric(sim))
 
 tollandOnsetMini = tollandParamsMini %>%
   apply(1, function(params) { outbreak.calc.thresholds(seasonThreshold, 1-seasonThreshold)(tollandModel, params, modelTime) } ) %>%
@@ -37,21 +38,14 @@ tollandParamsFull = randomMVN(coef(tollandModel), tollandModel$Vp, tollandNsimFu
 tollandPredFull = tollandParamsFull %>%
   apply(1, function(params) { outbreak.calc.cum(1)(tollandModel, params, modelTime) } ) %>%
   data.frame() %>%
+  setnames(as.character(seq(1:tollandNsimFull))) %>%
   cbind(time=modelTime) %>%
   melt(c("time")) %>%
-  mutate(variable=as.numeric(substr(variable, 2, 2))) %>%
   rename(sim=variable, rsv.cum.frac=value) %>%
-  group_by(time) %>%
-  summarize(
-    min=min(rsv.cum.frac), 
-    max=max(rsv.cum.frac)
-  )
+  mutate(sim=as.numeric(sim))
 
 tollandOnsetFull = tollandParamsFull %>%
   apply(1, function(params) { outbreak.calc.thresholds(seasonThreshold, 1-seasonThreshold)(tollandModel, params, modelTime) } ) %>%
   bind_rows() %>%
   select(onset)
-
-zoomedStartWeekFull = min(monthBoundaries$min) + 5
-zoomedEndWeekFull = zoomedStartWeekFull + 21
 

### 2019-03-01 Paper/Supplement.R
Refactoring

@@ -5,47 +5,43 @@ library(ggstance)
 tollandObs = obsByCounty %>% filter(county=="Tolland")
 tollandModel = gam(rsv ~ s(time, k=20, bs="cp", m=3), family=poisson, data=tollandObs)
 
-tollandNsimMini = 5
-
 randomMVN = function(mu, sig, nsim) {
   L = mroot(sig)
   m = ncol(L)
   t(mu + L %*% matrix(rnorm(m * nsim), m, nsim))
 }
 
+tollandCalcPred = function(tollandParams, tollandNsim) {
+  tollandParams %>%
+    apply(1, function(params) { outbreak.calc.cum(1)(tollandModel, params, modelTime) } ) %>%
+    data.frame() %>%
+    setnames(as.character(seq(1:tollandNsim))) %>%
+    cbind(time=modelTime) %>%
+    melt(c("time")) %>%
+    rename(sim=variable, rsv.cum.frac=value) %>%
+    mutate(sim=as.numeric(sim))  
+}
+
+tollandCalcOnset = function(tollandParams) {
+  tollandParams %>% 
+    apply(1, function(params) { outbreak.calc.thresholds(seasonThreshold, 1-seasonThreshold)(tollandModel, params, modelTime) } ) %>%
+    bind_rows() %>%
+    select(onset)
+}
+
+tollandParamsSingle = randomMVN(coef(tollandModel), tollandModel$Vp, 1)
+tollandPredSingle = tollandParamsSingle %>% tollandCalcPred(1)
+
+tollandNsimMini = 5
 tollandParamsMini = randomMVN(coef(tollandModel), tollandModel$Vp, tollandNsimMini)
-
-tollandPredMini = tollandParamsMini %>%
-  apply(1, function(params) { outbreak.calc.cum(1)(tollandModel, params, modelTime) } ) %>%
-  data.frame() %>%
-  setnames(as.character(seq(1:tollandNsimMini))) %>%
-  cbind(time=modelTime) %>%
-  melt(c("time")) %>%
-  rename(sim=variable, rsv.cum.frac=value) %>%
-  mutate(sim=as.numeric(sim))
-
-tollandOnsetMini = tollandParamsMini %>%
-  apply(1, function(params) { outbreak.calc.thresholds(seasonThreshold, 1-seasonThreshold)(tollandModel, params, modelTime) } ) %>%
-  bind_rows() %>%
-  select(onset)
[…]

### 2019-03-01 Paper/structure.tex
Delete thesis-related files that I don’t need for the paper
Supplement improvements
Use lualatex to dodge pdflatex memory issues with large pgf plots

--- 2018-01-24 Thesis/structure.tex
@@
 \usepackage[hang, small, labelfont=bf, up, textfont=it]{caption} % Custom captions under/above tables and figures
+\usepackage{subcaption}
 
@@
 
-\usepackage[T1]{fontenc} % Output font encoding for international characters
-\usepackage[utf8]{inputenc} % Required for inputting international characters
+\usepackage{fontspec} % Output font encoding for international characters
+\usepackage{luatexbase} % Output font encoding for international characters
 
@@
 
-\addbibresource{../Thesis.bib} % The filename of the bibliography
+\addbibresource{../RSVOptimization.bib} % The filename of the bibliography
 \renewcommand{\cite}[1]{\autocite{#1}}

### 2019-03-01 Paper/RSVOptimization.rnw
Don’t show bajillion splines

@@
     data = tollandPredFull
+    splineData = data %>% filter(sim < tollandDisplayNsim)
 
@@
       theme_light(base_size=plotTextBaseSize) +
-      geom_line(aes(x=time, y=rsv.cum.frac, group=sim), color="gray") +
+      geom_line(data=splineData, aes(x=time, y=rsv.cum.frac, group=sim), color="gray") +
       geom_segment(aes(x=-Inf, y=seasonThreshold, xend=+Inf, yend=seasonThreshold), linetype="11", data=data.frame(), size=.375) + 
@@
       )
+
       dev.off()
@@
 \input{\figuresDir/tollandOnsetFull}
-\caption{Distribution of approximating $P$-splines and the calculated season onset with $N=\Sexpr{simulations}$ samples, for cumulative relative incidence of RSV-associated hospitalizations in Tolland county, Connecticut.}
+\caption{Distribution of approximating $P$-splines ($N=\Sexpr{tollandDisplayNsim}$) and season onset ($N=\Sexpr{tollandNsimFull}$), for cumulative relative incidence of RSV-associated hospitalizations in Tolland county, Connecticut.}
 \label{fig:tollandOnsetFull}

### 2019-03-01 Paper/Supplement.R

@@ -45,3 +45,4 @@ tollandParamsFull = randomMVN(coef(tollandModel), tollandModel$Vp, tollandNsimFu
 tollandPredFull = tollandParamsFull %>% tollandCalcPred(tollandNsimFull)
 tollandOnsetFull = tollandParamsFull %>% tollandCalcOnset()
 
+tollandDisplayNsim = 100

### 2019-03-01 Paper/RSVOptimization.rnw
Preventable fraction plots in supplement

@@
 <<tollandOnsetFull, results='hide', warning=FALSE>>=
-    tikz(sprintf("%s/tollandOnsetFull", figuresDir), width=pagePlotWidth * 0.4, height=pagePlotHeight, pointsize=10)
+    tikz(sprintf("%s/tollandOnsetFull.tex", figuresDir), width=pagePlotWidth * 0.4, height=pagePlotHeight, pointsize=10)
 
@@
 
+<<tollandPredSingle, results='hide', warning=FALSE>>=
+    tikz(sprintf("%s/tollandPredSingle.tex", figuresDir), width=pagePlotWidth * 0.4, height=pagePlotHeight, pointsize=10)
+
+    data = tollandPredSingle
+
+    thresholds = data %>%
+    	mutate(ppx=strat(time)) %>%
+    	filter(ppx > 0) %>%
+    	do((function(df) {
+    	  df = df %>% arrange(time)
+    		data.frame(
+    			ppx.start=min(df$time),
+    			ppx.end=max(df$time),
+    			unprotected.start=first(df$rsv.cum.frac),
+    			unprotected.end=last(df$rsv.cum.frac)
+    		)
+    	})(.)) %>%
+    	ungroup() %>%
+    	as.data.frame()
+
+    ggplot(data) +
+      theme_light(base_size=plotTextBaseSize) +
+      geom_line(aes(x=time, y=rsv.cum.frac, group=sim), color="grey") +
+      geom_segment(data=thresholds, aes(x=ppx.start, y=unprotected.start, xend=ppx.start, yend=+Inf), linetype="11", size=.375) + 
+      geom_segment(data=thresholds, aes(x=ppx.end, y=unprotected.end, xend=ppx.end, yend=+Inf), linetype="11", size=.375) + 
+      geom_segment(data=thresholds, aes(x=ppx.start, y=unprotected.start, xend=+Inf, yend=unprotected.start), linetype="11", size=.375) + 
+      geom_segment(data=thresholds, aes(x=ppx.end, y=unprotected.end, xend=+Inf, yend=unprotected.end), linetype="11", size=.375) + 
+      geom_point(data=tollandObs, aes(x=time, y=rsv.cum.frac, size=0.5), size=0.5) +
+    	geom_rect(data=thresholds, aes(xmin=ppx.start, xmax=ppx.end, ymin=1, ymax=1.1), size=.375) + 
+    	geom_text(data=thresholds, aes(x=mean(c(ppx.start, ppx.end)), y=1.05, label="Prophylaxis window"), color="white", size=1.75) + 
+    	geom_rect(data=thresholds, aes(xmin=max(monthBoundaries$max) - 3, xmax=max(monthBoundaries$max), ymin=unprotected.start, ymax=unprotected.end), size=.375) + 
+    	geom_text(data=thresholds, aes(x=max(monthBoundaries$max) - 1.5, y=mean(c(unprotected.start, unprotected.end)), label="$\\Delta$ = preventable fraction", angle=90, lineheight=0.5), color="white", size=1.75) +
+      scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, limits=range(c(monthBoundaries$min, monthBoundaries$max)), expand=c(0, 0)) + 
+      theme(
+        panel.grid.major.x=element_blank(),
+        legend.title=element_blank(),
+        axis.title.y=element_blank(),
+        axis.ticks.x=element_blank(),
+        axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
+        legend.position="bottom"
+      )
+
+    dev.off()
+@
+
+<<tollandPreventableFractionFull, results='hide', warning=FALSE>>=
+    tikz(sprintf("%s/tollandPreventableFractionFull.tex", figuresDir), width=pagePlotWidth * 0.4, height=pagePlotHeight, pointsize=10)
+
+    data = tollandPredFull
+    splineData = data %>% filter(sim < tollandDisplayNsim)
+
+    splinePlot = ggplot(data) +
+      theme_light(base_size=plotTextBaseSize) +
+      geom_line(data=splineData, aes(x=time, y=rsv.cum.frac, group=sim), color="gray") +
+      geom_segment(data=thresholds, aes(x=ppx.start, y=-Inf, xend=ppx.start, yend=+Inf), linetype="11", size=.375) + 
+      geom_segment(data=thresholds, aes(x=ppx.end, y=-Inf, xend=ppx.end, yend=+Inf), linetype="11", size=.375) + 
+    	geom_rect(data=thresholds, aes(xmin=ppx.start, xmax=ppx.end, ymin=1, ymax=1.1), size=.375) + 
+    	geom_text(data=thresholds, aes(x=mean(c(ppx.start, ppx.end)), y=1.05, label="Prophylaxis window"), color="white", size=1.75) + 
+      geom_point(data=tollandObs, aes(x=time, y=rsv.cum.frac), size=0.5) +
+      scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, expand=c(0, 0)) +
+      scale_y_continuous() +
+      theme(
+        panel.grid.major.x=element_blank(),
+        legend.title=element_blank(),
+        axis.title.y=element_blank(),
+        axis.ticks.x=element_blank(),
+        axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
+        legend.position="bottom"
+      )
+
+    violinPlot <- ggplot(tollandFractionFull) +
+      theme_light(base_size=plotTextBaseSize) +
+      geom_violin(
+        aes(x=0, y=unprotected),
+        width=.01,
+        fill="gray50", color="black",
+        trim=FALSE, draw_quantiles=c(0.025, 0.5, 0.975)
+      ) +
+      scale_x_continuous() +
+      scale_y_continuous(limits=c(0, 1)) +
+      theme(
+        panel.grid.major.x=element_blank(),
+        legend.title=element_blank(),
+        axis.title.y=element_blank(),
+        axis.ticks.x=element_blank(),
+        axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
+        legend.position="bottom"
+      ) 
+    grid.arrange(splinePlot, violinPlot, layout_matrix=rbind(c(rep(1, 4), 2)))
+
+    dev.off()
+@
+
+\begin{figure}
+\begin{center}
+\begin{subfigure}{.4\textwidth}
+    \begin{center}
+    \input{\figuresDir/tollandPredSingle}
+    \caption{Preventable fraction derived from a randomly sampled $P$-spline approximating the RSV time series.}
+    \label{fig:tollandPredMini}
+    \end{center}
+\end{subfigure}
+\begin{subfigure}{.4\textwidth}
+    \begin{center}
+    \input{\figuresDir/tollandPreventableFractionFull}
+    \caption{Distribution of approximating $P$-splines ($N=\Sexpr{tollandDisplayNsim}$) and preventable fractions ($N=\Sexpr{tollandNsimFull}$) of RSV under the AAP prophylaxis guidelines  in Tolland county, Connecticut.}
+    \label{fig:tollandOnsetMini}
+    \end{center}
+\end{subfigure}
+\end{center}
+\caption{Cumulative relative incidence of RSV-associated hospitalizations in Tolland county, Connecticut, with five randomly sampled approximating $P$-splines.}
+\end{figure}
+
 We developed a custom R package for estimation of arbitrary characteristics of infectious disease outbreaks or seasons (as long as they are amenable to generalized additive modeling); the package is available at \href{https://github.com/airbornemint/outbreak-inference}{\nolinkurl{github.com/airbornemint/outbreak-inference}}.

### 2019-03-01 Paper/Supplement.R

@@ -1,5 +1,6 @@
 # ---- supplement_libraries ----
 library(ggstance)
+library(gridExtra)
 
 # ---- supplement ----
 tollandObs = obsByCounty %>% filter(county=="Tolland")
@@ -29,8 +30,31 @@ tollandCalcOnset = function(tollandParams) {
     select(onset)
 }
 
+tollandStrat = ppxFixedStrategies("all")[["aap"]]
+
+tollandCalcFraction = function(tollandPred) {
+  tollandPred %>%
+    mutate(ppx=tollandStrat(time)) %>%
+    filter(ppx > 0) %>%
+    group_by(sim) %>%
+    do((function(df) {
+      df = df %>% arrange(time)
+      data.frame(
+        ppx.start=min(df$time),
+        ppx.end=max(df$time),
+        unprotected.start=first(df$rsv.cum.frac),
+        unprotected.end=last(df$rsv.cum.frac)
+      ) %>% mutate(
+        unprotected=unprotected.end-unprotected.start
+      )
+    })(.)) %>%
+    ungroup() %>%
+    as.data.frame()  
+}
+
 tollandParamsSingle = randomMVN(coef(tollandModel), tollandModel$Vp, 1)
 tollandPredSingle = tollandParamsSingle %>% tollandCalcPred(1)
+tollandFractionSingle = tollandPredSingle %>% tollandCalcFraction()
 
 tollandNsimMini = 5
 tollandParamsMini = randomMVN(coef(tollandModel), tollandModel$Vp, tollandNsimMini)
@@ -44,5 +68,6 @@ tollandNsimFull = simulations
 tollandParamsFull = randomMVN(coef(tollandModel), tollandModel$Vp, tollandNsimFull)
 tollandPredFull = tollandParamsFull %>% tollandCalcPred(tollandNsimFull)
 tollandOnsetFull = tollandParamsFull %>% tollandCalcOnset()
+tollandFractionFull = tollandPredFull %>% tollandCalcFraction()
 
 tollandDisplayNsim = 100

### 2019-03-02 Paper/RSVOptimization.rnw
Pushed onset/offset drift figure to supplements; resized prevental fraction supplemental figures

--- 2019-03-01 Paper/RSVOptimization.rnw
@@
 
+Our linear regression of median RSV season onset and offset over three-year periods indicates that season onset has slowly been drifting earlier (Supplemental figure \ref{fig:onsetOffsetByYear}), at a rate of \Sexpr{formatDrift(onsetByYear)} (\Sexpr{formatDriftCI(onsetByYear, level)}).
+It is unclear whether this is a part of a larger pattern, such as a cycle spanning decades.
+
+Season offset, on the other hand, has not been drifting earlier or later (\Sexpr{formatDriftCI(offsetByYear, level)}).
+
+\paragraph{Temporally-adjusted prophylaxis regimens are non-superior to others}
+
+<<coverageByRegionWithSliding, results='hide', warning=FALSE>>=
+    tikz(sprintf("%s/coverageByRegionRegimenWithSliding.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10)
+    data = unprotectedByCounty %>% 
+        filter(county %in% countiesForPlots, rounding==0, !grepl("county", strat))
+
+    ggplot(data) +
+        theme_light(base_size=plotTextBaseSize) +
+        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
+        scale_color_manual(name="Prophylaxis regimen", labels=legendLabels(stratLabels[c(seq(1, 3), seq(7, 10))]), values=c(rep(c(darkBrown, darkGreen), each=3), darkPurple)) + 
+        scale_shape_manual(name="Prophylaxis regimen", labels=legendLabels(stratLabels[c(seq(1, 3), seq(7, 10))]), values=c(16, 15, 17, 16, 15, 17, 16)) + 
+        geom_errorbar(
+            aes(ymin=frac.lower, ymax=frac.upper, x=county, color=strat, group=strat), 
+            width=.3, 
+            position=position_dodge(.5)
+        ) + 
+        geom_point(aes(y=frac.median, x=county, color=strat, shape=strat), position=position_dodge(.5), size=.75) +
+        labs(y="Preventable fraction") +
+        guides(color=guide_legend(keywidth=3, keyheight=1, ncol=3)) + 
+        scale_x_discrete(labels=countyLabels) + 
+        theme(
+            axis.title.x=element_blank(),
+            axis.ticks.x=element_blank(),
+            legend.position="bottom"
+        )
+    dev.off()
+@
+
+Compared to our regional all-years analysis, the three regimens based on statewide recent-years analysis produced non-superior results everywhere, and inferior results in the low-RSV counties (Figure \ref{fig:coverageByRegionRegimenWithSliding}).
+
+Due to the non-superiority of regimens based on statewide recent-years analysis, we did not evaluate regimens based on regional recent-years data.
+
+\section{Discussion}
+
+\begin{figure}
+\begin{center}
+\input{\figuresDir/coverageByRegionRegimenWithSliding.tex}
+\caption[Comparison of prophylaxis regimens based on all-years data to those based on recent-years data]{Comparison of prophylaxis regimens based on all-years data to those based on recent-years data, showing temporal analysis adds no benefit over spatial analysis alone.
+Preventable fraction: fraction of RSV hospitalizations occurring while the prophylaxis regimen offers protection}
+\label{fig:coverageByRegionRegimenWithSliding}
+\end{center}
+\end{figure}
+
+\subsection{Conclusions}
+
+Our analysis confirms the existence of regional variation of RSV season timing in Connecticut (defined by RSV season onset and offset) observable at the county level.
+
+We have also shown a misalignment between the prophylaxis schedule recommended by the AAP and the timing of the RSV season throughout Connecticut, with most counties' RSV season starting before protection from the first dose of prophylaxis takes hold, and ending before protection from the last dose wanes.
+This misalignment is particularly notable in Fairfield County, due to its early season onset.
+
+Our effort to optimize timing of the prophylaxis regimen (without changing its duration, and therefore its pharmaceutical cost) shows the possibility of a theoretical 1-2\% statewide decrease in RSV-associated hospitalizations among high-risk infants each year, primarily in counties with higher RSV burden (Fairfield, Hartford, and New Haven counties).
+
+The magnitude of that improvement wanes upon encountering practicalities of clinical practice guideline implementation.
+Nonetheless, with clinical practice guidelines localized at the county level, and the timing of prophylaxis adjusted in each county by less than a whole month from the current AAP guidelines, we still found the potential for $\sim$1\% statewide decrease in RSV-associated hospitalizations among high risk infants.
+
+The prophylaxis regimen with which we were able to attain this improvement is the one in which prophylaxis in each county is timed relative to the midpoint of the RSV season (rounded to two weeks) in that county, which simultaneously reduces unprotected cases early in the season and ineffective prophylaxis late in the season.
+
+Increasing complexity of practice guidelines carries with it increased cost of implementation, such as training of clinicians and other healthcare workers.
+It is therefore not apparent from our research alone that the potential benefits would outweigh the costs.
+
+Although we found a weak statewide trend in RSV season onset becoming earlier over time, further analysis did not yield any improvements to prophylaxis based on that trend.
+Since temporal variation in clinical guidelines would lead to a higher implementation burden than spatial variation, we see no reason to base RSV immunoprophylaxis clinical practice guidelines on temporal variation in RSV season timing.
+
+\subsection{Limitations}
+
+Although we were able to reach some conclusions about the impact of calendrical rounding on spatially adjusted prophylaxis regimens, ultimately our analysis is hamstrung by weekly aggregation of hospital admission data.
+To properly propose and evaluate any fine-tuning to RSV prophylaxis guidelines, we recommend use of daily data.
+
+Throughout, we assumed that RSV-associated hospitalizations are an unbiased estimate of RSV incidence in the general population; in doing so, we implicitly assumed that infectiousness and virulence of RSV are constant over time, for which we have no verification.
+
+Our model of palivizumab immunoprophylaxis assumes a protection period with a hard start at administration and a hard stop at 24 weeks post-administration; the physiologic response to monoclonal antibody immunoprophylaxis is actually tapered on both ends.
+
+Similarly, we assumed the protection by palivizumab is constant at 100\% throughout the protection period; however, not only is breakthrough RSV illness known to occur in patients on palivizumab, but it is an indication for discontinuing the prophylaxis regimen.
+
+In areas of Connecticut associated with a relatively high amount of interstate travel (such as urban centers near the state lines), our analysis --- by only considering residents of Connecticut --- likely underestimates RSV burden.
+
+Finally, towns that see substantial inter-county travel (for example, employment hubs near county lines) likely bias our regional analysis.
+
+\phantomsection
+\addcontentsline{toc}{section}{Bibliography}
+\printbibliography[title={Bibliography}]
+
+\cleardoublepage
+\begin{appendices}
+\renewcommand\thesection{\Roman{section}}
+\renewcommand\thefigure{S\arabic{figure}}
+\setcounter{figure}{0}
+
+\section{Supplemental figures}
+
+\label{supplement:figures}
+
 <<onsetOffsetByYear, results='hide', warning=FALSE>>=
@@
 
-Our linear regression of median RSV season onset and offset over three-year periods indicates that season onset has slowly been drifting earlier (Figure \ref{fig:onsetOffsetByYear}), at a rate of \Sexpr{formatDrift(onsetByYear)} (\Sexpr{formatDriftCI(onsetByYear, level)}).
-It is unclear whether this is a part of a larger pattern, such as a cycle spanning decades.
-
-Season offset, on the other hand, has not been drifting earlier or later (\Sexpr{formatDriftCI(offsetByYear, level)}).
-
 \begin{figure}
@@
 
-\paragraph{Temporally-adjusted prophylaxis regimens are non-superior to others}
-
-<<coverageByRegionWithSliding, results='hide', warning=FALSE>>=
-    tikz(sprintf("%s/coverageByRegionRegimenWithSliding.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10)
-    data = unprotectedByCounty %>% 
-        filter(county %in% countiesForPlots, rounding==0, !grepl("county", strat))
-
-    ggplot(data) +
-        theme_light(base_size=plotTextBaseSize) +
-        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
-        scale_color_manual(name="Prophylaxis regimen", labels=legendLabels(stratLabels[c(seq(1, 3), seq(7, 10))]), values=c(rep(c(darkBrown, darkGreen), each=3), darkPurple)) + 
-        scale_shape_manual(name="Prophylaxis regimen", labels=legendLabels(stratLabels[c(seq(1, 3), seq(7, 10))]), values=c(16, 15, 17, 16, 15, 17, 16)) + 
-        geom_errorbar(
-            aes(ymin=frac.lower, ymax=frac.upper, x=county, color=strat, group=strat), 
-            width=.3, 
-            position=position_dodge(.5)
-        ) + 
-        geom_point(aes(y=frac.median, x=county, color=strat, shape=strat), position=position_dodge(.5), size=.75) +
-        labs(y="Preventable fraction") +
-        guides(color=guide_legend(keywidth=3, keyheight=1, ncol=3)) + 
-        scale_x_discrete(labels=countyLabels) + 
-        theme(
-            axis.title.x=element_blank(),
-            axis.ticks.x=element_blank(),
-            legend.position="bottom"
-        )
-    dev.off()
-@
-
-Compared to our regional all-years analysis, the three regimens based on statewide recent-years analysis produced non-superior results everywhere, and inferior results in the low-RSV counties (Figure \ref{fig:coverageByRegionRegimenWithSliding}).
-
-Due to the non-superiority of regimens based on statewide recent-years analysis, we did not evaluate regimens based on regional recent-years data.
-
-\section{Discussion}
-
-\begin{figure}
-\begin{center}
-\input{\figuresDir/coverageByRegionRegimenWithSliding.tex}
-\caption[Comparison of prophylaxis regimens based on all-years data to those based on recent-years data]{Comparison of prophylaxis regimens based on all-years data to those based on recent-years data, showing temporal analysis adds no benefit over spatial analysis alone.
-Preventable fraction: fraction of RSV hospitalizations occurring while the prophylaxis regimen offers protection}
-\label{fig:coverageByRegionRegimenWithSliding}
-\end{center}
-\end{figure}
-
-\subsection{Conclusions}
-
-Our analysis confirms the existence of regional variation of RSV season timing in Connecticut (defined by RSV season onset and offset) observable at the county level.
-
-We have also shown a misalignment between the prophylaxis schedule recommended by the AAP and the timing of the RSV season throughout Connecticut, with most counties' RSV season starting before protection from the first dose of prophylaxis takes hold, and ending before protection from the last dose wanes.
-This misalignment is particularly notable in Fairfield County, due to its early season onset.
-
-Our effort to optimize timing of the prophylaxis regimen (without changing its duration, and therefore its pharmaceutical cost) shows the possibility of a theoretical 1-2\% statewide decrease in RSV-associated hospitalizations among high-risk infants each year, primarily in counties with higher RSV burden (Fairfield, Hartford, and New Haven counties).
-
-The magnitude of that improvement wanes upon encountering practicalities of clinical practice guideline implementation.
-Nonetheless, with clinical practice guidelines localized at the county level, and the timing of prophylaxis adjusted in each county by less than a whole month from the current AAP guidelines, we still found the potential for $\sim$1\% statewide decrease in RSV-associated hospitalizations among high risk infants.
-
-The prophylaxis regimen with which we were able to attain this improvement is the one in which prophylaxis in each county is timed relative to the midpoint of the RSV season (rounded to two weeks) in that county, which simultaneously reduces unprotected cases early in the season and ineffective prophylaxis late in the season.
-
-Increasing complexity of practice guidelines carries with it increased cost of implementation, such as training of clinicians and other healthcare workers.
-It is therefore not apparent from our research alone that the potential benefits would outweigh the costs.
-
-Although we found a weak statewide trend in RSV season onset becoming earlier over time, further analysis did not yield any improvements to prophylaxis based on that trend.
-Since temporal variation in clinical guidelines would lead to a higher implementation burden than spatial variation, we see no reason to base RSV immunoprophylaxis clinical practice guidelines on temporal variation in RSV season timing.
-
-\subsection{Limitations}
-
-Although we were able to reach some conclusions about the impact of calendrical rounding on spatially adjusted prophylaxis regimens, ultimately our analysis is hamstrung by weekly aggregation of hospital admission data.
-To properly propose and evaluate any fine-tuning to RSV prophylaxis guidelines, we recommend use of daily data.
-
-Throughout, we assumed that RSV-associated hospitalizations are an unbiased estimate of RSV incidence in the general population; in doing so, we implicitly assumed that infectiousness and virulence of RSV are constant over time, for which we have no verification.
-
-Our model of palivizumab immunoprophylaxis assumes a protection period with a hard start at administration and a hard stop at 24 weeks post-administration; the physiologic response to monoclonal antibody immunoprophylaxis is actually tapered on both ends.
-
-Similarly, we assumed the protection by palivizumab is constant at 100\% throughout the protection period; however, not only is breakthrough RSV illness known to occur in patients on palivizumab, but it is an indication for discontinuing the prophylaxis regimen.
-
-In areas of Connecticut associated with a relatively high amount of interstate travel (such as urban centers near the state lines), our analysis --- by only considering residents of Connecticut --- likely underestimates RSV burden.
-
-Finally, towns that see substantial inter-county travel (for example, employment hubs near county lines) likely bias our regional analysis.
-
-\phantomsection
-\addcontentsline{toc}{section}{Bibliography}
-\printbibliography[title={Bibliography}]
-
 \cleardoublepage
-\begin{appendices}
-
 \section{Interval estimation of complex outcomes using penalized basis splines}
@@
 
+<<tollandPredSingle, results='hide', warning=FALSE>>=
+    tikz(sprintf("%s/tollandPredSingle.tex", figuresDir), width=0.8*pagePlotWidth, height=2*pagePlotHeight, pointsize=10)
+
+    data = tollandPredSingle
+
+    thresholds = data %>%
+    	mutate(ppx=strat(time)) %>%
+    	filter(ppx > 0) %>%
+    	do((function(df) {
+    	  df = df %>% arrange(time)
+    		data.frame(
+    			ppx.start=min(df$time),
+    			ppx.end=max(df$time),
+    			unprotected.start=first(df$rsv.cum.frac),
+    			unprotected.end=last(df$rsv.cum.frac)
+    		)
+    	})(.)) %>%
+    	ungroup() %>%
+    	as.data.frame()
+
+    ggplot(data) +
+      theme_light(base_size=plotTextBaseSize) +
+      geom_line(aes(x=time, y=rsv.cum.frac, group=sim), color="grey") +
+      geom_segment(data=thresholds, aes(x=ppx.start, y=unprotected.start, xend=ppx.start, yend=+Inf), linetype="11", size=.375) + 
+      geom_segment(data=thresholds, aes(x=ppx.end, y=unprotected.end, xend=ppx.end, yend=+Inf), linetype="11", size=.375) + 
+      geom_segment(data=thresholds, aes(x=ppx.start, y=unprotected.start, xend=+Inf, yend=unprotected.start), linetype="11", size=.375) + 
+      geom_segment(data=thresholds, aes(x=ppx.end, y=unprotected.end, xend=+Inf, yend=unprotected.end), linetype="11", size=.375) + 
+      geom_point(data=tollandObs, aes(x=time, y=rsv.cum.frac, size=0.5), size=0.5) +
+    	geom_rect(data=thresholds, aes(xmin=ppx.start, xmax=ppx.end, ymin=1, ymax=1.1), size=.375) + 
+    	geom_text(data=thresholds, aes(x=mean(c(ppx.start, ppx.end)), y=1.05, label="Prophylaxis window"), color="white", size=3.5) + 
+    	geom_rect(data=thresholds, aes(xmin=max(monthBoundaries$max) - 3, xmax=max(monthBoundaries$max), ymin=unprotected.start, ymax=unprotected.end), size=.375) + 
+    	geom_text(data=thresholds, aes(x=max(monthBoundaries$max) - 1.5, y=mean(c(unprotected.start, unprotected.end)), label="$\\Delta$ = preventable fraction", angle=90, lineheight=0.5), color="white", size=3.5) +
+      scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, limits=range(c(monthBoundaries$min, monthBoundaries$max)), expand=c(0, 0)) + 
+      theme(
+        panel.grid.major.x=element_blank(),
+        legend.title=element_blank(),
+        axis.title.y=element_blank(),
+        axis.ticks.x=element_blank(),
+        axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
+        legend.position="bottom"
+      )
+
+    dev.off()
+@
+
+<<tollandPreventableFractionFull, results='hide', warning=FALSE>>=
+    tikz(sprintf("%s/tollandPreventableFractionFull.tex", figuresDir), width=0.8*pagePlotWidth, height=2*pagePlotHeight, pointsize=10)
+
+    data = tollandPredFull
+    splineData = data %>% filter(sim < tollandDisplayNsim)
+
+    splinePlot = ggplot(data) +
+      theme_light(base_size=plotTextBaseSize) +
+      geom_line(data=splineData, aes(x=time, y=rsv.cum.frac, group=sim), color="gray") +
+      geom_segment(data=thresholds, aes(x=ppx.start, y=-Inf, xend=ppx.start, yend=+Inf), linetype="11", size=.375) + 
+      geom_segment(data=thresholds, aes(x=ppx.end, y=-Inf, xend=ppx.end, yend=+Inf), linetype="11", size=.375) + 
+    	geom_rect(data=thresholds, aes(xmin=ppx.start, xmax=ppx.end, ymin=1, ymax=1.1), size=.375) + 
+    	geom_text(data=thresholds, aes(x=mean(c(ppx.start, ppx.end)), y=1.05, label="Prophylaxis window"), color="white", size=1.75) + 
+      geom_point(data=tollandObs, aes(x=time, y=rsv.cum.frac), size=0.5) +
+      scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, expand=c(0, 0)) +
+      scale_y_continuous() +
+      theme(
+        panel.grid.major.x=element_blank(),
+        legend.title=element_blank(),
+        axis.title.y=element_blank(),
+        axis.ticks.x=element_blank(),
+        axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
+        legend.position="bottom"
+      )
+
+    violinPlot <- ggplot(tollandFractionFull) +
+      theme_light(base_size=plotTextBaseSize) +
+      geom_violin(
+        aes(x=0, y=unprotected),
+        width=.01,
+        fill="gray50", color="black",
+        trim=FALSE, draw_quantiles=c(0.025, 0.5, 0.975)
+      ) +
+      scale_x_continuous() +
+      scale_y_continuous(limits=c(0, 1)) +
+      theme(
+        panel.grid.major.x=element_blank(),
+        legend.title=element_blank(),
+        axis.title.y=element_blank(),
+        axis.ticks.x=element_blank(),
+        axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
+        legend.position="bottom"
+      ) 
+    grid.arrange(splinePlot, violinPlot, layout_matrix=rbind(c(rep(1, 4), 2)))
+
+    dev.off()
+@
+
+\begin{figure}
+    \begin{center}
+    \input{\figuresDir/tollandPredSingle}
+    \caption{A single estimate of the preventable fraction of RSV under the AAP prophylaxis guidelines, derived from a randomly sampled $P$-spline approximating the time series of RSV-associated hospitalizations in Tolland county, Connecticut.}
+    \label{fig:tollandPredMini}
+    \end{center}
+\end{figure}
+\begin{figure}
+    \begin{center}
+    \input{\figuresDir/tollandPreventableFractionFull}
+    \caption{Distribution of approximating $P$-splines ($N=\Sexpr{tollandDisplayNsim}$) and RSV preventable fractions ($N=\Sexpr{tollandNsimFull}$) under the AAP prophylaxis guidelines in Tolland county, Connecticut.}
+    \label{fig:tollandOnsetMini}
+    \end{center}
+\end{figure}
+
 We developed a custom R package for estimation of arbitrary characteristics of infectious disease outbreaks or seasons (as long as they are amenable to generalized additive modeling); the package is available at \href{https://github.com/airbornemint/outbreak-inference}{\nolinkurl{github.com/airbornemint/outbreak-inference}}.

### 2019-03-02 Paper/RSVOptimization.rnw
Fixing AAP placement in plots

@@
     data = unprotectedByCounty %>% 
-        filter(county %in% countiesForPlots, rounding==0, sliding==FALSE)
+        filter(county %in% countiesForPlots, rounding==0, sliding==FALSE) %>%
+        mutate(strat=factor(strat, levels=c(levels(strat)[1], "_1", "_2", levels(strat)[2:7])))
 
@@
         scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
-        scale_color_manual(name="Prophylaxis regimen", labels=legendLabels(stratLabels[c(seq(1, 6), 10)]), values=c(rep(c(darkBrown, darkOrange), each=3), darkPurple)) + 
-        scale_shape_manual(name="Prophylaxis regimen", labels=legendLabels(stratLabels[c(seq(1, 6), 10)]), values=c(16, 15, 17, 16, 15, 17, 16)) + 
+        scale_color_manual(
+          name="Prophylaxis regimen", 
+          labels=legendLabels(c(as.vector(stratLabels[10]), "_1", "_2", as.vector(stratLabels[1:6]))),
+          values=c(
+            darkPurple, 
+            NA, NA, 
+            rep(c(darkBrown, darkOrange), each=3), darkPurple
+          ), 
+          drop=FALSE
+        ) + 
+        scale_shape_manual(
+          name="Prophylaxis regimen", 
+          labels=legendLabels(c(as.vector(stratLabels[10]), "_1", "_2", as.vector(stratLabels[1:6]))),
+          values=c(
+            16, 
+            16, 16, 
+            16, 15, 17, 
+            16, 15, 17
+          ), 
+          drop=FALSE
+        ) + 
         geom_errorbar(
@@
           breaks=factor(sprintf("%s.%s", levels(data$strat), FALSE), levels=strat.isRepeat.levels),
-          labels=legendLabels(c(as.vector(stratLabels[10]), "_", "__", as.vector(stratLabels[1:6]))),
+          labels=legendLabels(c(as.vector(stratLabels[10]), "_1", "_2", as.vector(stratLabels[1:6]))),
           values=c(
@@
     data = unprotectedByCounty %>% 
-        filter(county %in% countiesForPlots, rounding==0, !grepl("county", strat))
+        filter(county %in% countiesForPlots, rounding==0, !grepl("county", strat)) %>%
+        mutate(strat=factor(strat, levels=c(levels(strat)[1], "_1", "_2", levels(strat)[2:4], levels(strat)[8:10])))
 
@@
         scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
-        scale_color_manual(name="Prophylaxis regimen", labels=legendLabels(stratLabels[c(seq(1, 3), seq(7, 10))]), values=c(rep(c(darkBrown, darkGreen), each=3), darkPurple)) + 
-        scale_shape_manual(name="Prophylaxis regimen", labels=legendLabels(stratLabels[c(seq(1, 3), seq(7, 10))]), values=c(16, 15, 17, 16, 15, 17, 16)) + 
+        scale_color_manual(
+          name="Prophylaxis regimen", 
+          labels=legendLabels(c(as.vector(stratLabels[10]), "_1", "_2", as.vector(stratLabels[1:3]), as.vector(stratLabels[7:9]))),
+          values=c(
+            darkPurple, 
+            NA, NA, 
+            rep(c(darkBrown, darkGreen), each=3), darkPurple
+          ), 
+          drop=FALSE
+        ) + 
+        scale_shape_manual(
+          name="Prophylaxis regimen", 
+          labels=legendLabels(c(as.vector(stratLabels[10]), "_1", "_2", as.vector(stratLabels[1:3]), as.vector(stratLabels[7:9]))),
+          values=c(
+            16, 
+            16, 16, 
+            16, 15, 17, 
+            16, 15, 17
+          ), 
+          drop=FALSE
+        ) + 
         geom_errorbar(

### 2019-03-02 Paper/Paper.R

@@ -168,7 +168,7 @@ epiWeekBreaks = sort(unique(c(monthBoundaries$min, monthBoundaries$max)))
 legendLabels = function(labels, leading=0, trailing=2) {
   as.vector(sapply(labels, function(label) {
     if(substr(label, 1, 1) == "_") {
-      paste0(rep(" ", nchar(label)), collapse="")
+      paste0(rep(" ", as.numeric(substring(label, 2))), collapse="")
     } else {
       if (leading > 0) {
         label = sprintf("%s%s", strrep("\\qquad{}", leading), label)

### 2019-03-11 Paper/RSVOptimization.rnw
Arabic numbers for supplements
Various feedback from Ginny

@@
 \documentclass[10pt,letter]{article}
+\usepackage{verbatim}
 \usepackage{float}
@@
 \renewcommand*{\thefootnote}{\fnsymbol{footnote}}
+\renewenvironment{knitrout}{\expandafter\comment}{\expandafter\endcomment}
 
@@
     \authorstyle{Ben Artin, MEng, MPH, MMSc\textsuperscript{1}}
-    \newline\newline
     \authorstyle{Daniel Weinberger, PhD\textsuperscript{1}}\\
@@
 In all states except for Florida, RSV shows an annual or biennial cycle with a stable seasonal onset between mid-November and early January and a stable seasonal offset between mid-March and late April.\cite{CentersforDiseaseControlandPreventionCDC:2011wt,CentersforDiseaseControlandPreventionCDC:2013wv} RSV season in Florida begins approximately two months earlier than in other states.
-\cite{CentersforDiseaseControlandPreventionCDC:2013wv}
-
-The AAP acknowledges the potential significance of spatial and temporal variation in RSV incidence, but --- outside of Florida --- does not recommend local variance from nationwide prophylaxis guidelines.\cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
+\cite{CentersforDiseaseControlandPreventionCDC:2013wv} The AAP acknowledges the potential significance of spatial and temporal variation in RSV incidence, but --- outside of Florida --- does not recommend local variance from nationwide prophylaxis guidelines.\cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
 
@@
 To that end, we fit smooth curves through annual RSV hospitalization data, and used resampling to obtain interval estimates.
-(See Supplement \ref{supplement:splines}.)
+(See ???.)
+
+% TODO ref spline paper
 
@@
     \item \textbf{By statewide all-years offset}: prophylaxis administration begins 24 weeks before the (statewide all-years median) RSV season offset. 
-    \item \textbf{By regional all-years onset}: prophylaxis administration begins at regional\footnote{county-wide, or --- in the case of low-RSV counties --- low-RSV-region-wide} all-years median RSV season onset.
+    \item \textbf{By regional all-years onset}: prophylaxis administration begins at regional (county-wide, or --- in the case of low-RSV counties --- low-RSV-region-wide) all-years median RSV season onset.
     \item \textbf{By regional all-years midpoint}: prophylaxis administration begins 12 weeks before the average of the (regional all-years median) RSV season onset and offset. 
@@
 To analyze the effects on prophylaxis regimens of year-to-year variation between RSV seasons, we chose to aggregate our data into (overlapping) periods of three consecutive years --- in order to maintain a higher level of statistical power, as well as to limit the impact of short-term variation on our results.
-
-TODO This gave us \Sexpr{year(endDate) - year(startDate) -1} three-year periods, with the \Sexpr{formatYear(startDate + 2*365)} period covering surveillance years \Sexpr{formatYear(startDate)} through \Sexpr{formatYear(startDate + 2*365)}, and the \Sexpr{formatYear(endDate)} period covering \Sexpr{formatYear(endDate - 2*365)} through \Sexpr{formatYear(endDate)}.
+This gave us \Sexpr{year(endDate) - year(startDate) - 1} three-year periods, with the \Sexpr{formatYear(startDate + 2*365)} period covering surveillance years \Sexpr{formatYear(startDate)} through \Sexpr{formatYear(startDate + 2*365)}, and the \Sexpr{formatYear(endDate)} period covering \Sexpr{formatYear(endDate - 2*365)} through \Sexpr{formatYear(endDate)}.
 
 We began our temporal analysis by estimating onset and offset for each three-year period, using the same penalized spline GAM as for the all-years analysis, producing --- as before --- statewide and regional estimates of \Sexpr{seasonThreshold * 100}\% onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset.
-
 To evaluate year-to-year variation in RSV season onset and offset we modeled median RSV three-year onset and offset against time using simple linear regression.
-
 We did not analyze any other long-term patterns, such as cyclicity.
@@
 We then compared those regimens to the one recommended by the AAP and to the six spatially adjusted alternatives (with no calendrical rounding) discussed above.
-
 As before, these alternative regimens involved five monthly doses of palivizumab giving 24 weeks of protection.
@@
 
-Compared to the statewide median onset of RSV season at \Sexpr{regionOnset("all")} weeks (\Sexpr{regionOnsetCI("all", level)} weeks) and offset at \Sexpr{regionOffset("all")} weeks (\Sexpr{regionOffsetCI("all", level)} weeks), RSV season in Fairfield county has earlier median onset at \Sexpr{regionOnset("Fairfield")} weeks (\Sexpr{regionOnsetCI("Fairfield", level)} weeks) and later median offset at \Sexpr{regionOffset("Fairfield")} weeks (\Sexpr{regionOffsetCI("Fairfield", level)} weeks) (Figure \ref{fig:seasonByRegion}).
-
 \begin{figure}
@@
 
-TODO Meanwhile, in comparison with the statewide RSV season onset and offset, the low-RSV region has RSV season with later onset at \Sexpr{regionOnset("lowIncidence")} weeks (\Sexpr{regionOnsetCI("all", level)} weeks); season offset shows no change from the statewide median (Figure \ref{fig:seasonByRegion}).
+Compared to the statewide median onset of the RSV season at \Sexpr{regionOnset("all")} weeks (\Sexpr{regionOnsetCI("all", level)} weeks) and offset at \Sexpr{regionOffset("all")} weeks (\Sexpr{regionOffsetCI("all", level)} weeks), RSV season in Fairfield county the earliest median onset at \Sexpr{regionOnset("Fairfield")} weeks (\Sexpr{regionOnsetCI("Fairfield", level)} weeks) and the latest median offset at \Sexpr{regionOffset("Fairfield")} weeks (\Sexpr{regionOffsetCI("Fairfield", level)} weeks).
+Meanwhile, the RSV season in the low-RSV region has the latest onset at \Sexpr{regionOnset("lowIncidence")} weeks (\Sexpr{regionOnsetCI("all", level)} weeks); its season offset shows no change from the statewide median (Figure \ref{fig:seasonByRegion}).
 
@@
 
-Statewide, our model shows that \Sexpr{regionStrategyCoverage("all", "aap", 0)} of RSV cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) occur while palivizumab, administered per the AAP guidelines, offers protection.
-
 \begin{figure}
@@
 
+Statewide, our model shows that \Sexpr{regionStrategyCoverage("all", "aap", 0)} of RSV cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) occur while palivizumab, administered per the AAP guidelines, offers protection.
 The AAP guidelines perform better in the low-RSV counties, where \Sexpr{regionStrategyCoverage("lowIncidence", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("lowIncidence", "aap", 0, level)}) occur during the prophylaxis interval, but worse in Fairfield county, where \Sexpr{regionStrategyCoverage("Fairfield", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("Fairfield", "aap", 0, level)}) occur during this time (Figure \ref{fig:coverageByRegionAAP}).
+
+% Separate paragraph because observation above, cause below
 
@@
 Based on all-years data, the six spatially adjusted prophylaxis regimens (with no rounding of prophylaxis dates), when compared to the AAP guidelines, yield non-inferior results in all regions, and superior results statewide (Figure \ref{fig:coverageByRegionRegimen}).
-
 Statewide, the AAP guidelines offer protection to \Sexpr{regionStrategyCoverage("all", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}).
 The alternative regimen based on all-years statewide onset yields the smallest increase, to \Sexpr{regionStrategyCoverage("all", "stateOnset", 0)} (\Sexpr{regionStrategyCoverageCI("all", "stateOnset", 0, level)}); other alternative regimens yield similar results.
-
 Most of the increase comes from Hartford county, where the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", 0, level)}), whereas the alternative regimen based on all-years regional offset generates the smallest increase, to \Sexpr{regionStrategyCoverage("Hartford", "countyOffset", 0)} (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", 0, level)}); other alternative regimens are comparable.
-
 In every region, all alternative regimens based on all-years analysis are non-inferior to the AAP guidelines and non-superior to each other.
@@
 
-After we applied weekly, biweekly, and monthly rounding to start and end dates of our six alternative immunoprophylaxis regimens, we found that longer rounding intervals diminished the benefit of spatial analysis (Figure \ref{fig:coverageByRoundingRegimen}).
-
-With weekly rounding, our regimens were non-inferior to the AAP recommendation, and produced an increase in preventable fraction from AAP's \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) to \Sexpr{bestCaseCoverage(1)} (\Sexpr{bestCaseCoverageCI(1, level)}) statewide.
-
-Biweekly rounding yielded regimens similarly non-inferior to the AAP recommendation, with an increase in preventable fraction to \Sexpr{bestCaseCoverage(2)} (\Sexpr{bestCaseCoverageCI(2, level)}) statewide.
-
-However, with monthly rounding, the gains almost completely vanished, with preventable fraction not exceeding \Sexpr{bestCaseCoverage(4)} (\Sexpr{bestCaseCoverageCI(4, level)}).
-Furthermore, all our regimens with monthly rounding were non-superior to the AAP-recommended regimen in all regions.
-
 \begin{figure}
@@
 
-%\columnbreak
+After we applied weekly, biweekly, and monthly rounding to start and end dates of our six alternative immunoprophylaxis regimens, we found that longer rounding intervals diminished the benefit of spatial analysis (Figure \ref{fig:coverageByRoundingRegimen}).
+With weekly rounding, our regimens were non-inferior to the AAP recommendation, and produced an increase in preventable fraction from AAP's \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) to \Sexpr{bestCaseCoverage(1)} (\Sexpr{bestCaseCoverageCI(1, level)}) statewide.
+Biweekly rounding yielded regimens similarly non-inferior to the AAP recommendation, with an increase in preventable fraction to \Sexpr{bestCaseCoverage(2)} (\Sexpr{bestCaseCoverageCI(2, level)}) statewide.
+However, with monthly rounding, the gains almost completely vanished, with preventable fraction not exceeding \Sexpr{bestCaseCoverage(4)} (\Sexpr{bestCaseCoverageCI(4, level)}).
+Furthermore, all our regimens with monthly rounding were non-superior to the AAP-recommended regimen in all regions.
 
@@
 It is unclear whether this is a part of a larger pattern, such as a cycle spanning decades.
-
 Season offset, on the other hand, has not been drifting earlier or later (\Sexpr{formatDriftCI(offsetByYear, level)}).
@@
 
-Compared to our regional all-years analysis, the three regimens based on statewide recent-years analysis produced non-superior results everywhere, and inferior results in the low-RSV counties (Figure \ref{fig:coverageByRegionRegimenWithSliding}).
-
-Due to the non-superiority of regimens based on statewide recent-years analysis, we did not evaluate regimens based on regional recent-years data.
-
-\section{Discussion}
-
 \begin{figure}
@@
 
+Compared to our regional all-years analysis, the three regimens based on statewide recent-years analysis produced non-superior results everywhere, and inferior results in the low-RSV counties (Figure \ref{fig:coverageByRegionRegimenWithSliding}).
+Due to the non-superiority of regimens based on statewide recent-years analysis, we did not evaluate regimens based on regional recent-years data.
+
+\section{Discussion}
+
 \subsection{Conclusions}
@@
 Our analysis confirms the existence of regional variation of RSV season timing in Connecticut (defined by RSV season onset and offset) observable at the county level.
-
 We have also shown a misalignment between the prophylaxis schedule recommended by the AAP and the timing of the RSV season throughout Connecticut, with most counties' RSV season starting before protection from the first dose of prophylaxis takes hold, and ending before protection from the last dose wanes.
@@
 
+% Separate paragraph here because seasonal variation above, prophylaxis optimization below
+
 Our effort to optimize timing of the prophylaxis regimen (without changing its duration, and therefore its pharmaceutical cost) shows the possibility of a theoretical 1-2\% statewide decrease in RSV-associated hospitalizations among high-risk infants each year, primarily in counties with higher RSV burden (Fairfield, Hartford, and New Haven counties).
-
 The magnitude of that improvement wanes upon encountering practicalities of clinical practice guideline implementation.
 Nonetheless, with clinical practice guidelines localized at the county level, and the timing of prophylaxis adjusted in each county by less than a whole month from the current AAP guidelines, we still found the potential for $\sim$1\% statewide decrease in RSV-associated hospitalizations among high risk infants.
-
 The prophylaxis regimen with which we were able to attain this improvement is the one in which prophylaxis in each county is timed relative to the midpoint of the RSV season (rounded to two weeks) in that county, which simultaneously reduces unprotected cases early in the season and ineffective prophylaxis late in the season.
-
 Increasing complexity of practice guidelines carries with it increased cost of implementation, such as training of clinicians and other healthcare workers.
@@
 Our model of palivizumab immunoprophylaxis assumes a protection period with a hard start at administration and a hard stop at 24 weeks post-administration; the physiologic response to monoclonal antibody immunoprophylaxis is actually tapered on both ends.
-
 Similarly, we assumed the protection by palivizumab is constant at 100\% throughout the protection period; however, not only is breakthrough RSV illness known to occur in patients on palivizumab, but it is an indication for discontinuing the prophylaxis regimen.
@@
 In areas of Connecticut associated with a relatively high amount of interstate travel (such as urban centers near the state lines), our analysis --- by only considering residents of Connecticut --- likely underestimates RSV burden.
-
 Finally, towns that see substantial inter-county travel (for example, employment hubs near county lines) likely bias our regional analysis.
@@
 \begin{appendices}
-\renewcommand\thesection{\Roman{section}}
+\renewcommand\thesection{\arabic{section}}
 \renewcommand\thefigure{S\arabic{figure}}

### 2019-03-11 Paper/RSVOptimization.rnw
Taking out the spline supplement

@@
 \usepackage[toc,page]{appendix}
-\renewcommand{\appendixpagename}{Supplements}
-\renewcommand{\appendixname}{Supplement}
+\renewcommand{\appendixpagename}{Supplemental Figures}
+\renewcommand{\appendixname}{Supplemental Figures}
 
@@
 knitr::read_chunk("../Paper/Paper.R")
-knitr::read_chunk("../Paper/Supplement.R")
 @
@@
 
-\section{Supplemental figures}
-
 \label{supplement:figures}
@@
 
-\cleardoublepage
-\section{Interval estimation of complex outcomes using penalized basis splines}
-\begin{refsection}
-
-\label{supplement:splines}
-
-<<supplement_libraries, cache=FALSE>>=
-@
-
-<<supplement, cache=TRUE>>=
-@
-
-Penalized basis splines (``$P$-splines'') provide a smoothing mechanism with several qualities desirable in analysis of experimental data, including computational compactness and efficiency, and well-understood statistical behavior.
-Most importantly for our RSV analysis, the parameters of a $P$-spline approximation have known statistical distributions, which allows interval estimation of arbitrary outcome measures.\cite{Eilers:1996kz}
-
-A simple application of this is our estimation of RSV season onset.
-Consider, for example, RSV-associated hospitalizations in Tolland county, Connecticut in Figure \ref{fig:tollandCases}.
-(This is a low-incidence county, which makes it a poor candidate for our main analysis, but its large confidence intervals make it easier to visualize our methods.)
-
-<<tollandCases, results='hide', warning=FALSE>>=
-    tikz(sprintf("%s/tollandCases.tex", figuresDir), width=pagePlotWidth * 0.4, height=pagePlotHeight, pointsize=10)
-
-    ggplot(tollandObs) +
-        theme_light(base_size=plotTextBaseSize) +
-        geom_point(aes(x=time, y=rsv.cum.frac), size=.5) +
-        scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, limits=range(c(monthBoundaries$min, monthBoundaries$max)), expand=c(0, 0)) + 
-        theme(
-            panel.grid.major.x=element_blank(),
-            legend.title=element_blank(),
-            axis.title.y=element_blank(),
-            axis.ticks.x=element_blank(),
-            axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
-            legend.position="bottom"
-        )
-
-    dev.off()
-@
-
-\begin{figure}
-\begin{center}
-\input{\figuresDir/tollandCases.tex}
-\caption{Cumulative relative incidence of RSV-associated hospitalizations in Tolland county, Connecticut, aggregated across years \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}}
-\label{fig:tollandCases}
-\end{center}
-\end{figure}
-
-<<tollandPredMini, results='hide', warning=FALSE>>=
-    tikz(sprintf("%s/tollandPredMini.tex", figuresDir), width=pagePlotWidth * 0.4, height=pagePlotHeight, pointsize=10)
-
-    ggplot(tollandPredMini) +
-      theme_light(base_size=plotTextBaseSize) +
-      geom_line(aes(x=time, y=rsv.cum.frac, group=sim), color="grey") +
-      geom_segment(aes(x=-Inf, y=seasonThreshold, xend=+Inf, yend=seasonThreshold), linetype="11", data=data.frame(), size=.375) + 
-      geom_point(data=tollandObs, aes(x=time, y=rsv.cum.frac), size=0.5) +
-      scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, limits=range(c(monthBoundaries$min, monthBoundaries$max)), expand=c(0, 0)) + 
-      theme(
-        panel.grid.major.x=element_blank(),
-        legend.title=element_blank(),
-        axis.title.y=element_blank(),
-        axis.ticks.x=element_blank(),
-        axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
-        legend.position="bottom"
-      )
-
-    dev.off()
-@
-
-<<tollandOnsetMini, results='hide', warning=FALSE>>=
-    tikz(sprintf("%s/tollandOnsetMini.tex", figuresDir), width=pagePlotWidth * 0.4, height=pagePlotHeight, pointsize=10)
-
-    ggplot(tollandPredMini) +
-      theme_light(base_size=plotTextBaseSize) +
-      geom_line(aes(x=time, y=rsv.cum.frac, group=sim), color="grey") +
-      geom_segment(aes(x=-Inf, y=seasonThreshold, xend=+Inf, yend=seasonThreshold), linetype="11", data=data.frame(), size=.375) + 
-      geom_point(data=tollandObs, aes(x=time, y=rsv.cum.frac), size=0.5) +
-      geom_point(data=tollandOnsetMini, aes(x=onset, y=seasonThreshold), size=0.75, shape=17) + 
-      geom_segment(data=tollandOnsetMini, aes(x=onset, xend=onset, y=seasonThreshold, yend=0), linetype="11") + 
-      scale_y_continuous(limits=c(0, 2*seasonThreshold)) + 
-      scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, limits=c(zoomedStartWeek, zoomedEndWeek), expand=c(0, 0)) + 
-      theme(
-        panel.grid.major.x=element_blank(),
-        legend.title=element_blank(),
-        axis.title.y=element_blank(),
-        axis.ticks.x=element_blank(),
-        axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
-        legend.position="bottom"
-      )
-
-    dev.off()
-@
-
-\begin{figure}
-\begin{center}
-\begin{subfigure}{.4\textwidth}
-    \begin{center}
-    \input{\figuresDir/tollandPredMini}
-    \caption{Five randomly sampled $P$-splines approximating the RSV time series.}
-    \label{fig:tollandPredMini}
-    \end{center}
-\end{subfigure}
-\begin{subfigure}{.4\textwidth}
-    \begin{center}
-    \input{\figuresDir/tollandOnsetMini}
-    \caption{Season onsets derived from five randomly sampled approximating splines.}
-    \label{fig:tollandOnsetMini}
-    \end{center}
-\end{subfigure}
-\end{center}
-\caption{Cumulative relative incidence of RSV-associated hospitalizations in Tolland county, Connecticut, with five randomly sampled approximating $P$-splines.}
-\end{figure}
-
-We begin the process by defining season onset to occur when cumulative incidence rises above \Sexpr{seasonThreshold * 100}\% of total cases, and obtaining a $P$-spline approximation to our data (using the \texttt{mgcv} R package).
-This approximation is characterized by a matrix of coefficients, each of which is normally distributed with a known mean and variance.
-
-We randomly sample each coefficient from its distribution, thereby obtaining a specific spline that smoothly approximates our data.
-Five such randomly sampled splines are shown in Figure \ref{fig:tollandPredMini}.
-We then calculate RSV season onset for each sampled spline (Figure \ref{fig:tollandOnsetMini}).
-
-Repeating this process many times (\Sexpr{simulations}, in our main analysis) then allows us to estimate the distribution of RSV season onset and therefore make interval estimates.
-In the case of Tolland county, the result of such season onset sampling is shown in Figure \ref{fig:tollandOnsetFull}.
-
-<<tollandOnsetFull, results='hide', warning=FALSE>>=
-    tikz(sprintf("%s/tollandOnsetFull.tex", figuresDir), width=pagePlotWidth * 0.4, height=pagePlotHeight, pointsize=10)
-
-    data = tollandPredFull
-    splineData = data %>% filter(sim < tollandDisplayNsim)
-
-    ggplot(data) +
-      theme_light(base_size=plotTextBaseSize) +
-      geom_line(data=splineData, aes(x=time, y=rsv.cum.frac, group=sim), color="gray") +
-      geom_segment(aes(x=-Inf, y=seasonThreshold, xend=+Inf, yend=seasonThreshold), linetype="11", data=data.frame(), size=.375) + 
-      geom_point(data=tollandObs, aes(x=time, y=rsv.cum.frac), size=0.5) +
-      geom_violinh(
-        data=tollandOnsetFull,
-        aes(x=onset, y=seasonThreshold),
-        width=.01,
-        fill="gray50", color="black",
-        trim=FALSE, draw_quantiles=c(0.025, 0.5, 0.975)
-      ) +
-      scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, expand=c(0, 0)) +
-      scale_y_continuous() +
-      coord_cartesian(xlim=c(zoomedStartWeek, zoomedEndWeek), ylim=c(0, 4*seasonThreshold)) +
-      theme(
-        panel.grid.major.x=element_blank(),
-        legend.title=element_blank(),
-        axis.title.y=element_blank(),
-        axis.ticks.x=element_blank(),
-        axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
-        legend.position="bottom"
-      )
-
-      dev.off()
-@
-
-\begin{figure}
-\begin{center}
-\input{\figuresDir/tollandOnsetFull}
-\caption{Distribution of approximating $P$-splines ($N=\Sexpr{tollandDisplayNsim}$) and season onset ($N=\Sexpr{tollandNsimFull}$), for cumulative relative incidence of RSV-associated hospitalizations in Tolland county, Connecticut.}
-\label{fig:tollandOnsetFull}
-\end{center}
-\end{figure}
-
-We use the same process to estimate RSV season offset; the process can be generalized to any scalar outcome measure of an infectious disease outbreak or season.
-
-Furthermore, because our approach involves sampling approximations to the observed time series as a whole, rather than estimating the time series at isolated points in time, we are able to produce interval estimates of arbitrarily complex outcome measures.
-
-We take advantage of this in our estimation of the preventable fraction of RSV cases.
-Here we begin by defining a preventable case of RSV to be a case of RSV that occurs while prophylaxis offers protection, and we define the preventable fraction of a prophylaxis administration strategy to be the ratio of preventable cases under that prophylaxis strategy to the total cases of RSV.
-
-As before, we then sample $P$-spline coefficients to obtain a specific $P$-spline approximation, and compute preventable fraction for each sampled $P$-spline in order to obtain the distribution of preventable fractions.
-
-<<tollandPredSingle, results='hide', warning=FALSE>>=
-    tikz(sprintf("%s/tollandPredSingle.tex", figuresDir), width=0.8*pagePlotWidth, height=2*pagePlotHeight, pointsize=10)
-
-    data = tollandPredSingle
-
-    thresholds = data %>%
-    	mutate(ppx=strat(time)) %>%
-    	filter(ppx > 0) %>%
-    	do((function(df) {
-    	  df = df %>% arrange(time)
-    		data.frame(
-    			ppx.start=min(df$time),
-    			ppx.end=max(df$time),
-    			unprotected.start=first(df$rsv.cum.frac),
-    			unprotected.end=last(df$rsv.cum.frac)
-    		)
-    	})(.)) %>%
-    	ungroup() %>%
-    	as.data.frame()
-
-    ggplot(data) +
-      theme_light(base_size=plotTextBaseSize) +
-      geom_line(aes(x=time, y=rsv.cum.frac, group=sim), color="grey") +
-      geom_segment(data=thresholds, aes(x=ppx.start, y=unprotected.start, xend=ppx.start, yend=+Inf), linetype="11", size=.375) + 
-      geom_segment(data=thresholds, aes(x=ppx.end, y=unprotected.end, xend=ppx.end, yend=+Inf), linetype="11", size=.375) + 
-      geom_segment(data=thresholds, aes(x=ppx.start, y=unprotected.start, xend=+Inf, yend=unprotected.start), linetype="11", size=.375) + 
-      geom_segment(data=thresholds, aes(x=ppx.end, y=unprotected.end, xend=+Inf, yend=unprotected.end), linetype="11", size=.375) + 
-      geom_point(data=tollandObs, aes(x=time, y=rsv.cum.frac, size=0.5), size=0.5) +
-    	geom_rect(data=thresholds, aes(xmin=ppx.start, xmax=ppx.end, ymin=1, ymax=1.1), size=.375) + 
-    	geom_text(data=thresholds, aes(x=mean(c(ppx.start, ppx.end)), y=1.05, label="Prophylaxis window"), color="white", size=3.5) + 
-    	geom_rect(data=thresholds, aes(xmin=max(monthBoundaries$max) - 3, xmax=max(monthBoundaries$max), ymin=unprotected.start, ymax=unprotected.end), size=.375) + 
-    	geom_text(data=thresholds, aes(x=max(monthBoundaries$max) - 1.5, y=mean(c(unprotected.start, unprotected.end)), label="$\\Delta$ = preventable fraction", angle=90, lineheight=0.5), color="white", size=3.5) +
-      scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, limits=range(c(monthBoundaries$min, monthBoundaries$max)), expand=c(0, 0)) + 
-      theme(
-        panel.grid.major.x=element_blank(),
-        legend.title=element_blank(),
-        axis.title.y=element_blank(),
-        axis.ticks.x=element_blank(),
-        axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
-        legend.position="bottom"
-      )
-
-    dev.off()
-@
-
-<<tollandPreventableFractionFull, results='hide', warning=FALSE>>=
-    tikz(sprintf("%s/tollandPreventableFractionFull.tex", figuresDir), width=0.8*pagePlotWidth, height=2*pagePlotHeight, pointsize=10)
-
-    data = tollandPredFull
-    splineData = data %>% filter(sim < tollandDisplayNsim)
-
-    splinePlot = ggplot(data) +
-      theme_light(base_size=plotTextBaseSize) +
-      geom_line(data=splineData, aes(x=time, y=rsv.cum.frac, group=sim), color="gray") +
-      geom_segment(data=thresholds, aes(x=ppx.start, y=-Inf, xend=ppx.start, yend=+Inf), linetype="11", size=.375) + 
-      geom_segment(data=thresholds, aes(x=ppx.end, y=-Inf, xend=ppx.end, yend=+Inf), linetype="11", size=.375) + 
-    	geom_rect(data=thresholds, aes(xmin=ppx.start, xmax=ppx.end, ymin=1, ymax=1.1), size=.375) + 
-    	geom_text(data=thresholds, aes(x=mean(c(ppx.start, ppx.end)), y=1.05, label="Prophylaxis window"), color="white", size=1.75) + 
-      geom_point(data=tollandObs, aes(x=time, y=rsv.cum.frac), size=0.5) +
-      scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, expand=c(0, 0)) +
-      scale_y_continuous() +
-      theme(
-        panel.grid.major.x=element_blank(),
-        legend.title=element_blank(),
-        axis.title.y=element_blank(),
-        axis.ticks.x=element_blank(),
-        axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
-        legend.position="bottom"
-      )
-
-    violinPlot <- ggplot(tollandFractionFull) +
-      theme_light(base_size=plotTextBaseSize) +
-      geom_violin(
-        aes(x=0, y=unprotected),
-        width=.01,
-        fill="gray50", color="black",
-        trim=FALSE, draw_quantiles=c(0.025, 0.5, 0.975)
-      ) +
-      scale_x_continuous() +
-      scale_y_continuous(limits=c(0, 1)) +
-      theme(
-        panel.grid.major.x=element_blank(),
-        legend.title=element_blank(),
-        axis.title.y=element_blank(),
-        axis.ticks.x=element_blank(),
-        axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
-        legend.position="bottom"
-      ) 
-    grid.arrange(splinePlot, violinPlot, layout_matrix=rbind(c(rep(1, 4), 2)))
-
-    dev.off()
-@
-
-\begin{figure}
-    \begin{center}
-    \input{\figuresDir/tollandPredSingle}
-    \caption{A single estimate of the preventable fraction of RSV under the AAP prophylaxis guidelines, derived from a randomly sampled $P$-spline approximating the time series of RSV-associated hospitalizations in Tolland county, Connecticut.}
-    \label{fig:tollandPredMini}
-    \end{center}
-\end{figure}
-\begin{figure}
-    \begin{center}
-    \input{\figuresDir/tollandPreventableFractionFull}
-    \caption{Distribution of approximating $P$-splines ($N=\Sexpr{tollandDisplayNsim}$) and RSV preventable fractions ($N=\Sexpr{tollandNsimFull}$) under the AAP prophylaxis guidelines in Tolland county, Connecticut.}
-    \label{fig:tollandOnsetMini}
-    \end{center}
-\end{figure}
-
-We developed a custom R package for estimation of arbitrary characteristics of infectious disease outbreaks or seasons (as long as they are amenable to generalized additive modeling); the package is available at \href{https://github.com/airbornemint/outbreak-inference}{\nolinkurl{github.com/airbornemint/outbreak-inference}}.
-
-\printbibliography[heading=subbibliography]
-\end{refsection}
-
 \end{appendices}

### 2019-03-11 Paper/Supplement.R

@@ -1,73 +1,0 @@
-# ---- supplement_libraries ----
-library(ggstance)
-library(gridExtra)
-
-# ---- supplement ----
-tollandObs = obsByCounty %>% filter(county=="Tolland")
-tollandModel = gam(rsv ~ s(time, k=20, bs="cp", m=3), family=poisson, data=tollandObs)
-
-randomMVN = function(mu, sig, nsim) {
-  L = mroot(sig)
-  m = ncol(L)
-  t(mu + L %*% matrix(rnorm(m * nsim), m, nsim))
-}
-
-tollandCalcPred = function(tollandParams, tollandNsim) {
-  tollandParams %>%
-    apply(1, function(params) { outbreak.calc.cum(1)(tollandModel, params, modelTime) } ) %>%
-    data.frame() %>%
-    setnames(as.character(seq(1:tollandNsim))) %>%
-    cbind(time=modelTime) %>%
-    melt(c("time")) %>%
-    rename(sim=variable, rsv.cum.frac=value) %>%
-    mutate(sim=as.numeric(sim))  
-}
-
-tollandCalcOnset = function(tollandParams) {
-  tollandParams %>% 
-    apply(1, function(params) { outbreak.calc.thresholds(seasonThreshold, 1-seasonThreshold)(tollandModel, params, modelTime) } ) %>%
-    bind_rows() %>%
-    select(onset)
-}
-
-tollandStrat = ppxFixedStrategies("all")[["aap"]]
-
-tollandCalcFraction = function(tollandPred) {
-  tollandPred %>%
-    mutate(ppx=tollandStrat(time)) %>%
-    filter(ppx > 0) %>%
-    group_by(sim) %>%
-    do((function(df) {
-      df = df %>% arrange(time)
-      data.frame(
-        ppx.start=min(df$time),
-        ppx.end=max(df$time),
-        unprotected.start=first(df$rsv.cum.frac),
-        unprotected.end=last(df$rsv.cum.frac)
-      ) %>% mutate(
-        unprotected=unprotected.end-unprotected.start
-      )
-    })(.)) %>%
-    ungroup() %>%
-    as.data.frame()  
-}
-
-tollandParamsSingle = randomMVN(coef(tollandModel), tollandModel$Vp, 1)
-tollandPredSingle = tollandParamsSingle %>% tollandCalcPred(1)
-tollandFractionSingle = tollandPredSingle %>% tollandCalcFraction()
-
[…]

### 2019-03-11 Paper/RSVOptimization.rnw
Improved figure placement and legend layout

@@
 <<map, results='hide'>>=
-    tikz(sprintf("%s/map.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
+    tikz(sprintf("%s/map.tex", figuresDir), width=1.5*inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
     US.counties = readOGR(dsn="../Maps/cb_2016_us_county_5m",layer="cb_2016_us_county_5m")
@@
 
+\begin{figure}
+\begin{center}
+\input{\figuresDir/map.tex}
+\caption{Subdivision of Connecticut into high-RSV and low-RSV counties}
+\label{fig:map}
+\end{center}
+\end{figure}
+
 For our spatial analysis, we aggregated RSV incidence data between \Sexpr{formatYear(startDate)} and \Sexpr{formatYear(endDate)} into five regions:
@@
 We chose to aggregate low-RSV counties into a single region because our analysis in those counties individually yielded results with low statistical power.
-
-\begin{figure}
-\begin{center}
-\input{\figuresDir/map.tex}
-\caption{Subdivision of Connecticut into high-RSV and low-RSV counties}
-\label{fig:map}
-\end{center}
-\end{figure}
 
@@
 
-\begin{figure}[b]
-\begin{center}
-\input{\figuresDir/coverageByRegionAAPInsight.tex}
-\caption[Regional variation in the relative timing of the RSV season in Connecticut and the AAP-recommended prophylaxis regimen]{Regional variation in the relative timing of the RSV season in Connecticut and the AAP-recommended prophylaxis regimen, showing the gap between season onset and prophylaxis start date, notable particularly in Fairfield county}
-\label{fig:coverageByRegionAAPInsight}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\input{\figuresDir/seasonByRegion.tex}
-\caption{Regional variation in RSV season onset and offset in Connecticut}
-\label{fig:seasonByRegion}
-\end{center}
-\end{figure}
-
 We then compared those regimens to the one recommended by the AAP and to the six spatially adjusted alternatives (with no calendrical rounding) discussed above.
@@
 \begin{center}
-\input{\figuresDir/coverageByRegionAAP.tex}
-\caption[Regional variation in the fraction of RSV hospitalizations occurring while the AAP-recommended RSV prophylaxis is active]{Regional variation in the fraction of RSV hospitalizations occurring while protection by palivizumab --- administered per the AAP guidelines ---  is active}
-\label{fig:coverageByRegionAAP}
+\input{\figuresDir/seasonByRegion.tex}
+\caption{Regional variation in RSV season onset and offset in Connecticut}
+\label{fig:seasonByRegion}
 \end{center}
@@
 \begin{center}
-\input{\figuresDir/coverageByRegionRegimen.tex}
-\caption[Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen]{Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen, showing statewide superiority and regional non-inferiority of spatially adjusted regimens.
-Preventable fraction: the fraction of all RSV-associated hospitalizations occurring while the prophylaxis regimen provides protection}
-\label{fig:coverageByRegionRegimen}
+\input{\figuresDir/coverageByRegionAAP.tex}
+\caption[Regional variation in the fraction of RSV hospitalizations occurring while the AAP-recommended RSV prophylaxis is active]{Regional variation in the fraction of RSV hospitalizations occurring while protection by palivizumab --- administered per the AAP guidelines ---  is active}
+\label{fig:coverageByRegionAAP}
 \end{center}
@@
 
+\begin{figure}[b]
+\begin{center}
+\input{\figuresDir/coverageByRegionAAPInsight.tex}
+\caption[Regional variation in the relative timing of the RSV season in Connecticut and the AAP-recommended prophylaxis regimen]{Regional variation in the relative timing of the RSV season in Connecticut and the AAP-recommended prophylaxis regimen, showing the gap between season onset and prophylaxis start date, notable particularly in Fairfield county}
+\label{fig:coverageByRegionAAPInsight}
+\end{center}
+\end{figure}
+
 \paragraph{Spatially adjusted regimens are superior to the AAP recommendations}
@@
 <<coverageByRegion, results='hide', warning=FALSE>>=
+    GeomErrorbar$draw_key = draw_key_vline_small
+
     tikz(sprintf("%s/coverageByRegionRegimen.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10)
@@
         labs(y="Preventable fraction", color="Prophylaxis regimen") +
-        guides(color=guide_legend(keywidth=3, keyheight=1, ncol=3)) + 
+        guides(color=guide_legend(keywidth=1, keyheight=1.5, ncol=3)) + 
         scale_x_discrete(labels=countyLabels) + 
@@
 @
+
+\begin{figure}
+\begin{center}
+\input{\figuresDir/coverageByRegionRegimen.tex}
+\caption[Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen]{Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen, showing statewide superiority and regional non-inferiority of spatially adjusted regimens.
+Preventable fraction: the fraction of all RSV-associated hospitalizations occurring while the prophylaxis regimen provides protection}
+\label{fig:coverageByRegionRegimen}
+\end{center}
+\end{figure}
 
@@
           breaks=factor(sprintf("%s.%s", levels(data$strat), FALSE), levels=strat.isRepeat.levels),
-          labels=legendLabels(c(as.vector(stratLabels[10]), "_1", "_2", as.vector(stratLabels[1:6]))),
+          labels=legendLabels(c(as.vector(stratLabels[10]), "_1", "_2", as.vector(stratLabels[1:6])), trailing=0),
           values=c(
@@
         labs(x="Calendrical rounding", y="Preventable fraction") +
-        guides(color=guide_legend(keywidth=3, keyheight=1, ncol=3)) + 
         theme(
-            legend.position="bottom"
-        )
+            legend.position="bottom",
+            legend.key=element_rect(fill="white"),
+        ) +
+        guides(color=guide_legend(keywidth=1, keyheight=1.5, ncol=3))
     dev.off()
@@
 Preventable fraction: the fraction of all RSV hospitalizations occurring while the prophylaxis regimen offers protection.
-Hollow plot markers ($\Circle$, $\square$, and $\triangle$) denote a prophylaxis strategy which, as a result of rounding, is identical to another, and therefore does not provide additional insights.}
+Hollow plot markers ($\raisebox{1pt}{\Circle}$, $\square$, and $\triangle$) denote a prophylaxis strategy which, as a result of rounding, is identical to another, and therefore does not provide additional insights.}
 \label{fig:coverageByRoundingRegimen}
@@
         labs(y="Preventable fraction") +
-        guides(color=guide_legend(keywidth=3, keyheight=1, ncol=3)) + 
+        guides(color=guide_legend(keywidth=1, keyheight=1.5, ncol=3)) + 
         scale_x_discrete(labels=countyLabels) + 

### 2019-03-11 Paper/Paper.R

@@ -199,3 +199,14 @@ darkBrown = "#b15928"
 # Counties which we plot (so, not individual low-incidence counties)
 countiesForPlots = thresholdsByCounty$county[!thresholdsByCounty$county %in% lowIncidenceCounties]
 
+# Use this to draw legend indicators that don't take up the entire height of the key
+draw_key_vline_small = function(data, params, size) {
+  segmentsGrob(0.5, 0.125, 0.5, 0.875,
+    gp = gpar(
+      col = alpha(data$colour, data$alpha),
+      lwd = data$size * .pt,
+      lty = data$linetype,
+      lineend = "butt"
+    )
+  )    
+}

### 2019-03-15 Paper/RSVOptimization.rnw
Conclusion

@@
 
+\subsection{Conclusion}
+
+In summary, our analysis reveals the potential for $\sim 1\%$ gain in prevented RSV cases in Connecticut using a two-week (rather than monthly) basis for prophylaxis guidelines.
+Practical merits of this potential gain --- including implementation cost and absolute magnitude of such gains --- require further investigation.
+Additionally, our method can be applied to county-level or state-level analysis of seasonal RSV patterns in other regions --- some of which are likely to show a greater relative benefit than Connecticut (due to a greater degree of misalignment between RSV season and prophylaxis window) as well as a greater absolute benefit (due to population size).
+
 \phantomsection

### 2019-03-15 Paper/RSVOptimization.rnw
Discussion tweaks

@@
 
-\subsection{Conclusions}
+\subsection{Results}
 
@@
 
-Our effort to optimize timing of the prophylaxis regimen (without changing its duration, and therefore its pharmaceutical cost) shows the possibility of a theoretical 1-2\% statewide decrease in RSV-associated hospitalizations among high-risk infants each year, primarily in counties with higher RSV burden (Fairfield, Hartford, and New Haven counties).
-The magnitude of that improvement wanes upon encountering practicalities of clinical practice guideline implementation.
+Our effort to optimize timing of the prophylaxis regimen (without changing its duration, and therefore its pharmaceutical cost) shows a theoretical 1-2\% statewide decrease in RSV-associated hospitalizations among high-risk infants each year, primarily in counties with higher RSV burden (Fairfield, Hartford, and New Haven counties).
+The magnitude of that improvement declines after accounting for practicalities of clinical practice guideline implementation.
 Nonetheless, with clinical practice guidelines localized at the county level, and the timing of prophylaxis adjusted in each county by less than a whole month from the current AAP guidelines, we still found the potential for $\sim$1\% statewide decrease in RSV-associated hospitalizations among high risk infants.
 The prophylaxis regimen with which we were able to attain this improvement is the one in which prophylaxis in each county is timed relative to the midpoint of the RSV season (rounded to two weeks) in that county, which simultaneously reduces unprotected cases early in the season and ineffective prophylaxis late in the season.
-Increasing complexity of practice guidelines carries with it increased cost of implementation, such as training of clinicians and other healthcare workers.
-It is therefore not apparent from our research alone that the potential benefits would outweigh the costs.
+Increasing complexity of practice guidelines would carry with it increased cost of implementation (such as training of clinicians and other healthcare workers); it is therefore not apparent from our research alone that the potential benefits would outweigh the costs.
 

### 2019-03-15 Paper/RSVOptimization.rnw
Todo re citing spatial variability
Missing author list line break
Revised previous research on spatial variability

@@
 \author{
-    \authorstyle{Ben Artin, MEng, MPH, MMSc\textsuperscript{1}}
+    \authorstyle{Ben Artin, MEng, MPH, MMSc\textsuperscript{1}}\\
     \authorstyle{Daniel Weinberger, PhD\textsuperscript{1}}\\
@@
 
-RSV seasonality and spatial variability have been established throughout the United States, based on National Respiratory and Enteric Virus Surveillance System data.
-In all states except for Florida, RSV shows an annual or biennial cycle with a stable seasonal onset between mid-November and early January and a stable seasonal offset between mid-March and late April.\cite{CentersforDiseaseControlandPreventionCDC:2011wt,CentersforDiseaseControlandPreventionCDC:2013wv} RSV season in Florida begins approximately two months earlier than in other states.
-\cite{CentersforDiseaseControlandPreventionCDC:2013wv} The AAP acknowledges the potential significance of spatial and temporal variation in RSV incidence, but --- outside of Florida --- does not recommend local variance from nationwide prophylaxis guidelines.\cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
+% TODO cite DW/VP paper re spatial variability
 
-Previous analysis of RSV-associated hospital admissions in Connecticu has shown regional variability in time of peak RSV incidence within Connecticut.\cite{Noveroske:y4fi3188} No prior research is available regarding year-to-year variation in timing of RSV season in Connecticut.
+RSV seasonality and spatial variability have been established throughout the United States, based on National Respiratory and Enteric Virus Surveillance System data; RSV has been found to have an annual or biennial cycle with regionally variable seasonal onset ranging from late August to mid-December and offset ranging from mid-March to late April.\cite{CentersforDiseaseControlandPreventionCDC:2011wt,CentersforDiseaseControlandPreventionCDC:2013wv,Weinberger:2015hj} The AAP acknowledges the potential significance of spatial and temporal variation in RSV incidence, but --- outside of Florida, whose RSV season leads most of the rest of the nation by approximately two months --- does not recommend local variance from nationwide prophylaxis guidelines.\cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
+
+Previous analysis of RSV-associated hospital admissions has shown regional variability in time of peak RSV incidence within Connecticut.\cite{Noveroske:y4fi3188} No prior research is available regarding year-to-year variation in timing of RSV season in Connecticut.
 

### 2019-03-15 Paper/RSVOptimization.rnw
Conclusion tweaks

@@
 Practical merits of this potential gain --- including implementation cost and absolute magnitude of such gains --- require further investigation.
-Additionally, our method can be applied to county-level or state-level analysis of seasonal RSV patterns in other regions --- some of which are likely to show a greater relative benefit than Connecticut (due to a greater degree of misalignment between RSV season and prophylaxis window) as well as a greater absolute benefit (due to population size).
+Additionally, the method we developed for this analysis can be applied to county-level or state-level analysis of seasonal RSV patterns in other regions, some of which are likely to show a greater relative benefit than Connecticut (due to a greater degree of misalignment between RSV season and prophylaxis window) as well as a greater absolute benefit (due to population size).
 

### 2019-03-15 Paper/RSVOptimization.rnw
Heading tweaks

@@
 
-\paragraph{Spatially adjusted regimens are superior to the AAP recommendations}
+\paragraph{Without calendarical rounding, spatially adjusted regimens are superior to the AAP recommendations}
 
@@
 
-\paragraph{Calendrical rounding rapidly erases gains over the AAP-recommended regimen}
+\paragraph{Calendrical rounding rapidly diminishes gains over the AAP-recommended regimen}
 

### 2019-03-26 Paper/RSVOptimization.rnw
Don’t need this Sweave nonsense

@@
 
-<<options, echo=FALSE>>=
-    knitr::opts_chunk$set(echo=FALSE, message=FALSE, error=FALSE)
-@
-
-<<load>>=
-knitr::read_chunk("../Analysis/RSV.R")
-knitr::read_chunk("../Paper/Paper.R")
-@
-
-<<libraries, cache=FALSE>>=
-@
-
-<<external, cache=TRUE>>=
-@
-
-<<paper, warning=FALSE>>=
+<<knitr, child='Paper.Rnw'>>=
 @
@@
 \begin{document}
-% \SweaveOpts{concordance=TRUE}
 
@@
 
-<<map, results='hide'>>=
-    tikz(sprintf("%s/map.tex", figuresDir), width=1.5*inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
-    US.counties = readOGR(dsn="../Maps/cb_2016_us_county_5m",layer="cb_2016_us_county_5m")
-    US.counties = US.counties[US.counties$STATEFP == "09",]
-    county.data = US.counties@data %>%
-        mutate(id=rownames(.)) %>%
-        data.table() %>%
-        mutate(highRSV=ifelse(NAME %in% lowIncidenceCounties, FALSE, TRUE))
-
-    map.df = US.counties %>% 
-        fortify() %>% 
-        data.table() %>%
-        inner_join(county.data %>% select(highRSV, id), by="id")
-
-    county.data = map.df %>%
-        group_by(id) %>%
-        summarize(lat=mean(range(lat)), long=mean(range(long))) %>%
-        ungroup() %>%
-        inner_join(county.data, by="id") %>%
-        rename(name=NAME)
-
-    ggplot(map.df, aes(x=long, y=lat)) +
-        theme_light(base_size=plotTextBaseSize) +
-        scale_fill_manual(labels=legendLabels(c("$<$50", "$>$100")), values=c(lightBlue, darkBlue)) +
-        geom_polygon(aes(fill=highRSV, group=group), color="white", size=.5) +
-        geom_text(data=county.data, aes(label=name), size=2.2) +
-        coord_map() + 
-        labs(fill="Average RSV-associated hospitalizations per year") +
-        theme(
-            rect=element_blank(),
-            line=element_blank(),
-            axis.text=element_blank(),
-            axis.title=element_blank(),
-            legend.position="bottom"
-        )
-    dev.off()
-@
-
 \begin{figure}
@@
 
-<<seasonByRegion, results='hide'>>=
-    tikz(sprintf("%s/seasonByRegion.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
-    data = thresholdsByCounty %>% 
-        filter(county %in% countiesForPlots) %>%
-        melt(id=c("county")) %>%
-        cSplit(c("variable"), c(".")) %>%
-        rename(variable=variable_1, pctile=variable_2) %>%
-        mutate(variable=factor(variable, levels=c("offset", "onset"))) %>%
-        cast(county + variable ~ pctile)
-
-    onsetOffsetRange = 6 # weeks
-    onsetOffsetAdjust = data.frame(variable=c("onset", "offset"), nudge=c(-1, -2))
-
-    limits = data %>% 
-        select(variable, median) %>%
-        group_by(variable) %>%
-        summarize(mid=round(mean(range(median)))) %>%
-        inner_join(onsetOffsetAdjust, by="variable") %>%
-        mutate(mid=mid + nudge, min=mid - onsetOffsetRange / 2, max=mid + onsetOffsetRange / 2)
-
-    monthBarX = 0.5 + (0.5 - 5.5) * 0.04
-    monthGrob = function(month) {
-        textGrob(epiWeekLabels[month], just="right", gp=gpar(fontsize="6.4", col="grey30"))
-    }
-
-    plot = ggplot(data) +
-        theme_light(base_size=plotTextBaseSize) +
-        geom_errorbar(aes(ymin=lower, ymax=upper, x=county), width=.1) + 
-        geom_point(aes(y=median, x=county), size=.75) + 
-        geom_blank(data=limits, aes(y=min)) + 
-        geom_blank(data=limits, aes(y=max)) + 
-        labs(aes(x=variable)) +
-        facet_wrap(~variable, ncol=1, scales="free_y", labeller=onsetOffsetLabeller) +
-        scale_x_discrete(labels=countyLabels) + 
-        scale_y_continuous(minor_breaks=seq(1, 52), breaks=epiWeekBreaks, labels=rep("\\qquad\\qquad", length(epiWeekBreaks)), sec.axis=sec_axis(trans=~., breaks=seq(1, 52))) + 
-        labs(y=NULL) + 
-        annotation_custom(monthGrob(4), xmin=monthBarX, xmax=monthBarX, ymin=monthBoundaries$mid[4], ymax=monthBoundaries$mid[4]) + 
-        annotation_custom(monthGrob(5), xmin=monthBarX, xmax=monthBarX, ymin=monthBoundaries$mid[5], ymax=monthBoundaries$mid[5]) + 
-        annotation_custom(monthGrob(9), xmin=monthBarX, xmax=monthBarX, ymin=monthBoundaries$mid[9], ymax=monthBoundaries$mid[9]) + 
-        annotation_custom(monthGrob(10), xmin=monthBarX, xmax=monthBarX, ymin=monthBoundaries$mid[10], ymax=monthBoundaries$mid[10]) + 
-        theme(
-            panel.grid.major.y=element_blank(),
-            panel.grid.minor.y=element_line(size=rel(2)),
-            axis.title.x=element_blank(),
-            axis.ticks.x=element_blank(),
-            axis.text.x=element_text(angle=30, hjust=1)
-        )
-
-	plotGrob = ggplotGrob(plot)
-	plotGrob$layout$clip[grepl("panel", plotGrob$layout$name)] <- "off"
-	grid.draw(plotGrob)
-
-    dev.off()
-@
-
 \begin{figure}
@@
 \paragraph{The AAP guidelines perform best in low-RSV counties and worst in Fairfield county}
-
-<<coverageByRegionAAP, results='hide'>>=
-    tikz(sprintf("%s/coverageByRegionAAP.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
-
-    data = unprotectedByCounty %>% 
-        filter(strat=="aap", rounding==0) %>% 
-        filter(county %in% countiesForPlots)
-
-    ggplot(data) +
-        theme_light(base_size=plotTextBaseSize) +
-        geom_errorbar(aes(ymax=frac.upper, ymin=frac.lower, x=county), width=.1) + 
-        geom_point(aes(y=frac.median, x=county), size=.75) + 
-        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
-        scale_x_discrete(labels=countyLabels) + 
-        labs(y="Preventable fraction") +
-        theme(
-            axis.title.x=element_blank(),
-            axis.ticks.x=element_blank(),
-            axis.text.x=element_text(angle=30, hjust=1)
-        )
-    dev.off()
-@
-
-<<coverageByRegionAAPInsight, results='hide'>>=
-    tikz(sprintf("%s/coverageByRegionAAPInsight.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight, pointsize=10)
-
-    strat = ppxFixedStrategies("all")[["aap"]]
-
-    data = predByCounty %>%
-	    filter(county %in% countiesForPlots)
-
-    thresholds = data %>%
-    	mutate(ppx=strat(time)) %>%
-    	filter(ppx > 0) %>%
-    	group_by(county) %>%
-    	do(
-    		data.frame(
-    			ppx.start=min(.$time),
-    			ppx.end=max(.$time),
-    			unprotected.start=min(.$rsv.cum.fit),
-    			unprotected.end=max(.$rsv.cum.fit)
-    		)
-    	) %>%
-    	ungroup() %>%
-    	as.data.frame() %>%
-    	inner_join(thresholdsByCounty, by="county")
-
-    barYmin = 0.025
-    barYmax = 0.075
-
-    spanExtents = data.frame(
-        variable=c("ppx", "season"), 
-        barYmin=c(1 + barYmin, -barYmax), 
-        barYmax=c(1 + barYmax, -barYmin), 
-        lineYmin=c(0, -barYmin), 
-        lineYmax=c(1 + barYmin, 1)
-    )
-
-    spans = thresholds %>%
-        select(county, matches("ppx."), matches(".median")) %>%
-        rename(season.start=onset.median, season.end=offset.median) %>%
-        melt(id.vars="county") %>%
-        cSplit("variable", ".") %>%
-        rename(variable=variable_1, part=variable_2) %>%
-        cast(county + variable ~ part) %>%
-        right_join(spanExtents, by="variable")
-
-    spanLabels = legendLabels(c("AAP-recommended prophylaxis", "RSV season"), leading=1)
-
-    ggplot(data) +
-        theme_light(base_size=plotTextBaseSize) +
-        geom_ribbon(aes(ymin=rsv.cum.fit.lower, ymax=rsv.cum.fit.upper, x=time), fill=grey(.25)) +
-    	geom_segment(aes(x=start, y=lineYmin, xend=start, yend=lineYmax, color=variable), data=spans, size=.375) + 
-    	geom_segment(aes(x=end, y=lineYmin, xend=end, yend=lineYmax, color=variable), data=spans, size=.375) + 
-    	geom_rect(aes(xmin=start, ymin=barYmin, xmax=end, ymax=barYmax, fill=variable, color=variable), data=spans, size=.375) + 
-    	geom_segment(aes(x=-Inf, y=unprotected.start, xend=ppx.start, yend=unprotected.start), linetype="11", data=thresholds, size=.375) + 
-        geom_segment(aes(x=-Inf, y=unprotected.end, xend=ppx.end, yend=unprotected.end), linetype="11", data=thresholds, size=.375) + 
-        geom_point(aes(x=min(monthBoundaries$min), y=unprotected.end), data=thresholds, shape=18) + 
-        geom_point(aes(x=min(monthBoundaries$min), y=unprotected.start), data=thresholds, shape=18) + 
-        scale_y_continuous(labels=latexPercent, breaks=seq(0, 1, by=.2), limits=c(-0.1, 1.1), expand=c(0, 0)) +
-        scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, limits=range(c(monthBoundaries$min, monthBoundaries$max)), expand=c(0, 0)) + 
-        scale_color_manual(labels=spanLabels, values=c(darkPurple, darkRed)) +
-        scale_fill_manual(labels=spanLabels, values=c(darkPurple, darkRed)) +
-        guides(color=guide_legend(keywidth=3, keyheight=.4)) + 
-        facet_wrap(~county, ncol=5, labeller=labeller(county=countyLabels)) +
-        labs(x=NULL, y="Cumulative indicence fraction") + 
-        theme(
-            panel.grid.major.x=element_blank(),
-            legend.title=element_blank(),
-            axis.title.y=element_blank(),
-            axis.ticks.x=element_blank(),
-            axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
-            legend.position="bottom"
-        )
-
-    dev.off()
-@
 
@@
 
-<<coverageByRegion, results='hide', warning=FALSE>>=
-    GeomErrorbar$draw_key = draw_key_vline_small
-
-    tikz(sprintf("%s/coverageByRegionRegimen.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10)
-    data = unprotectedByCounty %>% 
-        filter(county %in% countiesForPlots, rounding==0, sliding==FALSE) %>%
-        mutate(strat=factor(strat, levels=c(levels(strat)[1], "_1", "_2", levels(strat)[2:7])))
-
-    ggplot(data) +
-        theme_light(base_size=plotTextBaseSize) +
-        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
-        scale_color_manual(
-          name="Prophylaxis regimen", 
-          labels=legendLabels(c(as.vector(stratLabels[10]), "_1", "_2", as.vector(stratLabels[1:6]))),
-          values=c(
-            darkPurple, 
-            NA, NA, 
-            rep(c(darkBrown, darkOrange), each=3), darkPurple
-          ), 
-          drop=FALSE
-        ) + 
-        scale_shape_manual(
-          name="Prophylaxis regimen", 
-          labels=legendLabels(c(as.vector(stratLabels[10]), "_1", "_2", as.vector(stratLabels[1:6]))),
-          values=c(
-            16, 
-            16, 16, 
-            16, 15, 17, 
-            16, 15, 17
-          ), 
-          drop=FALSE
-        ) + 
-        geom_errorbar(
-            aes(ymin=frac.lower, ymax=frac.upper, x=county, color=strat, group=strat), 
-            width=.3, 
-            position=position_dodge(.5)
-        ) + 
-        geom_point(aes(y=frac.median, x=county, color=strat, shape=strat), position=position_dodge(.5), size=.75) +
-        labs(y="Preventable fraction", color="Prophylaxis regimen") +
-        guides(color=guide_legend(keywidth=1, keyheight=1.5, ncol=3)) + 
-        scale_x_discrete(labels=countyLabels) + 
-        theme(
-            axis.title.x=element_blank(),
-            axis.ticks.x=element_blank(),
-            legend.position="bottom"
-        )
-    dev.off()
-@
-
 \begin{figure}
@@
 \paragraph{Calendrical rounding rapidly diminishes gains over the AAP-recommended regimen}
-
-<<calendarForRounding, results='hide', warning=FALSE>>=
-    tikz(sprintf("%s/calendarForRoundingRegimen.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10)
-
-    roundingStrat = unprotectedByCounty %>% 
-        filter(county %in% countiesForPlots, sliding==FALSE) %>%
-        select(strat, rounding) %>%
-        unique()
-
-    dataAll = predByCounty %>%
-        filter(county %in% countiesForPlots) %>%
-        group_by(county, time) %>%
-        do(
-            roundingStrat
-        ) %>%
-        ungroup() %>%
-        group_by(county, strat, rounding) %>%
-        do(
-            (function(df) {
-                county = unique(df$county)
-                rounding = as.numeric(unique(df$rounding))
-                strat = as.character(unique(df$strat))
-                strat = ppxFixedStrategies(county, rounding)[[strat]]
-                stratActive = strat(df$time)
-                df %>%
-                    mutate(stratActive=stratActive)
-            })(.)
-        ) %>%
-        ungroup() %>%
-        filter(stratActive > 0) %>%
-        group_by(county, strat, rounding) %>%
-        summarize(start=min(time), end=max(time)) %>%
-        ungroup()
-
-    aapStartEnd = dataAll %>%
-        filter(strat == "aap") %>%
-        select(start, end) %>%
-        unique()
-
-    aap = dataAll %>%
-        filter(strat != "aap") %>%
-        group_by(strat, rounding) %>%
-        do(
-            aapStartEnd
-        ) %>%
-        ungroup() %>%
-        mutate(y=ifelse(grepl("state", strat), "all", "lowIncidence")) %>%
-        mutate(y=factor(y, levels(dataAll$county)))
-
-    data = dataAll %>% 
-        filter(strat != "aap") %>%
-        filter(xor(grepl("county", strat), county == "all"))
-
-    ggplot(data) +
-        theme_light(base_size=plotTextBaseSize) +
-    	geom_rect(aes(xmin=start, xmax=end, ymin=as.numeric(county)-0.25, ymax=as.numeric(county)+0.25), size=.375) + 
-    	geom_rect(data=aap, aes(xmin=start, xmax=end, ymin=as.numeric(y)+0.75, ymax=as.numeric(y)+1.25), size=.375) + 
-        scale_y_continuous(breaks=as.numeric(countiesForPlots), labels=countyLabels[as.character(countiesForPlots)]) + 
-        scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, limits=range(c(monthBoundaries$min, monthBoundaries$max)), expand=c(0, 0)) + 
-#        scale_color_manual(labels=spanLabels, values=twoToneAlt) +
-#        scale_fill_manual(labels=spanLabels, values=twoToneAlt)# +
-#        guides(color=guide_legend(keywidth=3, keyheight=.4)) + 
-        facet_wrap(~ rounding + strat, nrow=8, labeller=labeller(rounding=roundingLabels, strat=stratLabels), scales="free_y") #+
-#        labs(x=NULL, y="Cumulative indicence fraction") + 
-#        theme(
-#            panel.grid.major.x=element_blank(),
-#            legend.title=element_blank(),
-#            axis.title.y=element_blank(),
-#            axis.ticks.x=element_blank(),
-#            axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
-#            legend.position="bottom"
-#        )
-    dev.off()
-@
-
-<<coverageByRounding, results='hide', warning=FALSE>>=
-    tikz(sprintf("%s/coverageByRoundingRegimen.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10)
-
-    # We are going to de-emphasize some data points, because sometimes different strategies under different rounding end up producing the same prophylaxis schedule, and there is no point in showing all of them equally on the plot.
-To do this, we consider the left-to-right order in which strategies will appear in the plot, and then de-emphasize any strategy whose schedule is the same as some strategy that appears on its left
-    data = unprotectedByCounty %>% 
-        filter(county == "all", sliding==FALSE) %>%
-        arrange(rounding, strat) %>%
-        mutate(strat=factor(strat, levels=c(levels(strat)[1], "_1", "_2", levels(strat)[2:7])))
-
-    data$startIdx = match(data$desc, data$desc)
-    data$isRepeat = data$startIdx != seq(1, length(data$startIdx))
-    data$isRepeat = data$isRepeat & !data$strat == "aap" 
-    data$strat.isRepeat = sprintf("%s.%s", data$strat, data$isRepeat)
-    idx = order(rep(seq(1, length(levels(data$strat))), 2))
-    strat.isRepeat.levels = (c(
-      sprintf("%s.%s", levels(data$strat), FALSE), 
-      sprintf("%s.%s", levels(data$strat), TRUE)
-    ))[idx]
-    data$strat.isRepeat = factor(data$strat.isRepeat, strat.isRepeat.levels)
-
-    ggplot(data) +
-        theme_light(base_size=plotTextBaseSize) +
-        scale_y_continuous(labels=latexPercent, limits=c(0.90, 1.00), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
-        scale_alpha_manual(guide=FALSE, breaks=c(FALSE, TRUE), values=c(1, 0.5)) + 
-        scale_color_manual(
-          name="Prophylaxis regimen", 
-          breaks=factor(sprintf("%s.%s", levels(data$strat), FALSE), levels=strat.isRepeat.levels),
-          labels=legendLabels(c(as.vector(stratLabels[10]), "_1", "_2", as.vector(stratLabels[1:6])), trailing=0),
-          values=c(
-            darkPurple, darkPurple, 
-            NA, NA, NA, NA, 
-            rep(c(darkBrown, darkOrange), each=6)
-          ), 
-          drop=FALSE
-        ) + 
-        scale_shape_manual(
-          name="Prophylaxis regimen", 
-          breaks=factor(sprintf("%s.%s", levels(data$strat), FALSE), levels=strat.isRepeat.levels),
-          labels=legendLabels(c(as.vector(stratLabels[10]), "_1", "_2", as.vector(stratLabels[1:6])), trailing=0),
-          values=c(
-            16, 16, 
-            16, 16, 16, 16, 
-            16, 21, 15, 22, 17, 24, 
-            16, 21, 15, 22, 17, 24
-          ), 
-          drop=FALSE
-        ) + 
-        scale_x_discrete(labels=roundingLabels) + 
-        geom_errorbar(
-            aes(ymin=frac.lower, ymax=frac.upper, x=rounding, color=strat.isRepeat, group=strat.isRepeat), 
-            width=.25, 
-            position=position_dodge(.5)
-        ) + 
-        geom_point(aes(y=frac.median, x=rounding, color=strat.isRepeat, shape=strat.isRepeat), position=position_dodge(.5), size=0.75, fill="white") +
-        labs(x="Calendrical rounding", y="Preventable fraction") +
-        theme(
-            legend.position="bottom",
-            legend.key=element_rect(fill="white"),
-        ) +
-        guides(color=guide_legend(keywidth=1, keyheight=1.5, ncol=3))
-    dev.off()
-@
 
@@
 \paragraph{Temporally-adjusted prophylaxis regimens are non-superior to others}
-
-<<coverageByRegionWithSliding, results='hide', warning=FALSE>>=
-    tikz(sprintf("%s/coverageByRegionRegimenWithSliding.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10)
-    data = unprotectedByCounty %>% 
-        filter(county %in% countiesForPlots, rounding==0, !grepl("county", strat)) %>%
-        mutate(strat=factor(strat, levels=c(levels(strat)[1], "_1", "_2", levels(strat)[2:4], levels(strat)[8:10])))
-
-    ggplot(data) +
-        theme_light(base_size=plotTextBaseSize) +
-        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
-        scale_color_manual(
-          name="Prophylaxis regimen", 
-          labels=legendLabels(c(as.vector(stratLabels[10]), "_1", "_2", as.vector(stratLabels[1:3]), as.vector(stratLabels[7:9]))),
-          values=c(
-            darkPurple, 
-            NA, NA, 
-            rep(c(darkBrown, darkGreen), each=3), darkPurple
-          ), 
-          drop=FALSE
-        ) + 
-        scale_shape_manual(
-          name="Prophylaxis regimen", 
-          labels=legendLabels(c(as.vector(stratLabels[10]), "_1", "_2", as.vector(stratLabels[1:3]), as.vector(stratLabels[7:9]))),
-          values=c(
-            16, 
-            16, 16, 
-            16, 15, 17, 
-            16, 15, 17
-          ), 
-          drop=FALSE
-        ) + 
-        geom_errorbar(
-            aes(ymin=frac.lower, ymax=frac.upper, x=county, color=strat, group=strat), 
-            width=.3, 
-            position=position_dodge(.5)
-        ) + 
-        geom_point(aes(y=frac.median, x=county, color=strat, shape=strat), position=position_dodge(.5), size=.75) +
-        labs(y="Preventable fraction") +
-        guides(color=guide_legend(keywidth=1, keyheight=1.5, ncol=3)) + 
-        scale_x_discrete(labels=countyLabels) + 
-        theme(
-            axis.title.x=element_blank(),
-            axis.ticks.x=element_blank(),
-            legend.position="bottom"
-        )
-    dev.off()
-@
 
@@
 
-<<onsetOffsetByYear, results='hide', warning=FALSE>>=
-    tikz(sprintf("%s/onsetOffsetByYear.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
-    data = stateThresholdsByWindow %>% 
-        melt(id=c("epiyear")) %>%
-        cSplit(c("variable"), c(".")) %>%
-        rename(variable=variable_1, pctile=variable_2) %>%
-        mutate(variable=factor(variable, levels=c("offset", "onset"))) %>%
-        cast(epiyear + variable ~ pctile)
-
-    onsetOffsetAdjust = data.frame(variable=c("onset", "offset"), nudge=c(0, -1))
-
-    limits = data %>% 
-        select(variable, median) %>%
-        group_by(variable) %>%
-        summarize(mid=round(mean(range(median)))) %>%
-        inner_join(onsetOffsetAdjust, by="variable") %>%
-        mutate(mid=mid + nudge) %>%
-        mutate(min=mid - onsetOffsetRange / 2, max=mid + onsetOffsetRange / 2)
-
-    monthBarX = 1998.5 + (1998.5 - 2013.5) * 0.04
-
-    plot = ggplot(data) +
-        theme_light(base_size=plotTextBaseSize) +
-        geom_errorbar(aes(ymin=lower, ymax=upper, x=epiyear), width=.3) + 
-        geom_point(aes(y=median, x=epiyear), size=.75) +
-        geom_blank(data=limits, aes(y=min)) + 
-        geom_blank(data=limits, aes(y=max)) + 
-        facet_wrap(~variable, ncol=1, scales="free_y", labeller=onsetOffsetLabeller) +
-        scale_x_continuous(breaks=seq(1990, 2020, by=5)) +
-        scale_y_continuous(minor_breaks=seq(1, 52), breaks=epiWeekBreaks, labels=rep("\\qquad\\qquad", length(epiWeekBreaks)), sec.axis=sec_axis(trans=~., breaks=seq(1, 52))) + 
-        annotation_custom(monthGrob(4), xmin=monthBarX, xmax=monthBarX, ymin=monthBoundaries$mid[4], ymax=monthBoundaries$mid[4]) + 
-        annotation_custom(monthGrob(5), xmin=monthBarX, xmax=monthBarX, ymin=monthBoundaries$mid[5], ymax=monthBoundaries$mid[5]) + 
-        annotation_custom(monthGrob(9), xmin=monthBarX, xmax=monthBarX, ymin=monthBoundaries$mid[9], ymax=monthBoundaries$mid[9]) + 
-        annotation_custom(monthGrob(10), xmin=monthBarX, xmax=monthBarX, ymin=monthBoundaries$mid[10], ymax=monthBoundaries$mid[10]) + 
-        labs(y=NULL) + 
-        theme(
-            panel.grid.major.y=element_blank(),
-            panel.grid.minor.y=element_line(size=rel(2)),
-            axis.title.x=element_blank()
-        )
-
-	plotGrob = ggplotGrob(plot)
-	plotGrob$layout$clip[grepl("panel", plotGrob$layout$name)] <- "off"
-	grid.draw(plotGrob)
-
-    dev.off()
-@
-
 \begin{figure}

### 2019-03-26 Paper/RSVOptimization.rnw
Feedback from Dan

@@
 
+% TODO "regional" -> county level
+% TODO is rounded to weeks primary analysis?
+% TODO DPH acknowledgement
+
 \thispagestyle{firstpage}
@@
 
-\abstractsection{Background}Respiratory syncytial virus (RSV) causes seasonal respiratory infection with potentially serious complications in children, and leads to hospitalization rates of up to 50\% in high-risk infants.
+\abstractsection{Background}Respiratory syncytial virus (RSV) causes seasonal respiratory infection with potentially serious complications in children and leads to hospitalization rates of up to 50\% in high-risk infants.
 Safe and effective immunoprophylaxis (palivizumab) is available, but costly.
@@
 \abstractsection{Results}Using preventable fraction to assess different immunoprophylaxis regimens, we found that regimens adjusted for county-level variation in timing of RSV seasons are superior to the current AAP-recommended regimen.
-We also considered the effect of rounding the timing of the first dose of prophylaxis to pragmatic calendrical boundaries (weekly, biweekly, and monthly), and found that benefits of alternative regimens over the AAP-recommended regimen persisted with biweekly rounding, but not with monthly rounding.
+We also considered the effect of rounding the recommended start date of prophylaxis by week, biweekly period, or month and found that benefits of alternative regimens over the AAP-recommended regimen persisted with biweekly rounding, but not with monthly rounding.
 Our best-performing pragmatic alternative to the AAP guidelines was based on the regional RSV season midpoint with biweekly rounding.
@@
 
-\subsection{Respiratory syncytial virus}
-
 Respiratory syncytial virus (RSV) causes upper respiratory infections in humans of all ages.
@@
 
-Since 1998, a monoclonal antibody (palivizumab), has been approved in the US for prevention of RSV infection in high-risk infants less than 2 years old.
-Palivizumab is administered via intramuscular injection and requires five monthly doses, priced at \$1500-\$3000 per dose.\cite{Hampp:2011ju,Andabaka:2013dr} Palivizumab has been found to be effective in reducing hospitalizations due to RSV; in double-blinded trials in high-risk infants, it reduced the hospitalization rate by 45-55\% compared to placebo.\cite{Group:1998ih,Feltes:2003wm} It has also been found to be safe and well-tolerated in clinical trials.\cite{Group:1998ih} Owing to the high cost, the 2014 revision of the American Academy of Pediatrics (AAP) RSV prophylaxis guidelines, recommends palivizumab only for high-risk infants, and only during the RSV season.\cite{Anonymous:1998up,AmericanAcademyofPediatricsCommitteeonInfectiousDiseasesandCommitteeonFetusandNewborn:2003ug,AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
+A monoclonal antibody (palivizumab) is available in the US for prevention of RSV infection in high-risk infants less than 2 years old.
+Palivizumab is administered via intramuscular injection and requires five monthly doses, priced at \$1500-\$3000 per dose.\cite{Hampp:2011ju,Andabaka:2013dr} Palivizumab has been found to be effective in reducing hospitalizations due to RSV; in double-blinded trials in high-risk infants, it reduced the hospitalization rate by 45-55\% compared to placebo.\cite{Group:1998ih,Feltes:2003wm} It has also been found to be safe and well-tolerated in clinical trials.\cite{Group:1998ih} Owing to the high cost, the 2014 revision of the American Academy of Pediatrics (AAP) RSV prophylaxis guidelines recommends palivizumab only for high-risk infants and only during the RSV season.\cite{Anonymous:1998up,AmericanAcademyofPediatricsCommitteeonInfectiousDiseasesandCommitteeonFetusandNewborn:2003ug,AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
 
@@
 
-RSV seasonality and spatial variability have been established throughout the United States, based on National Respiratory and Enteric Virus Surveillance System data; RSV has been found to have an annual or biennial cycle with regionally variable seasonal onset ranging from late August to mid-December and offset ranging from mid-March to late April.\cite{CentersforDiseaseControlandPreventionCDC:2011wt,CentersforDiseaseControlandPreventionCDC:2013wv,Weinberger:2015hj} The AAP acknowledges the potential significance of spatial and temporal variation in RSV incidence, but --- outside of Florida, whose RSV season leads most of the rest of the nation by approximately two months --- does not recommend local variance from nationwide prophylaxis guidelines.\cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
+RSV seasonality and spatial variability have been established throughout the United States, based on the CDC's National Respiratory and Enteric Virus Surveillance System data; RSV has been found to have an annual or biennial cycle with regionally variable seasonal onset ranging from late August to mid-December and offset ranging from mid-March to late April.\cite{CentersforDiseaseControlandPreventionCDC:2011wt,CentersforDiseaseControlandPreventionCDC:2013wv,Weinberger:2015hj} The AAP acknowledges the potential significance of spatial and temporal variation in RSV incidence, but --- outside of Florida, whose RSV season leads most of the rest of the nation by approximately two months --- does not recommend local variance from nationwide prophylaxis guidelines.\cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
 
-Previous analysis of RSV-associated hospital admissions has shown regional variability in time of peak RSV incidence within Connecticut.\cite{Noveroske:y4fi3188} No prior research is available regarding year-to-year variation in timing of RSV season in Connecticut.
+Previous analysis of RSV-associated hospital admissions has shown spatial variability in the timing of peak RSV incidence within Connecticut.\cite{Noveroske:y4fi3188} Epidemics tends to occur earlier in large urban areas and later in sparsely-populated rural areas.
 
-\subsection{Study aims}
-
-Motivated by the AAP's recognition of the significance of spatial variation in formulating prophylaxis guidelines, and the known spatial variability of RSV incidence in Connecticut, we aim to determine whether spatial and temporal variability can be used to optimize RSV prophylaxis in Connecticut by
+Motivated by the AAP's recognition of the significance of spatial variation in formulating prophylaxis guidelines and the known spatial variability of RSV incidence in Connecticut, we aim to determine whether protection due to RSV prophylaxis would be enhanced by having localized guidelines for the initiation of prophylaxis.
 
@@
 	\item To what extent does regional variability of RSV incidence in Connecticut impact the effectiveness of the AAP-recommended prophylaxis regimen?
-	\item Can we use spatial analysis of RSV to propose alternative regimens that would increase the benefits of prophylaxis in comparison to the AAP-recommended regimen, without increasing the total cost of the regimen?
-	\item Is there year-to-year variation in timing of RSV season in Connecticut?
-	\item Can we take advantage of any year-to-year variation to improve upon AAP-recommended prophylaxis, without increasing treatment cost?
+	\item Would county- or state-specific alternative regimens increase the benefits of prophylaxis in comparison to the AAP-recommended regimen without increasing the total cost of the regimen?
+	\item Is there important year-to-year variation in timing of RSV season in Connecticut?
 \end{itemize}
@@
 
-\subsection{Case definition}
+\subsection{Source of data}
 
-In Connecticut, the Department of Public Health (CT DPH), via its Office of Health Care Access (OHCA), maintains a database of all hospitalizations in every non-federal short-stay acute-care general hospital in the state.
+We obtained data consisting of all hospitalizations among children <2 years old in Connecticut from 1996 to 2013 from the Connecticut State Inpatient Database through the Connecticut Department of Public Health (CT DPH).
+Relevant variables in the data were ZIP code of residence, patient age, ICD-9 defined diagnoses (up to 10 diagnoses per hospital admission), and week and year of hospital admission.
+
+\subsection{Definitions}
+
 We defined an RSV-associated hospitalization in Connecticut to be a hospital stay for which:
@@
 
-Using the OHCA weekly hospitalization statistics, we identified \Sexpr{prettyNum(nrow(dataset), big.mark=",")} RSV-associated hospitalizations in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)} (inclusive).
+Using the weekly hospitalization data, we identified \Sexpr{prettyNum(nrow(dataset), big.mark=",")} RSV-associated hospitalizations in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)} (inclusive).
 
@@
 
-\subsection{Data normalization}
-
-We designated epidemiological years as beginning in the first full week of July, in order to accommodate the timing of RSV peaks (which span two calendar years) and the limitations of hospitalization records (which OHCA aggregated into Monday-Sunday calendar weeks).
-Due to changes in diagnostic coding, we excluded data prior to July 1996; we similarly excluded data after June 2013 due to incompleteness.
-
-\subsection{Choice of model}
-
-Our goal was to construct a model of annual RSV incidence that allowed us to obtain interval estimates of complex characteristics of RSV seasons, such as season onset, season offset, and preventable fraction of a prophylaxis regimen.
-To that end, we fit smooth curves through annual RSV hospitalization data, and used resampling to obtain interval estimates.
-(See ???.)
-
-% TODO ref spline paper
+We designated epidemiological years as beginning in the first full week of July, in order to accommodate the timing of RSV peaks (which span two calendar years).
+Due to changes in diagnostic coding, we excluded data prior to July 1996; we similarly excluded data after June 2013 due to incompleteness of data for the 2013-14 epidemiological year.
 
@@
 \input{\figuresDir/map.tex}
-\caption{Subdivision of Connecticut into high-RSV and low-RSV counties}
+\caption{Subdivision of Connecticut into high-population and low-population counties}
 \label{fig:map}
@@
 
-For our spatial analysis, we aggregated RSV incidence data between \Sexpr{formatYear(startDate)} and \Sexpr{formatYear(endDate)} into five regions:
+We analyzed RSV data between \Sexpr{formatYear(startDate)} and \Sexpr{formatYear(endDate)} aggregated either to the state level or into four regions:
 
 \begin{itemize}
-    \item One region for the entire state
-    \item One region for each of the counties with high RSV case counts: Hartford County, Fairfield County, and New Haven County (Figure \ref{fig:map}).
-    \item One discontiguous region comprised of all remaining counties in Connecticut: \Sexpr{gsub("(.*), (.*)", "\\1, and \\2", paste(lowIncidenceCounties, collapse=", "))} (``low-RSV counties'').
+    \item One region for each of the counties with high population levels and high RSV case counts: Hartford County, Fairfield County, and New Haven County (Figure \ref{fig:map}).
+    \item One discontiguous region comprised of all remaining counties in Connecticut: \Sexpr{gsub("(.*), (.*)", "\\1, and \\2", paste(lowIncidenceCounties, collapse=", "))} (``low-population counties'').
 \end{itemize}
@@
 
-We chose to aggregate low-RSV counties into a single region because our analysis in those counties individually yielded results with low statistical power.
+We chose to aggregate low-population counties into a single region because our analysis in those counties individually yielded results with low statistical power.
 
-\subsection{Evaluating the AAP prophylaxis recommendation}
+\subsection{Analysis approach}
 
-We began by assessing the current AAP RSV prophylaxis guidelines.
-These guidelines recommend RSV prophylaxis with 5 monthly doses of palivizumab, starting in November, for all high-risk infants in their first year of life; in the second year of life, palivizumab is only recommended for some subgroups.
-For simplicity, we assumed that protection by palivizumab begins on November 15th and lasts 24 weeks.
+Our goal was to construct a model of annual RSV incidence that allowed us to estimate characteristics of RSV seasons, such as season onset, season offset, and preventable fraction of a prophylaxis regimen.
+To that end, we fit smooth curves through annual RSV hospitalization data, and used resampling to obtain confidence intervals.
+This was performed using the ???
+package in R (See ???
+for details on the analytical method and R package.)
 
+We defined season onset as the time when cumulative incidence rises beyond \Sexpr{seasonThreshold * 100}\% of the total cumulative incidence, and season offset as the time when cumulative incidence rises beyond \Sexpr{(1 - seasonThreshold) * 100}\% of the total cumulative incidence.
+We aggregated our data by surveillance week across all surveillance years, and estimated RSV season onset and offset for each region.
+
+The choice of \Sexpr{seasonThreshold * 100}\% and \Sexpr{(1 - seasonThreshold) * 100}\% incidence thresholds was based on our intent to use estimates of RSV season onset and offset to evaluate alternative prophylaxis regimens (as described below), while maintaining the 5-month dosing schedule (and therefore not increasing medication cost).
+Incidence cutoffs other than \Sexpr{seasonThreshold * 100}\% and \Sexpr{(1 - seasonThreshold) * 100}\% were briefly investigated, but quickly ruled out because they produced prophylaxis regimens starting long prior to RSV season onset or ending long after RSV season offset, and therefore had very low preventable fractions.
+
+% TODO ref spline paper
+
+\subsection{Evaluating alternative prophylaxis regimens}
+
+We estimated the fraction of preventable cases at the state and county level by following the current AAP guidelines or six alternative regimens:
+
+\begin{itemize}
+    \item \textbf{By current AAP national guidelines}: These guidelines recommend RSV prophylaxis with 5 monthly doses of palivizumab, starting in November, for all high-risk infants in their first year of life; in the second year of life, palivizumab is only recommended for some subgroups.
+For simplicity, we assumed that protection by palivizumab begins on November 15th.
+    \item \textbf{By statewide all-years onset}: prophylaxis administration begins at statewide all-years median RSV season onset.
+\item \textbf{By statewide all-years midpoint}: prophylaxis administration begins 12 weeks before the average of the (statewide all-years median) season onset and offset.
+    \item \textbf{By statewide all-years offset}: prophylaxis administration begins 24 weeks before the (statewide all-years median) RSV season offset. 
+    \item \textbf{By regional all-years onset}: prophylaxis administration begins at regional (county-wide, or --- in the case of low-population counties --- low-population-region-wide) all-years median RSV season onset.
+    \item \textbf{By regional all-years midpoint}: prophylaxis administration begins 12 weeks before the average of the (regional all-years median) RSV season onset and offset. 
+    \item \textbf{By regional all-years offset}: prophylaxis administration begins 24 weeks before the (regional all-years median) RSV season offset. 
+\end{itemize}
+
+In all these regimens, prophylaxis consists of five monthly doses of palivizumab, and protection is assumed to last 24 weeks from the first dose.
 We defined the fraction of all RSV cases that is preventable by a prophylaxis regimen (``preventable fraction'') to be the ratio of
@@
 
-\subsection{Estimating all-years characteristics of RSV seasons}
-
-We then turned our attention to spatial variation of seasonal RSV patterns between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)}.
-In particular, we defined season onset as the time when cumulative incidence rises beyond \Sexpr{seasonThreshold * 100}\% of the total cumulative incidence, and season offset as the time when cumulative incidence rises beyond \Sexpr{(1 - seasonThreshold) * 100}\% of the total cumulative incidence.
-We aggregated our data by surveillance week across all surveillance years, and estimated RSV season onset and offset for each region.
-
-The choice of \Sexpr{seasonThreshold * 100}\% and \Sexpr{(1 - seasonThreshold) * 100}\% incidence thresholds was based on our intent to use estimates of RSV season onset and offset to put forth alternative prophylaxis regimens (as described below), while maintaining the 5-month dosing schedule (and therefore not increasing medication cost).
-Incidence cutoffs other than \Sexpr{seasonThreshold * 100}\% and \Sexpr{(1 - seasonThreshold) * 100}\% were briefly investigated, but quickly ruled out because they produced prophylaxis regimens starting long prior to RSV season onset or ending long after RSV season offset, and therefore had very low preventable fractions.
-
-\subsection{Evaluating spatially adjusted prophylaxis regimens}
-
-Following this analysis, we estimated the regional and statewide preventable fraction for six spatially adjusted prophylaxis regimens:
-
-\begin{itemize}
-    \item \textbf{By statewide all-years onset}: prophylaxis administration begins at statewide all-years median RSV season onset. 
-    \item \textbf{By statewide all-years midpoint}: prophylaxis administration begins 12 weeks before the average of the (statewide all-years median) season onset and offset. 
-    \item \textbf{By statewide all-years offset}: prophylaxis administration begins 24 weeks before the (statewide all-years median) RSV season offset. 
-    \item \textbf{By regional all-years onset}: prophylaxis administration begins at regional (county-wide, or --- in the case of low-RSV counties --- low-RSV-region-wide) all-years median RSV season onset.
-    \item \textbf{By regional all-years midpoint}: prophylaxis administration begins 12 weeks before the average of the (regional all-years median) RSV season onset and offset. 
-    \item \textbf{By regional all-years offset}: prophylaxis administration begins 24 weeks before the (regional all-years median) RSV season offset. 
-\end{itemize}
-
-In all our alternative regimens, prophylaxis consists of five monthly doses of palivizumab, and protection is assumed to last 24 weeks from the first dose.
-
 \subsection{Accommodating implementation complexity}
@@
 
-In each variant, we again estimated the preventable fraction of all six spatially adjusted regimens.
+In each variant, we again estimated the preventable fraction of all 6 alternative regimens.
 
@@
 
-\paragraph{RSV season timing varies regionally}
+\paragraph{Timing of the RSV season varies within the state}
 
@@
 
-Compared to the statewide median onset of the RSV season at \Sexpr{regionOnset("all")} weeks (\Sexpr{regionOnsetCI("all", level)} weeks) and offset at \Sexpr{regionOffset("all")} weeks (\Sexpr{regionOffsetCI("all", level)} weeks), RSV season in Fairfield county the earliest median onset at \Sexpr{regionOnset("Fairfield")} weeks (\Sexpr{regionOnsetCI("Fairfield", level)} weeks) and the latest median offset at \Sexpr{regionOffset("Fairfield")} weeks (\Sexpr{regionOffsetCI("Fairfield", level)} weeks).
-Meanwhile, the RSV season in the low-RSV region has the latest onset at \Sexpr{regionOnset("lowIncidence")} weeks (\Sexpr{regionOnsetCI("all", level)} weeks); its season offset shows no change from the statewide median (Figure \ref{fig:seasonByRegion}).
+Statewide, the median onset of the RSV season is at week \Sexpr{regionOnset("all")} (\Sexpr{regionOnsetCI("all", level)}), and offset is at week \Sexpr{regionOffset("all")} (\Sexpr{regionOffsetCI("all", level)}).
+Fairfield county had the the earliest RSV season, with a median onset at week \Sexpr{regionOnset("Fairfield")} (\Sexpr{regionOnsetCI("Fairfield", level)}).
+Fairfield also had the latest median offset at week \Sexpr{regionOffset("Fairfield")} (\Sexpr{regionOffsetCI("Fairfield", level)}).
+Meanwhile, the RSV season in the low-population counties had the latest onset at week \Sexpr{regionOnset("lowIncidence")} (\Sexpr{regionOnsetCI("all", level)}); the season offset in these counties was not different than the statewide median (Figure \ref{fig:seasonByRegion}).
 
-\paragraph{The AAP guidelines perform best in low-RSV counties and worst in Fairfield county}
+\paragraph{The AAP guidelines perform best in low-population counties and worst in Fairfield county}
 
@@
 
-Statewide, our model shows that \Sexpr{regionStrategyCoverage("all", "aap", 0)} of RSV cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) occur while palivizumab, administered per the AAP guidelines, offers protection.
-The AAP guidelines perform better in the low-RSV counties, where \Sexpr{regionStrategyCoverage("lowIncidence", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("lowIncidence", "aap", 0, level)}) occur during the prophylaxis interval, but worse in Fairfield county, where \Sexpr{regionStrategyCoverage("Fairfield", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("Fairfield", "aap", 0, level)}) occur during this time (Figure \ref{fig:coverageByRegionAAP}).
+Statewide, our model shows that \Sexpr{regionStrategyCoverage("all", "aap", 0)} of RSV cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) occur while palivizumab offers protection when administered per the AAP guidelines.
+The AAP guidelines perform better in the low-population counties, where \Sexpr{regionStrategyCoverage("lowIncidence", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("lowIncidence", "aap", 0, level)}) occur during the prophylaxis interval, but worse in Fairfield county, where \Sexpr{regionStrategyCoverage("Fairfield", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("Fairfield", "aap", 0, level)}) occur during this time (Figure \ref{fig:coverageByRegionAAP}).
 
@@
 This is caused by temporal misalignment between the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each region) and the timing of the AAP-recommended prophylaxis regimen (Figure \ref{fig:coverageByRegionAAPInsight}).
-Fairfield county, owing to its early season onset, sees disproportionately more cases before prophylaxis administration begins; on the other hand, the low-RSV counties, owing to their late season onset and relatively shorter RSV seasons, see almost all of their RSV cases within the prophylaxis window.
+Fairfield county, owing to its early season onset, sees disproportionately more cases before prophylaxis administration begins; on the other hand, the low-population counties, owing to their late season onset and relatively shorter RSV seasons, see almost all of their RSV cases within the prophylaxis window.
 
@@
 
-\paragraph{Without calendarical rounding, spatially adjusted regimens are superior to the AAP recommendations}
+\paragraph{Without calendrical rounding, spatially adjusted regimens are superior to the AAP recommendations}
 
@@
 
-Based on all-years data, the six spatially adjusted prophylaxis regimens (with no rounding of prophylaxis dates), when compared to the AAP guidelines, yield non-inferior results in all regions, and superior results statewide (Figure \ref{fig:coverageByRegionRegimen}).
+Based on all-years data, the six spatially-adjusted prophylaxis regimens (with no rounding of prophylaxis dates), yield results in all regions that are as good or better than the AAP guidelines.
+(Figure \ref{fig:coverageByRegionRegimen}).
 Statewide, the AAP guidelines offer protection to \Sexpr{regionStrategyCoverage("all", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}).
-The alternative regimen based on all-years statewide onset yields the smallest increase, to \Sexpr{regionStrategyCoverage("all", "stateOnset", 0)} (\Sexpr{regionStrategyCoverageCI("all", "stateOnset", 0, level)}); other alternative regimens yield similar results.
+The alternative regimen based on statewide onset yields the smallest increase, to \Sexpr{regionStrategyCoverage("all", "stateOnset", 0)} (\Sexpr{regionStrategyCoverageCI("all", "stateOnset", 0, level)}); other alternative regimens yield similar results.
 Most of the increase comes from Hartford county, where the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", 0, level)}), whereas the alternative regimen based on all-years regional offset generates the smallest increase, to \Sexpr{regionStrategyCoverage("Hartford", "countyOffset", 0)} (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", 0, level)}); other alternative regimens are comparable.
@@
 
-Compared to our regional all-years analysis, the three regimens based on statewide recent-years analysis produced non-superior results everywhere, and inferior results in the low-RSV counties (Figure \ref{fig:coverageByRegionRegimenWithSliding}).
+Compared to our regional all-years analysis, the three regimens based on statewide recent-years analysis produced non-superior results everywhere, and inferior results in the low-population counties (Figure \ref{fig:coverageByRegionRegimenWithSliding}).
 Due to the non-superiority of regimens based on statewide recent-years analysis, we did not evaluate regimens based on regional recent-years data.
@@
 \section{Discussion}
-
-\subsection{Results}
 
@@
 
-\subsection{Limitations}
-
 Although we were able to reach some conclusions about the impact of calendrical rounding on spatially adjusted prophylaxis regimens, ultimately our analysis is hamstrung by weekly aggregation of hospital admission data.
@@
 Finally, towns that see substantial inter-county travel (for example, employment hubs near county lines) likely bias our regional analysis.
-
-\subsection{Conclusion}
 

### 2019-03-26 Paper/Paper.R

@@ -48,7 +48,7 @@ regionOffset = function(c) {
 }
 
 formatThresholdCI = function(lower, upper, level) {
-  sprintf("%d\\%% CI: %.2f -- %.2f", level * 100, lower %% 52, upper %% 52)
+  sprintf("%d\\%% CI: week %.2f -- %.2f", level * 100, lower %% 52, upper %% 52)
 }
 
 regionOnsetCI = function(c, level) {

### 2019-03-27 Paper/Figures.Rnw
Extracted figures and assorted other R code into separate files, to make life easier with overleaf

--- 2018-01-24 Thesis/Thesis.rnw
@@
-% TODO: Plot regression line in onset/offset analysis
-% TODO clarify all years analysis in figure captions
-% TODO Put 1-2% punchline in the abstract, maybe
-% TODO So it turns out that several regimens are actually the same, and that the best regional regimen @ 2w rounding is actually the same as the best statewide regimen @ 2w rounding.
-As a result, the conclusion could be simplified to statewide 2w rounding.
-% TODO paragraphs
-
-<<options, echo=FALSE>>=
-    opts_chunk$set(echo=FALSE, message=FALSE)
-@
-
-<<load>>=
-read_chunk("../Analysis/RSV.R")
-read_chunk("../Thesis/Thesis.R")
-@
-
-<<libraries, cache=FALSE>>=
-@
-
-<<external, cache=TRUE>>=
-@
-
-<<util, warning=FALSE>>=
-@
-
-\documentclass[10pt,letter]{article}
-
-\usepackage{multicol,float}
-\floatplacement{figure}{H}
-\raggedcolumns
-
-\usepackage{printlen}
-\usepackage{textcomp}
-\usepackage{setspace}
-
-\usepackage[hidelinks]{hyperref}
-\usepackage[svgnames]{xcolor} % Must go before tikz and before structure.tex
-\usepackage{tikz}
-%\usepackage{draftwatermark}
-%\SetWatermarkScale{1}
-%\SetWatermarkAngle{45}
-%\SetWatermarkFontSize{4ex}
-%\SetWatermarkHorCenter{12ex}
-%\SetWatermarkVerCenter{12ex}
-%\SetWatermarkLightness{.5}
-%\SetWatermarkText{DRAFT 5}
-
-\input{structure.tex}
-\edef\figuresDir{\Sexpr{figuresDir}}
-
-\usepackage[bf,medium,raggedright,compact]{titlesec}
-\titleformat{\section}{\normalfont\large\bfseries\scshape}{\thesection}{1em}{}
-\titleformat{\subsection}{\normalfont\normalsize\bfseries\scshape}{}{0em}{}
-\titleformat{\paragraph}{\normalfont\normalsize\bfseries}{}{0em}{}
-\titlespacing*{\paragraph}{0pt}{3.25ex plus 1ex minus .2ex}{0em}
-
-\usepackage{hanging}
-\usepackage{graphicx}
-
-\newlength\abstractindent
-\setlength\abstractindent{1in}
-\newcommand{\abstractsection}[1]{\hangpara{\abstractindent}{1}\makebox[1in][l]{\textbf{\textsc{#1}}}}
-\newcommand{\abstractpara}{\hskip\abstractindent\hskip\baseparindent}
-
-\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
-
-\title{Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}}
-\def\headertitle{Assessment and optimization of RSV prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}}
-
-\author{
-    \authorstyle{Ben Artin\textsuperscript{1}}
-    \newline\newline
-    \authorstyle{Daniel Weinberger, PhD\textsuperscript{2}, advisor}\\
-    \authorstyle{Virginia Pitzer, ScD\textsuperscript{2}, advisor}
-    \newline\newline
-    \textsuperscript{1}\institution{Yale University, School of Public Health and School of Medicine}\\
-    \textsuperscript{2}\institution{Yale University, School of Public Health}
-}
-
-\date{\today}
-
-\begin{document}
-
-\newlength\baseparindent
-\setlength\baseparindent{\parindent}
-\begingroup
-\setlength\parindent{0em}
-
-\maketitle
-
-\begin{center}
-
-\vspace{20pt}
-\large Submitted to the School of Public Health and the School of Medicine, in partial fulfillment of the requirements for the degrees of Master of Public Health and Master of Medical Sciences
-
-\vspace{40pt}
-
-\includegraphics[height=160pt]{EPH}
-\hspace{40pt}
-\includegraphics[height=160pt]{Medicine}
-
-\end{center}
-
-\thispagestyle{firstpage}
-
-\clearpage
-\endgroup
-
-\section*{\centerline{Abstract}}
-\begin{hangparas}{\abstractindent}{1}
-\begin{onehalfspacing}
-
-\abstractsection{Background}Respiratory syncytial virus (RSV) causes seasonal respiratory infection with potentially serious complications in children, and leads to hospitalization rates as high as 50\% in high-risk infants.
-Safe and effective immunoprophylaxis (palivizumab) is available, but costly.
-The American Academy of Pediatrics (AAP) recommends palivizumab only for infants at high risk of complications, and only during the RSV season.
-Although the current AAP guidelines acknowledge the existence of spatial and temporal variation in RSV incidence, they do not recommend spatial or temporal adjustments to immunoprophylaxis regimen outside of Florida.
-In this study, we investigate the value of using spatial and temporal variation in RSV incidence to adjust the RSV prophylaxis regimen in Connecticut.
-
-\abstractsection{Methods}We describe a generalized additive model of RSV incidence using cubic cyclic penalized splines and apply that model to hospital admissions in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)}.
-We use the model to estimate the fraction of all RSV cases in Connecticut occurring while immunoprophylaxis (administered according to the AAP guidelines) offers protection from RSV infection (``preventable fraction'').
-We also formulate several alternative immunoprophylaxis regimens, with the same net pharmaceutical cost as the AAP-recommended regimen, and similarly estimate their preventable fraction.
-
-\abstractsection{Results}Using preventable fraction to assess different immunoprophylaxis regimens, we found that regimens adjusted for county-level variation in timing of RSV seasons are superior to the current AAP-recommended regimen.
-We also considered the effect of rounding the timing of the first dose of prophylaxis to pragmatic calendrical boundaries (weekly, biweekly, and monthly), and found that benefits of alternative regimens over the AAP-recommended regimen persisted with biweekly rounding, but not with monthly rounding.
-Our best-performing pragmatic alternative to the AAP guidelines was based on the regional RSV season midpoint with biweekly rounding.
-In comparison to the AAP recommendation, whose preventable fraction is \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}), that alternative yielded improvement to preventable fraction of \Sexpr{regionStrategyCoverage("all", "countyMiddle", 2)} (\Sexpr{regionStrategyCoverageCI("all", "countyMiddle", 2, level)}).
-We also found that alternative regimens adjusted for annual variation in RSV season are non-superior to spatially adjusted regimens.
-
-\abstractsection{Conclusion}Overall, we recommend county-level spatial analysis of RSV incidence as the starting point for RSV immunoprophylaxis optimization in Connecticut.
-However, the potential reduction in RSV hospitalizations should be weighed against the potential increase in implementation cost.
-
-\abstractpara{}
-
-\end{onehalfspacing}
-\end{hangparas}
-
-\thispagestyle{empty}
-\clearpage
-
-\tableofcontents
-\clearpage
-
-%\listoftables
-%\clearpage
-
-\listoffigures
-\clearpage
-
-\begin{multicols}{2}
-
-\section{Introduction}
-
-\subsection{Respiratory syncytial virus}
-
-Respiratory syncytial virus (RSV) causes upper respiratory infections in humans of all ages.
-In adults, RSV infection is typically asymptomatic or gives rise to mild respiratory illness.
-However, RSV infection often incites more serious respiratory illness in children, with hospitalization rates as high as 4.4\% in infants with no comorbidities, making RSV a leading cause of hospitalization among infants.\cite{Hall:2009gi,Hall:2013jo,Zhou:2012ho,Boyce:2000gz}
-
-For infants, risk factors of serious illness and hospitalization due to RSV infection include prematurity, chronic lung disease of prematurity, congenital heart disease, anatomic pulmonary abnormalities, neuromuscular disorders, trisomy 21, and immunocompromised status.\cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj} Hospitalization rate due to RSV among high-risk infants is anywhere from two to ten times higher than among infants with no comorbidities.\cite{Boyce:2000gz}
-
-\subsection{RSV immunoprophylaxis}
-
-Immunoprophylaxis with palivizumab, a monoclonal antibody medication, has been approved in the US for prevention of RSV infection since 1998.
-Palivizumab is administered via intramuscular injection and requires five monthly doses, priced at \$1500-\$3000 per dose.\cite{Hampp:2011ju,Andabaka:2013dr}
-
-Palivizumab has been found to be effective in reducing hospitalizations due to RSV; in double-blinded trials in high-risk infants, it reduced hospitalization rate by 45-55\% compared to placebo.\cite{Group:1998ih,Feltes:2003wm} Its has also been found to be safe and well-tolerated in clinical trials.\cite{Group:1998ih}
-
-Owing to the high cost, the American Academy of Pediatrics (AAP) guidelines, revised in 2014, recommend palivizumab immunoprophylaxis only for high-risk infants, and only during RSV season.\cite{Anonymous:1998up,AmericanAcademyofPediatricsCommitteeonInfectiousDiseasesandCommitteeonFetusandNewborn:2003ug,AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
-
-\subsection{RSV seasonality}
-
-RSV seasonality has been established throughout the United States, based on National Respiratory and Enteric Virus Surveillance System data.
-In all states except for Florida, it shows a stable season onset between mid-November and early January and a stable season offset between mid-March and late April.\cite{CentersforDiseaseControlandPreventionCDC:2011wt,CentersforDiseaseControlandPreventionCDC:2013wv} RSV season in Florida begins approximately two months earlier than in other states.
-\cite{CentersforDiseaseControlandPreventionCDC:2013wv}
-
-The AAP acknowledges the potential significance of spatial and temporal variation in RSV incidence, but --- outside of Florida --- does not recommend local variance from nation-wide prophylaxis guidelines.\cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
-
-\subsection{Spatio-temporal variability of RSV}
-
-Nationwide spatial variability of RSV season has been established by the Centers for Disease Control and Prevention (CDC).\cite{CentersforDiseaseControlandPreventionCDC:2011wt,CentersforDiseaseControlandPreventionCDC:2013wv}
-
-In Connecticut, the Department of Public Health (CT DPH), via its Office of Health Care Access (OHCA), maintains a database of all hospitalizations in every non-federal short-stay acute-care general hospital in the state.
-Previous analysis of this database at the Yale University School of Public Health has shown regional variability in time of peak RSV incidence within Connecticut.\cite{Noveroske:y4fi3188} No prior research is available regarding year-to-year variation in timing of RSV season in Connecticut.
-
-\subsection{Study aims}
-
-Motivated by the AAP's recognition of the significance of spatial variation in formulating prophylaxis guidelines, and the known spatial variability of RSV incidence in Connecticut, we aim to determine whether spatial and temporal variability can be used to optimize RSV prophylaxis in Connecticut by asking these questions:
-
-\begin{itemize}
-	\item To what extent does regional variability of RSV incidence in Connecticut impact the effectiveness of the AAP-recommended prophylaxis regimen?
-	\item Can we use spatial analysis of RSV to propose alternative regimens that would increase the benefits of prophylaxis in comparison to the AAP-recommended regimen, without increasing the total cost of the prophylactics the regimen?
-	\item Is there year-to-year variation in timing of RSV season in Connecticut?
-	\item Can we take advantage of any year-to-year variation to improve upon AAP-recommended prophylaxis, without increasing treatment cost?
-\end{itemize}
-
-The study was approved by the Human Investigation Committees at Yale University and the CT DPH. The authors assume full responsibility for analyses and interpretation of the data obtained from CT DPH.
-
-\section{Methods}
-
-\subsection{Case definition}
-
-We defined an RSV-associated hospitalization in Connecticut to be a hospital stay for which:
-
-\begin{itemize}
-    \item the postal code of residence listed in patient's medical record was in Connecticut\footnote{According to the zipcode $\rightarrow$ state mapping in R \texttt{zipcode} package version 1.0}, and
-    \item the hospital stay was associated with ICD-9-CM diagnosis code \texttt{079.6} (RSV), \texttt{466.11} (Acute bronchiolitis due to RSV), or \texttt{480.1} (Pneumonia due to RSV).
-\end{itemize}
-
-Using the OHCA weekly hospitalization statistics, we identified \Sexpr{nrow(dataset)} RSV-associated hospitalizations in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)} (inclusive).
-
-% TODO patient age
-
-\subsection{Data normalization}
-
-Given that RSV seasons peak early in each calendar year, we assigned to each surveillance year 12 months of data starting in July of previous year.
-OHCA provided us with hospitalization records aggregated into Monday-Sunday calendar weeks; we assigned the first full calendar week of July to be surveillance week 1 in each surveillance year.
-
-Due to changes in diagnostic coding, we excluded data prior to July 1996; we similarly excluded data starting after June 2013, due to incompleteness.
-
-\subsection{Choice of model}
-
-Our goal was to construct a model of annual RSV incidence that allowed us to easily estimate complex characteristics of RSV seasons, such as season onset and offset.
-To that end, we looked for a model that allowed easy sampling of estimated model parameters; coupling this with Monte Carlo sampling --- after transforming model parameters into response variables --- allowed us to sample arbitrary response variables.
-
-We were willing to assume that RSV incidence is the result of a Poisson process whose $\log$ can be modeled as a piecewise twice-differentiable function of time.
-To meet those criteria and assumptions, we chose a log-linked generalized additive model (GAM) with penalized cubic B-splines for our analysis.
-
-% Looked for prior art on using GAM/pspline for ID epi, didn't find anything that was relevant. (Not even by Goldstein or Lipsitch.)
-
-We developed a custom R package for estimation of arbitrary characteristics of infectious disease outbreaks (as long as the outbreaks are amenable to GAM); this package is available at \href{https://github.com/airbornemint/outbreak-inference}{\nolinkurl{github.com/airbornemint/outbreak-inference}}.
-
-\subsection{Spatial aggregation of RSV incidence}
-
 <<map, results='hide'>>=
-    tikz(sprintf("%s/map.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
+    tikz(sprintf("%s/map.tex", figuresDir), width=1.5*inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
     US.counties = readOGR(dsn="../Maps/cb_2016_us_county_5m",layer="cb_2016_us_county_5m")
@@
 @
-
-For our spatial analysis, we aggregated RSV incidence data between \Sexpr{formatYear(startDate)} and \Sexpr{formatYear(endDate)} into five regions:
-
-\begin{itemize}
-    \item One region for the entire state
-    \item One region for each of the counties with high RSV case counts: Hartford County, Fairfield County, and New Haven County (Figure \ref{fig:map}).
-    \item One discontiguous region comprised of all remaining counties in Connecticut: \Sexpr{gsub("(.*), (.*)", "\\1, and \\2", paste(lowIncidenceCounties, collapse=", "))} (``low-RSV counties'').
-\end{itemize}
-
-We chose county-level aggregation with an eye towards using this data to inform clinical practice guidelines, which are typically based on administrative regions for reasons of administrative and implementation simplicity.
-
-We chose to aggregate low-RSV counties into a single region because our analysis in those counties individually would have yielded results with unacceptably low statistical power.
-
-\begin{figure}
-\begin{center}
-\input{\figuresDir/map.tex}
-\caption{Subdivision of Connecticut into high-RSV and low-RSV counties}
-\label{fig:map}
-\end{center}
-\end{figure}
-
-\subsection{Evaluating the AAP prophylaxis recommendation}
-
-We began by assessing the current AAP RSV prophylaxis guidelines.
-These guidelines recommend RSV prophylaxis with 5 monthly doses of palivizumab, starting in November, for all high-risk infants in their first year of life; in the second year of life, only some subgroups are recommended to receive palivizumab.
-
-For simplicity, we assumed that protection by palivizumab begins on November 15th and lasts 24 weeks.
-
-We defined the fraction of all RSV cases that is preventable by a prophylaxis regimen (``preventable fraction'') to be the ratio of
-
-\begin{itemize}
-\item the number of RSV-associated hospitalizations that occur while the prophylaxis regimen offers protection to those who receive prophylaxis as scheduled, and
-\item the total number of RSV-associated hospitalizations.
-\end{itemize}
-
-%TODO citation needed
-
-Given that high-risk infants are a small subgroup of the general population, we assumed that our model of RSV hospitalizations among all infants is an unbiased approximation of RSV hospitalizations among high-risk infants, and that, therefore, the preventable fraction of a prophylactic regimen is an unbiased estimate of the fraction of high-risk infants who benefit from prophylaxis.
-
-\subsection{Estimating all-years characteristics of RSV seasons}
-
-We then turned our attention to spatial variation of seasonal RSV patterns between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)}.
-In particular, we defined season onset as the time when cumulative incidence rises beyond \Sexpr{seasonThreshold * 100}\% of the total cumulative incidence, and season offset as the time when cumulative incidence rises beyond \Sexpr{(1 - seasonThreshold) * 100}\% of the total cumulative incidence.
-We aggregated our data by surveillance week across all surveillance years, and estimated RSV season onset and offset for each region.
-
-The choice of \Sexpr{seasonThreshold * 100}\% and \Sexpr{(1 - seasonThreshold) * 100}\% incidence thresholds was based on our intent to use estimates of RSV season onset and offset to put forth alternative prophylaxis regimens (as described below), while maintaining 5-month dosing schedule (and therefore not increasing medication cost).
-Incidence cutoffs other than \Sexpr{seasonThreshold * 100}\% and \Sexpr{(1 - seasonThreshold) * 100}\% were briefly investigated, but quickly ruled out because they produced prophylaxis regimens starting long prior to RSV season onset or ending long after RSV season offset, and therefore had very low preventable fractions.
-
-\subsection{Evaluating spatially adjusted prophylaxis regimens}
-
-Following this analysis, we estimated the regional and statewide preventable fraction for six spatially adjusted prophylaxis regimens:
-
-\begin{itemize}
-    \item \textbf{By statewide all-years onset}: prophylaxis administration begins at statewide all-years median RSV season onset. 
-    \item \textbf{By statewide all-years midpoint}: prophylaxis administration begins 12 weeks before the average of the (statewide all-years median) season onset and offset. 
-    \item \textbf{By statewide all-years offset}: prophylaxis administration begins 24 weeks before the (statewide all-years median) RSV season offset. 
-    \item \textbf{By regional all-years onset}: prophylaxis administration begins at regional\footnote{county-wide, or --- in the case of low-RSV counties --- low-RSV-region-wide} all-years median RSV season onset.
-    \item \textbf{By regional all-years midpoint}: prophylaxis administration begins 12 weeks before the average of the (regional all-years median) RSV season onset and offset. 
-    \item \textbf{By regional all-years offset}: prophylaxis administration begins 24 weeks before the (regional all-years median) RSV season offset. 
-\end{itemize}
-
-In all our alternative regimens, prophylaxis consists of five monthly doses of palivizumab, and protection is assumed to last 24 weeks from the first dose.
-
-\subsection{Accommodating implementation complexity}
-
-Keeping in mind implementation constraints of clinical practice guidelines, we performed three additional variants of our spatial analysis:
-
-\begin{itemize}
-    \item \textbf{Weekly rounding}: prophylaxis start and end date rounded to the nearest calendar week,
-    \item \textbf{Biweekly rounding}: prophylaxis start and end date rounded to the nearest two-week calendar period, with periods chosen to approximately align with November 15th, and
-    \item \textbf{Monthly rounding}: prophylaxis start and end date rounded to the nearest four-week calendar periods, with periods chosen to approximately align with November 15th.
-\end{itemize}
-
-In each variant, we again estimated the preventable fraction of all six spatially adjusted regimens.
-
-\subsection{Temporal aggregation of RSV incidence}
-
-Our analysis thus far assumed that RSV seasons are similar year-to-year.
-To analyze the effects of year-to-year variation between RSV seasons on prophylaxis regimens, we chose to aggregate our data into (overlapping) periods of three consecutive years --- in order to maintain a higher level of statistical power, as well as to limit impact of short-term variation on our results.
-
-This gave us \Sexpr{year(endDate) - year(startDate) -1} three-year periods, with the \Sexpr{formatYear(startDate + 2*365)} period covering surveillance years \Sexpr{formatYear(startDate)} through \Sexpr{formatYear(startDate + 2*365)}, and the \Sexpr{formatYear(endDate)} period covering \Sexpr{formatYear(endDate - 2*365)} through \Sexpr{formatYear(endDate)}.
-
-We began our temporal analysis by estimating onset and offset for each three-year period, using the same penalized spline GAM as all-years analysis, producing --- as before --- statewide and regional estimates of \Sexpr{seasonThreshold * 100}\% onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset.
-
-To evaluate year-to-year variation in RSV season onset and offset we modeled median RSV three-year onset and offset against time using simple linear regression.
-
-We did not analyze any other long-term patterns, such as cyclicity.
-
-\subsection{Evaluating alternative recent-years prophylaxis regimens}
-
-Finally, to assess the impact of any long-term trends in RSV season timing on prophylaxis, we evaluated three additional prophylaxis regimens.
-Here, each prophylaxis regimen is adjusted annually based on RSV data from the preceding three-year period:
-
-\begin{itemize}
-    \item \textbf{By statewide recent-years onset}: prophylaxis administration in a given year begins at statewide median onset from the preceding three years. 
-    \item \textbf{By statewide recent-years midpoint}: prophylaxis administration begins 12 weeks before the average of the (statewide median) onset and offset from the preceding three years. 
-    \item \textbf{By statewide recent-years offset}: prophylaxis administration in a given year begins 24 weeks before the (statewide median) offset from the preceding three years.
-\end{itemize}
-
-\setcounter{figure}{3}
-\begin{figure*}[b]
-\begin{center}
-\input{\figuresDir/coverageByRegionAAPInsight.tex}
-\caption[Regional variation in the relative timing of the RSV season in Connecticut and the AAP-recommended prophylaxis regimen]{Regional variation in the relative timing of the RSV season in Connecticut and the AAP-recommended prophylaxis regimen, showing the gap between season onset and prophylaxis start date, notable particularly in Fairfield county}
-\label{fig:coverageByRegionAAPInsight}
-\end{center}
-\end{figure*}
-\setcounter{figure}{1}
-
-\begin{figure}
-\begin{center}
-\input{\figuresDir/seasonByRegion.tex}
-\caption{Regional variation in RSV season onset and offset in Connecticut}
-\label{fig:seasonByRegion}
-\end{center}
-\end{figure}
-
-We then compared those regimens to the one recommended by AAP and to the six spatially adjusted alternatives (with no calendrical rounding) discussed above.
-
-As before, these alternative regimens involved five monthly doses of palivizumab giving 24 weeks of protection.
-
-% \uselengthunit{in}\printlength{\columnwidth}
-% column width = 3.20929 in
-
-\section{Results}
-
-\paragraph{RSV season timing varies regionally}
 
@@
 @
-
-Compared to the statewide median onset of RSV season at \Sexpr{regionOnset("all")} weeks (\Sexpr{regionOnsetCI("all", level)} weeks) and offset at \Sexpr{regionOffset("all")} weeks (\Sexpr{regionOffsetCI("all", level)} weeks), RSV season in Fairfield county has earlier median onset at \Sexpr{regionOnset("Fairfield")} weeks (\Sexpr{regionOnsetCI("Fairfield", level)} weeks) and later median offset at \Sexpr{regionOffset("Fairfield")} weeks (\Sexpr{regionOffsetCI("Fairfield", level)} weeks) (Figure \ref{fig:seasonByRegion}).
-
-\begin{figure}
-\begin{center}
-\input{\figuresDir/coverageByRegionAAP.tex}
-\caption[Regional variation in the fraction of RSV hospitalizations occurring while the AAP-recommended RSV prophylaxis is active]{Regional variation in the fraction of RSV hospitalizations occurring while protection by palivizumab --- administered per the AAP guidelines ---  is active}
-\label{fig:coverageByRegionAAP}
-\end{center}
-\end{figure}
-
-Meanwhile, in comparison with the statewide RSV season onset and offset, the low-RSV region has RSV season with later onset at \Sexpr{regionOnset("lowIncidence")} weeks (\Sexpr{regionOnsetCI("all", level)} weeks); season offset shows no change from the statewide median (Figure \ref{fig:seasonByRegion}).
-
-\paragraph{The AAP guidelines perform best in low-RSV counties and worst in Fairfield county}
 
@@
 
-    spanLabels = legendLabels(c("AAP-recommended prophylaxis", "RSV season"))
+    spanLabels = legendLabels(c("AAP-recommended prophylaxis", "RSV season"), leading=1)
 
@@
 
-Statewide, our model shows that \Sexpr{regionStrategyCoverage("all", "aap", 0)} of RSV cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) occur while palivizumab, administered per the AAP guidelines, offers protection.
+<<coverageByRegion, results='hide', warning=FALSE>>=
+    GeomErrorbar$draw_key = draw_key_vline_small
 
-\setcounter{figure}{4}
-\begin{figure*}
-\begin{center}
-\input{\figuresDir/coverageByRegionRegimen.tex}
-\caption[Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen]{Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen, showing statewide superiority and regional non-inferiority of spatially adjusted regimens.
-Preventable fraction: the fraction of all RSV-associated hospitalizations occurring while the prophylaxis regimen provides protection}
-\label{fig:coverageByRegionRegimen}
-\end{center}
-\end{figure*}
-
-The AAP guidelines perform better in the low-RSV counties, where \Sexpr{regionStrategyCoverage("lowIncidence", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("lowIncidence", "aap", 0, level)}) occur during the prophylaxis interval, but worse in Fairfield county, where \Sexpr{regionStrategyCoverage("Fairfield", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("Fairfield", "aap", 0, level)}) occur during this time (Figure \ref{fig:coverageByRegionAAP}).
-
-This is caused by temporal misalignment between the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each region), and the timing of the AAP-recommended prophylaxis regimen (Figure \ref{fig:coverageByRegionAAPInsight}).
-Fairfield county, owing to its early season onset, sees disproportionately many cases before prophylaxis administration begins; on the other hand, the low-RSV counties, owing to their late season onset and relatively shorter RSV seasons, see almost all of their RSV cases within the prophylaxis window.
-
-\paragraph{Spatially adjusted regimens are superior to the AAP recommendations}
-
-<<coverageByRegion, results='hide', warning=FALSE>>=
     tikz(sprintf("%s/coverageByRegionRegimen.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10)
     data = unprotectedByCounty %>% 
-        filter(county %in% countiesForPlots, rounding==0, sliding==FALSE)
+        filter(county %in% countiesForPlots, rounding==0, sliding==FALSE) %>%
+        mutate(strat=factor(strat, levels=c(levels(strat)[1], "_1", "_2", levels(strat)[2:7])))
 
@@
 
-Based on all-years data, the six spatially adjusted prophylaxis regimens (with no rounding of prophylaxis dates), when compared to the AAP guidelines, yield non-inferior results in all regions, and superior results statewide (Figure \ref{fig:coverageByRegionRegimen}).
-
-Statewide, the AAP guidelines offer protection to \Sexpr{regionStrategyCoverage("all", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}).
-The alternative regimen based on all-years statewide onset yields the smallest increase, to \Sexpr{regionStrategyCoverage("all", "stateOnset", 0)} (\Sexpr{regionStrategyCoverageCI("all", "stateOnset", 0, level)}); other alternative regimens yield similar results.
-
-Most of the increase comes from Hartford county, where the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", 0, level)}), whereas the alternative regimen based on all-years regional offset generates the smallest increase, to \Sexpr{regionStrategyCoverage("Hartford", "countyOffset", 0)} (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", 0, level)}); other alternative regimens are comparable.
-
-In every region, all alternative regimens based on all-years analysis are non-inferior to the AAP guidelines and non-superior to each other.
-
-\paragraph{Calendrical rounding rapidly erases gains over the AAP-recommended regimen}
-
-<<calendarForRounding, results='hide', warning=FALSE>>=
-    tikz(sprintf("%s/calendarForRoundingRegimen.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10)
-
-    roundingStrat = unprotectedByCounty %>% 
-        filter(county %in% countiesForPlots, sliding==FALSE) %>%
-        select(strat, rounding) %>%
-        unique()
-
-    dataAll = predByCounty %>%
-        filter(county %in% countiesForPlots) %>%
-        group_by(county, time) %>%
-        do(
-            roundingStrat
-        ) %>%
-        ungroup() %>%
-        group_by(county, strat, rounding) %>%
-        do(
-            (function(df) {
-                county = unique(df$county)
-                rounding = as.numeric(unique(df$rounding))
-                strat = as.character(unique(df$strat))
-                strat = ppxFixedStrategies(county, rounding)[[strat]]
-                stratActive = strat(df$time)
-                df %>%
-                    mutate(stratActive=stratActive)
-            })(.)
-        ) %>%
-        ungroup() %>%
-        filter(stratActive > 0) %>%
-        group_by(county, strat, rounding) %>%
-        summarize(start=min(time), end=max(time)) %>%
-        ungroup()
-
-    aapStartEnd = dataAll %>%
-        filter(strat == "aap") %>%
-        select(start, end) %>%
-        unique()
-
-    aap = dataAll %>%
-        filter(strat != "aap") %>%
-        group_by(strat, rounding) %>%
-        do(
-            aapStartEnd
-        ) %>%
-        ungroup() %>%
-        mutate(y=ifelse(grepl("state", strat), "all", "lowIncidence")) %>%
-        mutate(y=factor(y, levels(dataAll$county)))
-
-    data = dataAll %>% 
-        filter(strat != "aap") %>%
-        filter(xor(grepl("county", strat), county == "all"))
-
-    ggplot(data) +
-        theme_light(base_size=plotTextBaseSize) +
-    	geom_rect(aes(xmin=start, xmax=end, ymin=as.numeric(county)-0.25, ymax=as.numeric(county)+0.25), size=.375) + 
-    	geom_rect(data=aap, aes(xmin=start, xmax=end, ymin=as.numeric(y)+0.75, ymax=as.numeric(y)+1.25), size=.375) + 
-        scale_y_continuous(breaks=as.numeric(countiesForPlots), labels=countyLabels[as.character(countiesForPlots)]) + 
-        scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, limits=range(c(monthBoundaries$min, monthBoundaries$max)), expand=c(0, 0)) + 
-#        scale_color_manual(labels=spanLabels, values=twoToneAlt) +
-#        scale_fill_manual(labels=spanLabels, values=twoToneAlt)# +
-#        guides(color=guide_legend(keywidth=3, keyheight=.4)) + 
-        facet_wrap(~ rounding + strat, nrow=8, labeller=labeller(rounding=roundingLabels, strat=stratLabels), scales="free_y") #+
-#        labs(x=NULL, y="Cumulative indicence fraction") + 
-#        theme(
-#            panel.grid.major.x=element_blank(),
-#            legend.title=element_blank(),
-#            axis.title.y=element_blank(),
-#            axis.ticks.x=element_blank(),
-#            axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
-#            legend.position="bottom"
-#        )
-    dev.off()
-@
-
 <<coverageByRounding, results='hide', warning=FALSE>>=
@@
 
+    # We are going to de-emphasize some data points, because sometimes different strategies under different rounding end up producing the same prophylaxis schedule, and there is no point in showing all of them equally on the plot.
+To do this, we consider the left-to-right order in which strategies will appear in the plot, and then de-emphasize any strategy whose schedule is the same as some strategy that appears on its left
     data = unprotectedByCounty %>% 
-        filter(county == "all", sliding==FALSE)
+        filter(county == "all", sliding==FALSE) %>%
+        arrange(rounding, strat) %>%
+        mutate(strat=factor(strat, levels=c(levels(strat)[1], "_1", "_2", levels(strat)[2:7])))
+
+    data$startIdx = match(data$desc, data$desc)
+    data$isRepeat = data$startIdx != seq(1, length(data$startIdx))
+    data$isRepeat = data$isRepeat & !data$strat == "aap" 
+    data$strat.isRepeat = sprintf("%s.%s", data$strat, data$isRepeat)
+    idx = order(rep(seq(1, length(levels(data$strat))), 2))
+    strat.isRepeat.levels = (c(
+      sprintf("%s.%s", levels(data$strat), FALSE), 
+      sprintf("%s.%s", levels(data$strat), TRUE)
+    ))[idx]
+    data$strat.isRepeat = factor(data$strat.isRepeat, strat.isRepeat.levels)
 
@@
         scale_y_continuous(labels=latexPercent, limits=c(0.90, 1.00), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
-        scale_color_manual(name="Prophylaxis regimen", labels=legendLabels(stratLabels[c(seq(1, 6), 10)]), values=c(rep(c(darkBrown, darkOrange), each=3), darkPurple)) + 
-        scale_shape_manual(name="Prophylaxis regimen", labels=legendLabels(stratLabels[c(seq(1, 6), 10)]), values=c(16, 15, 17, 16, 15, 17, 16)) + 
+        scale_alpha_manual(guide=FALSE, breaks=c(FALSE, TRUE), values=c(1, 0.5)) + 
+        scale_color_manual(
+          name="Prophylaxis regimen", 
+          breaks=factor(sprintf("%s.%s", levels(data$strat), FALSE), levels=strat.isRepeat.levels),
+          labels=legendLabels(c(as.vector(stratLabels[10]), "_1", "_2", as.vector(stratLabels[1:6])), trailing=0),
+          values=c(
+            darkPurple, darkPurple, 
+            NA, NA, NA, NA, 
+            rep(c(darkBrown, darkOrange), each=6)
+          ), 
+          drop=FALSE
+        ) + 
+        scale_shape_manual(
+          name="Prophylaxis regimen", 
+          breaks=factor(sprintf("%s.%s", levels(data$strat), FALSE), levels=strat.isRepeat.levels),
+          labels=legendLabels(c(as.vector(stratLabels[10]), "_1", "_2", as.vector(stratLabels[1:6])), trailing=0),
+          values=c(
+            16, 16, 
+            16, 16, 16, 16, 
+            16, 21, 15, 22, 17, 24, 
+            16, 21, 15, 22, 17, 24
+          ), 
+          drop=FALSE
+        ) + 
         scale_x_discrete(labels=roundingLabels) + 
         geom_errorbar(
-            aes(ymin=frac.lower, ymax=frac.upper, x=rounding, color=strat, group=strat), 
+            aes(ymin=frac.lower, ymax=frac.upper, x=rounding, color=strat.isRepeat, group=strat.isRepeat), 
             width=.25, 
@@
         ) + 
-        geom_point(aes(y=frac.median, x=rounding, color=strat, shape=strat), position=position_dodge(.5), size=.75) +
+        geom_point(aes(y=frac.median, x=rounding, color=strat.isRepeat, shape=strat.isRepeat), position=position_dodge(.5), size=0.75, fill="white") +
         labs(x="Calendrical rounding", y="Preventable fraction") +
-        guides(color=guide_legend(keywidth=3, keyheight=1, ncol=3)) + 
         theme(
+            legend.position="bottom",
+            legend.key=element_rect(fill="white"),
+        ) +
+        guides(color=guide_legend(keywidth=1, keyheight=1.5, ncol=3))
+    dev.off()
+@
+
+<<coverageByRegionWithSliding, results='hide', warning=FALSE>>=
+    tikz(sprintf("%s/coverageByRegionRegimenWithSliding.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10)
+    data = unprotectedByCounty %>% 
+        filter(county %in% countiesForPlots, rounding==0, !grepl("county", strat)) %>%
+        mutate(strat=factor(strat, levels=c(levels(strat)[1], "_1", "_2", levels(strat)[2:4], levels(strat)[8:10])))
+
+    ggplot(data) +
+        theme_light(base_size=plotTextBaseSize) +
+        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
+        scale_color_manual(
+          name="Prophylaxis regimen", 
+          labels=legendLabels(c(as.vector(stratLabels[10]), "_1", "_2", as.vector(stratLabels[1:3]), as.vector(stratLabels[7:9]))),
+          values=c(
+            darkPurple, 
+            NA, NA, 
+            rep(c(darkBrown, darkGreen), each=3), darkPurple
+          ), 
+          drop=FALSE
+        ) + 
+        scale_shape_manual(
+          name="Prophylaxis regimen", 
+          labels=legendLabels(c(as.vector(stratLabels[10]), "_1", "_2", as.vector(stratLabels[1:3]), as.vector(stratLabels[7:9]))),
+          values=c(
+            16, 
+            16, 16, 
+            16, 15, 17, 
+            16, 15, 17
+          ), 
+          drop=FALSE
+        ) + 
+        geom_errorbar(
+            aes(ymin=frac.lower, ymax=frac.upper, x=county, color=strat, group=strat), 
+            width=.3, 
+            position=position_dodge(.5)
+        ) + 
+        geom_point(aes(y=frac.median, x=county, color=strat, shape=strat), position=position_dodge(.5), size=.75) +
+        labs(y="Preventable fraction") +
+        guides(color=guide_legend(keywidth=1, keyheight=1.5, ncol=3)) + 
+        scale_x_discrete(labels=countyLabels) + 
+        theme(
+            axis.title.x=element_blank(),
+            axis.ticks.x=element_blank(),
             legend.position="bottom"
@@
 @
-
-After we applied weekly, biweekly, and monthly rounding to start and end dates of our six alternative immunoprophylaxis regimens, we found that longer rounding intervals diminished the benefit of spatial analysis (Figure \ref{fig:coverageByRoundingRegimen}).
-
-With weekly rounding, our regimens were non-inferior to the AAP recommendation, and produced an increase in preventable fraction from AAP's \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) to \Sexpr{bestCaseCoverage(1)} (\Sexpr{bestCaseCoverageCI(1, level)}) statewide.
-
-Biweekly rounding yielded regimens similarly non-inferior to the AAP recommendation, with an increase in preventable fraction to \Sexpr{bestCaseCoverage(2)} (\Sexpr{bestCaseCoverageCI(2, level)}) statewide.
-
-However, with monthly rounding, the gains almost completely vanished, with preventable fraction not exceeding \Sexpr{bestCaseCoverage(4)} (\Sexpr{bestCaseCoverageCI(4, level)}).
-Furthermore, all our regimens with monthly rounding were non-superior to the AAP-recommended regimen in all regions.
-
-\begin{figure*}
-\begin{center}
-\input{\figuresDir/coverageByRoundingRegimen.tex}
-\caption[The effect of calendrical rounding of start and end of spatially adjusted RSV prophylaxis regimens on their performance]{The effect of calendrical rounding of start and end of spatially adjusted RSV prophylaxis regimens on their performance, showing that longer rounding intervals diminish the benefits of alternative regimens over the AAP-recommended regimen.
-Preventable fraction: the fraction of all RSV hospitalizations occurring while the prophylaxis regimen offers protection}
-\label{fig:coverageByRoundingRegimen}
-\end{center}
-\end{figure*}
-
-\columnbreak
-
-\paragraph{RSV season onset is slowly moving earlier}
 
@@
 @
-
-Our linear regression of median RSV season onset and offset over three-year periods indicates that season onset has slowly been drifting earlier (Figure \ref{fig:onsetOffsetByYear}), at a rate of \Sexpr{formatDrift(onsetByYear)} (\Sexpr{formatDriftCI(onsetByYear, level)}).
-It is unclear whether this is a part of a larger pattern, such as a cycle spanning decades.
-
-Season offset, on the other hand, has not been drifting earlier or later (\Sexpr{formatDriftCI(offsetByYear, level)}).
-
-\setcounter{figure}{6}
-\begin{figure}
-\begin{center}
-\input{\figuresDir/onsetOffsetByYear.tex}
-\caption{Annual variability in RSV season onset and offset in Connecticut}
-\label{fig:onsetOffsetByYear}
-\end{center}
-\end{figure}
-
-\paragraph{Temporally-adjusted prophylaxis regimens are non-superior to others}
-
-<<coverageByRegionWithSliding, results='hide', warning=FALSE>>=
-    tikz(sprintf("%s/coverageByRegionRegimenWithSliding.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10)
-    data = unprotectedByCounty %>% 
-        filter(county %in% countiesForPlots, rounding==0, !grepl("county", strat))
-
-    ggplot(data) +
-        theme_light(base_size=plotTextBaseSize) +
-        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
-        scale_color_manual(name="Prophylaxis regimen", labels=legendLabels(stratLabels[c(seq(1, 3), seq(7, 10))]), values=c(rep(c(darkBrown, darkGreen), each=3), darkPurple)) + 
-        scale_shape_manual(name="Prophylaxis regimen", labels=legendLabels(stratLabels[c(seq(1, 3), seq(7, 10))]), values=c(16, 15, 17, 16, 15, 17, 16)) + 
-        geom_errorbar(
-            aes(ymin=frac.lower, ymax=frac.upper, x=county, color=strat, group=strat), 
-            width=.3, 
-            position=position_dodge(.5)
-        ) + 
-        geom_point(aes(y=frac.median, x=county, color=strat, shape=strat), position=position_dodge(.5), size=.75) +
-        labs(y="Preventable fraction") +
-        guides(color=guide_legend(keywidth=3, keyheight=1, ncol=3)) + 
-        scale_x_discrete(labels=countyLabels) + 
-        theme(
-            axis.title.x=element_blank(),
-            axis.ticks.x=element_blank(),
-            legend.position="bottom"
-        )
-    dev.off()
-@
-
-Compared to our regional all-years analysis, the three regimens based on statewide recent-years analysis produced non-superior results everywhere, and inferior results in the low-RSV counties (Figure \ref{fig:coverageByRegionRegimenWithSliding}).
-
-Due to the non-superiority of regimens based on statewide recent-years analysis, we did not evaluate regimens based on regional recent-years data.
-
-\section{Discussion}
-
-\setcounter{figure}{7}
-\begin{figure*}
-\begin{center}
-\input{\figuresDir/coverageByRegionRegimenWithSliding.tex}
-\caption[Comparison of prophylaxis regimens based on all-years data to those based on recent-years data]{Comparison of prophylaxis regimens based on all-years data to those based on recent-years data, showing temporal analysis adds no benefit over spatial analysis alone.
-Preventable fraction: fraction of RSV hospitalizations occurring while the prophylaxis regimen offers protection}
-\label{fig:coverageByRegionRegimenWithSliding}
-\end{center}
-\end{figure*}
-
-\subsection{Conclusions}
-
-% TODO figure showing prophylaxis regimens on a calendar?
-
-Our analysis confirms the existence of regional variation of RSV season timing in Connecticut (defined by RSV season onset and offset) observable at the county level.
-
-We have also shown a misalignment between the prophylaxis schedule recommended by the AAP and the timing of the RSV season throughout Connecticut, with most counties' RSV season starting before protection from the first dose of prophylaxis takes hold, and ending before protection from the last dose wanes.
-This misalignment is particularly notable in Fairfield County, due to its early season onset.
-
-Our effort to optimize timing of the prophylaxis regimen (without changing its duration, and therefore its pharmaceutical cost) shows the possibility of a theoretical 1-2\% statewide decrease in RSV-associated hospitalizations among high-risk infants each year, primarily in counties with higher RSV burden (Fairfield, Hartford, and New Haven counties).
-
-The magnitude of that improvement wanes upon encountering practicalities of clinical practice guideline implementation.
-Nonetheless, with clinical practice guidelines localized at the county level, and the timing of prophylaxis adjusted in each county by less than a whole month from the current AAP guidelines, we still found the potential for $\sim$1\% statewide decrease in RSV-associated hospitalizations among high risk infants.
-
-The prophylaxis regimen with which we were able to attain this improvement is the one in which prophylaxis in each county is timed relative to the midpoint of the RSV season (rounded to two weeks) in that county, which simultaneously reduces unprotected cases early in the season and ineffective prophylaxis late in the season.
-
-Increasing complexity of practice guidelines carries with it increased cost of implementation, such as training of clinicians and other healthcare workers.
-It is therefore not apparent from our research alone that the potential benefits would outweigh the costs.
-
-Although we found a weak statewide trend in RSV season onset becoming earlier over time, further analysis did not yield any improvements to prophylaxis based on that trend.
-Since temporal variation in clinical guidelines would lead to a higher implementation burden than spatial variation, we see no reason to base RSV immunoprophylaxis clinical practice guidelines on temporal variation in RSV season timing.
-
-\subsection{Limitations}
-
-Although we were able to reach some conclusions about the impact of calendrical rounding on spatially adjusted prophylaxis regimens, ultimately our analysis is hamstrung by weekly aggregation of hospital admission data.
-To properly propose and evaluate any fine-tuning to RSV prophylaxis guidelines, we recommend use of daily data.
-
-Throughout, we assumed that RSV-associated hospitalizations are an unbiased estimate of RSV incidence in the general population; in doing so, we implicitly assumed that infectiousness and virulence of RSV are constant over time, for which we have no verification.
-
-Our model of palivizumab immunoprophylaxis assumes a protection period with a hard start at administration and a hard stop at 24 weeks post-administration; the physiologic response to monoclonal antibody immunoprophylaxis is actually tapered on both ends.
-
-Similarly, we assumed the protection by palivizumab is constant at 100\% throughout the protection period; however, not only is breakthrough RSV illness known to occur in patients on palivizumab, but it is an indication for discontinuing the prophylaxis regimen.
-
-In areas of Connecticut associated with a relatively high amount of interstate travel (such as urban centers near the state lines), our analysis --- by only considering residents of Connecticut --- likely underestimates RSV burden.
-
-Finally, towns that see substantial inter-county travel (for example, employment hubs near county lines) likely bias our regional analysis.
-
-\end{multicols}
-
-\phantomsection
-\addcontentsline{toc}{section}{Bibliography}
-\printbibliography[title={Bibliography}] % Print the bibliography, section title in curly brackets
-
-\end{document}

### 2019-03-27 Paper/RSVOptimization.rnw
Extracted figures and assorted other R code into separate files, to make life easier with overleaf
Structural changes based on Dan’s feedback

@@
 \usepackage[toc,page]{appendix}
-\renewcommand{\appendixpagename}{Supplemental Figures}
-\renewcommand{\appendixname}{Supplemental Figures}
+\renewcommand{\appendixpagename}{Supplements}
+\renewcommand{\appendixname}{Supplements}
 
@@
 \titlespacing*{\paragraph}{0pt}{3.25ex plus 1ex minus .2ex}{0em}
+\setcounter{secnumdepth}{4} % For paragraph numbering
 
@@
 
-% TODO "regional" -> county level
-% TODO is rounded to weeks primary analysis?
+% TODO make 1-week rounding primary analysis
 % TODO DPH acknowledgement
+% TODO transpose onset-offset plots
 
@@
 We also considered the effect of rounding the recommended start date of prophylaxis by week, biweekly period, or month and found that benefits of alternative regimens over the AAP-recommended regimen persisted with biweekly rounding, but not with monthly rounding.
-Our best-performing pragmatic alternative to the AAP guidelines was based on the regional RSV season midpoint with biweekly rounding.
+Our best-performing pragmatic alternative to the AAP guidelines was based on the country-level RSV season midpoint with biweekly rounding.
 In comparison to the AAP recommendation, whose preventable fraction is \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}), that alternative yielded improvement to \Sexpr{regionStrategyCoverage("all", "countyMiddle", 2)} (\Sexpr{regionStrategyCoverageCI("all", "countyMiddle", 2, level)}).
@@
 \begin{itemize}
-	\item To what extent does regional variability of RSV incidence in Connecticut impact the effectiveness of the AAP-recommended prophylaxis regimen?
+	\item To what extent does county-level variability of RSV incidence in Connecticut impact the effectiveness of the AAP-recommended prophylaxis regimen?
 	\item Would county- or state-specific alternative regimens increase the benefits of prophylaxis in comparison to the AAP-recommended regimen without increasing the total cost of the regimen?
@@
 
-We analyzed RSV data between \Sexpr{formatYear(startDate)} and \Sexpr{formatYear(endDate)} aggregated either to the state level or into four regions:
+We analyzed RSV data between \Sexpr{formatYear(startDate)} and \Sexpr{formatYear(endDate)} aggregated either to the state level or into four geographic areas:
 
 \begin{itemize}
-    \item One region for each of the counties with high population levels and high RSV case counts: Hartford County, Fairfield County, and New Haven County (Figure \ref{fig:map}).
-    \item One discontiguous region comprised of all remaining counties in Connecticut: \Sexpr{gsub("(.*), (.*)", "\\1, and \\2", paste(lowIncidenceCounties, collapse=", "))} (``low-population counties'').
+    \item One area for each of the counties with high population levels and high RSV case counts: Hartford County, Fairfield County, and New Haven County (Figure \ref{fig:map}).
+    \item One discontiguous area comprised of all remaining counties in Connecticut: \Sexpr{gsub("(.*), (.*)", "\\1, and \\2", paste(lowIncidenceCounties, collapse=", "))} (``low-population counties'').
 \end{itemize}
 
-We chose county-level aggregation with an eye towards using this data to inform clinical practice guidelines, which are typically based on administrative regions for reasons of administrative and implementation simplicity.
+We chose county-level aggregation with an eye towards using this data to inform clinical practice guidelines, which are typically based on administrative areas for reasons of administrative and implementation simplicity.
 
-We chose to aggregate low-population counties into a single region because our analysis in those counties individually yielded results with low statistical power.
+We chose to aggregate low-population counties into a single area because our analysis in those counties individually yielded results with low statistical power.
 
@@
 We defined season onset as the time when cumulative incidence rises beyond \Sexpr{seasonThreshold * 100}\% of the total cumulative incidence, and season offset as the time when cumulative incidence rises beyond \Sexpr{(1 - seasonThreshold) * 100}\% of the total cumulative incidence.
-We aggregated our data by surveillance week across all surveillance years, and estimated RSV season onset and offset for each region.
+We aggregated our data by surveillance week across all surveillance years, and estimated RSV season onset and offset for each county.
 
@@
 For simplicity, we assumed that protection by palivizumab begins on November 15th.
-    \item \textbf{By statewide all-years onset}: prophylaxis administration begins at statewide all-years median RSV season onset.
-\item \textbf{By statewide all-years midpoint}: prophylaxis administration begins 12 weeks before the average of the (statewide all-years median) season onset and offset.
-    \item \textbf{By statewide all-years offset}: prophylaxis administration begins 24 weeks before the (statewide all-years median) RSV season offset. 
-    \item \textbf{By regional all-years onset}: prophylaxis administration begins at regional (county-wide, or --- in the case of low-population counties --- low-population-region-wide) all-years median RSV season onset.
-    \item \textbf{By regional all-years midpoint}: prophylaxis administration begins 12 weeks before the average of the (regional all-years median) RSV season onset and offset. 
-    \item \textbf{By regional all-years offset}: prophylaxis administration begins 24 weeks before the (regional all-years median) RSV season offset. 
+    \item \textbf{By statewide onset}: prophylaxis administration begins at statewide median RSV season onset. 
+    \item \textbf{By statewide midpoint}: prophylaxis administration begins 12 weeks before the average of the statewide median season onset and offset. 
+    \item \textbf{By statewide offset}: prophylaxis administration begins 24 weeks before the statewide median RSV season offset. 
+    \item \textbf{By county-level onset}: prophylaxis administration begins at county-level median RSV season onset.
+    \item \textbf{By county-level midpoint}: prophylaxis administration begins 12 weeks before the average of the county-level median RSV season onset and offset. 
+    \item \textbf{By county-level offset}: prophylaxis administration begins 24 weeks before the county-level median RSV season offset. 
 \end{itemize}
@@
 
-We began our temporal analysis by estimating onset and offset for each three-year period, using the same penalized spline GAM as for the all-years analysis, producing --- as before --- statewide and regional estimates of \Sexpr{seasonThreshold * 100}\% onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset.
+We began our temporal analysis by estimating onset and offset for each three-year period, using the same penalized spline GAM as for the all-years analysis, producing --- as before --- statewide and county-level estimates of \Sexpr{seasonThreshold * 100}\% onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset.
 To evaluate year-to-year variation in RSV season onset and offset we modeled median RSV three-year onset and offset against time using simple linear regression.
@@
 \input{\figuresDir/seasonByRegion.tex}
-\caption{Regional variation in RSV season onset and offset in Connecticut}
+\caption{County-level variation in RSV season onset and offset in Connecticut}
 \label{fig:seasonByRegion}
@@
 \input{\figuresDir/coverageByRegionAAP.tex}
-\caption[Regional variation in the fraction of RSV hospitalizations occurring while the AAP-recommended RSV prophylaxis is active]{Regional variation in the fraction of RSV hospitalizations occurring while protection by palivizumab --- administered per the AAP guidelines ---  is active}
+\caption[County-level variation in the fraction of RSV hospitalizations occurring while the AAP-recommended RSV prophylaxis is active]{County-level variation in the fraction of RSV hospitalizations occurring while protection by palivizumab --- administered per the AAP guidelines ---  is active}
 \label{fig:coverageByRegionAAP}
@@
 
-This is caused by temporal misalignment between the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each region) and the timing of the AAP-recommended prophylaxis regimen (Figure \ref{fig:coverageByRegionAAPInsight}).
+This is caused by temporal misalignment between the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each county) and the timing of the AAP-recommended prophylaxis regimen (Figure \ref{fig:coverageByRegionAAPInsight}).
 Fairfield county, owing to its early season onset, sees disproportionately more cases before prophylaxis administration begins; on the other hand, the low-population counties, owing to their late season onset and relatively shorter RSV seasons, see almost all of their RSV cases within the prophylaxis window.
@@
 \input{\figuresDir/coverageByRegionAAPInsight.tex}
-\caption[Regional variation in the relative timing of the RSV season in Connecticut and the AAP-recommended prophylaxis regimen]{Regional variation in the relative timing of the RSV season in Connecticut and the AAP-recommended prophylaxis regimen, showing the gap between season onset and prophylaxis start date, notable particularly in Fairfield county}
+\caption[County-level variation in the relative timing of the RSV season in Connecticut and the AAP-recommended prophylaxis regimen]{County-level variation in the relative timing of the RSV season in Connecticut and the AAP-recommended prophylaxis regimen, showing the gap between season onset and prophylaxis start date, notable particularly in Fairfield county}
 \label{fig:coverageByRegionAAPInsight}
@@
 \input{\figuresDir/coverageByRegionRegimen.tex}
-\caption[Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen]{Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen, showing statewide superiority and regional non-inferiority of spatially adjusted regimens.
+\caption[Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen]{Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen, showing statewide superiority and county-level non-inferiority of spatially adjusted regimens.
 Preventable fraction: the fraction of all RSV-associated hospitalizations occurring while the prophylaxis regimen provides protection}
@@
 
-Based on all-years data, the six spatially-adjusted prophylaxis regimens (with no rounding of prophylaxis dates), yield results in all regions that are as good or better than the AAP guidelines.
+The six spatially-adjusted prophylaxis regimens (with no rounding of prophylaxis dates), yield results in all counties that are as good or better than the AAP guidelines.
 (Figure \ref{fig:coverageByRegionRegimen}).
@@
 The alternative regimen based on statewide onset yields the smallest increase, to \Sexpr{regionStrategyCoverage("all", "stateOnset", 0)} (\Sexpr{regionStrategyCoverageCI("all", "stateOnset", 0, level)}); other alternative regimens yield similar results.
-Most of the increase comes from Hartford county, where the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", 0, level)}), whereas the alternative regimen based on all-years regional offset generates the smallest increase, to \Sexpr{regionStrategyCoverage("Hartford", "countyOffset", 0)} (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", 0, level)}); other alternative regimens are comparable.
-In every region, all alternative regimens based on all-years analysis are non-inferior to the AAP guidelines and non-superior to each other.
+Most of the increase comes from Hartford county, where the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", 0, level)}), whereas the alternative regimen based on county-level offset generates the smallest increase, to \Sexpr{regionStrategyCoverage("Hartford", "countyOffset", 0)} (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", 0, level)}); other alternative regimens are comparable.
+In every county, all alternative regimens are non-inferior to the AAP guidelines and non-superior to each other.
 
-\paragraph{Calendrical rounding rapidly diminishes gains over the AAP-recommended regimen}
+\paragraph{Additional results}
 
-\begin{figure}
-\begin{center}
-\input{\figuresDir/coverageByRoundingRegimen.tex}
-\caption[The effect of calendrical rounding of start and end of spatially adjusted RSV prophylaxis regimens on their performance]{The effect of calendrical rounding of start and end of spatially adjusted RSV prophylaxis regimens on their performance, showing that longer rounding intervals diminish the benefits of alternative regimens over the AAP-recommended regimen.
-Preventable fraction: the fraction of all RSV hospitalizations occurring while the prophylaxis regimen offers protection.
-Hollow plot markers ($\raisebox{1pt}{\Circle}$, $\square$, and $\triangle$) denote a prophylaxis strategy which, as a result of rounding, is identical to another, and therefore does not provide additional insights.}
-\label{fig:coverageByRoundingRegimen}
-\end{center}
-\end{figure}
-
-After we applied weekly, biweekly, and monthly rounding to start and end dates of our six alternative immunoprophylaxis regimens, we found that longer rounding intervals diminished the benefit of spatial analysis (Figure \ref{fig:coverageByRoundingRegimen}).
-With weekly rounding, our regimens were non-inferior to the AAP recommendation, and produced an increase in preventable fraction from AAP's \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) to \Sexpr{bestCaseCoverage(1)} (\Sexpr{bestCaseCoverageCI(1, level)}) statewide.
-Biweekly rounding yielded regimens similarly non-inferior to the AAP recommendation, with an increase in preventable fraction to \Sexpr{bestCaseCoverage(2)} (\Sexpr{bestCaseCoverageCI(2, level)}) statewide.
-However, with monthly rounding, the gains almost completely vanished, with preventable fraction not exceeding \Sexpr{bestCaseCoverage(4)} (\Sexpr{bestCaseCoverageCI(4, level)}).
-Furthermore, all our regimens with monthly rounding were non-superior to the AAP-recommended regimen in all regions.
-
-\paragraph{RSV season onset is slowly moving earlier}
-
-Our linear regression of median RSV season onset and offset over three-year periods indicates that season onset has slowly been drifting earlier (Supplemental figure \ref{fig:onsetOffsetByYear}), at a rate of \Sexpr{formatDrift(onsetByYear)} (\Sexpr{formatDriftCI(onsetByYear, level)}).
-It is unclear whether this is a part of a larger pattern, such as a cycle spanning decades.
-Season offset, on the other hand, has not been drifting earlier or later (\Sexpr{formatDriftCI(offsetByYear, level)}).
-
-\paragraph{Temporally-adjusted prophylaxis regimens are non-superior to others}
-
-\begin{figure}
-\begin{center}
-\input{\figuresDir/coverageByRegionRegimenWithSliding.tex}
-\caption[Comparison of prophylaxis regimens based on all-years data to those based on recent-years data]{Comparison of prophylaxis regimens based on all-years data to those based on recent-years data, showing temporal analysis adds no benefit over spatial analysis alone.
-Preventable fraction: fraction of RSV hospitalizations occurring while the prophylaxis regimen offers protection}
-\label{fig:coverageByRegionRegimenWithSliding}
-\end{center}
-\end{figure}
-
-Compared to our regional all-years analysis, the three regimens based on statewide recent-years analysis produced non-superior results everywhere, and inferior results in the low-population counties (Figure \ref{fig:coverageByRegionRegimenWithSliding}).
-Due to the non-superiority of regimens based on statewide recent-years analysis, we did not evaluate regimens based on regional recent-years data.
+We also applied biweekly and monthly rounding to the start and end dates of our six alternative immunoprophylaxis regimens, and found that doing so diminished or erased the benefits.
+(Supplemental result \ref{sresult:rounding}).
+Finally, we analyzed long-term trends in the RSV season onset and offset and found that the season onset may be moving earlier (Supplemental result \ref{sresult:seasonDrift}), but that accounting for that drift did not yield a significant further increase in preventable RSV cases (Supplemental result \ref{sresult:temporalAdjustment}).
 
@@
 
-Our analysis confirms the existence of regional variation of RSV season timing in Connecticut (defined by RSV season onset and offset) observable at the county level.
+Our analysis confirms the existence of county-level variation of RSV season timing in Connecticut (defined by RSV season onset and offset) observable at the county level.
 We have also shown a misalignment between the prophylaxis schedule recommended by the AAP and the timing of the RSV season throughout Connecticut, with most counties' RSV season starting before protection from the first dose of prophylaxis takes hold, and ending before protection from the last dose wanes.
@@
 
-Although we were able to reach some conclusions about the impact of calendrical rounding on spatially adjusted prophylaxis regimens, ultimately our analysis is hamstrung by weekly aggregation of hospital admission data.
-To properly propose and evaluate any fine-tuning to RSV prophylaxis guidelines, we recommend use of daily data.
+The use of data aggregated by epidemiological weeks created a challenge for both our analysis and the interpretation of our results.
+In practice, clinical guidelines are typically expressed in terms of calendar weeks or months; as a result, our analysis contains errors of up to $\pm 0.5$ weeks when applied to the more natural calendar boundaries.
+Ideally, our analysis should be repeated with daily case counts aggregated into weeks and months that match week and month boundaries used in clinical guidelines.
 
@@
 In areas of Connecticut associated with a relatively high amount of interstate travel (such as urban centers near the state lines), our analysis --- by only considering residents of Connecticut --- likely underestimates RSV burden.
-Finally, towns that see substantial inter-county travel (for example, employment hubs near county lines) likely bias our regional analysis.
+Finally, towns that see substantial inter-county travel (for example, employment hubs near county lines) likely bias our county-level analysis.
 
@@
 \setcounter{figure}{0}
+\renewcommand{\theparagraph}{S\arabic{paragraph}}
+\titleformat{\paragraph}{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
 
-\label{supplement:figures}
+\section{Supplemental results}
+
+\paragraph{County-level recommendations are most useful when rounded to the nearest 1- or 2-week period}
+\label{sresult:rounding}
+
+\begin{figure}
+\begin{center}
+\input{\figuresDir/coverageByRoundingRegimen.tex}
+\caption[The effect of calendrical rounding of start and end of spatially adjusted RSV prophylaxis regimens on their performance]{The effect of calendrical rounding of start and end of spatially adjusted RSV prophylaxis regimens on their performance, showing that longer rounding intervals diminish the benefits of alternative regimens over the AAP-recommended regimen.
+Preventable fraction: the fraction of all RSV hospitalizations occurring while the prophylaxis regimen offers protection.
+Hollow plot markers ($\raisebox{1pt}{\Circle}$, $\square$, and $\triangle$) denote a prophylaxis strategy which, as a result of rounding, is identical to another, and therefore does not provide additional insights.}
+\label{fig:coverageByRoundingRegimen}
+\end{center}
+\end{figure}
+
+After we applied weekly, biweekly, and monthly rounding to start and end dates of our six alternative immunoprophylaxis regimens, we found that longer rounding intervals diminished the benefit of spatial analysis (Supplemental figure \ref{fig:coverageByRoundingRegimen}).
+With weekly rounding, our regimens were non-inferior to the AAP recommendation, and produced an increase in preventable fraction from AAP's \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) to \Sexpr{bestCaseCoverage(1)} (\Sexpr{bestCaseCoverageCI(1, level)}) statewide.
+Biweekly rounding yielded regimens similarly non-inferior to the AAP recommendation, with an increase in preventable fraction to \Sexpr{bestCaseCoverage(2)} (\Sexpr{bestCaseCoverageCI(2, level)}) statewide.
+However, with monthly rounding, the gains almost completely vanished, with preventable fraction not exceeding \Sexpr{bestCaseCoverage(4)} (\Sexpr{bestCaseCoverageCI(4, level)}).
+Furthermore, all our regimens with monthly rounding were non-superior to the AAP-recommended regimen in all counties.
+
+\paragraph{RSV season onset is slowly moving earlier}
+\label{sresult:seasonDrift}
 
@@
 
+Our linear regression of median RSV season onset and offset over three-year periods indicates that season onset has slowly been drifting earlier (Supplemental figure \ref{fig:onsetOffsetByYear}), at a rate of \Sexpr{formatDrift(onsetByYear)} (\Sexpr{formatDriftCI(onsetByYear, level)}).
+It is unclear whether this is a part of a larger pattern, such as a cycle spanning decades.
+Season offset, on the other hand, has not been drifting earlier or later (\Sexpr{formatDriftCI(offsetByYear, level)}).
+
+\paragraph{Temporally-adjusted prophylaxis regimens are non-superior to others}
+\label{sresult:temporalAdjustment}
+
+\begin{figure}
+\begin{center}
+\input{\figuresDir/coverageByRegionRegimenWithSliding.tex}
+\caption[Comparison of prophylaxis regimens based on all-years data to those based on recent-years data]{Comparison of prophylaxis regimens based on all-years data to those based on recent-years data, showing temporal analysis adds no benefit over spatial analysis alone.
+Preventable fraction: fraction of RSV hospitalizations occurring while the prophylaxis regimen offers protection}
+\label{fig:coverageByRegionRegimenWithSliding}
+\end{center}
+\end{figure}
+
+Compared to our county-level all-years analysis, the three regimens based on statewide recent-years analysis produced non-superior results everywhere, and inferior results in the low-population counties (Supplemental figure \ref{fig:coverageByRegionRegimenWithSliding}).
+Due to the non-superiority of regimens based on statewide recent-years analysis, we did not evaluate regimens based on county-level recent-years data.
+
 \end{appendices}

### 2019-03-27 Paper/RSVOptimization.rnw
More structural changes based on Dan’s feedback (supplemental methods)

@@
 \titleformat{\section}{\normalfont\large\bfseries\scshape}{\thesection}{1em}{}
-\titleformat{\subsection}{\normalfont\normalsize\bfseries\scshape}{}{0em}{}
-\titleformat{\paragraph}{\normalfont\normalsize\bfseries}{}{0em}{}
-\titlespacing*{\paragraph}{0pt}{3.25ex plus 1ex minus .2ex}{0em}
-\setcounter{secnumdepth}{4} % For paragraph numbering
+\titleformat{\subsection}{\normalfont\normalsize\bfseries}{}{0em}{}
+\setcounter{secnumdepth}{3}
 
@@
 In all these regimens, prophylaxis consists of five monthly doses of palivizumab, and protection is assumed to last 24 weeks from the first dose.
+We rounded each alternative regimen to the nearest week, to more closely reflect how prophylaxis guidelines might be implemented in practice.
+(Supplemental methods \ref{smethod:rounding}.)
+
 We defined the fraction of all RSV cases that is preventable by a prophylaxis regimen (``preventable fraction'') to be the ratio of
@@
 
-\subsection{Accommodating implementation complexity}
+\subsection{Additional analyses}
 
-Keeping in mind implementation constraints of clinical practice guidelines, we performed three additional variants of our spatial analysis:
+In addition to 1-week rounding of our alternative prophylaxis schedules, we calculated 2- and 4-week rounding, to assess the impact of calendrical rounding on prophylaxis performance.
+(Supplemental methods \ref{smethod:rounding}.)
 
-\begin{itemize}
-    \item \textbf{Weekly rounding}: prophylaxis start and end date rounded to the nearest calendar week,
-    \item \textbf{Biweekly rounding}: prophylaxis start and end date rounded to the nearest two-week calendar period, with periods chosen to approximately align with November 15th, and
-    \item \textbf{Monthly rounding}: prophylaxis start and end date rounded to the nearest four-week calendar periods, with periods chosen to approximately align with November 15th.
-\end{itemize}
-
-In each variant, we again estimated the preventable fraction of all 6 alternative regimens.
-
-\subsection{Temporal aggregation of RSV incidence}
-
-Our analysis thus far assumed that RSV seasons are similar year-to-year.
-To analyze the effects on prophylaxis regimens of year-to-year variation between RSV seasons, we chose to aggregate our data into (overlapping) periods of three consecutive years --- in order to maintain a higher level of statistical power, as well as to limit the impact of short-term variation on our results.
-This gave us \Sexpr{year(endDate) - year(startDate) - 1} three-year periods, with the \Sexpr{formatYear(startDate + 2*365)} period covering surveillance years \Sexpr{formatYear(startDate)} through \Sexpr{formatYear(startDate + 2*365)}, and the \Sexpr{formatYear(endDate)} period covering \Sexpr{formatYear(endDate - 2*365)} through \Sexpr{formatYear(endDate)}.
-
-We began our temporal analysis by estimating onset and offset for each three-year period, using the same penalized spline GAM as for the all-years analysis, producing --- as before --- statewide and county-level estimates of \Sexpr{seasonThreshold * 100}\% onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset.
-To evaluate year-to-year variation in RSV season onset and offset we modeled median RSV three-year onset and offset against time using simple linear regression.
-We did not analyze any other long-term patterns, such as cyclicity.
-
-\subsection{Evaluating alternative recent-years prophylaxis regimens}
-
-Finally, to assess the impact of any long-term trends in RSV season timing on prophylaxis, we evaluated three additional prophylaxis regimens.
-Here, each prophylaxis regimen is adjusted annually based on RSV data from the preceding three-year period:
-
-\begin{itemize}
-    \item \textbf{By statewide recent-years onset}: prophylaxis administration in a given year begins at statewide median onset from the preceding three years. 
-    \item \textbf{By statewide recent-years midpoint}: prophylaxis administration begins 12 weeks before the average of the (statewide median) onset and offset from the preceding three years. 
-    \item \textbf{By statewide recent-years offset}: prophylaxis administration in a given year begins 24 weeks before the (statewide median) offset from the preceding three years.
-\end{itemize}
-
-We then compared those regimens to the one recommended by the AAP and to the six spatially adjusted alternatives (with no calendrical rounding) discussed above.
-As before, these alternative regimens involved five monthly doses of palivizumab giving 24 weeks of protection.
-
-% \uselengthunit{in}\printlength{\columnwidth}
-% column width = 3.20929 in
+To analyze the effects of year-to-year variation between RSV seasons, we performed similar analysis, but with prophylaxis start in a given year being determined by the RSV timing of three prior years, rather than all years.
+(Supplemental methods \ref{smethod:seasonDrift} and \ref{smethod:temporalAdjustment}.)
 
@@
 
-\paragraph{Timing of the RSV season varies within the state}
+\subsection{Timing of the RSV season varies within the state}
 
@@
 
-\paragraph{The AAP guidelines perform best in low-population counties and worst in Fairfield county}
+\subsection{The AAP guidelines perform best in low-population counties and worst in Fairfield county}
 
@@
 
-\paragraph{Without calendrical rounding, spatially adjusted regimens are superior to the AAP recommendations}
+\subsection{Without calendrical rounding, spatially adjusted regimens are superior to the AAP recommendations}
 
@@
 
-\paragraph{Additional results}
+\subsection{Additional results}
 
@@
 \setcounter{figure}{0}
-\renewcommand{\theparagraph}{S\arabic{paragraph}}
-\titleformat{\paragraph}{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
+\renewcommand{\thesubsection}{S\arabic{section}.\arabic{subsection}}
+\titleformat{\subsection}{\normalfont\normalsize\bfseries}{\thesubsection}{1em}{}
+
+\section{Supplemental methods}
+
+\subsection{Accommodating implementation complexity}
+\label{smethod:rounding}
+
+We performed three variants of our spatial analysis:
+
+\begin{itemize}
+    \item \textbf{With weekly rounding}: prophylaxis start and end date rounded to the nearest calendar week,
+    \item \textbf{With biweekly rounding}: prophylaxis start and end date rounded to the nearest two-week calendar period, with periods chosen to approximately align with November 15th, and
+    \item \textbf{With monthly rounding}: prophylaxis start and end date rounded to the nearest four-week calendar periods, with periods chosen to approximately align with November 15th.
+\end{itemize}
+
+Alignment of rounding periods to November 15th was done to make our regimens more clearly comparable to the AAP-recommended regimen, whose (average) start is also November 15th.
+This alignment of rounding periods was only approximate because we were working with data aggregated by epidemiological weeks, which aren't aligned to calendar months.
+
+\subsection{Temporal aggregation of RSV incidence}
+\label{smethod:seasonDrift}
+
+To analyze the effects on prophylaxis regimens of year-to-year variation between RSV seasons, we aggregated our data into (overlapping) periods of three consecutive years (in order to maintain a higher level of statistical power, as well as to limit the impact of short-term variation on our results).
+This gave us \Sexpr{year(endDate) - year(startDate) - 1} three-year periods, with the \Sexpr{formatYear(startDate + 2*365)} period covering surveillance years \Sexpr{formatYear(startDate)} through \Sexpr{formatYear(startDate + 2*365)}, and the \Sexpr{formatYear(endDate)} period covering \Sexpr{formatYear(endDate - 2*365)} through \Sexpr{formatYear(endDate)}.
+
+We then estimated the onset and offset for each three-year period, using the same penalized spline GAM as for the all-years analysis, producing --- as before --- statewide and county-level estimates of \Sexpr{seasonThreshold * 100}\% onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset.
+To evaluate year-to-year variation in RSV season onset and offset we modeled median RSV three-year onset and offset against time using simple linear regression.
+We did not analyze any other long-term patterns, such as cyclicity.
+
+\subsection{Evaluating alternative recent-years prophylaxis regimens}
+\label{smethod:temporalAdjustment}
+
+Finally, to assess the impact of any long-term trends in RSV season timing on prophylaxis, we evaluated three additional prophylaxis regimens.
+Here, each prophylaxis regimen is adjusted annually based on RSV data from the preceding three-year period:
+
+\begin{itemize}
+    \item \textbf{By statewide recent-years onset}: prophylaxis administration in a given year begins at statewide median onset from the preceding three years. 
+    \item \textbf{By statewide recent-years midpoint}: prophylaxis administration begins 12 weeks before the average of the (statewide median) onset and offset from the preceding three years. 
+    \item \textbf{By statewide recent-years offset}: prophylaxis administration in a given year begins 24 weeks before the (statewide median) offset from the preceding three years.
+\end{itemize}
+
+We then compared those regimens to the one recommended by the AAP and to the six spatially adjusted alternatives (with no calendrical rounding) from our main analysis.
+As in the main analysis, these alternative regimens involved five monthly doses of palivizumab giving 24 weeks of protection.
 
@@
 
-\paragraph{County-level recommendations are most useful when rounded to the nearest 1- or 2-week period}
+\subsection{County-level recommendations are most useful when rounded to the nearest 1- or 2-week period}
 \label{sresult:rounding}
@@
 
-\paragraph{RSV season onset is slowly moving earlier}
+\subsection{RSV season onset is slowly moving earlier}
 \label{sresult:seasonDrift}
@@
 
-\paragraph{Temporally-adjusted prophylaxis regimens are non-superior to others}
+\subsection{Temporally-adjusted prophylaxis regimens are non-superior to others}
 \label{sresult:temporalAdjustment}

### 2019-03-27 Paper/Figures.Rnw
Transposed onset-offset plots

@@
     tikz(sprintf("%s/seasonByRegion.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
+    onOffLevels = c("onset", "offset")
+
     data = thresholdsByCounty %>% 
@@
         rename(variable=variable_1, pctile=variable_2) %>%
-        mutate(variable=factor(variable, levels=c("offset", "onset"))) %>%
+        mutate(variable=factor(variable, levels=onOffLevels)) %>%
         cast(county + variable ~ pctile)
@@
     onsetOffsetRange = 6 # weeks
-    onsetOffsetAdjust = data.frame(variable=c("onset", "offset"), nudge=c(-1, -2))
+    onsetOffsetAdjust = data.frame(variable=factor(c("onset", "offset"), levels=onOffLevels), nudge=c(-1, -2))
 
@@
 
-    monthBarX = 0.5 + (0.5 - 5.5) * 0.04
+    monthBarY = 0.7 + (0.5 - 5.5) * 0.04
     monthGrob = function(month) {
@@
         theme_light(base_size=plotTextBaseSize) +
-        geom_errorbar(aes(ymin=lower, ymax=upper, x=county), width=.1) + 
-        geom_point(aes(y=median, x=county), size=.75) + 
-        geom_blank(data=limits, aes(y=min)) + 
-        geom_blank(data=limits, aes(y=max)) + 
-        labs(aes(x=variable)) +
-        facet_wrap(~variable, ncol=1, scales="free_y", labeller=onsetOffsetLabeller) +
-        scale_x_discrete(labels=countyLabels) + 
-        scale_y_continuous(minor_breaks=seq(1, 52), breaks=epiWeekBreaks, labels=rep("\\qquad\\qquad", length(epiWeekBreaks)), sec.axis=sec_axis(trans=~., breaks=seq(1, 52))) + 
-        labs(y=NULL) + 
-        annotation_custom(monthGrob(4), xmin=monthBarX, xmax=monthBarX, ymin=monthBoundaries$mid[4], ymax=monthBoundaries$mid[4]) + 
-        annotation_custom(monthGrob(5), xmin=monthBarX, xmax=monthBarX, ymin=monthBoundaries$mid[5], ymax=monthBoundaries$mid[5]) + 
-        annotation_custom(monthGrob(9), xmin=monthBarX, xmax=monthBarX, ymin=monthBoundaries$mid[9], ymax=monthBoundaries$mid[9]) + 
-        annotation_custom(monthGrob(10), xmin=monthBarX, xmax=monthBarX, ymin=monthBoundaries$mid[10], ymax=monthBoundaries$mid[10]) + 
+        geom_errorbarh(aes(xmin=lower, xmax=upper, y=county), height=.1) + 
+        geom_point(aes(x=median, y=county), size=.75) + 
+        geom_blank(data=limits, aes(x=min)) + 
+        geom_blank(data=limits, aes(x=max)) + 
+        labs(aes(y=variable)) +
+        facet_wrap(~variable, ncol=2, scales="free_x", labeller=onsetOffsetLabeller) +
+        scale_y_discrete(labels=countyLabels, limits=rev(unique(data$county))) + 
+        scale_x_continuous(breaks=seq(0, 52, 2), minor_breaks=seq(1, 52)) + 
+        labs(x=NULL) + 
+        annotation_custom(monthGrob(4), ymin=monthBarY, ymax=monthBarY, xmin=monthBoundaries$mid[4], xmax=monthBoundaries$mid[4]) + 
+        annotation_custom(monthGrob(5), ymin=monthBarY, ymax=monthBarY, xmin=monthBoundaries$mid[5], xmax=monthBoundaries$mid[5]) + 
+        annotation_custom(monthGrob(9), ymin=monthBarY, ymax=monthBarY, xmin=monthBoundaries$mid[9], xmax=monthBoundaries$mid[9]) + 
+        annotation_custom(monthGrob(10), ymin=monthBarY, ymax=monthBarY, xmin=monthBoundaries$mid[10], xmax=monthBoundaries$mid[10]) + 
         theme(
-            panel.grid.major.y=element_blank(),
-            panel.grid.minor.y=element_line(size=rel(2)),
-            axis.title.x=element_blank(),
-            axis.ticks.x=element_blank(),
-            axis.text.x=element_text(angle=30, hjust=1)
+            panel.grid.major.x=element_line(size=rel(2)),
+            panel.grid.minor.x=element_line(size=rel(2)),
+            axis.title.y=element_blank(),
+            axis.ticks.y=element_blank(),
+            axis.text.y=element_text(hjust=1)
         )
@@
         rename(variable=variable_1, pctile=variable_2) %>%
-        mutate(variable=factor(variable, levels=c("offset", "onset"))) %>%
+        mutate(variable=factor(variable, levels=onOffLevels)) %>%
         cast(epiyear + variable ~ pctile)
 
-    onsetOffsetAdjust = data.frame(variable=c("onset", "offset"), nudge=c(0, -1))
+    onsetOffsetAdjust = data.frame(variable=factor(c("onset", "offset"), levels=onOffLevels), nudge=c(0, -1))
 
@@
 
-    monthBarX = 1998.5 + (1998.5 - 2013.5) * 0.04
+    monthBarY = 1998.5 + (1998.5 - 2013.5) * 0.04
 
@@
         theme_light(base_size=plotTextBaseSize) +
-        geom_errorbar(aes(ymin=lower, ymax=upper, x=epiyear), width=.3) + 
-        geom_point(aes(y=median, x=epiyear), size=.75) +
-        geom_blank(data=limits, aes(y=min)) + 
-        geom_blank(data=limits, aes(y=max)) + 
-        facet_wrap(~variable, ncol=1, scales="free_y", labeller=onsetOffsetLabeller) +
-        scale_x_continuous(breaks=seq(1990, 2020, by=5)) +
-        scale_y_continuous(minor_breaks=seq(1, 52), breaks=epiWeekBreaks, labels=rep("\\qquad\\qquad", length(epiWeekBreaks)), sec.axis=sec_axis(trans=~., breaks=seq(1, 52))) + 
-        annotation_custom(monthGrob(4), xmin=monthBarX, xmax=monthBarX, ymin=monthBoundaries$mid[4], ymax=monthBoundaries$mid[4]) + 
-        annotation_custom(monthGrob(5), xmin=monthBarX, xmax=monthBarX, ymin=monthBoundaries$mid[5], ymax=monthBoundaries$mid[5]) + 
-        annotation_custom(monthGrob(9), xmin=monthBarX, xmax=monthBarX, ymin=monthBoundaries$mid[9], ymax=monthBoundaries$mid[9]) + 
-        annotation_custom(monthGrob(10), xmin=monthBarX, xmax=monthBarX, ymin=monthBoundaries$mid[10], ymax=monthBoundaries$mid[10]) + 
-        labs(y=NULL) + 
+        geom_errorbarh(aes(xmin=lower, xmax=upper, y=epiyear), height=.3) + 
+        geom_point(aes(x=median, y=epiyear), size=.75) +
+        geom_blank(data=limits, aes(x=min)) + 
+        geom_blank(data=limits, aes(x=max)) + 
+        facet_wrap(~variable, ncol=2, scales="free_x", labeller=onsetOffsetLabeller) +
+        scale_y_continuous(breaks=seq(1990, 2020, by=5)) +
+        scale_x_continuous(breaks=seq(0, 52, 2), minor_breaks=seq(1, 52)) + 
+        annotation_custom(monthGrob(4), ymin=monthBarY, ymax=monthBarY, xmin=monthBoundaries$mid[4], xmax=monthBoundaries$mid[4]) + 
+        annotation_custom(monthGrob(5), ymin=monthBarY, ymax=monthBarY, xmin=monthBoundaries$mid[5], xmax=monthBoundaries$mid[5]) + 
+        annotation_custom(monthGrob(9), ymin=monthBarY, ymax=monthBarY, xmin=monthBoundaries$mid[9], xmax=monthBoundaries$mid[9]) + 
+        annotation_custom(monthGrob(10), ymin=monthBarY, ymax=monthBarY, xmin=monthBoundaries$mid[10], xmax=monthBoundaries$mid[10]) + 
+        labs(x=NULL) + 
         theme(
-            panel.grid.major.y=element_blank(),
-            panel.grid.minor.y=element_line(size=rel(2)),
-            axis.title.x=element_blank()
+            panel.grid.major.x=element_blank(),
+            panel.grid.minor.x=element_line(size=rel(2)),
+            axis.title.y=element_blank()
         )

### 2019-03-27 Paper/Figures.Rnw
Changed map to refer to county population

@@
         theme_light(base_size=plotTextBaseSize) +
-        scale_fill_manual(labels=legendLabels(c("$<$50", "$>$100")), values=c(lightBlue, darkBlue)) +
+        scale_fill_manual(labels=legendLabels(c("$<300,000$", "$>900,000$")), values=c(lightBlue, darkBlue)) +
         geom_polygon(aes(fill=highRSV, group=group), color="white", size=.5) +
@@
         coord_map() + 
-        labs(fill="Average RSV-associated hospitalizations per year") +
+        labs(fill="Total county population in 2010 census") +
         theme(

### 2019-03-27 Paper/Paper.R
More low-pop renaming

@@ -140,7 +140,7 @@ countyLabels = c(
   `New Haven` = "New Haven county",
   `Fairfield` = "Fairfield county",
   `Hartford` = "Hartford county",
-  `lowIncidence` = "Low-RSV counties"
+  `lowIncidence` = "Low-population counties"
 )
 
 # .01 to let minor gridlines show through
@@ -196,7 +196,7 @@ darkPurple = "#6a3d9a"
 lightBrown = "#E3C0AC"
 darkBrown = "#b15928"
 
-# Counties which we plot (so, not individual low-incidence counties)
+# Counties which we plot (so, not individual low-population counties)
 countiesForPlots = thresholdsByCounty$county[!thresholdsByCounty$county %in% lowIncidenceCounties]
 
 # Use this to draw legend indicators that don't take up the entire height of the key

### 2019-03-27 Paper/Figures.Rnw
Plot tweaks

@@
             panel.grid.minor.x=element_line(size=rel(2)),
+            panel.grid.major.y=element_blank(),
             axis.title.y=element_blank(),
@@
         geom_point(aes(y=frac.median, x=county), size=.75) + 
-        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
-        scale_x_discrete(labels=countyLabels) + 
+        scale_y_continuous(labels=latexPercent, limits=c(0.88, 1), breaks=seq(0, 1, by=0.04), expand=c(0.05, 0)) +
+        scale_x_discrete(labels=countyLabelsShort) + 
         labs(y="Preventable fraction") +
         theme(
+            panel.grid.major.x=element_blank(),
             axis.title.x=element_blank(),
             axis.ticks.x=element_blank(),
-            axis.text.x=element_text(angle=30, hjust=1)
+            axis.text.x=element_text(angle=30, hjust=0.5, vjust=0.5)
         )
+
     dev.off()
@@
         geom_point(aes(x=min(monthBoundaries$min), y=unprotected.start), data=thresholds, shape=18) + 
-        scale_y_continuous(labels=latexPercent, breaks=seq(0, 1, by=.2), limits=c(-0.1, 1.1), expand=c(0, 0)) +
+        scale_y_continuous(labels=latexPercent, breaks=seq(0, 1, by=.25), limits=c(-0.1, 1.1), expand=c(0, 0)) +
         scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, limits=range(c(monthBoundaries$min, monthBoundaries$max)), expand=c(0, 0)) + 
@@
             panel.grid.major.x=element_blank(),
+            panel.grid.minor.x=element_blank(),
             legend.title=element_blank(),

### 2019-03-27 Paper/Paper.R

@@ -143,6 +143,14 @@ countyLabels = c(
   `lowIncidence` = "Low-population counties"
 )
 
+countyLabelsShort = c(
+  `all` = "Statewide",
+  `New Haven` = "New Haven c.",
+  `Fairfield` = "Fairfield c.",
+  `Hartford` = "Hartford c.",
+  `lowIncidence` = "Low-population c."
+)
+
 # .01 to let minor gridlines show through
 epiWeekBreaks = c(3.01, 7.25, 11.75, 16.01, 20.25, 24.75, 29.01, 33.01, 37.5, 42.01, 46.25, 50.75)
 epiWeekLabels = c("Jul", "Aug", "Sep", "Oct", "Nov", "Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun")

### 2019-03-28 Paper/RSVOptimization.rnw
Transposed onset-offset plots
Tweaks

@@
 % TODO DPH acknowledgement
-% TODO transpose onset-offset plots
+% TODO better month labels in onset-offset plots
 
@@
 Palivizumab is administered via intramuscular injection and requires five monthly doses, priced at \$1500-\$3000 per dose.\cite{Hampp:2011ju,Andabaka:2013dr} Palivizumab has been found to be effective in reducing hospitalizations due to RSV; in double-blinded trials in high-risk infants, it reduced the hospitalization rate by 45-55\% compared to placebo.\cite{Group:1998ih,Feltes:2003wm} It has also been found to be safe and well-tolerated in clinical trials.\cite{Group:1998ih} Owing to the high cost, the 2014 revision of the American Academy of Pediatrics (AAP) RSV prophylaxis guidelines recommends palivizumab only for high-risk infants and only during the RSV season.\cite{Anonymous:1998up,AmericanAcademyofPediatricsCommitteeonInfectiousDiseasesandCommitteeonFetusandNewborn:2003ug,AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
-
-% TODO cite DW/VP paper re spatial variability
 
@@
 To that end, we fit smooth curves through annual RSV hospitalization data, and used resampling to obtain confidence intervals.
-This was performed using the ???
-package in R (See ???
-for details on the analytical method and R package.)
+This was performed using the \texttt{outbreak-inference} package in R, which we developed for this purpose.
+(See ???
+for details on the analytical method and the R package.)
+
+% TODO ref spline paper
 
@@
 Incidence cutoffs other than \Sexpr{seasonThreshold * 100}\% and \Sexpr{(1 - seasonThreshold) * 100}\% were briefly investigated, but quickly ruled out because they produced prophylaxis regimens starting long prior to RSV season onset or ending long after RSV season offset, and therefore had very low preventable fractions.
-
-% TODO ref spline paper
 
@@
 
-%TODO citation needed
+%TODO citation needed re small subgroup
 
@@
 
-In addition to 1-week rounding of our alternative prophylaxis schedules, we calculated 2- and 4-week rounding, to assess the impact of calendrical rounding on prophylaxis performance.
+In addition to the 1-week rounding of our alternative prophylaxis schedules, we also calculated schedules using 2- and 4-week rounding, to assess the impact of calendrical rounding on prophylaxis performance.
 (Supplemental methods \ref{smethod:rounding}.)
 
-To analyze the effects of year-to-year variation between RSV seasons, we performed similar analysis, but with prophylaxis start in a given year being determined by the RSV timing of three prior years, rather than all years.
+To analyze the effects of year-to-year variation between RSV seasons, we performed similar analysis, but with prophylaxis start in a given year being determined by the RSV season timing of the preceding three years, rather than all years.
 (Supplemental methods \ref{smethod:seasonDrift} and \ref{smethod:temporalAdjustment}.)
@@
 
-\subsection{Without calendrical rounding, spatially adjusted regimens are superior to the AAP recommendations}
+\subsection{Spatially adjusted regimens are superior to the AAP recommendations}
 
@@
 
-The six spatially-adjusted prophylaxis regimens (with no rounding of prophylaxis dates), yield results in all counties that are as good or better than the AAP guidelines.
+% TODO Update results to 1-week rounding
+
+The six spatially-adjusted prophylaxis regimens, yield results in all counties that are as good or better than the AAP guidelines.
 (Figure \ref{fig:coverageByRegionRegimen}).
@@
 
-We also applied biweekly and monthly rounding to the start and end dates of our six alternative immunoprophylaxis regimens, and found that doing so diminished or erased the benefits.
+We also applied 2-week and 4-week rounding to the start and end dates of our six alternative immunoprophylaxis regimens, and found that doing so diminished or erased the potential benefits.
 (Supplemental result \ref{sresult:rounding}).
@@
 
-Our effort to optimize timing of the prophylaxis regimen (without changing its duration, and therefore its pharmaceutical cost) shows a theoretical 1-2\% statewide decrease in RSV-associated hospitalizations among high-risk infants each year, primarily in counties with higher RSV burden (Fairfield, Hartford, and New Haven counties).
-The magnitude of that improvement declines after accounting for practicalities of clinical practice guideline implementation.
-Nonetheless, with clinical practice guidelines localized at the county level, and the timing of prophylaxis adjusted in each county by less than a whole month from the current AAP guidelines, we still found the potential for $\sim$1\% statewide decrease in RSV-associated hospitalizations among high risk infants.
-The prophylaxis regimen with which we were able to attain this improvement is the one in which prophylaxis in each county is timed relative to the midpoint of the RSV season (rounded to two weeks) in that county, which simultaneously reduces unprotected cases early in the season and ineffective prophylaxis late in the season.
+Our effort to optimize timing of the prophylaxis regimen (without changing its duration, and therefore its pharmaceutical cost) shows a potential $\sim1\%$ statewide decrease in RSV-associated hospitalizations among high-risk infants each year, primarily in counties with higher RSV burden (Fairfield, Hartford, and New Haven counties), by using clinical practice guidelines localized at the county level, and with the timing of prophylaxis adjusted in each county by less than a whole month from the current AAP guidelines.
+The prophylaxis regimen with which we were able to attain this improvement is the one in which prophylaxis in each county is timed relative to the midpoint of the RSV season in that county, which simultaneously reduces unprotected cases early in the season and ineffective prophylaxis late in the season.
 Increasing complexity of practice guidelines would carry with it increased cost of implementation (such as training of clinicians and other healthcare workers); it is therefore not apparent from our research alone that the potential benefits would outweigh the costs.
@@
 The use of data aggregated by epidemiological weeks created a challenge for both our analysis and the interpretation of our results.
-In practice, clinical guidelines are typically expressed in terms of calendar weeks or months; as a result, our analysis contains errors of up to $\pm 0.5$ weeks when applied to the more natural calendar boundaries.
+In practice, clinical guidelines are typically expressed in terms of calendar weeks or months; as a result, our analysis contains errors of up to $\pm 0.5$ weeks when applied to the more natural calendar boundaries of clinical guidelines.
 Ideally, our analysis should be repeated with daily case counts aggregated into weeks and months that match week and month boundaries used in clinical guidelines.

### 2019-03-28 Paper/Figures.Rnw
Figure sizing

@@
 <<seasonByRegion, results='hide'>>=
-    tikz(sprintf("%s/seasonByRegion.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
+    tikz(sprintf("%s/seasonByRegion.tex", figuresDir), width=1.5*inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
     onOffLevels = c("onset", "offset")

### 2019-03-28 Paper/RSVOptimization.rnw
Bumped draft #
Pagination
Figure placement
Promoting 1-week rounding to main analysis

@@
 \SetWatermarkLightness{.5}
-\SetWatermarkText{DRAFT 1}
+\SetWatermarkText{DRAFT 2}
 
@@
 
+\begin{samepage}
+
 We estimated the fraction of preventable cases at the state and county level by following the current AAP guidelines or six alternative regimens:
@@
 \end{itemize}
+
+\end{samepage}
 
@@
 
-\begin{figure}[b]
+\begin{figure}
 \begin{center}
@@
 
-% TODO Update results to 1-week rounding
-
-The six spatially-adjusted prophylaxis regimens, yield results in all counties that are as good or better than the AAP guidelines.
+The six spatially-adjusted prophylaxis regimens yield results in all counties that are as good or better than the AAP guidelines.
 (Figure \ref{fig:coverageByRegionRegimen}).
 Statewide, the AAP guidelines offer protection to \Sexpr{regionStrategyCoverage("all", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}).
-The alternative regimen based on statewide onset yields the smallest increase, to \Sexpr{regionStrategyCoverage("all", "stateOnset", 0)} (\Sexpr{regionStrategyCoverageCI("all", "stateOnset", 0, level)}); other alternative regimens yield similar results.
-Most of the increase comes from Hartford county, where the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", 0, level)}), whereas the alternative regimen based on county-level offset generates the smallest increase, to \Sexpr{regionStrategyCoverage("Hartford", "countyOffset", 0)} (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", 0, level)}); other alternative regimens are comparable.
+The least favorable of our alternative regimens --- based on statewide onset --- yields the increase to \Sexpr{regionStrategyCoverage("all", "stateOnset", 1)} (\Sexpr{regionStrategyCoverageCI("all", "stateOnset", 1, level)}); other alternative regimens yield similar results.
+Most of the increase comes from Hartford county, where the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", 0, level)}), whereas the least favorable of our alternative regimens --- based on county-level offset --- generates an increase to \Sexpr{regionStrategyCoverage("Hartford", "countyOffset", 1)} (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", 1, level)}), with other alternative regimens being comparable.
 In every county, all alternative regimens are non-inferior to the AAP guidelines and non-superior to each other.

### 2019-03-28 Paper/Paper.R
Fixing CI order

@@ -81,8 +81,8 @@ regionStrategyCoverage = function(c, s, r) {
 
 regionStrategyCoverageCI = function(c, s, r, level) {
   formatPctCI(
-    (unprotectedByCounty %>% filter(county==c, strat==s, rounding==r))$frac.upper,
     (unprotectedByCounty %>% filter(county==c, strat==s, rounding==r))$frac.lower,
+    (unprotectedByCounty %>% filter(county==c, strat==s, rounding==r))$frac.upper,
     level
   )
 }
@@ -93,8 +93,8 @@ bestCaseCoverage = function(r) {
 
 bestCaseCoverageCI = function(r, level) {
   formatPctCI(
-    (bestCaseCoverageByRounding %>% filter(rounding==r))$frac.upper,
     (bestCaseCoverageByRounding %>% filter(rounding==r))$frac.lower,
+    (bestCaseCoverageByRounding %>% filter(rounding==r))$frac.upper,
     level
   )
 }

### 2019-03-28 Paper/RSVOptimization.rnw
Drop secondary analysis from abstract

@@
 \abstractsection{Results}Using preventable fraction to assess different immunoprophylaxis regimens, we found that regimens adjusted for county-level variation in timing of RSV seasons are superior to the current AAP-recommended regimen.
-We also considered the effect of rounding the recommended start date of prophylaxis by week, biweekly period, or month and found that benefits of alternative regimens over the AAP-recommended regimen persisted with biweekly rounding, but not with monthly rounding.
-Our best-performing pragmatic alternative to the AAP guidelines was based on the country-level RSV season midpoint with biweekly rounding.
-In comparison to the AAP recommendation, whose preventable fraction is \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}), that alternative yielded improvement to \Sexpr{regionStrategyCoverage("all", "countyMiddle", 2)} (\Sexpr{regionStrategyCoverageCI("all", "countyMiddle", 2, level)}).
-We also found that alternative regimens adjusted for annual variation in the RSV season are non-superior to spatially adjusted regimens.
+Our best alternative to the AAP guidelines was based on the county-level RSV season midpoint.
+In comparison to the AAP recommendation, whose preventable fraction is \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}), that alternative yielded improvement to \Sexpr{regionStrategyCoverage("all", "countyMiddle", 1)} (\Sexpr{regionStrategyCoverageCI("all", "countyMiddle", 1, level)}).
 

### 2019-03-28 Paper/RSVOptimization.rnw
More abstract editing

@@
 
-% TODO make 1-week rounding primary analysis
 % TODO DPH acknowledgement
@@
 The American Academy of Pediatrics (AAP) recommends palivizumab only for infants at high risk of complications, and only during the RSV season.
-Although the current AAP guidelines acknowledge the existence of spatial and temporal variation in RSV incidence, they do not recommend spatial or temporal adjustments to the immunoprophylaxis regimen outside of Florida.
-In this study, we investigate the value of using spatial and temporal variation in RSV incidence to adjust the RSV prophylaxis regimen in Connecticut.
+The current AAP guidelines do not recommend spatial or temporal adjustments to the immunoprophylaxis regimen outside of Florida.
+In this study, we investigate the benefits of adjusting the RSV prophylaxis regimen in Connecticut based on the spatial and temporal variation of RSV incidence.
 
 \abstractsection{Methods}We obtained weekly ZIP-code-level counts of RSV-associated hospital admission in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)}.
-We fit smoothed curves to these admission counts and used these curves to estimate the fraction of all RSV cases in Connecticut occurring during the period of protection offered by RSV immunoprophylaxis (``preventable fraction'') under the AAP guidelines.
-We then used the same model to estimate protection conferred by immunoprophylaxis regimens with alternate start dates (but unchanged duration and net pharmaceutical cost).
+We fit smoothed curves to these admission counts and thus estimated the fraction of all RSV cases in Connecticut occurring during the period of protection offered by RSV immunoprophylaxis (``preventable fraction'') under the AAP guidelines.
+We then used the same model to estimate protection conferred by immunoprophylaxis regimens with alternate start dates (but unchanged duration).
 

### 2019-03-28 Paper/RSVOptimization.rnw
Even more abstract editing

@@
 
-\abstractsection{Conclusion}Overall, we recommend county-level spatial analysis of RSV incidence as the starting point for RSV immunoprophylaxis optimization in Connecticut.
-However, the potential reduction in RSV hospitalizations should be weighed against the potential increase in implementation cost.
+\abstractsection{Conclusion}Initiating RSV prophylaxis based on county-level data may provide marginal improvement in protection over regimens based on state-level and national data.
 

### 2019-03-28 Paper/RSVOptimization.rnw
Ongoing abstract editing

@@
 \abstractsection{Background}Respiratory syncytial virus (RSV) causes seasonal respiratory infection with potentially serious complications in children and leads to hospitalization rates of up to 50\% in high-risk infants.
-Safe and effective immunoprophylaxis (palivizumab) is available, but costly.
-The American Academy of Pediatrics (AAP) recommends palivizumab only for infants at high risk of complications, and only during the RSV season.
-The current AAP guidelines do not recommend spatial or temporal adjustments to the immunoprophylaxis regimen outside of Florida.
-In this study, we investigate the benefits of adjusting the RSV prophylaxis regimen in Connecticut based on the spatial and temporal variation of RSV incidence.
+Palivizumab provides safe, effective, and costly immunoprophylaxis.
+The American Academy of Pediatrics (AAP) recommends palivizumab only for high-risk infants, and only during the RSV season.
+The current guidelines do not recommend spatial or temporal adjustments to the immunoprophylaxis regimen outside of Florida.
+In this study, we investigate the benefits of adjusting the RSV prophylaxis regimen in Connecticut based on the spatial variation of RSV incidence.
 
@@
 
-\abstractsection{Results}Using preventable fraction to assess different immunoprophylaxis regimens, we found that regimens adjusted for county-level variation in timing of RSV seasons are superior to the current AAP-recommended regimen.
+\abstractsection{Results}Using preventable fraction to assess immunoprophylaxis regimens, we found that regimens adjusted for county-level variation in timing of RSV seasons are superior to the AAP-recommended regimen.
 Our best alternative to the AAP guidelines was based on the county-level RSV season midpoint.

### 2019-03-28 Paper/RSVOptimization.rnw
Creeping up on 250 words

@@
 
-\abstractsection{Background}Respiratory syncytial virus (RSV) causes seasonal respiratory infection with potentially serious complications in children and leads to hospitalization rates of up to 50\% in high-risk infants.
+\abstractsection{Background}Respiratory syncytial virus (RSV) causes seasonal respiratory infection with potentially serious complications in children and hospitalization rates of up to 50\% in high-risk infants.
 Palivizumab provides safe, effective, and costly immunoprophylaxis.
 The American Academy of Pediatrics (AAP) recommends palivizumab only for high-risk infants, and only during the RSV season.
-The current guidelines do not recommend spatial or temporal adjustments to the immunoprophylaxis regimen outside of Florida.
-In this study, we investigate the benefits of adjusting the RSV prophylaxis regimen in Connecticut based on the spatial variation of RSV incidence.
+Outside of Florida, the current guidelines do not recommend regional adjustments to the immunoprophylaxis.
+We investigate the benefits of adjusting the RSV prophylaxis regimen in Connecticut based on the spatial variation of RSV incidence.
 
-\abstractsection{Methods}We obtained weekly ZIP-code-level counts of RSV-associated hospital admission in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)}.
-We fit smoothed curves to these admission counts and thus estimated the fraction of all RSV cases in Connecticut occurring during the period of protection offered by RSV immunoprophylaxis (``preventable fraction'') under the AAP guidelines.
-We then used the same model to estimate protection conferred by immunoprophylaxis regimens with alternate start dates (but unchanged duration).
+\abstractsection{Methods}We obtained weekly RSV-associated hospital admissions by ZIP-code in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)}.
+We estimated the fraction of all RSV cases in Connecticut occurring during the period of protection offered by RSV immunoprophylaxis (``preventable fraction'') under the AAP guidelines.
+We then used the same model to estimate protection conferred by immunoprophylaxis regimens with alternate start dates, but unchanged duration.
 
-\abstractsection{Results}Using preventable fraction to assess immunoprophylaxis regimens, we found that regimens adjusted for county-level variation in timing of RSV seasons are superior to the AAP-recommended regimen.
-Our best alternative to the AAP guidelines was based on the county-level RSV season midpoint.
-In comparison to the AAP recommendation, whose preventable fraction is \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}), that alternative yielded improvement to \Sexpr{regionStrategyCoverage("all", "countyMiddle", 1)} (\Sexpr{regionStrategyCoverageCI("all", "countyMiddle", 1, level)}).
+\abstractsection{Results}Using preventable fraction to assess immunoprophylaxis regimens, we found that regimens adjusted for county-level variation in RSV seasons are superior to the AAP-recommended regimen.
+Our best alternative to the AAP guidelines was based on the county-level RSV season midpoint; in comparison to the AAP recommendation, whose preventable fraction is \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}), that alternative yielded improvement to \Sexpr{regionStrategyCoverage("all", "countyMiddle", 1)} (\Sexpr{regionStrategyCoverageCI("all", "countyMiddle", 1, level)}).
 

### 2019-03-28 Paper/RSVOptimization.rnw
Updating results to 1-week rounding

@@
 \abstractsection{Results}Using preventable fraction to assess immunoprophylaxis regimens, we found that regimens adjusted for county-level variation in RSV seasons are superior to the AAP-recommended regimen.
-Our best alternative to the AAP guidelines was based on the county-level RSV season midpoint; in comparison to the AAP recommendation, whose preventable fraction is \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}), that alternative yielded improvement to \Sexpr{regionStrategyCoverage("all", "countyMiddle", 1)} (\Sexpr{regionStrategyCoverageCI("all", "countyMiddle", 1, level)}).
+In comparison to the AAP recommendation, whose preventable fraction is \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}), our best alternative yielded improvement to \Sexpr{regionStrategyCoverage("all", "countyMiddle", 1)} (\Sexpr{regionStrategyCoverageCI("all", "countyMiddle", 1, level)}).
 
@@
 Statewide, the AAP guidelines offer protection to \Sexpr{regionStrategyCoverage("all", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}).
-The least favorable of our alternative regimens --- based on statewide onset --- yields the increase to \Sexpr{regionStrategyCoverage("all", "stateOnset", 1)} (\Sexpr{regionStrategyCoverageCI("all", "stateOnset", 1, level)}); other alternative regimens yield similar results.
-Most of the increase comes from Hartford county, where the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", 0, level)}), whereas the least favorable of our alternative regimens --- based on county-level offset --- generates an increase to \Sexpr{regionStrategyCoverage("Hartford", "countyOffset", 1)} (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", 1, level)}), with other alternative regimens being comparable.
+The least favorable of our alternative regimens --- based on couty-level offset --- yields the increase to \Sexpr{regionStrategyCoverage("all", "countyOffset", 1)} (\Sexpr{regionStrategyCoverageCI("all", "countyOffset", 1, level)}); other alternative regimens yield similar results.
+Most of the increase comes from Hartford county, where the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", 0, level)}), whereas the least favorable of our alternative regimens --- based on county-level midpoint --- generates an increase to \Sexpr{regionStrategyCoverage("Hartford", "countyMiddle", 1)} (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", 1, level)}), with other alternative regimens being comparable.
 In every county, all alternative regimens are non-inferior to the AAP guidelines and non-superior to each other.

### 2019-03-28 Paper/Figures.Rnw
Onset/offset plot improvements

@@
 
-    monthBarY = 0.7 + (0.5 - 5.5) * 0.04
-    monthGrob = function(month) {
-        textGrob(epiWeekLabels[month], just="right", gp=gpar(fontsize="6.4", col="grey30"))
-    }
-
-    plot = ggplot(data) +
+    ggplot(data) +
         theme_light(base_size=plotTextBaseSize) +
@@
         labs(x=NULL) + 
-        annotation_custom(monthGrob(4), ymin=monthBarY, ymax=monthBarY, xmin=monthBoundaries$mid[4], xmax=monthBoundaries$mid[4]) + 
-        annotation_custom(monthGrob(5), ymin=monthBarY, ymax=monthBarY, xmin=monthBoundaries$mid[5], xmax=monthBoundaries$mid[5]) + 
-        annotation_custom(monthGrob(9), ymin=monthBarY, ymax=monthBarY, xmin=monthBoundaries$mid[9], xmax=monthBoundaries$mid[9]) + 
-        annotation_custom(monthGrob(10), ymin=monthBarY, ymax=monthBarY, xmin=monthBoundaries$mid[10], xmax=monthBoundaries$mid[10]) + 
+        geom_rect(data=onsetOffsetMonthBoundaries, aes(xmin=min + 0.05, xmax=max - 0.05, ymin=0.6, ymax=0.8), color="grey70", fill="grey70") + 
+        geom_text(data=onsetOffsetMonthBoundaries, aes(x=mid, label=label, y=0.7), color="white", size=2.2) + 
         theme(
@@
         )
-
-	  plotGrob = ggplotGrob(plot)
-	  plotGrob$layout$clip[grepl("panel", plotGrob$layout$name)] <- "off"
-	  grid.draw(plotGrob)
 
@@
 
-    monthBarY = 1998.5 + (1998.5 - 2013.5) * 0.04
-
-    plot = ggplot(data) +
+    ggplot(data) +
         theme_light(base_size=plotTextBaseSize) +
@@
         geom_blank(data=limits, aes(x=max)) + 
+        geom_rect(data=onsetOffsetMonthBoundaries, aes(xmin=min + 0.05, xmax=max - 0.05, ymin=1997.8, ymax=1998.2), color="grey70", fill="grey70") + 
+        geom_text(data=onsetOffsetMonthBoundaries, aes(x=mid, label=label, y=1998), color="white", size=2.2) + 
         facet_wrap(~variable, ncol=2, scales="free_x", labeller=onsetOffsetLabeller) +
@@
         scale_x_continuous(breaks=seq(0, 52, 2), minor_breaks=seq(1, 52)) + 
-        annotation_custom(monthGrob(4), ymin=monthBarY, ymax=monthBarY, xmin=monthBoundaries$mid[4], xmax=monthBoundaries$mid[4]) + 
-        annotation_custom(monthGrob(5), ymin=monthBarY, ymax=monthBarY, xmin=monthBoundaries$mid[5], xmax=monthBoundaries$mid[5]) + 
-        annotation_custom(monthGrob(9), ymin=monthBarY, ymax=monthBarY, xmin=monthBoundaries$mid[9], xmax=monthBoundaries$mid[9]) + 
-        annotation_custom(monthGrob(10), ymin=monthBarY, ymax=monthBarY, xmin=monthBoundaries$mid[10], xmax=monthBoundaries$mid[10]) + 
         labs(x=NULL) + 
@@
 
-  	plotGrob = ggplotGrob(plot)
-  	plotGrob$layout$clip[grepl("panel", plotGrob$layout$name)] <- "off"
-  	grid.draw(plotGrob)
-
     dev.off()

### 2019-03-28 Paper/Paper.R

@@ -173,6 +173,10 @@ monthBoundaries = breaks.df %>%
 
 epiWeekBreaks = sort(unique(c(monthBoundaries$min, monthBoundaries$max)))
 
+onsetOffsetMonthBoundaries = data.frame(i=c(4, 5, 9, 10), variable=c("onset", "onset", "offset", "offset")) %>%
+  inner_join(monthBoundaries, by="i") %>%
+  mutate(label=epiWeekLabels[i])
+  
 legendLabels = function(labels, leading=0, trailing=2) {
   as.vector(sapply(labels, function(label) {
     if(substr(label, 1, 1) == "_") {

### 2019-03-28 Paper/Figures.Rnw
Onset/offset plot improvements

@@
         labs(x=NULL) + 
-        geom_rect(data=onsetOffsetMonthBoundaries, aes(xmin=min + 0.05, xmax=max - 0.05, ymin=0.6, ymax=0.8), color="grey70", fill="grey70") + 
-        geom_text(data=onsetOffsetMonthBoundaries, aes(x=mid, label=label, y=0.7), color="white", size=2.2) + 
+        geom_rect(data=onsetOffsetMonthBoundaries, aes(xmin=min + 0.05, xmax=max - 0.05, ymin=0.5, ymax=0.8), color="grey70", fill="grey70") + 
+        geom_text(data=onsetOffsetMonthBoundaries, aes(x=mid, label=label, y=0.65), color="white", size=2.2) + 
         theme(
@@
         geom_blank(data=limits, aes(x=max)) + 
-        geom_rect(data=onsetOffsetMonthBoundaries, aes(xmin=min + 0.05, xmax=max - 0.05, ymin=1997.8, ymax=1998.2), color="grey70", fill="grey70") + 
+        geom_rect(data=onsetOffsetMonthBoundaries, aes(xmin=min + 0.05, xmax=max - 0.05, ymin=1997.6, ymax=1998.4), color="grey70", fill="grey70") + 
         geom_text(data=onsetOffsetMonthBoundaries, aes(x=mid, label=label, y=1998), color="white", size=2.2) + 

### 2019-03-28 Paper/Paper.R
More regional → county-level renaming

@@ -126,9 +126,9 @@ stratLabels = c(
   `stateOnset` = "Statewide all-years onset",
   `stateMiddle` = "Statewide all-years midseason", 
   `stateOffset` = "Statewide all-years offset", 
-  `countyOnset` = "Regional all-years onset",
-  `countyMiddle` = "Regional all-years midseason",
-  `countyOffset` = "Regional all-years offset", 
+  `countyOnset` = "County-level all-years onset",
+  `countyMiddle` = "County-level all-years midseason",
+  `countyOffset` = "County-level all-years offset", 
   `stateSlidingOnset` = "Statewide recent-years onset",
   `stateSlidingMiddle` = "Statewide recent-years midseason",
   `stateSlidingOffset` = "Statewide recent-years offset", 

### 2020-06-26 Analysis/RSV.R
Refactored with docker and renv; updated to current pspline.inference

@@ -2,7 +2,7 @@
 library(reshape)
 library(dplyr)
 library(mgcv)
-library(outbreakinference)
+library(pspline.inference)
 library(zipcode)
 library(ggplot2)
 library(easyGgplot2)
@@ -113,7 +113,7 @@ startDate = min(dataset$adate)
 endDate = max(dataset$adate)
 
 rsvTime = dataset$epiweek
-modelTime = seq(min(rsvTime) - 1 + eps, max(rsvTime), eps)
+modelTime = data.frame(time=seq(min(rsvTime) - 1 + eps, max(rsvTime), eps))
 
 # *** Prophyaxis assessment helpers
 
@@ -191,23 +191,15 @@ ppxSlidingStrategies = function(c=NULL, y=NULL) {
 # *** Prophylaxis coverage estimation
 
 # Estimate % left unprotected by prophylaxis strategy
-outbreak.calc.unprotected = function(strategies) {
-  function(model, params, time) {
-    # Get model predictions for given (randomized) param values
-    time = time + 0.5
-    predictors = model %>% predict(data.frame(time=time), type="lpmatrix")
-    fit = predictors %*% params
-
-    # Map spline fit back to data
-    fit = fit %>% model$family$linkinv()
-
+pspline.outbreak.unprotected = function(strategies) {
+  function(model, data) {
     # Calculate total # of unprotected cases for each strategy
     unprotected = as.data.frame(lapply(strategies, function(strat) {
-      sum(fit * (1 - sapply(time, strat)))
+      sum(data * (1 - sapply(time, strat)))
     }))
 
     # Calculate total # of cases
-    total = sum(fit)
+    total = sum(data$rsv)
 
     unprotected %>%
       rename_all(list(
@@ -235,20 +227,18 @@ stateObs = dataset %>%
 stateModel = gam(rsv ~ s(time, k=20, bs="cp", m=3), family=poisson, data=stateObs)
 
 statePred = stateModel %>%
-  predict(type="response", newdata=data.frame(time=modelTime), se.fit=TRUE)
+  predict(type="response", newdata=modelTime, se.fit=TRUE)
 
-statePred = modelTime %>%
+statePred = stateModel %>%
+  pspline.estimate.timeseries(modelTime, pspline.outbreak.cumcases, samples=simulations) %>%
   cbind(data.frame(rsv.fit=statePred$fit, rsv.fit.se=statePred$se.fit)) %>%
[…]

### 2020-06-26 Paper/Figures.Rnw
Explicit mapproj dependency

@@
 <<map, results='hide'>>=
+    library(mapproj)
     tikz(sprintf("%s/map.tex", figuresDir), width=1.5*inlinePlotWidth, height=inlinePlotHeight, pointsize=10)

### 2020-06-26 Analysis/RSV.R
Progress messages

@@ -262,14 +262,13 @@ fixedStratDescByCountyRounding = data.frame()
 fixedStratUnprotectedByCounty = data.frame()
 
 for (c in levels(obsByCounty$county)) {
-  message(paste("County:", c))
+  message(paste("Regional all-years:", c))
   countyObs = obsByCounty %>% filter(county==c)
   countyModel = gam(rsv ~ s(time, k=20, bs="cp", m=3), family=poisson, data=countyObs)
 
   countyPred = countyModel %>%
     predict(type="response", newdata=modelTime, se.fit=TRUE)
 
-  message("Timeseries")
   countyPred = countyModel %>%
     pspline.estimate.timeseries(
       modelTime,
@@ -282,7 +281,6 @@ for (c in levels(obsByCounty$county)) {
 
   predByCounty = predByCounty %>% rbind(countyPred)
 
-  message("Thresholds")
   countyThresholds = countyModel %>%
     pspline.estimate.scalars(
       modelTime,
@@ -294,7 +292,7 @@ for (c in levels(obsByCounty$county)) {
   thresholdsByCounty = thresholdsByCounty %>% rbind(countyThresholds)
 
   for (rounding in ppxRounding) {
-    message(paste("Rounding:", as.character(rounding)))
+    message(paste("Regional all-years with rounding:", as.character(rounding)))
     # Separate simulation from confidence intervals in order to use simulation data to get statewide estimates
     countyUnprotectedSim = countyModel %>%
       pspline.sample.scalars(
@@ -411,6 +409,7 @@ statePredByWindow = data.frame()
 stateThresholdsByWindow = data.frame()
 
 for (y in rsvWindowYears) {
+  message(paste("State-wide lsiding window:", y))
 
   stateYearObs = stateObsByWindow %>% filter(epiyear==y)
   stateYearModel = gam(rsv ~ s(time, k=5, bs="cp", m=3), family=poisson, data=stateYearObs)
@@ -461,7 +460,9 @@ thresholdsByCountyYear = data.frame()
 slidingStratUnprotectedSimByCountyYear = data.frame()
 
 for (c in levels(obsByCountyYear$county)) {
+  message(paste("Regional sliding window:", c))
   for (y in rsvEpiYears) {
+    message(paste("Regional sliding window:", y))
     countyYearObs = obsByCountyYear %>% filter(county==c, epiyear==y)
     countyYearModel = gam(rsv ~ s(time, k=4, bs="cp", m=3), family=poisson, data=countyYearObs)
 

### 2020-06-27 Analysis/RSV.R
Fixed plot problems introduced by refactoring

@@ -195,7 +195,7 @@ pspline.outbreak.unprotected = function(strategies) {
   function(model, data) {
     # Calculate total # of unprotected cases for each strategy
     unprotected = as.data.frame(lapply(strategies, function(strat) {
-      sum(data * (1 - sapply(time, strat)))
+      sum(data$rsv * (1 - sapply(data$time, strat)))
     }))
 
     # Calculate total # of cases
@@ -230,9 +230,9 @@ statePred = stateModel %>%
   predict(type="response", newdata=modelTime, se.fit=TRUE)
 
 statePred = stateModel %>%
-  pspline.estimate.timeseries(modelTime, pspline.outbreak.cumcases, samples=simulations) %>%
+  pspline.estimate.timeseries(modelTime, pspline.outbreak.cumcases.relative, samples=simulations) %>%
   cbind(data.frame(rsv.fit=statePred$fit, rsv.fit.se=statePred$se.fit)) %>%
-  rename(rsv.cum.fit.lower=rsv.cum.lower, rsv.cum.fit.upper=rsv.cum.upper, rsv.cum.fit=rsv.cum.median)
+  rename(rsv.cum.fit.lower=rsv.cumrel.lower, rsv.cum.fit.upper=rsv.cumrel.upper, rsv.cum.fit=rsv.cumrel.median)
 
 stateThresholds = stateModel %>%
   pspline.estimate.scalars(
@@ -272,11 +272,11 @@ for (c in levels(obsByCounty$county)) {
   countyPred = countyModel %>%
     pspline.estimate.timeseries(
       modelTime,
-      pspline.outbreak.cumcases,
+      pspline.outbreak.cumcases.relative,
       samples=simulations
     ) %>%
     cbind(data.frame(rsv.fit=countyPred$fit, rsv.fit.se=countyPred$se.fit)) %>%
-    rename(rsv.cum.fit.lower=rsv.cum.lower, rsv.cum.fit.upper=rsv.cum.upper, rsv.cum.fit=rsv.cum.median) %>%
+    rename(rsv.cum.fit.lower=rsv.cumrel.lower, rsv.cum.fit.upper=rsv.cumrel.upper, rsv.cum.fit=rsv.cumrel.median) %>%
     mutate(county=factor(c, levels=levels(obsByCounty$county)))
 
   predByCounty = predByCounty %>% rbind(countyPred)
[…]

### 2020-06-27 Paper/Figures.Rnw

@@
 
-    ggplot(data) +
+    p = ggplot(data) +
         theme_light(base_size=plotTextBaseSize) +
@@
         )
+	p
 
+    dev.off()
+
+    tikz(sprintf("%s/coverageByRegionAAPInsight-Standalone.tex", figuresDir), width=16/3, height=3, pointsize=10, standAlone=TRUE)
+	p = p + facet_wrap(~county, ncol=3, labeller=labeller(county=countyLabels))
+	p
     dev.off()

### 2020-06-28 analysis/RSV.R
Rearranged file structure

@@ -14,7 +14,11 @@ library(maps)
 data(zipcode)
 set.seed(0)
 
-simulations = 2000
+if (Sys.getenv("KNITR_DRAFT_MODE", "") != "") {
+  simulations = 5
+} else {
+  simulations = 2000
+}
 
 # *** Data munging helpers
 
@@ -45,7 +49,7 @@ ppxRounding = c(0, 1, 2, 4)
 # *** Load / munge data
 
 # Load data
-admissions = fread("../ct rsv time series.csv", sep=",", header=TRUE, colClasses=c("patzip"="character"))
+admissions = fread("data/ct rsv time series.csv", sep=",", header=TRUE, colClasses=c("patzip"="character"))
 
 epiyear = function(date) {
   ifelse(month(date) > 6, year(date), year(date) - 1)
@@ -78,7 +82,7 @@ dataset = dataset %>%
   left_join(zipcode %>% select(zip, state), by=c("patzip"="zip")) %>%
   filter(state=="CT")
 # Add county based on zipcode
-countyByZip = fread("../ct counties.csv", sep=",", header=TRUE, colClasses=c("zip"="character"))
+countyByZip = fread("data/ct counties.csv", sep=",", header=TRUE, colClasses=c("zip"="character"))
 counties = countyByZip %>% select(county) %>% distinct()
 dataset = dataset %>% inner_join(countyByZip, by=c("patzip"="zip"))
 
@@ -409,7 +413,7 @@ statePredByWindow = data.frame()
 stateThresholdsByWindow = data.frame()
 
 for (y in rsvWindowYears) {
-  message(paste("State-wide lsiding window:", y))
+  message(paste("State-wide sliding window:", y))
 
   stateYearObs = stateObsByWindow %>% filter(epiyear==y)
   stateYearModel = gam(rsv ~ s(time, k=5, bs="cp", m=3), family=poisson, data=stateYearObs)

### 2020-06-28 paper/figures.Rnw
Fixing case sensitivity

--- 2020-06-27 Paper/Figures.Rnw
@@
     tikz(sprintf("%s/map.tex", figuresDir), width=1.5*inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
-    US.counties = readOGR(dsn="../Maps/cb_2016_us_county_5m",layer="cb_2016_us_county_5m")
+    US.counties = readOGR(dsn="./data.maps/cb_2016_us_county_5m",layer="cb_2016_us_county_5m")
     US.counties = US.counties[US.counties$STATEFP == "09",]

### 2020-06-28 paper/figures.Rnw
Typo

--- 2020-06-27 Paper/Figures.Rnw
@@
     tikz(sprintf("%s/map.tex", figuresDir), width=1.5*inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
-    US.counties = readOGR(dsn="../Maps/cb_2016_us_county_5m",layer="cb_2016_us_county_5m")
+    US.counties = readOGR(dsn="./data/maps/cb_2016_us_county_5m",layer="cb_2016_us_county_5m")
     US.counties = US.counties[US.counties$STATEFP == "09",]

### 2020-06-28 paper/figures.Rnw
Apparently here workdir is in ./paper even if knit started in .

--- 2020-06-27 Paper/Figures.Rnw
@@
     tikz(sprintf("%s/map.tex", figuresDir), width=1.5*inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
-    US.counties = readOGR(dsn="../Maps/cb_2016_us_county_5m",layer="cb_2016_us_county_5m")
+    US.counties = readOGR(dsn="../data/maps/cb_2016_us_county_5m",layer="cb_2016_us_county_5m")
     US.counties = US.counties[US.counties$STATEFP == "09",]

### 2020-06-29 analysis/RSV.R
Fixed check for draft mode

@@ -14,7 +14,7 @@ library(maps)
 data(zipcode)
 set.seed(0)
 
-if (Sys.getenv("KNITR_DRAFT_MODE", "") != "") {
+if (as.logical(Sys.getenv("KNITR_DRAFT_MODE", "FALSE"))) {
   simulations = 5
 } else {
   simulations = 2000

### 2020-07-01 RSVOptimization.rnw
Rearranged file structure
Ginny’s assorted feedback

--- 2019-03-28 Paper/RSVOptimization.rnw
@@
 
-\input{structure.tex}
+\input{paper/structure.tex}
 \usepackage{amssymb}
@@
 
-<<knitr, child='Paper.Rnw'>>=
+<<options, echo=FALSE>>=
+    knitr::opts_chunk$set(echo=FALSE, message=FALSE, error=FALSE)
+@
+
+<<load>>=
+knitr::read_chunk("analysis/RSV.R")
+knitr::read_chunk("paper/paper.R")
+@
+
+<<libraries, cache=FALSE>>=
+@
+
+<<external, cache=TRUE>>=
+@
+
+<<paper, warning=FALSE>>=
+@
+
+<<figures, child='paper/figures.Rnw'>>=
 @
@@
 \title{Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}}
-\def\headertitle{Assessment and optimization of RSV prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}}
+\def\headertitle{Evaluating the benefit of initiating RSV prophylaxis based on state- and county-level data}
 
@@
     \authorstyle{Daniel Weinberger, PhD\textsuperscript{1}}\\
-    \authorstyle{Virginia Pitzer, ScD\textsuperscript{1}}
+    \authorstyle{Virginia E. Pitzer, ScD\textsuperscript{1}}
     \newline\newline
-    \textsuperscript{1}\institution{Yale University, School of Public Health}
+    \textsuperscript{1}\institution{Department of Epidemiology of Microbial Diseases, Yale School of Public Health, Yale University}
 }
@@
 \abstractsection{Background}Respiratory syncytial virus (RSV) causes seasonal respiratory infection with potentially serious complications in children and hospitalization rates of up to 50\% in high-risk infants.
-Palivizumab provides safe, effective, and costly immunoprophylaxis.
-The American Academy of Pediatrics (AAP) recommends palivizumab only for high-risk infants, and only during the RSV season.
-Outside of Florida, the current guidelines do not recommend regional adjustments to the immunoprophylaxis.
-We investigate the benefits of adjusting the RSV prophylaxis regimen in Connecticut based on the spatial variation of RSV incidence.
+Palivizumab provides safe and effective, yet costly, immunoprophylaxis.
+The American Academy of Pediatrics (AAP) recommends palivizumab only for high-risk infants and only during the RSV season.
+Outside of Florida, the current guidelines do not recommend regional adjustments to the immunoprophylaxis regimen.
+We investigate the benefits of adjusting the RSV prophylaxis regimen in Connecticut based on spatial variation of RSV incidence.
 
@@
 \abstractsection{Results}Using preventable fraction to assess immunoprophylaxis regimens, we found that regimens adjusted for county-level variation in RSV seasons are superior to the AAP-recommended regimen.
-In comparison to the AAP recommendation, whose preventable fraction is \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}), our best alternative yielded improvement to \Sexpr{regionStrategyCoverage("all", "countyMiddle", 1)} (\Sexpr{regionStrategyCoverageCI("all", "countyMiddle", 1, level)}).
+The best alternative strategy yielded a preventable fraction of \Sexpr{regionStrategyCoverage("all", "countyMiddle", 1)} (\Sexpr{regionStrategyCoverageCI("all", "countyMiddle", 1, level)}), compared to \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) for the AAP recommendation.
 
@@
 
-Respiratory syncytial virus (RSV) causes upper respiratory infections in humans of all ages.
+Respiratory syncytial virus (RSV) causes upper respiratory tract infections in humans of all ages.
 In adults, RSV infection is typically asymptomatic or gives rise to mild respiratory illness.
@@
 A monoclonal antibody (palivizumab) is available in the US for prevention of RSV infection in high-risk infants less than 2 years old.
-Palivizumab is administered via intramuscular injection and requires five monthly doses, priced at \$1500-\$3000 per dose.\cite{Hampp:2011ju,Andabaka:2013dr} Palivizumab has been found to be effective in reducing hospitalizations due to RSV; in double-blinded trials in high-risk infants, it reduced the hospitalization rate by 45-55\% compared to placebo.\cite{Group:1998ih,Feltes:2003wm} It has also been found to be safe and well-tolerated in clinical trials.\cite{Group:1998ih} Owing to the high cost, the 2014 revision of the American Academy of Pediatrics (AAP) RSV prophylaxis guidelines recommends palivizumab only for high-risk infants and only during the RSV season.\cite{Anonymous:1998up,AmericanAcademyofPediatricsCommitteeonInfectiousDiseasesandCommitteeonFetusandNewborn:2003ug,AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
+Palivizumab is administered via intramuscular injection and requires five monthly doses, priced at \$1500-\$3000 per dose.\cite{Hampp:2011ju,Andabaka:2013dr} Palivizumab has been found to be effective in reducing hospitalizations due to RSV; in double-blinded trials in high-risk infants, it reduced the hospitalization rate by 45-55\% compared to placebo.\cite{Group:1998ih,Feltes:2003wm} It has also been found to be safe and well-tolerated.\cite{Group:1998ih} Owing to the high cost, the 2014 revision of the American Academy of Pediatrics (AAP) RSV prophylaxis guidelines recommends palivizumab only for high-risk infants and only during the RSV season.\cite{Anonymous:1998up,AmericanAcademyofPediatricsCommitteeonInfectiousDiseasesandCommitteeonFetusandNewborn:2003ug,AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
 
-RSV seasonality and spatial variability have been established throughout the United States, based on the CDC's National Respiratory and Enteric Virus Surveillance System data; RSV has been found to have an annual or biennial cycle with regionally variable seasonal onset ranging from late August to mid-December and offset ranging from mid-March to late April.\cite{CentersforDiseaseControlandPreventionCDC:2011wt,CentersforDiseaseControlandPreventionCDC:2013wv,Weinberger:2015hj} The AAP acknowledges the potential significance of spatial and temporal variation in RSV incidence, but --- outside of Florida, whose RSV season leads most of the rest of the nation by approximately two months --- does not recommend local variance from nationwide prophylaxis guidelines.\cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
+RSV seasonality and spatial variability have been established throughout the United States, based on the CDC's National Respiratory and Enteric Virus Surveillance System data; RSV has been found to have an annual or biennial cycle with regionally variable seasonal onset ranging from late August to mid-December and offset ranging from mid-March to late April.\cite{CentersforDiseaseControlandPreventionCDC:2011wt,CentersforDiseaseControlandPreventionCDC:2013wv,Weinberger:2015hj} In Connecticut, previous analysis of RSV-associated hospital admissions has shown spatial variability in the timing of peak RSV incidence, with epidemics occurring earlier in large urban areas and later in sparsely-populated rural areas.\cite{Noveroske:y4fi3188} The AAP acknowledges the potential significance of spatial and temporal variation in RSV incidence, but --- outside of Florida, whose RSV season leads most of the rest of the nation by approximately two months --- does not recommend local variance from nationwide prophylaxis guidelines.\cite{AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
 
-Previous analysis of RSV-associated hospital admissions has shown spatial variability in the timing of peak RSV incidence within Connecticut.\cite{Noveroske:y4fi3188} Epidemics tends to occur earlier in large urban areas and later in sparsely-populated rural areas.
-
-Motivated by the AAP's recognition of the significance of spatial variation in formulating prophylaxis guidelines and the known spatial variability of RSV incidence in Connecticut, we aim to determine whether protection due to RSV prophylaxis would be enhanced by having localized guidelines for the initiation of prophylaxis.
+Motivated by the AAP's recognition of the significance of spatial variation in formulating prophylaxis guidelines and the known spatial variability of RSV incidence in Connecticut, we aim to determine whether protection due to RSV prophylaxis would be enhanced by having localized guidelines for the initiation of prophylaxis by addressing the following questions:
 
@@
     \item the postal code of residence listed the in patient's medical record was in Connecticut, and
-    \item the hospital stay was associated with ICD-9-CM diagnosis code \texttt{079.6} (RSV), \texttt{466.11} (Acute bronchiolitis due to RSV), or \texttt{480.1} (Pneumonia due to RSV).
+    \item the hospital stay was associated with ICD-9-CM diagnosis code \texttt{079.6} (RSV), \texttt{466.11} (acute bronchiolitis due to RSV), or \texttt{480.1} (pneumonia due to RSV).
 \end{itemize}
 
+We designated epidemiological years as beginning in the first full week of July, in order to accommodate the timing of RSV peaks (which span two calendar years).
+Due to changes in diagnostic coding, we excluded data prior to \Sexpr{formatMonth(startDate)}; we similarly excluded data after \Sexpr{formatMonth(endDate)} due to incompleteness of data for the 2013-14 epidemiological year.
 Using the weekly hospitalization data, we identified \Sexpr{prettyNum(nrow(dataset), big.mark=",")} RSV-associated hospitalizations in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)} (inclusive).
+
+% TODO patient age
 
@@
 
-% TODO patient age
+\subsection{Spatial aggregation of RSV incidence}
 
-We designated epidemiological years as beginning in the first full week of July, in order to accommodate the timing of RSV peaks (which span two calendar years).
-Due to changes in diagnostic coding, we excluded data prior to July 1996; we similarly excluded data after June 2013 due to incompleteness of data for the 2013-14 epidemiological year.
+We analyzed RSV data aggregated either to the state level or into four geographic areas:
 
-\subsection{Spatial aggregation of RSV incidence}
+\begin{itemize}
+    \item One area for each of the counties with high population levels and high RSV case counts: Hartford, Fairfield, and New Haven (Figure \ref{fig:map}).
+    \item One discontiguous area comprised of all remaining counties in Connecticut: Tolland, Windham, Middlesex, Litchfield, and New London (``low-population counties'').
+\end{itemize}
 
@@
 
-We analyzed RSV data between \Sexpr{formatYear(startDate)} and \Sexpr{formatYear(endDate)} aggregated either to the state level or into four geographic areas:
-
-\begin{itemize}
-    \item One area for each of the counties with high population levels and high RSV case counts: Hartford County, Fairfield County, and New Haven County (Figure \ref{fig:map}).
-    \item One discontiguous area comprised of all remaining counties in Connecticut: \Sexpr{gsub("(.*), (.*)", "\\1, and \\2", paste(lowIncidenceCounties, collapse=", "))} (``low-population counties'').
-\end{itemize}
-
 We chose county-level aggregation with an eye towards using this data to inform clinical practice guidelines, which are typically based on administrative areas for reasons of administrative and implementation simplicity.
-
 We chose to aggregate low-population counties into a single area because our analysis in those counties individually yielded results with low statistical power.
@@
 Our goal was to construct a model of annual RSV incidence that allowed us to estimate characteristics of RSV seasons, such as season onset, season offset, and preventable fraction of a prophylaxis regimen.
-To that end, we fit smooth curves through annual RSV hospitalization data, and used resampling to obtain confidence intervals.
-This was performed using the \texttt{outbreak-inference} package in R, which we developed for this purpose.
-(See ???
-for details on the analytical method and the R package.)
+To that end, we fit smooth curves through annual RSV hospitalization data and used resampling to obtain confidence intervals.
+This was performed using the \texttt{pspline.inference} package in R, which we developed for this purpose.\cite{methods,package}
 
-% TODO ref spline paper
-
-We defined season onset as the time when cumulative incidence rises beyond \Sexpr{seasonThreshold * 100}\% of the total cumulative incidence, and season offset as the time when cumulative incidence rises beyond \Sexpr{(1 - seasonThreshold) * 100}\% of the total cumulative incidence.
+We defined season onset as the time when cumulative incidence rises beyond \Sexpr{seasonThreshold * 100}\% of the total cumulative incidence, and season offset as the time when cumulative incidence rises beyond \Sexpr{(1 - seasonThreshold) * 100}\% of the total cumulative incidence for an epidemiological year.
 We aggregated our data by surveillance week across all surveillance years, and estimated RSV season onset and offset for each county.
@@
 In all these regimens, prophylaxis consists of five monthly doses of palivizumab, and protection is assumed to last 24 weeks from the first dose.
-We rounded each alternative regimen to the nearest week, to more closely reflect how prophylaxis guidelines might be implemented in practice.
-(Supplemental methods \ref{smethod:rounding}.)
+We rounded each alternative regimen to the nearest week to more closely reflect how prophylaxis guidelines might be implemented in practice (Supplemental Methods \ref{smethod:rounding}).
 
@@
 
-Given that high-risk infants are a small subgroup of the general population, we assumed that our model of RSV hospitalizations among all infants is an unbiased approximation of RSV hospitalizations among high-risk infants, and that, therefore, the preventable fraction of a prophylactic regimen is an unbiased estimate of the fraction of high-risk infants who benefit from prophylaxis.
+Given that high-risk infants are a small subgroup of the general population, we assumed that our model of RSV hospitalizations among all infants is an unbiased approximation of RSV hospitalizations among high-risk infants, and therefore that the preventable fraction of a prophylactic regimen is an unbiased estimate of the fraction of high-risk infants who benefit from prophylaxis.
 
@@
 
-In addition to the 1-week rounding of our alternative prophylaxis schedules, we also calculated schedules using 2- and 4-week rounding, to assess the impact of calendrical rounding on prophylaxis performance.
-(Supplemental methods \ref{smethod:rounding}.)
+In addition to the 1-week rounding of our alternative prophylaxis schedules, we also calculated schedules using 2- and 4-week rounding, to assess the impact of calendrical rounding on prophylaxis performance (Supplemental Methods \ref{smethod:rounding}).
 
-To analyze the effects of year-to-year variation between RSV seasons, we performed similar analysis, but with prophylaxis start in a given year being determined by the RSV season timing of the preceding three years, rather than all years.
-(Supplemental methods \ref{smethod:seasonDrift} and \ref{smethod:temporalAdjustment}.)
+To analyze the effects of year-to-year variation between RSV seasons, we performed a similar analysis, but with the prophylaxis start date in a given year determined by the median RSV season timing during the preceding three years, rather than all years (Supplemental Methods \ref{smethod:seasonDrift} and \ref{smethod:temporalAdjustment}).
 
@@
 \subsection{Timing of the RSV season varies within the state}
+
+Statewide, the median onset of the RSV season is at week \Sexpr{regionOnset("all")} (\Sexpr{regionOnsetCI("all", level)}), and offset is at week \Sexpr{regionOffset("all")} (\Sexpr{regionOffsetCI("all", level)}).
+Fairfield county had the the earliest RSV season, with a median onset at week \Sexpr{regionOnset("Fairfield")} (\Sexpr{regionOnsetCI("Fairfield", level)}).
+Fairfield also had the latest median offset at week \Sexpr{regionOffset("Fairfield")} (\Sexpr{regionOffsetCI("Fairfield", level)}).
+Meanwhile, the RSV season in the low-population counties had the latest onset at week \Sexpr{regionOnset("lowIncidence")} (\Sexpr{regionOnsetCI("all", level)}); the season offset in these counties was not different from the statewide median (Figure \ref{fig:seasonByRegion}).
 
@@
 
-Statewide, the median onset of the RSV season is at week \Sexpr{regionOnset("all")} (\Sexpr{regionOnsetCI("all", level)}), and offset is at week \Sexpr{regionOffset("all")} (\Sexpr{regionOffsetCI("all", level)}).
-Fairfield county had the the earliest RSV season, with a median onset at week \Sexpr{regionOnset("Fairfield")} (\Sexpr{regionOnsetCI("Fairfield", level)}).
-Fairfield also had the latest median offset at week \Sexpr{regionOffset("Fairfield")} (\Sexpr{regionOffsetCI("Fairfield", level)}).
-Meanwhile, the RSV season in the low-population counties had the latest onset at week \Sexpr{regionOnset("lowIncidence")} (\Sexpr{regionOnsetCI("all", level)}); the season offset in these counties was not different than the statewide median (Figure \ref{fig:seasonByRegion}).
+\subsection{The AAP guidelines perform best in low-population counties and worst in Fairfield county}
 
-\subsection{The AAP guidelines perform best in low-population counties and worst in Fairfield county}
+Statewide, our model estimates that \Sexpr{regionStrategyCoverage("all", "aap", 0)} of RSV cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) occur while palivizumab offers protection when administered per the AAP guidelines.
+The AAP guidelines perform better in the low-population counties, where \Sexpr{regionStrategyCoverage("lowIncidence", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("lowIncidence", "aap", 0, level)}) occur during the prophylaxis interval, but worse in Fairfield county, where \Sexpr{regionStrategyCoverage("Fairfield", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("Fairfield", "aap", 0, level)}) occur during this time (Figure \ref{fig:coverageByRegionAAP}).
 
@@
 \input{\figuresDir/coverageByRegionAAP.tex}
-\caption[County-level variation in the fraction of RSV hospitalizations occurring while the AAP-recommended RSV prophylaxis is active]{County-level variation in the fraction of RSV hospitalizations occurring while protection by palivizumab --- administered per the AAP guidelines ---  is active}
+\caption[County-level variation in the fraction of RSV hospitalizations occurring while the AAP-recommended RSV prophylaxis is active]{County-level variation in the preventable fraction of RSV hospitalizations according to AAP guidelines.
+The percentage of RSV hospitalizations occurring while protection by palivizumab --- administered per the AAP guidelines ---  is active is plotted for each geographic region in Connecticut.
+TODO Bars = 95\% CI.}
 \label{fig:coverageByRegionAAP}
@@
 \end{figure}
-
-Statewide, our model shows that \Sexpr{regionStrategyCoverage("all", "aap", 0)} of RSV cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) occur while palivizumab offers protection when administered per the AAP guidelines.
-The AAP guidelines perform better in the low-population counties, where \Sexpr{regionStrategyCoverage("lowIncidence", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("lowIncidence", "aap", 0, level)}) occur during the prophylaxis interval, but worse in Fairfield county, where \Sexpr{regionStrategyCoverage("Fairfield", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("Fairfield", "aap", 0, level)}) occur during this time (Figure \ref{fig:coverageByRegionAAP}).
 
@@
 
+The six spatially-adjusted prophylaxis regimens yield results in all counties that are as good or better than the AAP guidelines.
+(Figure \ref{fig:coverageByRegionRegimen}).
+Statewide, the AAP guidelines offer protection to \Sexpr{regionStrategyCoverage("all", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}).
+The least favorable of our alternative regimens --- based on county-level offset --- yields an increase in the preventable fraction to \Sexpr{regionStrategyCoverage("all", "countyOffset", 1)} (\Sexpr{regionStrategyCoverageCI("all", "countyOffset", 1, level)}); other alternative regimens yield similar results.
+Most of the increase occurs in Hartford county, where the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", 0, level)}), whereas the least favorable of our alternative regimens --- based on county-level midpoint --- generates an increase to \Sexpr{regionStrategyCoverage("Hartford", "countyMiddle", 1)} (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", 1, level)}), with other alternative regimens being comparable.
+In every county, all alternative regimens are non-inferior to the AAP guidelines and non-superior to each other.
+
 \begin{figure}
@@
 
-The six spatially-adjusted prophylaxis regimens yield results in all counties that are as good or better than the AAP guidelines.
-(Figure \ref{fig:coverageByRegionRegimen}).
-Statewide, the AAP guidelines offer protection to \Sexpr{regionStrategyCoverage("all", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}).
-The least favorable of our alternative regimens --- based on couty-level offset --- yields the increase to \Sexpr{regionStrategyCoverage("all", "countyOffset", 1)} (\Sexpr{regionStrategyCoverageCI("all", "countyOffset", 1, level)}); other alternative regimens yield similar results.
-Most of the increase comes from Hartford county, where the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", 0, level)}), whereas the least favorable of our alternative regimens --- based on county-level midpoint --- generates an increase to \Sexpr{regionStrategyCoverage("Hartford", "countyMiddle", 1)} (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", 1, level)}), with other alternative regimens being comparable.
-In every county, all alternative regimens are non-inferior to the AAP guidelines and non-superior to each other.
-
 \subsection{Additional results}
 
-We also applied 2-week and 4-week rounding to the start and end dates of our six alternative immunoprophylaxis regimens, and found that doing so diminished or erased the potential benefits.
-(Supplemental result \ref{sresult:rounding}).
-Finally, we analyzed long-term trends in the RSV season onset and offset and found that the season onset may be moving earlier (Supplemental result \ref{sresult:seasonDrift}), but that accounting for that drift did not yield a significant further increase in preventable RSV cases (Supplemental result \ref{sresult:temporalAdjustment}).
+We also applied 2-week and 4-week rounding to the start and end dates of our six alternative immunoprophylaxis regimens, and found that doing so diminished or erased the potential benefits (Supplemental Results \ref{sresult:rounding}).
+Finally, we analyzed long-term trends in the RSV season onset and offset and found that the season onset may be moving earlier (Supplemental Results \ref{sresult:seasonDrift}), but that accounting for that drift did not yield a significant further increase in preventable RSV cases (Supplemental Results \ref{sresult:temporalAdjustment}).
 
@@
 Our analysis confirms the existence of county-level variation of RSV season timing in Connecticut (defined by RSV season onset and offset) observable at the county level.
-We have also shown a misalignment between the prophylaxis schedule recommended by the AAP and the timing of the RSV season throughout Connecticut, with most counties' RSV season starting before protection from the first dose of prophylaxis takes hold, and ending before protection from the last dose wanes.
-This misalignment is particularly notable in Fairfield County, due to its early season onset.
+We have also shown a misalignment between the prophylaxis schedule recommended by the AAP and the timing of the RSV season throughout Connecticut, with most counties' RSV season starting before protection from the first dose of prophylaxis is administered, and ending before protection from the last dose wanes.
+This misalignment is particularly notable in Fairfield County due to its early season onset.
 
@@
 
-Our effort to optimize timing of the prophylaxis regimen (without changing its duration, and therefore its pharmaceutical cost) shows a potential $\sim1\%$ statewide decrease in RSV-associated hospitalizations among high-risk infants each year, primarily in counties with higher RSV burden (Fairfield, Hartford, and New Haven counties), by using clinical practice guidelines localized at the county level, and with the timing of prophylaxis adjusted in each county by less than a whole month from the current AAP guidelines.
-The prophylaxis regimen with which we were able to attain this improvement is the one in which prophylaxis in each county is timed relative to the midpoint of the RSV season in that county, which simultaneously reduces unprotected cases early in the season and ineffective prophylaxis late in the season.
+Our effort to optimize timing of the prophylaxis regimen (without changing its duration and therefore its pharmaceutical cost) shows a potential $\sim1\%$ statewide decrease in RSV-associated hospitalizations among high-risk infants each year, primarily in counties with higher RSV burden (Fairfield, Hartford, and New Haven counties).
+The prophylaxis regimen with which we were able to attain the best improvement is the one in which prophylaxis in each county is timed relative to the midpoint of the RSV season in that county, which simultaneously reduces unprotected cases early in the season and ineffective prophylaxis late in the season.
+Nevertheless, all of the alternative regimens yielded similar results, with the timing of prophylaxis adjusted in each county or statewide by less than a whole month from the current AAP guidelines.
 Increasing complexity of practice guidelines would carry with it increased cost of implementation (such as training of clinicians and other healthcare workers); it is therefore not apparent from our research alone that the potential benefits would outweigh the costs.
 
-Although we found a weak statewide trend in RSV season onset becoming earlier over time, further analysis did not yield any improvements to prophylaxis based on that trend.
+Although we found a weak statewide trend in RSV season onset becoming earlier over time, further analysis did not yield any improvements to the preventable fraction of the prophylaxis regimen based on that trend.
 Since temporal variation in clinical guidelines would lead to a higher implementation burden than spatial variation, we see no reason to base RSV immunoprophylaxis clinical practice guidelines on temporal variation in RSV season timing.
@@
 
-Throughout, we assumed that RSV-associated hospitalizations are an unbiased estimate of RSV incidence in the general population; in doing so, we implicitly assumed that infectiousness and virulence of RSV are constant over time, for which we have no verification.
+Throughout, we assumed that RSV-associated hospitalizations are an unbiased estimate of RSV incidence in the general population.
+In doing so, we implicitly assumed that infectiousness and virulence of RSV are constant over time, for which we have no verification.
 
-Our model of palivizumab immunoprophylaxis assumes a protection period with a hard start at administration and a hard stop at 24 weeks post-administration; the physiologic response to monoclonal antibody immunoprophylaxis is actually tapered on both ends.
-Similarly, we assumed the protection by palivizumab is constant at 100\% throughout the protection period; however, not only is breakthrough RSV illness known to occur in patients on palivizumab, but it is an indication for discontinuing the prophylaxis regimen.
+Our model of palivizumab immunoprophylaxis assumes a constant protection period with a hard start at administration and a hard stop at 24 weeks post-administration.
+The physiologic response to monoclonal antibody immunoprophylaxis is actually tapered on both ends.
+Similarly, we assumed the protection conferred by palivizumab is constant at 100\% throughout the protection period; however, not only is breakthrough RSV illness known to occur in patients on palivizumab, but it is an indication for discontinuing the prophylaxis regimen.
 
@@
 
-In summary, our analysis reveals the potential for $\sim 1\%$ gain in prevented RSV cases in Connecticut using a two-week (rather than monthly) basis for prophylaxis guidelines.
+In summary, our analysis reveals the potential for a $\sim 1\%$ gain in preventable RSV cases in Connecticut when a locally-tailored two-week (rather than monthly) prophylaxis guideline is used in place of the established AAP guidelines.
 Practical merits of this potential gain --- including implementation cost and absolute magnitude of such gains --- require further investigation.
-Additionally, the method we developed for this analysis can be applied to county-level or state-level analysis of seasonal RSV patterns in other regions, some of which are likely to show a greater relative benefit than Connecticut (due to a greater degree of misalignment between RSV season and prophylaxis window) as well as a greater absolute benefit (due to population size).
+Additionally, the method we developed for this analysis can be applied to county-level or state-level analysis of seasonal RSV patterns in other regions, some of which are likely to show a greater relative benefit (due to a greater degree of misalignment between the RSV season and the AAP guidelines' prophylaxis window) as well as a greater absolute benefit (due to population size) than Connecticut.
 
@@
 
-Alignment of rounding periods to November 15th was done to make our regimens more clearly comparable to the AAP-recommended regimen, whose (average) start is also November 15th.
+Alignment of rounding periods to November 15th was done to make our regimens more clearly comparable to the AAP-recommended regimen, whose (average) start date is also November 15th.
 This alignment of rounding periods was only approximate because we were working with data aggregated by epidemiological weeks, which aren't aligned to calendar months.
@@
 
-To analyze the effects on prophylaxis regimens of year-to-year variation between RSV seasons, we aggregated our data into (overlapping) periods of three consecutive years (in order to maintain a higher level of statistical power, as well as to limit the impact of short-term variation on our results).
+To analyze the effects of year-to-year variation between RSV seasons on the preventable fraction of prophylaxis regimens, we aggregated our data into (overlapping) periods of three consecutive years.
+We chose to use three-year periods in order to maintain a higher level of statistical power, as well as to limit the impact of short-term variation on our results.
 This gave us \Sexpr{year(endDate) - year(startDate) - 1} three-year periods, with the \Sexpr{formatYear(startDate + 2*365)} period covering surveillance years \Sexpr{formatYear(startDate)} through \Sexpr{formatYear(startDate + 2*365)}, and the \Sexpr{formatYear(endDate)} period covering \Sexpr{formatYear(endDate - 2*365)} through \Sexpr{formatYear(endDate)}.
 
-We then estimated the onset and offset for each three-year period, using the same penalized spline GAM as for the all-years analysis, producing --- as before --- statewide and county-level estimates of \Sexpr{seasonThreshold * 100}\% onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset.
-To evaluate year-to-year variation in RSV season onset and offset we modeled median RSV three-year onset and offset against time using simple linear regression.
-We did not analyze any other long-term patterns, such as cyclicity.
+We then estimated the onset and offset for each three-year period, using the same penalized spline generalized additive model as for the all-years analysis, producing --- as before --- statewide and county-level estimates of \Sexpr{seasonThreshold * 100}\% onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset.
+To evaluate year-to-year variation in RSV season onset and offset, we modeled median RSV three-year onset and offset against time using simple linear regression.
+We did not analyze any other long-term patterns, such as multi-year cycles.
 
@@
 We then compared those regimens to the one recommended by the AAP and to the six spatially adjusted alternatives (with no calendrical rounding) from our main analysis.
-As in the main analysis, these alternative regimens involved five monthly doses of palivizumab giving 24 weeks of protection.
+As in the main analysis, these alternative regimens involved five monthly doses of palivizumab providing 24 weeks of protection.
 
@@
 
+After we applied weekly, biweekly, and monthly rounding to start and end dates of our six alternative immunoprophylaxis regimens, we found that longer rounding intervals diminished the benefit of tailoring the guidelines to local data (Supplemental figure \ref{fig:coverageByRoundingRegimen}).
+With weekly rounding, our regimens were non-inferior to the AAP recommendation, and produced an increase in preventable fraction from \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) under the AAP guidelines to \Sexpr{bestCaseCoverage(1)} (\Sexpr{bestCaseCoverageCI(1, level)}) statewide.
+Biweekly rounding yielded regimens that were similarly non-inferior to the AAP recommendation, with an increase in the preventable fraction to \Sexpr{bestCaseCoverage(2)} (\Sexpr{bestCaseCoverageCI(2, level)}) statewide.
+However, with monthly rounding, the gains almost completely vanished, with the preventable fraction not exceeding \Sexpr{bestCaseCoverage(4)} (\Sexpr{bestCaseCoverageCI(4, level)}).
+Furthermore, all our regimens with monthly rounding were non-superior to the AAP-recommended regimen in all counties.
+
 \begin{figure}
@@
 \input{\figuresDir/coverageByRoundingRegimen.tex}
-\caption[The effect of calendrical rounding of start and end of spatially adjusted RSV prophylaxis regimens on their performance]{The effect of calendrical rounding of start and end of spatially adjusted RSV prophylaxis regimens on their performance, showing that longer rounding intervals diminish the benefits of alternative regimens over the AAP-recommended regimen.
-Preventable fraction: the fraction of all RSV hospitalizations occurring while the prophylaxis regimen offers protection.
-Hollow plot markers ($\raisebox{1pt}{\Circle}$, $\square$, and $\triangle$) denote a prophylaxis strategy which, as a result of rounding, is identical to another, and therefore does not provide additional insights.}
+\caption[The effect of calendrical rounding of start and end of spatially adjusted RSV prophylaxis regimens on their performance]{The effect of calendrical rounding of start and end of spatially adjusted RSV prophylaxis regimens on their performance.
+The preventable fraction (i.e.
+the fraction of all RSV hospitalizations occurring while the prophylaxis regimen offers protection) is plotted for TODO Our results show that longer rounding intervals diminish the benefits of alternative regimens over the AAP-recommended regimen.
+Hollow plot markers ($\raisebox{1pt}{\Circle}$, $\square$, and $\triangle$) denote a prophylaxis strategy which, as a result of rounding, is identical to another, and therefore does not provide additional benefit.}
 \label{fig:coverageByRoundingRegimen}
@@
 
-After we applied weekly, biweekly, and monthly rounding to start and end dates of our six alternative immunoprophylaxis regimens, we found that longer rounding intervals diminished the benefit of spatial analysis (Supplemental figure \ref{fig:coverageByRoundingRegimen}).
-With weekly rounding, our regimens were non-inferior to the AAP recommendation, and produced an increase in preventable fraction from AAP's \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) to \Sexpr{bestCaseCoverage(1)} (\Sexpr{bestCaseCoverageCI(1, level)}) statewide.
-Biweekly rounding yielded regimens similarly non-inferior to the AAP recommendation, with an increase in preventable fraction to \Sexpr{bestCaseCoverage(2)} (\Sexpr{bestCaseCoverageCI(2, level)}) statewide.
-However, with monthly rounding, the gains almost completely vanished, with preventable fraction not exceeding \Sexpr{bestCaseCoverage(4)} (\Sexpr{bestCaseCoverageCI(4, level)}).
-Furthermore, all our regimens with monthly rounding were non-superior to the AAP-recommended regimen in all counties.
-
 \subsection{RSV season onset is slowly moving earlier}
 \label{sresult:seasonDrift}
-
-\begin{figure}
-\begin{center}
-\input{\figuresDir/onsetOffsetByYear.tex}
-\caption{Annual variability in RSV season onset and offset in Connecticut}
-\label{fig:onsetOffsetByYear}
-\end{center}
-\end{figure}
 
@@
 
+\begin{figure}
+\begin{center}
+\input{\figuresDir/onsetOffsetByYear.tex}
+\caption{Annual variability in RSV season onset and offset in Connecticut.}
+\label{fig:onsetOffsetByYear}
+\end{center}
+\end{figure}
+
 \subsection{Temporally-adjusted prophylaxis regimens are non-superior to others}
 \label{sresult:temporalAdjustment}
+
+Compared to our county-level all-years analysis, the three regimens based on statewide recent-years analysis produced non-superior results everywhere and inferior results in the low-population counties (Supplemental figure \ref{fig:coverageByRegionRegimenWithSliding}).
+Due to the non-superiority of regimens based on statewide recent-years analysis, we did not evaluate regimens based on county-level recent-years data.
 
@@
 
-Compared to our county-level all-years analysis, the three regimens based on statewide recent-years analysis produced non-superior results everywhere, and inferior results in the low-population counties (Supplemental figure \ref{fig:coverageByRegionRegimenWithSliding}).
-Due to the non-superiority of regimens based on statewide recent-years analysis, we did not evaluate regimens based on county-level recent-years data.
-
 \end{appendices}

### 2020-07-01 RSVOptimization.rnw
Plot clarifications

@@
 \caption[County-level variation in the fraction of RSV hospitalizations occurring while the AAP-recommended RSV prophylaxis is active]{County-level variation in the preventable fraction of RSV hospitalizations according to AAP guidelines.
-The percentage of RSV hospitalizations occurring while protection by palivizumab --- administered per the AAP guidelines ---  is active is plotted for each geographic region in Connecticut.
-TODO Bars = 95\% CI.}
+The percentage of RSV hospitalizations occurring while protection by palivizumab --- administered per the AAP guidelines ---  is active is plotted for each geographic region in Connecticut.}
 \label{fig:coverageByRegionAAP}
@@
 The preventable fraction (i.e.
-the fraction of all RSV hospitalizations occurring while the prophylaxis regimen offers protection) is plotted for TODO Our results show that longer rounding intervals diminish the benefits of alternative regimens over the AAP-recommended regimen.
+the fraction of all RSV hospitalizations occurring while the prophylaxis regimen offers protection) is plotted for each prophylaxis regimen and for each rounding interval.
+Our results show that longer rounding intervals diminish the benefits of alternative regimens over the AAP-recommended regimen.
 Hollow plot markers ($\raisebox{1pt}{\Circle}$, $\square$, and $\triangle$) denote a prophylaxis strategy which, as a result of rounding, is identical to another, and therefore does not provide additional benefit.}

### 2020-07-01 paper/figures.Rnw
Plot clarifications

@@
         scale_x_discrete(labels=countyLabelsShort) + 
-        labs(y="Preventable fraction") +
+        labs(y="Preventable fraction, median (95% CI)") +
         theme(
@@
         geom_point(aes(y=frac.median, x=county, color=strat, shape=strat), position=position_dodge(.5), size=.75) +
-        labs(y="Preventable fraction", color="Prophylaxis regimen") +
+        labs(y="Preventable fraction, median (95% CI)", color="Prophylaxis regimen") +
         guides(color=guide_legend(keywidth=1, keyheight=1.5, ncol=3)) + 
@@
         geom_point(aes(y=frac.median, x=rounding, color=strat.isRepeat, shape=strat.isRepeat), position=position_dodge(.5), size=0.75, fill="white") +
-        labs(x="Calendrical rounding", y="Preventable fraction") +
+        labs(x="Calendrical rounding", y="Preventable fraction, median (95% CI)") +
         theme(
@@
         geom_point(aes(y=frac.median, x=county, color=strat, shape=strat), position=position_dodge(.5), size=.75) +
-        labs(y="Preventable fraction") +
+        labs(y="Preventable fraction, median (95% CI)") +
         guides(color=guide_legend(keywidth=1, keyheight=1.5, ncol=3)) + 

### 2020-07-01 paper/paper.R

@@ -117,7 +117,7 @@ latexPercent = function(f) {
 }
 
 onsetOffsetLabeller = labeller(
-  variable=c(`onset` = "RSV season onset", `offset` = "RSV season offset")
+  variable=c(`onset` = "RSV season onset, median (95% CI)", `offset` = "RSV season offset, median (95% CI)")
 )
 
 roundingLabels = c(`0` = "No rounding", `1` = "Weekly rounding", `2` = "Biweekly rounding", `4` = "Monthly rounding")

### 2020-07-02 paper/figures.Rnw
Fixed percent escaping

--- 2020-06-28 paper/figures.Rnw
@@
         scale_x_discrete(labels=countyLabelsShort) + 
-        labs(y="Preventable fraction") +
+        labs(y="Preventable fraction, median (95\\% CI)") +
         theme(
@@
         geom_point(aes(y=frac.median, x=county, color=strat, shape=strat), position=position_dodge(.5), size=.75) +
-        labs(y="Preventable fraction", color="Prophylaxis regimen") +
+        labs(y="Preventable fraction, median (95\\% CI)", color="Prophylaxis regimen") +
         guides(color=guide_legend(keywidth=1, keyheight=1.5, ncol=3)) + 
@@
         geom_point(aes(y=frac.median, x=rounding, color=strat.isRepeat, shape=strat.isRepeat), position=position_dodge(.5), size=0.75, fill="white") +
-        labs(x="Calendrical rounding", y="Preventable fraction") +
+        labs(x="Calendrical rounding", y="Preventable fraction, median (95\\% CI)") +
         theme(
@@
         geom_point(aes(y=frac.median, x=county, color=strat, shape=strat), position=position_dodge(.5), size=.75) +
-        labs(y="Preventable fraction") +
+        labs(y="Preventable fraction, median (95\\% CI)") +
         guides(color=guide_legend(keywidth=1, keyheight=1.5, ncol=3)) + 

### 2020-07-02 paper/paper.R

@@ -117,7 +117,7 @@ latexPercent = function(f) {
 }
 
 onsetOffsetLabeller = labeller(
-  variable=c(`onset` = "RSV season onset, median (95% CI)", `offset` = "RSV season offset, median (95% CI)")
+  variable=c(`onset` = "RSV season onset, median (95\\% CI)", `offset` = "RSV season offset, median (95\\% CI)")
 )
 
 roundingLabels = c(`0` = "No rounding", `1` = "Weekly rounding", `2` = "Biweekly rounding", `4` = "Monthly rounding")

### 2020-07-02 RSVOptimization.rnw
Better plot labels

@@
 
-We estimated the fraction of preventable cases at the state and county level by following the current AAP guidelines or six alternative regimens:
+We compared the current AAP guidelines with six alternative prophylaxis regimens:
 
@@
 \begin{itemize}
-\item the number of RSV-associated hospitalizations that occur while the prophylaxis regimen offers protection to those who receive prophylaxis as scheduled, and
-\item the total number of RSV-associated hospitalizations.
+\item the number of RSV-associated hospitalizations that occur in a given region (state or county) while the prophylaxis regimen offers protection to those who receive prophylaxis as scheduled, and
+\item the total number of RSV-associated hospitalizations that occur in the same region during a single epidemiologic year.
 \end{itemize}

### 2020-07-02 paper/figures.Rnw
Better plot labels

@@
         scale_x_continuous(breaks=seq(0, 52, 2), minor_breaks=seq(1, 52)) + 
-        labs(x=NULL) + 
+        labs(x="Epidemiological week") + 
         geom_rect(data=onsetOffsetMonthBoundaries, aes(xmin=min + 0.05, xmax=max - 0.05, ymin=0.5, ymax=0.8), color="grey70", fill="grey70") + 
@@
         scale_y_continuous(labels=latexPercent, limits=c(0.88, 1), breaks=seq(0, 1, by=0.04), expand=c(0.05, 0)) +
-        scale_x_discrete(labels=countyLabelsShort) + 
+        scale_x_discrete(labels=countyLabelsCompact) + 
         labs(y="Preventable fraction, median (95\\% CI)") +
@@
 <<onsetOffsetByYear, results='hide', warning=FALSE>>=
-    tikz(sprintf("%s/onsetOffsetByYear.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
+    tikz(sprintf("%s/onsetOffsetByYear.tex", figuresDir), width=1.5*inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
     data = stateThresholdsByWindow %>% 
@@
         scale_x_continuous(breaks=seq(0, 52, 2), minor_breaks=seq(1, 52)) + 
-        labs(x=NULL) + 
+        labs(x="Epidemiological week") + 
         theme(

### 2020-07-02 paper/paper.R

@@ -143,12 +143,12 @@ countyLabels = c(
   `lowIncidence` = "Low-population counties"
 )
 
-countyLabelsShort = c(
+countyLabelsCompact = c(
   `all` = "Statewide",
-  `New Haven` = "New Haven c.",
-  `Fairfield` = "Fairfield c.",
-  `Hartford` = "Hartford c.",
-  `lowIncidence` = "Low-population c."
+  `New Haven` = "\\begin{tabular}{c}New Haven \\\\ county\\end{tabular}",
+  `Fairfield` = "\\begin{tabular}{c}Fairfield \\\\ county\\end{tabular}",
+  `Hartford` = "\\begin{tabular}{c}Hartford \\\\ county\\end{tabular}",
+  `lowIncidence` = "\\begin{tabular}{c}Low-population \\\\ counties\\end{tabular}"
 )
 
 # .01 to let minor gridlines show through

### 2020-07-02 RSVOptimization.rnw
Plot caption improvements

@@
 
-% Separate paragraph because observation above, cause below
-
-This is caused by temporal misalignment between the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each county) and the timing of the AAP-recommended prophylaxis regimen (Figure \ref{fig:coverageByRegionAAPInsight}).
+The county-to-county to variation in the protected fraction of the AAP-recommended prophylaxis is caused by temporal misalignment between the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\% onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each county) and the timing of the AAP-recommended prophylaxis regimen (Figure \ref{fig:coverageByRegionAAPInsight}).
 Fairfield county, owing to its early season onset, sees disproportionately more cases before prophylaxis administration begins; on the other hand, the low-population counties, owing to their late season onset and relatively shorter RSV seasons, see almost all of their RSV cases within the prophylaxis window.
@@
 \input{\figuresDir/coverageByRegionAAPInsight.tex}
-\caption[County-level variation in the relative timing of the RSV season in Connecticut and the AAP-recommended prophylaxis regimen]{County-level variation in the relative timing of the RSV season in Connecticut and the AAP-recommended prophylaxis regimen, showing the gap between season onset and prophylaxis start date, notable particularly in Fairfield county}
+\caption[County-level variation in the relative timing of the RSV season in Connecticut and the AAP-recommended prophylaxis regimen]{County-level variation in the relative timing of the RSV season in Connecticut and the AAP-recommended prophylaxis regimen.
+Comparison of the RSV season (red bar) and the prophylaxis window (purple bar) shows the misalignment between the two, notable particularly in Fairfield county.}
 \label{fig:coverageByRegionAAPInsight}
@@
 \input{\figuresDir/coverageByRegionRegimen.tex}
-\caption[Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen]{Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen, showing statewide superiority and county-level non-inferiority of spatially adjusted regimens.
+\caption[Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen]{Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen.
+Spatially adjusted propxylaxis regimens are either non-inferior (for county-level analysis) or superior (for statewide analysis) to the AAP-recommended regimen.
 Preventable fraction: the fraction of all RSV-associated hospitalizations occurring while the prophylaxis regimen provides protection}
@@
 \input{\figuresDir/onsetOffsetByYear.tex}
-\caption{Annual variability in RSV season onset and offset in Connecticut.}
+\caption{Annual variability in RSV season onset and offset in Connecticut. While season offset has been stable, season onset has shown a statistically significant drift toward an earliear RSV season.}
 \label{fig:onsetOffsetByYear}
@@
 \input{\figuresDir/coverageByRegionRegimenWithSliding.tex}
-\caption[Comparison of prophylaxis regimens based on all-years data to those based on recent-years data]{Comparison of prophylaxis regimens based on all-years data to those based on recent-years data, showing temporal analysis adds no benefit over spatial analysis alone.
+\caption[Comparison of prophylaxis regimens based on all-years data to those based on recent-years data]{Comparison of prophylaxis regimens based on all-years data to those based on recent-years data.
+Recent-years analysis analysis adds no benefit over all-years analysis, for either statewide or county-level analysis.
 Preventable fraction: fraction of RSV hospitalizations occurring while the prophylaxis regimen offers protection}

### 2020-07-02 paper/figures.Rnw
Tinkering with onset/offset facet wrap

@@
         rename(variable=variable_1, pctile=variable_2) %>%
-        mutate(variable=factor(variable, levels=onOffLevels)) %>%
-        cast(county + variable ~ pctile)
+        cast(county + variable ~ pctile) %>%
+        mutate(variable=factor(variable, levels=onOffLevels))
 
@@
         rename(variable=variable_1, pctile=variable_2) %>%
-        mutate(variable=factor(variable, levels=onOffLevels)) %>%
-        cast(epiyear + variable ~ pctile)
+        cast(epiyear + variable ~ pctile) %>%
+        mutate(variable=factor(variable, levels=onOffLevels))
 

### 2020-07-02 RSVOptimization.rnw
Cite package
Wording

@@
 To that end, we fit smooth curves through annual RSV hospitalization data and used resampling to obtain confidence intervals.
-This was performed using the \texttt{pspline.inference} package in R, which we developed for this purpose.\cite{methods,package}
+This was performed using the \texttt{pspline.inference} package in R, which we developed for this purpose.\cite{psplineInferencePackage,methods}
 
@@
 Statewide, the median onset of the RSV season is at week \Sexpr{regionOnset("all")} (\Sexpr{regionOnsetCI("all", level)}), and offset is at week \Sexpr{regionOffset("all")} (\Sexpr{regionOffsetCI("all", level)}).
-Fairfield county had the the earliest RSV season, with a median onset at week \Sexpr{regionOnset("Fairfield")} (\Sexpr{regionOnsetCI("Fairfield", level)}).
-Fairfield also had the latest median offset at week \Sexpr{regionOffset("Fairfield")} (\Sexpr{regionOffsetCI("Fairfield", level)}).
-Meanwhile, the RSV season in the low-population counties had the latest onset at week \Sexpr{regionOnset("lowIncidence")} (\Sexpr{regionOnsetCI("all", level)}); the season offset in these counties was not different from the statewide median (Figure \ref{fig:seasonByRegion}).
+The earliest season onset occurred in Fairfield county, with median at week \Sexpr{regionOnset("Fairfield")} (\Sexpr{regionOnsetCI("Fairfield", level)}).
+The latest season offset also occurrent in Fairfield county, with median at week \Sexpr{regionOffset("Fairfield")} (\Sexpr{regionOffsetCI("Fairfield", level)}).
+Meanwhile, the latest season onset occurred in the low-population counties, with median at week \Sexpr{regionOnset("lowIncidence")} (\Sexpr{regionOnsetCI("all", level)}); the season offset in these counties was not different from the statewide median (Figure \ref{fig:seasonByRegion}).
 

### 2020-07-02 RSVOptimization.rnw
Wording

--- 2020-07-02 RSVOptimization.rnw
@@
 
-We compared the current AAP guidelines with six alternative prophylaxis regimens:
+We estimated the fraction of preventable cases at the state and county level by following the current AAP guidelines or six alternative regimens:
 
@@
 \begin{itemize}
-\item the number of RSV-associated hospitalizations that occur in a given region (state or county) while the prophylaxis regimen offers protection to those who receive prophylaxis as scheduled, and
-\item the total number of RSV-associated hospitalizations that occur in the same region during a single epidemiologic year.
+\item the number of RSV-associated hospitalizations that occur while the prophylaxis regimen offers protection to those who receive prophylaxis as scheduled, and
+\item the total number of RSV-associated hospitalizations.
 \end{itemize}

### 2020-07-02 RSVOptimization.rnw
Fixed number of hospitalizations

@@
 Due to changes in diagnostic coding, we excluded data prior to \Sexpr{formatMonth(startDate)}; we similarly excluded data after \Sexpr{formatMonth(endDate)} due to incompleteness of data for the 2013-14 epidemiological year.
-Using the weekly hospitalization data, we identified \Sexpr{prettyNum(nrow(dataset), big.mark=",")} RSV-associated hospitalizations in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)} (inclusive).
-
-% TODO patient age
+Using the weekly hospitalization data, we identified \Sexpr{prettyNum(totalRSV, big.mark=",")} RSV-associated hospitalizations among \Sexpr{prettyNum(nrow(dataset), big.mark=",")} total hospitalizations of patients <2 years old in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)} (inclusive).
 

### 2020-07-02 RSVOptimization.rnw
Fixed number of hospitalizations

--- 2020-07-02 RSVOptimization.rnw
@@
 Due to changes in diagnostic coding, we excluded data prior to \Sexpr{formatMonth(startDate)}; we similarly excluded data after \Sexpr{formatMonth(endDate)} due to incompleteness of data for the 2013-14 epidemiological year.
-Using the weekly hospitalization data, we identified \Sexpr{prettyNum(nrow(dataset), big.mark=",")} RSV-associated hospitalizations in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)} (inclusive).
-
-% TODO patient age
+Using the weekly hospitalization data, we identified \Sexpr{prettyNum(nrow(dataset %>% filter(rsv==1)), big.mark=",")} RSV-associated hospitalizations among \Sexpr{prettyNum(nrow(dataset), big.mark=",")} total hospitalizations of patients <2 years old in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)} (inclusive).
 

### 2020-07-02 RSVOptimization.rnw
Grammar

--- 2020-07-02 RSVOptimization.rnw
@@
 We obtained data consisting of all hospitalizations among children <2 years old in Connecticut from 1996 to 2013 from the Connecticut State Inpatient Database through the Connecticut Department of Public Health (CT DPH).
-Relevant variables in the data were ZIP code of residence, patient age, ICD-9 defined diagnoses (up to 10 diagnoses per hospital admission), and week and year of hospital admission.
+The relevant variables in the data were ZIP code of residence, patient age, ICD-9 defined diagnoses (up to 10 diagnoses per hospital admission), and week and year of hospital admission.
 

### 2020-07-02 RSVOptimization.rnw
Corrected total cases calculation

@@
 Due to changes in diagnostic coding, we excluded data prior to \Sexpr{formatMonth(startDate)}; we similarly excluded data after \Sexpr{formatMonth(endDate)} due to incompleteness of data for the 2013-14 epidemiological year.
-Using the weekly hospitalization data, we identified \Sexpr{prettyNum(nrow(dataset %>% filter(rsv==1)), big.mark=",")} RSV-associated hospitalizations among \Sexpr{prettyNum(nrow(dataset), big.mark=",")} total hospitalizations of patients <2 years old in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)} (inclusive).
+Using the weekly hospitalization data, we identified \Sexpr{prettyNum(totalRSV, big.mark=",")} RSV-associated hospitalizations among \Sexpr{prettyNum(nrow(dataset), big.mark=",")} total hospitalizations of patients <2 years old in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)} (inclusive).
 

### 2020-07-02 analysis/RSV.R

@@ -93,6 +93,9 @@ totalRSVByCounty = dataset %>%
   arrange(total_rsv) %>%
   mutate(county=factor(county, county))
 
+totalRSV = sum(dataset$rsv)
+totalYears = max(dataset$epiyear) - min(dataset$epiyear) + 1
+
 rsvCounties = totalRSVByCounty$county
 rsvEpiYears = sort(unique(dataset$epiyear))
 rsvEpiWeekRange = sort(unique(dataset$epiweek))

### 2020-07-02 RSVOptimization.rnw
Absolute #s in conclusion

@@
 In summary, our analysis reveals the potential for a $\sim 1\%$ gain in preventable RSV cases in Connecticut when a locally-tailored two-week (rather than monthly) prophylaxis guideline is used in place of the established AAP guidelines.
-Practical merits of this potential gain --- including implementation cost and absolute magnitude of such gains --- require further investigation.
+At an average of $\Sexpr{prettyNum(totalRSV / totalYears, digits=3)}$ RSV-associated hospitalizations per year in children under 2 years old in Connecticut, this corresponds to $\sim \Sexpr{prettyNum(totalRSV / totalYears / 100, digits=4)}$ hospitalizations prevented per year, and an unknown number of prevented cases not necessitating hospitalization.
+Practical aspects of this potential gain --- such as implementation cost --- require further investigation.
 Additionally, the method we developed for this analysis can be applied to county-level or state-level analysis of seasonal RSV patterns in other regions, some of which are likely to show a greater relative benefit (due to a greater degree of misalignment between the RSV season and the AAP guidelines' prophylaxis window) as well as a greater absolute benefit (due to population size) than Connecticut.

### 2020-07-02 RSVOptimization.rnw
Absolute #s in conclusion

@@
 To that end, we fit smooth curves through annual RSV hospitalization data and used resampling to obtain confidence intervals.
-This was performed using the \texttt{pspline.inference} package in R, which we developed for this purpose.\cite{psplineInferencePackage,methods}
+This was performed using the \texttt{pspline.inference} package in R, which we developed for this purpose.\cite{methods,package}
 
@@
 
-The county-to-county to variation in the protected fraction of the AAP-recommended prophylaxis is caused by temporal misalignment between the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\% onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each county) and the timing of the AAP-recommended prophylaxis regimen (Figure \ref{fig:coverageByRegionAAPInsight}).
+% Separate paragraph because observation above, cause below
+
+This is caused by temporal misalignment between the RSV season (delineated by median \Sexpr{seasonThreshold * 100}\%  onset and \Sexpr{(1 - seasonThreshold) * 100}\% offset in each county) and the timing of the AAP-recommended prophylaxis regimen (Figure \ref{fig:coverageByRegionAAPInsight}).
 Fairfield county, owing to its early season onset, sees disproportionately more cases before prophylaxis administration begins; on the other hand, the low-population counties, owing to their late season onset and relatively shorter RSV seasons, see almost all of their RSV cases within the prophylaxis window.
@@
 \input{\figuresDir/coverageByRegionAAPInsight.tex}
-\caption[County-level variation in the relative timing of the RSV season in Connecticut and the AAP-recommended prophylaxis regimen]{County-level variation in the relative timing of the RSV season in Connecticut and the AAP-recommended prophylaxis regimen.
-Comparison of the RSV season (red bar) and the prophylaxis window (purple bar) shows the misalignment between the two, notable particularly in Fairfield county.}
+\caption[County-level variation in the relative timing of the RSV season in Connecticut and the AAP-recommended prophylaxis regimen]{County-level variation in the relative timing of the RSV season in Connecticut and the AAP-recommended prophylaxis regimen, showing the gap between season onset and prophylaxis start date, notable particularly in Fairfield county}
 \label{fig:coverageByRegionAAPInsight}
@@
 \input{\figuresDir/coverageByRegionRegimen.tex}
-\caption[Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen]{Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen.
-Spatially adjusted propxylaxis regimens are either non-inferior (for county-level analysis) or superior (for statewide analysis) to the AAP-recommended regimen.
+\caption[Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen]{Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen, showing statewide superiority and county-level non-inferiority of spatially adjusted regimens.
 Preventable fraction: the fraction of all RSV-associated hospitalizations occurring while the prophylaxis regimen provides protection}
@@
 \input{\figuresDir/onsetOffsetByYear.tex}
-\caption{Annual variability in RSV season onset and offset in Connecticut. While season offset has been stable, season onset has shown a statistically significant drift toward an earliear RSV season.}
+\caption{Annual variability in RSV season onset and offset in Connecticut.}
 \label{fig:onsetOffsetByYear}
@@
 \input{\figuresDir/coverageByRegionRegimenWithSliding.tex}
-\caption[Comparison of prophylaxis regimens based on all-years data to those based on recent-years data]{Comparison of prophylaxis regimens based on all-years data to those based on recent-years data.
-Recent-years analysis analysis adds no benefit over all-years analysis, for either statewide or county-level analysis.
+\caption[Comparison of prophylaxis regimens based on all-years data to those based on recent-years data]{Comparison of prophylaxis regimens based on all-years data to those based on recent-years data, showing temporal analysis adds no benefit over spatial analysis alone.
 Preventable fraction: fraction of RSV hospitalizations occurring while the prophylaxis regimen offers protection}

### 2020-07-02 paper/paper.R
Moved this code to avoid dirtying the cache

@@ -222,3 +222,6 @@ draw_key_vline_small = function(data, params, size) {
     )
   )    
 }
+
+totalRSV = sum(dataset$rsv)
+totalYears = max(dataset$epiyear) - min(dataset$epiyear) + 1

### 2020-07-02 analysis/RSV.R
Moved this code to avoid dirtying the cache

@@ -93,9 +93,6 @@ totalRSVByCounty = dataset %>%
   arrange(total_rsv) %>%
   mutate(county=factor(county, county))
 
-totalRSV = sum(dataset$rsv)
-totalYears = max(dataset$epiyear) - min(dataset$epiyear) + 1
-
 rsvCounties = totalRSVByCounty$county
 rsvEpiYears = sort(unique(dataset$epiyear))
 rsvEpiWeekRange = sort(unique(dataset$epiweek))

### 2020-07-02 RSVOptimization.rnw
Typo

@@
 In summary, our analysis reveals the potential for a $\sim 1\%$ gain in preventable RSV cases in Connecticut when a locally-tailored two-week (rather than monthly) prophylaxis guideline is used in place of the established AAP guidelines.
-At an average of $\Sexpr{prettyNum(totalRSV / totalYears, digits=3)}$ RSV-associated hospitalizations per year in children under 2 years old in Connecticut, this corresponds to $\sim \Sexpr{prettyNum(totalRSV / totalYears / 100, digits=4)}$ hospitalizations prevented per year, and an unknown number of prevented cases not necessitating hospitalization.
+At an average of $\Sexpr{prettyNum(totalRSV / totalYears, digits=3)}$ RSV-associated hospitalizations per year in children under 2 years old in Connecticut, this corresponds to $\sim \Sexpr{prettyNum(totalRSV / totalYears / 100, digits=3)}$ hospitalizations prevented per year, and an unknown number of prevented cases not necessitating hospitalization.
 Practical aspects of this potential gain --- such as implementation cost --- require further investigation.

### 2020-07-02 paper/figures.Rnw
Fixing onset/offset facet order

@@
     tikz(sprintf("%s/seasonByRegion.tex", figuresDir), width=1.5*inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
-    onOffLevels = c("onset", "offset")
 

### 2020-07-02 paper/paper.R

@@ -116,9 +116,11 @@ latexPercent = function(f) {
   sprintf("%.0f\\%%", f * 100)
 }
 
-onsetOffsetLabeller = labeller(
-  variable=c(`onset` = "RSV season onset, median (95\\% CI)", `offset` = "RSV season offset, median (95\\% CI)")
-)
+onsetOffsetLabeller = as_labeller(function(labels) {
+  sapply(labels, function(label) {
+    list(`onset` = "RSV season onset, median (95\\% CI)", `offset` = "RSV season offset, median (95\\% CI)")[[label]]
+  })
+})
 
 roundingLabels = c(`0` = "No rounding", `1` = "Weekly rounding", `2` = "Biweekly rounding", `4` = "Monthly rounding")
 
@@ -173,10 +175,13 @@ monthBoundaries = breaks.df %>%
 
 epiWeekBreaks = sort(unique(c(monthBoundaries$min, monthBoundaries$max)))
 
+onOffLevels = c("onset", "offset")
+
 onsetOffsetMonthBoundaries = data.frame(i=c(4, 5, 9, 10), variable=c("onset", "onset", "offset", "offset")) %>%
   inner_join(monthBoundaries, by="i") %>%
-  mutate(label=epiWeekLabels[i])
-  
+  mutate(label=epiWeekLabels[i]) %>%
+  mutate(variable=factor(variable, levels=onOffLevels))
+
 legendLabels = function(labels, leading=0, trailing=2) {
   as.vector(sapply(labels, function(label) {
     if(substr(label, 1, 1) == "_") {

### 2020-07-02 RSVOptimization.rnw

--- 2020-07-02 RSVOptimization.rnw
@@
 \input{\figuresDir/coverageByRegionRegimen.tex}
+\caption[Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen]{Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen, showing statewide superiority and county-level non-inferiority of spatially adjusted regimens.
+Preventable fraction: the fraction of all RSV-associated hospitalizations occurring while the prophylaxis regimen provides protection}
 \caption[Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen]{Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen.

### 2020-07-02 paper/figures.Rnw
Fixed missing y axis label

@@
             legend.title=element_blank(),
-            axis.title.y=element_blank(),
             axis.ticks.x=element_blank(),

### 2020-07-02 data/fetch-dev-data.sh
Simplified data set access

@@ -1,0 +1,1 @@
+ln -s "./rsv.csv" "./data/ct rsv time series.csv"

### 2020-07-09 RSVOptimization.rnw
Fixed duplicated caption
Version bump
Dan’s feedback

@@
     \authorstyle{Ben Artin, MEng, MPH, MMSc\textsuperscript{1}}\\
-    \authorstyle{Daniel Weinberger, PhD\textsuperscript{1}}\\
-    \authorstyle{Virginia E. Pitzer, ScD\textsuperscript{1}}
+    \authorstyle{Virginia E. Pitzer, ScD\textsuperscript{1}}\\
+    \authorstyle{Daniel Weinberger, PhD\textsuperscript{1}}
     \newline\newline
@@
 
-\abstractsection{Background}Respiratory syncytial virus (RSV) causes seasonal respiratory infection with potentially serious complications in children and hospitalization rates of up to 50\% in high-risk infants.
+\abstractsection{Background}Respiratory syncytial virus (RSV) causes seasonal respiratory infection, with hospitalization rates of up to 50\% in high-risk infants.
 Palivizumab provides safe and effective, yet costly, immunoprophylaxis.
 The American Academy of Pediatrics (AAP) recommends palivizumab only for high-risk infants and only during the RSV season.
-Outside of Florida, the current guidelines do not recommend regional adjustments to the immunoprophylaxis regimen.
-We investigate the benefits of adjusting the RSV prophylaxis regimen in Connecticut based on spatial variation of RSV incidence.
+Outside of Florida, the current guidelines do not recommend regional adjustments to the timing of the immunoprophylaxis regimen.
+We investigate the benefits of adjusting the RSV prophylaxis regimen in Connecticut based on spatial variation in the timing of RSV incidence.
 
@@
 
-\abstractsection{Results}Using preventable fraction to assess immunoprophylaxis regimens, we found that regimens adjusted for county-level variation in RSV seasons are superior to the AAP-recommended regimen.
+\abstractsection{Results}The fraction of RSV hospitalizations preventable by the AAP guidelines varies by county because of variations in epidemic timing.
+Prophylaxis regimens adjusted for state- or county-level  variation in the timing of RSV seasons are modestly superior to the AAP-recommended regimen.
 The best alternative strategy yielded a preventable fraction of \Sexpr{regionStrategyCoverage("all", "countyMiddle", 1)} (\Sexpr{regionStrategyCoverageCI("all", "countyMiddle", 1, level)}), compared to \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) for the AAP recommendation.
 
-\abstractsection{Conclusion}Initiating RSV prophylaxis based on county-level data may provide marginal improvement in protection over regimens based on state-level and national data.
+\abstractsection{Conclusion}Initiating RSV prophylaxis based on state-level data may improve protection compared with the standard AAP recommendations.
+In Connecticut, county-level recommendations would provide only a modest additional benefit while adding complexity.
 
@@
 
-Respiratory syncytial virus (RSV) causes upper respiratory tract infections in humans of all ages.
+Respiratory syncytial virus (RSV) causes upper respiratory tract infections in people of all ages.
 In adults, RSV infection is typically asymptomatic or gives rise to mild respiratory illness.
@@
 The relevant variables in the data were ZIP code of residence, patient age, ICD-9 defined diagnoses (up to 10 diagnoses per hospital admission), and week and year of hospital admission.
+The study was approved by the Human Investigation Committees at Yale University and the CT DPH.
+The authors assume full responsibility for analyses and interpretation of the data obtained from CT DPH.
 
@@
 Using the weekly hospitalization data, we identified \Sexpr{prettyNum(totalRSV, big.mark=",")} RSV-associated hospitalizations among \Sexpr{prettyNum(nrow(dataset), big.mark=",")} total hospitalizations of patients <2 years old in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)} (inclusive).
-
-The study was approved by the Human Investigation Committees at Yale University and the CT DPH. The authors assume full responsibility for analyses and interpretation of the data obtained from CT DPH.
 
@@
 Statewide, the AAP guidelines offer protection to \Sexpr{regionStrategyCoverage("all", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}).
-The least favorable of our alternative regimens --- based on county-level offset --- yields an increase in the preventable fraction to \Sexpr{regionStrategyCoverage("all", "countyOffset", 1)} (\Sexpr{regionStrategyCoverageCI("all", "countyOffset", 1, level)}); other alternative regimens yield similar results.
-Most of the increase occurs in Hartford county, where the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", 0, level)}), whereas the least favorable of our alternative regimens --- based on county-level midpoint --- generates an increase to \Sexpr{regionStrategyCoverage("Hartford", "countyMiddle", 1)} (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", 1, level)}), with other alternative regimens being comparable.
+The most favorable of our alternative regimens --- based on statewide midseason --- yields an increase in the preventable fraction to \Sexpr{regionStrategyCoverage("all", "stateMiddle", 1)} (\Sexpr{regionStrategyCoverageCI("all", "stateMiddle", 1, level)}); other alternative regimens yield similar results.
+Most of the increase occurs in Hartford county, where the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", 0, level)}), whereas the most favorable of our alternative regimens --- also based on statewide midseason --- generates an increase to \Sexpr{regionStrategyCoverage("Hartford", "stateMiddle", 1)} (\Sexpr{regionStrategyCoverageCI("Hartford", "stateMiddle", 1, level)}), with other alternative regimens being comparable.
 In every county, all alternative regimens are non-inferior to the AAP guidelines and non-superior to each other.
@@
 \input{\figuresDir/coverageByRegionRegimen.tex}
-\caption[Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen]{Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen, showing statewide superiority and county-level non-inferiority of spatially adjusted regimens.
-Preventable fraction: the fraction of all RSV-associated hospitalizations occurring while the prophylaxis regimen provides protection}
 \caption[Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen]{Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen.

### 2020-07-09 paper/paper.R
Generate rtf output for AAP Pediatrics

@@ -14,7 +14,13 @@ figuresDir = paste0(texOutputDir, "/figures")
 if (!dir.exists(figuresDir)) {
   dir.create(figuresDir, recursive=TRUE)
 }
-options(tikzMetricsDictionary=paste0(texOutputDir, '/tikzDictionary.dat'))
+options(
+  tikzMetricsDictionary=paste0(texOutputDir, '/tikzDictionary.dat'),
+  tikzDocumentDeclaration='\\documentclass[tikz]{standalone}',
+  tikzLatexPackages=c(
+    "\\usepackage{tikz}\n"
+  )
+)
 
 inlinePlotWidth = 3.1
 inlinePlotHeight = 2.5

### 2020-07-09 paper/figures.Rnw
Figure must be standalone for TIF conversion

@@
     library(mapproj)
-    tikz(sprintf("%s/map.tex", figuresDir), width=1.5*inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
+    tikz(sprintf("%s/map.tex", figuresDir), width=1.5*inlinePlotWidth, height=inlinePlotHeight, pointsize=10, standAlone=TRUE)
     US.counties = readOGR(dsn="../data/maps/cb_2016_us_county_5m",layer="cb_2016_us_county_5m")
@@
 <<seasonByRegion, results='hide'>>=
-    tikz(sprintf("%s/seasonByRegion.tex", figuresDir), width=1.5*inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
+    tikz(sprintf("%s/seasonByRegion.tex", figuresDir), width=1.5*inlinePlotWidth, height=inlinePlotHeight, pointsize=10, standAlone=TRUE)
 
@@
 <<coverageByRegionAAP, results='hide'>>=
-    tikz(sprintf("%s/coverageByRegionAAP.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
+    tikz(sprintf("%s/coverageByRegionAAP.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10, standAlone=TRUE)
 
@@
 <<coverageByRegionAAPInsight, results='hide'>>=
-    tikz(sprintf("%s/coverageByRegionAAPInsight.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight, pointsize=10)
+    tikz(sprintf("%s/coverageByRegionAAPInsight.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight, pointsize=10, standAlone=TRUE)
 
@@
 
-    tikz(sprintf("%s/coverageByRegionRegimen.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10)
+    tikz(sprintf("%s/coverageByRegionRegimen.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10, standAlone=TRUE)
     data = unprotectedByCounty %>% 
@@
 <<coverageByRounding, results='hide', warning=FALSE>>=
-    tikz(sprintf("%s/coverageByRoundingRegimen.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10)
+    tikz(sprintf("%s/coverageByRoundingRegimen.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10, standAlone=TRUE)
 
@@
 <<coverageByRegionWithSliding, results='hide', warning=FALSE>>=
-    tikz(sprintf("%s/coverageByRegionRegimenWithSliding.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10)
+    tikz(sprintf("%s/coverageByRegionRegimenWithSliding.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10, standAlone=TRUE)
     data = unprotectedByCounty %>% 
@@
 <<onsetOffsetByYear, results='hide', warning=FALSE>>=
-    tikz(sprintf("%s/onsetOffsetByYear.tex", figuresDir), width=1.5*inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
+    tikz(sprintf("%s/onsetOffsetByYear.tex", figuresDir), width=1.5*inlinePlotWidth, height=inlinePlotHeight, pointsize=10, standAlone=TRUE)
     data = stateThresholdsByWindow %>% 

### 2020-07-09 paper/export-aap-pediatrics.py
Use python instead of sed for more rtf rewriting

@@ -1,0 +1,57 @@
+# Helper for exporting for AAP pediatrics
+# - Inlines bibliography
+# - Renames images to match the text order
+# - Rewrites a few other things to make conversion to RTF work
+
+import re
+import sys
+import os
+import shutil
+
+# Inline the bibliography
+tex = open(sys.argv[1]).read()
+# tex = re.sub(r'\\bibliography\{(.*)\}', lambda f: open(f'{f.group(1)}.bbl').read(), tex)
+
+# Get the figure names (in order) and rename the images
+# Also pull out captions and labels to build list of figures and update references later
+figRE = r'(?s)\\begin\{figure\}.*?\\end\{figure\}'
+graphicRE = r'\\input\{\\figuresDir/(.*)\.tex\}'
+captionRE = r'\\caption(?:\[(.*)\])?\{(.*)\}'
+labelRE = r'\\label\{(.*)\}'
+
+captions = []
+labels = []
+
+for figIdx, figM in enumerate(re.finditer(figRE, tex)):
+	m = re.search(graphicRE, figM.group(0))
+	shutil.copy(f'output/figures/{ m.group(1) }.pdf', f'output/figures/Fig{ figIdx + 1 }.pdf')
+	captions.append(re.search(captionRE, figM.group(0)).group(2))
+	labels.append(re.search(labelRE, figM.group(0)).group(1))
+
+# Change preamble to RTF
+tex = tex.replace(r'paper/preamble.tex', r'paper/preamble-rtf.tex')
+# Drop graphics from figures
+tex = re.sub(r'\\input\{\\figuresDir/(.*)\.tex\}', r'', tex)
+# Delete knitr preamble
+tex = re.sub(r'(?s)(\\documentclass[^\\]*)\\[^\n]*\n.*%%% end knitr preamble', r'\1\n', tex)
+# Delete hangparas, it causes a weird RTF artifact
+tex = re.sub(r'.*\{hangparas\}.*', r'', tex)
+
+# Migrate figures to before appendix. This is basically a list of figures but generated by this script instead of latex
+tex = re.sub(figRE, '', tex)
+lof = '\n'.join(fr"\item \textbf{{Figure {idx + 1}: }}{caption}" for (idx, caption) in enumerate(captions))
+lof = fr'''\section{{List of figures}}
+\begin{{itemize}}
+{ lof }
+\end{{itemize}}
+'''
+
[…]

### 2020-07-20 paper/paper.R
AAP wants percent with 1 decimal place

@@ -74,11 +74,11 @@ regionOffsetCI = function(c, level) {
 }
 
 formatPct = function(pct) {
-  sprintf("%.2f\\%%", pct * 100)
+  sprintf("%.1f\\%%", pct * 100)
 }
 
 formatPctCI = function(lower, upper, level) {
-  sprintf("%d\\%% CI: %.2f -- %.2f\\%%", level * 100, lower * 100, upper * 100)
+  sprintf("%d\\%% CI: %.1f -- %.1f\\%%", level * 100, lower * 100, upper * 100)
 }
 
 regionStrategyCoverage = function(c, s, r) {

### 2020-07-20 RSVOptimization.rnw
Generate rtf output for AAP Pediatrics
First-page abstract for medrxiv
Preprint watermark
Abstract reformatting

@@
 \documentclass[10pt,letter]{article}
-\usepackage{verbatim}
-\usepackage{float}
-\floatplacement{figure}{H}
+%%% end knitr preamble
 
-\usepackage[toc,page]{appendix}
-\renewcommand{\appendixpagename}{Supplements}
-\renewcommand{\appendixname}{Supplements}
+% Do some things differently depending on which variant we're compiling
+\input{paper/preamble.tex}
 
-\usepackage{printlen}
-\usepackage{textcomp}
-\usepackage{setspace}
-
-\usepackage[hidelinks]{hyperref}
-\usepackage[svgnames]{xcolor} % Must go before tikz and before structure.tex
-\usepackage{tikz}
-\usepackage{draftwatermark}
-\SetWatermarkScale{1}
-\SetWatermarkAngle{45}
-\SetWatermarkFontSize{4ex}
-\SetWatermarkHorCenter{12ex}
-\SetWatermarkVerCenter{12ex}
-\SetWatermarkLightness{.5}
-\SetWatermarkText{DRAFT 3}
-
-\input{paper/structure.tex}
-\usepackage{amssymb}
-\usepackage{wasysym}
-
-\usepackage[bf,medium,raggedright,compact]{titlesec}
-\titleformat{\section}{\normalfont\large\bfseries\scshape}{\thesection}{1em}{}
-\titleformat{\subsection}{\normalfont\normalsize\bfseries}{}{0em}{}
-\setcounter{secnumdepth}{3}
-
-\usepackage{hanging}
-\usepackage{graphicx}
-
-\newlength\abstractindent
-\setlength\abstractindent{1in}
-\newcommand{\abstractsection}[1]{\hangpara{\abstractindent}{1}\makebox[1in][l]{\textbf{\textsc{#1}}}}
-\newcommand{\abstractpara}{\hskip\abstractindent\hskip\baseparindent}
-
-\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
-\renewenvironment{knitrout}{\expandafter\comment}{\expandafter\endcomment}
-
+%%% begin knitr output
 <<options, echo=FALSE>>=
-    knitr::opts_chunk$set(echo=FALSE, message=FALSE, error=FALSE)
+    knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
 @
@@
 @
+%%% end knitr output
 
@@
 \section*{\centerline{Abstract}}
-\begin{hangparas}{\abstractindent}{1}
 \begin{onehalfspacing}
 
-\abstractsection{Background}Respiratory syncytial virus (RSV) causes seasonal respiratory infection, with hospitalization rates of up to 50\% in high-risk infants.
+\abstractsection{Background and Objectives} Respiratory syncytial virus (RSV) causes seasonal respiratory infection, with hospitalization rates of up to 50\% in high-risk infants.
 Palivizumab provides safe and effective, yet costly, immunoprophylaxis.
@@
 
-\abstractsection{Methods}We obtained weekly RSV-associated hospital admissions by ZIP-code in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)}.
+\abstractsection{Methods} We obtained weekly RSV-associated hospital admissions by ZIP-code in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)}.
 We estimated the fraction of all RSV cases in Connecticut occurring during the period of protection offered by RSV immunoprophylaxis (``preventable fraction'') under the AAP guidelines.
@@
 
-\abstractsection{Results}The fraction of RSV hospitalizations preventable by the AAP guidelines varies by county because of variations in epidemic timing.
+\abstractsection{Results} The fraction of RSV hospitalizations preventable by the AAP guidelines varies by county because of variations in epidemic timing.
 Prophylaxis regimens adjusted for state- or county-level  variation in the timing of RSV seasons are modestly superior to the AAP-recommended regimen.
@@
 
-\abstractsection{Conclusion}Initiating RSV prophylaxis based on state-level data may improve protection compared with the standard AAP recommendations.
+\abstractsection{Conclusions} Initiating RSV prophylaxis based on state-level data may improve protection compared with the standard AAP recommendations.
 In Connecticut, county-level recommendations would provide only a modest additional benefit while adding complexity.
 
-\abstractpara{}
-
 \end{onehalfspacing}
-\end{hangparas}
 

### 2020-07-20 paper/export-aap-pediatrics.py
LOF like Pediatrics expects

@@ -39,12 +39,7 @@ tex = re.sub(r'.*\{hangparas\}.*', r'', tex)
 
 # Migrate figures to before appendix. This is basically a list of figures but generated by this script instead of latex
 tex = re.sub(figRE, '', tex)
-lof = '\n'.join(fr"\item \textbf{{Figure {idx + 1}: }}{caption}" for (idx, caption) in enumerate(captions))
-lof = fr'''\section{{List of figures}}
-\begin{{itemize}}
-{ lof }
-\end{{itemize}}
-'''
+lof = '\n\n'.join(fr"\textbf{{Figure {idx + 1}: }}{caption}" for (idx, caption) in enumerate(captions))
 
 tex = re.sub(r'(?s)(?=\\phantomsection.*\\addcontentsline\{toc\}\{section\}\{Bibliography\})', lambda m: lof, tex)
 

### 2020-07-20 RSVOptimization.rnw
Standalone figures
Figure caption rewriting for Pediatrics

@@
 \begin{center}
-\input{\figuresDir/map.tex}
+\includestandalone{\figuresDir/map}
 \caption{Subdivision of Connecticut into high-population and low-population counties}
@@
 \begin{center}
-\input{\figuresDir/seasonByRegion.tex}
+\includestandalone{\figuresDir/seasonByRegion}
 \caption{County-level variation in RSV season onset and offset in Connecticut}
@@
 \begin{center}
-\input{\figuresDir/coverageByRegionAAP.tex}
+\includestandalone{\figuresDir/coverageByRegionAAP}
 \caption[County-level variation in the fraction of RSV hospitalizations occurring while the AAP-recommended RSV prophylaxis is active]{County-level variation in the preventable fraction of RSV hospitalizations according to AAP guidelines.
@@
 \begin{center}
-\input{\figuresDir/coverageByRegionAAPInsight.tex}
+\includestandalone{\figuresDir/coverageByRegionAAPInsight}
 \caption[County-level variation in the relative timing of the RSV season in Connecticut and the AAP-recommended prophylaxis regimen]{County-level variation in the relative timing of the RSV season in Connecticut and the AAP-recommended prophylaxis regimen.
@@
 \begin{center}
-\input{\figuresDir/coverageByRegionRegimen.tex}
+\includestandalone{\figuresDir/coverageByRegionRegimen}
 \caption[Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen]{Comparison of six spatially adjusted RSV prophylaxis regimens to the AAP-recommended regimen.
@@
 \begin{center}
-\input{\figuresDir/coverageByRoundingRegimen.tex}
-\caption[The effect of calendrical rounding of start and end of spatially adjusted RSV prophylaxis regimens on their performance]{The effect of calendrical rounding of start and end of spatially adjusted RSV prophylaxis regimens on their performance.
-The preventable fraction (i.e.
-the fraction of all RSV hospitalizations occurring while the prophylaxis regimen offers protection) is plotted for each prophylaxis regimen and for each rounding interval.
-Our results show that longer rounding intervals diminish the benefits of alternative regimens over the AAP-recommended regimen.
-Hollow plot markers ($\raisebox{1pt}{\Circle}$, $\square$, and $\triangle$) denote a prophylaxis strategy which, as a result of rounding, is identical to another, and therefore does not provide additional benefit.}
+\includestandalone{\figuresDir/coverageByRoundingRegimen}
+\caption[The effect of calendrical rounding of start and end of spatially adjusted RSV prophylaxis regimens on their performance]{The effect of calendrical rounding on prophylaxis regimens.
+The fraction of RSV hospitalizations occurring while a regimen offers protection is shown for each regimen and rounding interval.
+Longer rounding intervals diminish the advantage over the AAP-recommended regimen.
+Hollow plot markers ($\raisebox{1pt}{\Circle}$, $\square$, and $\triangle$) denote regimens which, due to rounding, are identical to others.}
 \label{fig:coverageByRoundingRegimen}
@@
 \begin{center}
-\input{\figuresDir/onsetOffsetByYear.tex}
+\includestandalone{\figuresDir/onsetOffsetByYear}
 \caption{Annual variability in RSV season onset and offset in Connecticut. While season offset has been stable, season onset has shown a statistically significant drift toward an earliear RSV season.}
@@
 \begin{center}
-\input{\figuresDir/coverageByRegionRegimenWithSliding.tex}
+\includestandalone{\figuresDir/coverageByRegionRegimenWithSliding}
 \caption[Comparison of prophylaxis regimens based on all-years data to those based on recent-years data]{Comparison of prophylaxis regimens based on all-years data to those based on recent-years data.

### 2020-07-20 RSVOptimization.rnw
Pediatrics frontmatter

@@
 \author{
-    \authorstyle{Ben Artin, MEng, MPH, MMSc\textsuperscript{1}}\\
-    \authorstyle{Virginia E. Pitzer, ScD\textsuperscript{1}}\\
-    \authorstyle{Daniel Weinberger, PhD\textsuperscript{1}}
-    \newline\newline
-    \textsuperscript{1}\institution{Department of Epidemiology of Microbial Diseases, Yale School of Public Health, Yale University}
+    \authorstyle{Ben Artin, MEng, MPH, MMSc\textsuperscript{a}}\\
+    \authorstyle{Virginia E. Pitzer, ScD\textsuperscript{a}}\\
+    \authorstyle{Daniel Weinberger, PhD\textsuperscript{a}}
+}
+
+\postauthor{
+
+    \titlesection{Affiliations}{\textsuperscript{a}Department of Epidemiology of Microbial Diseases, Yale School of Public Health, Yale University}
+
+    \titlesection{Address correspondence to}{Ben Artin, 350 George St, Room 2-xxx, New Haven CT, 06519, ben@artins.org, +1 (617) 953 7243}
+
+    \titlesection{Short title}{Optimization of RSV prophylaxis in Connecticut}
+
+    \titlesection{Conflict of interest disclosures}{The authors have no conflicts of interest to disclose.}
+
+    \titlesection{Funding}{}
+
+    \titlesection{Role of funder}{The NIH had no role in the design and conduct of the study. CT DPH had no role in the design and conduct of the study.}
+
+    \titlesection{Clinical trial registration}{Not applicable.}
+
+    \titlesection{Abbreviations}{RSV: respiratory syncytial virus; AAP: American Academy of Pediatrics; CT DPH: Connecticut Department of Public Health}
+
+    \titlesection{Table of contents summary}{We used Connecticut RSV hospitalization data to propose an adjusted RSV prophylaxis schedule and compare it to the AAP-recommended prophylaxis schedule.}
+
+    \titlesection{What's known on this subject}{RSV is a seasonal respiratory infection, and a major cause of mortality and morbidity in high-risk infants worldwide.
+RSV chemoprophylaxys is expensive.
+In the US, the prophylaxys schedule recommendation is published by the AAP.
+The AAP recommens the same schedule for all states other than Florida.}
+
+    \titlesection{What's this study adds}{We present a method for optimizing the RSV prophylaxis schedule on a regional basis, and show that our method offers only a modest benefit when applied to the state of Connecticut, with no additional benefit when applied to counties within Connecticut.}
+
+    \titlesection{Contributors}{Ben Artin implemented and published the R tools used in the analysis, carried out the analysis, drafted the initial manuscript, and reviewed and revised the manuscript.
+Daniel Weinberger obtained the data from CT DPH, proposed the study design, conceptualized the analytic approach, and reviewed and revised the manuscript.
+Virginia Pitzer reviewed and revised the manuscript.
+All author approved the final manuscript as submitted an agree to be accountable for all aspects of the work.}
 }

### 2020-07-20 RSVOptimization.rnw
Abbreviations in front matter

@@
 
-\abstractsection{Background and Objectives} Respiratory syncytial virus (RSV) causes seasonal respiratory infection, with hospitalization rates of up to 50\% in high-risk infants.
+\abstractsection{Background and Objectives} RSV causes seasonal respiratory infection, with hospitalization rates of up to 50\% in high-risk infants.
 Palivizumab provides safe and effective, yet costly, immunoprophylaxis.
-The American Academy of Pediatrics (AAP) recommends palivizumab only for high-risk infants and only during the RSV season.
+The AAP recommends palivizumab only for high-risk infants and only during the RSV season.
 Outside of Florida, the current guidelines do not recommend regional adjustments to the timing of the immunoprophylaxis regimen.
@@
 
-Respiratory syncytial virus (RSV) causes upper respiratory tract infections in people of all ages.
+RSV causes upper respiratory tract infections in people of all ages.
 In adults, RSV infection is typically asymptomatic or gives rise to mild respiratory illness.
@@
 A monoclonal antibody (palivizumab) is available in the US for prevention of RSV infection in high-risk infants less than 2 years old.
-Palivizumab is administered via intramuscular injection and requires five monthly doses, priced at \$1500-\$3000 per dose.\cite{Hampp:2011ju,Andabaka:2013dr} Palivizumab has been found to be effective in reducing hospitalizations due to RSV; in double-blinded trials in high-risk infants, it reduced the hospitalization rate by 45-55\% compared to placebo.\cite{Group:1998ih,Feltes:2003wm} It has also been found to be safe and well-tolerated.\cite{Group:1998ih} Owing to the high cost, the 2014 revision of the American Academy of Pediatrics (AAP) RSV prophylaxis guidelines recommends palivizumab only for high-risk infants and only during the RSV season.\cite{Anonymous:1998up,AmericanAcademyofPediatricsCommitteeonInfectiousDiseasesandCommitteeonFetusandNewborn:2003ug,AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
+Palivizumab is administered via intramuscular injection and requires five monthly doses, priced at \$1500-\$3000 per dose.\cite{Hampp:2011ju,Andabaka:2013dr} Palivizumab has been found to be effective in reducing hospitalizations due to RSV; in double-blinded trials in high-risk infants, it reduced the hospitalization rate by 45-55\% compared to placebo.\cite{Group:1998ih,Feltes:2003wm} It has also been found to be safe and well-tolerated.\cite{Group:1998ih} Owing to the high cost, the 2014 revision of the AAP RSV prophylaxis guidelines recommends palivizumab only for high-risk infants and only during the RSV season.\cite{Anonymous:1998up,AmericanAcademyofPediatricsCommitteeonInfectiousDiseasesandCommitteeonFetusandNewborn:2003ug,AmericanAcademyofPediatricsCommitteeonInfectiousDiseases:2014bj}
 
@@
 
-We obtained data consisting of all hospitalizations among children <2 years old in Connecticut from 1996 to 2013 from the Connecticut State Inpatient Database through the Connecticut Department of Public Health (CT DPH).
+We obtained data consisting of all hospitalizations among children <2 years old in Connecticut from 1996 to 2013 from the Connecticut State Inpatient Database through the CT DPH.
 The relevant variables in the data were ZIP code of residence, patient age, ICD-9 defined diagnoses (up to 10 diagnoses per hospital admission), and week and year of hospital admission.

### 2020-07-20 RSVOptimization.rnw
No LOF in the front
Pediatrics frontmatter

@@
 \postauthor{
-
+	\vspace{10pt}
     \titlesection{Affiliations}{\textsuperscript{a}Department of Epidemiology of Microbial Diseases, Yale School of Public Health, Yale University}
-
+    \vspace{10pt} % Space before the rule
+	\par{\HorRule} % Horizontal rule after the title
+	\vspace{10pt} % Space after the title section
     \titlesection{Address correspondence to}{Ben Artin, 350 George St, Room 2-xxx, New Haven CT, 06519, ben@artins.org, +1 (617) 953 7243}
-
     \titlesection{Short title}{Optimization of RSV prophylaxis in Connecticut}
-
     \titlesection{Conflict of interest disclosures}{The authors have no conflicts of interest to disclose.}
-
     \titlesection{Funding}{}
-
     \titlesection{Role of funder}{The NIH had no role in the design and conduct of the study. CT DPH had no role in the design and conduct of the study.}
-
     \titlesection{Clinical trial registration}{Not applicable.}
-
     \titlesection{Abbreviations}{RSV: respiratory syncytial virus; AAP: American Academy of Pediatrics; CT DPH: Connecticut Department of Public Health}
-
     \titlesection{Table of contents summary}{We used Connecticut RSV hospitalization data to propose an adjusted RSV prophylaxis schedule and compare it to the AAP-recommended prophylaxis schedule.}
-
     \titlesection{What's known on this subject}{RSV is a seasonal respiratory infection, and a major cause of mortality and morbidity in high-risk infants worldwide.
@@
 The AAP recommens the same schedule for all states other than Florida.}
-
-    \titlesection{What's this study adds}{We present a method for optimizing the RSV prophylaxis schedule on a regional basis, and show that our method offers only a modest benefit when applied to the state of Connecticut, with no additional benefit when applied to counties within Connecticut.}
-
+    \titlesection{What this study adds}{We present a method for optimizing the RSV prophylaxis schedule on a regional basis, and show that our method offers only a modest benefit when applied to the state of Connecticut, with no additional benefit when applied to counties within Connecticut.}
     \titlesection{Contributors}{Ben Artin implemented and published the R tools used in the analysis, carried out the analysis, drafted the initial manuscript, and reviewed and revised the manuscript.
@@
 
-\date{\today}
+\date{}
 
@@
 
-\abstractsection{Background and Objectives} RSV causes seasonal respiratory infection, with hospitalization rates of up to 50\% in high-risk infants.
+\abstractsection{Background and Objectives}{RSV causes seasonal respiratory infection, with hospitalization rates of up to 50\% in high-risk infants.
 Palivizumab provides safe and effective, yet costly, immunoprophylaxis.
@@
 Outside of Florida, the current guidelines do not recommend regional adjustments to the timing of the immunoprophylaxis regimen.
-We investigate the benefits of adjusting the RSV prophylaxis regimen in Connecticut based on spatial variation in the timing of RSV incidence.
+We investigate the benefits of adjusting the RSV prophylaxis regimen in Connecticut based on spatial variation in the timing of RSV incidence.}
 
-\abstractsection{Methods} We obtained weekly RSV-associated hospital admissions by ZIP-code in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)}.
+\abstractsection{Methods}{We obtained weekly RSV-associated hospital admissions by ZIP-code in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)}.
 We estimated the fraction of all RSV cases in Connecticut occurring during the period of protection offered by RSV immunoprophylaxis (``preventable fraction'') under the AAP guidelines.
-We then used the same model to estimate protection conferred by immunoprophylaxis regimens with alternate start dates, but unchanged duration.
+We then used the same model to estimate protection conferred by immunoprophylaxis regimens with alternate start dates, but unchanged duration.}
 
-\abstractsection{Results} The fraction of RSV hospitalizations preventable by the AAP guidelines varies by county because of variations in epidemic timing.
+\abstractsection{Results}{The fraction of RSV hospitalizations preventable by the AAP guidelines varies by county because of variations in epidemic timing.
 Prophylaxis regimens adjusted for state- or county-level  variation in the timing of RSV seasons are modestly superior to the AAP-recommended regimen.
-The best alternative strategy yielded a preventable fraction of \Sexpr{regionStrategyCoverage("all", "countyMiddle", 1)} (\Sexpr{regionStrategyCoverageCI("all", "countyMiddle", 1, level)}), compared to \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) for the AAP recommendation.
-
-\abstractsection{Conclusions} Initiating RSV prophylaxis based on state-level data may improve protection compared with the standard AAP recommendations.
-In Connecticut, county-level recommendations would provide only a modest additional benefit while adding complexity.
+The best alternative strategy yielded a preventable fraction of \Sexpr{regionStrategyCoverage("all", "countyMiddle", 1)} (\Sexpr{regionStrategyCoverageCI("all", "countyMiddle", 1, level)}), compared to \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) for the AAP recommendation.}
 
 \end{onehalfspacing}
+\abstractsection{Conclusions}{Initiating RSV prophylaxis based on state-level data may improve protection compared with the standard AAP recommendations.
+In Connecticut, county-level recommendations would provide only a modest additional benefit while adding complexity.}
 
@@
 
-\listoffigures
-\clearpage
+% \listoffigures
+% \clearpage
 

### 2020-07-20 RSVOptimization.rnw
Spacing
Skip frontmatter for PDF preprint

@@
 	\par{\HorRule} % Horizontal rule after the title
-	\vspace{10pt} % Space after the title section
-    \titlesection{Address correspondence to}{Ben Artin, 350 George St, Room 2-xxx, New Haven CT, 06519, ben@artins.org, +1 (617) 953 7243}
-    \titlesection{Short title}{Optimization of RSV prophylaxis in Connecticut}
-    \titlesection{Conflict of interest disclosures}{The authors have no conflicts of interest to disclose.}
-    \titlesection{Funding}{}
-    \titlesection{Role of funder}{The NIH had no role in the design and conduct of the study. CT DPH had no role in the design and conduct of the study.}
-    \titlesection{Clinical trial registration}{Not applicable.}
-    \titlesection{Abbreviations}{RSV: respiratory syncytial virus; AAP: American Academy of Pediatrics; CT DPH: Connecticut Department of Public Health}
-    \titlesection{Table of contents summary}{We used Connecticut RSV hospitalization data to propose an adjusted RSV prophylaxis schedule and compare it to the AAP-recommended prophylaxis schedule.}
-    \titlesection{What's known on this subject}{RSV is a seasonal respiratory infection, and a major cause of mortality and morbidity in high-risk infants worldwide.
+    \corremail{Address correspondence to}{Ben Artin, ben@artins.org}
+    \corrfull{Address correspondence to}{Ben Artin, 350 George St, Room 2-xxx, New Haven CT, 06519, ben@artins.org, +1 (617) 953 7243}
+    \frontmatter{Short title}{Optimization of RSV prophylaxis in Connecticut}
+    \frontmatter{Conflict of interest disclosures}{The authors have no conflicts of interest to disclose.}
+    \frontmatter{Funding}{}
+    \frontmatter{Role of funder}{The NIH had no role in the design and conduct of the study. CT DPH had no role in the design and conduct of the study.}
+    \frontmatter{Clinical trial registration}{Not applicable.}
+    \frontmatter{Abbreviations}{RSV: respiratory syncytial virus; AAP: American Academy of Pediatrics; CT DPH: Connecticut Department of Public Health}
+    \frontmatter{Table of contents summary}{We used Connecticut RSV hospitalization data to propose an adjusted RSV prophylaxis schedule and compare it to the AAP-recommended prophylaxis schedule.}
+    \frontmatter{What's known on this subject}{RSV is a seasonal respiratory infection, and a major cause of mortality and morbidity in high-risk infants worldwide.
 RSV chemoprophylaxys is expensive.
@@
 The AAP recommens the same schedule for all states other than Florida.}
-    \titlesection{What this study adds}{We present a method for optimizing the RSV prophylaxis schedule on a regional basis, and show that our method offers only a modest benefit when applied to the state of Connecticut, with no additional benefit when applied to counties within Connecticut.}
-    \titlesection{Contributors}{Ben Artin implemented and published the R tools used in the analysis, carried out the analysis, drafted the initial manuscript, and reviewed and revised the manuscript.
+    \frontmatter{What this study adds}{We present a method for optimizing the RSV prophylaxis schedule on a regional basis, and show that our method offers only a modest benefit when applied to the state of Connecticut, with no additional benefit when applied to counties within Connecticut.}
+    \frontmatter{Contributors}{Ben Artin implemented and published the R tools used in the analysis, carried out the analysis, drafted the initial manuscript, and reviewed and revised the manuscript.
 Daniel Weinberger obtained the data from CT DPH, proposed the study design, conceptualized the analytic approach, and reviewed and revised the manuscript.
 Virginia Pitzer reviewed and revised the manuscript.
-All author approved the final manuscript as submitted an agree to be accountable for all aspects of the work.}
+All author approved the final manuscript as submitted and agree to be accountable for all aspects of the work.}
 }
@@
 
-\clearpage
 \endgroup
@@
 \section*{\centerline{Abstract}}
-\begin{onehalfspacing}
 
@@
 
-\end{onehalfspacing}
 \abstractsection{Conclusions}{Initiating RSV prophylaxis based on state-level data may improve protection compared with the standard AAP recommendations.
@@
 % \clearpage
+
+\doublespace
 

### 2020-07-20 paper/structure.tex
Fixing case sensitivity
Fit abstract on page 1
Really fit abstract on page 1
Bibliography inlining
Switched from biblatex to bibtex
https://tex.stackexchange.com/questions/12175/biblatex-submitting-to-a-journal

--- 2019-03-01 Paper/structure.tex
@@
 
-\usepackage[backend=bibtex,style=nejm,sorting=none,autocite=superscript,articledoi=true,url=false]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
-%\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
-\usepackage[nottoc]{tocbibind}
-
-\addbibresource{../RSVOptimization.bib} % The filename of the bibliography
-\renewcommand{\cite}[1]{\autocite{#1}}
-
-\usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography
+\bibliographystyle{ama}

### 2020-07-20 RSVOptimization.rnw
Methods citation
First page adjustments
Switched from biblatex to bibtex
https://tex.stackexchange.com/questions/12175/biblatex-submitting-to-a-journal
Front matter wrangling

@@
 
-\postauthor{
-	\vspace{10pt}
+\newcommand\affiliations{
     \titlesection{Affiliations}{\textsuperscript{a}Department of Epidemiology of Microbial Diseases, Yale School of Public Health, Yale University}
-    \vspace{10pt} % Space before the rule
-	\par{\HorRule} % Horizontal rule after the title
     \corremail{Address correspondence to}{Ben Artin, ben@artins.org}
+}
+
+\newcommand\frontmatter{
     \corrfull{Address correspondence to}{Ben Artin, 350 George St, Room 2-xxx, New Haven CT, 06519, ben@artins.org, +1 (617) 953 7243}
-    \frontmatter{Short title}{Optimization of RSV prophylaxis in Connecticut}
-    \frontmatter{Conflict of interest disclosures}{The authors have no conflicts of interest to disclose.}
-    \frontmatter{Funding}{}
-    \frontmatter{Role of funder}{The NIH had no role in the design and conduct of the study. CT DPH had no role in the design and conduct of the study.}
-    \frontmatter{Clinical trial registration}{Not applicable.}
-    \frontmatter{Abbreviations}{RSV: respiratory syncytial virus; AAP: American Academy of Pediatrics; CT DPH: Connecticut Department of Public Health}
-    \frontmatter{Table of contents summary}{We used Connecticut RSV hospitalization data to propose an adjusted RSV prophylaxis schedule and compare it to the AAP-recommended prophylaxis schedule.}
-    \frontmatter{What's known on this subject}{RSV is a seasonal respiratory infection, and a major cause of mortality and morbidity in high-risk infants worldwide.
+    \frontmattersection{Short title}{Optimization of RSV prophylaxis in Connecticut}
+    \frontmattersection{Conflict of interest disclosures}{The authors have no conflicts of interest to disclose.}
+    \frontmattersection{Funding}{}
+    \frontmattersection{Role of funder}{The NIH had no role in the design and conduct of the study. CT DPH had no role in the design and conduct of the study.}
+    \frontmattersection{Clinical trial registration}{Not applicable.}
+    \frontmattersection{Abbreviations}{RSV: respiratory syncytial virus; AAP: American Academy of Pediatrics; CT DPH: Connecticut Department of Public Health}
+    \frontmattersection{Table of contents summary}{We used Connecticut RSV hospitalization data to propose an adjusted RSV prophylaxis schedule and compare it to the AAP-recommended prophylaxis schedule.}
+    \frontmattersection{What's known on this subject}{RSV is a seasonal respiratory infection, and a major cause of mortality and morbidity in high-risk infants worldwide.
 RSV chemoprophylaxys is expensive.
@@
 The AAP recommens the same schedule for all states other than Florida.}
-    \frontmatter{What this study adds}{We present a method for optimizing the RSV prophylaxis schedule on a regional basis, and show that our method offers only a modest benefit when applied to the state of Connecticut, with no additional benefit when applied to counties within Connecticut.}
-    \frontmatter{Contributors}{Ben Artin implemented and published the R tools used in the analysis, carried out the analysis, drafted the initial manuscript, and reviewed and revised the manuscript.
+    \frontmattersection{What this study adds}{We present a method for optimizing the RSV prophylaxis schedule on a regional basis, and show that our method offers only a modest benefit when applied to the state of Connecticut, with no additional benefit when applied to counties within Connecticut.}
+    \frontmattersection{Contributors}{Ben Artin implemented and published the R tools used in the analysis, carried out the analysis, drafted the initial manuscript, and reviewed and revised the manuscript.
 Daniel Weinberger obtained the data from CT DPH, proposed the study design, conceptualized the analytic approach, and reviewed and revised the manuscript.
@@
 All author approved the final manuscript as submitted and agree to be accountable for all aspects of the work.}
+}
+
+\postauthor{
+	\vspace{10pt}
+    \affiliations
+    \vspace{10pt}
+    \par{\HorRule}
 }
@@
 
-\newlength\baseparindent
-\setlength\baseparindent{\parindent}
-\begingroup
-\setlength\parindent{0em}
-
 \maketitle
+\makefrontmatter
 
@@
 \thispagestyle{firstpage}
-
-\endgroup
 
@@
 To that end, we fit smooth curves through annual RSV hospitalization data and used resampling to obtain confidence intervals.
-This was performed using the \texttt{pspline.inference} package in R, which we developed for this purpose.\cite{psplineInferencePackage,methods}
+This was performed using the \texttt{pspline.inference} package in R, which we developed for this purpose.\cite{psplineInferencePackage,Artin:fe}
 
@@
 \addcontentsline{toc}{section}{Bibliography}
-\printbibliography[title={Bibliography}]
+\bibliography{RSVOptimization}
 

### 2020-07-20 paper/export-aap-pediatrics.py
Bibliography wrangling

@@ -46,6 +46,27 @@ tex = re.sub(r'(?s)(?=\\phantomsection.*\\addcontentsline\{toc\}\{section\}\{Bib
 # Correct figure references
 tex = re.sub(r'\\ref\{(fig:.*?)\}', lambda m: str(labels.index(m.group(1)) + 1), tex)
 
+# Inline the bibliography
+tex = re.sub(r'\\bibliography\{(.*)\}', lambda f: open(f'output/{f.group(1)}.bbl').read(), tex)
+tex = re.sub(r'(?s)\\begin\{thebibliography\}\{.*?\}(.*)\\end\{thebibliography\}', r'\\section*{References}\n\1\n', tex)
+
+# Rewrite citations by turning each into superscript number
+# First identify them and figure out the order
+citeRE = r'\\cite\{(.*?)\}'
+citations = []
+for citeM in re.finditer(citeRE, tex):
+	for cite in citeM.group(1).split(','):
+		if cite not in citations:
+			citations.append(cite)
+
+for idx, cite in enumerate(citations):
+	citationRE = fr'(\\cite\{{(?:[^\{{\}}]+,)?){ re.escape(cite) }((?:,[^\{{\}}]*?)?\}})'
+	tex = re.sub(citationRE, lambda m: f'{ m.group(1) }{ idx + 1 }{ m.group(2) }', tex)
+	bibRE = fr'(\\bibitem\{{){ re.escape(cite) }(\}})'
+	tex = re.sub(bibRE, lambda m: f'[{ idx + 1 }]', tex)
+
+tex = re.sub(citeRE, r'\\textsuperscript{\1}', tex)
+
 # Misc
 tex = tex.replace(r'\raisebox{1pt}{\Circle}', r'\Circle')
 

### 2020-07-20 paper/export-aap-pediatrics.py
Removed obsolete code

@@ -34,8 +34,6 @@ tex = tex.replace(r'paper/preamble.tex', r'paper/preamble-rtf.tex')
 tex = re.sub(r'\\input\{\\figuresDir/(.*)\.tex\}', r'', tex)
 # Delete knitr preamble
 tex = re.sub(r'(?s)(\\documentclass[^\\]*)\\[^\n]*\n.*%%% end knitr preamble', r'\1\n', tex)
-# Delete hangparas, it causes a weird RTF artifact
-tex = re.sub(r'.*\{hangparas\}.*', r'', tex)
 
 # Migrate figures to before appendix. This is basically a list of figures but generated by this script instead of latex
 tex = re.sub(figRE, '', tex)

### 2020-07-20 paper/export-aap-pediatrics.py
Figure wrangling

@@ -15,7 +15,7 @@ tex = open(sys.argv[1]).read()
 # Get the figure names (in order) and rename the images
 # Also pull out captions and labels to build list of figures and update references later
 figRE = r'(?s)\\begin\{figure\}.*?\\end\{figure\}'
-graphicRE = r'\\input\{\\figuresDir/(.*)\.tex\}'
+graphicRE = r'\\includestandalone\{\\figuresDir/(.*)\}'
 captionRE = r'\\caption(?:\[(.*)\])?\{(.*)\}'
 labelRE = r'\\label\{(.*)\}'
 
@@ -31,7 +31,7 @@ for figIdx, figM in enumerate(re.finditer(figRE, tex)):
 # Change preamble to RTF
 tex = tex.replace(r'paper/preamble.tex', r'paper/preamble-rtf.tex')
 # Drop graphics from figures
-tex = re.sub(r'\\input\{\\figuresDir/(.*)\.tex\}', r'', tex)
+tex = re.sub(graphicRE, r'', tex)
 # Delete knitr preamble
 tex = re.sub(r'(?s)(\\documentclass[^\\]*)\\[^\n]*\n.*%%% end knitr preamble', r'\1\n', tex)
 

### 2020-07-21 paper/export-aap-pediatrics.py
Pagination LaTeX→RTF

@@ -65,6 +65,9 @@ for idx, cite in enumerate(citations):
 
 tex = re.sub(citeRE, r'\\textsuperscript{\1}', tex)
 
+# Encode page breaks so that filter can output rtf page breaks later
+tex = re.sub(r'\\clear(double)?page', r'[[clearpage]]', tex)
+
 # Misc
 tex = tex.replace(r'\raisebox{1pt}{\Circle}', r'\Circle')
 

### 2020-07-21 paper/filter-aap-pediatrics.py

@@ -1,0 +1,10 @@
+#!/usr/bin/env python3
+from pandocfilters import toJSONFilter, walk, RawBlock, RawInline, Plain, Para, Str
+from sys import stderr
+
+def behead(key, value, format, meta):
+  if value == "[[clearpage]]":
+    return RawInline("rtf", r"\page")
+
+if __name__ == "__main__":
+  toJSONFilter(behead)

### 2020-07-21 RSVOptimization.rnw
Title edits

@@
 \edef\figuresDir{\Sexpr{figuresDir}}
-\title{Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}}
-\def\headertitle{Evaluating the benefit of initiating RSV prophylaxis based on state- and county-level data}
+\title{Assessment and optimization of respiratory syncytial virus prophylaxis in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}}
+\def\headertitle{Optimization of RSV prophylaxis in Connecticut}
 
@@
     \corrfull{Address correspondence to}{Ben Artin, 350 George St, Room 2-xxx, New Haven CT, 06519, ben@artins.org, +1 (617) 953 7243}
-    \frontmattersection{Short title}{Optimization of RSV prophylaxis in Connecticut}
+    \frontmattersection{Short title}{\headertitle}
     \frontmattersection{Conflict of interest disclosures}{The authors have no conflicts of interest to disclose.}

### 2020-07-21 RSVOptimization.rnw
Front matter tweaks

@@
     \frontmattersection{Conflict of interest disclosures}{The authors have no conflicts of interest to disclose.}
-    \frontmattersection{Funding}{}
-    \frontmattersection{Role of funder}{The NIH had no role in the design and conduct of the study. CT DPH had no role in the design and conduct of the study.}
-    \frontmattersection{Clinical trial registration}{Not applicable.}
+    \frontmattersection{Funding}{This stuy was funded by the NIH grant R01AI137093.}
+    \frontmattersection{Role of funder}{The NIH had no role in the design and conduct of the study.}
+    \frontmattersection{IRB approval}{This study was approved by the IRB at Yale School of Medicine and the HIC at the Connecticut Department of Public Health.}
+    \frontmattersection{Data sharing}{The data can be requested through the Connecticut Department of Public Health.
+The analysis code is available at \url{https://github.com/weinbergerlab/rsv-ct-optimization}.}
     \frontmattersection{Abbreviations}{RSV: respiratory syncytial virus; AAP: American Academy of Pediatrics; CT DPH: Connecticut Department of Public Health}
@@
 Virginia Pitzer reviewed and revised the manuscript.
-All author approved the final manuscript as submitted and agree to be accountable for all aspects of the work.}
+All authors approved the final manuscript as submitted and agree to be accountable for all aspects of the work.}
 }

### 2020-07-21 RSVOptimization.rnw
Typo
Address room number

@@
 \newcommand\frontmatter{
-    \corrfull{Address correspondence to}{Ben Artin, 350 George St, Room 2-xxx, New Haven CT, 06519, ben@artins.org, +1 (617) 953 7243}
+    \corrfull{Address correspondence to}{Ben Artin, 350 George St, Room C323, New Haven CT, 06519, ben@artins.org, +1 (617) 953 7243}
     \frontmattersection{Short title}{\headertitle}
     \frontmattersection{Conflict of interest disclosures}{The authors have no conflicts of interest to disclose.}
-    \frontmattersection{Funding}{This stuy was funded by the NIH grant R01AI137093.}
+    \frontmattersection{Funding}{This study was funded by the NIH/NIAID grant R01AI137093.}
     \frontmattersection{Role of funder}{The NIH had no role in the design and conduct of the study.}

### 2020-07-21 RSVOptimization.rnw
Frontmatter tweaks

@@
     \frontmattersection{Abbreviations}{RSV: respiratory syncytial virus; AAP: American Academy of Pediatrics; CT DPH: Connecticut Department of Public Health}
-    \frontmattersection{Table of contents summary}{We used Connecticut RSV hospitalization data to propose an adjusted RSV prophylaxis schedule and compare it to the AAP-recommended prophylaxis schedule.}
+    \frontmattersection{Article summary}{We used Connecticut RSV hospitalization data to propose an adjusted RSV prophylaxis schedule and compare it to the AAP-recommended prophylaxis schedule.}
     \frontmattersection{What's known on this subject}{RSV is a seasonal respiratory infection, and a major cause of mortality and morbidity in high-risk infants worldwide.
@@
     \frontmattersection{What this study adds}{We present a method for optimizing the RSV prophylaxis schedule on a regional basis, and show that our method offers only a modest benefit when applied to the state of Connecticut, with no additional benefit when applied to counties within Connecticut.}
+    \clearpage
     \frontmattersection{Contributors}{Ben Artin implemented and published the R tools used in the analysis, carried out the analysis, drafted the initial manuscript, and reviewed and revised the manuscript.

### 2020-07-21 RSVOptimization.rnw
Front matter tweaks

@@
     \frontmattersection{IRB approval}{This study was approved by the IRB at Yale School of Medicine and the HIC at the Connecticut Department of Public Health.}
-    \frontmattersection{Data sharing}{The data can be requested through the Connecticut Department of Public Health.
+    \frontmattersection{Data sharing}{Deidentified hospitalization data can be requested from the Connecticut Department of Public Health.
 The analysis code is available at \url{https://github.com/weinbergerlab/rsv-ct-optimization}.}
@@
 All authors approved the final manuscript as submitted and agree to be accountable for all aspects of the work.}
+    \clearpage
 }

### 2020-07-22 paper/filter-aap-pediatrics.py
Fixed sample code naming

@@ -2,9 +2,9 @@
 from pandocfilters import toJSONFilter, walk, RawBlock, RawInline, Plain, Para, Str
 from sys import stderr
 
-def behead(key, value, format, meta):
   if value == "[[clearpage]]":
+def filter(key, value, format, meta):
     return RawInline("rtf", r"\page")
 
 if __name__ == "__main__":
-  toJSONFilter(behead)
+  toJSONFilter(filter)

### 2020-07-22 paper/export-aap-pediatrics.py
Unified page break and spacing into one

@@ -65,8 +65,8 @@ for idx, cite in enumerate(citations):
 
 tex = re.sub(citeRE, r'\\textsuperscript{\1}', tex)
 
-# Encode page breaks so that filter can output rtf page breaks later
-tex = re.sub(r'\\clear(double)?page', r'[[clearpage]]', tex)
+# Encode page breaks and spacing so that filter can output rtf commands later
+tex = re.sub(r'\\(clear(?:double)?page|(:?double|single)spacing)', lambda m: rf'[[{m.group(1)}]]', tex)
 
 # Misc
 tex = tex.replace(r'\raisebox{1pt}{\Circle}', r'\Circle')

### 2020-07-22 paper/filter-aap-pediatrics.py

@@ -2,9 +2,23 @@
 from pandocfilters import toJSONFilter, walk, RawBlock, RawInline, Plain, Para, Str
 from sys import stderr
 
-  if value == "[[clearpage]]":
+doublespace = False
+
 def filter(key, value, format, meta):
+  global doublespace
+  if value in ("[[clearpage]]", "[[cleardoublepage]]"):
     return RawInline("rtf", r"\page")
+  elif value == "[[doublespacing]]":
+    doublespace = True
+    return []
+  elif value == "[[singlespacing]]":
+    doublespace = False
+    return []
+  elif key == 'Para':
+    return Para([
+      RawInline("rtf", r"\sl480\slmult1") if doublespace else RawInline("rtf", r"\sl240\slmult1")
+    ] + value)
 
 if __name__ == "__main__":
   toJSONFilter(filter)
+

### 2020-07-22 RSVOptimization.rnw
Switch to single spacing for LOF and references
Abstract tweaks

@@
 Outside of Florida, the current guidelines do not recommend regional adjustments to the timing of the immunoprophylaxis regimen.
-We investigate the benefits of adjusting the RSV prophylaxis regimen in Connecticut based on spatial variation in the timing of RSV incidence.}
+Our hypothesis is that adjusting the RSV prophylaxis regimen in Connecticut based on spatial variation in the timing of RSV incidence can reduce the disease burden compared to the current AAP-recommended RSV prophylaxis regimen.}
 
@@
 Prophylaxis regimens adjusted for state- or county-level variation in the timing of RSV seasons are modestly superior to the AAP-recommended regimen.
-The best alternative strategy yielded a preventable fraction of \Sexpr{regionStrategyCoverage("all", "countyMiddle", 1)} (\Sexpr{regionStrategyCoverageCI("all", "countyMiddle", 1, level)}), compared to \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) for the AAP recommendation.}
+The best alternative strategy yielded a preventable fraction of \Sexpr{regionStrategyCoverage("all", "stateMiddle", 1)} (\Sexpr{regionStrategyCoverageCI("all", "stateMiddle", 1, level)}), compared to \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) for the AAP recommendation.}
 
@@
 
-\doublespace
+\doublespacing
 
@@
 
+\singlespacing
+
 \phantomsection
@@
 
+\doublespacing
 \section{Supplemental methods}

### 2020-07-26 RSVOptimization.rnw
Separated supplemental figures

@@
 
+\listoffigures
+
 \phantomsection
@@
 
-After we applied weekly, biweekly, and monthly rounding to start and end dates of our six alternative immunoprophylaxis regimens, we found that longer rounding intervals diminished the benefit of tailoring the guidelines to local data (Supplemental figure \ref{fig:coverageByRoundingRegimen}).
+After we applied weekly, biweekly, and monthly rounding to start and end dates of our six alternative immunoprophylaxis regimens, we found that longer rounding intervals diminished the benefit of tailoring the guidelines to local data (Supplemental figure \ref{suppfig:coverageByRoundingRegimen}).
 With weekly rounding, our regimens were non-inferior to the AAP recommendation, and produced an increase in preventable fraction from \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) under the AAP guidelines to \Sexpr{bestCaseCoverage(1)} (\Sexpr{bestCaseCoverageCI(1, level)}) statewide.
@@
 
-\begin{figure}
+\begin{supplementalfigure}
 \begin{center}
@@
 Hollow plot markers ($\raisebox{1pt}{\Circle}$, $\square$, and $\triangle$) denote regimens which, due to rounding, are identical to others.}
-\label{fig:coverageByRoundingRegimen}
+\label{suppfig:coverageByRoundingRegimen}
 \end{center}
-\end{figure}
+\end{supplementalfigure}
 
@@
 
-Our linear regression of median RSV season onset and offset over three-year periods indicates that season onset has slowly been drifting earlier (Supplemental figure \ref{fig:onsetOffsetByYear}), at a rate of \Sexpr{formatDrift(onsetByYear)} (\Sexpr{formatDriftCI(onsetByYear, level)}).
+Our linear regression of median RSV season onset and offset over three-year periods indicates that season onset has slowly been drifting earlier (Supplemental figure \ref{suppfig:onsetOffsetByYear}), at a rate of \Sexpr{formatDrift(onsetByYear)} (\Sexpr{formatDriftCI(onsetByYear, level)}).
 It is unclear whether this is a part of a larger pattern, such as a cycle spanning decades.
@@
 \caption{Annual variability in RSV season onset and offset in Connecticut. While season offset has been stable, season onset has shown a statistically significant drift toward an earliear RSV season.}
-\label{fig:onsetOffsetByYear}
+\label{suppfig:onsetOffsetByYear}
 \end{center}
-\end{figure}
+\end{supplementalfigure}
 
@@
 
-Compared to our county-level all-years analysis, the three regimens based on statewide recent-years analysis produced non-superior results everywhere and inferior results in the low-population counties (Supplemental figure \ref{fig:coverageByRegionRegimenWithSliding}).
+Compared to our county-level all-years analysis, the three regimens based on statewide recent-years analysis produced non-superior results everywhere and inferior results in the low-population counties (Supplemental figure \ref{suppfig:coverageByRegionRegimenWithSliding}).
 Due to the non-superiority of regimens based on statewide recent-years analysis, we did not evaluate regimens based on county-level recent-years data.
 
-\begin{figure}
+\begin{supplementalfigure}
 \begin{center}
@@
 Preventable fraction: fraction of RSV hospitalizations occurring while the prophylaxis regimen offers protection}
-\label{fig:coverageByRegionRegimenWithSliding}
+\label{suppfig:coverageByRegionRegimenWithSliding}
 \end{center}
-\end{figure}
+\end{supplementalfigure}
+
+\singlespacing
+\listofsupplementalfigures
+\doublespacing
 

### 2020-07-26 paper/export-aap-pediatrics.py

@@ -14,19 +14,20 @@ tex = open(sys.argv[1]).read()
 
 # Get the figure names (in order) and rename the images
 # Also pull out captions and labels to build list of figures and update references later
-figRE = r'(?s)\\begin\{figure\}.*?\\end\{figure\}'
+figRE = r'(?s)\\begin\{([^\}]*figure)\}.*?\\end\{[^\}]*figure\}'
 graphicRE = r'\\includestandalone\{\\figuresDir/(.*)\}'
 captionRE = r'\\caption(?:\[(.*)\])?\{(.*)\}'
 labelRE = r'\\label\{(.*)\}'
 
-captions = []
-labels = []
+captions = {}
+labels = {}
 
 for figIdx, figM in enumerate(re.finditer(figRE, tex)):
 	m = re.search(graphicRE, figM.group(0))
+	figType = figM.group(1)
 	shutil.copy(f'output/figures/{ m.group(1) }.pdf', f'output/figures/Fig{ figIdx + 1 }.pdf')
-	captions.append(re.search(captionRE, figM.group(0)).group(2))
-	labels.append(re.search(labelRE, figM.group(0)).group(1))
+	captions.setdefault(figType, []).append(re.search(captionRE, figM.group(0)).group(2))
+	labels.setdefault(figType, []).append(re.search(labelRE, figM.group(0)).group(1))
 
 # Change preamble to RTF
 tex = tex.replace(r'paper/preamble.tex', r'paper/preamble-rtf.tex')
@@ -35,14 +36,18 @@ tex = re.sub(graphicRE, r'', tex)
 # Delete knitr preamble
 tex = re.sub(r'(?s)(\\documentclass[^\\]*)\\[^\n]*\n.*%%% end knitr preamble', r'\1\n', tex)
 
-# Migrate figures to before appendix. This is basically a list of figures but generated by this script instead of latex
+# Migrate figure captions to end of main/supplemental text
 tex = re.sub(figRE, '', tex)
-lof = '\n\n'.join(fr"\textbf{{Figure {idx + 1}: }}{caption}" for (idx, caption) in enumerate(captions))
+lof = '\n\n'.join(fr"\textbf{{Figure {idx + 1}: }}{caption}" for (idx, caption) in enumerate(captions['figure']))
+tex = re.sub(r'\\listoffigures', lambda m: lof, tex)
 
[…]

### 2020-07-26 paper/aap-pediatrics-cover.tex
Cover letter for Pediatrics

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Thin Formal Letter
% LaTeX Template
% Version 2.0 (7/2/17)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Author:
% Vel (vel@LaTeXTemplates.com)
%
% Originally based on an example on WikiBooks 
% (http://en.wikibooks.org/wiki/LaTeX/Letters) but rewritten as of v2.0
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{letter} % 10pt font size default, 11pt and 12pt are also possible

\usepackage{geometry} % Required for adjusting page dimensions

%\longindentation=0pt % Un-commenting this line will push the closing "Sincerely," to the left of the page

\geometry{
	paper=letterpaper, % Change to letterpaper for US letter
	top=1in, % Top margin
	bottom=1in, % Bottom margin
	left=2in, % Left margin
	right=2in, % Right margin
	%showframe, % Uncomment to show how the type block is set on the page
}

\usepackage[T1]{fontenc} % Output font encoding for international characters
\usepackage[utf8]{inputenc} % Required for inputting international characters

\usepackage{stix} % Use the Stix font by default

\usepackage{microtype} % Improve justification
\usepackage{url}

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\signature{Ben Artin} % Your name for the signature at the bottom

\address{Ben Artin \\ ben@artins.org \\ 350 College St Rm C323 \\ New Haven, CT 06519} % Your address and phone number

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{} % Name/title of the addressee

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{\textbf{Dear \textit{Pediatrics} editor,}}

I am pleased to submit an original research article titled \textit{Assessment and optimization of respiratory syncytial virus prophylaxis in Connecticut, 1996-2013} by Ben Artin, Virginia E. Pitzer, an Daniel M. Weinberger for consideration for publication in \textit{Pediatrics}. In this manuscript, we developed a general method of evaluating timing of RSV prophylaxis and applied it to RSV-associated hospitalization data in Connecticut to show that regionally-adjusted prophylaxis regimens would confer a modest improvement over the current AAP-recommended regimen.

We believe that this manuscript is appropriate for publication by \textit{Pediatrics} because of the impact of RSV on infant hospitalizations, mortality, and morbidity, as well as the role of your audience in implementing RSV prophylaxis guidelines.

This manuscript has not been published elsewhere and is not under consideration for publication elsewhere. Should it be published in \textit{Pediatrics}, it will not be published elsewhere without the editors' consent. Preprint is available on medRxiv at \url{https://doi.org/10.1101/2020.07.13.20152215}. All authors have participated in the concept and design, analysis and interpretation of data, and drafting or revising of the manuscript, have approved the manuscript as submitted, and are responsible for the reported research.

Our conflicts of interest are: Virginia E. Pitzer has received reimbursement from Merck and Pfizer for travel expenses to Scientific Input Engagements related to RSV vaccines. Daniel M. Weinberger has received consulting fees from Pfizer, Merck, GSK, and Affinivax for topics unrelated to this manuscript and is the Principal Investigator on a research grant from Pfizer on an unrelated topic. Ben Artin reports no relevant conflicts.

Thank you for your consideration!

\vspace{2\parskip} % Extra whitespace for aesthetics
\closing{Sincerely,}
\vspace{2\parskip} % Extra whitespace for aesthetics

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}

### 2020-07-27 paper/export-aap-pediatrics.py
Better figure naming

@@ -22,12 +22,18 @@ labelRE = r'\\label\{(.*)\}'
 captions = {}
 labels = {}
 
-for figIdx, figM in enumerate(re.finditer(figRE, tex)):
+for figM in re.finditer(figRE, tex):
 	m = re.search(graphicRE, figM.group(0))
 	figType = figM.group(1)
-	shutil.copy(f'output/figures/{ m.group(1) }.pdf', f'output/figures/Fig{ figIdx + 1 }.pdf')
-	captions.setdefault(figType, []).append(re.search(captionRE, figM.group(0)).group(2))
-	labels.setdefault(figType, []).append(re.search(labelRE, figM.group(0)).group(1))
+	captions.setdefault(figType, [])
+	labels.setdefault(figType, [])
+
+	figIdx = len(captions[figType]) + 1
+	figName = f"Fig{ figIdx }.pdf" if figType == 'figure' else f"SuppFig{ figIdx }.pdf"
+	shutil.copy(f'output/figures/{ m.group(1) }.pdf', f'output/figures/{ figName }')
+
+	captions[figType].append(re.search(captionRE, figM.group(0)).group(2))
+	labels[figType].append(re.search(labelRE, figM.group(0)).group(1))
 
 # Change preamble to RTF
 tex = tex.replace(r'paper/preamble.tex', r'paper/preamble-rtf.tex')

### 2020-07-27 RSVOptimization.rnw

@@
     \authorstyle{Virginia E. Pitzer, ScD\textsuperscript{a}}\\
-    \authorstyle{Daniel Weinberger, PhD\textsuperscript{a}}
+    \authorstyle{Daniel M. Weinberger, PhD\textsuperscript{a}}
 }
@@
     \frontmattersection{Short title}{\headertitle}
-    \frontmattersection{Conflict of interest disclosures}{The authors have no conflicts of interest to disclose.}
+    \frontmattersection{Conflict of interest disclosures}{Virginia E.
+Pitzer has received reimbursement from Merck and Pfizer for travel expenses to Scientific Input Engagements related to RSV vaccines.
+Daniel M.
+Weinberger has received consulting fees from Pfizer, Merck, GSK, and Affinivax for topics unrelated to this manuscript and is the Principal Investigator on a research grant from Pfizer on an unrelated topic.
+Ben Artin reports no relevant conflicts.}
     \frontmattersection{Funding}{This study was funded by the NIH/NIAID grant R01AI137093.}
@@
 RSV chemoprophylaxys is expensive.
-In the US, the prophylaxys schedule recommendation is published by the AAP.
+In the US, the prophylaxis schedule recommendation is published by the AAP.
 The AAP recommens the same schedule for all states other than Florida.}
@@
     \frontmattersection{Contributors}{Ben Artin implemented and published the R tools used in the analysis, carried out the analysis, drafted the initial manuscript, and reviewed and revised the manuscript.
-Daniel Weinberger obtained the data from CT DPH, proposed the study design, conceptualized the analytic approach, and reviewed and revised the manuscript.
-Virginia Pitzer reviewed and revised the manuscript.
+Daniel M.
+Weinberger obtained the data from CT DPH, proposed the study design, conceptualized the analytic approach, and reviewed and revised the manuscript.
+Virginia E.
+Pitzer reviewed and revised the manuscript.
 All authors approved the final manuscript as submitted and agree to be accountable for all aspects of the work.}

### 2020-07-27 paper/aap-pediatrics-cover.tex

@@
 Weinberger for consideration for publication in \textit{Pediatrics}.
-In this manuscript, we developed a general method of evaluating timing of RSV prophylaxis and applied it to RSV-associated hospitalization data in Connecticut to show that regionally-adjusted prophylaxis regimens would confer a modest improvement over the current AAP-recommended regimen.
+The American Academyc of Pediatrics makes recommendations about when to start prophylaxis against RSV.
+Aside from Florida, the recommended start date is the same for the entire US.
+Using county-level data from Connecticut, we considered whether a recommended start date that varies by state or county would provide any benefit compared with the national recommendation.
+We find that a state-specific prophylaxis regimen would confer a modest improvement over the current AAP-recommended regimen.
+This general approach could be used to evaluate the timing of prophylaxis in other states as well.
 

### 2020-07-27 paper/structure.tex
Separated supplemental figures

@@
 \usepackage{subcaption}
+\DeclareCaptionType{supplementalfigure}[Supplemental Figure][List of supplemental figures]
 
@@
 
-\newcommand{\authorstyle}[1]{{\large\usefont{OT1}{phv}{b}{n}\color{DarkRed}#1}} % Authors style (Helvetica)
+\newcommand{\authorstyle}[1]{{\noindent\large\usefont{OT1}{phv}{b}{n}\color{DarkRed}#1}} % Authors style (Helvetica)
 

### 2020-07-27 paper/figures.Rnw
Improved label layout for Fig 3

@@
 <<coverageByRegionAAP, results='hide'>>=
-    tikz(sprintf("%s/coverageByRegionAAP.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10, standAlone=TRUE)
+    tikz(sprintf("%s/coverageByRegionAAP.tex", figuresDir), width=1.5*inlinePlotWidth, height=inlinePlotHeight, pointsize=10, standAlone=TRUE)
 
@@
             axis.ticks.x=element_blank(),
-            axis.text.x=element_text(angle=30, hjust=0.5, vjust=0.5)
+            axis.text.x=element_text(hjust=0.5, vjust=0.5)
         )

### 2020-07-28 paper/aap-pediatrics-cover.tex
Typo
Duplicative work

@@
 Weinberger for consideration for publication in \textit{Pediatrics}.
-The American Academyc of Pediatrics makes recommendations about when to start prophylaxis against RSV.
+The American Academy of Pediatrics makes recommendations about when to start prophylaxis against RSV.
 Aside from Florida, the recommended start date is the same for the entire US.
@@
 All authors have participated in the concept and design, analysis and interpretation of data, and drafting or revising of the manuscript, have approved the manuscript as submitted, and are responsible for the reported research.
+
+The same data was used in: Noveroske Douglas Brian. Respiratory syncytial virus in Connecticut: Predictors of seasonal epidemic timing \textit{Public Health Theses}. 2016.
 

### 2020-07-28 RSVOptimization.rnw
Removed rogue list of tables/figures
Adjustments for Pediatrics word limits

@@
 RSV chemoprophylaxys is expensive.
-In the US, the prophylaxis schedule recommendation is published by the AAP.
-The AAP recommens the same schedule for all states other than Florida.}
-    \frontmattersection{What this study adds}{We present a method for optimizing the RSV prophylaxis schedule on a regional basis, and show that our method offers only a modest benefit when applied to the state of Connecticut, with no additional benefit when applied to counties within Connecticut.}
+In the US, the AAP recommends the same schedule for all states other than Florida.}
+    \frontmattersection{What this study adds}{We present a method for optimizing the RSV prophylaxis schedule on a regional basis, and show that our method offers only a modest benefit when applied to Connecticut, with no additional benefit when applied to counties within Connecticut.}
     \clearpage
@@
 Outside of Florida, the current guidelines do not recommend regional adjustments to the timing of the immunoprophylaxis regimen.
-Our hypothesis is that adjusting the RSV prophylaxis regimen in Connecticut based on spatial variation in the timing of RSV incidence can reduce the disease burden compared to the current AAP-recommended RSV prophylaxis regimen.}
+Our hypothesis is that adjusting the RSV prophylaxis regimen in Connecticut based on spatial variation in the timing of RSV incidence can reduce the disease burden compared to the current AAP-recommended prophylaxis regimen.}
 
 \abstractsection{Methods}{We obtained weekly RSV-associated hospital admissions by ZIP-code in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)}.
-We estimated the fraction of all RSV cases in Connecticut occurring during the period of protection offered by RSV immunoprophylaxis (``preventable fraction'') under the AAP guidelines.
+We estimated the fraction of all Connecticut RSV cases occurring during the period of protection offered by immunoprophylaxis (``preventable fraction'') under the AAP guidelines.
 We then used the same model to estimate protection conferred by immunoprophylaxis regimens with alternate start dates, but unchanged duration.}
@@
 
-\abstractsection{Conclusions}{Initiating RSV prophylaxis based on state-level data may improve protection compared with the standard AAP recommendations.
+\abstractsection{Conclusions}{Initiating RSV prophylaxis based on state-level data may improve protection compared with the AAP recommendations.
 In Connecticut, county-level recommendations would provide only a modest additional benefit while adding complexity.}
@@
 \pagestyle{fancy}
-
-%\listoftables
-%\clearpage
-
-% \listoffigures
-% \clearpage
 

### 2020-07-29 paper/export-aap-pediatrics.py
RTF is a lie

@@ -77,7 +77,7 @@ for idx, cite in enumerate(citations):
 tex = re.sub(citeRE, r'\\textsuperscript{\1}', tex)
 
 # Encode page breaks and spacing so that filter can output rtf commands later
-tex = re.sub(r'\\(clear(?:double)?page|(:?double|single)spacing)', lambda m: rf'[[{m.group(1)}]]', tex)
+tex = re.sub(r'\\(clear(?:double)?page|(:?double|single)spacing)', lambda m: f'[[{m.group(1)}]]\n', tex)
 
 # Misc
 tex = tex.replace(r'\raisebox{1pt}{\Circle}', r'\Circle')

### 2020-07-29 paper/filter-aap-pediatrics.py

@@ -7,7 +7,7 @@ doublespace = False
 def filter(key, value, format, meta):
   global doublespace
   if value in ("[[clearpage]]", "[[cleardoublepage]]"):
-    return RawInline("rtf", r"\page")
+    return RawInline("openxml", r'<w:r><w:br w:type="page"/></w:r>')
   elif value == "[[doublespacing]]":
     doublespace = True
     return []
@@ -16,7 +16,7 @@ def filter(key, value, format, meta):
     return []
   elif key == 'Para':
     return Para([
-      RawInline("rtf", r"\sl480\slmult1") if doublespace else RawInline("rtf", r"\sl240\slmult1")
+      RawInline("openxml", r'<w:pPr><w:spacing w:line="480" w:lineRule="auto"/></w:pPr>') if doublespace else RawInline("openxml", r'<w:pPr><w:spacing w:line="240" w:lineRule="auto"/></w:pPr>')
     ] + value)
 
 if __name__ == "__main__":

### 2020-10-04 RSVOptimization.rnw
Refactored for SciRep

@@
-\documentclass[10pt,letter]{article}
+\documentclass[10pt,letter]{wlscirep}
 %%% end knitr preamble
@@
 \title{Assessment and optimization of respiratory syncytial virus prophylaxis in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}}
-\def\headertitle{Optimization of RSV prophylaxis in Connecticut}
 
-\author{
-    \authorstyle{Ben Artin, MEng, MPH, MMSc\textsuperscript{a}}\\
-    \authorstyle{Virginia E. Pitzer, ScD\textsuperscript{a}}\\
-    \authorstyle{Daniel M. Weinberger, PhD\textsuperscript{a}}
-}
+\author[1,*]{Ben Artin, MEng, MPH, MMSc}
+\author[1]{Virginia E. Pitzer, ScD}
+\author[1]{Daniel M. Weinberger, PhD}
+\affil[1]{Department of Epidemiology of Microbial Diseases, Yale School of Public Health, Yale University}
+\affil[*]{ben@artins.org}
 
-\newcommand\affiliations{
-    \titlesection{Affiliations}{\textsuperscript{a}Department of Epidemiology of Microbial Diseases, Yale School of Public Health, Yale University}
-    \corremail{Address correspondence to}{Ben Artin, ben@artins.org}
-}
-
-\newcommand\frontmatter{
-    \corrfull{Address correspondence to}{Ben Artin, 350 George St, Room C323, New Haven CT, 06519, ben@artins.org, +1 (617) 953 7243}
-    \frontmattersection{Short title}{\headertitle}
-    \frontmattersection{Conflict of interest disclosures}{Virginia E.
-Pitzer has received reimbursement from Merck and Pfizer for travel expenses to Scientific Input Engagements related to RSV vaccines.
-Daniel M.
-Weinberger has received consulting fees from Pfizer, Merck, GSK, and Affinivax for topics unrelated to this manuscript and is the Principal Investigator on a research grant from Pfizer on an unrelated topic.
-Ben Artin reports no relevant conflicts.}
-    \frontmattersection{Funding}{This study was funded by the NIH/NIAID grant R01AI137093.}
-    \frontmattersection{Role of funder}{The NIH had no role in the design and conduct of the study.}
-    \frontmattersection{IRB approval}{This study was approved by the IRB at Yale School of Medicine and the HIC at the Connecticut Department of Public Health.}
-    \frontmattersection{Data sharing}{Deidentified hospitalization data can be requested from the Connecticut Department of Public Health.
-The analysis code is available at \url{https://github.com/weinbergerlab/rsv-ct-optimization}.}
-    \frontmattersection{Abbreviations}{RSV: respiratory syncytial virus; AAP: American Academy of Pediatrics; CT DPH: Connecticut Department of Public Health}
-    \frontmattersection{Article summary}{We used Connecticut RSV hospitalization data to propose an adjusted RSV prophylaxis schedule and compare it to the AAP-recommended prophylaxis schedule.}
-    \frontmattersection{What's known on this subject}{RSV is a seasonal respiratory infection, and a major cause of mortality and morbidity in high-risk infants worldwide.
-RSV chemoprophylaxys is expensive.
-In the US, the AAP recommends the same schedule for all states other than Florida.}
-    \frontmattersection{What this study adds}{We present a method for optimizing the RSV prophylaxis schedule on a regional basis, and show that our method offers only a modest benefit when applied to Connecticut, with no additional benefit when applied to counties within Connecticut.}
-    \clearpage
-    \frontmattersection{Contributors}{Ben Artin implemented and published the R tools used in the analysis, carried out the analysis, drafted the initial manuscript, and reviewed and revised the manuscript.
-Daniel M.
-Weinberger obtained the data from CT DPH, proposed the study design, conceptualized the analytic approach, and reviewed and revised the manuscript.
-Virginia E.
-Pitzer reviewed and revised the manuscript.
-All authors approved the final manuscript as submitted and agree to be accountable for all aspects of the work.}
-    \clearpage
-}
-
-\postauthor{
-	\vspace{10pt}
-    \affiliations
-    \vspace{10pt}
-    \par{\HorRule}
-}
-
-\date{}
-
-\pagestyle{empty}
-\begin{document}
-
-\maketitle
-\makefrontmatter
-
-% TODO DPH acknowledgement
-% TODO better month labels in onset-offset plots
-
-\thispagestyle{firstpage}
-
-\section*{\centerline{Abstract}}
+\begin{abstract}
 
@@
 Our hypothesis is that adjusting the RSV prophylaxis regimen in Connecticut based on spatial variation in the timing of RSV incidence can reduce the disease burden compared to the current AAP-recommended prophylaxis regimen.}
-
 \abstractsection{Methods}{We obtained weekly RSV-associated hospital admissions by ZIP-code in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)}.
@@
 We then used the same model to estimate protection conferred by immunoprophylaxis regimens with alternate start dates, but unchanged duration.}
-
 \abstractsection{Results}{The fraction of RSV hospitalizations preventable by the AAP guidelines varies by county because of variations in epidemic timing.
@@
 The best alternative strategy yielded a preventable fraction of \Sexpr{regionStrategyCoverage("all", "stateMiddle", 1)} (\Sexpr{regionStrategyCoverageCI("all", "stateMiddle", 1, level)}), compared to \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) for the AAP recommendation.}
-
 \abstractsection{Conclusions}{Initiating RSV prophylaxis based on state-level data may improve protection compared with the AAP recommendations.
@@
 
+\end{abstract}
+
+\begin{document}
+
+\maketitle
+
+\thispagestyle{empty}
+
 \clearpage
-
-\pagestyle{fancy}
-
-\doublespacing
 
@@
 
-% Separate paragraph here because seasonal variation above, prophylaxis optimization below
-
 Our effort to optimize timing of the prophylaxis regimen (without changing its duration and therefore its pharmaceutical cost) shows a potential $\sim1\%$ statewide decrease in RSV-associated hospitalizations among high-risk infants each year, primarily in counties with higher RSV burden (Fairfield, Hartford, and New Haven counties).
@@
 
-\singlespacing
-
-\listoffigures
-
 \phantomsection
@@
 \bibliography{RSVOptimization}
+
+\section*{Author contributions statement}
+
+B.A.
+implemented and published the R tools used in the analysis, carried out the analysis, drafted the initial manuscript, and reviewed and revised the manuscript.
+D.M.W.
+obtained the data from CT DPH, proposed the study design, conceptualized the analytic approach, and reviewed and revised the manuscript.
+V.E.P.
+reviewed and revised the analytic approach, and reviewed and revised the manuscript.
+All authors approved the final manuscript as submitted and agree to be accountable for all aspects of the work.
+
+\section*{Additional information}
+
+\textbf{Competing interests:} Virginia E.
+Pitzer has received reimbursement from Merck and Pfizer for travel expenses to Scientific Input Engagements related to RSV vaccines.
+Daniel M.
+Weinberger has received consulting fees from Pfizer, Merck, GSK, and Affinivax for topics unrelated to this manuscript and is the Principal Investigator on a research grant from Pfizer on an unrelated topic.
+Ben Artin reports no relevant conflicts.
+
+\listoffigures
 
@@
 \setcounter{figure}{0}
+\renewcommand{\thesection}{S\arabic{section}}
 \renewcommand{\thesubsection}{S\arabic{section}.\arabic{subsection}}
@@
 
-\doublespacing
 \section{Supplemental methods}
@@
 
-\singlespacing
 \listofsupplementalfigures
-\doublespacing
 

### 2020-10-04 paper/structure.tex
Refactored for SciRep

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Wenneker Article
-% Structure Specification File
-% Version 1.0 (28/2/17)
-%
-% This file originates from:
-% http://www.LaTeXTemplates.com
-%
-% Authors:
-% Frits Wenneker
-% Vel (vel@LaTeXTemplates.com)
-%
-% License:
-% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 %----------------------------------------------------------------------------------------
@@
 
-\usepackage[svgnames]{xcolor} % Enabling colors by their 'svgnames'
-
-\usepackage[hang, small, labelfont=bf, up, textfont=it]{caption} % Custom captions under/above tables and figures
+\usepackage[labelfont=bf, textfont=it]{caption} % Custom captions under/above tables and figures
 \usepackage{subcaption}
@@
 \usepackage{booktabs} % Horizontal rules in tables
-
-\usepackage{lastpage} % Used to determine the number of pages in the document (for "Page X of Total")
 
@@
 \allsectionsfont{\usefont{OT1}{phv}{b}{n}} % Change the font of all section commands (Helvetica)
-
-%----------------------------------------------------------------------------------------
-%	MARGINS AND SPACING
-%----------------------------------------------------------------------------------------
-
-\usepackage{geometry} % Required for adjusting page dimensions
-
-\geometry{
-	top=1cm, % Top margin
-	bottom=1.5cm, % Bottom margin
-	left=2.5cm, % Left margin
-	right=1.5cm, % Right margin
-	includehead, % Include space for a header
-	includefoot, % Include space for a footer
-	%showframe, % Uncomment to show how the type block is set on the page
-}
-
-\setlength{\columnsep}{7mm} % Column separation width
-
-%----------------------------------------------------------------------------------------
-%	FONTS
-%----------------------------------------------------------------------------------------
-
-\usepackage{fontspec} % Output font encoding for international characters
-\usepackage{luatexbase} % Output font encoding for international characters
-
-\usepackage{XCharter} % Use the XCharter font
-
-%----------------------------------------------------------------------------------------
-%	HEADERS AND FOOTERS
-%----------------------------------------------------------------------------------------
-
-\usepackage{fancyhdr} % Needed to define custom headers/footers
-\pagestyle{fancy} % Enables the custom headers/footers
-
-\renewcommand{\headrulewidth}{0.0pt} % No header rule
-\renewcommand{\footrulewidth}{0.4pt} % Thin footer rule
-
-\renewcommand{\sectionmark}[1]{\markboth{#1}{}} % Removes the section number from the header when \leftmark is used
-
-%\nouppercase\leftmark % Add this to one of the lines below if you want a section title in the header/footer
-
-% Headers
-\lhead{} % Left header
-\chead{\textit{\headertitle}} % Center header - currently printing the article title
-\rhead{} % Right header
-
-% Footers
-\lfoot{} % Left footer
-\cfoot{} % Center footer
-\fancyfoot[RO,LE]{\footnotesize Page \thepage\ of \pageref{LastPage}} % Right footer, "Page 1 of 2"
-
-\fancypagestyle{firstpage}{ % Page style for the first page with the title
-	\fancyhf{}
-	\renewcommand{\footrulewidth}{0pt} % Suppress footer rule
-}
-
-%----------------------------------------------------------------------------------------
-%	TITLE SECTION
-%----------------------------------------------------------------------------------------
-
-\newcommand{\authorstyle}[1]{{\noindent\large\usefont{OT1}{phv}{b}{n}\color{DarkRed}#1}} % Authors style (Helvetica)
-
-\newcommand{\institution}[1]{{\footnotesize\usefont{OT1}{phv}{m}{sl}\color{Black}#1}} % Institutions style (Helvetica)
-
-\usepackage{titling} % Allows custom title configuration
-
-\newcommand{\HorRule}{\color{DarkGoldenrod}\rule{\linewidth}{1pt}} % Defines the gold horizontal rule around the title
-
-\pretitle{
-	\vspace{-30pt} % Move the entire title section up
-	\HorRule\vspace{10pt} % Horizontal rule before the title
-	\fontsize{32}{36}\usefont{OT1}{phv}{b}{n}\selectfont % Helvetica
-	\color{DarkRed} % Text colour for the title and author(s)
-	\raggedright
-}
-
-\posttitle{\par\vskip 15pt} % Whitespace under the title
-
-\preauthor{} % Anything that will appear before \author is printed
-
-\postauthor{ % Anything that will appear after \author is printed
-	\vspace{10pt} % Space before the rule
-	\par\HorRule % Horizontal rule after the title
-	\vspace{20pt} % Space after the title section
-}
-
-%----------------------------------------------------------------------------------------
-%	ABSTRACT
-%----------------------------------------------------------------------------------------
-
-\usepackage{lettrine} % Package to accentuate the first letter of the text (lettrine)
-\usepackage{fix-cm}	% Fixes the height of the lettrine
-
-\newcommand{\initial}[1]{ % Defines the command and style for the lettrine
-	\lettrine[lines=3,findent=4pt,nindent=0pt]{% Lettrine takes up 3 lines, the text to the right of it is indented 4pt and further indenting of lines 2+ is stopped
-		\color{DarkGoldenrod}% Lettrine colour
-		{#1}% The letter
-	}{}%
-}
-
-\usepackage{xstring} % Required for string manipulation
-
-\newcommand{\lettrineabstract}[1]{
-	\StrLeft{#1}{1}[\firstletter] % Capture the first letter of the abstract for the lettrine
-	\initial{\firstletter}\textbf{\StrGobbleLeft{#1}{1}} % Print the abstract with the first letter as a lettrine and the rest in bold
-}
-
-%----------------------------------------------------------------------------------------
-%	BIBLIOGRAPHY
-%----------------------------------------------------------------------------------------
-
-\bibliographystyle{ama}

### 2020-10-04 paper/export-nature-scirep.py

@@ -1,7 +1,6 @@
-# Helper for exporting for AAP pediatrics
+# Helper for exporting for Nature Scientific Reports
 # - Inlines bibliography
 # - Renames images to match the text order
-# - Rewrites a few other things to make conversion to RTF work
 
 import re
 import sys
@@ -10,7 +9,6 @@ import shutil
 
 # Inline the bibliography
 tex = open(sys.argv[1]).read()
-# tex = re.sub(r'\\bibliography\{(.*)\}', lambda f: open(f'{f.group(1)}.bbl').read(), tex)
 
 # Get the figure names (in order) and rename the images
 # Also pull out captions and labels to build list of figures and update references later
@@ -35,21 +33,16 @@ for figM in re.finditer(figRE, tex):
 	captions[figType].append(re.search(captionRE, figM.group(0)).group(2))
 	labels[figType].append(re.search(labelRE, figM.group(0)).group(1))
 
-# Change preamble to RTF
-tex = tex.replace(r'paper/preamble.tex', r'paper/preamble-rtf.tex')
-# Drop graphics from figures
-tex = re.sub(graphicRE, r'', tex)
 # Delete knitr preamble
 tex = re.sub(r'(?s)(\\documentclass[^\\]*)\\[^\n]*\n.*%%% end knitr preamble', r'\1\n', tex)
 
 # Migrate figure captions to end of main/supplemental text
 tex = re.sub(figRE, '', tex)
-lof = '\n\n'.join(fr"\textbf{{Figure {idx + 1}: }}{caption}" for (idx, caption) in enumerate(captions['figure']))
+lof = r"\section{List of figures}" + '\n\n'.join(fr"\textbf{{Figure {idx + 1}: }}{caption}" for (idx, caption) in enumerate(captions['figure']))
 tex = re.sub(r'\\listoffigures', lambda m: lof, tex)
 
-supplof = '\n\n'.join(fr"\textbf{{Supplemental figure {idx + 1}: }}{caption}" for (idx, caption) in enumerate(captions['supplementalfigure']))
+supplof = r"\section{List of supplemental figures}" + '\n\n'.join(fr"\textbf{{Supplemental figure {idx + 1}: }}{caption}" for (idx, caption) in enumerate(captions['supplementalfigure']))
[…]

### 2020-10-04 RSVOptimization.rnw
Simplifications
Supplemental → supplementary

@@
 
-% Do some things differently depending on which variant we're compiling
+% Packages and options
 \input{paper/preamble.tex}
@@
 In all these regimens, prophylaxis consists of five monthly doses of palivizumab, and protection is assumed to last 24 weeks from the first dose.
-We rounded each alternative regimen to the nearest week to more closely reflect how prophylaxis guidelines might be implemented in practice (Supplemental Methods \ref{smethod:rounding}).
+We rounded each alternative regimen to the nearest week to more closely reflect how prophylaxis guidelines might be implemented in practice (Supplementary Methods \ref{smethod:rounding}).
 
@@
 
-%TODO citation needed re small subgroup
-
 Given that high-risk infants are a small subgroup of the general population, we assumed that our model of RSV hospitalizations among all infants is an unbiased approximation of RSV hospitalizations among high-risk infants, and therefore that the preventable fraction of a prophylactic regimen is an unbiased estimate of the fraction of high-risk infants who benefit from prophylaxis.
@@
 
-In addition to the 1-week rounding of our alternative prophylaxis schedules, we also calculated schedules using 2- and 4-week rounding, to assess the impact of calendrical rounding on prophylaxis performance (Supplemental Methods \ref{smethod:rounding}).
+In addition to the 1-week rounding of our alternative prophylaxis schedules, we also calculated schedules using 2- and 4-week rounding, to assess the impact of calendrical rounding on prophylaxis performance (Supplementary Methods \ref{smethod:rounding}).
 
-To analyze the effects of year-to-year variation between RSV seasons, we performed a similar analysis, but with the prophylaxis start date in a given year determined by the median RSV season timing during the preceding three years, rather than all years (Supplemental Methods \ref{smethod:seasonDrift} and \ref{smethod:temporalAdjustment}).
+To analyze the effects of year-to-year variation between RSV seasons, we performed a similar analysis, but with the prophylaxis start date in a given year determined by the median RSV season timing during the preceding three years, rather than all years (Supplementary Methods \ref{smethod:seasonDrift} and \ref{smethod:temporalAdjustment}).
 
@@
 
-We also applied 2-week and 4-week rounding to the start and end dates of our six alternative immunoprophylaxis regimens, and found that doing so diminished or erased the potential benefits (Supplemental Results \ref{sresult:rounding}).
-Finally, we analyzed long-term trends in the RSV season onset and offset and found that the season onset may be moving earlier (Supplemental Results \ref{sresult:seasonDrift}), but that accounting for that drift did not yield a significant further increase in preventable RSV cases (Supplemental Results \ref{sresult:temporalAdjustment}).
+We also applied 2-week and 4-week rounding to the start and end dates of our six alternative immunoprophylaxis regimens, and found that doing so diminished or erased the potential benefits (Supplementary Results \ref{sresult:rounding}).
+Finally, we analyzed long-term trends in the RSV season onset and offset and found that the season onset may be moving earlier (Supplementary Results \ref{sresult:seasonDrift}), but that accounting for that drift did not yield a significant further increase in preventable RSV cases (Supplementary Results \ref{sresult:temporalAdjustment}).
 
@@
 
-\section{Supplemental methods}
+\section{Supplementary methods}
 
@@
 
-\section{Supplemental results}
+\section{Supplementary results}
 
@@
 
-After we applied weekly, biweekly, and monthly rounding to start and end dates of our six alternative immunoprophylaxis regimens, we found that longer rounding intervals diminished the benefit of tailoring the guidelines to local data (Supplemental figure \ref{suppfig:coverageByRoundingRegimen}).
+After we applied weekly, biweekly, and monthly rounding to start and end dates of our six alternative immunoprophylaxis regimens, we found that longer rounding intervals diminished the benefit of tailoring the guidelines to local data (Supplementary figure \ref{suppfig:coverageByRoundingRegimen}).
 With weekly rounding, our regimens were non-inferior to the AAP recommendation, and produced an increase in preventable fraction from \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) under the AAP guidelines to \Sexpr{bestCaseCoverage(1)} (\Sexpr{bestCaseCoverageCI(1, level)}) statewide.
@@
 
-\begin{supplementalfigure}
+\begin{supplementaryfigure}
 \begin{center}
@@
 \end{center}
-\end{supplementalfigure}
+\end{supplementaryfigure}
 
@@
 
-Our linear regression of median RSV season onset and offset over three-year periods indicates that season onset has slowly been drifting earlier (Supplemental figure \ref{suppfig:onsetOffsetByYear}), at a rate of \Sexpr{formatDrift(onsetByYear)} (\Sexpr{formatDriftCI(onsetByYear, level)}).
+Our linear regression of median RSV season onset and offset over three-year periods indicates that season onset has slowly been drifting earlier (Supplementary figure \ref{suppfig:onsetOffsetByYear}), at a rate of \Sexpr{formatDrift(onsetByYear)} (\Sexpr{formatDriftCI(onsetByYear, level)}).
 It is unclear whether this is a part of a larger pattern, such as a cycle spanning decades.
@@
 
-Compared to our county-level all-years analysis, the three regimens based on statewide recent-years analysis produced non-superior results everywhere and inferior results in the low-population counties (Supplemental figure \ref{suppfig:coverageByRegionRegimenWithSliding}).
+Compared to our county-level all-years analysis, the three regimens based on statewide recent-years analysis produced non-superior results everywhere and inferior results in the low-population counties (Supplementary figure \ref{suppfig:coverageByRegionRegimenWithSliding}).
 Due to the non-superiority of regimens based on statewide recent-years analysis, we did not evaluate regimens based on county-level recent-years data.
 
-\begin{supplementalfigure}
+\begin{supplementaryfigure}
 \begin{center}
@@
 \end{center}
-\end{supplementalfigure}
+\end{supplementaryfigure}
 
-\listofsupplementalfigures
+\listofsupplementaryfigures
 

### 2020-10-04 paper/export-nature-scirep.py

@@ -36,17 +36,17 @@ for figM in re.finditer(figRE, tex):
 # Delete knitr preamble
 tex = re.sub(r'(?s)(\\documentclass[^\\]*)\\[^\n]*\n.*%%% end knitr preamble', r'\1\n', tex)
 
-# Migrate figure captions to end of main/supplemental text
+# Migrate figure captions to end of main/supplementary text
 tex = re.sub(figRE, '', tex)
 lof = r"\section{List of figures}" + '\n\n'.join(fr"\textbf{{Figure {idx + 1}: }}{caption}" for (idx, caption) in enumerate(captions['figure']))
 tex = re.sub(r'\\listoffigures', lambda m: lof, tex)
 
-supplof = r"\section{List of supplemental figures}" + '\n\n'.join(fr"\textbf{{Supplemental figure {idx + 1}: }}{caption}" for (idx, caption) in enumerate(captions['supplementalfigure']))
-tex = re.sub(r'\\listofsupplementalfigures', lambda m: supplof, tex)
+supplof = r"\section{List of supplementary figures}" + '\n\n'.join(fr"\textbf{{Supplementary figure {idx + 1}: }}{caption}" for (idx, caption) in enumerate(captions['supplementaryfigure']))
+tex = re.sub(r'\\listofsupplementaryfigures', lambda m: supplof, tex)
 
 # Correct figure references
 tex = re.sub(r'\\ref\{(fig:.*?)\}', lambda m: str(labels['figure'].index(m.group(1)) + 1), tex)
-tex = re.sub(r'\\ref\{(suppfig:.*?)\}', lambda m: str(labels['supplementalfigure'].index(m.group(1)) + 1), tex)
+tex = re.sub(r'\\ref\{(suppfig:.*?)\}', lambda m: str(labels['supplementaryfigure'].index(m.group(1)) + 1), tex)
 
 # Inline the bibliography
 tex = re.sub(r'\\bibliography\{(.*)\}', lambda f: open(f'output/{f.group(1)}.bbl').read(), tex)

### 2020-10-04 paper/nature-scirep-cover.tex
Fit cover on one page

--- 2020-07-27 paper/aap-pediatrics-cover.tex
@@
 
-\opening{\textbf{Dear \textit{Pediatrics} editor,}}
+\opening{\textbf{Dear \textit{Scientific Reports} editor,}}
 
@@
 Pitzer, an Daniel M.
-Weinberger for consideration for publication in \textit{Pediatrics}.
-The American Academyc of Pediatrics makes recommendations about when to start prophylaxis against RSV.
+Weinberger for consideration for publication in \textit{Scientific Reports}.
+The American Academy of Pediatrics makes recommendations about when to start prophylaxis against respiratory syncytial virus (RSV).
 Aside from Florida, the recommended start date is the same for the entire US.
@@
 
-We believe that this manuscript is appropriate for publication by \textit{Pediatrics} because of the impact of RSV on infant hospitalizations, mortality, and morbidity, as well as the role of your audience in implementing RSV prophylaxis guidelines.
+We believe that this manuscript is appropriate for publication by \textit{Scientific Reports} because of the impact of RSV on infant hospitalizations, mortality, and morbidity, as well as the role of your audience in setting and carrying out RSV prophylaxis guidelines.
 
 This manuscript has not been published elsewhere and is not under consideration for publication elsewhere.
-Should it be published in \textit{Pediatrics}, it will not be published elsewhere without the editors' consent.
+It has not been previously discussed with an EBM.
+Should it be published in \textit{Scientific Reports}, it will not be published elsewhere without the editors' consent.
 Preprint is available on medRxiv at \url{https://doi.org/10.1101/2020.07.13.20152215}.

### 2020-10-06 analysis/RSV.R
Refactored using plz

@@ -15,7 +15,7 @@ data(zipcode)
 set.seed(0)
 
 if (as.logical(Sys.getenv("KNITR_DRAFT_MODE", "FALSE"))) {
-  simulations = 5
+  simulations = 1
 } else {
   simulations = 2000
 }

### 2020-10-06 data/fetch-dev-data.sh

@@ -1,1 +1,1 @@
-ln -s "./rsv.csv" "./data/ct rsv time series.csv"
+ln -s "/data/rsv.csv" "ct rsv time series.csv"

### 2020-10-11 data/fetch-dev-data.sh
Data file location change to avoid GitLab errors

@@ -1,1 +1,1 @@
-ln -s "/data/rsv.csv" "ct rsv time series.csv"
+ln -s "/data/rsv.csv" "data/ct rsv time series.csv"

### 2020-10-13 RSVOptimization.rnw
Switched to using plz for builds
Put abbreviations back in main text

@@
 % Packages and options
-\input{paper/preamble.tex}
+\input{preamble.tex}
 
@@
 
-\abstractsection{Background and Objectives}{RSV causes seasonal respiratory infection, with hospitalization rates of up to 50\% in high-risk infants.
+\abstractsection{Background and Objectives}{Respiratory syncytial virus (RSV) causes seasonal respiratory infection, with hospitalization rates of up to 50\% in high-risk infants.
 Palivizumab provides safe and effective, yet costly, immunoprophylaxis.
-The AAP recommends palivizumab only for high-risk infants and only during the RSV season.
+The American Academy of Pediatrics (AAP) recommends palivizumab only for high-risk infants and only during the RSV season.
 Outside of Florida, the current guidelines do not recommend regional adjustments to the timing of the immunoprophylaxis regimen.
@@
 
-We obtained data consisting of all hospitalizations among children <2 years old in Connecticut from 1996 to 2013 from the Connecticut State Inpatient Database through the CT DPH.
+We obtained data consisting of all hospitalizations among children <2 years old in Connecticut from 1996 to 2013 from the Connecticut State Inpatient Database through the Connecticut Department of Public Health (CT DPH).
 The relevant variables in the data were ZIP code of residence, patient age, ICD-9 defined diagnoses (up to 10 diagnoses per hospital admission), and week and year of hospital admission.

### 2020-10-20 paper/nature-scirep-cover.tex
Clickable link

@@
 \usepackage{geometry} % Required for adjusting page dimensions
+\usepackage[hidelinks,breaklinks=true]{hyperref} % Required for adjusting page dimensions
 
@@
 We find that a state-specific prophylaxis regimen would confer a modest improvement over the current AAP-recommended regimen.
-This general approach could be used to evaluate the timing of prophylaxis in other states as well.
+This approach could also be used to evaluate the timing of prophylaxis in other states.
 
@@
 
+The same data was used in: Noveroske Douglas Brian. Respiratory syncytial virus in Connecticut: Predictors of seasonal epidemic timing \textit{Public Health Theses}. 2016.
+
 Our conflicts of interest are: Virginia E.
@@
 
-\vspace{2\parskip} % Extra whitespace for aesthetics
+\vspace{1\parskip} % Extra whitespace for aesthetics
 \closing{Sincerely,}
-\vspace{2\parskip} % Extra whitespace for aesthetics
+\vspace{1\parskip} % Extra whitespace for aesthetics
 

### 2021-03-30 RSVOptimization.rnw
Separate main and supplement PDF
No abstract in supplement
TItle page for supplement
Reviewer feedback

@@
 \affil[1]{Department of Epidemiology of Microbial Diseases, Yale School of Public Health, Yale University}
-\affil[*]{ben@artins.org}
+\affil[*]{Correspondence to ben@artins.org}
 
+% No abstract in supplement
+\ifdef\skipmain{\def\noabstract}{
 \begin{abstract}
-
 \abstractsection{Background and Objectives}{Respiratory syncytial virus (RSV) causes seasonal respiratory infection, with hospitalization rates of up to 50\% in high-risk infants.
@@
 \abstractsection{Results}{The fraction of RSV hospitalizations preventable by the AAP guidelines varies by county because of variations in epidemic timing.
-Prophylaxis regimens adjusted for state- or county-level variation in the timing of RSV seasons are modestly superior to the AAP-recommended regimen.
+Prophylaxis regimens adjusted for state- or county-level variation in the timing of RSV seasons \cbstart are superior \cbend to the AAP-recommended regimen.
 The best alternative strategy yielded a preventable fraction of \Sexpr{regionStrategyCoverage("all", "stateMiddle", 1)} (\Sexpr{regionStrategyCoverageCI("all", "stateMiddle", 1, level)}), compared to \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}) for the AAP recommendation.}
-\abstractsection{Conclusions}{Initiating RSV prophylaxis based on state-level data may improve protection compared with the AAP recommendations.
-In Connecticut, county-level recommendations would provide only a modest additional benefit while adding complexity.}
+\abstractsection{Conclusions}{\cbstart In Connecticut, county-level recommendations would provide only a minimal additional benefit while adding complexity.
+Initiating RSV prophylaxis based on state-level data may improve protection compared with the AAP recommendations.
+\cbend}
 
 \end{abstract}
+}
 
@@
 
+\ifdef\skipmain{}{
 \clearpage
-
 \section{Introduction}
@@
 In adults, RSV infection is typically asymptomatic or gives rise to mild respiratory illness.
-However, RSV infection often incites more serious respiratory illness in children, with hospitalization rates as high as 4.4\% in infants with no comorbidities, making RSV a leading cause of hospitalization among infants.\cite{Hall:2009gi,Hall:2013jo,Zhou:2012ho,Boyce:2000gz}
+However, RSV infection often incites more serious respiratory illness in children, with hospitalization rates as high as 4.4\% in infants with no comorbidities, making RSV a leading cause of hospitalization among infants.\cite{Hall:2009gi,Hall:2013jo,Zhou:2012ho,Boyce:2000gz} \cbstart Adults act as a reservoir of RSV and thereore play an important role in RSV mortality and morbidity in infants.
+\cbend
 
@@
 
+\cbstart Further improvement in disease burden could likely be attained by extending the duration of the prophylaxis regimen to cover both the start and the end of the RSV season in the most populous counties (especially Fairfield county), but doing so would likely require extending the prophylaxis regimen by one additional dose and therefore increae the overall cost.
+\cbend
+
 Although we found a weak statewide trend in RSV season onset becoming earlier over time, further analysis did not yield any improvements to the preventable fraction of the prophylaxis regimen based on that trend.
@@
 Practical aspects of this potential gain --- such as implementation cost --- require further investigation.
-Additionally, the method we developed for this analysis can be applied to county-level or state-level analysis of seasonal RSV patterns in other regions, some of which are likely to show a greater relative benefit (due to a greater degree of misalignment between the RSV season and the AAP guidelines' prophylaxis window) as well as a greater absolute benefit (due to population size) than Connecticut.
+
+\cbstart Additionally, the method we developed for this analysis can be applied to county-level or state-level analysis of seasonal RSV patterns in other regions, some of which are likely to show a greater relative benefit (due to a greater degree of misalignment between the RSV season and the AAP guidelines' prophylaxis window) as well as a greater absolute benefit (due to population size) than Connecticut.
+In particular, states of the US Pacific Northwest would likely benefit more than Connecticut, due to their later RSV season.\cite{Weinberger:2015hj} A similar approach is applicable to any other intervention against RSV that is sensitive to timing, including maternal vaccines and novel chemoprophylaxis.
+\cbend
 
@@
 \listoffigures
+
+} % main
+
+\ifdef\skipsupplement{}{
 
@@
 
+} % supplement
 \end{document}

### 2021-04-20 paper/reviewer-response.tex

\documentclass{article}
\usepackage{markdown}
\usepackage{csquotes}

\setcounter{secnumdepth}{0}

\begin{document}
\begin{markdown*}{hybrid}

To the Editor,

We are pleased to submit the revision for our manuscript “Assessment and optimization of respiratory syncytial virus prophylaxis in Connecticut, 1996-2013” for consideration in Scientific Reports. We thank the reviewers for their feedback and have edited the manuscript to address their suggestions. Most of these changes are in the introduction, abstract, and discussion. Specific responses to their comments are below.

## Reviewer 1

\begin{displayquote}
With interest I read the paper by Artin and colleagues describing spatial variation in RSV seasonality may be used to optimize RSV immunoprophylaxis. The authors analyzed the proportion of RSV-related hospitalizations when applying AAP guidelines at a state level or  county level in Connecticut from 1996-2013. They analyzed whether county-specific adjustment of immunoprophylaxis would improve palivizumab use. The results show that there are differences (up to one month) in county-specific RSV epidemiology, but that refinement of immunoprophylaxis only provide little added value over the current AAP guidelines which do not take into account local variation in RSV epidemiology. Apparently, applying the the AAP guidelines already covers 92-97\% (according to figure 5) of the preventable burden. The study is simple and reads well. It is relevant to the large audience of researchers and policy makers in the field of RSV prevention. The methods used are appropriate for the research question.
\end{displayquote}

Thank you for your positive feedback.

#### The paper would increase interest from an even broader audience when a paragraph in the discussion would be added in which the authors speculate how and where the results can be applied to have stronger impact than in Connecticut.

We updated the discussion as requested. In particular, we added the following paragraph:

"The method we developed for this analysis can be applied to county-level or state-level analysis of seasonal RSV patterns in other regions, some of which are likely to show a greater relative benefit (due to a greater degree of misalignment between the RSV season and the AAP guidelines' prophylaxis window) as well as a greater absolute benefit (due to population size) than Connecticut. In particular, states of the US Upper Midwest and Pacific Northwest would likely benefit more than Connecticut, due both to their later RSV season and to the greater county-to-county differences in RSV season timing in those states.\cite{Weinberger:2015hj} A similar approach is applicable to other interventions against RSV that are sensitive to timing, including maternal vaccines and novel chemoprophylaxis."

##### 1. Are there US states in which a more impressive effect could be observed?

Based on our prior work on ascertaining state- and county-level seasonality patterns of RSV, we might expect to see a larger benefit of diverging from the CDC recommended start dates in the Upper Midwest and Pacific Northwest\footnote{See https://pubmed.ncbi.nlm.nih.gov/25904370}. It is possible that local/county-level recommendations might be more beneficial in states with more heterogeneous epidemic timing. Unfortunately, we do not have access to local RSV epidemic data for other states. Applying the method introduced by this paper to RSV hospitalization data from other states would be a natural next step in our research. We have added comments about these points to the discussion, as noted above.

##### 2. Would there be applicability in low and middle income countries with acceptable surveillance?

Regardless of availability of surveillance, palivizumab is not widely used in LMIC settings due to its high cost. However, the same principles could apply to the use of cheaper or long-lasting prophylaxis and to the use of maternal vaccines, both of which would benefit from appropriate timing of the intervention. We have added a comment to the discussion about the general use of this approach for any intervention against RSV that depends on timing, regardless of context, and about the need for local surveillance data.

##### 3. Could syndromic surveillance in LMIC be sufficient to apply such local use of RSV immunoprophylaxis?

Syndromic surveillance (e.g., for bronchiolitis) is often a good proxy for RSV activity and could therefore be used in a similar way in LMIC settings (potentially for different interventions, as mentioned in response #2).

##### 4. Do the results have any relevance after upcoming introduction of nirsevimab?

While the specific application discussed in the paper (palivizumab) will likely become less relevant, the principle of this study will still be useful, for example when considering the administration of maternal vaccines and nirsevimab. The guidelines for nirsevimab administration in infants may still include a component of seasonality, since clinical trials of nirsevimab have been limited to 150-day clinical endpoints\footnote{See https://www.nejm.org/doi/full/10.1056/NEJMoa1913556}. Likewise, administration of maternal vaccines might benefit from seasonal timing. Our method (as well as the R package we implemented to facilitate the use of that method in other research) will remain relevant and will likely be applicable to those questions.

## Reviewer 2

\begin{displayquote}
“Artin et al. have examined the timing of the onset and offset dates for the use of palivizumab in the state of Connecticut. Palivizumab is used to treat infants with underlying conditions that predispose them to severe consequences of respiratory syncytial virus (RSV) infection during their first year of life. Current practice is to use the average numbers for the whole state. They found that the onset and offset of RSV season varies, depending on the county, with the larger counties reaching the threshold earlier than the less populous counties. They conclude that “initiating RSV prophylaxis based on state-level data may improve protection compared with the AAP recommendations. In Connecticut, county-level recommendations would provide only a modest additional benefit while adding complexity.”
\end{displayquote}

Thank you for your review and your feedback.

##### In the Abstract, a 1\% difference seems to be less than “modest”, as it is described.

We have changed this to “minimal”.

##### Abstract conclusion – Switch the order of the sentences so that the conclusion comes first, and the alternative comes last.

We have reordered this as suggested.

##### Introduction, first paragraph. RSV is also a problem for elders, causing 10,000 to 14,000 deaths/year in the US. It’s not the point of this report, but it is a major source of health problems caused by RSV. Could RSV from elders possibly be the source of the RSV in infants?

The reviewer is correct to point out the burden of disease in the elderly. Also, adults in general, including elders, are a reservoir of RSV and transmission between adults and infants is a likely factor in epidemiology of RSV. However, as you remarked, this is not central to the topic of this paper, and therefore was not discussed. Nevertheless, we added a sentence about the importance of RSV in adults to the introduction.

##### Because Fairfield, the most populous county starts its RSV season before the less populous counties, the chances of preventing hospitalizations by palivizumab treatment is only 91.9\% effective while the treatment in the least populous county is 96.6\% effective because the state averages the RSV season start times by their initial cases. Using the Fairfield County numbers would seem to be the best idea because it would protect 5\% more infants. This would involve starting and ending the season based on the most populous county, because RSV always arrives a week earlier and ends a week and a half later, there. It should be used as a sentinel county.

An excellent point. Based on this feedback, we performed a post-hoc analysis of our data using RSV season timing in Fairfield county to generate three additional state-wide propxhylaxis schedules: one based on the start of Fairfield county RSV season, one based on the midpoint of the season, and one based on the end of the season. We applied 1-, 2-, and 4-week rounding to each of those schedules, and calculated the protected fraction.

We found that the schedules based on Fairfield county season timing are statistically indistinguishable from the schedules based on statewide season start and season midpoint. This is likely because the most populous Connecticut counties have similar RSV season timing similar to Fairfield county, and therefore schedules based on statewide timing are already similar to schedules based on Fairfield county timing.

We agree that using a schedule based on Fairfield country season start *and* end would confer a greater increase in protected fraction; however, that would increase the overall cost of prophylaxis because an additional dose would be necessary to cover both Fairfield county season start (1.35 weeks before statewide season start) and Fairfield county season end (1.38 weeks after statewide season end). This approach was therefore excluded from our analysis because we set out to optimize protection without increasing cost.

We have added a paragraph to the discussion highlighting these points.

##### Patients from the neighboring state, treated in Connecticut are not included in this analysis but they may well be the earlier harbingers of the RSV wave that enters the state and first appears in the most populous counties. Why wouldn’t they be included in this study? They might be the best sentinels if RSV is entering from even more populous counties in other states.

The practical reason for excluding these cases is that only the ZIP code of residence (not the ZIP code of hospitalization) is present in the data available to us, and therefore attributing an out-of-state RSV case to a specific county in Connecticut is not easily accomplished. (This was significant because county-level analysis was our goal from the outset of this study.) Since only 2\% of RSV cases in our data were from the neighboring states, we elected to exclude those cases.

Furthermore, in our county-level analysis, we already had to combine low-population counties into one analysis group to obtain adequate statistical power, due to the low incidence of RSV in those counties. Out-of-state cases are even less common (likely because out-of-state cases are typically hospitalized out-of-state, even if they travel to CT during their illness), and therefore aren't captured in our data. Due to the low number of out-of-state cases hospitalized in-state, they would have presented a similar challenge in our analysis.

That said, we agree that out-of-state cases likely play a role as early indicators of RSV season onset, and — with a different study design — could be a valuable input into RSV immunoprophylaxis policy.

\end{markdown*}
\end{document}

### 2021-04-20 RSVOptimization.rnw

@@
 In adults, RSV infection is typically asymptomatic or gives rise to mild respiratory illness.
-However, RSV infection often incites more serious respiratory illness in children, with hospitalization rates as high as 4.4\% in infants with no comorbidities, making RSV a leading cause of hospitalization among infants.\cite{Hall:2009gi,Hall:2013jo,Zhou:2012ho,Boyce:2000gz} \cbstart Adults act as a reservoir of RSV and thereore play an important role in RSV mortality and morbidity in infants.
-\cbend
+However, RSV infection often incites more serious respiratory illness in children, with hospitalization rates as high as 4.4\% in infants with no comorbidities, making RSV a leading cause of hospitalization among infants.\cite{Hall:2009gi,Hall:2013jo,Zhou:2012ho,Boyce:2000gz} \cbstart There is also an underdiagnosed burden of disease in the elderly, and adults can act as a reservoir of RSV transmission in the population.\cite{Htar:bi} \cbend
 
@@
 
+\cbstart The method we developed for this analysis can be applied to county-level or state-level analysis of seasonal RSV patterns in other regions, some of which are likely to show a greater relative benefit (due to a greater degree of misalignment between the RSV season and the AAP guidelines' prophylaxis window) as well as a greater absolute benefit (due to population size) than Connecticut.
+In particular, states of the US Upper Midwest and Pacific Northwest would likely benefit more than Connecticut, due both to their later RSV season and to the greater county-to-county differences in RSV season timing in those states.\cite{Weinberger:2015hj} A similar approach is applicable to other interventions against RSV that are sensitive to timing, including maternal vaccines and novel chemoprophylaxis, in regions where local surveillance data can be obtained.
+\cbend
+
 In summary, our analysis reveals the potential for a $\sim 1\%$ gain in preventable RSV cases in Connecticut when a locally-tailored two-week (rather than monthly) prophylaxis guideline is used in place of the established AAP guidelines.
@@
 Practical aspects of this potential gain --- such as implementation cost --- require further investigation.
-
-\cbstart Additionally, the method we developed for this analysis can be applied to county-level or state-level analysis of seasonal RSV patterns in other regions, some of which are likely to show a greater relative benefit (due to a greater degree of misalignment between the RSV season and the AAP guidelines' prophylaxis window) as well as a greater absolute benefit (due to population size) than Connecticut.
-In particular, states of the US Pacific Northwest would likely benefit more than Connecticut, due to their later RSV season.\cite{Weinberger:2015hj} A similar approach is applicable to any other intervention against RSV that is sensitive to timing, including maternal vaccines and novel chemoprophylaxis.
-\cbend
 

### 2021-04-20 paper/export-nature-scirep.py
Image credits in LOF

@@ -45,7 +45,9 @@ tex = re.sub(r'(?s)(\\documentclass[^\\]*)\\[^\n]*\n.*%%% end knitr preamble', r
 
 # Migrate figure captions to end of main/supplementary text
 tex = re.sub(figRE, '', tex)
-lof = r"\section{List of figures}" + '\n\n'.join(fr"\textbf{{Figure {idx + 1}: }}{caption}" for (idx, caption) in enumerate(captions['figure']))
+lof = r"\section{List of figures}" + '\n\n'.join(fr"""\textbf{{Figure {idx + 1}: }}{caption}
+
+\em{{Figure created using \texttt{{ggplot2}} version 3.3.2}} (\url{{https://ggplot2.tidyverse.org}})""" for (idx, caption) in enumerate(captions['figure']))
 tex = re.sub(r'\\listoffigures', lambda m: lof, tex)
 
 supplof = r"\section{List of supplementary figures}" + '\n\n'.join(fr"\textbf{{Supplementary figure {idx + 1}: }}{caption}" for (idx, caption) in enumerate(captions['supplementaryfigure']))
